\chapter{04}
\section{}
A Deal  

Oken and Jay's was not the only meeting to have taken place that night.  A little after the party at the Zone had finished, Jessie made a short visit to the local police station and inquired as to where the nearest G-TEP office could be found.  Oken's reading of the boy's forgiving nature had been far from the truth and now Jessie sat there in this office, which smelled faintly of liquor and waited for the police chief to make his entry.  Accusations of G-TEP violations were serious business and every effort had to be made to ensure that the perpetrators were caught and crushed.  

Jessie looked out across the park which was now only lit by the hovering lights, one of the parks many attractions.  Jessie pondered whether Oken would have expected it to be him who turned him in to the G-TEP.  The thought excited him as he concluded that Oken would probably never have suspected him.  This was going to be glorious, he was going to get back at the idiot once and for all.  Oken had often made jokes towards Jessie.  It was never meant to hurt, yet Jessie had always taken it that way.

As the hover-lights danced around on the parks surface they made playful shadows on the walls of the interrogation room in which Jessie was now situated.  He raised his hand up and played with the light like an innocent child.  The windows were slightly open and the bars which secured them joined in the puppet show.  Jessie could see no pattern in the lights movements and likened it to a symphony.  One set of shadows moved one way, then another set darted in front of it, all the time creating a complex light show which intrigued Jessie's mind for well over ten minutes.

When the police chief entered, Jessie immediately shrank back into his chair.  The chief frowned at him as if to question Jessie of his actions.  The snitch's expression was that of a five year old boy.  He didn't belong here.  The chief, who was wearing the normal black police uniform, sat down opposite Jessie and pressed a few buttons on the computer keyboard which lay in front of him.   He turned the paper like screen which was mounted in a stiff frame, so that Jessie could see it.  The young man could see the chief scrolling through reams and reams of records.  He presumed they must be G-TEP related.

``Do you know how many G-TEP allegations we receive every month?'' the police chief asked of Jessie.  The boy shook his head and the policeman noticed the large bump, which had appeared after the door incident.  The chief continued, ``Over six hundred.''  He paused, ``people seem to think that they can use it to easily remove others who are making their lives difficult.  Now that isn't what's happening here now is it Jessie?''  Jessie once again shook his head in a schoolboy like manner.  It had just occurred to the police chief what Jessie reminded him of, a weasel.  

The law enforcer shook his head and looked over at the small being that sat across from him.  ``I'm sorry Jessie,'' he said, ``but I just don't believe you.''  Jessie wasn't surprised in the least.  He took a small object from his pocket and placed it down on the table.

``I had a feeling you were gonna say that,'' said the boy, ``so I brought you a little proof.''  The object turned out to be a data disk.  The chief moved his hand forward to retrieve the disk but Jessie slid it away from him.  ``When do I get my money?'' he asked.

``When the offender is dead,'' came the reply of a second man who had just entered the room.  The police chief took the disk from Jessie and loaded it into one the computer's many drives.  Various accessing noises were heard and finally an image appeared on the screen.  It was obvious that Jessie had taken the footage from the producers control room.  His hands were sweaty and his heart was pounding.  The images showed Oken defying the laws of physics quite spectacularly and Jessie couldn't help but be a little impressed with his enemy's moves.

The police chief and the G-TEP enforcer were also impressed by the implementation of Oken's weapon and Jessie revelled in the attention that his footage had obtained.  It was, of course, the nature of the footage that had gained their undivided attention, but Jessie was not about to admit to that.  His ego was on a major trip and that would end no time soon.

As Oken moved, swiftly and skilfully, the light from the screen filled the almost black room.  The hover-lights in the park had been turned off since and the only external light now entering the room was that of the moon.  The enforcer took a cigarette out of his pocket and lit it.  He puffed several times and nodded slowly.  It looked like Jessie was telling the truth.  It looked like he was about to get his hands on the first temporal directive violator in the last three years.

The enforcer was, of course, still wary.  Computer animation was almost photo-realistic and even he couldn't tell the difference between some of these films and real life.  There was also the fact of the source to be considered.  Sitting there quietly playing with his fingers, the enforcer could not help but feel sorry for the pathetic little loser who sat before him.  There was a small part of him that felt a little jealous.  If Jessie's claim was indeed genuine, then he would be up for the reward approaching a sum of 25 million credits.

The only way to know for sure though, was to be there and the enforcer was already planning his deployment of troops, in order to trap and contain the acrobatic dancer who was performing unimaginable tricks on the screen in front of him.  He turned to Jessie and began to speak.  

``Jessie, you understand that as of this moment you are now under the G-TEP secrecy act of 2030.  If you so much as breathe a word of this operation to anyone, not only will your reward be forfeit, but it is probable that you could be incarcerated for a period of no less than 45 years and in the extreme cases, the offence is punishable by death.''  His words were stern and throughout the whole speech Jessie never looked up once. 

There was a pause in which there was enough time for the police chief to swat a fly dead.  Jessie knew exactly what the enforcer was trying to say.  If Jessie bungled the operation, then his life would effectively be over.  He didn't like the tone that the G-TEP enforcer used, but at the same time, he knew how important catching Oken must be to him and his team.  

Jessie looked up and spoke in a chilling tone which disturbed the other two men in the room.  ``I want to bring him down.  I saw what he did and he deserves to be punished.''  The police chief squirmed uneasily in his chair.  For a moment it seemed as if Jessie was the one interrogating the two law enforcers.  

The G-TEP enforcer nodded, ``OK then Jessie.  After a brief investigation, we'll begin the planning and deployment of troops to crush this guy.  We want to bring him down as much as you do.  Remember that.''   Jessie nodded and his brief moment of superiority was gone, evaporating into the ether as quickly as it had come.  It didn't bother Jessie in the slightest.  They believed him and Oken was finally going to get what was coming to him.  Jessie performed a grim little smile which the police chief could only describe as half-evil, half-weasel.

The enforcer left the room and closed the door behind him.  Jessie could hear his shoes making a slow tapping noise as he walked down the long corridor to the reception area.  The police building was an old one, full of long corridors that wound their way from room to room, sporting various off-shoots along the way.  In the hour or so that the meeting had lasted, Jessie had been unaware of the hum of distant traffic that now seemed to fill the room.  It was the early hours of the morning now, and Jessie's eyes were tired.  He rubbed them, and the chief realised that through this hard exterior lay a small boy who hadn't yet grown up.  Jessie's hard nature was all a façade.  

He spoke to the boy.  ``You go home now Jessie,'' said the rounded figure of the police chief.  Jessie was sure he could detect a hint of chubbiness in the man's voice.  He decided that it wasn't worth dwelling on now, stood up, and reaching down, picked up his coat which he had neatly folded and placed on the chair next to him.  He held the small package of material by the collar and shook it.  In one swift motion the package unfolded with a whoosh and Jessie put the long black coat on.  It was definitely not new and some holes were visible, along with a rather weird smell.  The chief guessed the smell that was emanating from the costume in front of him was a cocktail of various alcoholic beverages.

Jessie looked up at the police chief and for a moment he felt the urge to reveal his dislike for him.  He quickly concluded, it was not the best of ideas.  Even though he didn't like it, Jessie needed this man and his balding friend, who had departed not five minutes before.  He opened the door of the room and the click from the latch echoed around the reverberant chamber like a pistol shot.  He paused, gave the police chief one last knowing look and then closed the door behind him.

As Jessie walked down the long corridor he could feel the swish of air on his legs, made by the swaying folds of material which hung off of his body.  His dark black boots made a crunching tone on the stark tile floor and occasionally left marks in the layers of polish which had built up over the months.  The police stations in the Emblem were fairly quiet places now and it was not uncommon to go a whole half-day without a single customer.  

Jessie was being watched by the police chief who had exited the room in order to check on the weasel-esque figure who had now reached the reception area.  Jessie never paused to listen or reply to the electronic receptionist's friendly greeting.  Instead he barged his way through the automated doors, not waiting for them to open for him, and made his way home.

It looked as though Jessie was angry, though there was nothing that he had to be angry for.  He had gotten what he wanted.  He had obtained the police and G-TEP's backing.  Now all he had to do was to wait and not give the game away.  Easy, thought Jessie as he began his long walk home.  Easy.

