\chapter{47}
\section{Revelations}


As he was flung into the air, he felt the train shift through him.  In an instant he could see every part of the carriages as they ripped through his out of phase body.  The pain, once again, was excruciating, made all the more real by the cuts and bruises he had sustained.  As his body started convulsing, his lacerations opened up, pouring blood into the void that was the shell.  It swirled in the viscous ether, defying gravity and all laws of physics.  It hung in the air and coated the otherwise perfectly white shell with a worrying tone of pink.

The train was now far from sight, it hadn't felt close to him for what seemed like an eternity.  As his body moved in an apparent convulsion, he opened his eyes.  He could see all the events in that location flooding through his senses like jumping under a waterfall.  It washed over him.  He was unable to pick out anything specific, but it was a truly spectacular sight.

His body calmed down as the sphere contracted on him and for a moment he was in complete peace as his body was whisked through a tunnel like construct.  It was white, pure white, with the occasional line joining up with each other along its winding path.  He could feel all the experiences since that moment in the past, he closed his eyes.  Last time he had travelled he hadn't had time to enjoy it.  He had been too scared to open his eyes, to let go.  This time he knew different.  This time he was ready.  He braced himself for the re-entry to the basement.  

The sphere hung there for seemed like an eternity, covering his body with a warming feel.  He looked down at the injuries he had sustained in the train.  As his suspension diminished, his lacerations did too.  The sphere collapsed wistfully, leaving Zane sat in the middle of the room dazed and confused.  His cuts and bruises gone.  He had been healed, preserved in the same state as which he had left.  As he looked up, he was instantly aware of two figures suddenly getting to their feet.  One was Ruben, the other was Mark.  

The two ogres were locked in a struggle, a battle.  Shortly before Zane had arrived back, Jessie had made his way back through the fabric of time to end up once more in the basement.  This time though, he had been surprised to see the basement wasn't empty.  Ruben, upon seeing that the returner was Jessie, had pounced on him and had started beating him in the face.  

Jessie had begun by laughing, until he had realised that the punches weren't getting any lighter and seemed to be going on for eternity.  He had pushed Ruben off of him and then begun to search for anything he could use to disable the black figure.

Zane was still blinking, his eyes suffering from the shift, as the huge figure of Ruben landed next to him.  He scrambled over to the corner, realising he was in no fit state to do anything other than recuperate.  He watched as the weasel picked up a long steel pole which had been used to prop up a makeshift washing line.  Jessie swung the pole towards Ruben, but the burly figure managed to just hop out of its way and return to his feet.

Zane's eyes continued to watch the pole as it continued onwards, spurred on by its momentum.  It flew through the air before coming into contact with the delicate chin of a certain young lady.  Jolie cried out as the rough edge of the pole sliced through her neck.  It wasn't deep enough to kill her outright, but she was beginning to lose blood rapidly.  The pumping of her heart made the red goo spray out into the room, showering its floor with her life force.  

Kiele screamed and narrowly missed being hit in the face herself as the pole continued on its fateful journey.  Zane scrambled over to Jolie as the two men fought.  Jessie punched Ruben in his already disfigured face.  It didn't hurt.  Nothing hurt any more, thought the bouncer.  It was his job to keep out the bad guys and protect the good.  It was no different to what he had been doing years ago in the Zone, just with a lot more at stake.

The pole came back from its journey and almost clipped Jolie again as Jessie tried in desperation to silence the retard in front of him.  He threw a head butt and caught Ruben off guard.  His nose smashed in a cruel revenge.  Ruben stumbled backwards and fell into the shelving which divided the basement.  

Though the shelves themselves remained upright, the force of the burly man crashing into them had been enough to dislodge practically everything which had called the wooden structure home.  Ornaments, components and various files and papers were strewn across the basement floor.  Zane was slowly beginning to regain his composure, Jolie looked comfortable enough.  She was holding her neck with her hand at this point in time there was precious little they could do to get her out.  

Zane stood up, trying in desperation to regain his balance.  He swayed a little.  Kiele, noticing his fragility tried to reach him, but Jessie was too quick for her.  As she crossed the room behind him, he assumed she was going to attack him.  He spun around in a half circle and punched, not even looked where his fist was going.  It hit her in the side of the face and sent her flying away from the antagonist.  

Her protector saw this happen in slow motion and instantly gained some lost coherence.  He sprang to his feet, grabbing a wrench from the workbench as he did so.  His body now somehow airborne flew gracefully towards an unsuspecting Jessie.  The schemer had had his back to the boy, enjoying the aftermath of hitting that little witch in the face, and watching her pompous educator bleed out all over the floor.  

Zane wrapped the wrench round Jessie's neck, instantly knocking the wind out of him.  As the other end of the wrench became visible, Zane grabbed hold of it with both hands and yanked backwards.  The new titan tumbled backwards to the floor.  Where the boy was already waiting with a shin which he planted heavily on the fallen man's skull.

From underneath the debris from the wreckage, Ruben found an ounce of extra strength.  He lunged forward and lay across the writhing figure of a former threat.  The dark skinned man punched Jessie hard in the stomach and the insects body doubled up as it died a little inside.  

The pain ripped through Jessie like a dog through silk, its teeth well and truly sunken in.  It was agony.  He couldn't breathe properly, yet at the same time he felt like laughing.  His stomach was in pain, but his head was as calm and clear as a summers day.  Ric would be watching for the second leap in time.  Though Jessie hadn't expected Zane to have made a jump, he knew that Ric would be expecting his call.  When it didn't arrive he would come and investigate himself.  

The little child roared with laughter and out of character completely, Zane punched him in the face.  It knocked the laughter out of him, yet the smile still remained on his lips as he licked the blood that the boy had managed to spill from his crushed flesh.

``You just don't get it do you,'' he said gleefully, trying to breath through the restrictions of both Zane on his neck and Ruben on his chest.  ``There's nothing more you can do now.  It's over.  We have won.''  He seemed a little insane, like a bad actor in a movie playing someone from an asylum.   

Jolie coughed in the corner and her body started to lose all the life that it had left in it.  All their eyes had been focussed on Jessie.  Kiele was still out cold on the floor, lying in a crumpled heap.  Zane looked across at Ruben who motioned for him to go help Jolie.  As he released his hold on the python below him, the snake exploded throwing both of them away.  How had he managed to keep back that much energy?

The weasel made a break for it and ran up the stairs.  Ruben and Zane were in quick pursuit.  Zane turned back to look at the two girls lying helplessly on the floor.  He left Ruben to deal with Jessie and ran over to Jolie.  

``Come on Jolie,'' he said frantically.  His thoughts and actions were now totally focussed on her.  Kiele was out cold, but Zane knew she was relatively OK.  Jolie on the other hand was about to die, there was no doubt about it.  He gently tapped her face with his hand trying to bring her back into consciousness.  ``Come on damn it,'' he screamed.  

From the doorway to the basement, he could hear Jessie laughing.  ``She'll never make it,'' he screeched before Zane heard another thud as the dumper truck sized fist of Ruben rained down on the man's skull.  Zane couldn't believe she was already gone.  He took hold of her shoulders and shook her a little.  Her head flopped forwards in complete freedom.  There was nothing there.  He tapped her again, a little harder this time and she coughed again.  

The breathing had come as a surprise to him and he half expected her entire body to lift up off the floor.  The convulsion of coughing had roused her into a new sense of life.  She was breathing on her own and relatively steadily.  He looked into her eyes as she opened them.

``Jolie, you gotta stay with me,'' he said, ``You have to stay with us.''  Her head rolled around a little as she tried her best to remain present and correct but it was getting harder and harder.  She could feel everything slipping away.  She wasn't entirely sure who it was sitting in front of her.  There were aspects she remembered, pain, her neck, the floor, but others that seemed to have been part of some distant time, Zane, Kiele, Ruben?

It was only now that Zane realised just how much blood there was on the floor.  It was a sea of red, travelling across the stone floor, making its way in every direction.  If it hit an object in its path, it would just subvert it, shocking every one with its shade and purpose.  If she survived it would be a miracle.  If she survived.

The shouts and screams from upstairs started to get louder and as Jolie seemed to be stable, Zane made a run for it.  They couldn't let Jessie get away, it would have been worse than suicide.  He felt bad for leaving Kiele, but she would be fine.  He knew that.  She was tougher than she looked.  

Zane darted up the stairs and grabbed hold of the first part of Jessie he could to pin the monster down.  He was laughing again now.  Laughing at how it was taking two of them to hold him down, when he was only one little man.  People had made fun of his physique for years.  Now he had proven that he wasn't all that weak after all.

Jessie was now on his front on the floor, with Ruben on his back and Zane holding whatever extremities were being aimed at the heavyweight in the middle.  Jessie looked back at Zane.  

``Bet you never saw this coming did you?'' he said, grinning from ear to ear, intending his words for Zane.  ``I'm surprised you're not down there looking after your little bitches.''  He spat the words towards the young boy who looked at him with immediate disdain.

``You make me sick Jessie,'' he said, ``your own daughter.  You put your own daughter's life in danger.  How could you do such a thing.''  Jessie roared with laughter, it was like a game now.  He knew it was only a matter of time before Ric came.  Only a matter of time before everything would pan out just as they had planned.  Though neither of them had expected Zane and crew to show up, there was always a contingency plan.

``Relax,'' he said softly, ``It's not like she's my real daughter.''  He laughed again, ``She's not even my own flesh and blood.''  Zane looked confused.  ``I made her.  I created her as a bargaining chip.  Tell them Rubie.  Tell them what an evil little boy I've been.''

Ruben remained silent as the weasel still thrashed and kicked his legs.  Zane was having trouble comprehending what Jessie was saying.  If he wasn't her father, then who was.  He knew Kiele had been born In Vitro, but he had assumed that Jessie had been her biological father.  When Jessie spoke next, it was almost as if he was reading Zane's mind.

``Of course I'm not her biological father.  She's worthless, weak, how would she get any of those traits from me?''  He was giggling to himself now.  The disorder took full hold of him as his anger broke free.  ``Do you know how many times I wanted to kill her,'' he shouted, ``Do you know how many times I went into her room at night with a knife and pressed it against her throat until she almost choked.''

Zane put a hand across his face.  He had never in his life met a man so evil.  He had never before witnessed someone with such malice.  It was scaring him to the core and to think he had shared a house with this man, he had shared his time with this man, at several points almost wishing he would call him son.  Wishing he could be a father to him.

``Don't you want to know who her parents are Zane?'' asked Jessie, ``Don't you want to know?''  He spat on the floor, the blood from his lips now mingling with his saliva.  ``Your beloved Oken and his whore of a girlfriend.''  Jessie had been well aware of Zane's respect for the man.  He had read his assignment.  The one which he was still finalising.  Jessie's description of Jay had been entirely incorrect.  It hadn't even been an exaggeration.  The detainee was merely trying to coax Zane into an explosion of anger.  If Zane lost control, chances are Jessie could over power them both.

``I killed them both you know,'' he said proudly.  ``Indirectly of course.  I saw Oken using his blade and he thought he was king of the world.  He thought he was king of the universe.''  His tone changed once more, he became sullen, calculating, cold, collective.  ``But I won in the end didn't I Oken, I won in the end.  You son of a bitch, I got you.''  He turned to Ruben and roared with laughter, his eyes bulging out of their sockets.  ``She was too, wasn't she Ruben.  His mummy.''  He turned back to the centre again and looked down the hallway before breathing in as deeply as he could and letting out a scream of pain, anguish and sheer thrill as his disorder took hold.

Jessie didn't see the saucepan that knocked him out.  Ruben had been inching and inching towards the rack of pans as his victim had enjoyed his rapid verbalisation.  Jessie had wanted to disclose his plan so badly.  He had wanted to show everyone how clever he had been.  How smart he was.  

As Zane turned to look down into the basement, all he saw was a sobbing Kiele.  She was looking up at him with the largest, wettest eyes one could imagine.  She had heard every word.  She had always known that her father had hated her.  No, she rephrased it in her mind, she had always known that Mark had hated her.  Now it turned out Jessie had too.  

She looked down to her shoes and Zane was instantly aware of the returner device in her hand.  ``I'm sorry Zane,'' she said, ``I have to.''

The young boy leapt off of Jessie and almost flew down the stairs, he screamed the word 'No' as he fell forward.  She pressed the button and the basement was once again filled with the white shell.  He clasped his hands to his ears and then caught a glimpse of the slumped figure of Jolie.  He jumped through the railings.  Poor Jolie wouldn't stand another trip through the shell.  

Zane ran towards her as fast as he could, his muscles aching from all of his previous actions.  He lifted her limp body and curled his hands round her.  The shell was beginning to expand and he reached the bottom of the stairs just as it touched his foot.  He seemed to be anchored now and though he tugged and tugged his foot seemed stuck inside the shell.

Ruben appeared at the top of the stairs and stumbled down towards Zane.  He took the bleeding figure from the boy and effortlessly carried her up and out of harms way.  He ran down the hallway, figuring that moving in a straight line would get him as far away as quickly as possible.  

The shell exploded outwards and then in its customary fashion, receded quickly and Kiele was gone.  Zane thumped to the floor hard, again and again and again.  His knuckles bleeding and splatting their mark all over the stairs.  

``Damn it Kiele,'' he shouted at the top of his voice.  ``Damn it.''

Ruben began to tend to Jolie.  She was on the floor now, looking up at him and appeared to be much more coherent than before.  He couldn't quite put his finger on it, but there was a strange aura about her.  She was stable.  He got up and walked towards the basement doorway.  

``Where did she go?'' he asked Ruben.  Zane read off the date from the readout.  ``Just before Oken's first fight by the sounds of it.  She'll be back soon I'm sure.''  It had only taken a few minutes for Jessie and Zane to return.  The clock ticked by idly.  There was no sign of her.

Zane looked at the computer readout.  Something was wrong.  'Active Tethers : 0'

``Damn it,'' said Zane, ``She's not coming back.''

``Why do you say that?'' asked Ruben, he couldn't quite understand what extra information the boy had.  Zane ran to the top of the stairs.

``There are no tethers,'' he said, ``She's completely cut off.''  He looked at the power cells.  There was one left.  There was nothing he could do.  With only one power cell he couldn't go back and save her.  Something had gone wrong in the past, something had happened.  He just didn't know what.  Perhaps he never would.

He walked back down into the basement as Ruben turned to go and see Jolie.  She was looking towards him now and had regained some of the strength in her neck.  She needed an ambulance.  

``I'm going to call the ambulance,'' said Ruben, ``Take care of that lowlife for me, before I do something I really shouldn't.''

Zane nodded and walked around the basement searching for something, anything that he could use to bind the prisoner.  It would have to be strong.  He rummaged through the debris that had fallen from the shelving and picked up a nice bundle of old fashioned cable ties.  As he did so something caught his eye.  

There was a photo, clipped to a report.  It was of a girl lying in the street.  She was badly injured, blood everywhere.  There was something familiar about her.  He picked up the folder and read the title.  ``Misplaced Persons''

He took a closer look at the photo, the colour now seeped into his mind.  A purple blazer.  Kiele had been wearing a purple blazer just before she had left.  It had been customary for all the higher class girls to wear purple.  Kiele had opted for the blazer.  

Zane flicked through the pages of information and saw something about a lack of records, something about a lack of DNA records.  Signatures from G-TEP agents littered the pages.  Apparently Jessie had been involved in investigating these types of cases at some point.  

He clasped his hand to his mouth as he saw something protruding from under the girls skirt.  He tried to tip the photograph to get a better view.  A bandage.  The girl was Kiele.  



\thoughtbreak



``If I go, I can't ever come back,'' said Zane.  The ambulance was audible now, tearing down the street.  

``I know,'' said Ruben, ``The decision is yours.''

Zane looked across at Jolie.  The three of them had been sitting there talking for the last five minutes or so.  Jolie's voice was feint, but audible.

``Go and save her,'' she said, ``Go and save them all.  Jay, Oken, Kiele.''  Her voice seemed to crack at the end, and when Zane looked up at her, he saw she was smiling.  She nodded to him.  He loved Kiele so much, was he ready to give up everything in this world and live in the past?  Was he really ready?  

His mind answered immediately.  Of course he was.  Kiele had been the only decent thing in his life since his parents had died.  She had been his rock, his anchor, his love.  Her touch had been able to soothe his every anxiety, his every problem.  She was his soul mate and he would travel through space and time for her, to protect her.  

``But what about you two?'' he said solemnly.  ``What about your futures?''

``Zane,'' Jolie began, ``Look at me, if this can give me a second chance, I'll welcome it.  I spent far too much of my life obsessing over the past and look where it got me.''

Ruben chimed in to, ``Yah, Zane, I don't want to have to go through the last twenty years again if I can help it.''  He chuckled.  ``Go for it my man.  Change the past, give us a better future.''  

The ambulance was getting louder, and all at once Ruben's faced changed, as if he'd remembered something.  He ran into the kitchen and looked around frantically, opening drawers and cupboards.  Cutlery flew everywhere, and he even managed to knock a plate onto the floor.  It smashed outwards, mimicking the motion of the shell.

Ruben ran back to the hallway complete with a pad and a pen.  The pad had a logo at the top, 'Mitsumi's Bar : 7746 Bleaker'.  He began writing something furiously.  Zane looked over his shoulder, but was unable to make out the writing as the pad jolted up and down.  Without waiting for Zane to read it, Ruben tore it off, showering the nearby air with tiny paper particles.  He folded it up neatly and gave it to Zane.  

``You have to find a guy named Leon Jackson,'' he said.  ``I've given you the address.''  Ruben retracted his hand, leaving the folded piece of paper in Zane's palm.  He looked down at it and then back up.  

``Ruben, what is this?''

``It's a chance to save another man's life,'' he said before adding,  ``No pressure.''

Zane put the piece of paper into his pocket and stood up.  Jolie looked up at him.  She admired the boy so much, his strength of character.  He was going back in time to change the past, to try to convince Oken not to fight, to try to convince him to give up the blade.  Though she felt she had known Oken all her life, even she couldn't predict his reactions to the young boy.  

``Zane, I'm so proud of you,'' she said.

``May God be with you,'' said the large bear.

Zane walked down into the basement and tapped on the keys for what would, in all likelihood, be the last time.  He looked down at the photograph which he had placed on the bench and smiled. 

``Don't worry Kiele,'' he said, ``I'm coming.''

His finger hesitated over the button and he allowed himself a quick look back up the stairwell to see Jolie and Ruben.  The ambulance was just pulling up, he had to go now.  He pressed the trigger and once again succumbed to the pain.

Unfortunately Ric had seen the dispatch information and had jumped to the correct assumption, Jessie had failed.  Now Ric was on his way to clear up the mess that the little weasel had created, but there was no way Zane could have known that.



