\chapter{06}
\section{Beaten Track}


The train was moving faster now and he was sure he couldn't stop it even if he wanted to, but he had to try.  He was sure it was his destiny.  He was meant to stop this.  If he didn't?  Well he really didn't want to think about that.  The consequences were too much to bare.  This was a decision he'd made unreservedly and he wasn't about to back out now.

As he ran through the first carriage, he mentally programmed his destination.  Though he had never driven a train before, he knew they were normally controlled by one of the end cars.  Weren't they?  Since he had started at one end of the train, logically he would need to reach the other end.  It was a straight path, but his time was running out.

The train was older than most, probably around 40 years.  A real veteran by the present day's standards.  The older trains were still used as show pieces at exhibitions, or sometimes to transport freight slowly from one destination to another.  

It moved through the tunnel at blistering speed and the air around it was completely at it's mercy, being compressed and thrown against the tunnel walls.  The lights on the front of the train had a hard time keeping up with the moving scenery.  It was almost as if the light was trying to grab hold of the weeds and gravel as it zipped through the deep dark tunnel, but just couldn't quite make it.  Sparks flew from the trains wheels as pressure from cornering became too much.  

He reached the end of the first carriage and hammered on the button to open the adjoining door.  Nothing happened.  He took a step back and kicked it.  Still nothing.  He fumbled and pulled on the manual door release.  His heart was pounding and he wasn't quite strong enough to move the metal clasps.  He turned and looked at the metal kick railings running across one side of the train.  One section in the middle of the carriage was slightly loose.  Kicking it with all his might, he gained himself a lever and ran back to the door.

This time the clasps gave way easily and he managed to pull the doors open.  His face contorted with the amount effort he was required to expel.  He had never worked so hard in his life.  Air rushed in through the doorway, throwing grit and sand into his face.  The surround covering the gap between the two carriages had eroded a long time ago, and flecks of rubber were still being torn away as the train ripped through the air.

Making it through the next doors proved more difficult.  The clasps had seized, though he couldn't see it at first.  He tried the same trick he'd used on the previous door, but to no avail.  This time the door was stuck fast.  The sheer desperation on his face was clear.  He had to do it.  His mind was racing.  He had to get through the door, no matter what.  He looked up, climbing along the top of the train carriages was certainly an option.

The ladder to the side of the carriage was easily reachable and he climbed it with ease.  It was almost exciting as the air rushed past his face, distorting his cheeks and playing with his hair.  As he reached the top, a cable hanging from the roof of the tunnel hit a protruding part of the train, causing it to slap round to the side of the carriage, catching him in the face.  He screamed out as the sharp end of the cable lacerated his cheek.  Blood was being pulled from his body by the pressures created by the speed and it hurt.  

He grit his teeth and bit back on the pain, channelling it deep down.  He had to push on.  The roof no longer seemed an option.  Rapidly running out of time his frustration was turned to the glass window in the door ahead.  He looked at the tool still in his hand and then looked towards the window.  His hair whipped his face and the decision was made.  He slammed the tool into the glass again and again.  Tears began to well in his eyes.  He couldn't give up now, he just couldn't.  The noise of metal against toughened glass still couldn't really be heard above rumbling of the carriages against the ageing rails.

Finally the glass gave way in an explosion of shards.  Most flew drearily into his face and body, managing to avoid the pull of the air.  Had they been caught by the rushing tornado he would have been cut to shreds.  The gap was narrow and in climbing through to the next carriage he managed to slice his leg just above his ankle.  Almost not realising he continued, spurred on by his recent success.

As he ran through the second carriage, he tripped on a cable that some careless worker had left strewn across the floor and fell.  He hit the ground hard and it must have been about three feet before his body eventually came to a stop.  His chin had hit the ground and sent a shock-wave up through his bones to his cheeks, which began to pulsate in pain.  His eyes went blurry and he could feel himself losing consciousness.  ``No,'' his mind shouted.  ``Don't give up.''  But it was too late.  He felt the last trickle of conscious thought slip through his neurons and collapsed.



\thoughtbreak



When he came to there was no period of disorientation whatsoever.  He checked his watch, that beautiful old watch.  6m32s remaining.  He picked himself up and gasped at the pool of blood which he had left behind on the floor.  He was probably going to need that later.  He was also going to need some kind of medical attention if he made it out of here alive.

He began running again, and at the end of the second carriage, caught a glimpse of himself in one of the side door windows.  He was a real mess.  His clothes were stained in blood, and not the freshly coloured red blood either.  This stuff was thick and dark, making a kind of paste with the fabric.  

There was no time for self pity now.  Motivated by his own progress he began to attack the door in front of him.  Up in the top right hand corner of the door, almost smiling at him, was the number of the carriage, seemingly self illuminated by it's own material.  264.  He smashed his way through the door, having been unable to open the clasps once more.  He now realised that all the doors had been locked.  He had to move faster.

Above him to the right was an advert for Doxoproctamil, the wonder drug, though recently it had been discovered that it's long term effects were far from wonderful.  Doxoproctamil had been invented as a pick me up drug with apparently zero side effects.  It was supposedly a miracle for modern medicine, using only natural ingredients and promoting wakefulness and increased brain activity in the subject.  What the pharmaceutical companies had neglected to do was to perform long term studies on animal subjects, having been petrified of action by animal rights agents.  

Any pharmaceutical company testing on animals has always, throughout history, had a bad name.  The leading Doxoproctamil developer had managed to keep its testing out of the limelight so far, but the more rigorous testing that this drug so desperately needed would require a whole new facility and creating a whole new facility meant questions, inspections and guided tours.  

The result was a drug that worked fine for about ten to fifteen years of usage.  After a certain amount of the drug had been ingested by a subject, the body just stopped caring about everything.  Metabolic rates slowed, people became fatter and lazier.  Their brains, ravaged by an untested drug became slow and sluggish.  Doxoproctamil users were given the nickname 'zombies'.  

After about two years, conversation and general day to day interactions with the zombies became impossible.  They literally wandered around like their namesake, picking up food where they found it, and sleeping wherever their body gave up for the day.

After the euthanasia bill had been passed globally, much to the disgust of many religious groups, the zombies didn't stand a chance.  Police workers had been given the power to shoot people in that state in a supposed act of compassion.  The truth of the matter was far from it.  Some police workers used the excuse of ending a zombie's suffering to humiliate them and turn it into a game.  

He saw the advert and it immediately made him remember a story he had been told by his father.  His father had told him about the time he had seen a police officer playing a game known only as 'riddled'.  Essentially, a police officer loaded their gun and tried to shoot the former human being as many times as they could without it falling over.  

Once Doxoproctamil had been discovered to cause such effects, the suppliers trading days were very much numbered.  Several religious and extremist factions, terrorists in all truth, collaborated and planted high yield explosives at all Doxoproctamil sites, before killing the president of the company and destroying all known stock of the Doxoproctamil drug.



\thoughtbreak



Smash.  Another window.  He'd made it to the third carriage now.  The glass glinted in the light from the carriage lights and produced distorted patterns all around.  He was blissfully unaware of the tiny glass shards which were now embedded into his shoulders.  His mission was too great.  His drive was too extreme.  He had to get to that last carriage and for a second his mind stopped, though his body continued.  What would he do once he got there?  What did he expect to find?  How in the name of all things temporal was he going to stop this thundering beast?  

The designers of the train had done a good job of stopping people being able to run through the carriages.  He managed to bruise himself at least three times in this carriage, smashing his shins and arms into various protruding pieces of wood as he clumsily made haste through the narrow gap between the two sides of seats.

He was almost sure he could see the end of the train now.  His steps became heavier and his energy was getting sapped by the second.  Each step seemed to take an increasingly large amount of time.  His reserves were running low and he wish he'd eaten more of that breakfast.  His shoes were in almost as bad a state as he was.  The laces were worn from being trodden on, and to add to that they now had beautiful red streaks down them, hand painted by the blood oozing from his legs.

Smash.  Another window.  Surely he must be there by now.  As he stopped for a breath, he saw the electronic sign displaying the information ``This is coach 3 out of 8.''  The LEDs in the display were faded and many were missing.  He almost had trouble making out the words, but was thankful when he did.  He was almost there.

With his heart pounding that little bit faster he broke through into the next carriage.  A portion of the floor was missing here and he could see the ground merrily flying past him, not stopping to say hello, or to help his fear to subside.  He could easily run and jump over the gap, but how sturdy was the floor close to the hole?  He had no idea.

He thought back to using the roof again, but a quick touching of his cheek made him a) wince with pain and b) realise that the roof was still not an option.  If anything the train had increased in speed since then.  Looking upward he saw the railing which passengers used to hold on to when the number of seats was less than the number of passengers wishing to sit in them.  Even though it was old, the metal still shone.  Good old stainless steel, he thought.  

He grabbed hold of the rail and immediately left dirty marks all over.  The blood stained, grubby, fingerprints of a man on a mission were smeared all over the otherwise spotless railings.  He managed to hoist his body up, though how he managed it was a mystery to him.  He flung his legs over the railings so that he was now essentially hanging from this horizontal pole.

The idea had been good in theory, but he had forgotten all too soon about his bad leg.  As soon as he had swung his leg into the air, the blood rushing to it excited his neurons and gave him a quick indication that this really wasn't the best of ideas after all.  This was no time to be giving up however and inch by inch he worked his way along the railing, dripping blood and sweat into the void below.  

At about halfway along the railing, directly over the hole, one of his hands slipped.  It could have been the blood or the sweat or both, but something didn't want him to get to the other side.  As his weight shifted, his other hand was no longer able to hold all the mass of his body.  He fell, but luckily his reactions were a little quicker than gravity.  He tensed his leg muscles and locked his feet together.  As the rest of his body fell, the weight on his legs pushed his wound onto the railings and blood sprayed out all over the train and all over him.  His free-falling body was stopped by a chair, which had inappropriately been left half destroyed and overhanging the hole.  

His head slammed into the metal chair's railings and he instantly realised why this chair hadn't just fallen into oblivion.  Metal was hard.  Metal hurt.  A part of him wished the chair had given way at that point.  Put him out of his misery.  His mind was fuzzy and all he could think about were doughnuts with pink sprinkles.  Which was strange as he hadn't eaten a doughnut, let alone one with pink sprinkles, for many years.

He could feel himself losing consciousness again.  His head had been put through it's paces recently and it was all getting too much.  A voice started shouting.  ``Get up.  Do it.  Carry on.  You must.  Get up.  GET UP''  In an instant everything was quiet, as if his mind was clearing the way forward.  He put all his effort into pulling his body up and grabbing the railings.

He was only two or three feet from the end of his overhead journey and he so desperately wanted to finish.  Everything hurt.  He carried along, moving faster and faster.  Thinking how proud he was of himself as he got closer and closer to his goal.  The voice inside spurred him on, and he finally reached his destination.

What happened when he got there was a moment of sheer ambivalence.  His muscles just gave way and he fell five feet from the railing to the floor.  Half of him was pleased that his muscles were able to relax, if only for a moment.  The other half berated him for hitting the deck so hard.  He couldn't win and yet he must.



\thoughtbreak



The speed of the train had now begun to make the small air cracks in various parts of the chassis whistle tunes.  For a second he lay there, wondering how different tones were possible.  He couldn't help it, it was the academic inside him.  It would most likely be linked to speed.  Not the speed of the train so much, as the speed of the air rushing past the gap, though obviously the two were related.  

With the width of the tunnel varying slightly in places, the same amount of air was being pushed through larger and smaller surface area spaces between the train and the tunnel wall.  Smaller gaps mean the air had to travel faster to get the same volume through per second.  Elementary really.  

The tones still troubled him.  These tones were all over the shot.  Maybe it was his blurry brain, maybe it was his lack of coherent thinking at the moment, but these tones did not seem natural.  He got up and looked around before seeing what he feared most.

There was a figure standing at the end of the first carriage, in the drivers section though he knew he was no ordinary driver.  He was gripped with uncontrollable fear.  Just how was this going to go down.  He hadn't been spotted yet.  He looked all around him for something to give him an edge, but there was nothing.  He hadn't remembered his trusty window smashing tool, which had been left over the other side of the carriage.  That's the trouble with clouting your head with metallic objects he noted.  It was good advice.

When he looked back at the engineers section again, the figure was gone.  There was no shadow, no figure, no indication that anyone had ever been there, aside from the unmistakable speed of the train hurtling towards it's target.  He managed to get the next door open without using any tools.  Maybe he'd gotten stronger, or maybe this one was just loose.

In the final carriage, he was immediately aware of the smell of blood and death.  It seemed to be a sense he had.  He looked over to his right and walked forward, there was something there.  As he got closer, though his blurry vision he could see it was a person.  A person in a train drivers uniform.  The shiny label on his shirt spelt out the name 'Markus' and it was marked on a gold background in red letters.  He noticed the pool of blood cradling the man.  It seemed almost as if he belonged there.  

He'd reached his destination.  With one mighty push, he managed to open the door to the engineers section.  The control desk was spread out before him, but he had no idea what buttons to push.  In the bin next to him, a small fire was raging.  He bent down and was able to just about make out some of the text on the front cover.  ``Eng..... Tr........ Manu....''  Engineers Training Manual he guessed.  Damn it.  

Just as he was about to give up he heard coughing from behind him.  He spun round to see Markus the train driver spluttering.  Blood was being projected from his lips and was spraying over the train floor.  His head was cocked to one side and hung in an odd fashion.  It was only now that he'd moved slightly that he could see what had caused his injury.  Several shots through the stomach.  He ran over to Markus and knelt down beside him.  He felt bad for what he was about to do, but he really had no choice.

``Hey there, look I'm sorry for what's happened here, but I have to stop this train.  I must stop this train.''  he said.  Maybe Markus had heard the sheer desperation in his voice, or maybe he just didn't care, but he slowly nodded to his new companion.  His death partner.  Markus looked out of the window.  The train was going really fast now and the lights in the tunnel, which could usually be used as a good indication of speed by counting time between them were just a blur.  Markus knew in his mind there was only one real way to stop the train.  

``De...de...deral'' he said.  Even though Markus' pronunciation was a little off, he still understood what had been said.  He had to derail the train.  Though he had never driven a train before, he had even less experience in derailing one.  He guessed he'd need to make the carriage jump off the track by putting things in it's way.  But what exactly?  The train was heavy, and he just couldn't think of anything suitable.  Then he had an idea, it was risky, but it was all he could think of.



\thoughtbreak



As he swung the oversized fire axe towards the window he suddenly had a feeling of dread.  He had experienced high speed air currents at earlier points in the train, but the holes had been smaller then, and the train going slower, what the heck would happen now?

The axe tip flew through the air and sliced it's way to it's destination making a practically inaudible whoosh as it went.  As the blade struck the reinforced window, he realised that he had twisted a muscle in his shoulder, but that would just have to wait.  The tip dug in hard and forced a small shard of glass to fly out into the world outside the train.  It struck the tunnel wall and shattered into a further thousand pieces.

It was almost half a second later when the window exploded inwards.  The tip had shattered the glass, but the force of the air pressure had pushed it over the edge.  The window went from transparent to opaque in a matter of milliseconds as thousands of cracks wound their way to the edges of the frame.

Shards and plates flew towards him.  He threw up his arms around his face to offer some protection.  At this point he didn't really care much what happened to him.  Some smaller shards dug into his arms and other exposed flesh, making his face grimace with pain.  It was like taking a shower with a thousand knives.

The wind was almost unbearable and he was sure that it was driving the glass deeper and deeper into his arms.  He had to do this.  He had to stop caring.  He gripped the window frame with both hands and realised his mistake.  Through the slitted eyelids, protecting his vision, he had neglected to notice the few shards still sitting in the frame, now embedded in his palms.  He threw his head back and screamed.

The grenade in his pocket had seemed almost unnecessary when he had left.  Now it was going to be his saving grace.  He leaned out of the window and found a suitable location on the outside of the train, just above the window frame.  Elementary physics told him that applying a force at the top of the train would be much more likely to tip it, than applying it the lower down.  He had found some tape in the drivers cabin, and with this he taped the grenade to the side of the train.  He plastered the grenade with as much of the sticky stuff as he could muster.  

A thin rope had been also coiled up nicely in the engineers cabin.  He attached the rope to the pin, and uncoiled it.  It wasn't a lot, but it would do.  It should offer him enough time to get out of there.  His plan seemed crazy but deep in his mind it didn't matter how stupid it seemed, he had do it.  He had to save her.  His adversary was an oversized bullet, travelling through a barrel which twisted and turned to its eventual destination, and he had to do everything in his power to stop it reaching it.

His heart was pounding more than ever before.  He may not make it through this, but he had to try.  He ran to the nearest seat, hid behind it and tugged on the rope gently, nothing happened.  1m12s the watch displayed.  Damn.  There was no time.  It really was now or never.  He pulled the rope harder and this time pin flew out inadvertently becoming one with the tunnel wall.  The roped whipped away from him, almost taking his fingers as it went.  He got up and started running.  He made it through the first door before the explosion hit and pressed the button.  

The pressure wave generated by the explosion was so intense, it almost ripped the carriage from the chassis.  Luckily, the structural rigidity of this 40 year old train cabin held, and it tipped and fell.  The pressure of the explosion threw the carriage against the wall of the tunnel, catching one of the many support columns that protruded from the side.  

The column ripped through the top of the carriage like butter.  The carriage, now on it's side screeching along the rails and ground was being opened like a tin of sardines.  The seats and furnishings were shaken from their fixings and rattled around, some falling out along the way.

Eventually, the tin could be opened no further and it jackknifed across the rails.  The noise from the metal on metal was unbearable.  Almost all of the windows had now shattered in the first cabin.  The force of the other carriages ploughing into the side of the jackknifed bullet pushed it over, once, twice and it started to roll along the tracks before friction kicked in, and the rigidity of the cabin gave out.  

The carriage crumbled and created a kind of ramp for the rest of the train to launch from. As the connections between the carriages gave way and they made their way dangerously along the tracks, they seemed to dance to the speed.  It had been a long journey for this newly promoted carriage but it was coming to an end.  In a crescendo of sounds the carriage left the rails and ramped over the debris towards the end of the tunnel. 

The end of this particular tunnel was different to most.  Most tunnels end in an opening of some kind.  This one ended in a brick wall.  A solid brick wall.  Though the train had slowed it was still able to punch through the air with ease.  Had his watch been there, it would have been ticking 10:42:58, 10:42:59, 10:43:00.

The train hit the wall.



