\chapter{48}
\section{}
Mission  

She wandered through the streets aimlessly and in pain.  They looked familiar, but everything was sufficiently different that it felt like she was in a completely different place.  In truth she was, separate two locations by enough time and they can become vastly different, she thought.  The city looked drab and boring.  Much of the colour present in her time had faded away with her trip.  

Kiele hadn't realised just how painful the jump was.  It had felt as if her entire body was about to be ripped apart.  The convulsions had been the worst.  Her cut was bleeding again and as she stumbled through the streets of Alendria she felt more lost than she had ever felt before.  Even the people seemed different, more reserved, shifty.  One man eyed her from across the street as she made her way across the pavement.  His head turned slowly as he followed her with his eyes, never blinking once.  It spooked the poor girl.

A small café stood a few metres in front of her and as she walked past, the smell of a food hit her nose and she found herself unable to move.  She was hungry.  The trip had really taken it out of her and she pushed open the door hoping to gain some rejuvenation from the produce inside.

The café was smaller than Haito's, with only a few tables and chairs inside.  Each one was crammed with people, drinking and eating, talking and laughing.  She nervously walked up to the counter.  The guy standing behind it looked nice enough, but she still didn't trust anything in this time-frame  It was all still very alien to her.  A few of the customers watched the young girl as she stood awkwardly at the counter.  

``Yes love,'' came the greeting from the attendee, ``What can I get you?''

``Could I have a coffee,'' she said and pointing at a particularly tasty looking bun added, ``And could I have one of those too please.''  She suddenly realised her mistake.  She had no money.  She reached inside her pocket and pulled out the grubby wallet.  Inside was a DebitMate card, and a few old coins.  The guy behind the counter was already off fixing her drink.  If he asked her to pay she wouldn't be able to.  What was she going to do?

Instinct kicked in and Kiele turned and bolted for the door.  Several of the customers looked up, surprised to see someone running so fast inside the café.  She flung the door open, having to pull it inwards.  It struck a table behind it and the occupants cups were thrown around, spilling their contents everywhere.

``I'm so sorry,'' Kiele said, amidst the sounds and cries of the angry punters.  She continued through the door and ended up back on the street.  She ran for a short while before sitting down to rest against a pillar in the street.  It had once been part of a sculpture, but years of war and change had whittled it down to a simple symbol of a time gone by.  

She was breathing heavily again and her heart was in pain.  What exactly was she going to achieve by coming here?  It had been an impulse decision, based on a hate of Jessie and an apparent love for the parents she had never met.  She was on a mission to prevent their deaths.  It would mean in all seriousness that she probably wouldn't ever exist.  She knew Oken and Jay had been dating, but who knows if they would end up together, who knows if they would want to have a child of their own.

Still, there was nothing worse to Kiele, than sitting idly by, while someone else got away with an atrocity like Jessie had.  He was an evil little man.  She had always felt a little different to him.  She had always felt as if she didn't quite belong in his family of hatred.  Now it was quite clear why.  She was cut from an entirely different cloth.  It was as if she were a patch of new fabric on an otherwise filthy item of clothing.

Her parents were here.  Now.  Her parents were alive.  She was going to find them and meet them.  She deserved that much.  The universe owed her for her sufferings.  It wasn't that she was angry, but her life had been such a trial that just meeting her parents felt like the the most natural of compensations.  

The pillar was cold on her back, she felt it even through the thick purple blazer.  She had no idea where to start.  The Zone was an obvious place, and she knew how to get there, but she had no idea of what time the next event was due to start.  She was pretty sure she had arrived on the right day, but it seemed to her to be around midday.  The fighting wouldn't start till the evening that was for sure.

Kiele hadn't been concerned that someone would spot her jumping in to this time frame.  She hadn't even thought about it once.  Luck had been on her side though and the position of her exit point had meant that she had ended up in the middle of the same wooded section she had met Zane in earlier that day.  

She had been walking for what seemed like forever, streets losing all recognisable features in the drab time-frame  She was tired, and what she would have liked more than anything else was a nice warm bed and a sleep.  Her search for her parents could wait.  She knew she wasn't going back.  

She had left everyone and everything behind.  In a split second she had made a decision.  Now, part of her wished she could take it back.  The device was still warm in her pocket, itching for her to go home, but she couldn't.  She hadn't realised she had required a second power cell until now.

Zane loved her so much.  She knew that, but without a power cell, he couldn't come back.  She hadn't realised that she had left one behind.  Her mind started to spin.  She would never see his face again.  It was all Jessie's fault.  She focussed on the task in hand, her parents.  She had to find them.  Together or not, she had to meet them.

Kiele tried to get up, but found herself completely zapped of energy.  She stayed seated firmly against the pillar.  In all honesty she didn't look too out of place.  There were several other school students milling around the area and some homeless people kipping in the doorways to some shops.  

One poor man had chosen to sleep in the wrong place as one of the building security guards came outside and whacked him with a large metallic sounding object.  Kiele winced as the pole hit the man, sending cries of pain echoing across the city street.  Eventually the guard relented, and with one more gesture of attack, he left the man who was now lying at the bottom of the small flight of stairs leading up to the building, blood pouring from his mouth.  He was dead.

The young girl sitting only metres away from the event was disgusted.  She averted her eyes as some passers by took pleasure in kicking the man in the stomach.  'Useless bum' she heard one lady shout.  Finally she found the strength to stand once more.  She inched her way across the pedestrianised area until she found a quiet side street.

The street was a dead end and obviously meant for loading and unloading of goods at some of the smaller shops.  Paint was peeling off the side doors of the shops and it looked as if it had been twenty years since the alley had seen any real action.  It was blocked off at one end by a newer looking building.  Presumably the requirement for loading had long since past.

Kiele curled up in one of the many small alcoves.  She was exhausted and was in desperate need of some sleep.  She removed her blazer and placed it over her cold fragile body.  Her search for her parents could wait for a while.  She needed to rest.  She closed her eyes and suddenly was aware of a figure standing over her.

When she looked up and opened her eyes she saw a sweet smiling familiar face.  The woman looked down at the little girl and extended a hand.  

``Come now dear,'' she said, ``You'll catch a cold out here.''  It was Kaitlin.  She old lady didn't look so old any more.  Her hair was longer and tied back in a ponytail.  Kiele took hold of her hand and Kaitlin pulled her to her feet.

``You're not from around here are you?'' said Kaitlin.

Kiele smiled.  ``You could say that.''

The two of them exited the alley way.  Kaitlin had her arm round the young girl and though she wasn't wholly listening, Kiele could hear her chattering away about tea, cakes and a nice warm shower.  She breathed a sigh of relief.  She had been thrown a life line.  Someone was looking out for her.



\thoughtbreak



The ambulance had arrived and Ruben had let them in through the front door.  Jessie was still unconscious on the floor, but it was Jolie who they paid most attention to.  She was still bleeding, still weak.

``What's your name?'' asked one of the paramedics.

``Jolie,'' she croaked.  She noticed their green uniforms, so pristine.  One of them was standing over her left shoulder, whilst the other was crouched down, injecting her with some nondescript liquid.  She hoped it would do something for the pain.  Her neck was so sore and she could feel herself getting weaker by the minute.  

``How long has she been like this?'' the other paramedic asked Ruben.  He stuttered.  He couldn't remember.  It had felt like the battle against Jessie had lasted a lifetime.  It was Jolie who finally came to his rescue.

``About twenty minutes,'' she said.

The paramedic attending to her laughed.  ``Miss, you want to get your boyfriend in order, seems he's a little slow.''  She chuckled and looked up at Ruben, who after initially scowling at her, managed to see the funny side and laughed heartily.  

``BP's eighty over fifty five,'' he said to his companion, who had walked over to see whether Jessie was waking up yet.  The paramedic packed up a few things into his carry case and looked Jolie in her large beautiful eyes.  ``We need to get you to the hospital,'' he said.

Jolie liked the paramedic.  He had one of those faces that seemed to instantly calm a person.  He wasn't at all pretentious or condescending, just caring and kind.  He stood to his feet and gestured for his friend to come over.

``We're going to find it difficult to get the gurney in here,'' he said in a rich accent, ``Do you think you can walk to the ambulance if we help you along?''  She nodded.  The two of them hoisted her up one on each arm.  It felt like floating.  Her body weight was being entirely supported by the two strong men on either side of her.  She could get used to this.

The injured party turned back to look at Ruben.  She needed to thank him for his help.  As she looked at him he appeared to be looking back at her, except his face was that of sheer horror.  He was almost looking through her.  She also noticed that the men had stopped walking.  She was left hanging.

When she turned her head back to the centre, her optic nerve saw something her brain wasn't expecting.  It saw a man standing in front of her.  On his own he would have appeared quite charming, some may ever have described him as handsome.  It was Ric, and though Jolie didn't know what he looked like, the combination of Ruben's expression and the fact that the newcomer was carrying an assault rifle, made her speculate he must be the enemy.

Ric smiled grimly.  So Jessie had failed, but at least he could have some fun with what was left.  He pointed the rifle at one of the paramedics and pulled the trigger.  The gun exploded into life and peppered the man with bullets.  His body convulsed with the momentum of the fifteen bullets driving through.  Several of them managed to navigate through his torso and emerge from the other side, embedding themselves in walls and doorways.  Ruben had seen what was coming and had wisely sidestepped into one of the side rooms, Zane's bedroom.

With only one support column, Jolie's body hung awkwardly to one side, the other paramedic attempted to turn her and run, but her body just wouldn't cooperate and he ended up dropping her and running the length of the hallway on his own.  Another burst from Ric's gun showered the poor man and the entrance to the basement with more little killers.  He was hit several times and stumbled before falling headlong down the basement stairs, landing dead at the bottom in a tight mess, his legs almost touching his ears.

The gun's barrel was smoking a little now.  It had enjoyed being put to good use at the hands of its master.  Now it sat there, cradled in Ric's arms, silently resting, ready and waiting to do his bidding once more.  

``Come on out Ruben,'' said the man, ``I ain't gonna kill you.''  He began to walk forwards and added, ``yet.''  His boots crunched down on the soft carpet, now sprayed with blood from various sources.  Jessie was beginning to wake.  The noise of the shooting had awoken him from his unconscious slumber.  He now looked up at Ric who was walking slowly towards him.

``Ric, I can explain, there was.....''  Jessie was interrupted.

``No need,'' said Ric, pointing the rifle straight at Jessie's head and pulling the trigger, for far longer than was required.  The bullets poured into his skull like animals escaping a predator.  His head, or what was left of it, had vibrated heavily with the awesome forces that had been imparted upon it.  There was no doubt about it, Jessie was dead.  His eyes, still open in fear, told a story of pain and suffering.  

Ric was instantly aware of movement behind him.  Ruben had crept out of Zane's room, whose doorway was now behind Ric, and was attempting to help Jolie to safety.  The predator spun round to see Ruben cradling the almost lifeless figure as he attempted to pick up her body alone.

``Don't even think about it Ruben,'' said Ric.  ``You put her down or you both die, now.''



\thoughtbreak



Zane had arrived in Kiele's time-frame slightly later than she had.  The error had been mostly attributed to a mistype.  His plan was simple, though it was beginning to feel much more like a mission.  There wasn't a lot of time.  He knew where Oken had lived, he had gotten the data from his teacher for his report.  He had even wanted to visit the location to add more authenticity to his assignment, but after the accident it just hadn't been possible.  His life had been filled with continuing Oken's work, filled with moving forward and not dwelling on the past.  

When he had approached the device, he had been impressed with Kiele's choice of destination.  Secluded, well covered, clearly she had thought it through.  He had no idea it had been a decision of luck.  He had copied the information and had experienced the same walk she traversed to reach the Zone's backyard.

Now, as he walked through the streets he noticed the same drab and dull city that Kiele had seen.  People living in poverty.  Angry unhappy people.  He saw the remnants of the murdered bum in the form of blood stains and general avoidance by the public.  Something had happened there recently.  'Was this place really so brutal?' he thought.  Was it really so volatile?  

His stomach growled at him, he required food, but he too had no money with which to buy it.  No, his best course of action now, was to find Oken and tell him everything.  Kiele would be hit by the car in a few hours.  He knew the exact time and location, it had all been in the report.  He adjusted his watch to match a clock he could see hanging high on one of the city's buildings.  He would find another clock later to corroborate the correct time.

The boy's mission was simple, prevent Kiele from dying, convince Oken not to use his weapon and live there in the past, forever more.  He seemed incapable of realising that preventing Oken from using his weapon would, in all likely hood prevent him from possessing it in the future.  It was such a simple paradox, but the boy, tired from his earlier exploits hadn't yet realised the foolishness of his mission.

Most of the shops were beginning to close up now, this was a poorer district than most it seemed.  Zane had walked through many streets in his journey and this was by far the most dilapidated.  He walked up to the apartment building that housed his hero, and stepped inside.  The security guard watched him carefully as he pressed the button to Oken's apartment.  It buzzed and on the small screen in front of him, a familiar face appeared.  

``Whatd'ya want kid?'' came the voice and when Zane didn't answer in a predefined time Oken said, ``I don't feel like any cookies today thank you.''  The monitor went blank and Zane was once again staring at a dead screen.  He pressed the button again.  Surprisingly Oken picked up.  The security guard was interested now, just what did the boy want?

``I told you to get lost,'' said Oken rudely.  It wasn't Zane's fault, he was just having a bad day, he was trying to cram everything into what he now realised was a slightly too small black holdall.  

``I have a message from an old friend,'' he tried something, ``From Postremo.''  Oken was learned and even though his grammar was probably incorrect, Zane knew the older man would know 'Postremo' meant future in Latin.  There was an awkward silence as Oken quickly decided whether or not he wanted to know what the boy was going to say. 

``Come on up,'' he said finally.  Zane ran up the flights of stairs.  This was big.  He was going to meet Oken Brown, the man who single handedly built a time machine and changed history.  It was incredible.  His heart was beating ten to the dozen.  He had seemed like a nice guy.  One foot flew in front of the next as he continued his assault on the stairs.  Would he listen to his plan?  Would Oken possibly grace the boy by accepting his mission?  He had no idea.  This was something that he was hopefully about to find out.

When he reached the door he was a little disappointed at just how plain it seemed.  He had expected something magical, something which stood out, yet in front of him stood a bog standard door, with bog standard lettering.  He rapped on it carefully and listened for the latch to click.  It did, and the door swung open.  Oken was standing there holding the door with one hand, his arm partially outstretched, whilst motioning for the boy to enter with the other.  

Zane entered the plush apartment.  It hadn't been what he expected at all.  As he stepped further and further away from the door, he felt drawn to the centre of the room.  Oken watched the boy in mild amusement.  The kid was in awe, it was obviously not what he was expecting at all.  His mouth hung open, agape at the sophistication present in the room.  

Zane stood there in the middle of the room, rotating once, twice, three times before Oken had enough.

``Are you gonna sit down kid?'' he said wryly.  

Zane's train of thought was shattered and he turned to face the vocaliser.  He looked around him for the nearest chair and sat down on it with an odd look on his face.  He leaned back into the chair.  He could get used to this.  In his mind's eye he imagined living here with Oken, Kiele and Jay.  A proper family.  In his daydream Oken looked at him, 'What do you want?' he said dryly.  

``Hey kid,'' Oken shouted.  Zane looked up, he hadn't realised the 'What do you want?' had been a real question directed at him.  It had merged with his fantasy.  

``What did you say?'' asked the boy.

``I said, What do you want?''

``Oh,'' the boy looked down at his shoes and the reality of the situation came flooding back.  Usually he had his feet firmly on the ground.  Usually, he knew exactly what he wanted to say.  Today was different, after the train, Jessie, everything, his thoughts were entirely jumbled.  He felt so selfish for asking Oken his request, but he had no other choice.  He was stuck there.  Finally he plucked up the courage to talk.

``I'm from the future,'' he said initially.  It seemed so stupid.  Would Oken really believe him?  It felt like he was in a science fiction series, no one said that in real life.  Still, despite of the stupidity, Oken nodded.  Zane continued, ``Where I come from,'' he fought to find the right words, mulling several over in his mouth, ``you're dead.''  Oken raised an eyebrow, he didn't seem all that bothered.

His statement was entirely generic, but Zane hadn't realised.  He hadn't told Oken how far in the future he had come from, it could have been a year, two, fifty or four thousand.  

Zane continued, but his brain had lost all real cohesion, ``And...and...some guy made a girl from you and that girl you were seeings.......you know....stuff.''  He motioned his hands coming together, making a globe like shape.  Oken looked confused.  Zane picked up on it.  ``I'm sorry,'' he said.  ``I'm no good at this kinda stuff.''

Zane's heart was beating faster, and a knot had just formed in his throat.  Oken smiled at the boy.  

``Would you like a drink?'' the man ventured.  The question had come completely out of the blue and threw Zane for a second.  Oken walked to the kitchen.  The apartment was large, spacious and almost completely open plan.  The boy remained seated, unaware of what to say next.  He decided to hold his tongue until Oken returned.

Oken walked back over to where Zane was still sitting.  He placed a glass of water down on the coffee table.  Zane looked unimpressed.  When Oken had offered him a drink, he had expected coffee, tea or even something a little stiffer, but water?

``Drink,'' said the man.

``What?'' replied Zane.

``The water,'' Oken replied, ``drink it.  It'll help you concentrate.''

Zane leaned forward and took hold of the glass.  He hadn't even drunk it yet, but the side of the glass felt cold and refreshing.  He lifted the glass to his lips and drank the cool water.  Oken had been right, it really had cleared his head.  He felt much more ready to talk.

``Now, where did you specifically come from?''  His question to Zane was direct and to the point.  Now the boy was ready to answer.  

``I jumped back from 2057, after creating a time machine based on the temporal weapon that you are about to use for the first time tonight.''  Oken sat down and leaned back, putting his hands behind his head.  It was feasible, and the fact that the boy knew he had a temporal weapon made it all the more believable.  He nodded to the boy who seemed to have stopped to let digest Oken his sentence.  

``I travelled back here because, well, in the future,'' he looked down at the floor, ``things went kinda bad.''  Oken suddenly started taking notice as Zane continued.  ``Jessie, I take it you know him?''  The man nodded, taking his hands down from behind his head.  ``He leads the G-TEP to you after your fight this evening.''

``Figures,'' said Oken unabashed.  



\thoughtbreak



Zane had continued telling Oken the story of the last few months of his life, with the man listening intently to every word.  The inventor was now sat, head in his hands.

``A daughter you say?'' he asked again.

Zane nodded.

Oken half laughed, ``Wow, what do you say to something like that?''  Zane smiled at him.  He had imagined it would impossible to derail someone like Oken, but he had been wrong.  The man had clearly been thrown by his story.

``So what do you want from me?'' Oken finally asked.

``I want to stay here,'' he said, ``with Kiele.''

``I'm not going to stop you,'' said Oken.  He got up and walked towards the kitchen.  Now it was he who needed a drink, and not water either.  He poured a glass of vodka from a bottle on the shelf and sipped it slowly.  

Zane almost shouted out to Oken, ``I don't want you to use the device,'' he said.  ``I want you to destroy it.  It's caused so much pain and suffering.  Just get rid of it.''

Oken slammed his glass down on the counter, almost smashing it.  He was instantly angry with the boy.  For some reason Zane seemed to think the inventor could solve all his problems.  Why the hell was it up to him?  

He had also noticed a flaw in Zane's plan.  Destroying the device would remove Zane from this time-frame, Kiele too, there would be no device for them to use.  Had Zane even considered that?  Had he even though about Kiele?  His daughter.  A daughter.  A daughter?  To say he had been shocked was an understatement, he had been thrown across the room.  Oken mused on whether he would be able to protect them with a temporal shield of his own, but the boy's arrogance had put him off.

Oken wasn't about to be dictated to.  He would decide what to do with Bethany.  She was his creation after all.  No little know-it-all from the future had the right to tell him what to do.  He wouldn't change the future, he would be careful for sure, but he planned to change nothing.

``I think it's time you went,'' said Oken sharply.  ``I've heard enough.''

Zane could hardly believe it.  Was Oken really going to shut him out like that?  The one person left in the world who could help him wouldn't.  What kind of man was that?  Zane was angry.  He stood up.  

``How can you stand there, knowing your daughter goes through all that pain, because of you, because of your actions?  How can you be so brazen?''  The boy started shouting now.  ``I wanted so desperately to meet you,'' he screamed, ``I thought you of all people knew what was important.''  Zane walked over to the door and opened it.  ``Turned out I was wrong.''  He slammed the door.



\thoughtbreak



The bodies of Ruben and Jolie lay broken and bleeding on the floor.  Ric hadn't spared them.  Ruben hadn't put Jolie down and Ric had made good on his promise.  Now they both lay there, seemingly cradling each other in a twisted mess.  Ric stepped over the two corpses who were still bleeding all over the floor.  It hadn't been as much fun as he had hoped.  He walked out of the front door and stood facing the road.  His anger hadn't even begun to grow yet.  Years of planning gone, wasted.  This had been his only chance to do what he had felt necessary.  The rain beat down on him hard.

Ric's phone rang and he looked down at his pocket.  He lifted the phone, still ringing, from his pocket and placed it carefully on the floor.  He stamped down hard with his boot and the ringing stopped.  There was nothing left for him to do.  He took the rifle, pointed it at his head and pulled the trigger.



