\chapter{14}
\section{Beautiful Bride}


His beautiful bride sat before him in the meadow.  He still found it difficult to believe that she had betrothed herself to him, especially forever.  She smiled at him, the wind blowing softly through her hair, gently lifting her slightly clumped ringlets.  They had spent the afternoon swimming in the lake and had finally decided to retire to the grass to dry off.  The sun, still very visible in the sky warmed their skin and quickly dried the remaining water from their bodies.  

He had laid out a picnic for her under a huge oak tree.  It was as if there wasn't another soul in the world at that moment.  He picked up a sandwich and bit into it, the cucumber cooling his mouth as well as quenching his thirst.  He had always been fond of cucumbers, the way they tasted, their ability to satisfy both hunger and thirst coincidently.

``Can you think of a more perfect day?'' he asked her.  She shook her head, unable to speak as she herself had just bitten into her own sandwich.  The two of them continued to chew in silence, listening only to the sound of the water running quietly in a nearby stream, and the gentle breeze touching the trees with its presence.  She lent forward and put her hands down in front of her, gently placing her sandwich on a plate as she did so.  Then she turned  round and lay back into his lap.

He sat there with a sandwich in one hand and began to play with her hair with the other.  The strands of her hair seemed to glow luminously in the sweet light of the setting sun.  He had imagined he would begin to feel cold by now but no, everything was perfect.  It was unimaginable.

``I love you,'' she said.  ``I love you with all of my heart.''  Her eyes looked up into the sky above her, so bright and round, full of wonder at the lives that lay ahead of them.  She lifted up her hand and looked at the ring on her finger.  She twisted her hand so that the diamond in the centre caught the sun and winked at her.  She giggled.  He hugged her gently.  ``I never thought you'd have enough to buy it for me,'' she said.  He gave a brief smile.

``I'd find the world for you,'' he returned.  He meant it too and he was still in shock and awe that the most beautiful woman in the world, not just in his world, but the entire world, was lying there in front of him.  

``Aren't you hungry?'' he asked.  

She carried on with her train of thought, almost ignoring his query.  ``Not that I expected such a precious gem,'' she ensured him.  ``I'd be happy with you just the way you are.''

``Just the way I am eh?'' he replied.  ``You sure you're not going to leave me for a better man?''  As soon as the words left his mouth he regretted saying them.  There was something about them that rang in his head.  The word 'better' repeated itself over and over again.  He looked down at his hand which had found it's way into hers.  The contrast of his dark skin against her milky white silk was magnified by their difference in sizes.  His muscular clench could have completely crushed her delicate bones.  Of course he'd never have wanted to do such a thing.  

As he sat there a little longer something began to feel wrong.  His hand began to tighten around hers.  First gently and then tighter and tighter, like a boa constrictor.  He tried to let go, but found himself unable to.  She began to gasp, and with her other hand started clawing at him, first his hands, ripping into them like a rake to a lawn and then up to his face.  She dug her nails into his chin and pulled away hard, leaving Ruben with a huge gash.  

As she struggled she yelled out, ``You fat oaf.  You're hurting me.''  In an unforgettable instant she was suddenly in front of him, free from the ogre's grasp.  ``So where did the money come from then Ruben?  You stupid spac!  Why would you do that?  I didn't need the sodding ring, I loved you for who you were.''  Ruben withdrew.  Still sitting, he used his hands like oars to propel himself backwards.  

The love of his life now on all fours continued after him before standing up and walking towards him.  The sun, now an angry red was behind her and lit up her hair, making it look as if it was on fire.  Ruben began to stammer, ``Yazmine, darling,'' she kicked him in the leg as Ruben ran out of ground and hit a tree.  He seemed surprised.  This wasn't how it was supposed to be.  ``I love you Yazmine.  I love you,'' he blurted out like a fool.

``You love me??'' she shouted at him, ``YOU LOVE ME?''  She picked up his foot and began to drag him.  Ruben thrust his hands down into the ground.  He wasn't even sure where she was taking him.  ``If you loved me so damn much why did your precious little friend have to bail you out?''  She was of course talking about Oken.  Oken.  His best friend.  Suddenly it all came screaming back to him.  Of course this wasn't real but his head made it feel real, oh so real.  

``Yazmine stop.  Oken's dead.  We can be together.''  In an instant he felt a ripping in his heart.  Yazmine had never been able to accept that Oken had bailed Ruben out when he hadn't been able to pay off the debt of the ring, just like his little betting accident.  She held it over him like a treat to a puppy, making him jump whenever she wanted, torturing his very existence.  His heart hurt so badly right now.  Tearing for the love he felt for both Oken, his life long brother, now deceased, and his bride no longer, whom he had loved so dearly.

``How dare you,'' she said.  ``You would be so quick to betray the memories of your friend?''  The word friend echoed around his head once again and the ripping in his heart grew stronger.  Suddenly Ruben knew where she was dragging him.  His fingers tried in vain to grip the surface of the earth, but unsurprisingly he couldn't prevent his journey to the lake.  At least that's where Ruben thought he was going;  the lake.  She was going to drown him in the lake.  Except the lake had been replaced with a ranging sea of fire.  

``Welcome sweetheart,'' she said.  ``Welcome to your own personal hell.  On behalf of everybody here,'' she continued, ``I hope you rot here and burn in what you created for yourself.''  Ruben began to sob.  The tears streaming down his face as his heart ripped further with every inch closer to the furnace of his mistakes.  

All of a sudden the heart inside Ruben gave up and at that instant Yazmine threw him into the fire.  As the flames licked up around him, he screamed out.  Not in pain, but in regret.  Had he really caused it all?  Was it all his fault?  The flames burnt his body away and cleansed him.  He began to feel a relief, the kind of relief one feels when everything seems like it will be OK.  

As the flames grew closer to his heart the feeling vanished and was once again replaced by the guilt of his mistakes.  His body was no longer present.  Ruben was a lifeless soul floating where his body once existed, hanging on to his heart for dear life.  One single lick of the fire flicked his already fragile heart.  It was all to much.  His heart exploded, splitting into a million shards.



\thoughtbreak



Ruben coughed and woke with a start.  It shocked Leon, who hadn't believed he would wake up so soon.  He'd received quite a blow to the head.  Leon was also now fully aware of the strength of the veteran that was Ric.  Ruben groaned and spluttered as he became fully conscious.  Leon banged on the side of the ambulance between himself and the driver.  He was surprised to see another man sitting in the cabin.  It was this second occupant who responded to Leon's call and stepped back through to the rear of the vehicle.  

The man, in his early fifties, leaned over Ruben.  Leon just sat there, head in his hands.  

``You're going to be OK,'' said the second man.  ``My name is John.  I work for the hospital.  We're going to take good care of you.''  Leon admired the fact that John seemed to harbour no ill feelings towards Ruben.  He wouldn't have blamed him even if he did but he admired him all the same.  

John began to check various instruments from the medipanel looming over the bed.  Most of the treatments were administered from there nowadays, however there was still some preliminary work that the paramedics preferred to do themselves.  Preparing an IV was such a task.  John was about six foot tall and wore the same blue uniform as his partner.  They had been working together for about thirteen years and during that period had become very close friends.  

``How's he doing back there?'' asked the driver.  He turned his head to ask the question, but the roads had become increasingly busy and he couldn't afford to look back any longer.

``Mac, he's gonna be just fine.'' He afforded himself a little joke, ``If you can keep us on the road that is.''  Mac laughed.  Being slightly younger than John he had complete faith in his partner.  They'd been through some pretty rough patches together.  

'Just who was this guy?' John thought.  He certainly didn't seemed like a G-TEP soldier.  Mac had told him that they had been ordered to keep him under close guard at all times.  Said he'd been told this dude was a real troublemaker.

Ruben still lay there, but now looked over at Leon.  The mask on his face supplying oxygen was digging in to his chin.  Leon was actually surprised that the mask had been used, especially considering Ruben's injury.  It was then he noticed the cut out that John must have made.  They had done their best to make Ruben as comfortable as possible.  

Ruben's eyes locked onto Leon.  He spoke softly at first, then becoming audible, ``You.''  Leon looked up.  ``You were there weren't you?'' he asked of the G-TEP agent.

Leon desperately wanted to say no.  Unfortunately it wasn't in his nature to lie.  It's what had gotten the lieutenant so angry only a few moments ago.  He lifted his head an made eye contact with Ruben.  John had finished attending to the medipanel and began to return to his seat in the front.  Before he did so, he placed his hand on Ruben's shoulder.  

``I'm here if you need anything.'' whispered John to Ruben.  ``Just holler.''  Ruben gave a weak nod before redoubling his efforts on Leon.

``You were there, I saw you,'' came Ruben's next accusation.  His hand almost pointing, but in actuality just extending a finger, not even in Leon's direction.  The urge to confess was overwhelming and Leon could stand it no longer.

``Yes,'' he said.  ``I was there.''  Ruben nodded in acknowledgement.  He felt better now that he knew where he stood with this stranger.  He could sense that there was something this solemn figure wasn't telling him, but for now Ruben's energy levels wouldn't permit him to press the soldier further.

Leon looked at the doors to the outside.  Oh how he so badly wanted to be out of here now.  It had seemed like a good idea at the time, when Ruben had been unconscious.  He once again put his head into his hands and could feel the tears welling up behind his eyes.  He had seen how upset Ruben had been at the death of his friends.  His conscience kicked him in the gullet.  Admitting to being there wasn't confessing.  It was time to dig deep and grow a spine.

Leon began, ``I....''  

Ruben interrupted him before he could say anything further, ``What's your name soldier?'' he asked.  Ruben felt compelled to talk to this man.  Something inside him told him that he had something important to say.  

``Leon,'' replied the man.  ``My name is Leon and,'' there was no stalling any further, ``and I shot your friends.''  Ruben grimaced.  He hadn't expected the something important to be so cutting.  His mind was telling him to get up and punch this no good son of a gun in the face, but his body was telling him otherwise.  His body was telling him that he barely had the strength to talk.

``Why?'' asked Ruben.  Unable to continue looking at the G-TEP scum before him, he turned his head.  He had really hoped it had all been a dream.  He had prayed so hard that it would all go away, but nothing had worked.  Had God deserted him?  As Leon tried to find the courage to speak again, the ambulance slowed down to a crawl.  The traffic lights had changed to a deep red and Mac obeyed without question.  The ambulance tipped slightly as the brakes were released and the handbrake applied.  Many of the constructs had fancy new ambulances with FeelDrive fitted.  This one, however, was an old model.

Leon watched as some kids played merrily in the street, blissfully unaware of the cruel reality of the world around them.  He remembered what it had been like as a child, spinning and jumping without a care in the world.  No one to worry about, no responsibilities.  Then the world had taken hold.  It happened to everyone in one way or another.  

``It was an accident,'' said Leon.  The words had just left his mouth without him even realising.  He cursed his subconscious and felt the bitter urge to complement the statement with an explanation.  ``I mean, I was part of the task force, but I accidentally fired my weapon.''

He could hold on no longer.  Leon fell to his knees and wept.  ``I'm sorry'' he shouted out, ``I'm so sorry''  He sniffed long and hard, but the tears just kept coming.  ``I never meant to kill anyone.''  He couldn't even see any more, his eyes awash with salt water.  ``It was a mistake, I should never have joined.  I never really wanted to.''  His breathing became uncontrollable and as the ambulance turned a particularly sharp corner, he was thrown against the side of the vehicle.  John looked back into the rear, but Leon motioned for him to ignore the incident.

Ruben lay there, tears coming to his eyes.  He gathered enough strength to drop his arm to his side.  ``Take my hand'' he told the broken little man.  Leon looked at him confused.  Ruben nodded at him slowly.  The soldier reached out and took hold of the hulks hand.  His skin was so rough and rather sweaty, but Leon didn't mind.  ``Close your eyes,'' came the next whispered command.  Leon obliged.

Ruben closed his eyes too and tightened the grip on Leon's hand.  ``Oh dear Lord in heaven,'' he began, ``before you is a broken man.  He is very sorry for what he done.''  Leon's sobbing took full hold of him now and he started wailing in pain.  His heart was aching.  ``Lord you can forgive him of this and all of his sins if he so wishes you to.''  Leon's crying paused briefly as Ruben motioned for him to speak, but nothing came out.  ``Ya gotta ask him, if you want to be forgiven'' said Ruben, and he gave Leon a smile.

``Lord, forgive me'' sobbed Leon, ``forgive me....oh please Lord forgive me.''  He kept repeating the phrases over and over as Ruben pulled him close.  The two of them locked together rocked as Leon sobbed inconsolably.  The rocking hurt Ruben's head, but he didn't mind.  This man had been placed in his ambulance for a reason, a reason only he could answer the call of.  As the ambulance made its way through the streets, the two men sat there and talked until they could speak no more, brought together by the death of a titan, the death of Oken Brown.

