\chapter{40}
\section{Electrifying}


He had no idea where he was going at all.  She hadn't told him anything.  His birthday was in a couple of days and it was supposed to be a surprise, but yet she still hadn't told him exactly what he should expect.  Mark had still been at work when they had left.  Kiele had called a taxi and now the two of them sat in the back, both brimming with anticipation.  

Zane looked at the partition in front of him.  It was opaque, the driver mysteriously obscured from his view.  It felt strange, like they were riding in a train almost.  A part of him wished to see the driver, just to check on him, just to make sure he was still there, another was enjoying the privacy.  It was as if he and Kiele were sealed in a cocoon, into which nothing could break through.  

``Come on,'' he said, as the taxi wound its way through the streets of one of Alendria's most affluent neighbourhoods.  ``You gotta tell me where we're going.''

She shook her head.  ``No way,'' she replied.  ``You'll find out soon enough.  Besides, it won't be a surprise if I tell you now will it.''  He growled at her playfully.  She could be exceedingly stubborn he had discovered.  

Kiele had been saving up her money for a long time, primarily it was being put aside so she could finally break from her father's grasp when she reached eighteen.  She had worked a summer job a year or two ago and managed to save up a reasonable amount.  She also saved whatever she could from the money Mark gave her to buy her clothes and necessities.

When she had learned of Zane's impending birthday she had racked her brains to find the perfect gift.  Money was no object.  It would be her chance to show him how much she loved him.  She had heard the album she had bought him blaring out of the basement sometimes, more often than not when Mark wasn't there.  She had discovered C-bex Lunacy were playing a gig not too far from the commercial district and she had decided there and then to take Zane.  

The tickets had arrived in the nick of time earlier that morning, and they were now tucked inside a fancy envelope, inside her jacket pocket.  She still found it humorous that plastic card tickets were still used, when technologies in most of the other entertainment industries had advanced so much.  

Zane was racking his brains right now, trying to figure out what it was she was up to.  He tried again.

``Come on Kiele,'' he said in a whinging tone, ``I'm dying over here.''

She decided enough was enough.  He'd been like it for the last twenty minutes and they were bound to be nearing the venue sooner or later.  She reached into her jacket and pulled out the tickets, still encased in their envelope.  Kiele handed it to Zane who excitedly received it and stared at it for a good two minutes.

The envelope was gold in colour with a hypnotic pattern embellishing it.  Now it was in his hand he didn't want to open it.  He had enjoyed the excitement, the thrill of the unknown.  He half wanted to pass it back to Kiele till they arrived, but knew that would upset her.  He slipped his finger into one corner of the envelope and gently tore into the gold card.  Microscopic paper fibres were expelled and danced in the light, adding to the copious level of dust already present in the taxi.

As he opened the envelope he couldn't quite see what was inside, there were two of them, whatever they were.  Kiele was grinning now, knowing that in the next few moments he would find out just how much she loved him.  He pulled out the tickets and started at them.  He could hardly believe his eyes.  C-bex Lunacy tickets.  C-BEX LUNACY TICKETS!

Zane's mind was screaming at him.  He probably had some of the most expensive gig tickets in his hand right now.  C-bex Lunacy were big, really big.  A cross between traditional punk and heavy metal, they created a fusion of genres.  It was nothing new of course, but after thirty years, all the trends seemed to be coming around again.

He was speechless, still sat there looking at the two tickets in his hand.  Kiele could see his fingers gripping them so tightly.  He wasn't going to let them go without a fight.  She even wondered if the ticket inspector on the door would be able to prise them off him long enough to check that they were valid.  She could tell he was in shock.

``So?'' she ventured, ``you like your present?''

He was still sat there speechless.  No one, not even his loving parents had ever bought him such a meaningful and expensive gift as this.  It must have cost her an absolute fortune.

``Kiele,'' he whispered, ``you didn't have to do this.''  She smiled at him.  ``I mean, it's amazing, but you really didn't have to.  I love you for who you are.''

He turned to face her for the first time and the realisation of what he had just said sunk in.  He had told her he loved her.  It wasn't that it was a lie, it wasn't that he blurted it out without thinking, it was just that he had wanted to say it when they were in a more romantic situation, not stuck in the back of a taxi.

Now it was Kiele's turn to be speechless.  He had said the three words she had been dying for him to say and he had said them without any prompting or provocation either, bar the giving of the tickets.  He looked at her beautiful grey eyes, twinkling in the sudden oscillations of the street lamps.

``I really do you know,'' he said.  ``I love you Kiele.''

The taxi stopped, interrupting their revolutionary conversation.  The window became transparent and the driver announced their destination, whilst the two of them gathered their things hurriedly and exited the vehicle.  



\thoughtbreak



Jessie was sitting at home.  It was Friday.  Where was Zane?  He was supposed to be here working on the device.  He wasn't.  He was out.  Jessie was angry.  He had considered going after them, but thought better of it.  Kiele had told him they wouldn't be long.  Maybe his daughter-of-sorts had finally grown a backbone.  Maybe some of his personality had finally rubbed off on her.

He had always despised her weakness, her seemingly mouse like nature.  She was no daughter of his.  She lived in his house, ate his food, but in his mind she'd been nothing to do with him.  On several occasions, after a particularly difficult row, he had sometimes crept into her room and sat on the edge of her bed, knife in hand.  He had so wanted to slit that pretty young throat of hers.  He'd wanted so badly to end the prison that he'd built around himself.  

Ric had never had to deal with the same problems that Jessie had.  He hadn't been required to bring up a daughter on his own.  Granted, Jessie hadn't really cared how she had turned out, she could have been a street walker and he wouldn't have cared, he wouldn't even have batted an eyelid.  However, there had to be some restraint, some discipline to keep her in line.  For seventeen years he had thrown nothing but abuse at her.  He never wanted her to love him.  He wouldn't have been able to deal with it if she had.  It was far better this way.  She hated him and he hated her right back.

He looked down at his watch again.  Where the hell were they?  It was coming up to 9:00pm.  They only had a few hours of the day left.  Jessie had to get the device working, and soon.  Time was literally slipping away from him.  Perhaps they had been involved in a breakdown, he thought.  That was probably the most likely scenario.  He wasn't concerned for their safety one bit.  Once again, Jessie was thinking entirely of his own survival.  Selfish to the core, that was his motto.  



\thoughtbreak



The show was gearing up to be one of the greatest that C-bex Lunacy had ever put on and Cobery was pleased with the bands performance.  He stood at the front, surveying the jumping crowds before him.  It was an experience like no other.  He had dreamt of this moment all his life and now it was finally here.  The crowds swarmed the ground below him, like a colony of hungry ants, searching for some sugar.  Cobery was the sugar and C-bex Lunacy was like a banquet.

Cobery ran his fingers through his chin length black hair.  He was hot.  The stage was like a sauna, peeling off every layer of energy like an electric paint remover.  It hurt, but boy was it worth it.  He looked across at Roy Tuofa, the Lunacy lead guitarist and smiled.  Roy looked back grinning inanely.  He scratched his stubbly chin in apparent thought.  

The band was taking a five minute breather.  They never liked to go off stage, preferring to revel in the atmosphere that their music created.  They also hated playing predefined set lists, far preferring to go where the evening took them.  If the crowds wanted a certain song, they played a certain song and once they had exhausted the crowds in front of them, once the throng of their fans had nothing left to ask for, they'd pick the songs themselves.  It worked well.  The crowd was still going wild.  

Roy broke out into a sporadic solo, joined by the drummer, Oggie Detweiler.  The crowd started cheering louder.  The musicians just couldn't stop playing.  They were having the time of their lives.  Lisa Taylor, the bassist joined in too, and within a few seconds Cobery was there also, backing them all up with his insanely fast lead guitar.  The band played for another few minutes, just improvising, occasionally climaxing into a crescendo of pure rock power.  

Finally they decided to really take a break.  Cobery hung his guitar from his tired limp body and grabbed hold of the mic.

``My my my,'' he said, ``What a lot of beautiful looking people you are tonight.''  The crowd cheered, especially the girls who were screaming at the tops of their voices.

Zane and Kiele were roughly in the middle of the crowd of standing fans.  They were holding hands, partly to show their love for each other, but also to ensure they actually stayed together.  The crowd seemed to have a heartbeat, an entire rhythm of their own, pushing back and forth constantly.  If you didn't move with the rhythm, you were likely to get pushed in a direction against your wishes.

The boy was having the time of his life.  He had never been allowed to go to a gig such as this, his parents being far too overprotective.  He also loved his studies so much that since his parents passing, he'd never felt the need to go see any band live.  Now he regretted his decision.  This was living.  This was absolutely amazing.  

Kiele had been to several gigs before, but never out this late.  She loved the atmosphere also, the waving of the arms, the shouting of the lyrics, the connection she felt with each and every other fan on the field.  They were all there to see the same band play, they all loved the sound of this group of merry musicians, C-bex Lunacy.

Cobery was sat on one of the large amps at the front of the stage.  His hair was drenched in sweat, but he didn't mind.  He was talking to one of the members of the crowd who was sporting a C-bex Lunacy tee-shirt, asking him where he managed to find such a cool item of clothing.

``OK,'' said Cobery getting to his feet and grabbing the mic.  ``We're going to play another song for you guys now, cos we love you so damn much.''  He turned to Roy and nodded to Oggie.  Detweiler started to lay down a pretty funky beat.  Bum-ba-da-dum, Bum-ba-da-dum.  He continued whilst Lisa asked the crowd to join in if they knew the song.

Cobery and Roy, now in unison started strumming the quintet of notes that could only be the beginning of one song.  The crowd erupted in a frenzy of praise.  After the intro, Cobery let his guitar hang from his body, whilst he grabbed the mic, and singing in complete harmony with Taylor, belted out his lyrics.

``You can give me pigtails,'' He picked up the guitar and strummed the quintet, da-da-da-da-da, whilst Roy continued over the top with an arpeggio arrangement.  

``Colour in my hair,'' da-da-da-da-da,

``And all I gotta tell you,'' da-da-da-da

``Is that I don't care.''

They repeated the verse a second time, modifying the lyrics.  As they broke into the chorus, Cobery pointed the microphone at the audience and the crowd obliged by shouting out the lines in fantastic sync.  

``Colour me stupid. Or colour me green.  All I gotta tell you. Don't call me Jean.''

Each line of the chorus was punctuated with the same quintet of notes by Roy, whilst Cobery backed him up with some palm muted continuous strumming.  The crowd were going crazy once more.  Cobery, really beginning to feel the heat now, took of his check cotton shirt and threw it into the audience.  He's got it at a sale in a commercial district in Prestone, it was so long ago, he couldn't even remember where now.  

Cobery continued strumming, his fingers under intense pressure, getting ready to bleed forth if he so much as nicked the skin.  Oggie was twirling his drumsticks again, Lisa was singing her heart out and Roy was soloing as if his life depended on it.  Cobery and Roy liked to switch roles for different songs, they swapped between lead and rhythm often.  It was kind of their thing.

Kiele and Zane were both shouting and singing at the tops of their voices.  It had been an utterly amazing show, full of the energy the band had managed to capture so well on their album.  Each time Zane had listened to it, he had been amazed at how alive they had sounded, how natural and clean the instruments came across.  Listening to them live was something different entirely.  He was part of the music, he felt it coursing through his veins, almost as if it was the music beating his own heart.

Kiele looked happy he thought.  He stopped singing and for a second and just closed his eyes.  The band had reached an impromptu bridge and  Lisa and Cobery were singing to each other one after the other.  'I don't care' : 'No I don't care'  

It was truly electrifying.  He could stand it no longer.  Kiele had to know how he felt.  He felt like his heart was about to burst.  Was it the music?  Or was it his desire to kiss the lips of the woman he loved.  In a split second he was there, holding her close, looking into those hypnotic grey eyes.  He had taken her by surprise and several of the fans nearby had cheered him on.  

They were now stuck there in deadlock once more, neither one really wanting to make the first move, but both of them so desperate to conquer the milestone.  Zane moved closer, cradling her head as he had done on the bench.  Kiele closed her eyes and Zane smiled.  'Silly girl,' he thought, 'don't you want to see me.'  But Kiele was away in a different place, floating in the arms of Zane Krecker, the man she loved.  

As she lay there, almost lifeless, he moved his head towards hers.  Their hearts were beating faster now, and as he held her, he could almost feel his beat adjusting to match hers.  He gently pressed his lips against hers, taking her bottom lip gingerly between his.

They stood there for a few moments locked in an embrace as Cobery and his wife Lisa continued screaming at the tops of their voices.  Oggie got a little too carried away and broke a stick, but expertly replaced it with another from his stash on the bass drum.

Zane moved his hand through her beautiful blonde hair as they continued to kiss.  It was the most amazing feeling either of them had ever experienced.  It wasn't Kiele's first kiss, but it was most definitely her first kiss with a man she loved as much as Zane.  Eventually they broke away, and their parting was met with cheers from some of the surrounding fans.  One slightly drunk, older member of the crowd patted Zane on the back.  

``Gee you're a lucky guy,'' he shouted.

The band finished the song and the crowd managed to somehow get even louder.  The shouting and screaming was almost unbearable.  Cobery lifted Lisa up onto his shoulders and the two of them paraded around on stage to the cheers of their adoring fans.  As they walked past Roy, Cobery shook his hand.  He looked back at Oggie who gave him a 'what about me look,' and Cobery took his darling wife to the back of the stage where all four of them joined in a group hug.  

Kiele stood back up properly and was able to breathe once again for the first time in minutes.  Her heart had been beating so fast that she had been sure she was going to pass out.  It hadn't worried her though.  She knew Zane would catch her, and if he didn't, the thousands of milling fans would have provided a soft cushion for her weightless body.

Cobery was thanking the crowds for their hospitality and wishing them a safe journey home.  When he had finished the band walked off stage and their crew began to clear up the remains of what had been one fantastic show.  There had been no encore, there had been no need for one.

Zane and Kiele stood in the middle of crowds, slowly being directed by a greater force.  Eventually they were able to break free from the rest of the throng and managed to find themselves in a small patch under a tall oak tree, alone.  

``Kiele, that was electrifying,'' said Zane.

``I know,'' she replied, ``they were utterly amazing.''

Zane rolled his eyes.  ``I was talking about the kiss,'' he said.  Kiele had secretly hoped he had been talking about their passionate moment, but had decided to play it safe.  She had looked a little silly, but nothing compared to the alternative.  She played through the scenario in her mind, 'Kiele that was electrifying,' 'I know, it was a fantastic kiss,' 'No, I was talking about the band.' Gulp!

How glad she was that Zane had been talking about their kiss.  He was right of course, the kiss had been totally electrifying.  Like being reborn, like she had suddenly become a different person.  There was no way she was going to let Mark come between them.  Maybe they should just run away now?  That was it.  That was the solution.  Mark would never know, they would just leave.  She had enough money saved up to move to another construct.  She knew Zane had money put aside, and he was smart, so damn smart.

Kiele looked up at Zane who was holding her round the waist.  His attention had been grabbed by one of the bands crew, lugging a huge flight case off stage, containing one of Cobery's or possibly Roy's guitars.  He looked down, saw her looking at him and planted another kiss on her lips, once, twice then three times.

``Well well well'' said a voice from behind them.  ``Am I going to have to start putting locks on your doors at night?''  Zane smiled, it was Mark.  Kiele froze in terror.  Her worst nightmare had come true.  Her nemesis was standing behind her.  Unable to see her expression, Mark placed a hand on each of their shoulders.  ``So how long has this been going on for then,'' he said.  ``You guys should have told me.  I'd have been so happy for you.''

Mark was, of course, lying.  At his very core, Jessie was writhing in pain.  He hated how soft his alter ego had been forced to become.  Mark was nothing like the real him and it pained him to have to put on an act every single damn day.  His grip on Kiele's shoulder tightened.  She knew she was in serious trouble now.

``Sorry Mark,'' said Zane, ``You're right, we should have told you.''

``Hey, no sweat kid.''  He changed the subject entirely.  ``You know I had trouble finding you here.  Kiele's instructions weren't exactly clear.  I almost wonder if she didn't want me to find you.  Hmm?''

Kiele said nothing.  Mark was entirely correct, but then, she had no idea how he had found them anyway.  She had arranged for a taxi to take them home.  Now he had turned up, they would have to catch a lift instead.  She hated him more.  Why couldn't he just leave her alone?  He never cared for her anyway.  All he cared about was his stupid plan and she still didn't know what that was all about.  A chill wound its way up Kiele's spine, making her shiver.  Zane didn't notice, Mark did and smiled.



\thoughtbreak



The ride home was deathly uncomfortable.  Zane and Kiele hardly spoke, though it wasn't through lack of trying on Zane's part.  He had tried to spark up conversations with her several times, but she had just answered in the quickest way possible and in some cases, that had been not at all.

Zane was preferring it now that Mark knew.  It cleared the air and he was ready to begin his relationship with Kiele anew, with the approval of her father.  He really hadn't seen what Kiele had been making such a fuss about.  Mark had seemed like a decent enough guy, he cooked for them, cleaned, and generally seemed to look after his family, of which Zane now seemed to be a part of.  There had been that one outburst in the basement, but it had swiftly been swept under the rug.

They pulled into the drive way of the house and Zane was the first to exit the truck.  It was a black Mutaru X887, Jessie's own vehicle.  Of course it was an internal combustion engine, retro fitted with all the modern gadgets like a JEER fuel injection system, and XDS suspension.  When Mark wasn't planning to change history, his time had been spent creating his perfect vehicle.  The truck was it.  As Zane walked past it, he stroked the black metallic surface.  It felt so smooth and looked so black, almost as if it absorbed all the light that fell onto it.  

Of course, Zane was well aware that physically, being a black surface, meant it did absorb most wavelengths of light.  There was a small grey tinge to the surface, indicating a slight reflection of the entire spectrum he assumed.  To all intents and purposes however, it was jet black and Zane loved it.  The roar it made as it threw its weight forward at intersections, The thrill of the feeling of raw acceleratory power.  The Mutaru could go from 0 to 100 mph in a matter of seconds, despite it being a truck.  One could almost class it as a sports car.

Its handling on the road was impeccable and though he had only ridden in it a few times, Zane had loved each and every occasion.  Heat rose from the twin exhaust, disturbing the air and the light rays as it did so.  The engine was still running and with one more burst of revs, Mark killed the combustion and brought the beast to rest once more.  Kiele had also left he vehicle now and had overtaken Zane and entered the building.  'Just what was with her?' thought Zane as he rounded the right side of the truck and made his way to the door.

``Zane,'' called out Mark.  ``Listen, how about you head down to the takeaway alley, your choice, get enough for three of us.  Your birthday soon right?  Seems like the right time to celebrate.''

``You sure Mark?'' Zane asked.

``Go on.'' Mark walked away from the truck and once it had automatically locked and armed the defensive protocols he added, ``Before I change my mind.''

Zane turned and started walking but Mark whistled him back and gave him a small wodge of notes.  The boy walked off at a fairly brisk pace and the cash machine turned towards the front door.

Kiele was standing in the hallway, looking at her phone, waiting for Zane to enter the front door.  As long as he was with her, she would be safe.  The door opened and the figure of Mark appeared.  He shut the front door behind him as Kiele looked up.  Why had he shut the door?  Surely Zane would be entering any second.  She suddenly felt rather nervous.  Where was her guardian?  

``Good evening daughter dearest,'' said Mark, ``looks like we have a little something to discuss.''  



