\chapter{37}
\section{}
Frustration  

A whirring noise decreased as the boy let out his frustration on the metal desk in front of him

``Damn it!'' he shouted, punching his fists down onto the metallic surface, denting not only the cheap surface, but also his pride.  Today wasn't going well.  Zane's latest idea just wasn't going to plan.  He had tried hooking up the phasic oscillators backwards to try to stabilise the creation of the vortex, but it just hadn't managed to hold on long enough and the reactors had topped out again.

Mark had moved the gear to the basement of the house shortly after he had acquired Zane's trust.  The initial meeting place had been in the odd warehouse for several reasons.  If Zane had flipped out and started screaming at him for creating a temporal weapon, Mark could have disabled him in peace, no one to be suspicious, no one to call the police.  It was also far enough away that Zane would have a hard time locating it to give information to the authorities, had he managed to fool Mark into thinking he was going to go along with his plan.  Lastly, if Zane had removed the blade from the perimeter of the shields, the temporal residue would remain there and not at this house.

Mark had been fairly pleased with his plan.  The only scary part had been transporting a temporal weapon through the streets of the Emblem.  He was sure he was going to get stopped by the police that day for a routine check, but as luck would have it, he managed to transport it successfully without incurring any suspicion or panic.

Now the machine was in the comfort of his own home, Mark was feeling a little more ambivalent.  The blade was closer by, that was a good thing, it meant he could keep an eye on it.  Having Zane working on it close by was also useful.  What worried him though, was the sheer magnitude of the situation sitting below him on a daily basis whilst he munched through his cereal.

Not only were there twelve highly compacted, custom made, nuclear power cells, but there was a device which was so illegal that it was prohibited to even possess the knowledge of its construction.  Of course this made the whole idea more exciting, and as Mark stood there in the basement with Zane, he couldn't help but feel an adrenaline rush at the thought of what they may soon achieve.

Kiele had occasionally been down to see what Zane was up to.  He hadn't told her exactly what the device was, adhering to the plan without deviating.  It wasn't that he was lying to her, he was just waiting to surprise her, that's what Mark had told him at any rate.  Zane had bought it and from then on had kept Kiele at a distance, which had infuriated her on more than one occasion.

``Damn it!''  He repeated the words, slamming his hands down once more.  Mark walked over to him and put an arm around his shoulder.  

``Don't worry Zane,'' he said calmly, ``You'll get it.  OK?''

The boy looked tired.  He had been up since 5:40am and the tension in his brain was beginning to manifest itself onto his face, his brow furrowed, his hands deformed into fists.  He closed his eyes tightly let his head flop backwards.  He was getting nowhere fast.  Mark had placed a lot of faith in him, and currently his involvement didn't seem to be paying off, although that was Zane's take on the situation, not Mark's.

``Listen,'' suggested Mark, ``I'll watch the d-train oscillator, and you keep an eye on the power conversion ratio.  Once we hit three point six, ramp down the power and crank up the ASV OK?''

Zane nodded, though Mark wasn't a great physicist, he did know a thing or two about methodical thinking, something Zane felt he was currently lacking in spades.  He looked over at the modern day oscilloscope with its touch-screen interface and plethora of buttons.  As he watched it, something wasn't quite right.  He lent over and switched one of the dials to a new setting.

``Damn it!'' he exclaimed again, ``I'm not getting any output even on two units per second.''

Mark looked down and immediately saw the problem.  Something somewhere had gotten too hot and had burnt through the probes cable.  The probe and the oscilloscope were no longer attached.  As Zane began checking something on the other side of the room, Mark just stood there holding up the two ends of the cable for him to see upon turning round.  

Zane turned round and saw the frustrated look on Mark's face.  He then looked down and saw the two halves of the probes cable.  He sighed, threw his head back and growled.  Mark had always found his almost primaeval expression of anguish fascinating.  The boy was so mature in so many ways, but in others, it almost seemed as it he hadn't evolved past the stage of a cave man.  

``Guess I'll have to go buy a few more probe cables,'' exclaimed Zane finally.

``Can't we just solder these back together?'' asked a confused Mark.

``No, there's far too many cores in these ones, plus they're so tiny that soldering them is going to alter their physical properties anyway.''

``OK,'' he replied.

Neither of them had noticed Kiele sitting on the stairs watching them.  She hadn't been there long, in fact she had arrived after hearing the first 'Damn it' leave Zane's lips.  She hated hearing him all worked up in the basement.  There were no windows, no air, no escape.  

Zane had had enough.  He threw down the goggles he had been sporting and walked away from the experiment.  He walked up the stairs, and stopped when he saw Kiele.  She smiled at him sweetly .  He wasn't in the mood for a happy go lucky attitude today.  He walked past her without a word.

It cut her deep.  When Zane had passed her without so much as a single word, it had been one of the single most painful experiences of her life, second only to watching him almost die in that ambulance.  Her heart felt like the fists he had made only a few seconds earlier were now pummelling it into a milkshake.  She felt angry at her father for taking away Zane's otherwise happy and cheerful demeanour.  When Zane was with her they were always laughing and joking, but when he slipped into that damn basement, he changed into an obsessed hulk, never smiling or laughing, seemingly never feeling anything other than rage.

Mark had seen him stop on the stairs and moved around the room to gain a glimpse as to the cause.  He saw Kiele.  As he moved towards the bottom of the stairs, Kiele tried to get up to walk away but Mark being quicker, grabbed her by the ankle and tugged hard.  She fell clumsily against the stairs, banging her body against the brutal edges of the steps.  She ended up sat on one of the lower stairs, face to face with Mark as he leaned in towards her and pinned her to the stairs.

``I told you not to come down here didn't I?'' he said gruffly.

``You tell me a lot of things,'' she said defiantly.  He flicked his head to the side quickly before looking back at her, almost as if he were changing the record about to play in his mind.

``I swear to you, you are really starting to push me Kiele.''  His teeth were gritted and he was almost hissing as he spoke.  ``Do not keep this up.  It won't end well if you do.''

Lately she was becoming more and more of a handful Mark had noticed.  Maybe she was getting to that difficult age, but at seventeen, he had expected the worst to be over.  In point of fact, she knew she could get away with far more now that Zane was in the house.  The fall down the stairs she had just experienced would have been nothing compared to what he would have done if Zane hadn't been around.  

Mark had changed too, Kiele had noticed.  He was far more explosive, but never in front of Zane.  It was yet another reason to stay close to the man she loved.  She could see a definite shift in the father's reactions to events.  She knew Zane was the reason.  This stupid plan may not be so stupid after all.  She got to live in a practically normal home, with a father who pretended not to hate her, and the love of her life sleeping in the room next to her.

She nodded to her father and he got up, releasing the cage which had been preventing her from escaping.  She would most likely obtain some bruises from her fall, but it was nothing that some make-up couldn't cover.  She climbed to her feet and began to walk away up the stairs but a hand grabbed her ankle tightly.  She stopped and looked down at her feet and then at the owner of the hand.  He was gripping so tightly that she could almost feel a pulse in her ankle.

``Don't push me,'' he said.  She twisted her ankle and he released his grip, as if she had cast some kind of spell on him.  She ran up the stairs, relieving him of the opportunity to do it again and bolted around the corner into the kitchen, where Zane was now standing drinking a glass of orange juice.

``Things not going well?'' she asked.

He shook his head.  He hadn't meant to be so rude to her earlier, it had just annoyed him that once again he had been set back by another piece of equipment failing.  If Mark had been keeping his eyes on the probes, like he had asked him to do, it wouldn't have happened.  Zane should have learnt by now, not to trust Mark to look after the simple little things.  Though he seemed to comprehend most of what Zane was trying to achieve, his attention to detail seemed to be severely lacking.

 ``I'll get there,'' he said, ``Just more bits failing.''  He smiled at her.  ``Can you forgive me?'' he said ashamedly.

She nodded.  At first it had perplexed her, how Zane could apologise for a simple act of rudeness like ignoring her as he left the basement, yet Mark had never once apologise for any of the things he did on a day to day basis that made her life hell.  She had given up on him being a father a long time ago, now perhaps she was giving up on him even being a human being.  It was just so damn painful sometimes.  The double standards she was privy to now made her often go to sleep in tears.  Thankfully Zane hadn't heard her, or if he had, he hadn't ever said anything.  

Kiele was so fearful of Zane turning into a copy of Mark.  He seemed to respect her father a lot, and Kiele could see flashes of daddy occasionally appearing in the things that Zane did.  Leaving the basement as he had done earlier had been a prime example.  He had looked directly at her and just walked straight past, like she was nothing, like she didn't even exist, or more accurately, like Zane didn't want her to exist.

She opened the refrigerator and took out some orange juice for herself.  The cold carton felt refreshing in her hand and she eagerly awaited the feeling of the sweet juice coating her throat and quenching her thirst.  She took a glass from the cupboard and poured it to the brim.  She noticed some post had arrived and idly walked over to see what had been brought.

When she turned back to the glass she noticed someone had filled it right up to the rim.  It had of course been Zane.  She grinned at him.

``Very funny,'' she said.  ``Now how am I going to drink it.''

``Carefully,'' was his only reply.   

She had gotten used to the occasionally joke that he played on her.  It certainly made life more fun and interesting.  She lifted the glass carefully, managing to do so without spilling a drop, and put her lips to the glass.  She sipped a little from the top before relaxing into a routine drinking rhythm.  She finished off half the glass and placed it carefully down on the work surface.  She twisted her hands in a 'voilà' gesture and curtsied.

``Well done,'' said Zane.  ``And here was me hoping you'd spill it all down yourself.''

She laughed, ``You can be a real pig sometimes Zane.''

``I aim to please.''

The two of them stood there for a while before Zane broke the silence.

``Listen, I have to pop into the commercial district today to buy some more probes,'' he said, ``Care to join me?''

She smiled at him, her face brightening.  ``Well that depends on if you're going to try to make me spill orange juice again.'' she said cattily.  With his one free hand he pointed at himself.  

``Me?'' he asked.  She raised her eyebrows to him and they both laughed.  ``I'll just go grab my stuff,'' he said.  ``I'll be leaving in fifteen minutes.''  She nodded and walked out of the kitchen to ready herself. 

Mark had heard their little meeting from the top of the basement.  She was still serving a purpose he thought.  The boy needed a break every once in a while.  If she distracted him too much though, he would have to intervene.  There wasn't enough time for that.  His deadline was tight, very tight.  He had lost a week already and it seemed like the boy genius was getting nowhere fast.  To top it off, they were running out of power cells.  Oken had designed them specifically and finding suitable replacements was going to take time, too much time.  They had to conserve as much power as they could, but this meant changing too many things at once before testing, leading to mistakes and problems.  It was a particularly frustrating process.



\thoughtbreak



The two teenagers walked side by side as they wound their way through the narrow roads of the commercial district.  It was a hotter day that usual and the sun was beginning to beat down on Zane's back.  He adjusted his collar to keep the sun off his neck a little.  There was a light breeze whisking its way through the streets and each time it hit Zane he felt a short burst of relief from the heat.  It wasn't often this hot at this time of the year.  The sun was high in the sky now, offering little shade to the people milling around below.

They had walked the entire journey from the house to the commercial district and both of them were feeling severe fatigue now.  Zane had insisted on walking even though he was supposed to be recovering from his stay in the hospital, but despite Kiele's disapproval his stubbornness won through.  Kiele didn't think she'd ever walked so far in all her life.  Zane, thought he had, but not for a long time.  

He had been taken on numerous walks and treks when his parents had still been alive, but when they had left him for the better place, he had confined himself largely to his apartment.  Since living with Kiele and Mark he had begun to enjoy walking again and had often left the house on a trek when the physics had gotten too much for him.

``I really need something to drink,'' said Kiele.  

``Already?'' remarked the boy.  He was in desperate need of a drink too, but he wasn't about to admit that to Kiele.  It was far more fun to pretend otherwise.

``You're seriously telling me you're not thirsty?'' she said, totally unaware of Zane's smirk as he looked the other way.

``Kiele, I could walk another fifteen miles before I'd need a drink,'' he said, lying through his teeth.

It finally got the better of him and he laughed.  She slapped him across his left bicep and he yelped in woeful sarcastic pain.

They rounded a corner and Zane spotted a sign.  They were bound to have drinks there.  'Haito's Sandwich Bar'.  The little shop had hardly changed in twenty years, but its customer base had.  Haito's was now one of the busiest eateries in the district and it pleased the little man no end.  Finally he was serving his public as he had always dreamed.  Mrs. Haito had passed away recently, and though he had closed up shop for the first time since its opening, Haito had returned to work shortly afterwards.  

The proprietor knew it was what she would have wanted.  They'd had a long happy life together, building the shop from the ground up.  It was their life together and Haito wanted to continue it for as long as he was able.

Zane opened the door to the sandwich bar and immediately they were immersed with the smell of baked bread.  It was intoxicating.  Kiele closed her eyes and breathed in deeply.  It smelt just like the corner shop she had used to sit outside as a child, hoping that the proprietor would call her in, as they sometimes did, when the day was over and there were some leftovers.

``Mmmm,'' Kiele voiced.

The two of them walked in and Haito ushered them towards the counter.  

``Come, come, my friends, I see you like nice food.''  His English hadn't improved at all in twenty years, but to be fair, he looked remarkably good for his age.  

The two teenagers walked up to the counter.  ``Now, what I can get you?'' he asked excitedly, ``panini, sandwich, baguette?''  

Zane held up his hands, ``Thank you, but, we just need something to drink?''

``All drink, no food?'' exclaimed Haito.  ``Oh no no no no no no''  The repetition of the word 'no' reminded Zane of rapid machine gun fire, the little man seemed to be able to reel them off endlessly.  ``No food means very hungry later.''  He beamed at them, ``You two look like favourite customers of the day, you sit down, I bring you over snack.''

``I don't have much money on me,'' said Zane.  It was true that he literally had enough for the probe cables and a drink, which they would probably have had to share anyway.

``No charge,'' said Haito.  He pointed at them, ``Favourite  customers of day, remember?''

They both smiled as the little man ran off to the kitchen, shouting something about bacon and toast.  A cry came back, which was largely inaudible and Haito about turned, mid run, and came flying back out the doors again.

``You eat animals no?'' he asked in a rushed tone.  He had known the proper word for meat, but in haste had blurted out the first thing that had sprung to mind.  They both nodded and Haito was off again, rushing through the doors rattling off repetitions of 'yes'.

The couple sat down at a table near to the windows.  The place was fairly crowded, but not so much that Haito's remark about the 'Favourite customers of day' had gone unnoticed.  Everyone seemed to be looking at them and Kiele suddenly felt very self conscious.  Her cheeks started blooming into a beautiful shade of red and she hung her head in apparent shame.

``Kiele,'' motioned Zane, ``it's OK.  They're not looking at you.''  He tapped her on the shoulder and pointed out of the window.

``Look at that,'' he said.  

As Kiele turned and looked, several of the customers turned their heads to look towards what the young boy had been pointed at also.  In point of fact there was nothing out there, but Zane had subtly broken their fixation on him.  Slowly, as the other customers either realised there was nothing out there, or craned their necks to get a closer look, the mood of the establishment turned back to its usual drone of quiet banter and munching of good quality food.

They sat there idly chatting about the heat for a few minutes until Haito turned up with a plate full to the brim of bacon and cheese sandwiches.  Kiele's eyes grew wide in terror.  There was no way she would be able to eat half or even a quarter of that.  Zane too, was a little surprised at both how much Haito had managed to fit on the plate, and how much he was willing to give away for free.

He set the plate down in the centre of the table and hurried away to bring over two drinks.  He caught their attention from behind the counter and began to point at various beverages which Zane and Kiele were forced to shout out yes and no answers.  Eventually Haito was convinced he knew what they wanted and brought over two glasses of cola.  

``Thank you so much Mr?'' Zane stopped short knowing that he hadn't been introduced to the man yet.

``Haito,'' said the little man, ``Call me Haito.''

``Thank you Haito'' said Kiele sweetly.

``My pleasure,'' he said, placing the emphasis on the word 'my'.  

``You didn't have to do this,'' said Zane, ``we do have money, just not right now''

He felt bad for the man, though he could see the business was certainly doing well, Zane had never been one to accept charity.  Another leftover teaching from his father he supposed.

``I do for you, because when I see you, coming in to my shop.  I see two people very much in love.  Maybe love at first sight.  Very special thing indeed.''

Kiele and Zane both smiled, noticed each other smiling and then wiped the smiles off of their respective faces.  Haito laughed.  

``Still no tell each other yet.''  He giggled and walked away.

They sat together and ate well.  The food was delicious and Zane joked about taking the rest home with him.  Haito must have heard, as he brought over what appeared to be a purpose built cardboard box, just for the occasion.

After they had eaten all they could, they remained sitting for a while longer, watching the passers by.  As Zane sat there, arm resting on the table, Kiele reached out and placed her hand on his as she had done in the hospital several weeks ago.  It was so soft, thought Zane, as he sat there trying to prevent himself from turning his hand over and holding hers.

He lost the battle and amidst the hustle and bustle of the commercial district, two souls became closer together.  His hand wrapped tightly around hers, his longish fingers cradling her delicate pad.  He couldn't look at her yet, he was feeling far too embarrassed.  It was a strange feeling for him, yet he found he had experienced it most when he was around Kiele.  Maybe he was just too concerned with her opinion of him, but he detested being made a fool out of in front of her.  

He was due to start back at college next week and he could only imagine the utter ridicule they would both endure if someone found out that they were a) living in the same house and b) romantically involved.  

Kiele on the other hand was just happy, they were a couple of few words, never speaking a whole lot about their feelings, just content with being in each others company.  As she felt his strong hands holding hers, she was forced to consider Mark.  Just what would he do if he found her publicly showing her affection for this boy?  She still had to consider his plan.  Once it was over, it wouldn't matter, they would be together, she was sure of it.



