\chapter{29}
\section{Out Of Character}


Over the next few days Kiele had visited Zane a lot.  Though it had been during the week, the school had been surprisingly lenient with her attendance and had allowed her to leave early from lessons on several occasions.  Of course, the rest of the class knew where she was going, and a cheer of Oooooooooooo, would erupt whenever she did so, but she didn't really care about them any more.  She'd even started to stop turning that embarrassing shade of red, answering back with comments like ``You're obviously all jealous, or stupid, and I just can't decide which.''

Today she was going to visit him again.  It was Thursday, almost a full week since they had learnt about Oken for the first time.  So much had happened during those few short days that Kiele found it difficult to process everything.  Jolie had said she would be visiting this afternoon also.  Kiele marvelled at how awesome Jolie had been to her.  The dress, the lifts too and from the hospital whenever she was able, letting her go early from lessons.  It felt good to have someone look after her properly, for a change.  She finally felt like she knew what it was like to have a mother.

Having only had a male role model, and not a good one at that, she had been forced to learn everything about being a woman from either books, friends, TV or the net.  Conversations had been difficult and she had often heard the comment ``didn't your mum ever?......oh yeh.....sorry Kiele.''  Each time it was like a dagger through the heart.  She was different to everyone else it seemed.  Though there were many In Vitro children around, she felt particularly isolated by it, and considered herself, to all intents and purposes,  practically an orphan.

When she had been in her first few years at primary school she had often told people she was an orphan.  It was the only way she ever received any special treatment at all from the other children.  They would sit next to her at lunch, give her hugs and generally ensure that she was feeling OK.  Unfortunately, a teacher overheard her telling her tale to another student one day.  Knowing that Kiele had a 'loving' father, she berated the child in front of the whole class, telling them that this girl was the epitome of what they should look out for as they were growing up.  The teacher had made Kiele stand in the corner of the class room for most of the day, it had been one of the single most devastating moments in her life.  Coincidently, when the teacher had rung home to tell Mark, he hadn't cared in the slightest.

Kiele looked up at the clock, merrily ticking its way through the day.  Its slow beating could be heard over the classes hushed whispers.  They were currently studying biology and most of the class sat there in a state of disinterest.  It wasn't that the subject matter was particularly boring, it was the person delivering it.  

Mr Jugard, or 'Jughead' as they called him, was one of the most monotonous public speakers in the world.  It was practically impossible to impart any kind of enthusiasm into their work when each word seemed exactly like the last.  He occasionally tried to wake the class up by saying things like 'Come on class, I know you know the answer' but they had been drugged into a lethargic abstinence and were unable to contribute.

He had been their teacher for a few years now and Kiele wondered if during that time she had ever enjoyed one of his lectures at all.  She smiled as she remembered one particular lesson when Ol' Jughead had managed to set his tie on fire, teaching them about the calorific value of food.  It had been hilarious.  As he had realised what was happening he had danced around at the front of the class for a few seconds shouting 'Help me, Help me' in a robotic tone, before plunging his tie into the nearest sink.  As he withdrew the tie from the murky water, he had exclaimed, 'Oh, that was my favourite tie.'  In his monotonous nasal voice.  It had set the class into fits of hysterics and the phrase 'Oh, that was my favourite X,' became a long running joke among the students.  

Kiele hadn't realised that she had smiled, but Jughead had.  ``Something funny about aerobic respiration miss Matthews,'' he asked.  Kiele was so bored.  She shook her head.  ``I suggest you leave your mirthfulness outside next time, less it should interfere with your cogitation.''  What an ass.

She had another thirty minutes at least before she would be allowed to leave the class to see Zane.  Janus, was sitting next to her and they were situated near the back of the room.  In fact it had been surprising that Ol' Jughead had seen her without his big old glasses.  

``Bet you just wanna skip out and see him again right?'' asked Janus.  Kiele nodded.  They had been acquaintances for a while but had never really hit it off.  Janus was one of the popular girls.  Kiele, despite being one of the most beautiful in the class, had always been a little too reserved to make 'popular' status.

``Are you two going out?'' Janus asked.  Kiele answered 'no' quietly and rather ashamedly.  She would have loved to say yes to that question.  She picked up her pencil and began to doodle on the front cover of her notebook.  Most of the class used various e-ink pads now, but some still couldn't afford it, and others preferred the tactility of traditional pen and paper.  Kiele was the latter of the two.  

``Still,'' said Janus, ``I bet you like him a lot right?''  Kiele smiled and nodded.  Just what was with the third degree anyway?  Suddenly it hit her.  Did Janus have feelings for Zane too?  ``I used to have a big crush on him,'' she said, confirming Kiele's suspicions.  ``But I can see he likes you.''  Kiele hadn't been expecting that sentence.  Now she had heard it, it made her feel rather special.  Secretly she had been hoping Zane was falling for her.  She had been pretty sure he was, but if Janus' had noticed it too.  It had to be true.  Right?

``You really think he likes me?'' she said after a pause.

``You bet,'' smiled Janus.  

The two girls sat there whilst Mr Roboto continued his incessant ramblings about oxidation and the Krebs cycle.  Kiele drew a heart on her book and inside wrote KM 4 ZK in true teen style.  She drew the arrow through the heart catching the attention of her fellow classmate.  Janus giggled and Kiele contagiously obliged also.

The robot had heard them.  ``And so ATP stands for what, Kiele?''  It wasn't fair.  She had only giggled.  This guy was a real jerk.  Most of the other teachers let them chat whilst in lessons, doing so got them respect, respect meant the kids actually listened, and eventually led to good grades.  Jugard didn't let them talk.  Hell he wouldn't let let them do anything besides listen and write notes.

She knew the answer but something different left her mouth.  ``Aliens Take Prozac?'' she ventured.  Where had that come from?  In an instant she remembered.  'Aliens Take Prozac' was the name of a punk band she had used to listen to.  Jughead wasn't pleased.  He relinquished his position up on his podium and quickly, but purposefully, walked towards her, finger outstretched.  

``Young lady, would you kindly step out side, since you obviously have no intent on doing any learning today whatsoever.''  He stopped short of her.  In the staff room meeting at the beginning of the week, the teachers had all been informed of the accident and had been asked that they be gentle on Kiele for the next few days at least.

Juggard had no intention of being soft on this insolent brat who quite clearly needed to be taught a thing or two.  He stood their waiting.  Slowly but obediently, Kiele packed her bag and stood up.  She hadn't just been bored for the sake of it, she had studied aerobic respiration the previous year.  As she walked out of the room she offered up a piece of advice.

``You've spelt Adenosine wrong.''  The class roared.  Jughead, furious now, followed her to the door quickening his steps, seemingly desperate to catch up with her.  The class had broken into a round of applause.  She cross the threshold and jumped as the door was thrown into its frame by an angry mechanical creature, severing her connection to admiration from her peers.

The girl walked down the corridor, kicking a can as she did so.  She had never been thrown out of a lesson before.  Kiele hadn't meant to upset the old man, she just hadn't cared.  Her mind had been completely elsewhere.  Her mind had been with Zane.  

She supposed she should wait outside till the lesson was over, but she had no intention of doing that.  There was no point.  Jughead would only shout at her, and she refused to be put into a bad mood before she visited Zane.  She walked out of the corridor and into the hot sun.  It was getting close to autumn now but the sun was still quite warm.  She decided to head to the cafeteria.  Maybe they would serve her early.

As she entered the large hall she was called over by a large lady standing at the serving hatch.  Her name was Betty and she knew Kiele well.  It was usually her who served the young girl lunch everyday.  They often had a chat about the weather, or certain members of the rabble queueing up.  

``I hear you were in an accident darling?'' asked a concerned Betty.  She had already started dishing out Kiele's lunch, so it seemed as if she wouldn't have to ask after all.  ``I almost had a heart attack when I heard, I was so worried about you.''

Kiele smiled.  She liked Betty.  The lady was always smiling, a true ray of sunshine in an often harsh environment.  Kiele wouldn't say she had a hard life at school, but when the combination of a bad day and her father were getting her down, it was nice to have a friendly face who could make her day just that little bit sweeter.  

``I'm OK,'' she said assuringly, ``but Zane is still in hospital.''  It seemed as if Betty already knew this as she nodded whilst piling up yet more food onto Kiele's plate.  She often over filled it, but Kiele never complained, Betty was just looking out for her after all.

``I heard dear,'' she said.  ``He's the good looking one in your class isn't he?''  Kiele blushed slightly.  Betty hadn't even really mentioned her in the sentence, apart from as an identification of the class, but she still felt somewhat embarrassed.  ``And a little birdie told me that you two could soon become something special,'' said Betty as she waved her serving spoon at Kiele.

Now Kiele really did turn red.  Betty saw and ceased her current line of questioning.  She hadn't wanted to make the girl feel uneasy.  ``I'm sorry,'' she said, ``Your secret's safe with me.''  Kiele smiled and thanked her.  She took the tray of food and enquired how much she owed.  ``No charge,'' said Betty.  Kiele was ordered to go eat her meal before it got cold, to which she obeyed, sitting in a corner of the hall.  It would be fifteen minutes before anyone else came into the cafeteria, hopefully she could be finished before then.



\thoughtbreak



Jolie had dropped Kiele off today, as she had some errands to run.  It would be the first day that Kiele would visit Zane entirely alone.  She still hadn't managed to see what the present was that her father had given him.  Each time she had brought it up, Zane had changed the subject.  Was it something embarrassing?  Something about her?

As she walked through the corridors today, horrible though it was, it felt natural, like slipping into a warm bath.  She knew exactly where she was going.  As she got to the door of the ward, she stood there for a while, looking in at Zane.  He was sat there reading his book with his legs up in an upside down 'v' shape.  He looked deep in concentration, his brow furrowed and one hand holding his lower jaw pensively.  She walked in slowly, trying not to arouse his attention.

As she approached him, she accidentally squeaked her shoe on the hard, shiny, laminate flooring, which had obviously been polished that morning.  Zane looked up and upon seeing Kiele hurriedly closed the book and hid it under the covers.  She gave him a look, entirely unimpressed.

``What's the book Zane?'' she asked.  

There was no escaping now.  He had to give her the full explanation.  He had managed to hide it for a mere few days, but finally he could hold off her onslaught no more.  She could be very persistent when she wanted to be.  He motioned for her to come over.  She sat down on the single chair next to his bed.  As she looked across to the bed on his left, it seemed as if the patient there enjoyed one hell of a visit prior to her arrival.  At least ten chairs sat there in quiet audience in the presence of a now sleeping sufferer.

Zane slowly, but deliberately took the book out from under the covers.  As the cotton sheets slid over the front cover of the book, the author first became visible.  'Jamilio Hadrenkes.'  She'd never heard of him, or her come to that.  It was a name with which she was entirely unfamiliar.  It sounded like the author of a seedy romance novel.  Was that what he was so embarrassed about?

As the sheets completed their journey across the cover, the title became visible also.  ``The Temporal Nature of Time.''  She looked confused.  A science book?  Really?  Her father, Mark the dumb-ass-culous, had managed to pick out a science book that Zane would actually be interested in?  As she looked back up at the boy she could see an almost fearful look on his face.  Was he that scared by her finding out that he enjoyed reading books about scientific theories?  She wasn't that shallow.  Was she?

Suddenly Zane's body twitched and he winced in pain.  It seemed as though he wasn't one hundred percent better yet.  As his body flicked the covers, the book fell to the floor and a small piece of paper slipped out.  Zane, now relaxing once more looked down.  He could see the book and the paper, but there was nothing he could do about it.

``Please,'' he said, ``pick it up now.''  He sounded genuinely scared.  ``You can read it if you must, but please pick it up now.''  She obliged, recovering the book from its strewn position on the floor and passing it back to Zane.  As she bent down a second time she had to stretch a little further to reach the paper, tipping her chair forward as she did so.  Her hair fell either side of her face and created a shield, through which she could remain expressionless.  Righting herself, she read the note which had been scrawled in her fathers handwriting;



'Zane.  I know what it feels like to have a passion for something.  Here's a little something special to prevent you going crazy whilst recovering.  It's not what you would call an 'available' item any more.  Please keep it entirely to yourself.  You can probably understand why – Mark'



She looked back at Zane.  Was it really?  Had her father given him an abolished book?  Where had he managed to get such a thing?  More importantly why had he given it to Zane?  The poor boy still sat there, a look on his face of pure horror at her having read the note.  'A little something special.'  The words tore through her like a carnivore through meat.  Since when had she been given anything even minutely special, and now here he was getting gifts of almost priceless value.  She had had an her expensive dress bought for her by her history teacher.  She hadn't noticed her hands curling into fists.  The right one hanging down by her side, the left one, now void of the note, screwing up the cotton sheets.

``I'm sorry,'' said Zane, ``I should have told you when you asked the first time.''

She snapped back piercingly, ``Damn right you should have told me Zane Krecker.''  People rarely used his full name.  The surname, of Deutsch origin, was apparently hard to pronounce for some, the rolling of the first 'R' causing the most difficulty.  She was quite obviously mad, and Zane was fearful of more outbursts of frenetic behaviour.  

``That wasn't meant for you,'' she said.  ``It's just,'' she paused, ``my father hasn't ever given me anything a little special.''  It wasn't jealousy.  She just couldn't understand what Zane had brought to him that she hadn't.  She had no idea what Mark had planned for the young lad, no idea at all.  It was infuriating, yet it was totally unfair to release her anger on an entirely innocent party.  Zane had nothing to do with her fathers actions.  He apologised again and she smiled at him.  She couldn't stay mad at him for long.  

``What does he mean about keeping it to yourself?'' she asked naively.  ``Why isn't it available any more?''

``This book should have been destroyed years ago,'' replied Zane, ``It's a left over from the temporal period.  I've no idea how your father got hold of it, or why he gave it to me, but it's a damn good read.''

Kiele looked worried, ``Zane, are you sure you should be reading it?  If it was supposed to be destroyed, it was probably for a good reason right?''  Zane had never seen her face look so concerned in his life.  She was really disturbed by the presence of the book.  He should have listened to himself.  He had vowed the day he had opened it to only read it at night, that way no one would question what it was he was reading.  The pages had gotten the better of him however, enticing him further and further into the depths of its hidden secrets.  It was true, it had been a truly fascinating read but as a consequence, it had been harder and harder to put it down.

It had started with sneaking a page or two during his lunch but very quickly he had cottoned on to the fact that if he pulled his knees up, he could hide the cover effectively.  On several occasions, he had made himself stiff by sitting like it all morning.  Kiele had visited a little earlier than usual today and he hadn't had a chance to hide it as he usually managed.  

``I really don't think it's anything that bad,'' said Zane roughly.  ``You know what governments are like.  They always try to ban things which they don't understand.  They probably destroyed any physics book with the word time in the title.''  

He gripped the book tightly.  He was grasping at straws now.  He had already let Mark down by telling Kiele, the note had been specific, 'Please keep it entirely to yourself.'  Damn it.  If only she hadn't walked in at that moment, if only she hadn't come to visit him.  His mind halted and another voice stepped in.  'Is that what you really want?' it asked.  'You really want her to go?'  

``I'm sorry Kiele,'' he said sheepishly.  She was looking at him with a real effort of confusion.  She couldn't understand just what was so important about this book.  Neither could Zane.  It was something about the combination of Physics and it being a forbidden text.  It felt like it had been written by an ancient civilisation or something and he was unearthing it for the first time.  He couldn't tell that to Kiele, she would think him a fool.

She said nothing.  Still she sat there.  Mark was doing it again.  He had given her something, the opportunity to meet Zane, and now he was taking it away again.  She backtracked.  He hadn't just given her the opportunity, she had had that already, Mark had consciously told her to flirt with Zane.  Her feelings had done the rest.  She hadn't been able to contain those strong feelings, itching, scratching to get out.  She had fallen in love.  So quickly, so deeply, but she was there, and now once again Mark was breaking her heart.

``It's, just,'' she started and then backtracked, ``Zane, I really like you and I want to trust you, but,'' she was finding it difficult to see the words, ``when my father gets involved, things generally go bad for me.''  She didn't realise that her head was down now.  She was now looking at the hem of an orange skirt.  It held a history with it.  Slightly frayed, she had repaired it several times, yet as she studied it, even she couldn't tell where.  She was ashamed, ashamed of her father.

``He seemed like a nice enough guy to me?'' Zane said untactfully.  He had only met the guy twice, maybe three times, but he hadn't been able to detect any malice in his actions.  

``A nice enough guy eh?'' said Kiele.  She decided not to push it any further.  Zane would soon find out what her father was like.  Mark was probably trying to deliberately drive a wedge between them and she wasn't going to let that happen.  She would fight him to the bitter end.  Zane was hers, and he was going to have to realise that.  At the same time she reached her triumphant resolution, she also felt very scared of the preceding conversation.  If Mark found out she knew about the book, things could turn bad anyway.  As she mused further she remembered her fathers comment about 'finding out about it anyway.'  Maybe things would be all right after all.  At least on that front.

``I guess you could be right,'' she offered.  It was time to change the subject.  

The sun was fading already, though it was only three o'clock.  The light streaming in through the window created long shadows which seemed to touch everything in the room.  It had become quite hot and sticky on the ward and Kiele wished she had worn something a little lighter.  It would have been nice to take her top off and feel the cool breeze against her skin, the she remembered who was sitting in the bed next to her.  Zane would have just loved that, she thought.  

As the trees lining one side of the hospital entrance blew in the light breeze, their branches played with the light.  It was as if the leaves were the fingers of a young child, discovering water for the first time.  Inside the hospital, the perturbed light was dancing, or maybe it was the shadows that were dancing.

Zane looked down at the book, entirely shaded by the curtain on his left hand side.  Its cover was brown and thought it was a twenty first century book, it had been published to look like an old text.  In truth it was probably destined for the popular science section, a misclassification by the publishers.  The text on the cover was difficult to read against the the rest of the background.  There was no outlining or highlighting, or even a change of colour, the text was just an embossing.  Years later the text would probably fade into oblivion, worn away by years of shelf action.

It was a fairly thick book, around about one inch and Zane was already half way through.  The spine had slight tears at the top and bottom and he could sense the book had definitely been read by a large number of people.  He was actually holding a G-TEP copy of the text.  It had been confiscated by the force almost thirty years ago, and was used to teach new G-TEP recruits about the fickle nature of time.  

``I bought you some things,'' said Kiele, making the change of subject that was so desperately required.

Zane smiled, ``You didn't have to do that.''  

As she fished around in the bag that had accompanied her, Zane once again was dumbstruck by her beautiful face.  The light coming through the curtain lit up every feature and Zane was once again very much in awe of her gorgeously chiselled features.

``I know I didn't have to,'' she said, ``but I wanted to.''  She fished out a data disk, and a few e-ink pages.  ``I bought you some magazines to read,'' she said as if the book never even existed, ``and I thought you might like to listen to this.''  As she handed him the data disk he turned it over in hand.  On the side it read, 'Colour me stupid – C-bex Lunacy.'

Zane knew the song.  He knew it well.  It had been going round and round in his head for weeks now.  A part of him hated it for that, another had a strange respect for it.  Either way, it was an awesome feel good song.  He let out a big grin.

``Thanks Kiele,'' he said, ``I really like that track.''

``It's not just one track,'' she replied, ``they named the album after that one song.''

Zane took a second look at the data disk, as if he could somehow read the data from it with his eyes.  He turned if over again saying, ``Oh cool.''

A nurse arrived and began to prod at the monitor.  Neither of them had seen her coming.  It was the 'friend' Zane had made earlier.  Kiele and Zane sat there in complete silence, neither one wanting to speak whilst in the presence of the ogre.  She was rather terrifying and Kiele couldn't help but re-study her skirt once more.  She crossed her legs and as she did so she clipped one of the chrome rods of the bed with the toe of her shoe.  It clanged loudly and the hospital bouncer turned around and glared at them, seemingly melting them both with her laser eyes.

``Don't stop talking on my account,'' growled Natasha.  Zane had read the name from the badge on her tunic.  It seemed such a pretty name, why on earth was it hanging around someone so hideous?  He smiled at the towering column of hatred and spoke in a strong accent.  ``Oh we wouldn't dream of it, would we Kiele?''  On hearing Zane's words Kiele almost burst into laughter.  She was smiling too much and she couldn't lift her head now.  Instead she just shook it.  Thanks a bunch Zane, she thought, why did he have to drag her into his quarrels with the staff.

With that, the ogre was gone, stomping off into the distance.  Zane was sure he could sense small tremors in the ground, but there were none.  Kiele looked up, still smiling.  He shot her a grin.

``I almost burst out laughing then,'' she said in an angry tone.  It wasn't real anger of course, but Zane responded with a shrug of his shoulders and she retaliated by slapping the back of his hand with a very purposeful grimace on her face.

Oh how good it felt to be laughing with her again Zane thought.  He had hated the tense moment they had shared but a few minutes ago.   Kiele had hated it too and her thoughts were largely in tandem with his.  Though she had slapped his hand, it had stayed resting on his.  He could feel her hypnotic warmth seeping through into his comparatively cold body.  Her skin was so soft, and for a moment her had no idea where her hand ended and his began, the only indication being the heat potential that glued them together.  He didn't want it to move.

Kiele hadn't wanted to move her hand either.  She felt connected to Zane.  It was true, he had saved her life, but it felt much more than that.  Much more than simply an infatuation with a heroic figure.  Zane was handsome enough, but Kiele felt something different from him.  Something she had never experienced before, at least not so abundantly.  He was honest.  

Mark had been telling her lies for years; She couldn't go to the park because aliens roamed the neighbourhood looking for small children to eviscerate, not that she had known what that meant; There wasn't enough money for him to even buy enough food, let alone a new dress for her; The woman who was staying in his room was going to be her new mum.  

In time the truth of all the lies had found its way out.  There were no aliens at the park, he could afford anything he wanted, including a new TV and the woman in the room, she had only been there one night and Kiele hadn't ever wanted to know the real truth.  The only one that had mattered was that the woman wasn't going to be her new mum.



