\chapter{15}
\section{An Unexpected Gift}


Zane walked down the street towards the Zone.  In some ways he rather regretted his rash acceptance of Jolie's offer to revisit the place.  It was a beautiful day and he could have been outside doing anything.  Instead he was going to be stuck in a disused train platform, looking at bloodstains and concrete for most of the morning.  He had decided that the best way to approach this assignment was to actually begin writing it 'in the Zone'.  He hoped it would give him the drive and inspiration to really get inside Oken's head space.  After that he would retire to his room, where he would continue his efforts.  

The boy lived in an apartment, a hotel really.  His room was his only room, save that of a small bathroom at the rear of the place.  It had become government practice to all but abolish foster care.  It seemed to add too much of a drain on society; social service costs, psychiatric care, medical fees.  It really wasn't worth the effort.  Adoption was still available, but checks made against prospective parents were often poor.  If a child was old enough to look after themselves, the government rented them a cheap apartment until they were the age of eighteen, when they would be expected to begin paying their own way.  If they were under the age of 14, they were taken to one of many orphanages.  If someone was willing to look after the child, it was classed as an adoption and the newly created family would be sent on their merry way.

Zane enjoyed living on his own.  His time was his own, his space was his own.  Sure it got lonely sometimes, but it allowed him plenty of time to study, plenty of time to make his parents proud.  Though he wasn't of religious background, Zane believed in heaven.  It was that belief that kept him going, that his parents were somehow in a better place, looking down on him constantly.  Everything he did was for them, to please them, to win their approval.  

He kicked an empty can as he continued on the road.  He pulled out the piece of paper Jolie had given him and turned it over a few times before beginning to flick it with his right hand.  Rhythmically, he started humming along to 'Koken's – You ain't seen me till I'm Dead' an odd track about life as a zombie.  As he got more into the track he started shifting his shoulders from side to side.  His mouth hung open in a kind of gormless gaze and he puh'd the rest of the song, his gaze never leaving the folded piece of paper.    He'd have to unfold it pretty soon he thought.  

Bump.  He hit something soft.  He'd been concentrating on the paper for so long he hadn't realised that he'd still been walking and had actually crossed two roads in the meantime.  The drivers of the cars had shouted at him, presuming he was using a mindman; the most advanced of all personal media devices.  In truth he'd just been stuck in his own mind; no enhancement necessary.

Zane looked up and was taken aback by the sheer brilliance of her blonde hair.  The denim skirt had been chosen again today but Zane wasn't counting.  His glance continued upwards till his eyes met hers.  He stood there frozen, as if caught in her gaze, unable to talk, walk, or even squawk.  Finally he recovered enough to say something.  Only it wasn't a word, more like a gasp.

``An apology would be fine,'' she said.  His mind raced, 'an apology?  What for?'  Then he remembered that he had been so intent on his piece of paper that he'd walked straight into her.  She could see that he was struggling to compose himself.  To make his humiliation complete, she gently took hold of his lower jaw and mockingly made him speak.  ``I'm so sorry Kiele.''  He batted her hand away before trying to redeem himself.

``I didn't know you were coming today,'' he ventured.  Had she come because of the assignment, or because of him.  Why did his brain keep going down these paths?  He didn't care if she liked him or not, because he wanted nothing more from her than help finding the address Jolie had given him.  She leant against one of the many street lamps and as the wind dusted her hair she popped a lollipop back into her mouth.  

Taking a quick suck on the sweet strawberry flavour she removed the lollipop and added ``So if I were someone else, you would have apologised?''  Zane was trapped.  Damn her, she'd got him again with her quicker thinking, or maybe it was just because Zane was currently incapacitated by her beauty.  This blonde was definitely not stupid.  She knew exactly what she was doing.  She threw him a line as the silence was killing her, 

``I wasn't going to come.  But when my dad heard there was an extra session and that some loner idiot was going, he decided I should go too.''  

Though she said it in a tone that would have indicated resentment, Zane felt that she actually didn't have a problem being there.  True, it probably wasn't her first pick of things to do on a Saturday, but she didn't seem to be acting as hostile as she could have been.  Zane managed a fairly unimpressive, 'Oh', before holding out the piece of paper to Kiele.  He hadn't even unfolded it yet, but in his mind he assumed Jolie would have given it to Kiele had she known she would be joining him.

Kiele silently unfolded the piece of paper.  A car zoomed past them at breakneck speed, followed shortly afterwards by a police car.  In the distance Zane could see them darting in and out of pedestrians and other vehicles before turning a corner about half a mile away and disappearing from sight.  The siren had shocked Zane and re-engaged his brain.  Kiele in contrast hadn't even really noticed the chase as it had zoomed past her body.  

The girl read the paper quickly and folded it back up again.  She handed it back to Zane and he quickly pocketed it, pleased that she had acknowledged that he was the one in charge.  Deep down, both of them knew Kiele was in charge, but they both seemed to prefer it this way.  ``I think we need to go this way,'' she said, pointing to a small alleyway.  

Zane looked at her dainty finger, aiming at some nondescript passage way.  It seemed so smooth.  There were no lumps or bumps, not that people usually had lumps and bumps on their fingers.  Hers were just perfect.  Her veins, almost invisible, left slight raised tunnels across the back of her hand.

``Really?'' he questioned.  ``You want us to go this way?''  Zane was teasing her now.  He looked up and down the alleyway.  ``I'm not sure at all,'' he said and then raising a hand, whispered in her ear, ``I've heard it's haunted.''

She tipped her head to one side, completely unimpressed by his sarcasm.  ``You're such an ass'' she said as she flicked her head to the side causing her hair to slap Zane in the face. She began to walk towards the haunted passage.  'Haunted indeed' she thought.  Whoever heard of such nonsense in their lives.  The distance between them increased.  Zane was still standing there.  Her hair had smelt so damn good.  A part of him wanted to ask her about her brand of conditioner and shampoo, but no self respecting man would've done so.  Damn his little brain why did it keep getting stuck in loops involving Kiele.  

Zane was still mesmerised when a small rock hit him in the forehead.  He yelped in pain and looked up to see Kiele waiting for him.  He had no hard evidence that she had thrown the rock, but in all seriousness. there was no one else around.  A passer-by who had seen Kiele throw the stone commented on the situation and then walked between the couple, ``That's a real love/hate relationship ya got there.''  

Zane thought long and hard.  Really?  Did she actually like him?  His subconsciousness stepped in.  'Zane my boy, do stop thinking about this girl and get on with things.'  He walked towards her and the two of them continued down to the address which was written on the paper.

As they made their way down the street the door they were heading for became oddly apparent.  It was the only one in the small row of houses that had a different coloured door.  The houses were all two story and terraced.  There must have been around twenty houses in the same run, on both sides of the road.  There was little traffic here and around ten to fifteen children were playing in the street.  When the police car had rushed past, all the parents had poked their heads out of the windows and called them inside.  Now the drama was over, the little animals were once again let out of their cages, their parents glad of the rest.

Each house had a tiny garden, not more than thirty square foot or so.  Some had decided to pave the area, whilst others had replaced the original paving, from when the houses were first built, and had opted to replace it with small hydroponics labs.  In these they grew vegetables and herbs as it was far cheaper than buying them in the shops and plus the fact, you could be fairly certain of the source.  There had been instances of thugs injecting harmful substances into the bays, or even replacing the plants with drugs.  

It wasn't uncommon for dealers to find an unsuspecting elderly lady, break into her hydroponics bay, and have her cultivate and tend to their marijuana plants.  One lady had even caught a guy admiring her large stash of drugs.  Little did she know that these plants were actually illegal substances.  She also had no idea that the delightful young gentleman she was speaking to, was the one who had switched her prize young saplings for the naughty plants.

Each roof was the same grey colour, coated in solar panels.  The panels had been coated with a special laminate to ensure minimal reflection of sunlight.  In the early twenty first century, the various governments of the world had begun to fit solar panels to houses in an effort to rely less on fossil fuels.  As the number of them increased a very specific problem had been introduced.  Houses higher up on hills would reflect sunlight down onto roads in valleys, creating a serious driving hazard.  The accident rate increased dramatically until one manufacturer decided to incorporate a special anti-glare laminate into their designs to mitigate the issue.

The house they were headed for had no hydroponics bay, nor grass, nor concrete.  Outside this house was rubble.  Old bricks, some metal rods and a vast array of different coloured tarpaulin.  The garden, if it could be called such a thing, like every other house was fenced off with the same wooden fencing.  Two posts defined the three sides of the garden at the corners.  Most of the fences were painted black.  They were constructed of the typical vertical panels with pointed tops, alternating with white space to give at least some light into the garden.  The fence posts of this particular house had been eaten away by some kind of insect.  The tops of them were degraded in such a way that it made it look like a miniature landscape, raised high on a stalk.

Kiele and Zane reached the house and Zane gestured for the girl to go first.  It wasn't as if he was scared, she just seemed to take pleasure in taking the lead.  She walked up the two steps to the front door and looked to her left.  'Just who lived here?' she thought.  The front door was roughly in the centre of the garden as was the same with all the houses.  She looked back up at the door and found an old fashioned knocker.  It was a rare sight to see one of these around, especially in these parts of town.

She took a few seconds to study the device.  A jaguar's head and neck formed the base of the design, with the knocker being hinged at the far end of the neck.  It looked like it was made out of brass, but Kiele wasn't sure.  The eyes had been garnished with a single gem each, obviously not precious enough to be real stones, though Kiele could see some knife marks where eager thieves had tried to make themselves a quick bob or two.

``You pull it back, and then hit it against the door,'' Zane ventured.  He enjoyed ribbing her.  She breathed in deeply and closed her eyes, waiting for the annoyance to pass.  Who was she kidding, the 'annoyance' wasn't going anywhere.  She pulled back the jaguars head.  It was heavier than she had imagined and with definite purpose she thrust the head against the brass plate.  On the second knock, she noticed the pattern of previous knockings on the plate behind the head.  It had evidently been there for a great number of years.  The look of the houses suggested it may have been removed from a previous home, before being added to this one.  All the other houses had thumb-plates, but some people just loved to be different.

The door shook slightly with the weight of the jaguars head ploughing into it and the two of them waited for the jaguars call to arouse the occupant of the establishment.  A curtain to the right fluttered as the owner checked to see who was knocking.  After a few moments, the door was slowly opened and caught by a glittering sliver chain.  What was it with the old technology? thought Zane.  A withered face peered round the door.  The face belonged to an elderly lady, not too dissimilar from an auntie Zane had once visited.  She squinted before looking them up and down.

``You the two young oiks that Jolie sent?'' she asked in a raspy voice.  She had seemed approachable, even frail before she had opened her mouth.  Zane had put her age at around nine thousand mark, Kiele, a little more understanding, at around ninety.  Her face was wrinkled and her stance hunched.  

``We are two of her students, yes.'' came Kiele's polite reply.  Zane grinned a big beaming smile in the direction of the old lady.  People had often told him he had a look that could melt anyone's heart.  

``What are you grinning about, wise ass?'' she barked at Zane.  Whoever had commented on his smile had been lying.  He obviously hadn't melted the old lady's heart and the jury was still out on Kiele's.  Zane pulled his neck in and managed a brief little shake of his noggin.  The old lady closed the door to, and the students could hear the sound of cursing and a chain rattling.  She was quite probably having difficulty opening the door.

``Would you like a hand?'' Zane offered.  Stupid, stupid, stupid.  He was an A grade student, but even he had forgotten that he would need to be inside first in order to be able to help her.

``Oh thank you sweetheart,'' she hollered  from inside.  Zane and Kiele were both pleasantly surprised until she finished her sentence.  ``Why don't you just pick up one of those bricks from the front lawn and break one of my bloody windows, then you may be able to help out?''  Though the old lady was quite sure that Zane had enough intelligence not to even entertain the idea, she still found it necessary to add, ``Touch the bricks and I'll pop a pellet in your behind.''  'A gun carrying old coot,' Zane thought, 'great.'

Eventually the door opened fully and the old lady waved them both in, stopping only to place a key on a small vintage table in the hallway.  As she tottered off down towards what Kiele assumed was the kitchen, she shouted out, ``Would either of you two like a good old cup of real tea?''  

Zane began to answer no, but Kiele beat him to it.  ``Oh that would be lovely,'' she said.  For someone who may have had an interest in him, she sure enjoyed torturing him.

``Oh gee, thanks Kiele, how will I ever repay you?'' he mocked.

``I'll be back in a jiffy,'' the old lady called, ``do make yourselves at home.''

The two of them walked into what must have been the old lady's living room.  It was so vastly different to the outside of the house that Zane wondered if he'd been teleported somewhere else.  The room was square, about twelve foot in each direction, with a single door leading into it.  The room was adorned with the same whitewashed furniture that Zane had back at his hotel room.  It wasn't the most expensive furniture in the world, but it certainly wasn't the cheapest either.

Atop each item in the room were various trinkets, most sealed away in tiny display cases.  As Zane got closer he could see that almost all of them were either clocks or watches of some kind.  He bent down to take a closer look at one.  Not being in anyway informed about the vintage timepiece scene he had no idea it was a 2014 Rumchum Exo 4, with the rotating bezel.  Only 14 had ever been made.  This was the last surviving specimen, and to a collector, worth over \$12,000.  He extended an arm gingerly to rotate the case to get a better look.

``Look with your eyes lad, not with your hands,'' reeled off the old lady.  Kiele tittered.  It really wasn't turning into Zane's day.  The old dear had just appeared at the door with three cups of tea on a tray.  She set it down on a whitewashed coffee table in the middle of the room.  The tray seemed ancient, but then, apart from the furniture, everything in the house was; a real testimony to days gone by.  Everyone had, of course, seen items like this before but it was seeing them all together that was staggering.  Kiele supposed it was the most beautiful room she had ever seen.  Much more beautiful than her own house, her dad leaving tools and junk everywhere.  

The three of them sat down in silence.  It was somewhat awkward but then both the students were used to moments like this.  Kiele decided to break the ice.

``Excuse me ma'am, but we don't even know your name.''  It was a statement, not a question.  If she chose to take it as a question then she could, if she chose to acknowledge it as the true and leave it at that, then that was OK too.  Zane's ears pricked up at this moment.  He had been busy studying another of the ancient timepieces in the room, but he found himself wanting to know more about this strange old lady.  

``You can call me Kaitlin,'' she said, offering nothing more than a token.  It could have been her real name Kiele thought, but it most likely wasn't.  Zane went back to studying the watch.  He'd been told to look with his eyes, not with his hands so now, instinctively as he arose from the chair to gain a closer a look at this particular time piece, he put his hands behind his back, one hand gripping tightly on the others wrist.  

``Jolie took you down to the platform yesterday didn't she?'' asked Kaitlin.  

``Yes'' responded Zane simply, before adding, ``She's given us this awesome assignment on Oken Brown.  Have you heard of him?''  It wasn't a stupid question, but Zane figured that she must know something about the history of the platform.

``I have heard of him, yes'' she said.  ``I even knew him once.''  Her eyes turned to sadness before looking out of the window.  They glazed over, with all the indications of someone recalling a very precious memory.  ``But that was back when he was a little boy.  We had some fun together.''  She smiled and turned back to her guests.  

``You look incredibly familiar young lady,'' Kaitlin said.  ``Have we met before?''  Kiele looked across at Zane who gave her a weird confused face.  The young girl shook her head.

They sat there for a few more minutes, each party not wanting to disturb the others thoughts.  Zane had a million questions for Kaitlin, but decided out of respect to keep his mouth shut.  She shouldn't have to listen to his mindless banter, plus if she only knew him as a boy, it was unlikely that she could tell him anything too interesting.  Kiele too had questions, but of a different nature.  She was more interested in the origins of her fascinations with clocks and watches.  Kaitlin on the other hand, was just enjoying the company.  It wasn't often that she got visitors now.  She was too old.  

Kaitlin had been young too once; full of the joys of childhood.  How she wished she could bring back some of that feeling now.  She'd had her hip replaced a few years back.  It hadn't gone as well as she'd hoped.  The new surgical methods seemed to disagree with her old body.  'Leave them for the youngsters,' she had thought.

Three years later and she was still struggling to get up and down the stairs.  How she wished for a helper, but the government would never send one.  No, she would have to rely on help from neighbours and friends, but with a garden like that, no one ever came near her house.  Even the retro window cleaners skipped her place, unable to use their ladders and not thinking it profitable to use the d-scaff on such a small house.  Truth is, she would have paid them in gold, quite literally.

The three of them had all nearly finished their tea and Kaitlin supposed it was nearing time for them to leave.  Lately, she found it so hard to keep a conversation going.  Her mind seemed to run in its own circles, musing on the past, wishing she'd made changes, praying she could make a difference some day.  She was caught in a loop of dismay over her past actions.  She wasn't happy with many of the choices she'd made but after talking to some of her friends, it seemed many of them weren't either.

``I need to find the key,'' she announced finally.  ``Can't get in without a key.''  As she tried several times to get up unsuccessfully Zane moved over to her and offered a hand.  She smiled at him and grasped hold of his arm.  He wasn't a bad lad after all.  She walked slowly over to a chest of drawers and began systematically opening each one and rummaging through it.  Kiele and Zane both thought it a little odd that she had to 'find the key' when she'd obviously given it to Jolie the other day.  Maybe she was losing her memory.  

``Ahh.....found it,'' she said triumphantly.  Zane had returned to studying the watch.  It was an older model than the rest, mostly black, with hints of grey, it looked new, yet old at the same time.  A chronograph, it had one main dial, with three smaller ones round the outside.  It looked beautifully made.  The strap was a thick black leather, which seemed to offset the black of the bezel even more perfectly.  

Zane looked up at Kaitlin and she made her way over to him.  Zane was a little apprehensive.  Was he about to get another telling off?  Or was she actually going to hit him now?

``You like that one the best?'' she asked.

``Yes ma'am'' he replied.  He looked at it some more before his gaze was broken by Kaitlin removing the display case from his field of view.  She reached inside and took out the watch.  Turning it over a few times in her hand, she appeared to be deep in thought.  Then she then looked up at Zane.

``Put out your left hand,'' she commanded.  Zane obliged and the old lady placed the watch on his wrist, turning it over to do up the buckle.  It seemed weird that she had presented trouble opening the door, but seemed to have no difficulty in doing up a small watch buckle.  On second thoughts, with this many watches, she must have found a method that just worked for her.

``There you go,'' she said, ``take it.''  Zane's eyes widened.  

``Oh no, I couldn't''  He meant it too.  These watches and clocks seemed to be her life.  It would have felt like he was taking a part of her away with him.  Maybe that's what she wanted.

``All I ask in return is that whenever you tell the time, you think of me.''

As if by magic her mood changed, and she was once again tottering off towards the front door to let them out.  Kiele stood to her feet before mouthing the words 'say thank you' to her partner.  

``Thanks'' managed Zane.  He was in shock.

As the two students made it to the door, Kaitlin was waiting for them, key in hand.  She gave it over to Kiele, naturally.  Zane wasn't insulted.  As the two of them walked over the threshold to the warm day outside, Kaitlin cheered, ``Now, you two have a lovely day together.  Just post the key through the letterbox when you're done.  I'm going to have a sleep now.''  

Kiele smiled and nodded before uttering a thank you of her own.  Zane raised his hand in a wave and they both began walking away.  They were not ten feet from the door, when the cry came, ``and no drunken naked parties, I know what kids are like these days.''  Before either of them could reply, the door was slammed shut and they were once again alone together.  



