\chapter{02}
\section{Bethany}


Inside the bag, packed as tightly as it would allow, were various tools and weapons as well as some of the most advanced SupHum devices ever developed but Oken wasn't interested in these. It was the new additions that he was waiting to try out. He had packed four temporal shield generators; after all, what was the point in sporting the most advanced weapon ever made, if no one would remember its effects afterwards? He had also packed Bethany. That was the name he had decided to give to his ultimate weapon. He had always named his achievements, it came as second nature to him. He spent so much time tinkering and bringing them to life that to use them with some kind of personification just felt cold. In some ways they were his companions. He cared for them as he would his own child.

Once again, Oken began to feel rather hot and to his suprise, nervous. The full extent of his plan was beginning to sink in and perhaps, just perhaps, he was starting to rethink whether of not this was a good idea after all. He was about to use a weapon that was inherently banned globally, in a place that was totally illegal, against a fighter that was as yet unknown. He looked around the room. He knew everyone there. At some level he thought that that fact might trouble him. Knowing that he may have to kill one of those sat nearest to him should cause some kind of reaction he was sure. But it didn't. Oken mused further and settled on a simple justification for his lack of empathy. All the fighters were well aware of their potential fate, he thought and they all entered the Zone knowing full well what they were letting themselves in for. Of course the same didn't hold true for Oken, his initiation had been somewhat special but for everyone else they fought with full knowledge that every fight could be their last. It was how they lived. To his knowledge, none of these people had families of their own, it would be irresponsible if they did.

As Oken sat there in complete silence, half listening to the quiet banter that was going on around him, he tried to recall what Bethany looked like. She was very thin, sleek and her blade was made from a brushed metal which appeared to make her seem far more ornate than she was. Close to the grip the blade had a hole cut into it, into which a crystal looking object rested majestically. It offered a pale blue glow which was enough to light up a small room to some degree. The grip was made from a synthetic leather to allow Oken comfort in use, but also to protect the workings of the device from moisture, the innards were exceedingly sensitive.

Oken remembered the months he had spent in the library researching temporal mechanics and other related fields. He had spent so much time there in fact, that he was offered a job in the science reference section. He enjoyed his job there, helping people to find the information they needed for various projects and school work. The pay was far from adequate, but then Oken had no real need for it now anyway. The money from winning a Zone match was more than enough to pay for Oken's lifestyle. His occupation was more of a cover than anything else, allowing him to blend in with society and hide his secret underground connections. Many of the other fighters had cover jobs too. Skins was a pharmacist, Ruben was a antique clock dealer.

Outside the Chiller the crowd was growing impatient. There were rarely fights in the spectator stands but today was an exception. A man in a black t-shirt and blue baggy jeans decided that the guy standing next to him was annoying him more than he could possibly bare. He promptly punched the antagonist in the face which resulted in an eruption of cheering and shouting. The victim fought back with a swift uppercut to his opponent's chin knocking him to the floor with a soft thump. The shouting got louder and it wasn't long before Ruben was on the scene. His dumper truck sized fists clenched, ready to do his worst to retain peace inside the Zone. He picked the first man up off the floor and dragged him to a small room which acted as a detention cell. Anyone who caused trouble inside the Zone was locked inside one of these cells for the duration of the evening.

The man struggled and protested but Ruben had seen the whole thing and knew full well that the limp body of this kicking and screaming degenerate had been the mastermind behind the first punch. Ruben threw him into the cell and slammed the metal door shut. The clang was heard across the Zones platform and significant jeering filled erupted over the loud music and conversation. The bouncer opened the shutter located near the top of the door and shouted inside to the little man.

``Better learn to be a little nicer in future, hadn't you?'' Ruben too was an educated man who had been spotted by the Zone's creator six years ago and drafted in to 'beef' up their security. Since then Ruben had attended every meeting at the arena which occurred once a week. He was tired of these low life jerks, these deliquents who seemed to believe that they could do anything and get away with it. He walked over to the man who had been attacked. ``Nice punch,'' he said shaking the mans hand. The man nodded towards Ruben who slowly walked away a grin forming across his face. Nothing was going to spoil his mood. Oken had something special tonight. He just knew it.

Before the evening's so called entertainment started the platform was opened up to the spectators who used it as a dance floor. People from all walks of life visited the Zone and revelled in its atmosphere. The train tracks were terminated by brick walls at each end and large speaker stacks were situated above these. There were also large television screens lining the back wall opposite the platform itself. These showed various music videos and advertisements before fights, but during the matches, these were turned into gigantic action replay panels. The platform was littered with tiny radio controlled drones approaching the size of flies, ready and waiting to stream high definition footage of the fights back to the control room.

The control room was outfitted with an impressive array of technology. The Zone's owner had invested large sums of money, turning the Zone into a cover of its own. During the day, Neil Jones rented out the Zone as a recording studio for both music and television. He himself had recorded several albums here and was known in the underground music culture for his reasonable rates. The usual crew were lined up in their executive chairs, poised like flamingos in a row, waiting for the fights to begin. Neil shouted at one of the crew members who had begun to mess around with one of the drone cams, following various members of the crowd through the platform.

Five ash trays adorned the control desk, innocently sitting there waiting to catch the fruits of their owners bad habit. Almost all of the control team smoked. All but one. Darren sat in the corner with a bandanna covering his mouth, coughing occasionally in a display of protest at his disgust of the other crew member's appalling vice. They all knew he didn't like it but they couldn't help a life long addiction. Though uncomfortable at times, Darren was getting used to the smell.

The first match was a newbie bout. Two young recruits had been drafted in, probably frequent visitors hoping to make the transition from spectator to participant. They were now making their way to the platform, dazed, scared and confused. Bouncers and ring organisers began ushering people off of the platform and up into the spectator stands ready for the start of the first match. Oken was busy talking to the Neil, asking him if he could place these new high resolution cameras in each corner of the platform. He was of course referring to the temporal shields which he required to be placed at specific points around the arena, in order to cover the entire spectator and platform areas. Oken was unsure of what the Neil's reaction would be to him using a temporal weapon in his arena. He decided it would be best to leave it till the end of the show and explain it in full later, if the questions arose. Most people would simply see what Oken wanted them to see, a spectacular show, he doubted anyone would know that he was sporting a temporal weapon.

Oken moved to each corner of the large platform, carefully removing the shield generators from his bag, placing them on the floor, and hooking them up to the Zone's power supply as he went. This involved opening small access panels in the walls and rerouting power from other areas of the Zone. Neil had given him an allowance for the evening and he dearly hoped that the conduits would be able to provide enough juice. Temporal technology was power hungry, real hungry. His own electricity bill for the last few months had been through the roof. It had been so high in fact, that he had been concerned that an inquisitive G-TEP official may visit his residence to see just where all the power was going, but given the amount of air conditioning that certain residents of the block used, he was reasonably confident that it would mask his own usage.

He finished setting up the last generator and dutifully tested their operation with the remote control device. Their lights turned from red to green and back indicating that they were fully working. Oken opened the control device's top to check the small illuminated display which lay inside. All of the shields were working within normal parameters. Phase one was complete. Now he just had to wait until it was his turn.

The first fight ended fairly abruptly with one of the contenders giving up after acquiring a bleeding nose. The jeers and the shouting was tremendous and for an instant, Oken actually felt sorry for the poor young soul who had had his hopes of becoming a Zone master crushed at the first hurdle. The blood trickled down the poor boy's face and Oken was sure he could also see tears, glistening with the red stuff as it descended. The drips of blood collected on the floor and were trodden in as the participants went to leave the arena. One of the bouncers handed him a towel and told him to get into the spectator crowds or get out. The boy rejoined the spectators, hoping to gain another glimpse of the awesome power that he himself had hoped to harness. There would not be a next time. Vacariousness was his only option now.

The second fight was a lot more interesting. Both competitors were sporting SupHum devices, which they were really using to full effect. One of the fighters, a Chinese man in his early twenties, had configured a device to double his own body weight, with no ill effects on his own performance. His punches and kicks were so powerful that he had been warned to steer clear of the pillars, even with their steel reinforcement. The other competitor, a local guy, had configured his device to lower his local gravity to just under half the normal level. His agility and speed were incredible.

The two competitors stood facing each other across the platform and Oken was reminded of how he had felt the first time he had experienced the same thing. It had been scary, but anticipation had won him over in the end. The music began and the crowds flared. The two tigers roared at each other and began swinging. The Chinese fighter was raining blows down on his opponent, who seemed to be taking them with a pinch of salt. The density enhancer had failed, the poor guy was fighting with just his usual body mass. The local boy fought back and both of them exchanged numerous Kung-Fu style blows and punches. The fight was well into two minutes already. Not bad, thought Oken.

With the music blaring and the crowds shouting, Oken found it hard to concentrate on the two warriors fighting for dignity and their very lives below. He was now standing at the front of the spectator box, taking in all that lay below him. He knew the landscape well, that much was obvious, but it took more than that to win a fight and from his brief analysis, the Chinese competitor definitely had what it took. Even though he was at a significant disadvantage, he was still very much in command of the brawl. He was the one who was definitely calling the shots. The local boy was constantly in defence and was having problems keeping up even with his device running at full tilt.

With one final blow the Chinese fighter sent his opponent sprawling to the floor. Jimmy the local lad couldn't get up; it was time to finish it. With a quick kick to the head it was all over. The crack of the young boy's neck sent a shudder down Oken's spine, that felt somehow ironic. He assumed he would have been used to that by now.

Though Oken had not really seen any need to kill the boy, dealing a killing blow was always the victor's choice. Oken felt a glimmer of pride that he had never stooped that low. If he had killed his opponent, it had always been in the thick of the fight, never when it was clear that they had already lost. To him, that wasn't fighting, that wasn't honourable, that was just murder. His justification sat well with him.

Two bouncers went into the ring and dragged the body of the boy off for immediate disposal. It was vital bodies were disposed of quickly and effortlessly less any incriminating evidence find its way to the government. The Zone's patrons had no idea how this part of the operation ran. No one questioned where the victims of the their insatiable appetite for destruction were buried. No one cared. Once a fight was over, the loser was to totally forgotten. Oken guessed most spectators assumed he would be dumped in a park somewhere and that it would be dismissed as a drunken brawl by the authorities.

Oken returned to the Chiller. He sat down and poured another small glass of port. He sat back into the chair and put his feet up on the glass table in the centre. It wasn't a big room by any stretch of the imagination. Adorning the walls were posters of previous death blows and doctor's certificates detailing various chilling injuries. Hanging from the ceiling was a chandelier style light fixture. Oken watched the pattern the light made on the white painted ceiling as the chandelier swung gently back and forth, moved by the air from the ventilation system. The refraction fascinated him and he became fixated by the hundreds of tiny rainbows that danced across the wall.

The door swung open and the Chinese fellow entered victoriously, hands held high in the air by fellow fighters pushing him on. He picked up a bottle of beer from the table and began to hurriedly drink it down. Oken took little notice of the panting animal and instead turned his attention to one of the weekly newsletters lying on the table. The e-paper changed to show the face of the Chinese man who had just entered and the story appeared below. 'Huang hangs local star,' read the headline. Oken gathered that the young man's name must be Huang. He was a new fighter, not one that Oken had seen before. To him he just seemed to be another young hopeful who would soon be sipping his mid-morning milk through his nose, just like all of the other young kids who became too proud too fast.

The door opened again and Ruben poked his head round. Oken had always found it mildly amusing at the amount of light that was reflected by Ruben's bald head. Today was no exception and he almost felt like shielding his eyes in jest, but he decided to cut Ruben a little slack. Experience told him that Ruben did not always take kindly to jokes about his appearance.

``You're on next Oken my man,'' said Ruben as he looked around the room at the other fighters. Their discussions had become quieter as Huang rested. The bald man clicked his fingers and pointed at Oken. ``Make it a good one,'' he said, ``I took the night off for you.''

``I'll do my best Ruben,'' said Oken, though deep down he already knew the fight would be utterly spectacular. His confidence in this fact was brimming over. Though he had tested some of the weapons abilities, he had no idea what would be the result of killing someone with a temporal weapon. The theory was way out there and he had not had time to investigate it further. Would there be a shower of sparks, a ray of light, a big explosion? He knew not, but he had heard stories of the consequences of temporal expunging in the many temporal mechanics books he had read and the wintesses had always been left dumbfounded.

Though temporal weapons were abhorrent creations, banned and restricted the world over, the general public had some knowledge of their existance. They did not however have any real knowledge of what these devices could actually do. The G-TEP was a terrifying force, definitely not one to be challenged. Yet the thrill of developing something so dangerous, so sought after, was what had driven Oken from the beginning.

The G-TEP employed temporal shielding at their HQ, they could see echoes of temporal events a few days, sometimes even weeks before they would occur. It gave them time to prepare, and if luck was in their favour, to stop the event from taking place. The investigation began with an impact analysis, this step was mandatory, then the G-TEP forces would try to predict what the eventual outcome would be, taking into account whatever evidence they had at the time. After that would come the strike team, a highly trained ruthless team of individuals fighting for the greater good. At least that was the excuse for their brutality.

Throughout the development of his masterpiece, Oken had discovered that not only could he obliterate things from existence with the technology, but that he could also affect the flow of time. He was able to slow time down to a tenth of its normal speed, with his own body remaining unaffected. He had built this technology into Bethany also. To activate it, he just had to squeeze on the grip and she would do the rest. The harder he squeezed, the slower time passed. It took tremendous amounts of power to keep the temporal fields stretched and though Oken had never run them for more than a few seconds, he knew the power source in the hilt of Bethany wouldn't hold out for long. It was also unstable, highly unstable and pulling too much juice from it at once was a one way ticket to a bad place, a very bad place.

Bethany's master picked up his holdall and grinned at how light it seemed now that the four shield generators had been removed. He took one last look around the room and walked out, shutting the door to the Chiller behind him. Unbeknownst to him, the other fighters in the Chiller were all lining up ready to take up their positions in the spectator stands to watch what was rumoured to be the most important and monumental fight in the Zone's history. Ruben had to be thanked for that. He could spread a rumour quicker than a rash.

Oken walked down the stairs to the platform below. He noticed how cold and clinical the place felt. The stairs were constructed from solid concrete and he could see the light from the platform below billowing up the stairwell in a sort of cosmic mist. He continued to walk slowly down, checking his watch at the last step, 8:05pm. With any luck he'd be home before 10:00pm.

The crowds were jumping still and Oken was amazed at how much energy they seemed to possess. Many of them were drug takers, fuelled by an obsession which would eventually kill them. He had never taken drugs. He had never seen the point, the effect only lasted a short time, and take the wrong combination and you'd be dead. He drank a little alcohol, but nothing that would affect his performance; just a little to settle the nerves.

His opponent was making his way down the opposite stairwell. Oken knew him; Yaz. Yaz was famed for his technology and his speed. Oken found it fitting that they had been pitted against each other in what was a sincere clash of two titans. He hoped that his time-bending would teach Yaz a brief lesson, that speed wasn't everything. He walked to the graffitied star painted on the ground and then looked up. It seemed as if at that moment both of them transitioned from preparation to absolute readiness. The music thudded a dull beat that Oken found incessantly boring. Thump, thump, thump. He felt as if his head were about to explode.

Oken recovered the remote control from his pocket and activated the four temporal shields. Their lights changed from red to green. All systems go, he thought. He opened the black holdall and removed Bethany, still in her scabbard. As he slid her out of her shell, he could hear the metal scraping against the inside of the sheath, setting his teeth on edge as it did so. He was holding the sword out in front of him and he could see Yaz with his staff, performing complex patterns of twists and twirls. Oken pulled the tip of the katana from the scabbard with a delicate finesse. He held her in his hands knowing that soon he would be able to test her in her native environment; the battlefield. The scabbard he was now placing on the floor was of an ancient Japanese design. Oken had designed Bethany specifically to fit inside. He hadn't made the scabbard. As luck would have it, three days before beginning construction on the blade, he had found the sheath in a charity shop in the commercial district.

He now stood facing his opponent and Oken joined in the ritualistic twisting and twirling of weapons, first left then right, each time seemingly getting closer and closer to his own body, faster and faster until a blur was all that could be seen. As he swung Bethany through the air she made a gentle screech that Oken was sure he could hear even above that incessant thumping and with each cycle of movement he became increasingly lost in his own thoughts. His swordplay did not go unnoticed and the crowd started to point at Oken. They had noticed that he was sporting a new weapon and were ravenous to see the results. One smaller member of the congregation looked up and tugged at Ruben's shirt excitedly.

``Hey man,'' said the spectator, ``what's he got there?''

Ruben chuckled to himself and turned to speak to the excited fan. ``Your guess is as good as mine brother,'' he replied. The rest of the crowd were shouting and exchanging their own hypotheses as to what Oken had brought with him. This was what Oken enjoyed most. The excitement at the mystery he brought. Their electric anticipation. It was an art form that he had realised a long time ago. Almost all of the devoted fighters could create weapons, but only a few knew what the crowd really wanted and were able to use that knowledge to create masterpieces. Bethany was one such masterpiece.

No one could determine the class of Okens weapon. Many had suggested it could be some kind of gunblade, perhaps some kind of energy weapon. Whatever it was they were sure of one thing, despite its magestic appearance, the weapon carried a sting in its tail. Through all the speculation, none of them even came close to the truth. The crowd were becoming impatient and a few began to rhythmically bang their hands against the toughened glass, hoping to start a noise loud enough to catch Oken's attention.

As the temporal master was performing yet another twirl, he gripped the handle tightly and watched as time slowed to a snails pace. Everything grew dimmer, this was an effect Oken had not predicted, it was a gradual dulling of the worlds colour which also brought with it a sensation of desaturation which he wasn't sure was due to the world or his own eyes. He looked around at the crowds jumping in slow motion, their clothes caught in a viscous ether. He saw Yaz still twirling and spotted the anger on his face or was it concentration, it was hard to tell. He saw a man's drink being knocked out of his hand and the liquid glistening in the harsh lighting. Then he looked back across the platform and noticed the water dripping from the ceiling again as it had done three years ago when that fateful first fight had occured.

He watched one drop fall from above and followed it with his eyes till it reached the ground. He released his grip on the handle and time quickly returned to normal with a slow whoosh. He hadn't noticed the music slow down, but as the flow of time resumed, the tempo increase seemed insanely fast. The crowd went wild.

In the control room, the crew member who had been disciplined earlier for playing around with the cameras was given another lecture about not fiddling with the cameras operating speeds. The poor man protested that he had nothing to do with it, but the producer yelled back all the louder.

``You play with those damn cameras one more time sonny, and I'll stick 'em down ya throat,''

Jacobs knew when it was time to keep quiet and this was one of those times. He considered him self a hard working technician and had been attending the Zone for going on five years now. It didn't seem worth blowing it all on a silly little argument. Jacobs needed the money, he daughter was growing up fast and he was damned if he was going to let her make the same mistakes he did. No, she was going to college, he had decided, and to do that needed money, money that came from the Zone. Once a week he went out for a 'lads night out' and once a week he ended up here trying to find the most artistic way of portraying such brutality.

The time was fast approaching for the beginning of the battle. The music had thinned to a modulated bass line which seemed to cut through the ears, before the modulation vanished and the muted tones took over, thudding in anticipation. Oken knew that in a minute or so, Neil would yell 'go' and they'd be off, like horses leaving the gates at the races. It wasn't often that Neil took the opportunity to start the bouts, but tonight he was here in spades. The manager made his way to the microphone. Blinkers on, thought Oken, it's game time.

Oken decided to try one more little experiment. He gripped the handle tightly and once again felt time begin to slow. The lights went down, and the music began to crawl. He walked over to the water that was still dripping and sliced a single drop in half with ease. He watched as the drop split into two globules, and then he performed another slice, managing to cut both the droplets in half again. At these speeds, it could be accomplished by anyone, it was hardly a challenge, but getting to these speeds, something seemingly so unobtainable, this was where the diffuculty came in and Oken felt proud of his achievement. He returned to his starting position and released his grip. The crowd roared. In their eyes, Oken had just become immortal. This was something the likes of which they had never seen before in their lives.

Yaz, disappointed at losing the crowds attention, twirled his staff even faster in a desperate attempt to win back their admiration, but he could do nothing to turn their attention away from the grey haired figure standing not twenty metres from him. Oken turned to face the crowds and held up his sword with both hands high above his head. The crowd cheered all the louder. The man standing next to Ruben went mental and was shouting manically ``You the man Oken! You the man!'' at the top of his voice.

Yaz stopped twirling and shouted across at Oken,

``Fancy trick Oken, but aren't you a little old to be playing these games.'' Yaz chuckled to himself. He spotted an empty beer glass standing in front of him to the left. He gingerly put the end of his staff into the neck of the bottle and with one fluid motion flung it towards Oken's head. His aim was impecible and had Oken not seen it coming, he would have been knocked out for sure. Yaz was exceedingly fast, very strong and his reflexes were nothing to be sniffed at.

Oken watched the bottle coming towards him and gripped on the handle of Bethany. His cautious side berrated him for using yet more of Bethany's limited power supply on a parlour trick but he didn't care. The all too familiar whoosh rang in his ears, like the striking of a gong, and once again he entered the realm of treacle. The glass was still in mid air, slowly making its way towards him in a graceful dance. Oken swung the blade at just the right moment and sliced the glass clean from rim to base, right down the middle and as he released the grip he twisted the blade slightly and saw the two halves fly past and shatter as they hit the wall behind him. Oken looked down at the sword which was now stock still in front of him and the child inside him screamed, 'This is a cool toy.'

In the control room the producer was shouting. ``Did you get that? Tell me you got that.'' The shot was replayed on the big screens and for once Oken allowed himself a quick glance. It had been captured in super slow motion, half the speed of Oken's own new dimension. It looked even more spectacular on screen than Oken could have imagined. His body moved with a majestic stillness whilst the whole room seemed to have stopped. He could see the gaze of his fans watching him in the screens, their expression etched onto their faces like the screen burn for an old cathode ray tube.

Yaz now looked more than a little worried. Oken's superiority was now very evident and Yaz had no doubt that victory belonged to Oken. The staff bearer had never seen or heard of a weapon that could do what Oken was doing right now. He wondered if Oken would take the opportunity that had been given him, whether this fight would be his last. A pang of sadness hit him. How could Okwn not take it. The chance to perhaps put on the greatest show in the Zone's history. He should feel honoured.

To the crowds, it seemed as if Oken would suddenly slip into some kind of hyperactive spasm, almost as if he travelled halfway between the universe and somewhere else. A few of the journalists were trying to get reactions from the crowds, most were lost for words. Occasionally a word was uttered; Amazing, Awesome, Sweet. Had Oken been there he would have probably been a little disappointed at the adjectives being used to describe his life long achievement. The journalists would definitely need to add some embellishment.

Oken's heart was beating fast and not only fast, but hard. His chest cavity took a battering from the muscle inside, frantically trying to supply Oken. The man wanted to experiment more, but knew that the time had come to start the fight. Yaz's heart was beating fast too. He knew that this would probably be the end of his career and his life. The fighter now regretted requesting this fight against Oken. How foolish of him to underestimate Oken. His hands were sweating and as he performed one of his many twirls and twists his concentration waned and the staff left his sweaty palms.

As it fell to the floor, it bounced from end to end, making a racket that would have echoed for an eternity around the stone platform had it not been for the volume of the music which was still playing, drowning out the noise and softening Yaz's humility. Oken could hear the instruments building up and up. He looked down at his shoes and closed his eyes. It was getting there. His time was coming. He took a deep breath, looked up and opened his eyes. In the milliseconds that it took for his eyes to focus, he saw the manager open his mouth and scream one word down the microphone.

Already Oken knew what the word was going to be, but the loudspeakers didn't. The signal travelled from the microphone and along the copper wires at an almost infinite speed, through the mixing console, through the amplifier and onto the loudspeakers' cones. It pushed the cone in and out in, bursting the air as it did so, screaming the word every single person on the platform wanted to hear, every single person but one.

``GO!''
