\chapter{17}
\section{}
Visitors  

The ambulance was heading towards the hospital really fast now, zipping through the traffic like it were hot butter.  The rhythmic beeping of the monitor made her nervous.  She was still shaking as she pulled out her phone.  One of the paramedics turned round and noticed her using it.  ``Ma'am please,'' he said, ``not in here.  It can have adverse effects on the equipment.''  It didn't even matter, she couldn't have worked the buttons even if she had wanted to.  She just sat there.  A part of her wanting to hold his hand, part of her wanting to climb out.  She knew what she had to do but the situation didn't make it easy.  She felt sick to the stomach.  

The monitor continued beeping slowly, tortuously.  Kiele had always hated those things.  It always seemed like a constant waiting game.  Like measuring whether a person lived or died by the distance of the gaps between the beeps.  The silence was agonising.  Beep........Beep..........Beep.  In this case the silence wasn't really silence at all.  It was filled with the noise of the engine, the radio chatter, clanking of various items in cupboards which adorned the ambulance.  In fact, now that she came to think about it, she had to strain to hear the beeps clearly.

She looked at the young man laying motionless on the gurney.  He looked so peaceful, yet Kiele couldn't imagine the amount of pain his body must be in.  The drugs appeared to be doing their job well.  He was stable, the beeps had just the right amount of silence between them.  There was a fair amount of blood on his clothes.  The focus of her mind shifted.  Why had he done that?  Why had he saved her?  She wasn't worth saving.  Not after what she had done.

One of the paramedics looked back at her.  ``You doin' OK?'' he asked.  Of course he knew the real answer, but he just wanted to hear her speak.  She nodded to him and let out a small but audible 'yes'.  The radio chattered and interrupted their brief conversation.

``Accident on 6th avenue, you'll have to go around it Jim.''  Jim acknowledged the information and instructed the driver to turn left at the next available opportunity.  'Just their luck', thought Kiele.  It was at this moment that the constant beeping suddenly became less constant.  The bright trace of the monitor was bobbing up and down fast now.  Kiele shouted to Jim.  It was a single word, but one which Jim knew only too well.  'Help'.

With blistering speed, Jim was in the back of the vehicle.  It had seemed almost as if a monkey had swung back there.  As the ambulance turned corners sharply, Jim was holding on to whatever he could find as he scrambled to obtain the correct gear to try resuscitating Zane.  It was only now that Kiele realised how lucky she had been.  A slight bump to the head which had knocked her out was nothing compared to the trauma of Zane's injuries.  

Jim grabbed the defib kit from one of the cupboards and ripped apart Zane's shirt.  He had been wearing a simple cotton design, with bright embossing down one side.  It wasn't his favourite but then, he hadn't expected to be joined by company.  He also hadn't expected to be in the back of an ambulance receiving serious medical attention.  Jim twisted apart the two magnetically held pieces of the defib kit.  Like most things these days they were as small as possible.  Joined by a small thread of retractable cable,  Jim pulled them further apart until he could reach the parts of Zane's chest he needed.

Kiele was beginning to get worried now.  What if he didn't make it?  What if he died saving her?  Why was her father so insistent on her meeting him?  Jim shouted 'clear', even though there was no one around to stand clear apart from himself.  Truth be told it was probably either protocol or force of habit.  The jolt from the DFK was enough to send Zane's body a good half foot into the air.  Still the monitor let out a single beep as the ambulance literally raced against time to deliver Zane into more expert hands.  

Kiele started to cry.  She didn't know quite why.  The emotions had gotten too much for her.  She was being pulled in two directions at once.  It wasn't fair.  The tears started running down her cheeks leaving two parallel wet lines down her face.  When the tears reached the edge of her chin, they left her skin and landed on her lap, dampening the material.

``Clear,'' shouted Jim as he tried again.  Still nothing.  ``Damn it Marty, we need to get him there now.''  Marty put his foot down a little harder on the accelerator and the ambulance lurched forward.  The siren blaring outside made it almost impossible to hear what was going on inside.  Kiele couldn't even remember it being switched on, yet there it was screaming louder than ever.  The monitor too continued to scream.  

``Don't go now,'' Kiele started whispering, ``Please don't go now.''  She repeated her phrase over and over.  It became a chant and through tearful eyes she reached out to grab onto his hand.  She wasn't more than a foot away when the word 'clear' brought her back to her senses.  She withdrew her hand and made it into a tight fist.  The tears started streaming again, the monitor still sang and the siren wailed in chorus.



\thoughtbreak



He awoke in a very clean room.  The curtains seemed to be the only thing that wasn't white.  Instead they were a pale shade of grey.  He tried to sit up, but couldn't find the energy.  It felt like someone was sitting on his chest.  Why couldn't he move?  Out of the corner of his eye, he spotted someone walking past a window of the room he was in.  Where was he?  More to the point, where was Kiele?

The curtains fluttered in the breeze and the person now identified as a woman in a nurse's uniform walked on by without looking into the room.  He tried desperately to shout out but he couldn't seem to make any sound.  What was wrong with him?

A vase was sitting on the table to his left, once again white in colour, but filled with a beautiful array of flowers.  Some red, some blue, some yellow, they reflected the light from the overhead strips to decorate the walls with a subtle hint of colour.  The water in the vase was almost gone now, sucked up by the hungry plants.  The glass was semi transparent with a geometric motif.  Someone had been a little careless in watering the flowers last time as a few drops of water could be seen sitting on the top of the surface, begging to be absorbed by the atmosphere.

Zane looked down at his hands.  There were still there.  His legs also.  That was a relief.  The bed he was laying on was composed primarily of polycarbonate with a few pieces of metal thrown in for good measure.  The mattress was less than comfortable, but perfectly adequate for his needs.  Come to think of it, what were his needs?  Why was he here?  Zane remembered the accident with all the detail of a child's first crayon drawing.  He remembered a train.  That's it there was a train......some graffiti....and a loud noise........and Kiele.  Where was Kiele?

Again he tried to call out and this time made a real noise.  It was a muffled shout, the kind a person makes when having a nightmare when they are sound asleep.  The room seemed so quiet and cold.  He just wished there was someone else there.  A doctor walked by the window, but again Zane was unable to get his attention.  The worst part was that his foot had started to itch and he had no idea how he was going to get to it.

A nurse entered the room and seeing Zane awake quickly exited the room again before Zane could grab her attention.  She had faintly reminded him of Kiele.  Same build, but not as beautiful.  When she returned, doctor in tow, Zane was ready.  He tried to speak, but the words wouldn't come out.  Just grunts and squeaks.  The doctor could obviously sense the frustration on his face, the nurse too, as she moved closer, put a hand on his shoulder and told him it would be all right.  

Zane managed to move his arms and with his left he grabbed the doctor's bicep and pulled him close.  He tried just to utter one word, 'Kiele'.  He desperately wanted to hear she was OK.  The doctor almost seemed to know what he was trying to say as he turned to the nurse and muttered something about him 'doing it again'.  It was then Zane saw the pad and paper on his left on the table.  He reached out and managed to grab both, knocking a box of tissues onto the floor as he did so.

The pad, a cheap one from the hospital shop, seemed heavy in his hands.  He rested it on his legs, which were stretched out in front of him and held the pen, crayon style.  He traced the words of his protectee, K..I..E..L..E.  As soon as he finished he pointed to the word and widened his eyes before looking at the doctor.  He managed to nod feverishly as if asking the question by nodding Morse code.

The doctor sighed.  ``We've explained this to you before Zane,'' he started, ``and it pains me every time I have to break it to you.''  Zane started to panic, what did he mean?  His hands started involuntarily making fists and then relaxing several times per second.  He was shaking a little.  He lifted his finger and pointed once again at the word, the name of the girl he had suddenly felt so much for.  The doctor was taking too long.  What was going on?  Where was Kiele?

``I regret to inform you, that Kiele never made it to the hospital alive.  The ambulance that you were in crashed and she died at the scene.''  Zane shook his head and started trying to speak once more.  He started managing to say the word 'no'.  His head still shaking, he tore the top piece of paper from the pad.  The fibres released from the tearing settled gently on his bed.  He very carefully wrote on the pad, C...H...E...C...K.........A...G...A...I...N.

The doctor's face was one of plain sadness and the nurse had turned away from Zane.  Her hands now back by her side, she walked around to the other side of Zane and picked up the box of tissues, before taking one out and using it for herself.  He looked up at the doctor and pointed to his words once more.  The man of medicine looked distraught.  It seemed this poor lad was suffering from acute memory loss.  This was the forth time he had given him the news that the female he had been found with was in fact dead.  It got harder and harder each time, but Zane was always so insistent, they could never calm him down before he asked the question.

``There is no point checking again,'' he said bluntly.  ``She's gone.''  A tear rolled down his cheek and at this point Zane seemed to recover some use of his speech.

``How....what.....happened?'' he asked.  The doctor, who was genuinely surprised to be hearing him speak for the first time pulled up a chair from across the room.  This was the first time they had been able to talk since he had arrived.

``Some drunk driver in an ESUV pulled out in front of the ambulance.  It hit it and crashed.  I'm sorry Zane''

The cripple lay there completely dumbfounded.  He had sworn to himself to protect her, with his entire being.  Now she was dead.  He had......loved her.  The words rang inside his head.  He hadn't wanted to admit it before but now seemed like the only good time.  He had loved her so dearly.  Though they had only really known each other a short time, he had desperately wanted to get to know her better.  Why was life so hard?  Why didn't he have the power to save her?  He was weak.  A stupid weak cripple of a man.  

Zane's anger grew.  He thumped the bed, taking both the nurse and the doctor by surprise.  He thumped again and again.  The doctor tried in vain to restrain his arm, fearing the boy would do himself more harm than good.  Zane shot him a death glance.  'Leave me alone,' he thought.  He stopped thumping anyhow and just lay there.  

After a few minutes the doctor asked him, ``Do you feel up to a few visitors?'' The boy sat there in silence, ``I know we have some of your family here.''  Zane was confused, the only family he knew of in the local area was one auntie, a sister of his mother, but she wouldn't have come to visit him, she hated him.  According to her, he had caused his parents death.  Zane's confusion was borne out on his face, but he nodded all the same.  

The beeping monitor had increased its rhythm slightly in Zane's anger.  The doctor arose from his chair, mutter something to the nurse and then left the room, mentioning something about going to get his visitors.  Zane looked at the young nurse, the resemblance to Kiele was becoming more apparent now.  She could have been her sister, still definitely not Kiele, but reminding him of her nonetheless.  Poking at his memories, angering the remnants.

The nurse offered him some water which he was able to drink successfully, the cool liquid killing the flames in his throat.  The water hadn't been sparkling, but the millions of tiny bubbles on the side of the glass had suggested so.  He gave the glass back to the nurse who placed it on the white side cabinet.

Zane looked out towards the window.  It was definitely starting to get dark now.  The late evening sun streamed in through the window.  Had he really been there all day?  It had seemed like he had only just woken up, yet the doctor had alluded to the fact that he had been awake before, and heard the news about Kiele before.  Not true.  He would have remembered.  Thinking back, he found it hard to recall the exact events of the accident.  He remembered throwing himself at her.  He also recalled having to fight the urge to hold on to her instead of pushing her away.  That had been difficult.  He would have been quite happy if he had died in her place.  She deserved to live on.  He had quite obviously failed in his task.

Three figures were walking down the corridor towards Zane's door now.  He recognised one immediately, the doctor from before.  The other two looked familiar.  One was a man, tall and dressed in smart trousers and a shirt.  His hair was black with hints of grey.  The other, a woman, her dark brown hair bouncing around her shoulders.  The doctor seemed to be explaining something to them as they rounded the corner.  

Zane couldn't see their faces until they appeared at the doorway, and when they did he lost all comprehension.  Mum........Dad.........how?  It didn't make sense.  They were dead.  He couldn't understand.  People who were supposed to be dead, now weren't and people who were supposed to be alive had died.  

The woman, his mother, ran over to him and hugged him tightly.  It didn't hurt as much as Zane had imagined it would.  As she released him, his father did much the same, holding his son in love.  They didn't speak yet, just looked at him.  Their eyes looked happy thought Zane, as did their faces.  They were pleased.  Zane was happy.  For a second he had forgotten all about Kiele.  His parents were alive, and they were happy.

``We're so proud of you son,'' said his father.  Zane smiled.  ``You will do great things, but you must fight him first.''  His face looked confused.  Zane didn't understand.  He looked at his mother, who was standing beside her husband.  ``We love you,'' she said.  He turned to look at the nurse who was now sitting by his side.  He had been unaware of the fact that she had also taken his hand into hers.  As he looked closer she appeared to have changed a little.  He peered at her, confused at what seemed to be taking place.

The nurse, who was now identical to Kiele looked up and smiled at him.  Zane gasped and jolted in shock.  She was alive.  Kiele was alive.  Tears were running down her cheeks but she was alive.  Was that why they were proud of him?  Had he actually saved her?  Maybe they were playing a prank on him?  That had to be it.  She had been there all along, silly Kiele, always making jokes, always teasing him.

He looked back at where his parents were standing, but they appeared to have gone.  Vanished into thin air.  He blinked, but they were most definitely gone.  It was then that he noticed the coffins raised up off the floor, two of them to be exact.  In one lay his father, and in the other his mother.  Exactly as they had looked not a few minutes ago.  

This wasn't real he finally concluded.  No one could die and be placed in a coffin that quickly.  Could they?  But what had they meant when they had said he should fight him?  He looked back at Kiele who was still holding his hand.  It felt warm and oozed confidence.  With her there, he could fight anyone, anything.  He was strong.  He could take it.  His mind became confident.  Bring it on.  

As he turned back to see the coffins one more time, he noticed that the flowers in the vase had all died.  It was more apparent to him than the fact that the whitewashed furniture was now blacker than the ace of spades, or that the sun had exploded in the sky, or that Kiele was now wearing an outfit fit for a funeral.  The petals of the once vibrant flowers now lay strewn across the black surface.  The coffins were no longer there, but a figure stood in their place.  It was the doctor, no longer wearing a white coat, but now drenched in black.

He took a step towards Zane.  ``It's for your own good'' he said, as he took a jet black pillow and placed it over Zane's face.  At first it felt funny, like when Zane would play fight with friends when he was younger.  It didn't feel at all like death creeping up on him.  He started to get a little anxious, the doctor obviously wasn't playing games with him.  This was serious.  He was still holding onto Kiele's hand.  The monitor in the room had started beeping incessantly and it was hurting his head.

He began to writhe in pain.  The pillow was completely blocking his oxygen supply.  His energy was zapped, but he could feel power flowing from his hand; from Kiele's hand.  He grabbed it tighter, to ensure that he could make it out the other side, wherever that may be.  The pillow was crushing now, and Zane could see nothing else but blackness.  Suddenly there was a blinding pain through his heart.  

He screamed out.  This was hell.  Hell in a dream.  Maybe it wasn't a dream so much any more.  The beeping had been replaced by a single tone that cut through him like butter.  He could hear Kiele, still holding onto his hand, crying.  

``No Kiele, be strong,'' he said, his words muffled by the devil's pillow.  The bag of feathers was crushing now.  Its texture replaced by that of a large slab of concrete, cold, crushing and complex.  This couldn't be how it ended.  He fought back, pushing himself up, all the while holding on to her hand.  She was giving him strength.  He could feel it pulsing through his veins.  Another shock to his heart.  The devil was really trying to pull him down now, but he had other ideas.  It hurt so damn much.  

With one last push he let go of Kiele's hand and slammed them down onto the bed, pushing upwards, inching upwards.  Slowly, little by little, like playing a tug of war to the death.  If he fell backwards, he died.  If he made it upwards he lived.  He pushed back again, the monitors song still shrieking strongly and ringing in his ears.  Then her hand touched him again.  

He felt a pulse of pure energy through his heart.  Not like last time, this time it was different.  With one last push his face burned through the pillow.  The concrete turned back into pillow again before melting into something even softer, marshmallow perhaps.  The colour changed also, from a black to a brilliant white.  He continued pushing, but it had become easier now, almost as if he needn't bother any more.  

He was pulled upwards towards brightness, still lying down, his hands falling beneath him.  The monitors scream was getting fainter now as he shot upwards.  He wasn't holding Kiele's hand any more, however it hadn't been as if he let go.  He could still feel her there, pushing him onwards.  As he got higher, he hit a transparent membrane.  He brought this hands up from behind him and punched straight through.  His eyes failed in the brilliance that shone above him and he passed out.





