\chapter{45}
\section{}
A Resolution  

``It wasn't addressed to my father,'' said Kiele.  ``It was addressed to someone called Jessie.  How do you even know it was him?''

It was a good question, but Zane already knew the answer.  His father had told him that many people involved in the G-TEP had to go by aliases to protect their past.  He informed Kiele and she shrank back.  So it was really true.  The taxi was moving faster now, splashing through the wet roads.  

The weather had started off so beautifully for the festival, but had soon turned into a dull and rainy day.  The droplets of water bounced off the windscreen as the car battered its way through the sheets of water.  The tyres adjusted themselves for better grip and suddenly the car seemed to stabilise.  The driver apologised for the rough conditions and they continued on their way.

Puddles were ripped through like bullets through flesh, tearing their way through the absent viscosity of the water.  They were going so fast now that Kiele was worried they were going to have an accident.  She couldn't believe what they were on their way to do.  They had no idea how they were going to overpower and disable Jessie.  

He almost seemed like a different person with the new name, he almost seemed like the person her father had been all these years.    Though Jessie had been given a new name, his old personality had remained in both personae.  Maybe it was the Hyper Aggression Disorder, or maybe it was just Mark – of course she meant Jessie.  It was so confusing to think of him as two people, though it made so much more sense.

Jolie watched through the window of the taxi as they hit the central district.  Zane and Kiele had walked a fair distance to get to the school, and now the taxi was trying to complete the same journey in half the time.  She watched as the citizens of the Emblem went about their daily business, unaware of the taxi as it whipped through the weather, unaware also of its occupants.  The three people who were trying to save all their lives.  

The taxi had become stuck in traffic and Zane wondered at that instant whether they would be better off walking.  Then he saw the weather.  It was gearing up to be one hell of a storm.  What a coincidence.  The day they really needed to get home fast, and mother nature threw them a weather front.  The rain beat down against the window, solidifying Zane's decision.

They were still a few minutes away from the house yet it seemed like an eternity away.  Would they reach Jessie in time?  If they didn't what was left to try?  Zane knew when he returned from his deed, he didn't have to come back to the time and space he had left.  He could quite easily end up fifty miles away at a rendezvous with Ric.  As long as they had the devices and enough power cells they could go wherever, and whenever they desired.  

Of course Jessie would have to ensure the machine was running to be able to return.  With the second jump it wouldn't matter, Zane already knew Jessie had no intention of returning.  The first jump however was different, Jessie needed to return, he needed to keep an eye on the device, and to do that meant he would have to return to the basement.  

Whatever happened, it wasn't going to end well



\thoughtbreak



Ric was staring at his phone.  He still hadn't received a call from Jessie, but then it was early days yet.  He had been impressed that his partner had actually managed to pull off the most difficult part of the plan, obtaining the time machine.  He took a sip of his coffee and sighed, he was going to miss this office or not as the case may be.  It made him smile.  In a few hours he would hopefully never have sat in this chair, never have filled out any of the damn P3345 forms, possibly never have even existed.

He despised the way the Emblem had defied the rules they themselves had created.  They were hypocrites.  Hypocrites that had bent the flow of time to their will.  Sure it had led to his job, his promotion, his office, his control.  However, none of this seemed worth it.  None of this was a justification for their behaviour.

Never having existed didn't scare him in the slightest, it just amused him.  The end surely justified the means.  If he had to die to protect a just way of life, an honest way of life, then it was all worth it.  He smiled again.  He didn't even have to die, he just had to fade into non-existence.  He took another sip of the coffee, its hot flavour tingling the back of his throat as he swallowed.  

For the first time he wondered about the journey he would take.  He had heard people describe travelling through time as meeting their maker, a serene and joyful experience.  Others described it as the single most painful experience of their lives.  Ric liked to think of it as a kind of judgement from the gods.  If it felt good it was a sign that the journey was meant to be, that it had been a sanctioned action by the man upstairs.  Those suffering in pain had obviously made the wrong choice.  To be perfectly honest it was probably more to do with the persons respective pain threshold or other environmental factors.  In truth, Ric had no idea.

Ric looked down at the phone again, still nothing.  It had been all of three minutes and he was beginning to get impatient.  He fought off the urge to call the weasel and request a status report.  Instead he began to sign some paper work using the digitipen on his desk.  It was all irrelevant really.  Most of the missions he was signing off were reconnaissance missions anyway. 



\thoughtbreak



Jessie was breathing hard now.  He walked up to the machine in front of him and began typing.  He wasn't the slowest typist in the world but his speed had never frustrated him before now.  He couldn't get the numbers to work quick enough and several times had messed up the date and time of his arrival.  He double checked it.  He triple checked it.  It all appeared good.  

The screen glowed in the otherwise gloomy dungeon.  Nearby, several lights on the device started flickering.  It was time for the first test.  He had to watch Ruben for the phrase he had promised to obtain.  He had considered just looking it up in the police reports, or even visiting the train, but Ric had forbidden him from doing so.  It could have caused a loop, he had said, it could affect the time-line.  

Jessie hadn't quite seen the relevance.  The information couldn't just spring into existence.  If he hadn't looked back in time to retrieve it, someone else must have.  It confused the hell out of him, but he respected Ric.  The guy knew his temporal theory.  He had half expected Ric to want to be present at every stage of the devices development, but he had opted out.  He had trusted Jessie.

The basement looked as untidy as ever, components strewn everywhere, and cables and wires interconnecting various pieces of equipment.  To the untrained eye, it looked like a veritable birds nest of electronics.  Even a trained eye would have had some difficulty figuring out exactly what the mass of parts actually did.  

A circular device was sitting in front of Jessie.  They had affectionately called it 'the eye' of time.  It was a safety device more that anything else.  It allowed the viewing of a specific time and place without actually having to travel there.  The benefits were twofold.  For one it required significantly less power to run.  Secondly the flow of information was purely one way.  Particles hitting a certain plane of space in the source time-frame caused mirror particles to be emitted in the current time frame.

Oken had never envisaged anything like this before.  To be honest, neither had the G-TEP.  It was an entirely new piece of equipment, devised, planned and built by Zane.  Now, here it was sitting in front of Jessie.  He typed a few commands into the computer and the device sprang into life.  

It was comprised of a metal ring, flat, about five centimetres between the inner and outer radius and with an overall radius of around thirty centimetres.  Three small symbols sat in a groove which sat equally between the two radii and these began rotating clockwise.

The computer reported back that the EFI system was up to speed.  It was now or never.  It hadn't been tested, but then, unless there was another time machine in the immediate vicinity, this was how it was supposed to be.  Jessie had been following the 'Book of Ric' on this one.  His prophetic words apparently borne from recent echoes which had travelled back through time.  

The small symbols were spinning at a constant speed now and generated a small hum as they did so.  Suddenly an image became visible in the centre of the metallic disc.  As Jessie looked closer he could see it wasn't really an image at all, it was just like looking through a window.  A window into another point in space and time.  There was Ruben, as expected.  Jessie tapped on the keys again and moved the orientation of the plane in the target time-frame.  

He was now fully focussed on Ruben.  He was listening, he would hear the words first hand, and then he would travel back to fulfil the prophecy.  It was all coming together.  All he had to do for now as wait for something to happen.



\thoughtbreak



The three of them sat in the car, still waiting.  The traffic was beginning to clear, but not quickly enough.  A group of rowdy pedestrians began to cross the street in front of them.  It didn't matter, the cars were going nowhere currently.  

The driver hadn't overheard their conversation but he found it rather peculiar that here were three people sitting in the back, all looking at each other, yet in complete and utter silence.  He wanted to say something, but didn't.  The last time he had commented on how quiet one of his passengers had been, they had come at him with a scalpel blade.  He had considered giving up the job, but then, the money was good and he had a family to feed.  No choice at all really, nothing to consider.

``I still can't believe he refused to help you,'' said Zane to Jolie.  She had filled them in on who Ruben was, and how he knew so much about the G-TEP and temporal occurrences.

``He's a confused man Zane,'' she replied, ``He sometimes finds it hard even to pour milk for his cat in the mornings.''  Her mind was suddenly filled with pictures of a cute cat called Benzo.  She had wanted to take that little kitten home with her, he had been so unbelievably cute.  

It was true that Ruben was confused, but Jolie knew in her heart that it was more out of fear, that he had flatly refused to help.  If he didn't try, there was no chance of him failing, and failing was what destroyed him more than anything else.  Ruben had failed in his marriage, his friendship to Oken, Jay, Leon, and now he had failed what seemed like the entire world.  

The traffic cleared once more and the taxi began to move more freely through the streets.  They were only a few minutes from home now and each of them were beginning to feel the pressure.  If they could turn back the clock, change their minds, undo what they had done, each of them would.  However, in a strange round about way, there had been a positive side to each of their actions.

``I'll take him down Kiele,'' said Zane as if from nowhere.  He wasn't trying to act strong to impress her, he was just telling her truth, what she so desperately needed to hear; that everything would be OK.  In truth, it had been the silence that had gotten the better of him.  He had voiced his thoughts in order to subtly inform the others of his intentions.  His mind was entirely open to the possibility that he would have to kill Jessie.

``Don't hold back on my account,'' came the reply from the otherwise sweet looking girl.  She hadn't meant it to sound evil or even malicious, but he wasn't even a father to her any more.  Though she still believed she was his own flesh and blood, he had been dead to her long ago.  It was now time to stand up to him, to give him what he truly deserved.  She had been holding back her entire life.  Things were about to change.

Jolie listened to the two grown-ups, who seemed to be even more mature that her at this moment.  A part of her was scared, they seemed so resolute, so strong.



\thoughtbreak



The car screeched to a halt outside the house and the three of them exited.  The rain was really beginning to pour down again now and they ran to the front door.  It wasn't going to be easy, but it had to be done.  Zane fumbled with the key, but eventually clicked the latch to the door and fell inside, followed closely by his two companions.

They had been an odd trio, the driver thought as he got out of his car to close one particularly stubborn door.  They had each been so formally dressed.  It had reminded him of characters from the black and white films he often enjoyed.  He imagined them running on the platform, heading towards the open doors on a train carriage.  People in the past always seemed to be dressed smartly to journey on the train.

As Zane rounded the corner of the hallway, the basement door was all too visible.  It was open and there was a sullen glow coming from down the stairs.  Zane's heart sank, Jessie was obviously down there and the machine was powered up.  As he lurched down the hall he noticed the pictures on the walls for the first time.  Nondescript pictures of flowers and such, there was even one right opposite his door, but he'd never noticed before. 

Zane almost stopped to take a closer look at the paintings but then, in an instant, a flash of light seemed to emanate from the basement.  It was accompanied by a slowly rising tone which was so loud that Zane was dropped to the floor, his hands over his ears.  The flash of light no longer seemed as simple as a flash any more, it was more of a shell and seemed to be moving towards them at great speed.  

The girls had dropped to the floor too, their ears in agony, unable to hear anything else around them apart from the sound of Jessie's success.  Zane's mind screamed out.  He crawled forward and the shell of light hit him.  It didn't hurt.  It didn't seemingly do anything to him.  

Inside the shell was utter silence.  The tone was gone, and as he looked behind him, he could see it had just hit Kiele too.  He called out to her, but she couldn't hear him.  As he called again he realised he couldn't even hear himself.  It was as if they were trapped in a bubble with no air.  The shell continued expanding, unaffected by walls or the ground.  Jolie was now inside the shell too.  All three of them were kneeling up looking around each other, trying to communicate somehow.

Then, as quickly as it had appeared, the shell contracted.  It shrank by about a metre or so before rapidly contracting in about the same amount of time it takes to make a hand clap.  As it did so it seemed to pull its inhabitants with it, throwing them to floor and flooding their ears with sound once again.

The tone was gone, and now they could hear the world around them once again.  It seemed louder than before, their senses peaked by the otherwise harmless shell.  They sat up and looked at each other.  

``It's too late,'' Zane shouted, ``He's gone already.''

He thumped the ground with his fist and Kiele began to sob.  Her erratic breathing hitting his over sensitive ears.  He had promised to save her.  He moved to sit up against the wall and with his knees bent up either side of him and his head down he began thinking about just what he could have done differently.  Nothing obvious sprang to mind.  

He got up and walked down in the basement, keeping an eye out for anything dangerous, human or otherwise.  Jessie could have rigged up traps of any description in the basement, he had to keep his wits about him.  He looked at the screen and saw the date.  It seemed all was not entirely lost.  Jessie had gone back to rig up the train, not divide the Emblem.  

Seeing the shell expanding had filled him with dread, it had been his worst nightmare, for he knew it meant that Jessie had used the device.  Thinking about it now, Jessie hadn't yet started on his final journey.  They still had time to stop him, but it meant apprehending him as soon as he returned.  The problem was, they didn't know exactly where he was going to appear, what state he was going to be in, or who he was going to be with.



\thoughtbreak



His arrival had been rougher than he had expected.  His body appearing a good two feet above the floor.  On entering this time-frame he was dropped to the floor and spent a few minutes writhing in pain on the floor, his arms and legs making strange patterns in the dust that lay on the ground.

His journey had been uncomfortable, yet not exactly painful.  He hadn't dared look as he had travelled through some kind of viscous ether that had been tugging at every single cell in his body.  It had been a strange feeling indeed, like he had been crowd surfing naked, every part of him being touched by foreign hands, pulling at his skin, his organs, his spine.  It hadn't hurt, but it hadn't been comfortable either.  

He stood to his feet and brushed himself off.  The train yard had been exactly as Ric had described.  Though the instructions on the laptop had been brief, Ric had fleshed out details with him at one of their meetings.  Jessie knew exactly where he was going.  He walked over to the train which he expected to be his silver bullet and checked the registration plate, '2243', just as prophesied.  He felt like he was doing the will of the gods.  It was all coming true, like a true prophecy.  He left his mark on the front of the train with a nearby red spray can.  That should do nicely he thought as he made his way round to the side.  One of the doors was open and he climbed inside.  

The smell inside was musty and old.  The train was a veteran after all.  He began to make his way down through the carriages and checked his shield generator as he walked.  The generators had been improved since Oken's iteration.  Slimmer, sleeker and with lower power consumption, Zane had achieved some miracles of engineering during his work for the evil weasel.  

Jessie smiled to himself as he walked down through another carriage.  He had encountered a hole in the floor but had managed to drop down to the ground below to overcome the situation.  These trains really were falling apart he mused.  The train shuddered into life.  He needed to get a move on, it was obviously starting on its journey, but as yet Jessie had no clue as to its destination.  It mattered not, things were going just as they should.  He was a king among men.

It felt so good to be there, like he had been chosen from above to receive this power, this gift.  He was invincible.  He was Jessie and pretty soon he was going to change the world.  He smiled again.  The device for returning was still in his pocket, warm to the touch.  He took it out and looked at the small black cylinder.  He needed to change the power cell over.  It was a good thing Zane had managed to complete the device and leave enough for their journeys.  There were only four left in the basement.  One each for the final journey and two spare.  He ejected the old power cell and discarded it as he continued through the train.  

He plugged in a new power cell and the device leapt into life once more.  It was vaguely reminiscent of the handle which had once been used to wield that spiteful Bethany.  Zane had managed to make an exact carbon copy of the device in his hand.  The boy had always dreamed that Jessie had required him to make two so that one day they would both be allowed to make a trip, with G-TEP permission of course.

As Jessie reached the main cabin he was aware of another person up ahead.  He took out his gun, the same pistol that had killed Kaitlin.  The door to the main cabin opened to greet him and the driver turned round.  His face looked confused.

``What the hell are you doing here?'' he said, ``You're not allowed in here.''

``My apologies,'' said Jessie, as he raised the gun and shot the poor driver in the stomach several times.  The driver clutched at his stomach and fell backwards, narrowly missing the doorway, and instead hitting the side of the frame.

Jessie walked past him and into the engineer's section.  The train panel layout was confusing, but not wholly unusable.  He jabbed at a few buttons and closed off the doors as instructed, locking them in place.  He turned to the shaking figure who lay on the ground beneath him.  

``How do I enter program codes?'' he said.  The man wasn't really listening.  Jessie looked down and saw the name badge.  ``Markus, if you don't answer me, I will make the pain so much worse.''  He could feel anger starting to swell inside of him.  He checked his pocket.  Damn it!  He had forgotten his pills.  He had been so caught up in the events of the day that he had completely forgotten to take them.

Markus was still relatively silent.  He was murmuring softly to himself, preparing his mind for death.  He knew he wasn't getting out of here alive.  

``Markus!'' shouted an impatient Jessie, ``I really don't think you want to tick me off.  You didn't even say anything and I shot you.  Imagine what would happen if you said the wrong thing.''

The poor man let his head slip backwards against the wall.  Jessie stepped backwards and picked him up by his collar.  The man coughed up blood as his stomach was stretched by his dangling legs.  

``How do I enter program codes damn it!''

Markus, unable to fight any more, pointed at a button on the panel in front of him, his head had cocked to one side and his arm lifelessly hung at an odd angle, though still surprisingly accurate.  Jessie pushed the button and a prompt on one of the screens changed.  He typed in the code he had been given, and all of a sudden felt the train lurch forward.  

He sat there in the train, laughing to himself as the gigantic bullet began to pick up speed.  It was moving really fast now.  He looked down at his watch, not too long to go now.  He reached into his pocket and pressed the button on the returner.  His body flew up two feet into the air, suspended in the viscous ether and instantly phased out of existence with the universe, the train smashing through his apparently absent ghost of a body.

This time it was more painful.  



