\chapter{35}
\section{Revealing}


Zane had gotten up early the next morning.  Though his body was still sore all over he was driven by the promise of seeing Mark's physics experiment.  He didn't expect much, but it was interesting nonetheless.  At home, her never got a chance to share his ideas with anyone.  Now perhaps he'd met someone who would actually take an interest in his works, like his father had.

The boy had loved his father and mother dearly, they had both been responsible for encouraging him with his studies.  Though he had hated the pages and pages of cursive writing, he knew that when it came down to it, he was being prepared to be a formidable force in the world.  Whatever Zane had needed for his experiments and studies, his father had either bought, begged or borrowed, but never stolen.

They had spent countless afternoons tinkering with his new theories or experiments.  His father, unable to comprehend most of what his young boy was talking about, just acted as the hired help, holding things in place, whilst Zane perused their position or usefulness.  The scholarship would have made his dad so proud.  Zane had broken down into tears when he had been presented with it.  He still wasn't sure whether he was going to take it.  It was a good scholarship, in fact, good wasn't grand enough to describe it.  It was a fantastic scholarship, but he felt so at home in the apartment, and now he had met Kiele and Mark, he wondered if he would do better to stay.

He was sure his father would be proud of him no matter what he did.  Come rain or shine he had always been proud of him.  Even when Zane had gotten himself into trouble, his father had always been there to lead him through it.  Zane put a lot of what his father had been into his life.  His mannerisms and language, were often so similar that, had they both been in the same room, one could have been gotten their voices mixed up entirely.

Zane was already half up.  He had taken a shower in the downstairs bathroom and was now trying to get dressed in his room.  The plush carpet pushed through between his toes and tickled him as he tried in desperation to pull on the jeans he had been wearing before his accident but for some reason they wouldn't pull up.  His muscles just weren't strong enough.  To top it off he now had his legs stuck in them.  This wasn't going well.

He noticed the door was unlocked and tried to make his way over to lock it.  About halfway, one leg seemed to become entangled in the other and his entire body fell to the ground in a confused heap.  His head hadn't hit the floor hard, but it was hard enough to disorientate him.

Before he knew what was happening, the door was open, and Kiele was standing there.  Her presence seemed to have given him temporary amnesia, for he waved at her, and greeted her with a 'Hi', before suddenly realising that he was lying face down in his boxer shorts, with his trousers at his knees.  He tried in vain to cover his hind with his hands, but his arms were too sore to reach.  Instead he just lay there, his head now rolling left to right as he tried to melt away by becoming one with the carpet.  

Kiele laughed out loud.  She had never seen someone make a bigger fool of themselves.  Zane was currently being repainted in an embarrassing shade of ruby red as his head continued to hide his face.  She walked over to him and helped him up.  It was obvious what he had been trying to do and she assisted him in pulling up his jeans.  A motherly instinct took over and she almost went to do up the buttons.

``Hey, hey,'' said Zane, ``I'm not entirely crippled you know.''  She smiled at him.

``Just shout if you need help putting your trousers on in future then, superman.''  She giggled and walked out of the room, closing the door behind her.  Though she hadn't shown it she had been rather embarrassed by the whole situation as well.  She had never seen any man in his underwear before, let alone a guy she was so deeply in love with.

Eventually he emerged from the room, still in his jeans, and made his way to the kitchen.  Mark was standing next to the sink, eating a slice of toast.  He was wearing a different shirt today, but he still maintained his better appearance.  Kiele hadn't seen him yet, but when she did, she would most likely be quite impressed that the man had managed to keep it up for more than a day.

``Come on,'' said Mark, ``Grab your self a slice and let's go.''  Zane reached over and grabbed a slice of toast from the plate sitting behind Mark.  It had been buttered and spread with marmalade.  Mark picked up a key from the shelf and the two of them made their way to the back door.  As Mark opened it, Zane stopped.  

``Isn't Kiele coming?'' he asked concerned.

``No,'' replied Mark, ``She usually spends her Sunday mornings in bed till at least twelve.''  

Zane nodded and smiled.  He was slightly disappointed that she wouldn't be sharing in this moment.  To be honest, he was more disappointed that he wouldn't be able to wow her with his knowledge of physics, not that she seemed that impressed by academics anyway.

The two of them climbed into the car and Mark started the engine.  This was going to be a trip Zane would never forget.  



\thoughtbreak



As Mark turned the vehicle into the car park outside the warehouse, Zane became slightly nervous.  He had expected the 'experiment' to be in the shed, at the bottom of the garden, or even in the basement.  He hadn't expected them to drive for almost fifteen minutes to what seemed like an empty warehouse.  As he looked closer, he could see the fading words over the door, 'A V Onics'  Either someone with all the wordplay skill of a skunk had written it, or it was a joke.  Unfortunately the former had been the truth.

A disused warehouse, formally used for the repair of elderly aircraft was to be the initial meeting place of Zane and Bethany.  The paint was fading and it looked like it had been standing there for fifty years or more.  It was actually one of the last free standing buildings like it in Alendria, most had been destroyed when it was feared the war would be coming to the city.  

They both stepped out of the car and closed their respective doors almost simultaneously.  Zane looked around, it wasn't often that you found a place with real greenery in Alendria,  which was mostly a commercial construct.  Zane was sure that he had never seen so much grass in his life.  

Mark walked up to the door and put a small key into a lock.  It was an old fashioned padlock, with a digital key.  It sang as it opened, alerting the user that they had been successful in deactivating its hold over whatever was inside.  He took the lock off and placed it into his pocket.

Mark opened the door and stepped through first, followed shortly by Zane.  The boy had regained most of the strength he had lost that morning and was managing to keep up with Mark as he walked into the centre of the ware house.  As Zane followed he was utterly amazed at the size of the place.  It had been constructed with a metal shell, and covered mainly in sheets of ageing steel.  The whole place seemed to be filled with a musty smell and as the light came in through the windows, it illuminated the entire place in a sepia tone.  

The slight breeze coming in through various holes which had been left in the construction perturbed the natural steady state of the air, and gently blew around specks of dust which created a dreamy atmosphere.  This would have made a cool scene in a movie, thought Zane as he continued to follow Mark.

It was then that Zane noticed something in the middle of the warehouse.  It was a black holdall, surrounded by four smaller black objects.  Each of the small black boxes, he could tell they were boxes now, had a small green light on it, which illuminated only a very select portion of the warehouse, that being the tiny area surrounding the lamp itself.  The lights were dwarfed by what appeared to be a very coincidental column of light which was shining down from the ceiling.  It wasn't vertical, for the angle of the sun prohibited it, but it lit an area around about three metres in diameter.

Zane wasn't sure what the black boxes were, but as he stood there next to the black holdall, entirely surrounded by the invisible field of the temporal shield generators, he had a feeling he was going to find out.

Mark gingerly stepped forwards and began to unzip the holdall.  Like a clerk in an expensive jewellery store, unveiling their prized possessions.  As the zip moved, it created a low droning noise, which seemed to fill the void of the warehouse.  His position in the column of light cast a shadow over the bag and he sidestepped round in an arc, delicately tracing the circumference of the lit area.

It was taking an eternity.  Zane thought he had seen a glimpse of something shiny inside, but it could have just been his eyes.  All of a sudden his sense came to him.  'A physics experiment.  In a black holdall?'  This was obviously no ordinary experiment.  The zipper completed its journey along the peaks and troughs of the largely taught terrain and the top of the holdall lay split in two.

Mark pulled the two pieces apart and for the first time Zane saw what lay beneath.  A sword.  A strangely familiar looking blade.  Bethany.  His eyes widened and for a moment Mark was unable to determine if it was fear or excitement.  The boy looked down at her slender figure, once again lying there naked.  He bent down and studied her, his eyes caressing every part of her with intense attention.  He reached out and touched the grip, it was cold, so cold.  

How had Mark managed to get his hands on what was possibly one of the most revered weapons in history?  Zane was a little scared, but something invisible drove him forward.  He crouched there, completely dumbstruck.  In awe at the subtle majesty of the blade which lay there before him.  He had obviously never seen her in action, not in real life, but he had seen her dancing with Oken and he had wondered what it would have been like to dance with her too.

``You can pick it up,'' came Mark's voice softly, ``Just don't take it outside the black boxes.''

It wouldn't really matter if he did, but it would cause a little more of a headache for Mark and Ric.  A temporal residue of this size, whilst Bethany was idle, would largely go unnoticed.  However, if the signal was investigated, it would turn out to be a particularly abnormal fluctuation of time, a small rift, with an unmistakable signature, that of Oken Brown.

Coincidentally Zane did exactly as Mark had done, the first time he had held the blade.  He placed both hands underneath her and lifted her up.  He could feel her cold skin against his.  It was the complete opposite of Kiele.  She was warm, sometimes a little too warm, and here was her polar opposite, with a subtle coldness running through her veins.  A part of him wanted just to grip his hands, but doing so would have resulted in a serious injury to his left hand which was cradling the blade itself.

He shifted his position slightly and held the strong confident woman in a fighting stance.  She hadn't lit up when he had touched her, as she had when Mark had lifted her for the first time.  It wasn't due to any preference on Bethany's part, but due to the fact that Mark had removed the power cell from the innards of her body.  She was dead at this moment, encased in a state of stillness, which could never be broken by conventional means.

``This is it, isn't it?'' he said, ``This is Oken's blade.''

Mark nodded.

Zane's head suddenly filled with a million questions.  How did it work?  Could he have a go?  Where had Mark obtained it?  Had he paid for it at auction?  Why hadn't it been destroyed by the G-TEP?  He tried to settle for a particularly encompassing question, one which would answer most of his queries in the most economical manner.

``What are you doing with it?''

Mark was getting ready to lie.  It had to be good, something believable, but also watertight.  This was a very important moment.  This could be make or break.

``It's time I levelled with you,'' he said.  ``I'm a G-TEP researcher.  I've been asked to carry out some investigations into this weapon.  We've noticed some activity and it all points to this device being used a hundred years in the future to travel through time.''  Zane was listening intently, still clinging on to her dead limp body.  ``I am supposed to see if this really can be turned into a time machine, or if there are other factors involved.  I thought you may be interested in helping out.  I have already cleared it with my superior.  He has seen your physics scores and was eager for you to take a look too.''

Zane smiled, he had always known he would be involved in something great, but building a time machine?  That was just too much.  That was something astronomical.  Mark watched the boy as the realisation sunk in, that he could work on this without any fear of being caught or killed by the G-TEP.  The tiny flaws of the explanation smoothed over by the complete whitewash that was Bethany.  The boy was getting excited.

``But you can't tell Kiele.'' he said.

Zane looked up sharply, a face bearing confusion was immediately visible.

``She doesn't even know I'm a G-TEP agent,'' said Mark, ``and I'd prefer to keep it that way.  Plus the mission is of the utmost secrecy.  You can imagine why''

Zane nodded.  More and more of what she had told him made sense now.  Working for he G-TEP must have placed him under intense pressure.  No wonder he wasn't happy all the time.  Everyone had their bad days, he figured, especially G-TEP.  They must be working round the clock to ensure that the time-line stayed clean.  He admired Mark, someone who had dedicated their life to protecting the history and memories of others.  He also admired Oken, for his dedication in created the blade which lay in his hands right now.

``Why do we have to stay inside the black boxes?'' Zane asked.  It wasn't that he hadn't figured out roughly what they were, but he needed confirmation.  

``They are temporal shield generators.  Not only do they protect the history of what ever is inside, but they also  ensure that no temporal residue leaks out into the outside world.  The G-TEP are not the only party that would like a temporal weapon.  There are many terrorist groups that would love to get their hands on what you have there.''

Zane nodded again and replaced the blade into the holdall.  It had been one of the most exhilarating experiences of his life.  He was filled with energy, charged to the brim.  He had to sit down.  His legs were hurting now.  The excitement, coupled with standing for a long period of time was proving too much for his recovering body.

``So, do I take it you're interested in working with it?''

Zane nodded and smiled, ``Try and stop me.''

It was a shame he couldn't tell Kiele anything.  He would have loved to describe his work to her.  Would she have been interested?  Probably not, but she would have listened anyway.  That was the kind of person she was.  He loved her so much.  Once this was all over, he was sure Mark would let him tell her.  She would be so proud of him.  His father too.  It was a great day for Zane.  Finally he felt his life was complete.

``I have some literature at home,'' said Mark, ``to complement the book I lent you the other day.  There's quite a bit to read up on I guess and before I let you touch it, I want you to demonstrate to me you know your stuff.''  It was a clever idea.  He was going to force Zane to teach him the basics, under the pretence of demonstrating his knowledge, so that Mark could understand what was going on.  After all, Mark was no physicist.  He had walked over to the bag and had begun to zip it back up again, covering Bethany in the darkness she had resided in for many years.  Mark echoed his thoughts in speech, ``I have to admit, I'm not a great physicist, but I'll help you out all I can.  Maybe I can make you tea or coffee''

Zane laughed.  He liked Mark.  There was still something hidden there, but nothing important, felt Zane.  Someone of his stature deserved their secrecy.  He couldn't imagine how many missions Mark must have been on, protecting lives, saving the innocent.  Just like his father.  

Mark had picked his lines out well.  He had received instant and universal respect from the boy.  It was quite astounding that he had been so trusting, so quickly.  Mark had concluded that Zane's father being a former G-TEP agent may have had something to do with it.  Now he just needed to keep Kiele in order.

Ric had given him a deadline, a time by which the device would need to be complete.  Ric had seen the temporal echo shifting back through the time-line and had traced it forwards to about a month out.  Mark only had a month.  It hardly seemed possible, but if Zane kept focussed on his work, Kiele could provide the light entertainment and relaxation that he was bound to require.  The last week before the deadline was a school holiday.  He would have to make sure that Zane remained focussed throughout that period.  

Mark was warming to the boy.  He was quick, smart and most of all obedient.  It would be a shame to kill him after the device was fully complete, but Ric had told him to ensure there were no loose ends.  The boy could probably have created the device from scratch thought Mark.  In truth, this boy was almost a carbon copy of that man from the past, Oken Brown.





