\chapter{26}
\section{Interrogation}


Ruben repeated his question and embellished it by gripping her on the biceps, ``Did they say anything about any writing on the train?''  Jolie's face turned to one of utter confusion and she pushed his strong hands off of her.

``No,'' she replied.  Just what was with this guy?  A few hours ago he'd been a sad lonely figure, in a decrepit house, with not so much as  a few words to say.  Now he wanted to know about writings on trains.  

``Damn it,'' shouted Ruben, alerting the attention of the security guard.  He repeated his curse once again, banging his palm to his forehead in frustration before adding, ``If you ask them, and.....and they tell you, please, please let me know.''  He handed her a scrappy piece of paper with a number on it.  

She took the paper, and looked down at it.  4243799870012.  The writing was very messy, she had had trouble deciphering several of the digits, but she was pretty confident she had them all now.  

``What is all this about Ruben?'' she asked worryingly.

``I'm sorry,'' he said, ``I can't risk telling you.''  With that he had turned around and was already walking off quickly into the distance.  No explanation, no nothing.  She fought the urge to chase after him and force the reasons out of him.  She was there for Kiele, she could deal with some crazy man later.

It had been incredibly odd though.  He had turned up out of the blue, entirely out of the blue, knowing exactly where she was, and was talking about writings on a train.  It seemed bizarre, like the plot of some twisted novel.  She watched as Ruben tried to subvert the gaze of the security guard.  It worked and he skulked away into the distance, half walking, half running back to his lair. 

When he had awoken from his attack he had immediately visited the local store and bought an e-ink paper.  In it details about the crash were starting to come in, including details about the teacher whose students they were.  Ruben had scarcely believed it when a link had sent him to a picture of a glowing Jolie.  

Ruben had immediately called in to the local hospitals and found the one housing the young boy who had been injured.  He hadn't wanted to visit, not yet.  Jolie was a great link to the information he so desperately needed.  He had followed her, hoping to catch her at home, but the precinct had been an even better opportunity.



\thoughtbreak



As Kiele walked out of the changing area, head down, the clerk waiting at the door scanned the item to ensure it was as it had been when she entered.  The scanner had taken a digital imprint of the item before she had used the changing room and was now in the process of matching it against the scan just taken.  Criminals had begun to make small fortunes by carefully slicing off delicate pieces of expensive clothes at multiple stores and sewing them back together to make their own Mount Taleberg unique items.  

The clerk smiled as the machine confirmed her suspicions that the dress was completely intact.  ``Was it to your liking?'' she asked.  What a stupid question, of course it had been to her liking and had it not cost the earth and then some, she would have considered buying it.  It was the most beautiful she had ever looked.

``It looked great,'' she replied and then thinking quickly,  ``But I can't afford it this month.''  She gave it to the clerk who put it back on the rail behind her, ready for reimbursing the empty space which now stood where the dress once was.

Jolie walked over to her smiling.  She'd decided to put Ruben out of her mind completely.  ``Did it fit?'' she asked the girl.  

``Yes,'' said Kiele.  She wasn't about to lie to Jolie.  

Jolie frowned, ``Then why are you putting it back?'' she questioned.  The store clerk stood in the middle of this exchange, not knowing what to make of this mother and daughter squabble.  Jolie held out her hand to the clerk.  For a moment the clerk stood there in apparent confusion.  What was she being asked to do?  Then it dawned on her that the mother wanted the dress back.  Obviously she had picked it out for the girl to wear, the girl had hated it, made up an excuse and now the mother wanted to buy it anyway.  She couldn't have been further from the truth.

The clerk obliged and gave the dress to Jolie.  She turned and walked away smiling.  Kiele ran after her, the two of them now engaged in a power-walking contest to the finish line, the tills.  'Just what was Jolie thinking?' pondered Kiele.  The dress would have been more than an expensive purchase for Jolie too.

Though many stores had done away with 'point of sale' areas, Mount Taleberg still insisted that it offered the ultimate in customer care and satisfaction.  They also enjoyed being that little bit kooky.  Having a till on a desk was retro, very retro.

Jolie hit the desk and was followed quickly by Kiele.  She seemed a little more angry now.  ``You don't have to do this,'' barked Kiele.  ``I can handle the fact that I'll never wear a dress like that.''  Her voice was sad, but the anger carried it forward.

``Let me do this for you,'' uttered Jolie.  The words had come out wrong.  Kiele wasn't a charity case but Jolie had only wanted to explain her intentions.  She wanted Kiele to feel wonderful for a change.  ``Besides,'' she said, ``think of the look on Zane's face when he sees you in it.''

Kiele smiled and she even let out a little huff of laughter.  Why was Jolie being so nice to her?  She didn't deserve it.  Years of conditioning by her father had forced her to believe she was worth nothing.  Now here was Jolie spending half a months wage on a dress for her, just to make her feel good.  

The girl had to admit, it did feel good.  Her only concern now slipped into her mind.  Her father.  He wouldn't like the dress one bit, nor the fact that Jolie had bought it for her.  She thought a little more and resolved that her dear old dad would just have to get over it and live with it.  'Kiele!' she thought, 'are you really getting a little rebellious?'

For too long she had lived in the shadow of her father, existing, breathing, eating, sleeping, only when he said so.  It wasn't living, it was fearing and slowly but surely she was going to pull her way out of it.  The dress would be a perfect start.  He couldn't rip it up, else Jolie would ask where it was.  He couldn't ban her from wearing it tomorrow, as Jolie was expecting her to.  Little by little she would take her power back.  She grinned.  Kiele had only just discovered the power this item of clothing was going to have over her father.

She hadn't realised that the dress was already over the counter, and one of Taleberg's gatekeepers was now passing the tag near the reader.  Jolie was instructed to press her thumb to the plate and enter her passcode.  Two factor authentication had been introduced many years ago, as a way of safe guarding peoples credentials a little more than pin codes alone.

The dress was folded carefully and laid to rest in a beautiful stone coloured box, embossed with the words 'Mt' and 'Taleberg.'  The clerk placed the box into a Taleberg branded paper bag and put it on the counter, rotating it so that either one of them could grab the handle.  Jolie's arms stayed firmly by her side and she let Kiele be the one to receive the gift for the first time.  

The bag was barely large enough to hold one Mt. Taleberg box.  The heavy paper, being manufactured in a brownish tone, made it sit well with the stone tone of the box itself.  The handles were made from small sections of rope and were soft to the touch.  As Kiele grabbed the handles the softness rubbed off on her and a smiled crept across her face once more.  She pulled the bag off the counter and placed her other hand underneath to stop it from falling.  Jolie had never seen such care being taken over a paper bag before, but then it wasn't the bag so much, its contents were what mattered, she thought.

The bag was positioned by her side, and the two girls walked towards the exit.  The security guard tipped his imaginary hat towards them as they exited the store.  They had made a purchase, he thought, good for them.  He'd never be able to afford clothes from here, not on his salary, but it always made him happy to see the smile on girls faces when they left the store, some guys too come to that.

Jolie had suggested that they get something to eat after their visit to Mount Taleberg, and they now wound their way from one side of the precinct to the other, with their destination being the food court.  It was getting on for half past six now and most of the shoppers had retired to their homes for their evening meals.  This gave the girls free reign of the food court.

``Where d'ya wanna go eat?'' asked Kiele.  She was starving hungry.  They had given her some food at the hospital, but nothing substantial, and now after traipsing round just one store, she felt like her stomach was ready to burst from the cage within.

``You pick,'' said Jolie, ``I really don't mind.''  

``Hmm,'' mused Kiele.   If they went to 'Burgers'n'All' it would be an extremely greasy meal.  'Plump Muffins' just sold muffins, unsurprisingly.  No, the only real contenders were the pizza place and 'Grey's Old Bakery.'  Kiele opted for the pizza place.  ``How about Jahred's Pizzeria?''  she enquired.  

``Sounds good to me,'' replied the teacher.

The two of them continued to weave in and out of the dwindling numbers of shoppers.  It was amazing to think of how many people used this place on a daily basis.  The precinct was massive, covering the area of about five football pitches.  When Kiele had been meditating on their choice of restaurant she had limited herself to the few that were available in the eastern food court.  There were in fact three more areas identical in size to this.  It was sheer madness thought Kiele.

As they approached Jahred's establishment, Jolie saw a figure sitting down inside the restaurant.  She almost doubled back in fear.  Was it Ruben?  She had almost forgotten about their meeting in Mt. Taleberg.  As they got closer Jolie slowed, whilst Kiele began to decide what pizza she was going to have.  ``I think I'm going to go for the spicy one,'' she said.  ``What about you Jolie?''  

Jolie wasn't thinking about pizza, she was carefully analysing the figure inside the pizzeria.  If it was him, she didn't think it wise to go in.  He'd probably try to harass Kiele about the 'writings on the train'.  What was he doing here?  All of a sudden Jolie saw the figure twist its head and it became apparent that it had a large blonde ponytail.  She was off the hook.  Kiele repeated her name, and she broke free of her stare.

``Jolie?''

``Sorry,'' she said, ``I must have been some place else.  What were you saying?''

Still occasionally flitted her eyes back to the figure whilst Kiele spoke.  ``I asked what pizza you wanted,'' she was unaffected by Jolie's apparent lack of attention, ``I'm going to have the spicy one.''  

Jolie looked over the menu which was illuminated high above their heads.  ``I think I'm going to have a pepperoni,'' she said.  

They walked towards the counter and placed their order.  They had been first in the queue and there was only a handful of people left in the seating area.  It looked quite smart with its combination of red plush seats, and silver chrome support work.  All the walls were covered with a base colour of either red or white and where the two met, a wide transition area could be found detailing interlocking squares of each rivalling colour.  It was quite clear that the proprietors enjoyed the look of a good colour scheme.  The menus followed the same design theme too, with the top half being white and the bottom red.

The waiter had said their food would be ready in about two to three minutes.  Steamation cooking was all the rage now and boasted the best flavours, coupled with the shortest amount of time to cook.  They sat down at a table that was supposed to seat four.  Kiele placed her bag on the chair next to her, so she could keep it in sight at all times.  It amused Jolie that the young girl was taking so much care of the dress.  She wasn't even wearing it, and yet she was protecting it like a bodyguard.  Would she have taken a bullet for it?  Probably.

``I take it you enjoyed Mt. Taleberg?'' asked Jolie.  

Kiele nodded, it had been fantastic, the most amazing shopping trip she had ever been on.  Realistically, the only real shopping trip she'd ever been on.  Jolie had felt like a mother to her, and she had liked it.  

``It was amazing Jolie,'' she said.  ``You really didn't have to buy me that dress.  Browsing would have been just as much fun.''  

Jolie itched her tattoo subconsciously, ``You mean I could have gotten away without spending my life savings?'' she asked jokingly.  

``Stop it,'' whined Kiele, ``you're making me feel really bad now.''   They both smiled at each other.  She knew Jolie was joking.  It's what she liked best about her.  Though she was a teacher at the school, she was regarded by a good half of the population to be a friend more than an educator.  Maybe it was because they were so close in age, or maybe it was just because she cared more.

``So,'' Jolie began, ``are you going to visit Zane tomorrow?''

``I'd really like to,'' she replied, ``but I don't know how I'm going to get to the hospital.''

She hadn't been fishing, but Jolie's reply was music to her ears.  ``How about I pick you up on my way through?''

``You mean it?'' she asked excitedly?

``Sure.''  She smiled at Kiele before adding, ``I want to be there to see the look on his face when you walk in in that dress.''

They both laughed.  Kiele couldn't wait either.  There was something about Zane that she was really starting to like.  Though her father had sternly warned her off, she just couldn't help but feel a certain affinity with the strange young man.  It was as if destiny had thrown them together.  

Who would have thought it?  A week ago she'd never have looked at Zane as potential boyfriend material.  Sure, he was oddly cute, but he didn't have that 'Je ne sais quoi'.  Now it was an entirely different story.  She thought back to a quote she'd once heard;  'They say relationships based on intense circumstances never work'.  Pah, what did they know.

Kiele hadn't realised that she had been looking off up into the sky, day dreaming.  The waiter had arrived with the pizza and was just standing there, awaiting the princess to remove her arms from the table.  Eventually his patience ran out and he let out a poignant 'Ma'am'.  Suddenly she realised her mistake and apologetically moved her arms out of the way.

The waiter put down their pizzas and walked off tutting to himself.  It had been a long day and he was really tired.  Time to knock off early and go play Devil Hunter Dreamscape 3.  Man he loved that game.

``You really like him don't you?'' enquired Jolie.

``Is it obvious?''

``Not entirely.''  

It was supposed to be a cryptic answer.  It was supposed to entice her into asking more.  Yet she seemed to just accept it without saying anything further.  Finally the curiosity got the better of her.

``Do you think he's a good guy?'' Kiele asked the teacher.

Jolie sat there for a good few seconds before answering.  She already knew what she was going to say, but part of her wanted to confirm it, and the other just wanted to tease Kiele.

``I think you two would make a great couple,'' she said finally.  Kiele beamed and nodded.  It wasn't often she talked about things like this with anyone.  She had a few friends at school, but having a father like Mark made it difficult to keep any good ones.  

They sat there in silence for the first slice, both exceedingly hungry, fulfilling their appetites.  It had been a very long day and Kiele was really tired.  It had been a nice idea to go out with Jolie, and she was so grateful for all she had done for her, but all Kiele could think about now was getting back home and going to sleep.  She knew she would have to face her father sometime in between those two events, but she guessed she could handle him now.

Jolie wanted to know more about the young girl before her.  She felt she owed it to herself, and before she could take it back, she'd asked a very personal question.

``So, what happened to your mom?'' she asked.  It was instantly regretted.  Not that Kiele's reply was anything other than polite or interesting, she just hated herself for being so blunt with the poor girls feelings.

``I never met her.''  For an instant Jolie looked confused.  Kiele continued, ``I was born In Vitro.  My mother died about two years before I was born.  Mark decided he wanted a living memory of her.  So he created me.''  

The words rang through Jolie's head coldly.  He 'created' her?  How arrogant.  How bloody arrogant.  How did he feel he had the right?  She was angry.  It wasn't as if In Vitro births were uncommon.  Around five percent of all births now were a product of the lab, but it wasn't usually done for such selfish reasons.

The technology had been improved since the early twenty first century.  Babies could now be born with any number of characteristics.  In the cold cold world of the present day, mummies and daddies could choose everything about their baby.  The choices had to go past a governing board, to prevent too many infants being born with certain characteristics, but on the whole, it was fairly easy to design and create your own child.

``Does it bother you?'' Jolie asked.

``Which?'' said Kiele smiling, ``that I was born to fulfil a desire to fulfil a purpose, or that I was a product of a lab technicians afternoon.''

Clearly both perturbed her and to reel off a sentence like that meant she had though about it long and hard before.

``I'm sorry,'' said Jolie, ``I never meant to be so cold.''

Kiele was quick to put her in her place.  ``Don't you dare apologise.'' She said sternly.  ``You didn't do this to me.  You've been nothing but nice to me ever since I first met you.''  It was true.  ``I've never been able to talk to anyone about it quite like this.''

Though her voice had been stern, Jolie had known the sentiment.  There was anger there, but it was meant for Mark and quite rightly so.  It was all getting a little too much for Kiele, and Jolie only just noticed the tear running down her left cheek.  There weren't cascades of tears, just a lone soldier, who had managed to fight his way out and was now escaping the prison in which he'd been trapped so long.

``I'm so sorry,'' said Jolie, reaching across the table and grabbing hold of Kiele's hand.  ``Let's talk about something else.  Did you decide what you're going to do after you leave school?''

The question was different enough to shock Kiele out of her current state of mind.  In truth, she really hadn't though about it too much.  

``I've always liked cooking,'' said Kiele.  ``I'd love to have my own bakery one day.''  It was a nice dream, but possibly nothing more than that.  

``Really?'' said Jolie, genuinely surprised.  She'd imagined the girl to have so much more ambition.  So much more drive.

``Or maybe a doctor'' she offered, ignoring Jolie's question.  Her two career choices were currently very different indeed.  She really hadn't thought about it much.  It was glaringly obvious.

``It takes a long time to become one of those,'' Jolie advised her.  

Kiele just sat there musing.  She had no idea really what she wanted to do.  In some ways it scared her, but in other it just seemed kind of natural.  She went with the flow, a product of living with Mark, if he shouted jump, she jumped, if he left her alone for an afternoon, she chilled out.  

Jolie had been thinking too, but now as she sat there she was reminded once again of the figure who had been to see her earlier in the trip.  It was a hat and coat in a shop window which had brought the memories back.  She'd looked over and panicked, thinking she was being stalked again by that brute Ruben.  The question he had posed repeated itself in her mind.  'Had they seen any strange writings?'  No wait, that wasn't entirely accurate, Ruben hadn't described them as strange.  

As Jolie sat there, curiosity finally got he better of her and she decided to voice some question about the 'writings.'

``Kiele?'' she said, ``Did you......did you notice any writing on the train?''  

``Writing?''  The question seemed very odd indeed.  ``I don't know what make of train it was, if that's what you're asking.''  What was Jolie getting at?  Why change the subject?

``Don't worry,'' she said.  ``It was just a silly thought.''

It wasn't a silly thought, Kiele meditated.  It had been phrased too delicately.  What did she mean writings?  Where had that question come from?







