\chapter{16}
\section{Defence Mechanism}


``I still can't believe she just gave it to me,'' exclaimed Zane in excitement.  He'd been banging on about the watch for what seemed liked an age, even though it had only been five minutes in actuality.  

``I know Zane, I was there.'' She wasn't really angry with him, she just really didn't want to hear about that damned watch again.  

``Sorry,'' he offered.  They reached to entrance to the Zone.  The highly secretive hideout was almost unnoticeable on the street.  There was no singular point anyone could put their finger on, the door just seemed a little off.  People probably passed it on a daily basis, never once giving it another thought.  The paint was faded and the words, 'Best Time Ever', were just faintly visible beneath the whitewashed surface.  It had clearly rained the day they had painted this door as the whitewash had run and was exceedingly patchy in several places.

The padlock, for which the key mated, was rusted and worn.  It still held strong though, and Zane gave it a sharp little tug, rattling the lock and the door.  Kiele stepped forwards and placed the key into the lock.  It twisted free as if brand new and she wound the cylinder of the padlock through the holes of the brackets on the door.

They both stepped through the door simultaneously, but it was Zane who found the light switch behind some old mop handles on the right.  Turning it on, the crimson glow of the mop heads became abundantly clear.  Zane wondered just how many people were a part of those mops, they had clearly been used for sweeping and soaking up blood and guts.  He had to stop thinking about that now, else his stomach wouldn't allow him to go much further.

Unsurprisingly the layout of the room hadn't changed since yesterday.  The door to the right still led to the control room, whilst the door ahead of them was the vault door to the location's crown jewels.  The smell of death still lingered in the air like an unwanted fragrance.  Though the doors had been opened only yesterday, it seemed as if the platform itself emitted its own odour as a testament to the events which had unfolded within its four walls.

A rat ran past the control room door, making Kiele shriek.  It was true that now it was just them, the whole place did seem a lot scarier.  Undeterred they continued forward, pushing the vault door open and heading for the spiral staircase.  Ironically enough in the Zone, the stage was actually the lowest point of the whole building.  The layout of the train tracks, still faintly present, had been there for years.  The ground which would usually have held up hundreds of busy passengers, had been lowered to meet the level of the tracks.  The owner had had so many complaints about people falling off the back of the platform that in the end he had decided just to do away with it altogether.  

This time it was Kiele who went first.  She gingerly made her way down the short spiral staircase and exited once again on the stage below.  She walked into the centre of the stage which was actually fairly well lit now.  The lights streamed down upon her and she felt for a second, as if she was playing a part in some musical.  She did a quick little tap jump.  As her feet landed back down it made a thunderous raw, which echoed around the platform far less than it should have done.  

``I was expecting that to be a lot louder,'' she said to Zane.

He looked up and down the walls before exclaiming, ``either they coated the walls with some special sound absorption material, or there's an active filter still running.''  His knowledge of acoustics was pretty good.  ``They'd have to do something, else the music would have sounded awful.''  He had a point, and Kiele was briefly impressed by the boys statement.

``It's kind of amazing how they managed to last so long down here without anyone knowing,'' she said.  Zane nodded.  Though initially she had been less than impressed at Jolie's assignment, she had to admit that now she'd gotten into it, it wasn't all that bad.  ``How do you think he lost?'' she asked.  The tapes for that particular fight had been lost and details from eye witnesses who were interviewed by the G-TEP forces were sketchy at best.  It didn't matter, they were all dead now.  She continued, ``I mean, he had a weapon of unimaginable power.  How could he possibly have lost?''

Zane had been asking himself the same question for many hours now.  It had been claimed that he had simply been bettered by his opponent.  How could that have been?  Did his blade malfunction?  Did he refuse to end the fight?  It didn't make sense.  

``Maybe he just grew tired of it all?'' conjectured Zane.  It wasn't something that Kiele had expected him to say.  For the past forty eight hours, Zane had displayed nothing but the utmost respect for Oken, now he found himself wavering.  He was upset.  Overcome with emotion, yet he couldn't understand why.  Oken should still have been alive.  It hadn't been his time to go.  Why?  Why??!!

``I guess something could have happened to break his blade,'' she offered and to be honest to both of them it seemed the most likely solution.  Zane hadn't noticed but his hands had turned into tight fists and he was staring at the ground.  Kiele was looking back at him.  She'd offered the cause of death to try to calm him down.  He seemed to be taking it pretty hard.  In point of fact, it was Oken's sheer determination to create something against all the odds which Zane admired.  

The two of them stood there in silence a little longer until Zane broke the stillness by saying, ``One day I'll be like Oken.''  Kiele was a little taken aback.  Did he mean he wanted to kill people?  Suddenly she got quite frightened, had she walked into a trap.  There was no one else around, and the thick heavy vault door would mask any screaming that she attempted.  Suddenly the idea of going on this trip seemed not to have been so good, however her father had been exceedingly insistent.

``You mean you want to kill lots of people for no reason?'' she'd said it before she could stop herself.  It was make or break time.  Either he would offer up a reasonable explanation, or he'd turn to her nod his head and exclaim something like, 'and I want to start with YOU!!'

Zane's voice broke her train of thought.  It wasn't at all what she had expected, slow soft and with a hint of sadness.  

``I want to be as knowledgeable as Oken.  Though illegal, he accomplished something amazing.''  Kiele wasn't following.  ``Think about it Kiele.  The governments were so confident that no one would be able to piece everything together, that books on temporal mechanics were still allowed in libraries.''  She continued listening, but started to walk around the room.  Zane continued, ``This man taught himself everything he knew, he researched everything himself and created this weapon.''  He found himself gesturing the giving of a weapon, most likely a long ninja blade to an imaginary recruit.  Had Kiele been closer to him, he would have probably have 'given' it to her instead.

Kiele finally began to understood where he was coming from.  He wasn't a psychopath, he was a driven man.  Even at this early age, Zane was driven by some force to do well.  To break all the boundaries.  ``Do your parents encourage you much?'' she asked.  

``My parents are dead,'' he replied bluntly.  ``Both of them killed in an accident.''  She gasped slightly louder than she had wanted to, possibly as a result of the acoustics of the room.  

``I'm OK Kiele, I've been living in a g-tel for a while now.''  The term g-tel referred to the government run hotels, one of which Zane lived in.  Kiele was beginning to see a whole new side to Zane.  

At first he'd seemed academic, but cocky.  A product of parents with drive, but no vision.  He'd seemed like the kind of guy that new he would get what he wanted through good looks or money, but still had the brains to back it up.  Then he'd seemed quite scary, pushed to the brink of explosion by overbearing parents that forced him to study 24x7.  

Now she saw him for who he really was, a lonely soul, pushing to always better himself to satisfy the parents that he kept within his heart.  The more she thought about it, the more beautiful it seemed.  The memory of his parents was kept alive by striving to do better in everything he did.  Though they could never actually praise him for his work, Zane himself knew when they would approve and when they would disapprove.  

 ``Do you miss them?'' she asked.  What a stupid question, of course he missed them.  She berated herself for asking.  Yet Zane unreservedly answered her query.

``Sometimes.''  He looked up to an imaginary sky.  ``Sometimes I like to think of them looking down on me, seeing everything I say and do.  Like gods.''  He smiled up at the heavens.  ``They give me the power to continue,'' he said quietly, ``everyday, they give me the strength to go on.''

``I lost my mum before I was even born,'' said Kiele.  ``I was an In Vitro child.''  Zane sensed a feeling of embarrassment in her voice.  ``My mother couldn't have children apparently, so my dad decided to have me grown in a lab.''  

She seemed to be distressed by this and so suddenly her temper grew, intensifying more and more each second.  ``Why couldn't he have been content with his memories,'' she shouted.  ``I never wanted to be this....this...freak!''  The tears were genuine.  She had lost much more control than she should have.  Her eyes welling up once more, Zane walk towards her and comforted her as best he could.  

``I don't think you're a freak Kiele,'' he said gently.  ``In fact I think you're a pretty amazing person.''  She looked up at him as he placed his hands on her biceps.  Those tiny biceps, he thought, hardly even enough there to lift a banana.  Kiele wasn't super thin, but she was underweight.  Her father wouldn't let her eat much, citing a multitude of reasons, from weight gain to money, to the fact that she would just turn out plain ugly.  That would never do he had told her.

``You must be the only one,'' she said.  ``My father hates me.  All day long I just have to do his bidding.''  She'd said enough.  She pushed his arms away and turned around.  Her eyes were hurriedly dried and she recomposed herself.  When she spoke again, her voice was completely different.  It seemed totally unnatural and somewhat off-putting to Zane.  It seemed to be something that she had had a fair amount of practise in, to be able to turn her emotions off just like that.

``So did you want to look at anything in particular?'' came the dry unwavering voice of this rock solid young lady.  Zane, still slightly taken aback, attempted to break her shell again.

``You can talk to me you know.''

``About what,'' she said, ``you know Zane it's pretty difficult to talk to someone when there's nothing to talk about.''

He said nothing and noted to himself that this was a subject to steer clear of in the future.  She was scared of her father, that much was sure, but just what had he asked her to do?  It was at that moment that Zane decided he wanted to protect Kiele, with his life if he had to.  Unknowingly he had giving his heart to her.  He had totally fallen in love.  His brain of course hid the emotion.  It was gentlemanly, nay noble, to protect a damsel in distress.  The camouflage was adequate and Zane could continue his exploration of Oken's lair without too much more thought.

The two of them stood in emotional disarray, each unsure of the others state of mind.  It was a kind of a stalemate but at the same time, a pleasant stalemate.  Neither of them wanting to break the silence, they both walked around avoiding each other for at least two minutes before it hit Zane first.  He couldn't take it any more.  

``I'm sorry Kiele,'' he said.  ``I never meant to pry, or to hurt you.''  Even though his mind had told him to drop it, he just had to say something else.  He feared the worst as she turned round to face him, the lighting appeared different to before.  Though bright, it had a definite softness to it.  She made definite eye contact with him.

``It's OK.''

As the two of them stood there a little longer an unfamiliar sound reached their ears, first Zane's and then Kiele's.  It wasn't that the sound itself was unfamiliar, but the context.  Here they were in a disused platform that was used to host underground fighting bouts.    The noise got louder very quickly.  Kiele looked worried, but Zane, quick to display his affection shouted out.  It's probably just a train going down one of the other tunnels.

Instinctively he looked down at his wrist.  He never usually had a watch to look at.  Today was different and he actually felt quite proud.  Why he was looking down at his watch was another question.  It wasn't as if he had memorised the timetables.  He watched the seconds tick by 10:42:58, 10:42:59.  As the clock hit the minute an almighty explosion spewed forth from the wall behind them.  With every ounce of strength Zane threw himself at Kiele and pushed her clear.  

Rocks and debris flew through the air, dancing and play fighting with each other all the way.  Some were large and heavy, pushing the others out of the way with minimal effort, others less so, daintily showering the larger ones with tiny pitter patters.  Ultimately though, they all had one general direction, and that was towards Zane.

Kiele tumbled to the floor, scraping her legs and arms as she did so, her blood augmenting the stains already left by the victims of the Zone.  Her bones were almost to the point of breaking as she hit the cold hard floor beneath her.  She managed to capture a glimpse of Zane through the messy air and tried in desperation to call out to him, something, anything.  In the end a jumbled mess of vocal grunts was all she could muster, but it didn't matter, he wouldn't have been able to hear her anyway.

Rolling on to her side, she caught site of his figure as it became airborne from the blast of pressure emanating from the broken wall.  The wall was cracked in so many places that is was a wonder any of it was still remaining.  Kiele could see Zane's body as it headed towards a pillar, the motion appeared to slow down as she continued watching.  

Had she been at home watching it in a movie, she would be cringing and wincing right now, chewing on popcorn.  His new watch flashed a beam of light across her eyes, with it's Neo-tougheline coating, it was likely to exit the incident relatively unscathed. Her only expression currently was one of horror and shock as the body of a young man hit the pillar and was peppered with debris.  

Still caught in the momentum she was unable to prevent her head slamming into the concrete below her.  The pain was almost unbearable and for a second she was sure she was dead.  Instead of dying her brain decided to take time out, and she blacked out.  As she closed her eyes she was instantly aware of a train hanging through the hole, broken and wrecked, in a sea of rubble.  Only a glimmer of light still breaking through her eyelids, she tried to turn her head to see what had happened to her saviour.  

Her eyes closed and darkness ensued.  Damn her father.

