\chapter{18}
\section{Boyfriend}


His body convulsed and spluttered into life.  Kiele could hear him gasping for air which of course there was now plenty.  She breathed a sigh of relief.  Zane was alive once more.  The monitor returned to its stead plod and for once Kiele was happy to hear the gaps between the beeps.  Jim looked at the now awake young man before him.

``Are you in any pain right now?'' he asked.  Zane thought long and hard.  Obviously he took a little too long because the paramedic repeated he question again, except this time with a little more urgency and with the word Sir at the beginning.  

Zane replied, ``Not any more.''  The voice was weak but Kiele heard it, and it was music to her ears.  It had been the hardest thing in her life to watch a friend lying there, at death's door.  She never wanted to experience it again.  She wanted to hit him for scaring her like that, her feelings towards him drowned in ambivalence.   As he lay there moving, slowly and purposefully, she wondered what would have happened if he had died.  What would her father have said?

Kiele's thoughts were jolted by a large bump in the road which threw all the occupant of the ambulance into the air by a few inches before gravity took over and hoisted them back to the ground.  Zane winced in pain, some of the pieces of rubble were still in his flesh and slapping them with the bed was in no way comfortable.  

``How many times have we told them to remove that bump,'' shouted Marty after hearing the young boy gasp.  ``I'm sorry lad,'' he continued, ``I completely forgot it was there.''  Zane managed a short chuckle.  Though it had been painful, he didn't mind it one bit.  He was alive, but more to the point, so was Kiele, he had saved her.



\thoughtbreak



The hospital doors were flung open with all the drama of a TV show.  The gurney was wheeled though at top speed, doctors and nurses joining the cart and leaving it again as if part of some dance routine.  Occasionally there were words exchanged but other than that the trolley moved in almost complete silence.  Zane was a lot less critical now than he had been and what he needed now more than anything was a good long rest.  Kiele had been placed into a wheelchair and was being pushed along by Jim.  He had supposed to be off shift right now, but instead had opted to take Kiele in and make her comfortable.  

The wheels on the gurney squeaked slightly and that, combined with the moving ceiling tiles made the horizontal boy rather queasy.  It would be very embarrassing to hurl right now, thought Zane, so he closed his eyes and tried to imagine he was somewhere else other than on a gurney moving and shaking.  His mind took him to a ship, to-ing and fro-ing on the waves.  It didn't help at all.  Quietly Zane cursed his minds eye.  Damn this nausea.  

He opened his eyes once more, and turned his head to look at one of the orderlies who was pushing his train.  Keeping an eye on him helped and the nausea drifted away.  

Kiele was more intent on keeping an eye on Zane.  She wanted to be sure he was going to be OK before she left him.  Unfortunately the decision was not hers to make and her wheelchair veered off left whilst the young lad zoomed on straight ahead.  Kiele turned her head too sharply to try to follow her hero and cracked her neck.  She let out a yelp.

``Be careful there young missy,'' said Jim, ``don't want you sustaining any more injuries whilst you're in our care.''  He said it jokingly, but was also deadly serious.  If there was one thing that pained him more than anything else, it was patients who left the hospital in a worse state than when they arrived.  He'd seen it countless times, nurses prescribing the wrong dosage of drugs, doctors misdiagnosing patients, charts getting mixed up.  All these things were still prevalent, despite all the advances in medical care.  Doctors and nurses relied far too heavily on what the computers told them, unable to bring themselves to the realisation that someone had to enter the data initially, and that that was a human process and hence was prone to error.

Jim took her down another hallway and through a further set of double doors.  It looked like the hospital was almost brand new.  It was exceedingly clinical and reeked of the smell of disinfectant.  The walls were coloured depending on the department and right now Kiele was being wheeled down for an MRI scan.  Her other injuries had all been classified as minor, but the bang to the head had been pretty severe.  

The young girl held on tightly to the watch which Kaitlin had given Zane.  As they had neared the hospital, Jim had commented on it, and recommended Kiele keep hold of it for safetys sake.  Apparently there were a number of members of staff with sticky fingers at the hospital.  Jim had developed an affinity for the pair of students and would have hated for anything to upset them further.  She turned the watch over in her hands as the wheels of the chair trundled along.  The more modern hospitals would have had electric chairs, with mini navigation units in them.  The staff at the hospital programmed in the department of destination and the chair would take them there.  It freed up the staff to get on with other matters that required a more human approach.

As she turned the watch over again, the light hit it the back plate and Kiele noticed an inscription.  She wondered if Zane had noticed it yet.  Looking at it more closely she read it;



TO ROB

HAPPY BIRTHDAY



It seemed to Kiele to be a little impersonal, but then it wasn't a gift to her, so why should she care?  The letters were all in capitols in a standard block typeface, none of the swirly calligraphy.  She tried to imagine who Rob could have been.  She hoped he had been a little like Zane, a driven man, like the watch had been passed down from generation to generation.  It seemed almost like a fairy tale idea. 

Truth be told, she didn't know if Rob was old, young, tall, short, happy or sad.  Maybe his birthday had been made by the receiving of this watch.  On the other hand, she supposed it could also have been broken by it.  

Jim started whistling a gay little tune as they wound their way through yet another set of doors.  She'd heard it before somewhere, but couldn't remember exactly when.  It was the kind of tune you hum for an hour and then chronically hate with your entire being.  It would be fun to hear once or twice through, but then it would stick in your head and drive you crazy.  She tried in desperation to think of another song.  Ironically the only one she could think of was 'Colour Me', by C-bex Lunacy.  The words went round in her head, garnished with the imagined sound of distorted guitars punctuating each line with a quintet of strumming.



Colour me stupid, 

Colour me green, 

All I gotta tell you, 

Don't call me Jean. 



You can give me pigtails, 

Colour in my hair, 

All I gotta tell you, 

Is that I don't care. 



I will love you always, 

Till the end of time, 

I preach to the whole world, 

That you are mine.  



Not only was the song similar in annoyance to Jim's little ditty, it also made her think of Zane.  She had to stop thinking about him like that.  Sure he had saved her and everything, but her father would definitely not approve of such a union.  She'd been given strict instructions, and she was not about to disobey him again, not after last time.  The wheelchair stopped and Kiele could see they had halted next to a lift.  

``Would you do the honours?'' asked Jim.  Kiele obliged and pressed the lift call button.  The light illuminated indicating the impending arrival of the carriage.  The button was acutely rounded at the edges and had the symbol of a man shouting, with his hand to his face.  Some bright spark had decided long ago that symbols had to become more human.  In all truth it actually made them much more difficult to decipher and the whole idea had been scrapped a few years later.  The lift stood as a legacy to that dumb idea.

After a few verses of 'Colour Me' the lift arrived and the doors opened accompanied by an audible voice announcing that very fact.  Jim pushed her chair into the carriage and pressed the button for the fourth floor.

``He'll be fine you know,'' comforted Jim.  He wasn't supposed to make such sweeping statements but he could see this young girl was a sensible woman.  She wouldn't hold it against him personally if anything happened to the lad.  She seemed to have far greater things on her mind.  

``I've seen people come out of it in far worse conditions than that,'' he added.  Kiele looked upwards at his smiling face.  A youngish man in his early forties, Jim had still retained his boyish charm.

``Thanks,'' she said.  She meant it too.  It was increasingly difficult to find people with a genuine character in the medical industry.  All too often, doctors and nurses became power crazed zombies, trying to climb the medicinal ladder as fast as they could.  

Though she already knew the answer deep down, she still had to ask, ``When do you think I can go and visit him?''  Jim was hesitant to answer.  The truth was he really didn't know.  The injuries that Zane had sustained had seemed life threatening at the time and he had almost died in the ambulance, but his condition had stabilised.  The truth was, it was just too early to tell.

``Soon I'm sure,'' was his response.  The girl looked back down again at the watch and started playing with it again.  Jim seemed to have quenched her suspicious mind.  He decided to try to break the ice a little, ``He's a pretty hunky kinda guy,'' he said smiling before adding, ``Is he your boyfriend or something?''  Kiele shook her head.  A part of her maybe wanted to say yes, yet deep down she knew the answer was no, it had to be, there was no other way.  Jim noted her response and decided to forgo further questioning.  

The lift reached the third floor and the doors opened.  A small boy with his mother entered the lift.  They walked behind Jim and Kiele and stood there, obviously hoping to get to the fourth floor also.  The little boy pointed at the wheelchair stricken Kiele.  ``Look mommy, she's got wheels.  Can I have some?''  The mother batted his hand down before uttering something about not being so rude.  Kiele smiled, it was the only thing that had brightened her spirit since the accident.  The boy remained quiet for the next few seconds whilst the lift trundled on up to its destination.

The bell rang and the announcer spoke her parable.  Jim pushed Kiele out of the lift and she could hear the young boy, now certain they were out of earshot, shouting, 'mommy mommy, I want wheels too.'  Kiele couldn't hear the response, but she imagined it wasn't particularly positive.  

Jim pushed her a little further before arriving at a small room.  The door said MRI01 in a nice readable font.  Next to the door was a light with a sign saying, do not enter when red light is on, more for patient confidentiality than anything else.  Jim knocked on the door and a muffled 'come in' was the response.  He pushed down on the handle and opened the door.  Inside was a large bed covered with a semicircular strip.  As they entered the strip began to rotate and retracted into one side of the bed.  

``Please remove all items of jewellery and lay down on the bed,'' came the almost robotic instruction.  Kiele took off a metal bangle she had been wearing on her right hand and coupled it with the watch.  As she looked around for some where safe to put it.  Jim held out his hand.  Somehow she felt she could trust him and she tipped the contents of her hand into his.  

``Kiele Matthews?'' asked the robot again.  She acknowledged her name and climbed up onto the bed.  It was a good metre off the ground and it seemed to Jim, who was looking on, to be a fairly poor design.  The poor girl looked pretty scared thought Jim.  He waved at her from across the room and she gave a small nod in response.  She had mentioned something about having a father come meet her, but Jim hadn't seen anyone yet.  Though his shift was over a while ago, he wasn't about to abandon this young girl, who seemed in such desperate need of someone to care.

The machine started up and a small semicircular strip protruded from the right hand side of the bed and followed an arc until it hit the left hand side.  Shortly afterwards there was a humming noise, as the equipment charged the drive heads.  The scared little girl looked around.  How she wished that someone was here to look after her right now.  She was very grateful to Jim, but she would have loved a familiar face to comfort her.  Someone like Zane? her mind suggested.  Damn it!  Why did he keep polluting her thoughts like that?

It wasn't long before the scanner heads started flying back and forth along the semicircular strip.  Though it was protected from flying off by a sheet of thick acrylic, Kiele still closed her eyes in fear.  It had only been a short while ago that she'd witnessed other projectiles flying towards people and she hadn't been too fond of it then either.



\thoughtbreak



Zane wasn't in the operating theatre long.  The surgeons wanted to ensure that none of the debris had punctured vital organs.  Some had been removed by the nurses, but there was yet more that had required surgery.  The surgeons, highly skilled at their craft, sliced and sewed Zane's battered body back together.  Whilst under the anaesthetic Zane dreamt of nothing at all.  He just slept.

