\chapter{50}
\section{Final Decision}


As he walked to the Zone for what would be the last time, his mind was set on completely different things.  For a start he had a love interest now.  He didn't know entirely who Zane had been talking about, but the pretty young blond seemed like a good place to start.  

Oken had never had time for relationships, he had never had time for anyone other than himself.  Or Ruben.  Though he felt bad for thinking it, Ruben was fairly low maintenance.  He didn't have to be anyone different around the man.  Ruben accepted him for who he was, a slightly kooky, rather odd, obsessive warrior.

The walk filled him with more excitement than he had felt carrying Bethany to her first showing, but of course Oken didn't know that.  A part of him wished he had saved the boy and girl.  Kiele and Zane, he had to remember those names.  Deep down inside though, he knew he had made the right decision.  

The ambulance had cleared away the body of Jessie, before Oken had left the second time.  He looked down at his watch, a boring, cheap old model from a local shop.  Maybe after the battle he would go and visit his mother, make amends like he always told himself he would.

The air seemed warmer than before, full of hope, anticipation, new beginnings.  A part of him wanted to skip to the Zone but he quickly came to his senses.  What a stupid idea.  As he crossed the park, the birds twittered and sang sweet songs to him.  He stopped.  Why was he going to the zone again?

The harsh reality of his world fell back into place.  He had to.  If he missed a fight, he'd be found and most likely killed.  Then there was Jay.  In his mind she was the overwhelming reason for going.  Death he could handle, it was simple, you just lay there motionless.  Jay was something different, exciting, a complete unknown.  

In all honesty he was a little concerned that Zane had gotten his details wrong.  Was there really going to be such a beautiful woman there waiting for him?  He smiled to himself.  It was beyond thinking.  It was fantasy.  His life could take on a whole new meaning, he didn't have to be shackled by the years of hatred and pain he had suffered in the war, at the behest of his parents.  

He realised something; he'd hit something big this time.  He had made a choice.  All this time, he had imagined it something predetermined.  All this time he had believed that the events of his past had made him the way he was.  Sure they had shaped him, but it was his choice to decide who he was.  He had made the decision to make Bethany.  He had also made the decision to destroy her.  It had taken a visit from a boy from the future to show him that.

The Zone door was only a few metres away and Oken saw Ruben up ahead.  Zane hadn't given him too many details about his brother, but Oken had been able to fill in most of the blanks himself.  He had caused his friend unimaginable suffering.  Not this time.

``Okie,'' said Ruben in a cheery tone, ``something special planned for tonight?''

``You could say that,'' he said dryly.  Ruben began a little dance of joy singing 'yeh yeh yeh yeh yeh'.  Oken's next words shattered his illusion.  ``It's going to be my final fight.''

Ruben stopped dead and looked at him.  ``Where the hell did this come from?'' he said.

``I had a visit from a friend,'' said Oken.  He changed tact, Ruben was obviously unimpressed by his previous statement. ``Ruben, you ever get the feeling you're meant for something more than this?''

``All the time,'' said Ruben putting an arm round his friends shoulder, ``all the time.  It's called guilt and it's very hard to......''  His sentence was cut short by a swift slap to the back of his head.  He winced in jestful pain.  ``What the hell was that for?''

``I'm serious,'' said Oken.  ``This just isn't what I want any more.'' 

His friend nodded.  ``You don't know how many times, I've thought the same.''  He paused, ``I'll let them know, you want it kept secret I take it?''  Oken nodded.  The last thing he wanted was for news of his final fight to hit the stands.  It always made things so much more difficult.  He had seen it before on countless occasions.

``Thanks Ruben.''

Oken walked into the Zone and the familiar feelings of aggression and anticipation came flooding back.  This time however, they seemed out of character.  He had changed.  The fury that once fuelled him, that he once revelled in, was now an annoyance.  The dancing had commenced and people were busy gyrating their bodies to the whim of the pied piper in the corner of the room.  



\thoughtbreak



Oken hadn't spent any time in the chiller that evening.  Ruben had informed him that his fight would be against Yaz.  Apparently the fighter had requested it himself.  Lucky guy thought Oken.  If I'd have brought Bethany along, you wouldn't have stood a chance.  He breathed deeply.

Looking across the stands he saw the spectators beginning to make their way to their seats.  This fight wasn't going to be easy.  Yaz was good.  Very good.  As he scanned the stands subconsciously, one particular young woman grabbed his attention.  The pretty blonde in the third row from the back, second one in.  Could that be her?  Could that be Jay?

He sat down in the stands, totally uninterested in the fight which had raged below.  Amidst the shouting of the crowds, she seemed to be so peaceful.  Sitting there, writing notes, occasionally sweeping her hair back with her pencil.  Oken was feeling something he never had before.  He was completely infatuated with her.  

Oken hadn't realised that the fight below had finished.  The bouncers were busy dragging the corpses away and Ruben was making his way over to his friend.  

``This is it,'' he said as he approached Oken.  He held out a hand for his friend to shake.  ``Make it a good one.''

Oken smiled.  He didn't even know what that meant any more.  His desire to fuel the crowd with his exploits was well and truly past him.  He had a new goal now, to be happy, to change the world for the better.  He looked across at Jay who was coincidently looking at him.  All of a sudden he became shy and turned away blushing.  What the hell was this feeling?

The retiring man walked past her as he made his way down the stairs to the floor below.  It felt quite alien to him now.  So cold and deathly.  He was glad he hadn't watched the previous fight, judging by the blood, it had been particularly messy.  

He scanned the walls as he took up position on the stage.  The crowds were jumping and cheering now.  Oken had no weapon.  No visible weapon anyway.  Just what was he planning?  Jay was writing feverishly in her notebook.  The screens behind the platform were, currently all centred on him.  He clicked his neck left and then right.

Yaz made his way down on to the platform too.  'Someone's smiling down on you today,' thought Oken.  This was going to be without doubt, the hardest fight he had ever had in his life.  He realised though, that he had something he imagined Yaz didn't; purpose.  He knew he wanted to exit this place alive for a reason.  He had things to do, people to see, history to make.  Did Yaz?

His opponent started twirling his staff in his ritualistic dance.  Oken smiled.  A staff against hand to hand.  This was going to be so interesting.  As long as Oken could stay lightening fast, he stood a chance.  Not a great one, but a chance none the less.

Several of the spectators had started banging on the glass now and a full scale chant was beginning.  Oken couldn't quite make out the words.  It seemed more like a jumble to him.  Yaz couldn't make them out either and the two fighters exchanged confused glances before chuckling to each other.

There was no real animosity between the pair.  Yaz had merely requested the fight to improve his standings.  He wanted to be where Oken was.  Beating the man would put him in a prime position, and to be honest, out of all the things in the world, it was what he wanted more than anything else.

The music began thinning now.  Laying the ground work for the fight ahead.  Oken's mind ran through a few attack-block scenarios.  Fighting a staffed opponent was hard at the best of times, but Yaz was fast and skilful to boot, plus Oken only had the hands God had given him.

As he played through yet another three or four scenarios he almost missed it when the announcer screamed that all important word.

GO!



\thoughtbreak



The staff hurt.  Though Yaz hadn't been as brutal as some of the other fighters, attaching nails, sandpaper or other destructive objects to the ends, the force of the staff hitting his skin was damn painful.  He defended another onslaught from his opponent.  The fight was not going his way.

It wasn't an opinion he shared, alone, Jay was feeling the same way, as were half the spectators.  'Come on Oken, he ain't half the fighter you are' shouted one man behind Jay.  She noted it down, it may come in useful later.  

The older fighter did indeed look out gunned and out classed.  His heart just wasn't in it any more and as Yaz rained down blow after blow, his mind cleared and he prepared himself for the end.  

Then that face came to him.  Kiele.  His daughter.  He had seen her in pain.  She was looking at him, telling him to get up.  Asking around her why her father was such a loser.  'You're just like Jessie' she yelled.  'Isn't he?'  She turned around, apparently asking the opinion of others around her, but there was no one else there.  

Suddenly he was filled with rage, vision or subconscious, he wasn't going to let them be right.  He opened his eyes fully and saw Yaz about to rain down yet another blow on the poor fighters chest.  With expert precision he rolled to the side, trying to keep his feet in the same position as much as possible.  As Yaz turned mid stream, Oken pulled in a leg and fired his foot at the man's shin.

Yaz's left leg flew out from under him with such force that his entire body rotated and fell to the ground.  Yaz shook his head and blinked a few times.  How had Oken done that?  A few moments ago he had been lying on the floor, receiving the beating of a lifetime.  Yaz had been enjoying it so much, and it had been so easy, that he had turned to the crowds and lifted a hand to get them to cheer all the louder.

Now he was on the floor and Oken was all of a sudden on his feet.  He appeared to have some kind of secret weapon, what was it?  Oken looked up at Jay and smiled.  She saw it and looked behind her.  Who was he smiling at?

Yaz picked himself up and Oken allowed him some time to dust himself off.  It was odd how often fighters in the Zone actually did that.  It was almost like a time-out.  Yaz nodded to Oken.  He was ready once more.  At least he thought he was.  

Oken ran towards Yaz and Yaz ran towards Oken.  Yaz pulled back his staff, ready to thwack his opponent with the end, stinging the skin, but Oken was ready for it.  As the staff flew through the air, looking for its target, the target evaded and landed a punch in Yaz's side.

The crowd cheered.  This was turning out better than they had expected.  It had seemed as if Oken was about to roll over and give up, but now they had a real fight on their hands.  Yaz attempted to reign blow after blow onto the body of Oken Brown but his mastery seemed to have fallen on a deaf figure.

Oken was having none of it.  The staff came round once again and this time Oken let it hit his side, tensing his muscles to avoid the pain before looping his arm round it and locking it into place.  In one swift motion he ran up into the air, using Yaz's body as stepping stones, and slid his right foot down the staff, crushing Yaz's fingers as he did and making his opponent lose his most valuable  asset.  

Now it was Oken's turn.  He had never fully appreciated the staff as a weapon, now he could see its benefits.  He teased Yaz a little, slapping him in various parts of his body, whilst the other fighter tried in vain to stem his attacks.  Oken slung the end of the staff into Yaz's left knee and then masterfully spun to do the same to his right.  

Yaz dropped to his knees momentarily, before jumping up to his feet again.  It wasn't going to go down like this.  He was going to defeat Oken.  In truth they were equally matched.  Had Oken been accompanied by Bethany, Yaz wouldn't have stood a chance.  In his current state however, Oken now had a significant advantage.  

Oken's opponent danced around, changing his stance to more of a boxer.  He made a few rudimentary jabs, which Oken blocked with the staff.  Mr Brown looked a little clumsy using the staff, which was the one discipline he had never really trained in.  He was used to swords, but somehow, he hadn't felt the need to bring a weapon into the ring.  This fight was all about destiny.  If he won, he would start a new life, one without violence, one without hate, and hopefully one including Jay.  His mind hadn't even entertained the idea of losing.

With all his strength, Oken spun the staff round once in the air above his head, missing Yaz completely.  The young fighter grinned, but his glee was short lived.  Oken's staff continued through one revolution, before changing angle, like a helicopter rotor blade.  The very tip of the staff swung forward and hit Yaz in the knee again.  He yelled out in pain and the crowd went wild.

Jay, who had been watching Oken's mastery was impressed.  She had expected the fighter to be sporting another new sup-hum device.  Instead he had chosen to fight bare knuckled, something almost unheard of, bar the newbie fights.  He had something to prove.  Something to show to the entire audience.

The young girl was beginning to like Oken more and more.  She had been following his career with greater intensity lately.  There was something about him.  Something different.  He seemed to be fighting for a reason other than winning today.  She liked it.  It was exciting.  Jay was secretly hoping she could get an exclusive interview with him after the fight.  Something inside her told her he was going to win.  

After the impact, Yaz dropped to one side again.  He hadn't kept his guard up.  Oken had struck at the same point twice and now Yaz was paying for it.  As he tried to extend his good leg fully again to bring himself to a standing position, Oken did what Yaz feared most.  The staff spun around to the other side of his body and thwacked against his opposite knee.  The pain was excruciating and once again Yaz was on his knees.  

The crowd were cheering, pushing Oken forward, and for a second, the fighter seemed to be back in the game, forgetting his earlier promise of retirement and retreat.  He turned his body to one side and very quickly let out a swift kick at his opponents chest, but Yaz saw it coming and began to bring his hands in.

It was only now that Oken saw a secret weapon.  Something he had never seen Yaz use before.  In previous bouts, Oken had noticed Yaz wearing some kind of wrist bands.  They looked fairly ordinary, and only now did Oken see what they really were.  They were a safety net, a fighter's last resort.  His hands were now folded back and from his wrist bands protruded two beautifully crafted blades.  So sharp, so thin, that they were almost invisible in the chaos that was the Zone.  However, Oken saw them.  

In almost slow motion he watched as the blades sliced through the air, getting closer and closer to his ankle.  This would be Yaz's first true offence in a while.  'Not today', thought Oken.  He purposefully dropped his foot to the floor, leaving Yaz a little confused and spun round, catching the poor man with a foot in the side of his head.

Yaz closed his eyes and blinked hard.  The pain was getting to him now and he couldn't think clearly.  His only though at that moment was of obscure household objects.  They flashed through his mind one after the other.  Why?  He didn't know, his mind was playing tricks on him.  His mind was damaged.  He couldn't think clearly at all.  It was all over.  His mind and body gave up simultaneously and he slumped to the floor.  

On hitting the hard surface of the floor, he was almost brought to.  In a snap instant his mind reconfigured itself and was once again whole.  He looked up at Oken.  The man was standing proud, but not revelling like he used to.  There was something different about him now.  His shirt ripped in several places, made it look as if he had participated in a bar room brawl.  But there was no blood.  This man was a winner for sure.  Yaz had lost, unequivocally.  His mind went fuzzy once more and the loser lost consciousness. 

The crowds were really jumping now.  Screaming from the tops of their voices.  It was a clear victory.  They knew who they loved, and they loved Oken.  As he bowed to them as a mark of respect, the announcer broke the news that this had been Oken's last fight.  The fighter was a little nervous, no one got a decent reception on leaving the Zone.  His would be no different he was sure.

He closed his eyes.  The noise was deafening, but it wasn't the booing he had expected, it was a subtle cheer.  It seemed as though the crowds were really proud of him.  He looked down at the crumbling figure of Yaz.  He wasn't sorry for winning, but he hoped the Zone wouldn't terminate the loser of the battle, like they always seemed to.  He had liked Yaz, this last fight had been one to remember for sure.  

The Zone's owner rushed down the stairs and walked towards Oken.  He was carrying a bottle of champagne; a thank you for his years of service to the establishment.  Oken smiled and took the bottle.  It was expensive champagne.  Now to start his new life.  He looked up into the spectator stands, and saw the girl he had been fighting for.  She was sat there, writing away, her mind in a completely different place to the others, but she was smiling.

Oken walked away from the fight with his hands held high.  His foot steps felt lighter as he walked across the stone cold killer of a floor.  Dust sprayed from each step and his once jet black shoes, now sported a definite grey look.  As he reached the stairs, the crowds had already begun to pour down onto the platform floor restricting his movement like the viscous ether of time.  Pushing, shoving, pulsating.  They had been privy to a good fight and they had loved it.

As he reached the top of the stairs, Oken took a moment to breathe.  The crowds were running past him now and there were only a few left in the stands.  Of course Jay was still there, writing feverishly in her notebook.  He walked past her without saying a word, stopped and turned.  Her hair looked so soft.  Was she really destined to fall in love with him?  He leaned over so that his mouth was inches from her ear.  Through the harsh sounds of the Zone, only she heard his voice.

``How about an exclusive interview?''





\chapter{51}
\section{Epilogue}



He sat there, reading.  The sun was warm and the beach was beautiful.  Through the waving of the palm trees he occasionally felt a burst of sunlight on his legs, his torso and head being completely in shade.  This was just what he needed.  He picked up the drink from his side and sipped it slowly.  It wasn't alcoholic, just cool, refreshing his senses and filling him with a feeling of relaxation.

The man hadn't taken a holiday in years, previous events had meant he just couldn't afford it.  Now, finally he was able to give his family something they had desperately needed; a nice long vacation, somewhere hot, sunny, and relaxing.

Over in the water two teenagers were splashing each other.  The young boy ran towards the the girl, hands cupped into the water, spraying her as he did so.  She screamed in delight.  'They were having way too much fun,' he thought.  His train of thought was broken by a voice to his left.

``So, did it turn out how you expected?''  The author of the words was a woman in her early forties.  In her youth she had been ferociously beautiful and now?  'Time hadn't stolen anything from her', thought Oken as he looked at his wife.  Jay smiled.

``I guess so,'' said Oken.  ``Truth is, this part was never in the plan.''  He smiled back.  ``I'm just glad it turned out how it did, never mind what was intended to happen.''  He had realised there had been no point in trying to shape the future to be a carbon copy of what he had been told, or even to try to carve specific aspects.  Things would happen how they happened.  Ruben of course would have argued differently, and often did.  'God has a plan for all of us' was his favourite saying.  It wasn't that Oken didn't agree, he just wasn't ready to give up full control of his life just yet.  

The teenagers continued playing in the beautifully clear water in front of him.  The girl had managed to get the boy into a head lock and was now busy dunking his face into the water, amidst much splashing and shouting from her victim.  Oken laughed and pointed to the quarrelling pair.  They seemed to get along so well.

``Way to go Kiele,'' he shouted, his hands amplifying his voice.  Her likeness to the girl he had seen only briefly so many years ago was uncanny.  One in a million chance.  Perhaps not chance, Ruben wouldn't have called it chance.  It was as if that face, that beautiful girl, was meant to be on this planet, no matter what the events the time-frame threw in her way.  'Maybe that's how it really worked,' thought Oken, 'some people are just destined to be here.'  

Even more uncanny was the name of the young boy.  He lifted his head from the water and started objecting.  He yelled back across to Oken ``Why do you always have to take her side Mr Brown?''  The man smiled.  Zane Krecker, who really was a carbon copy of the boy who had changed his future was standing, or rather half drowning in front of him.  The two teenagers had met at school and had instantly fallen in inexplicable love.  Oken shook his head.  He still couldn't quite believe it, but it seemed God really wanted those two to be together.  Had it really been God who had changed the past?  Had his influence changed everything?  In his mind, the face of Ruben nodded emphatically.

He picked up the book and read a few more lines of the story.  He had never been one for fiction, a flight of fancy, he preferred to call it.  He saw little point in indulging oneself into an alternative reality for such a short period of time.  No, if Oken wanted to read, it had to be an entire series of books, something to really get his teeth in to.

The cover of the book was worn, where it had been read multiple times.  Shortly after their marriage, Jay had given Oken a set of books as a gift.  She had said that she hoped they would change his life forever.  They had.  He had become more assertive thought reading the tale, and they had become closer.  

Oken had told her everything about the past, the future, the present.  Everything.  It had been difficult and to this day, he was still unsure whether she treated it as truth, or fiction.  He knew the truth.  It was his legacy.  She had told him to write it all down, one day it would make a fascinating story for the kids.  He had obliged, albeit reluctantly.  

The two teenagers were now running up to him.  The boy first, followed by the girl.  She threw her body forward and rugby tackled him, landing inches from Oken's chair and spraying him and his drink with sand.  He glared at the boy with eyes of fire.

``Why is it always my fault?'' Zane screamed, smiling.  It was a running joke between the pair.  Everything that happened was his fault, never the good, always the bad.  He was happy though.  He had found someone wonderful, someone that he wanted to spend the rest of his life with.  Oken could see that in his eyes.  The pair were truly perfectly matched, much like he and Jay.  

``Because you're always the one doing stupid things,'' Oken said.  It wasn't meant as a malicious comment, and the tone of his voice echoed the sentiment.

Kiele nodded, ``He does have a point Zane.''  The young boy screwed up his face in disgust and his girlfriend released him from her grip.  He got up and dusted himself off, showering Oken and Jay with yet more sand.

``Are you trying to be annoying?'' he asked the boy in jest.

``No dad, it just comes naturally to him.''

They all laughed and Oken realised how good it felt to be called Dad.  Kiele had been a blessing, and not even in disguise.  She had changed the once harsh figure of a man, into a loving father.  His life with Jay had been perfect.  He had returned to university, but this time to teach, his course on temporal mechanics being one of the most popular in the construct.

In the absence of Oken's attack at the Zone, the government hadn't reacted in the same vain.  The G-TEP still existed, and were more ruthless than ever, but overall life was beginning to get better for everyone.

``I'm just going to get a drink,'' said Jay, ``anyone else want one?''

``I'll come with you,'' said Kiele, and the pair walked off towards the resorts bar.  The beach was beautiful and the ability to just pop twenty metres away for a nice cool drink was a definite advantage.

``I'll have another,'' said Oken, lifting the sand filled glass, ``As mine seems to have suffered some kind of accident.''  He looked at the boy who cowered away.  He chuckled again.  ``Lighten up kid.''  

Zane's face changed.  He looked down at Oken and made a face as if he was eating a toffee, a particularly sticky toffee at that.  He was looking for words, but found none.  Eventually he settled for the simplest option.

``Mr. Brown can we talk?''  Suddenly Oken's face changed too, to one of concern, one of a serious nature.

``Sure kid.''

``Mind if we walk and talk?''  Oken smiled and got up out of his chair.  He placed his hands in his pockets and began to walk off in the direction that Zane was already taking.  

The two of them walked in silence for at least ten metres before Zane stopped.  The sun was past its highest point now and had begun its lonely descent across the sky.  The shadows were taught and the hue a subtle red.  Zane looked at the man who he already felt was like a father to him.  His real parents were still alive, and though they loved him greatly, they had been far too preoccupied with his little brother lately.  Zane understood.  He was only twelve, and needed far much more looking after than he ever did.

``Mr. Brown,'' he started.  Oken held up his hand.

He spoke in a slow but caring way, ``Please, Oken.  Call me Oken.''

``Oken,'' the boy started again, ``You know I love your daughter very much.''  The man nodded.  ``And, well, I kinda feel like I want to spend the rest of my life with her.  You know what I mean?''

Oken's expression changed once more.  A Frisbee flew between the pair, narrowly missing Oken's face.  He looked across to see if his daughter had been the culprit.  He looked at her sarcastically, before returning to the boy.  

``Only kinda feel?'' he asked.

``OK,'' said Zane, ``I totally feel it.''  He paused, looking down at his shoes.  ``Man this is so much harder than it ought to be.''

The wise man spoke once more, ``Just go for it kid.''  He already had an inkling of what the boy was going to ask.  Zane and Kiele had been dating for years, and the time seemed to be approaching for them to want to branch off on their own.

``I was hoping that you may possibly consider consenting at the request of mine to perhaps take your daughter's hand in marriage.''  The sentence was long and the boy had paused several times throughout.  Oken looked thoughtful.  He turned back at the boy.  He knew how much he loved Kiele, and he also knew how much his alter ego had been through.  It wasn't even an alter ego, more of a shadow of the boy standing before him.  

``Zane,'' said Oken frankly, ``You'd do anything for her wouldn't you?''

  The boy nodded.  ``I'd die protecting her, you know I would.''  The man nodded slowly, breathing in deeply as he did so.  

``I know you would son,'' he said.  He put his arm round the boy and looked out over the ocean, the sun was bright and it almost burnt his eyes.  He squinted.  ``I know what you're capable of and, I have to say, I can think of no one better to protect my daughter than you.''

Zane looked at Oken talking as he finished his sentence.  Sometimes the boy found it impossible to comprehend how genuine this man really was.  He couldn't quite believe his response.  Though he had been hoping, and praying, that Mr. Brown would say yes, he still didn't quite believe it.  It was going to take a final confirmation.

``Is that a yes?'' he asked slowly and cautiously.

``No,'' said Oken, ``It's not just a yes, it's an irrevocable yes.  I wish you two all the happiness in the world.''  The boy, tears in his eyes hugged the big man.  ``Knock it off,'' he said, ``Go do it already.''

Zane looked up at him, slightly confused.

``If this isn't the perfect place and time to ask a woman to marry you, then I don't know what is.''  The boy smiled and felt around inside his pocket for something.  He suddenly became frantic and Oken lifted a small object from his pocket and placed it in Zane's free hand.  ``I guess you're looking for this,'' he said.

The ring box had fallen out when he had been tackled earlier, and Oken had been quick to disguise it.  He had known Zane was planning to give her a ring, marriage was predictable.  The kid smiled.  ``Thanks,'' he said.

Oken turned and walked away, with Zane staying behind.  When he reached Kiele, she asked him, ``And what were you two talking about?''  Oken sat in his chair and sipped his new drink.

``I think that's something you'd better ask your boyfriend about.'' he said dryly.  Kiele poked out her tongue at her father and walked off in the direction of Zane.  Jay, now lying down again on the reclined chair looked across at her husband, shielding her eyes from the light.  

``So what were you talking about?'' she asked.

Oken looked at the boy who was now knelt down on one knee.  He tapped his wife on the shoulder and pointed at the pair.  ``Say hello to our new son-in-law to be,'' he said.

Jay cooed happily at the proposal taking place.  Kiele suddenly flipped out and flung her arms around Zane's neck before kissing him, almost knocking him over.

``Remember when we were like that?'' she asked.  

A voice came from behind them.  ``Whatd'ya mean when,'' it said gruffly.  It was Ruben.  He threw a book down onto Oken's stomach.  ``I read it,'' he said.

``And?'' asked Oken.

``Yah, it was OK,'' he said, ``thought of a name yet?''

``I was thinking Emblem Divide,'' said Oken.

Ruben nodded slowly before crouching down between the couple.  ``It's OK I guess,'' he said.  The young pair at the waters edge were still locked in embrace.  ``Forgive me for being a little bit of a killjoy, but aren't those two acting even worse than usual?''

``That's because they're now engaged.''  

Ruben slapped Oken on the arm.  ``Congrats my man.''

Oken nodded.

``Oh by the way Okie,'' he said, ``You gotta change the end line.  It really stank.''

``Whatd'ya mean?'' said Oken.  ``I thought it was really good.''

``Yeh right,'' said his friend, ``And then he woke up and realised it had all been a dream.''

