\chapter{39}
\section{Pushed For Time}


He could definitely feel he was getting closer.  The graphs on the scope were looking better, and the power a lot more stable.  It was so frustrating having to work with such limited resources.  They were running out of power cells fast, and if he didn't make a break through soon he was going to be out of luck.  

Mark had gone out on an errand and Zane had been left alone in the house.  Kiele had gone to visit Janus, who was just desperate to hear all about Zane.  Reluctant to have the meeting at her place, and apparently forbidden from bringing Zane, Janus had invited Kiele to visit her alone at her house.

Zane switched on a short cycle of the ORT and waited a few minutes for it to warm up.  He began tapping furiously on the keyboard that sat in front of him.  He pressed the enter key and waited, reaching across and taking a sip from a nearby soda can.  He wasn't particularly enamoured with the taste, it was more that he was just thirsty down in the basement.  It was hot and humid in there, and though Mark had managed to rig up an excellent cooling solution, it still felt stuffy in the small room.

The ORT cycle was nearing completion and Zane switched the scope over to a different range of measurement.  He had to be sure he caught the spike that was pushing the power cycle over its limit.  Blip.  There it was.  He began tapping away again, typing at a speed most would find impossible.  Conducting numerous simulations over the years, Zane had become an accomplished computer user and developer.  He would have been able to pass as a higher than average software engineer at most establishments and his knowledge of hardware was also excellent.  

The spike had been his stopping point for the last week or more.  Now he only had three days of the holiday left before it would be back to school once more.  Though he hadn't managed to spend a great deal of time with Kiele, they had both either been working on assignments or Zane had been working on the blade and Kiele had been visiting friends, they had been together as much as possible.

Their evenings from around 10pm onwards were generally spent in the lounge, sometimes in the company of Mark, watching TV or a good film.  Kiele generally lay across the sofa, her legs across Zane, whilst Mark sat in a completely separate chair.  Apart from Mark, who found the social gatherings difficult, Zane and Kiele enjoyed the evenings.  It was a chance to unwind, and though Kiele had instructed Zane not to do anything that would give away their relationship, he occasionally sneaked in a tickle of her legs or feet, which usually resulted in her slapping his hand and giggling.

For now, Zane was stuck in the basement.  There were no windows to speak of, so trying to gauge the time was tricky without a clock.  Though there were several in the room, Zane always plumbed for his wrist watch, the one from Kaitlin.  It was nearing seven pm.  Kiele should be back shortly and Mark was bound to arrive soon after to make them all dinner.  Or was it Kiele's turn to cook?  He had forgotten.  

He turned his attention back to the bench and the task in hand.  The computer in front of him started graphing various mathematical functions related to the power consumption.  Something was drawing a significant amount of power close to the completion of the ORT cycle, he just needed to figure out what.  He attempted to graph all conceivable possibilities.  The computer beeped at him in annoyance.  Apparently there were not enough system resources to complete the task.  He cursed the wretched thing and dumped his head into his hands.

Zane looked around the basement.  It was brightly lit, with a large shelf dividing it in two.  The shelf had no back to it, it had been designed that way, and light spilled out either side creating an intricate display of shadows.  The shelves were comprised of forty centimetre box shapes into which papers, components, and ornaments had been placed.  It really was one of the most bizarre arrangements of paraphernalia that Zane had ever seen.

The physicist tried to narrow down his simulation scope and ran it again.  A progress bar displayed indicating that it would be complete in one to two thousand years.  Hilarious thought Zane, the computer actually believed it would be useful for that long?  He escaped the process and began to look for another way around the issue.  

Suddenly, he noticed a something pop up in the corner of the screen.  It was a calendar announcement.  He opened it up and was greeted with what appeared to be an encrypted message.  How odd.  Zane knew the computer belonged to Mark, but he also knew that Kiele's father had a completely separate machine which he performed all of his work related tasks on.  This reminder was obviously something personal.  But why encrypt it?  

It peaked his interest and he decided to delve further.  He opened the item and the word Kiele immediately became visible.  The item was about Kiele?  Created by Kiele?  Impossible.  She didn't know the credentials to access the machine.  It required fingerprint identification as well as a passcode.  A simple analysis of the text inside the entry showed it to be a fairly rudimentary encryption algorithm.  It was crackable, but Zane would have to decode it himself.  Curiosity got the better of him and he found himself spending the next thirty minutes trying to crack the code.

After thirty minutes were up and he still hadn't managed to decrypt the entry he gave up.  It was odd to encrypt a simple calendar item.  The only person he could be hiding it from would be Zane.  Kiele never accessed the PC.  It had been created a few weeks before Zane had started living with them, so either Mark was incredibly paranoid, or someone else accessed that PC routinely.

He settled on the paranoid approach and closed the entry.  The light in the basement flickered, which usually indicated that someone was upstairs using the washing unit.  Kiele must be back.  He ran up the stairs and found his sweetheart in the kitchen, munching on an apple.

``Have a good time with Janus?'' he asked, deliberately fishing for information.

``So what if I did,'' she replied slyly.  Giving him a knowing look and slinking away towards the hallway.  Zane jumped forward and grabbed her round the waist.  His warm hands caressing her stomach.  

``Zane,'' she said crossly, ``remember what we said.''

Of course he did, but he didn't fully understand.  Mark seemed like a nice enough guy and Zane was sure he wouldn't have too much of an issue with the pair dating.  On the other hand, he respected Kiele's wishes.  He let go and she continued walking down the hallway looking back just before she reached her room and giving him a smile.



\thoughtbreak



Kiele had enjoyed her afternoon with Janus.  Though the two of them had never really been close, today had felt as if they had known each other for a long time.  They had sat and talked about men, the pitfalls, the perils, and of course the perks.

``So have you kissed yet?'' Janus asked.  Kiele shook her head.  They had come so close the other day, but the stupid end of lecture had ruined the moment.  A part of her wished she had just lurched forward when they had heard the students coming through the doors.  

``He is pretty cute,'' said Janus.  Kiele smiled.  She couldn't deny that.  

``Well, I like to think so,'' said Kiele.  They both laughed.  It was good to talk with someone else her own age again.  It had been a long time since she had been out with friends.  This past week seemed to have propelled her into the forefront of people's minds and she had gotten several invites to attend parties or other social gatherings.

``I'm still looking for a decent guy,'' Janus offered in despair.  ``But all the good ones appear to be taken.''  She lay back on the bed that she and Kiele had been sitting on.  Kiele was still sitting, back against the wall.

``There's got to be some guys that are showing an interest in you right now,'' exclaimed Kiele.  Janus was a pretty brunette, with bright blue eyes and an insatiable amount of energy.  She got carried away easily, and often regretted saying, whatever it was she had just said.  Despite this, she was a good friend and though none of her friends would ever say it to her out loud, she was probably the one person in the class that they all wanted to be most like.

``Hmm,'' said Janus, ``Guys that like me.''  She put on a thinking pose, finger and thumb to chin, finger tapping against the side of her cheek.  ``Guys that like me,'' she continued in a sarcastic tone.  ``Well, there's always Mikael.''  Kiele screwed her face up into a ball.  She wanted to say 'Eeewwww,' but wasn't entirely sure that Janus was joking and really didn't want to offend her.

``You like Mikael?'' she asked tactfully.

``No,'' laughed Janus, ``but I know for a fact he likes me.  He tried to kiss me on a trip a few months back, and he keeps hovering around me in the cafeteria.''

They both laughed.  Mikael was a goof, certainly not boyfriend material, and definitely not husband material.  Both girls were looking for someone they could be in a relationship with for the long haul.  It set them apart from most of the rest of the class who were just out to have a good time and find someone who fit their needs for the time being; a boy who had a car, a boy who had money.

``You haven't told him where to go yet?'' asked Kiele.  Janus' face changed.  It became more sullen and the thinking pose was dropped.  

``I guess I kinda like the attention, even though I'd never go out with him.''  She so desperately wanted to find what it appeared Kiele so obviously had.  A strong confident male to protect her and be with her for the rest of her life.  They seemed like such a great match.  Janus was a little jealous, but she was happy for her new friend.

Many of the girls in the class had boyfriends, either in the same college, or in one of the neighbouring district colleges.  Janus sometimes felt ashamed that she hadn't yet achieved this all important milestone.

``It'll happen when it's right for you,'' Kiele said genuinely.

``Thanks Kiele.''  She believed her too.  Maybe she just wasn't ready for a relationship right now.  It would happen when it was right for her.  She liked that phrase.  They sat there in silence for a few moments before Kiele decided to break the ice.

``Did I tell you I accidentally saw Zane in his underwear the other day?''

Janus shook her head trying to contain laugher.  Janus was happy to have found such a genuine person to talk to as Kiele and Kiele was happy to have found someone she could talk genuinely to.  Kiele recounted the story and the two of them laughed and giggled the afternoon away.  



\thoughtbreak



 ``Friday night, I need us to finish up on the power circuitry,'' said Mark.  ``It would be really nice if we could have a visual test performed by the end of Friday night.''

Zane nodded.  He was in the basement again.  It was beginning to feel like a prison.  Kiele had gone to bed early, exhausted from her visit to Janus'.  That had left Zane and Mark with some time together to work on the device.  He wished he could have some time just to himself, but Mark was beginning to get rather insistent.  Sure Zane wanted to finish the project, but rushing things wasn't going to help anyone.  He had no idea of the deadlines that had been imposed by Ric or more accurately the time-line.  

``I'll do my best,'' he said, ``but I still can't resolve that spike.''  It was true, his earlier attempts in the day had been fruitless.  The simulations he had been running earlier had been incomplete but he had managed to gain some useful information from one of them.

Zane ran up another ORT short cycle to demonstrate the problem to Mark.  The system peaked once more and tripped out, the whirring dying away once more.  

Then something rather unexpected happened.  Mark picked up a nearby soda can, still full, and hurled it towards the shelves.  It hit one of the boxes containing what appeared to be a million tiny components, and they showered the stairs, sounding like a heavy hail storm as they did so.

It was the first time Mark had shown his anger in front of Zane and all of a sudden the boy became a little nervous of the other occupant of the basement.  He was standing now, with his hands resting on the bench breathing deeply.  Mark took two pills from a blister pack, threw them down into his throat and swallowed.  His anger was beginning to run away again, he couldn't let that happen.

``Why did you just run that test?'' asked Mark in a semi-calm fashion.

``To show you the spike,'' replied Zane.

``I'm well aware of the spike.  I don't need you wasting what little power we have on pointless cycle test.''  By the time he had reached the end of the sentence he had become angry once again, his hands as fists punctuating the penultimate and final words by slamming on to the desk.

Zane had had enough.  He wasn't going to be talked to like that.  This was supposed to be a fun project for them.  Mark had never mentioned that there was a deadline, or that he was in competition with anyone.  He couldn't understand the man's anger.  Of course the  Hyper Aggression Disorder had played its part, but it was more than that.  Mark was getting impatient.  

Zane tried to leave the room, walking quickly to the basement.  He was stopped by Mark who had about turned and grabbed hold of his arm.  His grip was unbelievably strong.  Zane had never figured Kiele's father for the strong type.  He had always seemed rather weedy, but his views of him were suddenly changing.

``I'm sorry Zane,'' said Mark.  Zane tugged away from Mark's grip and his captor let go.

``Whatever,'' he replied.  As he walked up the stairs, trying his best to avoid the strewn components, he inevitably stepped on one or two, their little legs breaking under the pressure of a fully grown teenager on them.  As he reached the top of the basement stairs, he took a couple of steps forwards and realised some of the components had gotten their legs stuck in the bottom of his shoe.

He lifted his foot and turned it over, picking the remains of the dead components before throwing them down into the basement.  Let Mark clear it up he thought.  It's his damn mess anyway.  He did the same to the other shoe and walked down the hallway to his room.

Mark stood there in the basement bewildered.  He had never, ever, had anyone walk out on him like that.  Kiele had been conditioned from birth.  She wouldn't have ever back-chatted towards him or gone against his wishes.  He had noticed Zane and hers  relationship getting closer by the day.  His anger was steaming and at that point he wanted to walk up to Zane's room, grab him by the throat and throttle him until he fixed the damned device.  

His mind raced further.  Maybe he could torture Kiele.  That should get the young boy moving.  In his minds eye, he tied her to a chair, scalpel in hand, whilst Zane sat across from them feverishly working away.  When Zane stopped, even for a second, Mark cut.  First her legs, then her arms.  He was smiling.  She would deserve it.  After the device was complete, chances are there would be nothing left of her.  If his mission succeeded they would divide the Emblem, create a new world, one where he hadn't had to look after the brat for seventeen years.

It would be a great day.  Mark's daydream finished with Kiele bleeding out, and Zane crying helplessly by her side, whilst the master picked up the finished device and conquered time.  Funnily enough Ric hadn't entered into his imagination once, even though undoubtedly it would be Ric who would decide when they travelled back in time.  There was no way Ric was going to leave such an important task to Jessie, but Jessie didn't seem to realise it.   He was far too involved in his fantasy where he would become a god among men.

As he began to pick up the hundreds of components, the drug began to take effect and his mind began to clear, once again becoming cold, calculating and cruel.  Time was almost up, time was of the essence.  Time waited for no man.  He had to finish this.  







