\chapter{24}
\section{Unwanted Engagement}


Jolie wasn't Ruben's only visitor that day.  Shortly after she left, there had been someone else requesting an audience with Michael Stapes.  Ironically, though Ruben had welcomed his previous visitor with open arms, even though he had no idea who she was, the next visitor he would have gladly left waiting on the doorstep, had he had the choice.

The door bell had rung and Ruben had walked slowly to the door.  Thanks to his paranoid installations, he already knew who was there and so he took his time.  Eventually he reached the door and pulled back the metal shutter that was placed at eye level.  It was about five by twenty centimetres and revealed a hole of about the same size.  Through it Ruben spied on his visitor.  

``I don't have all day Michael,'' said his visitor coldly.

``What a coincidence,'' started Ruben, ``because thanks to you, I do.''  

It sounded like typical friendly banter, but it was far from it.  Ruben blamed his guest for his confinement and rightly so.  He closed the shutter up and waited a good few minutes.  A rhythmic banging started on the door.  He wasn't going away.  Then there was the sound of something charging.  It started off low in frequency and then increased rapidly.  Suddenly Ruben was overcome with fear.  His company was getting ready to knock down the door by force.  

Ruben dived for the floor as the caller released the force of the sonic ram.  A huge metal cylinder about three feet long ten centimetres across suddenly shot forward and smashed a hole in the door, pretty much in the centre.

``We can do this the hard way or the easy way Michael,'' said the voice as the dust and shards of wood cleared.  Had he been allowed, Ruben would have fitted one of the top of the range security doors, but being under constant watch by the G-TEP made it difficult.  In addition to that, the G-TEP could open any door they wanted at the click of a button anyway.  They held all the keys.

Ruben picked himself up off the floor and dusted off his coat.  There had been no need for that.  Though Ruben wanted to put off the visit for as long as possible, he would have caved eventually.  Now he had a hole in his door, and an even angrier caller standing on his door step.

``There was no need for that Mark, you freakin cretin.'' shouted Ruben.  ``I'm not going to disobey the G-TEP am I?''  He slowly walked towards the door.

``You refused me entry Michael, what choice did I have?''  He put his hand through the door and released the lock.  Ruben had chosen an elderly looking lock, highly effective on houses fifty years ago. Now it offered the same level of security as locking a bike up to a thief.  Very little.  The door swung open and swept much of the debris along with it.  

``See, I even cleaned up after myself,'' said the cretin.  Ruben left him where he stood and walked into the lounge.  It was darker in there and he felt more comfortable.  As comfortable as he could with Mark in the room anyway.  

Mark followed him into the the lounge and sat down in a chair.  The room was distinctly different to the kitchen he had shared with the pretty Jolie earlier.  There were mountains of books in every corner and a small desk lamp in one corner was the only illumination in the entire room.  Mark picked up one of the books.  It was a fiction book.  A story.  He threw it across the room.  Ruben winced as it hit another stack of literature and the entire tower toppled over.  

``I'm not due for another visit for three weeks,'' said Ruben.  ``Why the heck have you decided to grace me with your presence this time?''  He always managed to sound infinitely more intelligent when Mark was around.  He tried extra hard so as not to look foolish in front of his enemy.

Mark remained quiet.  He enjoyed toying with the dark skinned man.  He hated him after all.  All that he once stood for, all that he once did, Mark hated him for it all.  That and the fact that Ruben's skin wasn't the same colour as his.  Ruben believed in God too.  In short, there was nothing about this man that Mark liked.  The only thing he admired was his ability to keep a secret for so long.  Yet the secret would soon be voiced, then there would be nothing to admire at all.

He picked up another book hurled it across the room, but this time aimed for the log fire which was burning listlessly on one side of room.  Ruben had it too good here thought Mark.  He deserved a slap in the face every now and then.  If Mark had had his way the man would have been dead a long time ago.  However they had wanted to keep him alive.  His employers.  The G-TEP.

Ruben had never revealed the location of Oken's weapons.  They had tried desperately to make him talk, but Ruben had stayed quiet for years, preserving the integrity and honour of his friend by keeping safe the one thing he held precious besides Jay; his beloved Bethany.   It was the only way Ruben could think of to keep him going.  He held  a small part of his friend, locked away safely.

Had the G-TEP possessed temporal weapons themselves they could have found the device.  It would still have taken months of work, tracing back Oken's life, but they would have gotten there in the end.  Oken had been careful to shield the device as much as possible.  The G-TEP had seen pockets of temporal energy cropping up, but they had no idea where or who was making them.  That was until Jessie had turned up that is.  Jessie had put the final piece in the puzzle and made Ric a very happy man indeed.

The G-TEP had vowed never to use temporal weapons to carry out their duties.  The global commander had built the force on this founding principal.  Though they were brutal in nature, the sheer hypocrisy of using temporal weapons would go against everything they stood for, it would make them as bad as the enemy.  

Anything even remotely suspicious was checked into, both inside the headquarters and out.  Devices were installed in employees homes and routine scans were initiated every three weeks to test for the presence of any temporal residue.

Mark picked up another book and hurled it across the room, aiming for another stack and successfully knocking it and about ten others over.  He understood that this was all Ruben had now.  Books.  His life was lived through fiction.  Mark had taken everything else away.  He was proud of his achievement.  This man was just a living shell, broken and empty.

Mark had heard something about an accident earlier involving his daughter, but that could wait.  She wasn't dead, that was the main thing.  The boy he needed so desperately wasn't dead either, that was also a plus, training the little witch again for a different target would have taken too much time, time he didn't have.  He would stop by the hospital later and play the loving father.  Until then this was the most important thing on his list of things to do today.

As Mark picked up the next book, Ruben, who had been pacing the room behind him, grabbed his arm.

``Stop this,'' he said.  ``Just tell me why you're here.''

Mark looked thoughtful and nodded faintly.  ``OK,'' he said finally, ``Seems you haven't been entirely truthful with us Michael.''

Ruben thought hard, what was he talking about?  He hadn't been there earlier in the day.  How could he have known what he said to Jolie?  His mind raced.  Had he said something?  Left some evidence somewhere?  

Mark allowed him a moment or two to think.  ``She was quite a pretty lady you met with,'' he said.  Ruben said nothing but just stood there.  He sidled his way round the sofa to a chair and sat down.    

The G-TEP had had their eye on Jolie for a while.  She had proved to be a most useful resource.  Her 'research' was largely what their continuing investigation had been based on.  It wasn't that she was more capable than the G-TEP, but she had put the time and effort into something she was passionate about and had gotten good results.  Why redo work which had already been done?  

The G-TEP had used much of her writings in their reports.  It wasn't underhanded in anyway, they were just using the resources made available to them.  They had kept her under surveillance for several years and though the supreme court order had expired, the G-TEP still maintained a close watch of her.  She was useful.  

Ruben hadn't known, but counter to their strong stance against the use of surveillance, they had installed it into Ruben's house and had been watching him 24x7 for years.  Mark had been assigned the case, and had been hoping that one day, just one day, Ruben would slip up.  He had.

``You were watching me?'' asked Ruben quietly.

``Yes''

``After that whole song and dance about privacy and rights, after I begged you to install it to clear my name and you refused?''  Ruben was getting angry now.  His whole trust of the organisation which he had come to accept, almost respect in a weird way, had just been torn down before his very eyes.

``Yes,'' said Mark, ``the whole time.''  He threw the book that was still in his hand.  ``The whole damn time.''  He was starting to get a little angry now.  ``Do you know how boring it was watching your sad pathetic life?  Do you know how many times I just wanted to come over here and end it for you?''  

It had crossed Mark's mind on multiple occasions, but he still needed Ruben.  Only this man knew where the blade was; sweet Bethany, nameless to her seeker, and her power.  Power that Mark desperately wanted for himself.  It was true he'd had to make some compromises over the years, getting a senior officer involved in his plan, but Ric had seemed as passionate about it as he was.

Mark continued, ``Today you made the biggest mistake of your life.  You let me know that you knew where it was.  The blade of course.''  Ruben shuddered.  Mark knew.  Mark knew everything.  All except the final detail.  The location of Oken's creation.  

``I'm not going to tell you anything,'' he said resolutely.  He was standing firm in his mind now.  Mark could do what he wanted, torture him, he'd survived that, berate him, that was a regular occurrence anyway.  Kill him?  Sure why not.  If it pained him so much to let Ruben live, he'd die for his cause, for his friends.  

Mark sat there calmly.  It had all been worth it.  The last seventeen years had all been worth it.  He knew he was finally going to get his hands on the one things he wanted more than anything else, the power was going to be his.  With the boy his slave of daughter was securing, he'd soon be able to turn the weapon into a real device of power.  It had been said there hadn't been a time machine built in over twenty three years.  The G-TEP held a special celebration ceremony every year to mark the occasion.  He was about to break that streak.  

Mark laughed.  It was all coming together.  ``So if you're not going to tell me anything,'' he said, ``I suppose I'd better provide you with an incentive.''

Ruben seemed insulted.  ``There's nothing you can offer me that will make me talk.''

``Oh, I beg to differ little man,'' he said ironically.  Ruben was far from little but Mark enjoyed cutting him down to size verbally.  Ruben wasn't the brightest of the bunch, but he had learnt so much from his years of reading.  ``In fact I think I have just the thing for you.''  

Mark pulled out an e-ink screen.  It had gotten slightly crumpled in his pocket, yet now it sat there in his hand, a testament to his seriousness and dedication to his cause.  He put it down on the table face down.  It's glow could be seen emanating from underneath.  In the dark room it let out a nice greeny blue aura on the table surrounding it.

Ruben stood there still.  He didn't want to move.  Mark couldn't have anything on that piece of paper that he would want.  It was ridiculous to think he could be bought so easily.  Yet something at the back of his mind pushed him forward.  He walked over to the table and looking at the intruder picked up his bribe and turned it over.  

It was a picture of a young girl.  She was pretty, thought Ruben.  Her blonde hair flowed unbounded around her face.  She must have been around seventeen thought the titan.  Suddenly he was snapped from his thoughts as a book hit him squarely in the forehead.  Ruben reeled and almost toppled over the table.  He righted himself and shook his head.

``Stop gawking at my daughter you pervert'' shouted Mark.  He was having the time of his life.  Never before had he been so certain of an outcome.  He could do what he wanted and he would still win.  He could have toyed with this man all day, but there was the matter of business to attend to.

``Your daughter?'' said Ruben in disbelief.  ``So what are you offering me, her hand in marriage?''  He threw the paper back at Mark.  ``Not interested pal, I'm not as sick as perhaps you think I am.''

``I'm not offering her to you.  I'm offering you the opportunity to save her.''

The words had been playing in his head for the last five minutes and Mark was satisfied with how they had been voiced.  Menacing, yet calm, almost calculating.  Ruben suddenly felt sick to the stomach.  What kind of sick game was he playing at?  He had known Mark a long time, but he had never displayed any behaviour that would suggest he was capable of murdering his own daughter.

Ruben had to remain strong, Mark would never want to kill his own daughter, he was evil, but not that evil.  He had to call his bluff.  Ruben wasn't going to give in without a fight.  

The fire had eaten through the book now, and the cover flared, a result of the lacquer used in the printing process.  As the flames consumed the books shield, Ruben looked down at Mark, his own defences being routinely punctured.  

Mark really was a pitiful little weasel.  Though he acted big and tough, Ruben could have flattened his face in one punch.  The only reason he held back was the fear of the G-TEP and of course, his eternal well being.

Through gritted teeth Ruben hissed, ``Why would I want to save your daughter?  I have no interest in her whatsoever.  If she's anything like you, the world would be better off without her anyway.''

``Pretty though, isn't she?'' his nemesis chirped.

``Appearances can be deceptive.''

Mark looked thoughtful again, before bursting out,  ``Don't you just love it when a plan comes together?'' He paced a few steps in a circle, ``I've been planning this since your incarceration in this dump.''  Ruben suddenly felt worried and awkward.  Though he wasn't known for his mental capacity, Mark could be inherently devious when he wanted to be.  

``What are you talking about?'' asked Ruben, though he was sure he didn't really want to know.

``Her name's Kiele,'' he said wistfully, ``she really is beautiful, don't you think?''  There was no denying it, but at this point Ruben didn't want to give Mark anything, not an inch, not even a millimetre.  ``She should be,'' he continued, ``her mother was gorgeous.''

Ruben couldn't quite make the connection that Mark was alluding to.  Then all of a sudden it fit, all of the pieces fit.  He couldn't have?  It would explain a lot, but surely even he wasn't that evil, was he?  Ruben's expression must have changed because Mark now smiled.  

``You know now right?'' he asked, ``You know the big secret.  Kiele's mother is Jay.''  He continued on whilst Ruben turned as white as a sheet.  The man looked back down at the sheet, the similarities were all there, he just hadn't noticed until now.  ``Now who could I pick as a suitable father?'' he began.  

``You're insane, you're freakin insane.''  Ruben started towards Mark, pointing and waving as he did.  He knocked over several of his own book stacks.  ``Do you seriously expect me to believe this?''  

Mark continued, ignoring Ruben's ranting.  ``A father who was strong of heart, whatever that means.''  He was enjoying this far too much.  It had been worth the sacrifice.  The seventeen years of caring for that brat.  She had been trouble from the start and though he had protected her for her entire life, he had only done it so she could become her purpose, a bargaining chip in his sick quest for power.  

``A father who you knew rather well I think.''  He turned to Ruben.  ``His name was Oken, Oken Brown.  Ring any bells.''  He chuckled.

Ruben could take it no longer.  He threw himself across the arm of the chair, aiming for Mark's neck with his left hand.  He pined the squirming weasel down like a vet about to perform a procedure on an injured animal.  He drew back his other arm, made a fist and punched his enemy squarely in the face.  Ruben didn't even feel the pain as his bones crunched against the skin and cartilage of Mark's nose.  The animal let out a yelp as his attacker withdrew from the procedure and  stood over his prey.  

Mark touched his hand to his nose and felt the blood.  It seeped out in small bursts, covering his hand and his shirt.  Ruben threw him a rag, which had been hanging over the back of one of his chairs.  He neglected to tell Mark that Benzo used it as his sleeping blanket.  The patient held the rag to the base of his nose.  Mark smiled, but his expression was invisible, covered by Benzo's sleepy blanket.

``I guess I deserved that one,'' Mark said.  ``Now let's talk business.  Surely you're not going to let their child die.  You swore to protect that which Oken held dear didn't you?  What do you think he'd hold closer to his heart, a temporal weapon or his own flesh and blood?''

Knowing what had happened in Oken's past, Ruben knew exactly what Oken's views on family were.  He would have protected his family above anything else, risking everything.  It had been one of the things that Ruben had admired most about his friend.  Oken had taken on board the short comings of his own family and had turned them into strengths, the strength to protect his friends, to keep them safe at any cost.

Ruben began thinking.  Was the temporal weapon a justified cost to save this poor girl's life?  What kind of life had she been subjected to?  How could he know she was really their child?  That seemed like a good starting place.  He'd work backwards from there.

``How can I tell that she really is their child?'' he said slyly.  Mark gave him a video and some documents on an e-ink screen.  It couldn't be faked.  The evidence was irrefutable.  This Kiele girl was Jay and Oken's child, there was no doubt.

Ruben walked over to one of the chairs and sat down, nursing a now slightly sore fist.  Mark looked over at him and stared, his eyes boring into the once soft skin of a broken man.  ``We could set up a little rendezvous for you two if you like, a nice candle lit dinner.'' 

``Cut it out Jessie,'' snapped back Ruben, ``Just, cut it out.''  He hadn't been thinking properly and had blurted out Mark's original name.  Mark was Jessie, the inconsiderate idiot that had been berated by Oken all those years ago.  In his head he had sworn revenge but it hadn't stopped at getting Oken and his girlfriend killed.  Jessie had taken things to a whole new level.  

``I never gave you permission to use that name,'' barked Jessie.  ``Keep your cool retard.''

Ruben's temper began to flare, but this time he settled for questioning him instead.

``How could you do this?'' asked Ruben.

``Everyone has a child for a reason Rubie,'' started Jessie, ``Some want a continuation of their legacy, others want to change the world from within.''  He picked up another book and tossed it into the fire.  It raged once more and Jessie continued, ``Some just want a guardian in their old age.  Me?'' he smiled evilly, ``I wanted a beautiful little bargaining chip.''





