\chapter{36}
\section{Haito's Advice}


It was fun to watch him, she thought.  Especially as he had no idea she was there.  There he sat reading in silence, making notes and occasionally wryly smiling to himself.  A part of her couldn't quite understand how he could find irony and humour in such dry subject matter.  Physics and the like had never interested her much.  At school it had been her least favourite subject.

She could feel his warmth each time she looked at him, yet he was unaware that she was there secretly stealing his energy with her eyes.  They hadn't known each other that long, but she definitely felt a connection to this strong willed young man.  He seemed so determined in everything he did, so driven.  She bit her lip as she looked on, totally infatuated with his presence.  

It was almost surreal to her.  She hadn't ever felt this way before about anyone.  OK, she wasn't old, there had been several guys she had been interested in.  None of them had ever reciprocated any of her feelings though.  Perhaps it was a good thing, perhaps her destiny had led her to him.

She didn't really believe in fate or destiny.  Each person made their own future, she was certain of that.  Someone had once opposed her opinion in a class discussion, 'What if person X comes and does something to you, entirely unprovoked?' they had asked.  She had replied that then it was how you reacted to that event that determined your future, not the event itself.  The comeback had been simple and had thrown her, 'What if person X kills you?'  It had been a good argument, but she had cleverly retorted 'then you don't have a future to decide.'

It had been a very clever comeback and the owner of the question had shrunk back in fear.  She had received a round of applause for her annihilation of her opponents argument.  It still stuck out as one of her defining moments.  She wasn't argumentative by nature, but she did enjoy a good debate about a controversial topic.  It kept her mind fresh, kept her writing new and exciting.

Jay continued to look through the piles of books at Oken.  It appeared as if he was multi-tasking.  An odd concept for a man to be putting into practice, she thought.  He was quite clearly performing his daily duties, but also taking some time out to read a book.  It seemed as if he was reading one page at a time, before going off and either collecting or replacing books.  Clever man, she thought.  She had always wondered how he managed to get so much reading done.  

She walked along the row of books she was currently using for cover.  Should she go greet him?  She decided against it.  Another time may be.  It was true she had been in the area, but the library hadn't originally been on her list of places to visit, and had she not met Oken, she most certainly wouldn't have been there.  Her studies kept her more than busy, if she wanted to pass this journalism course, she'd have to work very hard indeed.

Oken was back at his desk again feverishly scribbling something out.  She giggled quietly as he frustratingly screwed up his face in anger at an obvious mistake.  She turned away and felt her heart.  It was beating.  It was beating fast.  Had she really fallen for this man so quickly?  Was love at first sight really a possibility?  OK, so it hadn't been first sight, but she hadn't known Oken for very long, yet she could almost see their future together.  A child, a girl would be nice and beautiful summers by the beach.

As she turned back, one of the books in front of her vanished, and Oken's face was visible.  She'd been so wrapped up in her own thoughts that she hadn't noticed him rising from his chair and walking over towards her.  She had of course been looking in entirely the wrong direction, but it was no excuse, her mind told her.  She should have been keeping better watch.

She gave him a dazzling smile and walked to the end of the stack and turned to face Oken.  She walked up to him and smiled once more.

``Thought I'd come and say hello,'' she said and continued, ``as I was in the area.''  Oken didn't know what to do and his expression said it all.  He'd never had anyone come and visit him at work before,  let alone someone he'd just been thinking about.



\thoughtbreak



She had left earlier than she had wanted, but somehow it had just felt like the right time to go.  Oken was obviously busy, and she had a ton of work to do.  As she walked out of the library she stopped to pick up a leaflet from the counter containing coupons for a free meal.  She studied the coupon carefully, making sure there were no hidden terms and conditions.  Once she was satisfied that the coupon was kosher, she pocketed it and walked through the doors to the outside.

The wind was far cooler when she exited the library to when she had entered.  It wasn't exactly cold, but it wasn't warm either.  Fresh would be the most accurate description, thought Jay.  As the breeze danced past her, it took with it several leaves, which had fallen from the ageing sycamore trees lining the courtyard of the library.

It was an impressive building.  Built shortly after the war, it was the most exuberant piece of architecture for miles around.  It housed almost all of the classical books, i.e. those with paper and pages, along with the more recent e-ink editions and those purely in electronic format.  It was almost square in footprint, encompassing a small closed courtyard in the middle, which users of the library could utilise to sit down and read their chosen literature, in a setting of pure inspiration.

The walls looked so straight and sharp in the morning sunlight.  She'd had always found the morning sun to be far less forgiving than the evening.  It was true for faces, buildings, anything really. She much preferred the light of dusk.  It smoothed everything over, made things more bearable.  It softened reality to a point where almost anything was acceptable.

Jay continued walking and looked down at the coupons she had picked up, still in hand.  She could go eat and carry on with her latest assignment, she thought.  It sounded like a reasonable plan.  She rarely treated herself to much, especially in the way of food.  She cared about her figure, maybe a little too much,  The food establishment mentioned on the coupon was only a short distance away, 'Haito's Sandwich Bar'.  

As she continued moronically putting one foot in front of the other, a certain man entered her thoughts.  Of course it was the same man she had visited earlier who was now re-entering the fresh mind of a confused young woman.  She couldn't help it.  She smiled as she thought of him and his mannerisms.  He had looked so cute beavering away at his work, whilst sneaking a few pages of a good book at the same time.

Jay hadn't meant to disturb him.  She hadn't meant to be seen at all.  If she had concentrated on keeping watch like she had been supposed to, it would never have happened.  Of course now she had no idea how Oken had felt about her visit.  Had it freaked him out that the girl he'd met only recently was now stalking him at his work place? He had seemed a little surprised when she had appeared, maybe even a little uncomfortable.  She berated herself, of course he would feel uncomfortable.  How would she feel if whilst she was studying at university, he turned up outside one of her lectures and beckoned her to leave the class?  Uncomfortable.

Though she had justified it in her mind, it didn't make it easier.  She was thinking more and more about him with each passing moment.  Her mind was so entwined with thoughts of Oken that she didn't notice a particularly bad crack in the pavement.  As her foot tried to pass it, it was brought to rest and she tripped forward.  She didn't fall, but it was enough to reset her thoughts.

If she kissed him, she knew it would be game over.  He had already ensnared most of her heart, but if they kissed, she knew she would fall into his heart forever.  It felt so crazy to be thinking of him so deeply.  She wasn't even sure if he fully reciprocated her feelings but they were just so damn strong.

She felt as is she was floating in the middle of the ocean.  There was no land anywhere to be seen and the final outcome was inevitable.  She was going to drown.  Drown in feeling for Oken.  Yet she was still resisting, kicking and flailing her arms like a little child.  She believed in love at fist sight, but she had never believed it would happen to her, that it would be right for her.  She knew the water was waiting to engulf her, to take away any last shred of sanity from her.  She was falling for him, she was falling for him hard.

As she kicked and screamed in the ocean that was so desperately trying to take her forever, she reached the sandwich bar.  The letters on the sign above weren't particularly exciting, an over used rounded typeface adorning the majority.  Jay had always hated that typeface and refused to use it completely.  It looked like someone had created it whilst drugged up on happy pills, or whilst looking at rainbows.  It made her sick.  The last word was in a completely different font, giving the sign an edge, but coincidentally also looking shoddy and cheap.

The innards of the place looked a little better and as Jay opened he door, she was met with a smell of fresh bread, baguettes, cheese, bacon, all rolled into one glorious odour of baked goods.  The proprietor who had been short of customers this morning welcomed her in with a smile, waving her closer to the desk.

He was a strange little man, not overly short, but short enough that he looked a little stumpy and definitely of Eastern origin.  He was still smiling as she reached the counter.  She looked around to find only two other people in the establishment.  It was small and cosy, but not as buzzing as she would have expected by the number of coupons which had been adorning the library shelf.

``What can I get for you this morning,'' he said cheerily in a thick accent.  He stuck his head forward, like a pigeon, waiting for an answer from the pretty young woman who had just entered his store.

``I have a coupon,'' she said and robotically lifted her arm and waggled it in his view.  Had she kept it by her side, he wouldn't have been able to see it over the counter, he was only short after all.  

The man sighed.  Another coupon.  That's all most people ever showed him these days.  He had created them as a way to drum up more business, but these days people had so little, that they just took the free food and then went back to going to the cheapest place they could find.  Haito couldn't compete with the large outlet chains.  He bought in bulk, but they bought in far greater volumes.  Their monthly purchase would have kept him going for five years.

He smiled at the young woman, it wasn't her fault after all.  He had decided to give the coupon idea a try.

``What would you like?'' he asked and gestured to the electronic board above him, playing endless commercials for his new meaty combo on the left, and a cycling set of prices on the right.  She looked up and waited for something to catch her eye.  It took several rounds of the same prices before she realised that nothing really sprang out at her.  She looked at Haito.  He grinned at her expectantly and nodded several times for her to continue.  Poor little guy, she thought.  She looked back up at the menu.  Bacon and cheese sounded nice enough.

``One bacon and cheese sandwich,'' she said.  

``Oh,'' he replied, ``You make good choice.''  He almost skipped off to the kitchen, and Jay could hear him humming away to himself as he cooked her bacon.

She went and sat down at a table near to the window.  They were tinted and though the morning sun from outside filled the sandwich bar, it did not overpower the subtle feeling of Haito's establishment.  She placed her bag down on the floor below her, removing her e-pad and pen before she did so.  As she waited for her sandwich, she began to think about her assignment.  

She looked down at the title of the task she had scribbled down in haste the day before.  'Profile a leading member of the Emblem government'.  It had to be the most boring topic that she had ever been tasked to write about.  She enjoyed writing about politics sometimes, but had no desire to delve into the personal lives of leading politicians.  That held no interest to her whatsoever.

She scribbled a few names down and her mind drifted to the comings and goings of the street outside.  It was getting busier in the town now.  Some people walked at furious speeds, eager to go about their daily business, mostly wearing suits she noted.  Others, in less smart attire, were sauntering around, flitting from shop to shop carrying sometimes one, sometimes two, sometimes fifteen bags.  

Haito brought over her meal and placed it on the table.  She thanked him genuinely and handed him the coupon.

``No,'' he said, ``You keep it.  Maybe you come back another time?  Tell your friends about good food.''  He was serious.  Haito believed in the power of word of mouth.  It was how his establishment had grown in the early days and his faith was still strong that it would grow again.  He didn't want to own a large chain of sandwich bars, he just wanted the little one he had to do well.

He sat down at the table opposite Jay.  Part of her felt awkward, she didn't even know the guy.  He was probably in his early fifties, hair neatly shaven down to a mere stubble, and a small beard.  He was definitely of eastern origin, but Jay couldn't tell exactly where.

Haito's sandwich bar was about the size of a typical lounge.  There was a bar running round two of the sides, which were constructed from glass.  The shop itself was situated on the corner of an intersection in the pedestrianised area.  Out of the other two walls in the building, one was almost bare, containing only a drinks machine, and the other housed Haito's till, and pre-made sandwich display cabinet.  The cabinet itself was well lit and always stocked well.  Another of Haito's beliefs.  If the shop looks full of food, it will be full of customers.  

``You come to library often?'' he asked her?

She shook her head.  How had he known she had been to the library, had the weird little man been watching her.  Then she remembered where the coupon had come from.  Haito had guessed she had gotten it from the library.  He had been right.

Jay bit into the sandwich, the temperature was just right, not burning hot, but not too cold either.  The cheese was melted right through and the bacon particularly salty.  It tasted delicious.  So delicious in fact she considered attempting to pay for the sandwich.  She looked at the little man sat watching her with his hands on his lap smiling.  She smiled back.

``Sss good yes?'' he asked.

``Mmmm, very,'' she said, having to scoop a stray piece of cheese back into her mouth.  It was embarrassing, but strangely in front of Haito, she didn't mind.  

``I am Haito,'' he announced.  ``This is my sandwich bar.''  He extended a hand towards her for shaking.  She placed her sandwich back down on the plate and shook his hand.

``Nice to meet you Haito, I'm Jay.''

``Hai,'' he acknowledged.

The two of them sat there in silence.  It wasn't uncomfortable, just silent.  Haito looked out of the window at the passers-by.  He had hoped that more may pop in on their way to work, but alas, today had been a particularly quiet day so far.

Jay liked Haito.  He was an instantly likeable character and so genuine.  Jay could tell just by looking at him that there wasn't a bad bone in him.  He lived to serve his customers, never charging more than he needed to live.  It wasn't money that drove him, but being a friend, being in service to the people.

``Mr Haito?'' she asked.

``Just Haito,'' he replied.

``Do you believe in love at first sight?''

Haito chuckled and pointed towards Jay and then himself.  Jay smiled and chuckled too.

``No no no,'' she said, ``Not you I'm afraid.''

Haito playfully mopped his brow.  ``I get worried for second,'' he said, ``Mrs Haito?  Very jealous lady.''  He laughed again.  It sounded a very fake laugh, but Jay could tell that it was in fact entirely genuine.  She laughed too.  

When he had finished, Haito looked at her sincerely and spoke.  ``I remember my mother once tell me that falling in love at first sight?  Very rare and precious thing.  Two souls, bound by destiny, riding off into sunset.''  He gestured the riding off into the sunset with his hand.  ``She say, if their love is strong, that the gods will not be kind to anyone who break their love for each other.''

Jay smiled whilst she continued her sandwich, she had liked Haito's words.  They had filled her with mystery.  Two souls, bound by destiny.  It sounded so romantic.  Haito was looking off into the distance, remembering times gone by, grinning to himself.

``Did you and Mrs Haito?'' she nodded indicating a question.  Haito again laughed out loud.  

``Good heaven no,'' he said, ``I had to beg her to even go on date with me.''  His accent was strong and the word 'date' seemed oddly inappropriate for him.  She hadn't expected him to utilise it in his vocabulary.  The two of them laughed again.  

He leaned across the table and put one of his hands on hers.  ``Miss Jay,'' he began, ``You in love at first sight?''

She was a little taken aback by his question and unfortunately she had just taken another bite of the most delicious sandwich she had ever tasted.  She started to chew quickly and motion with her hands that she was going as fast as she could.  Haito lifted his hand and motioned for her to slow down.  She finished her mouthful and swallowed hard.

``I think I may be,'' she said finally.

``Oh,'' said the little man, ``something you just feel inside, yes?''  As he said the word inside he drew his hands to his heart and beat his chest twice.  She nodded.

``You are very lucky Miss Jay.  Very special thing is love, very rare thing is love first sight.''

As he finished his sentence a customer walked in and Haito turned round.  He seemed surprised to see someone else in his store and hurried off the chair.  As he was about to leave, he turned to Jay and placing his hand on hers again said, ``I wish you all happiness in the world.''

With that the little man was gone back behind the counter asking his next customer what they would be wanting in their sandwich.  Jay sat there finishing up her sandwich.  She had enjoyed talking to Haito.  He had been a breath of fresh air compared to her normal partners of conversation.  In a way he reminded her of Oken, mysterious and yet, entirely intoxicating.





