\chapter{31}
\section{}
Accomplished  

Rubens nostrils were flaring as he thundered towards the terrorist holding Kaitlin hostage.  Jessie, now fully aware that it was Ruben who was rumbling along towards him, smiled.  He had been right all along.  She had lied to him.  His mind held onto that thought and he drew back his gun and swiped at her head with the metallic object.  It made contact and Ruben's face turned to one of disgust as he witnessed the horror before his eyes.

Her body began to go limp as a result of loss of consciousness.  She felt like her life was finally drawing to a close.  She had made so many mistakes.  Would she be forgiven?  

When Ruben was two metres away from Jessie, he launched himself towards the giant.  Jessie hadn't expected Ruben to cover so much ground so quickly and inside he cursed himself for hitting Kaitlin, it had left him in a difficult situation.

Ruben was airborne with arms outstretched.  His reflection in the lounge mirror was also airborne and the two of them headed towards two evil figures, who had been holding two dear old ladies hostage.  As Ruben came into contact with Jessie he began to wrap his appendages around the man.  Jessie's body was unable to remain standing against the huge momentum imparted upon him by Ruben's less than slim build.  He fell backwards and onto a table containing nothing of interest to the two brawling figures.  

The table legs gave out under the weight of the two behemoths, and Ruben, Jessie and table contents fell together before breaking each others fall, the table receiving the worst of the injuries as it snapped in half.  The two rolled together for a while, Jessie trying to point the gun towards Ruben, Ruben trying to point it away.  In one motion Jessie managed to get the upper hand on his opponent.  He clawed his way to his feet and planted a foot squarely on the side of Ruben's head.  Crushing his skull into the floor.

``I'm going to enjoy killing you after this is all done,'' he said gleefully.  Ruben just lay there.  It seemed Jessie had won.  He had tried so hard, but again the weasel had gotten the better of him.  It made him sick.

``You'll never kill me,'' said Ruben defiantly.  

Jessie picked up the rifle from the floor and pointed it at the very top of Ruben's head.  ``I could kill right now if I wanted, teddy bear,'' he said.  He had used the term several times before now, referring mainly to Ruben's build, but also to his somewhat simplistic nature.

At that point the window in front of which Jessie was standing exploded into life.  A light began to shine from somewhere outside, bathing the entire room in a super bright white glow.  Glass sprayed the weasel and bullets ripped past his body, inches from bringing down the bully for ever.  Jessie ducked down, still managing to keep his command of Ruben.  'Damn it,' thought Jessie, 'what the hell was going on?'  He raised the tip of his rifle into sight above the windows ledge and more bullets peppered the back wall of the house, destroying several more of Kaitlin's display cases.  

As the two men sat there under the window ledge a voice came thundering through the airwaves.

``It's no use, we have the building completely surrounded.  Give yourselves up, and release your hostages.''

Jessie could scarcely believe it.  Of all the times he'd broken into someone's abode and terrorised them for information or money, none of them had ever managed to phone the police, nor had any of their neighbours.  He figured Kaitlin must have a pretty good relationship with whoever was next door.  

Mr Weasel couldn't have been further from the truth.  Next door was the home of Mrs. Jenkins, a Mrs. Celia Jenkins.  The two old birds hated each other with a passion and had taken every opportunity to shout abuse to each other over the fence.  Celia had however heard the goings on in Kaitlin's house and she had phoned the police.  Though the two of them didn't exactly get along, no one deserved to be treated like this.

``Guess you're out of options now,'' said Ruben smiling sweetly.  Jessie, still atop the man punched him in the face.

``Wipe that smile off your face, this ain't over yet.''  Jessie pulled out his phone and jabbed at a few of the keys.  He had to make sure Ruben didn't overhear who he was talking to else their plan could be in jeopardy.  As the phone dialled, he shouted out to the forces waiting outside.

``This is Mark Matthews, I'm a G-TEP agent, and I've cornered a temporal suspect in this building.  I require you all to leave right now.''

The reply came back, preceded with a little laugh, ``Sure you have little man.  Give us the mission id and we'll corroborate your story with G-TEP HQ.''

Damn it.  The mission didn't have an id.  It wasn't exactly a kosher operation after all.  The phone was still ringing.  Kaitlin was coming round now and was more than a little surprised to see that her living room had been turned into some kind of battle arena.  The light coming in from the window was so bright she could hardly make out the figures of Jessie and Ruben, just distorted silhouettes.

Finally the phone picked up and a gruff voice was heard.  ``What the hell is it now?  You have the device I take it?''  Once again it was Ric, and Jessie felt so ashamed at having to break yet more bad news to him.

``No, not yet,'' he started.  There was a scream from the other end of the phone, that was audible to both Kaitlin and Ruben.

``What!  How could you screw this up Jessie,'' shouted Ric.

Jessie winced, ``I do have Ruben though, I just need some help.  I have him held hostage at Kaitlin's, but someone phoned the cops and now I have a swat team outside.  They're asking me for a mission id?''

Ric was furious, ``You stupid idiot.  Do you know what you've done?''

He went silent and Jessie could hear him tapping away at some keys, he presumed Ric was creating a mission for him.  Ruben just lay there, as did Kaitlin.  Neither one wanted to move, neither one really had the energy either.  Jessie didn't answer on purpose.  He thought it best not to engage the beast further into a slanging match.  He knew he was in the wrong.

The tapping came to a halt and Ric spoke, ``Use this, AX4485233RP7, it's a code for a recon mission, I've made the description suitably generic and I will debrief you on your return.''  Jessie hung up without saying anything further to his superior.  

He smiled at Ruben, ``See, it all works out in the end.''  He shouted out of the window to the waiting force outside.  ``Alpha X-ray 4485233 Romeo Papa 7''

``Please give us a moment to verify,'' came the booming response.  

They sat there waiting, all three of them.  Two desperately hoping that the verification would fail and that the police would storm the building.  One desperately hoping for the opposite.  Jessie hoped he hadn't been too quick to provide the code.  Had Ric finished the submission?  He wasn't sure.

Out in the kitchen, milk dripped slowly from one of the upturned bowls now residing on the floor.  Jessie had made quite a mess.  Most of the crockery had survived, but a good portion of it had been destroyed when it had come into contact with the cupboards under the sink.  The pieces now lay confused on the floor, unable to determine who their neighbour should be.  There was a mix of soggy fruits and breakfast leftovers too.  

In the bedroom, the mirror shards sat in a fairly similar fashion.  The light from the window illuminating them and making a pretty mosaic type pattern on the hallway ceiling.  The mirror had been a gift to Kaitlin from a friend over thirty years ago.  She had always loved it, but somehow knew that one day, it would get broken.

The lounge was the messiest of all, though the kitchen could have contested that.  Broken glass lay everywhere and Kaitlin quietly sobbed to herself.  She hadn't seen it coming.  She hadn't known that this evil man was going to break in here.  She berated herself.  Even though deep down Kaitlin knew that there was nothing she could have done, no way she could have known, she still took the pain upon herself.  In part she was trying to lesser the suffering of Ruben, who was still being crushed in the neck by the leg of Jessie.

Ruben was finding it hard to breathe and maintain his composure.  He could feel an attack coming on.  It was all too much to take.  He hadn't managed to save Kiele yet, or Kaitlin.  Jessie was still very much in control.  It sickened him to the core.  Was Jessie really going to get away with it?

The radio crackled and a voice drifted in, ``OK, Echo Lima, you are confirmed.  Please give us your orders.''

Jessie smiled.  It had all worked out in the end.  He had gotten his way once more.  He still held the power and there wasn't a damn thing anyone could do about it.  He felt invincible.  

``Please withdraw from the area, I require no further assistance,'' shouted Jessie.  It had been a close call.  He had almost gotten himself shot and had it not been for Ric creating the fake mission description, they would have most certainly been captured by the police forces, and the entire mission would have been over.

``You're a sick man,'' cried out Kaitlin.  Jessie hadn't even been aware that she was awake.  He turned to look at her, hearing the cars retreating down the road.  He looked back at Ruben.

``No Kaitlin, I am a driven man.''  He smiled again, ``something that me and Ruben here, have in common.''  Ruben couldn't speak, he was too busy trying to prevent his body from falling into shock.  He'd be completely useless if that happened.  The feelings were beginning to overcome him once more.  He was losing control, losing power.  His mind washed over once, twice, completely void of all thought, all rational cognitive ability.  

``Ruben is nothing like you, you sick, twisted man.''  She had hardly finished the last word when a bullet pierced her skull and sent her head flying backwards.  Ruben screamed out and Jessie thwacked the side of his head with the rifle, sending his brain into a dismal spiral, from which the only inevitable outcome was blacking out.  



\thoughtbreak



Kaitlin lay there, eyes and mouth wide open.  The blood was starting to seep from her wound now, slowly at first, but then faster and faster, the beige carpet turning a deep shade of red.  The circle of blood seemed to grow unevenly as it was sucked up in small waves by the fibrous strands.  Her body had barely moved much, but her head looked as if someone had taken a swift kick to her lower jaw.  She didn't look at peace at all, she looked angry.  Frightened and angry.

In a way Jessie hadn't meant to kill her.  It had been a by product of what she had said and when she had said it.  She had ticked him off for the last time.  He was a volatile character by nature, but the added pressures that Ric had been placing on him over the years had made him even worse.  He was becoming a carbon copy of Ric, just without Ric's restraint and intellect.

Ric wouldn't have shot Kaitlin.  For a start he would have deemed it a waste of a good bullet, secondly it would have left too much evidence for him to clean up.  Jessie had acted purely on impulse, not caring who or what was destroyed in the process.  He had been focussed on one thing and one thing only; get Ruben out alive.  

Now he was back in his car again, the great lummox on the back seat gagged and bound.  He had called Ric to inform him of the events and his partner in crime was now busy smoothing things over with the big bosses.  Their story had been that Ruben had broken his  agreement.  

Driven by years of madness Ruben had decided it was all too much.  Jessie had, by chance, seen him at a supermarket outside of his allowed perimeter and Ruben had decided to make a run for it.  He had arrived at Kaitlin's house and taken her hostage.  Jessie had arrived to save her, but Ruben had lost his mind and in a struggle had shot her in the head.  It was believable and to be honest the G-TEP didn't care much about Kaitlin anyway.  She was a civilian, not a temporal offender.

Ruben started coming round, his body finally able to move again after its traumatic experiences.  He tried in vain to shout, but just couldn't get the words out.  The gag was partly the issue, his failing neurons were another.  Jessie flicked his head round to look back at the sniffling creature writhing on the back seat in pain and anguish.  He looked back at the road again and then back to Ruben.  

``Real shame she didn't make it Ruben,'' he said.  ``Now if you try anything else, I'll just kill Kiele anyway, and maybe I'll throw that little teacher in too, as kind of an added bonus.''

Ruben kicked the back of Jessie's seat with his legs.  Though they were bound together, he still managed to find enough leverage to make a pretty good impact.  He winced in pain as the ropes dug in, scraping yet more flesh from his already battered body.  The chair flew forwards by an inch or so, enough to jolt the driver who was now beginning to get very angry once again.

Jessie breathed heavily.  In and out.  Now was not the time, he had already messed up one mission, two if he counted Ruben and Kaitlin's houses as separate events.  This time it had to go smoothly.  This time he would recover the device.  His hands gripped the steering column tighter than before and he began to speed up slightly.  He wasn't sure for how much longer he could hold his anger inside.  It was getting more and more difficult.

As they sped along the dual carriageway, Jessie realised why he had been feeling especially charged today.  He hadn't taken his medication recently.  A few years ago he had been diagnosed with Hyper Aggression Disorder.  He'd kept it from everyone he could, but Ric had found out after a routine inspection of his subordinates medical records.  Jessie was prone to angry out bursts and upon examination it had been determined that he was suffering from a psychological disorder.

Jessie had been prescribed a series of medication to keep his anger under control.  The doctors had been unaware of the pressures of his occupation, and even if they had known his place of work, they wouldn't have had any idea about Ric and the extra pressure he placed on the weasel.

Jessie popped open the glove compartment and search single handedly for a pot of his pills.  Eventually after cursing to himself he found a small blister pack.  It would have to do.  He put the pack in his teeth as he recomposed his control over the car.  Taking both hands off the wheel he popped out two of the 200mg Ditraxicaemol tablets.  The car hit a bump and the pills were launched into the air before landing scattered on the floor.  Jessie threw his hands back on to the steering wheel again and managed to regain control.

The blister pack had fallen into his lap and he reached down looking once or twice to retrieve it.  He pressed out two more pills and swallowed them down.  In about fifteen minutes he would begin to feel a lot better.  The pills weren't a cure, but it did help to quell the anger which often sent Jessie off the rails.  Anger which the sideboard at Ruben's had been privy to, anger which Kaitlin had suffered first hand.  

Ruben lay still in the back seat.  Just where was he being taken?  He had no choice now.  He had lost the little advantage he had gained when he had burst out of the shower.  Kiele would be next, unless he told Jessie what he wanted to know.  There was no way out any more.  

