\chapter{09}
\section{}
Consequences  

Oken stood facing El Morra.  The sword he had been given was heavier than Bethany and Oken felt sure that some inexperienced cretin had been using it to hack at metal pillars, judging by the dents in the blade.  Oken wanted it to be over, but he also now wanted to live, something that he had never felt before in the ring.  He wanted to look up at Jay but decided against the idea.  He wasn't putting on the show he had last week and she would only worry about him.

The music, which Oken had been unaware of until now was thinned down once more, eager to answer the call of the DJ and spring into life, dosing the platform up with a cocktail of sound.  Oken's heart was pounding.  This was it.  He was ready.

The word 'go' came fairly unexpected for both fighters.  El Morra ran towards Oken who, in turn, ran towards El Morra.  They both sported swords and their blades glistened in the spotlights of the arena.  Oken felt the heat from the lights almost burning his skin, but continued on towards his enemy.  

El Morra swung his sword at Oken who masterfully blocked it and added a swipe of his own.  It hadn't been as difficult as he had remembered.  In his head he had planned out the fight using Bethany.  It would have been so much easier.  Oken had no time to think about that now though, as El Morra rained down blow upon blow, it was obvious that he was definitely out classed.

El Morra was a little disappointed that Oken was not using his new technology and the crowds too were getting impatient.  Jay was confused and looked over at Ruben who was standing next to her.  She saw the worry in his eyes and ventured a question.

``Ruben, what's happening, why isn't Oken winning?''  The words sounded so innocent, so childlike that Ruben felt as though he were talking to an infant.  He didn't want to tell her, but knew he had to.  He could see how confused she would be if he didn't.

``He forgot the blade,'' said Ruben.  He saw her mouth drop open in amazement.  She had thought that maybe it had gotten damaged or needed more development, but she had never once suspected that Oken had plain forgotten it.  It was so simple.  She soon realised that she had probably been the cause of the mishap.  

It felt like someone had just stuck a dagger through her heart.  If Oken died now, it would all be her fault.  She should have met him at his apartment.  She should have made sure he had everything.  She could have been his wife.  She would have loved to have been his wife.  To protect him.  But it was almost certainly all over now.

``It's my fault he forgot it,'' said Jay.  Her face look so contorted, as if she were about to cry but was trying to hold it in.  She looked so distraught that Ruben couldn't help but put his arm around her and pulled the devastated body towards him, cradling her and shielding her from the sights of below.

``It's nobody's fault Jay, it just happened,'' came Ruben's, soothing reply.  He held her next to him and tried to offer as much comfort as he could.  Her eyes were now filling with tears.  She loved Oken more than anything else in the world.  It was true she had only known him for a week, but she had noticed him a long time before their first meeting.  She had seen the strength in his eyes and the passion for his sport.  A single tear rolled down her cheek.

In the instant the tear hit the ground a large number of things happened.  The fight between El Morra and Oken had intensified and now the two of them stood locked in battle.  In that split second El Morra swung a last blow towards Oken who deflected it masterfully; unaware of the second sword that El Morra had just pulled from his back harness.  Later in that same split second, El Morra thrust the sword into Oken's chest, ploughing through the muscle and flesh to reveal the blood which lay within.

Oken didn't feel the sword go in, in fact he was about to take another swipe at the enemy before him when he noticed the sword sticking out of his chest.  He looked up into the spectator stands.  Time slowed down.  In the absence of Bethany, it was a much more natural retardation.  Oken's eyes became a little heavy and all he wanted to do was to go to sleep.  

He noticed Jay up in the spectator stands screaming, set apart from the crowds by her brilliantly coloured hair.  He watched on as she ran in slow motion to the stairwell that lead down onto the platform.  He was unaware of anything else in the arena besides her.  El Morra was a blur in the distance.  Shouts from Ruben of 'LET HER THROUGH' could be heard.  

Oken fell to his knees and then onto his back, the sword now pushed clear from his body.  He was dying.  He'd never felt like this before in his life.  His very essence seemed to be leaking from the hole that cleaved his chest.  He could feel little pain from his physical wounds, but the pain of his heart was strong.  Why hadn't he told her how much he loved her?  

Jay reached Oken and in his slow motion he saw her fall to her knees beside him.  Her fragile figure slumped forward and she held him in her arms and hugged the man that had been so brutally ripped away from her.  She had never kissed him, never heard him say those words that she so dearly needed to hear.  It was as if he had never existed.  She leant over his face and whispered in his ear.

``I love you,'' she said.



\thoughtbreak



The move had taken all of the G-TEP forces completely by surprise; no one had expected Oken to lose.  It was clear that he didn't have his weapon with him.  Leon and Ric stood by.  Leon was unaware that he was the only enforcer with a clear shot.  The instructions came across the battered old radio.  ``Watch him like a hawk, it could be a trick so stay on him Alpha 2, you have the shot, I repeat, you have the shot.'' 

Leon was unable to reply.  He couldn't do anything.  He was frozen on the spot.  His fingers were shaking at the murder that had occurred before his eyes.  He wondered why it bothered him so.  His mind was a mess and he couldn't think straight at all.  His eyes were blurry and his mouth was dry.  His hands shook more and more.  He had no idea what was happening.  His mind told him to get a grip on things, but he couldn't.  He had no grip on anything.

Everything around him was a blur.  The platform, the people, even Oken.  He had to stand fast and watch him; watch him like a hawk.  Leon had never known himself to feel like this before.  He was a wreck.



\thoughtbreak



Jay was still clinging onto the man whom she loved.  The body that lay in her arms seemed lifeless.  In the slow motion that still persisted, the crowds were  jumping and the music was still pounding.  El Morra was jumping around and screaming in excitement.  Jay was crying.  She once again leaned over the head of her beloved Oken.

``I love you,'' he said.  Had she heard that correctly?  Had he said those words?  She knew that he had but she just wanted to make sure.  Oken smiled and began to turn his head.



\thoughtbreak



Leon's gun fired.  He wasn't sure how or why, but it had.  He had seen Oken turn his head and had immediately tightened his muscles in fear.  His shaky finger had not been exempt from this reaction and the gun had fired.  It was still firing.  Leon released his finger.  Through the gunning hole that stood in the wall in front of him the platform once again regained focus and he could see the damage that he had caused.  He had unknowingly sprayed the platform in bullets.



\thoughtbreak



Oken didn't feel the first bullet, or the second, or the third.  The forth one hurt a little and the fifth one almost killed him.  The sixth missed him, but he watched in horror as it ploughed through the body of the woman next to him.  His little Jay had been hit several times.  He had never got the chance to show her how much he had loved her.  It was all over.  He was angry at the entity who had done this to her, but in a split second it didn't matter any more.  Oken was dead.

Jay's last thoughts were of happiness.  She had heard what she needed.  The man she loved more than anything in the world had reciprocated her feelings.  Granted the relationship had lasted a mere five seconds, but that was five seconds more than nothing.  She had wanted him to say those words more than anything else in the world.  Her wish had come true.  Her body became weak and she slumped down onto Oken's bullet ridden chest.  She too was dead.

Amid the explosions of gunfire which were now being exchanged between angry Zone addicts and G-TEP officers, lay two bodies.  They looked so peaceful in amongst the confusion of the battle.  As the bullets rained down on the platform, several hit Oken and Jay.  It was a final insult to their lives.  They were already dead and there was nothing anyone could do to bring them back.

As the bullets continued to fly they hit the ceiling tiles that were hanging high above.  One of these tiles shattered upon impact from a G-TEP round.  The pieces fell, twisting and turning as they did so.  They all hit the ground in a crescendo of applause. 



