\chapter{41}
\section{}
The Park At Drewery  

Zane arrived in takeaway alley.  How it got its name was blatantly obvious.  It had started with one takeaway shop, and just grown.  Now, there was only one shop in the so called alley that wasn't a takeaway establishment.  It was a small book shop, with a very limited supply of books.  The sign above it read simply, 'BookStore'.  The man inside, who looked like a cross between a hardened criminal and a postal worker, was sitting at his desk, watching the passers by.  

The birthday boy still hadn't decided which meal he wanted.  To be honest he was spoilt for choice.  There was Alendrian, Prestonian, Chinese, Indian, Full English, you name it.  As he mused up and down the takeaway fascias, his nose was drawn to the smell of pizza.  Ahh, he thought, good old Italian.  He walked up to the shop front and looked inside.  

The place was practically empty and it looked more like a Chinese than an Italian.  Though the proprietors were not of Italian origin, they still knew how to cook fantastic Italian food.  The smell was completely controlling.  Zane walked into the shop in a blind stupor, being guided one hundred percent by his sense of smell.

He looked up at the menu and was completely bewildered.  There must have been over a hundred choices.  Zane was sure that fifty years ago, they hadn't had a hundred different types of pizza, but then, they lived in crazy times now, where choice was everything, even if no one had much money to buy, perhaps especially since they had no money to buy things.  People wouldn't settle for just something generic any more, they wanted something specific, something that would fulfil their every need.  If they had to shell out their hard earned cash, they wanted to make damn sure the item did what they wanted.  Pizza was no different.

In the end he decided on a peperoni, a vegetarian and a BBQ.  He figured that he didn't have to rush home so much with pizza, they could always reheat it.  He paid for the food and left.  He still had some change in his pocket from paying Mark for his rent.  He skilfully placed the change from the pizza in one pocket, leaving his own change in the other.  

Zane left the shop, responding to the inordinate amount of waving and thanking from the foreign proprietors, before gently closing the door.  As he walked down the alleyway towards home, he looked up and smiled as the wind whisked through some distinctly Chinese lanterns lining the walkway.  They were red in colour, illuminating their surrounding area in a pale rouge glow.  There were approximately three per shop, hanging on a rope that seemed to span the entire street.  

The physicist couldn't resist looking back and counting the number of lanterns in total.  Forty.  As he had expected, they hadn't placed a certain number of lanterns per shop, there were a certain number per street.  He tried to do the calculation in his head, but his mind started to drift elsewhere.  Kiele.

As Zane crossed the quiet street he couldn't help but ponder on her earlier mood.  Their kiss had been startling.  What could have possibly upset her?  As he reached the kerb on the other side of the road he noticed an elderly woman selling flowers.  There were beautiful bunches of chrysanthemums, roses, tulips and daffodils, including some varieties Zane had never seen before.

'Kiele obviously needed cheering up,' he thought and promptly purchased a bunch of red and yellow tulips.  Fearing it to be too small, he purchased another and asked the kind woman if she could merge them into a single bouquet.

``For someone special?'' she asked.

``They're for my girlfriend,'' he replied.  It was the first time he had used the word girlfriend before, at least the first time he had used it in reference to someone he was dating.  

``Oh,'' said the woman, ``in that case.''  She took another two bunches of tulips and created a fabulous arrangement.  Zane looked worried and the old woman saw his anxious look.  ``You don't need to worry sonny,'' she said, ``these are on the house.''  

The young boy frantically tried to give her money for the initial two bunches, but she wouldn't take that either.  ``I was just about to give up and go home anyway,'' she said.  ``Please, just take these home to your girlfriend.  I'm sure she'll love them.''

Zane smiled and thanked the kind woman.  'Kiele would love the flowers,' he thought.  Now fully laden with three pizzas and an enormous bunch of flowers, he began to walk the ten minutes or so back home.  He couldn't wait to see the look on her face.  She was going to be astounded.

He could hardly believe how quickly they had made the transition from acquaintances, to friends, to good friends, to dating.  It had all seemed to flash by so quickly.  Part of him wished he could do it all over again.  It had been exciting, not knowing exactly what she thought, wondering if today would be the day he would get to taste her tender lips.  

Kiele was clearly being paranoid about her father's demeanour.  He had never shown any kind of malice towards her and the only time Zane had ever seen him angry had been that one time down in the basement and he was sure that that had just been down to a bad day at the office.  'It must be a stressful job,' thought Zane, and keeping it from Kiele for all these years must have been sheer hell.

He rounded another corner, and instantly regretted it.  There stood about thirty metres from him was a gang of vicious youths.  Some were wearing collars with chains hanging from them.  Some were shirtless, covered in tattoos instead.  Some just looked plain mean.  He thought about turning back.  If he did that, they would notice him for sure.  He was carrying pizza and flowers.  He was toast.

He ducked down slowly as he walked forwards a little more, managing to hide behind a fence.  If only he was more like Oken, if only he had the master's sword right now.  He could cut them down to size.  A voice popped into his head, it was his fathers.  'You wouldn't be passing judgement on these lads now would you?' it asked.  Zane decided against replying but instead got up and walked straight for the gang.  He wasn't trying to confront them, but his path unfortunately ran rather close to them.  

They saw him approaching, but made no efforts to make any contact with him.  They dressed like thugs, and if the police force had seen them, they would have been taken into custody for sure.  Zane had to conclude that this particular group of youngsters were playing at being thugs rather than actually being thugs.  He stepped past them slowly.  Don't make any sudden movements, his brain told him.  

They let him be.  It was astounding but true.  They had let him go without so much as a single word.  He picked up his pace a little more now, determined to reach the house before he came across any other unsavoury characters.  He was in luck, he made it back in a little under nine minutes, opened the door and breathed deeply.  



\thoughtbreak



The three of them sat in relative silence whilst they scoffed down the pizza which Zane had provided.  Kiele, did not eat much.  She ate a slice, maybe two and then asked to be excused from the table.  Zane had to admit, he was a little upset.  It was supposed to be a celebratory treat from Mark to them both and here she was acting like a disgruntled teenager.  He thought he knew her better than that.  He hadn't given her the flowers yet, he they were resting on her bed, a gift for her to find later.

Mark and Zane finished off as much as they could.  The air was filled with a rich smell of meat and vegetables, and of course, cheese.  The leftovers were put into a box and Zane was instructed to eat them up the next day if he got peckish.  The two men sat there for a few minutes, sipping cola, or in Mark's case, beer.

``I'm really sorry,'' Zane replied, ``I completely forgot about working on the device today, I'll make up for it tomorrow.''  Mark nodded and Zane added, ``It is Saturday after all.''  They both smiled and Zane excused himself.  

Zane went off in the direction of Kiele's room.  He wanted to talk to her.  He wanted to find out what it was he had done wrong.  He reached the door and knocked on it, but there was no answer.  Carefully he opened a crack in the door, the paint making a sticky snapping sound as he opened it.  She wasn't in the room.  He had to check twice, it was dark after all and he had expected to find her asleep in her bed, but she most certainly was not in there.

He took a quick scout around the rest of the house but to no avail, Kiele was nowhere to be found.  It was getting close to 11pm now, and Zane was beginning to worry about her.  If she was outside, he didn't want her running into a similar group of youths that he had encountered, so he decided to go looking for her.

It seemed as if she had snuck out of the front door, either himself or Mark would have seen her leaving through the back exit.  Something was clearly on her mind and he was desperate to find out what.  He hoped and prayed it was nothing he had done.

As he opened the door, a voice behind him said.  

``Try the park up on Drewery.''  Zane nodded to Mark and left the house.



\thoughtbreak



Kiele was sitting on a swing, slowly rocking backwards and forwards.  The park itself was fairly old, but the swings and climbing frame looked even more ancient.  Paint was cracking from the metallic surfaces and anyone performing a health and safety audit would have shut it down immediately.  The paint, though supposedly hard wearing seemed also to have incorporated some hardening agent.  It was solid and where it cracked, it had become razor sharp.  Spikes protruded from almost every painted surface in the park.

Luckily for Kiele, the seat was made of a plastic composite and the attaching chains had forgone the painting malice, presumably to allow them to swing easier.  As he approached her, he noticed her expression wasn't so much one of sulking, more of shock, like she had been given the bad news that something terrible had happened.

Zane sat down on the swing next to her and began to gently propel himself as she had obviously done.  The air was cold and although she was wrapped up pretty warm in a jacket, to Zane, she still looked as though she was suffering from the temperature.

``Kiele,'' he said softly, ``What's up?''

She ignored him or maybe she didn't hear him.

``Kiele?''  He said it a little louder this time, but still no response.  He tried a final time, gracing his vocal work with a hand on her shoulder.  Considering they were both swinging at the time it was actually quite an achievement.

``Kiele!''  

``What!?'' she snapped back.  It was the first time she had ever used that tone of voice with him.  It was even more succinct than when she had berated him for reading the book in the hospital.  What could have happened to make her turn on him so.  Part of him wanted to hold her close once again and kiss her.  Surely that would fix everything?  He reprimanded his brain for suggesting such an obviously flawed plan and tried to think of something to reply with.

``Didn't you like pizza?'' he asked

It had been a stupid question anyway but Kiele chose to ignore it verbally and she shook her head instead.  He could never understand what she was going through, what it was she had to do.  If Mark had told her to kill herself she would have found it less painful than this.

``Kiele, what's up?'' he took a different approach a much softer approach, removing himself from the swing and crouching down in front of her.  Her eyes were hidden from view, guarded by the curtain of hair protruding from scalp.  At any other time Zane would have brushed her hair aside, but right now, he was genuinely scared of her reaction.

``Kiele?'' he asked again.  He was beginning to get pushy now and though her reactions remain unchanged, Zane could sense an almost invisible elastic band being stretched further and further, brimming with the potential energy to cause vast amounts of damage.

He placed his hand on her leg.  She had been wearing her denim skirt to the gig but Zane hadn't noticed she had changed into trousers.  Though Zane fully expected her leg to be cold to the touch, he was once again shocked by its warmth.  She made no reply to him but the touch seemed to have unnerved her.  Kiele appeared to be perturbed by Zane stealing the heat from her thigh.  Finally she spoke, this time properly.

``Zane, I'm sorry but I just can't do this any more.''  He still couldn't see her face, but even so he moved his head to the left and right trying to catch a glimpse of her expression hiding behind the iron curtain.

``Do what Kiele?'' he questioned.

``Us,'' she replied sorrowfully.  He couldn't understand it.  Earlier in the evening, they had expressed their love for each other in a way they had never before.  What was she saying?

``What...Why...What did I do?'' he stammered, unable to comprehend the real meaning behind her statement.  Was it the kiss?  Everything had seemed OK up until then.  He had told her it had been electrifying, but as he thought back, she had made no response.  Was that it?  Was it the kiss that had changed her mind.

``Nothing Zane, you did nothing.''  Her voice was beginning to get unsteady now.  Tears were forming behind the tough exterior, the mask unwittingly hiding her very human emotions.

``I don't understand,'' said Zane, in what was probably the most accurate statement of the conversation so far.  ``Kiele, I love you.  I would die for you.  Don't you understand?''  It was time for his voice to receive its treatment of shake.  His eyes had filled with tears.  He had finally found someone who he felt he could share his life with, and for some reason she was taking it all away from him.  She remained silent still.  ``Kiele, I love you.''

In a soft simple tone she almost whispered her response.  As sharp as Bethany, as cutting as the most basic of knives.  She spoke her words and sliced a hole through the young, confused boy before her.

``That's the problem,'' she paused to regain composure, ``I don't love you.''  Zane couldn't see her face, but the tears streaming from her eyes fell in great torrents lighting up the denim with their silky wetness.  Her body was shaking and all Zane wanted to do was hold her close.  All he wanted to do was cradle her in his arms and tell her that everything was OK.  There was however a problem, she apparently didn't want him to.  

Zane just couldn't resist what his heart was telling him to do.  He knelt down on his knees and tried to put his arms round her.  She slammed her feet down onto the ground and pushed between Zane and the swing, ``Don't Zane,'' she cried, ``Just don't.''

He could hold back the tears no longer and as he sat there sobbing and looking at the swing slowly recovering from its terse detachment, Kiele looked up to the moon and the stars above.  She could hardly see anything.  The tears filled her eyes and adjusted her visual perception.  Everything seemed drenched in tears, sadness, despair.  

``What did I do?'' sobbed Zane.  He couldn't understand.  They had been so good together.  What could have changed so rapidly?  

``Maybe it's not about you Zane,'' she said coldly.  ``You can't control everything you know.  Maybe this was a decision I made.  You didn't do anything, it was me OK.  I don't love you.  Why can't you just understand that?''

She was almost screaming by the end of it, fuelled with anger and hatred, but not for Zane, that kind of emotion was never meant for him.  Her heart was ripping apart inside.  This was the last thing she ever wanted to do.  Why did it have to be like this?  She could feel her breathing becoming more and more erratic.

``I understand you, I just don't believe you,'' came his soothing words.  He had brought his breathing under control, unlike the young girl standing to his left.  

Suddenly she spun round on the spot and exploded, ``Why do you have to make this harder than it already has to be, you bastard?''

The words hit him like a shock wave.  Where had that come from?  He had never heard her swear before.  It just wasn't in her nature.  In truth, her aggression and language had been borrowed from her father.  His years of torment and abuse layering her mind with ill feelings and hatred.  Now the layers were tumbling down and the love, which she had felt for Zane, was becoming infected by the stark, disgusting virus that was her father.  She had tried so desperately to keep them separate.  She had failed.

She was standing there shivering, pointing at the man she loved so dearly, with a love that had been so strong.  Now it lay in tatters, broken and bruised.  She still loved him, but she wasn't allowed to.  That much had been made perfectly clear.

The boy stood to his feet and put his arms around her.  Whatever had driven her to speak to him like that must have been pretty severe.  Could it possibly have been something Mark had said?  Could he be the reason for all this?







