\chapter{11}
\section{}
Field Trip  

``And this is where the courageous G-TEP enforcers took up aim to take down Oken Brown.''  Jolie was pointing to the rectangular holes cut into the walls.  The arena hadn't changed much.  The Zone had kept its lustre, if it could be called that.  The lustre of death, loneliness, fear and anticipation.  

Little did the students know but they were part of only a very small handful of people who had ever been allowed into the room.  Temporal sites were always regarded as almost hallowed ground.  Sacred areas scattered throughout the globe that people feared to trifle with.  Better just to board them up, and slap a court order on them for protection from redevelopment.  They held residual temporal energy and the G-TEP preferred to auction the sites off to collectors to maintain in a state of perpetual stasis.

The room was practically untouched since the end of the last battle.  The blood of Jay and Oken could still be seen on the floor, though why wouldn't it, no one had ever tried to clear it up, Jolie thought.  Some cameras were still in place, though they had ceased rolling a long time ago.

Two of the gorillas who had been allowed on the trip started up mock play fighting, making whooshing noises as their imaginary swords sliced and diced each other into an honourable pile of imaginary blood and guts.  ``Disgusting,'' thought Zane.  These idiots obviously had no respect for what had happened here.  One of the cretins tripped and fell, slamming his knee into the ground, adding his own blood to the stained memories which adorned this palace of death.  

The monkey quickly jumped to his feet, and Zane heard him shout, ``I'm OK, I'm OK.''  Though he wondered if anyone actually cared.  The injured party started hobbling but instead of learning a lessons from his encounter, he used it as a display of his 'woundedness', limping and wincing in pain, whilst continuing to spar with his partner.  He was the heroic warrior, continuing fighting though his leg had been ripped off.  Stupid.

Zane looked around the room.  It was large, but the echo somehow didn't sound quite right.  It seemed more sullen, like the room was actually moping in depression.  The whole place filled him with a feeling of fear and dread.  Just what had it been like to come out here, knowing that it may be your last few minutes alive.  

Oken was a brave man.  Zane already knew that.  He wasn't stupid either.  The master wouldn't ever have entered the ring knowing he would fail.  It wasn't him.  The student's mind wandered.  Maybe he was coerced into it.  Maybe someone forced him to do it.  The tap on the shoulder was a wake up call and Zane spun round so fast that he almost knocked Kiele over.

``So how does it feel to actually be here?'' she asked.  Her eyes sparkled in the dim light and Zane could see a level of excitement definitely missing from yesterday's encounter.  It was as if being here had sparked her interest, had forced her to come to the reality that what had transpired here was truly influential.  It wasn't about a man on a mission any more, Zane could see that Kiele had started to sense a real passion for the man with the sword.  The man he wanted so desperately to find out more about.

``I don't know how it,'' he paused, ``feels.  But I know I want to know more.  This was a very influential event.  Plus,'' he looked down at his shoes.  The pause had gone on too long to make his next words part of the previous sentence.  ``I'm failing history, and I need to do well in this assignment.  Really well.''  He looked back up and grinned at Kiele, ``looks like this one came along at the right time.''

Jolie called the class over to look at some markings on the wall.  There were deep gouges where various weapons had hit with extreme force.  In certain places, tiny shards of metal, still embedded in the wall, glistened in the dim light.  Several members of the class took out media devices to capture the sight.  

Zane, uninterested in what everybody else was looking at, turned and walked over to another wall and ran his fingers over it.  The ridges and grooves bore the history of many battles.  He closed his eyes and tried to imagine what it would feel like to dodge one of those devastating blows.  He must have gotten a little too enthusiastic because a giggle from Kiele brought him back to his senses.

She seemed so much happier than when he had seen her the other day.  She wasn't so stern, so still.  He hadn't even noticed that he had been dodging imaginary blows from phantom swords, until Kiele had laughed at him.  Kiele was so cute when she laughed, Zane thought.  Damn  What was he thinking?  He wasn't interested in all that relationship rubbish.  He needed to concentrate on his studies.  His father had always told him how important study was.  He would do well.  He would impress people, but there was something about that smile she wore, something so interesting and cute.

``Something on my face?'' Kiele asked.  She tilted her head to one side and looked directly at Zane.

'Damn it', Zane thought, it's happening again.  One of the other members of the class must have cottoned on to what was going on.  

``Oooooooh,'' Janus jeered, ``Come on you two, get a room.''  Zane turned and faced the wall, but unfortunately Kiele did the same.  The class laughed and Zane's face turned redder than the bloodstains on the platform floor.

Jolie called the class over and they went up the stairwell to the control room.  The smoky atmosphere, though absent for years still seemed to linger somehow.  The equipment had long since been removed, but the design of the room still spoke volumes as to its purpose.  

Zane looked out of the observation window which was made up of four large plates of glass.  He could only imagine how exciting it must have been to stand here and see this for real.  Oken was fast becoming a hero of Zane's, even though the boy wasn't really aware of it yet.  

``This control room was where the remote and static cameras were controlled from.  They would mix live video and display it on the large screen over at the far side of the platform.''  Jolie continued.  ``The money from working here was pretty good compared to an average days wage.  People would give up a large portion of their hard earned cash to get into the Zone, and this money funded the equipment, wages and the advertising, which drew in more punters.''

Jolie was of course referring to the very subtle forms of advertising that the Zone was renowned for.  If they were too obvious, the cops would have been all over them.  It mostly relied on paying off certain regulars to spread the word to people they trusted, who would be invited to attend a special one off event.  Once they had been to one fight, they were usually hooked, and the Zone had procured another valuable monthly income.

Jolie turned and looked out of the window, leaning against the desk in front of her.  ``The Zone at its peak, had over three hundred regular viewers.  Videos were also posted out on the Mediaweb and due to clever image filtering were totally untraceable.''



\thoughtbreak



The Mediaweb had been created as an extension of the Internet.  In the early 2000s, the Internet had become saturated with video, music and images.  Internet companies eventually started to shut-down because they were no longer able to honour their service level agreements.  Service uptime regularly dropped to below 65% and soon it started affecting businesses too. 

To facilitate this, the government created an entirely separate ``Internet'' called the Mediaweb.  This was used to house all of the countries media sharing.  The music industry had all but collapsed, but it wasn't due to the high level of piracy per se, moreover, the fact that download limits had effectively been removed meant people could take whatever they wanted, whenever they wanted, within seconds.

Soon the governments realised the error of their ways and tried once again to unite all media and information traffic into one network.  This failed and led to the start up of many smaller networks by proprietary companies, using proprietary protocols, which made intercommunication between these smaller nodes difficult and expensive.  Strangely enough though it seemed to work better as a  model for communication.  Piracy crumbled, in part due to the intercommunication issues, and in part due to improved copy protection technology.  



\thoughtbreak



The tour was rounding up now and Jolie was trying to ensure that no stragglers got left behind.  True, it was only a short walk back to the college, away, but she was responsible for them and looked upon them almost as if they were her own children.

``So remember people, the title of the assignment is what, Mikael?''  Jolie asked.  She turned her head to look at one of the gorillas who had been play fighting earlier.  He looked blankly back at her and then down to the floor.  Then he seemed to remember something, his face contorting with the pain of retrieving a difficult memory from the depths of his brain.

``Sorry Jolie.  I got nothing,'' he blurted out.  Zane and Kiele simultaneously tutted at the oaf.  Why hadn't he been listening, thought Zane.  It's not as if it was a hard thing to remember.

The other gorilla, in an effort to redeem himself for his earlier indiscretion offered up his version of the title for the assignment, ``How would Odin feel after killing all these people?  Discuss.''  He knew he had the last bit right, Jolie always ended her assignments with the word 'discuss'.  He sure of this because he hated it, the assignment would have been a piece of cake otherwise.  'How did Odin feel after killing all these people?' : 'Bad' he would have thought.  That would have been it, job done, next assignment.  'Discuss' meant he had to read, and write neither of which generally ended well for him.

Jolie, who was looking in the other direction sighed and slightly rolled her eyes.  'No, Daniel you idiot,' is what she'd have liked to have said, but Jolie being Jolie just simply stated the problem again.  ``How do you think Oken would have felt knowing the impact of his actions during his last fight?  Discuss''

Daniel piped up, ``that's pretty much what I said Jolie.''  He knew it wasn't perfect, but he'd been at least part right.

``You called him Odin you great pleb,'' said Zane.  He wasn't looking for a fight but was simply trying to point out the inaccuracy of this idiots responses.  

``I have a problem remembering names dumb-ass'' was the response.  ``It's a medical problem, I've got pills for it an' everything.''

The entire class laughed.  Whenever there was a serious moment, you could always count on either Mikael or Daniel to lighten the mood.  Zane however, dissatisfied, decided to fire of one more remark.  

``What're they called, I'm-a-pleb-oxymol?''  He mentally slapped himself in the head, the retort was stupid.  Some of the other students laughed and Daniel had managed to find a cardboard box lying around which promptly hit Zane in the head.

``Come on guys,'' offered Jolie.  ``Let's wrap this up now.''  She started to walk towards the exit before turning back to add one more piece of information.  ``Oh, and I managed to get special access to this place again tomorrow.  Does anyone want to come and visit here again?''

Tomorrow was a Saturday.  No one was going to want to come here on a Saturday, but Jolie always liked to offer her students as much help and extra material as possible.  Unsurprisingly Zane's hand popped up and he credited the teacher for her effort, ``I'd like to come back Jolie?''  The class jeered.  Now he felt stupid, but he stood his ground.  ``Is that OK?''

Several of the class members took the opportunity to rib him over his previous statement, repeating it endlessly in different voices.  'Is that OK?' they asked rhetorically.  Of course Daniel and Mikael took it one step further 'Is that OK Jolie my love?' became their chant as they walked towards the exit.

Jolie motioned for the class to exit.  She walked back to Zane.  ``Ignore them, Zane,'' she said.  ``They know not what they do.''  Zane knew the reference was a biblical one.  Jolie was always embossing her everyday speech with quotes from the bible.  Not that she was religious in anyway, she was just very learned.  The boy raised one side of his lip and shrugged a single shoulder.  He didn't really care what the class thought.  He was failing history and needed to do well.  Finally he'd been given an assignment he cared about.  He was not about to mess this one up.

Jolie handed him a letter.  ``Here,'' she said, ``knock on the door at this address and tell the woman that I sent you, she'll let you in.''  Zane nodded and received the letter.  It was scrawled on standard white paper, yet in the light of the Zone it seemed almost grey.  The letters imprinted on the page were written in Jolie's hand, once again, curly and expressive.  It was a good job he was the one reading it, thought Zane, had the recipient been any of the others, they  would have probably spent most of the morning trying to decipher it.  He carefully folded the pristine piece of paper in half, and then in half again, garnishing each fold with an added score with his nails.

He placed the paper in his pocket and followed Jolie out of the exit.  The rest of the class were already on the street, awaiting the return to the school.  Zane took the opportunity to look back at the hall of pain behind him.  His view was obscured by the winding stairwell.  Never mind he thought, there's always tomorrow.  As he walked down the road he spotted Kiele.  Deep down he was a little disappointed that  she hadn't asked to join the trip tomorrow too.  He shook his head quickly, as if trying to dislodge an unpleasant thought.  It wasn't that the thought was unpleasant, more unwanted.  Kiele was very pleasant to look at.  Zane again shook his head and silently shouted the word 'No.'  He wasn't going to think about her right now.  As if by magic, Kiele turned round and shot him a winning smile.  Zane smiled back inanely.  'Damn it'



