\chapter{49}
\section{}
A Welcome Reunion  

Zane left the building confused and alone.  His dreams had been crushed.  Oken had refused to even consider his request and he was more than a little angry.  It was after all Oken's fault.  He had been the one who had created a temporal weapon in the first place.  He was the one who had used it in the Zone.  Shouldn't he be the one to fix everything?

The air had gotten even colder now and Zane was glad he was wearing the blazer.  It had seemed like a stupid idea at first, but now he was beginning to see the benefits.  He adjusted the collar and flicked it up to obtain maximum protection from the wind.

Zane couldn't have been in Oken's apartment for long, but already people had begun to leave the street for their houses.  It was getting late.  Zane watched as a woman with a small child tried desperately to persuade the little one that it was time to go home.  Evidently there was something inside one of the shops that the little brat wanted, for it was hanging off her arm like an unwanted extension.  The woman was shaking her arm, trying to dislodge the attention, but it all seemed to be in vain.

The slower he walked, the more natural it seemed.  It was almost uncanny.  This place wasn't his home, not in time anyway, but he felt happier here than he had ever felt at home.  He shifted his mind set once more.  

Kiele, where the heck was she?  He knew she wasn't at Oken's, he had just been there after all.  Jay's?  He had no idea where that was.  All at once his mission was beginning to feel a little fruitless, he would just have to wait for her to turn up at the accident site and hope that he could prevent her death.

He hadn't noticed Oken leave the building behind him and jog the few steps it took to catch him up.  The older man had felt sorry for the boy.  He believed his story wholeheartedly, but he had seen something in the boy he hadn't liked.  He had seen a reflection of himself.  

The woman had finally gotten the small child to see some form of reason and the two of them pushed past Oken as he got closer to Zane.

``Zane,'' he shouted.  The boy didn't turn round.  His brain had inadvertently come to the conclusion that nobody here would know him, and so had ignored all utterances of his name.

Oken tried again, ``Hey Zane.''

The boy turned round.  ``If you're going to tell me to get lost, save you breath,'' said Zane, ``I'm already going.''

``I was actually going to apologise.''  

It was the first time Zane had really felt that there was something human about this man.  His emotions had seemed so robotic in the apartment, yet now, he seemed far much more genuine.

``I'm sorry I went crazy at you.''  His voice was almost a whisper, almost a passing thought in the cold breeze.  `` I can't imagine how mixed up everything must seem for you right now.''  

Zane hadn't stopped walking and right now Oken was trailing behind him by a few feet.  The master was carrying the black holdall.  He was still going to the Zone, he had no choice on that detail, but he had decided he was still going to use his weapon also.  He just wanted to make peace with the boy.

``I do have a question for you though.''  Zane stopped and turned to face Oken.  The man standing before him could easily have been mistaken for a guy in their early forties.  The grey hair made it so.  

Oken smiled at him.  Finally he had gotten the boys attention.  A car zoomed past them, breaking the air as it did so and letting off a tired moan.  Zane looked at him expectantly.

``When are you going to give it back?'' he said.  Zane was confused.  What the hell was he talking about?  Give what back?  Was it some kind of cryptic message about control, power, love?  What did the man mean?  His mind conjured up scenarios and ideas, but nothing seemed to fit the context of the man's description.

Zane shrugged and shook his head slightly.  He had no idea what he was talking about.  The inventor pointed at the watch on Zane's wrist.  

``My watch,'' he said, ``I presume you brought it back as proof of your jump and just forgot to give it to me.''  

The watch?  It wasn't even his?  He had studied the inscription many times, just as Kiele had.  The watch had been a gift to Rob, not a particularly loving gift, but a gift all the same.  He looked down at the watch and then back up into Oken's eyes.

``Sorry pal,'' he said candidly, ``but this watch belonged to a guy named Rob before it was mine.  It ain't yours.''

``Ahh Rob,'' said Oken chuckling, ``you have no idea how much that name pains me.''  He walked right up to Zane and put his arm around him.  ``Let me tell you a little story.''  He started walking and it was all Zane could do but to start walking too.

A tramp with a small dog had decided to pick a fight with another tramp.  It appeared to be a territorial dispute.  Something about benches and papers.  An unimportant detail in the presence of the current conversation.

They walked together slowly.  Zane turning to look at the man's face every few minutes.  He was expecting him to being speaking any moment now.  After a few minutes Oken didn't disappoint.  In truth, he had been listening to the tramps arguments, but he wouldn't have ever admitted that.

``Rob was a name my parents sometimes called me,'' he said.  ``Or more accurately, The Reverend Oken Brown, R O B.''  Zane furrowed his brow and the man continued, ``Whenever we had discussions about philosophical or current affairs issues, my father would always be dismayed at how black and white I saw the world.  Always picking the side of the minority.''

The tramp match had broken up now, ending in a flurry of newspaper as the two parted.  Electronic papers offered far better protection against the cold.  For a start their circuitry emitted a slight warmth which acted like a mini electric blanket.  Tape together a whole bunch of them, and you had yourself a real nice bedtime cover.

Oken continued his story, ``My father used to say I was just like a priest, and so the name 'Reverend Oken Brown' stuck.  They knew I hated it, but whenever I showed my humanitarian side he would always exclaim something like, 'There goes the holy man again'.''

He seemed particularly saddened by this tale and Zane put a hand round his wrist, almost hiding the watch from view, as if by that simple act, he would be able to sooth Oken's pain.

``On my nineteenth birthday, three days before they sent me off to war, they gave me this watch.''  He sighed, ``They couldn't even let it go for one day.''  He shook his head and smiled, ``I never wore it once.''  He looked at Zane.  ``Where did you find it?''

Zane hadn't expected the last question.  He was far too interested in this different side of Oken.  During his time in the guys apartment, he had seemed so different, down to business, unemotional, almost unbreakable.  Until Zane had stated his demands.  Then he had seen the first change in this mighty character.

``A lady gave it to me.''

``Who?''

``Her name was Kaitlin.''  He replied.  Suddenly Oken's eyes became slightly redder.  ``She had so many clocks and watches Oken, it was fantastic.  It was like a shrine to time in there.''

``Is that so.''  He wanted to say more, but couldn't for fear of actually crying.  Oken held it in.  He bit his lip.

``Something wrong?'' offered Zane.

Oken hadn't noticed that he had stopped walking and now, as they stood on the street corner, he turned his head and looked over at where the house of his mother stood.  He hadn't spoken to her since coming back from the war, and that had only been a short visit, just to let his parents know that their son was alive.  Kaitlin had begged him to stay, but he had been too hurt by their disregard of his humanity.

``Kaitlin is my mother Zane.''  

The boy hadn't seen it coming, even though all the pieces had fit into place.  He had been so preoccupied by the fact that Oken was beginning to sound truly human that he hadn't had the mind to think it through properly.  

Oken started walking again, driven by the urge to prove himself even more.  He would go to the Zone.  He would become the master he so desperately sought to be.  Jay?  Kiele?  They meant nothing to him.  He hadn't met them.  He asked one more question of Zane.

``Is she OK?''

Zane hadn't expected that question either.  Could he really tell Oken that his mother was dead?  Perhaps it would change his mind, finally get him to see that changing the future mightn't be such a bad idea?

``She was killed by Jessie.''  He had neglected to mention it during his recollection of the events as in all honesty, he hadn't even processed it fully.  Jolie had told them about it earlier in the day.  This crazy day.  A day filled with despair, hope, sadness, love.  His emotions had taken a real beating.  

Oken let out a sigh.  His mother.  Though he hated what she had done, he still honoured her.  In his numerous conversations with Ruben, the dark skinned fellow had always tried to get the two to reconcile their differences, quoting 'Honour thy father and thy mother Oken.'  It had generally ended in them having a play fight, ruffling each other's hair.

Something was pushing its way into Oken's mind.  He had the power to change this.  He could make it all different if he wanted.  The power of hindsight was his.  He had never wanted to build a time machine.  He had known it was too dangerous, plus he couldn't quite get his head round some of the theories.  He had so many questions for Zane.  Could he really change everything?  Should he?

Zane looked down at the watch and his face turned to one of horror, the time.  It was.  Time.  Kiele.  The accident.  It would be happening any second now.  Where was he?  Where was she?  He had been so completely absorbed by his conversations with Oken, that he had forgotten to check the time.  

They rounded the next corner and instantly Zane recognised it.  It was the street from the picture.  Across the road there were more people than he expected.  Milling, walking running.  He searched for his sweetheart, his destiny.  She wasn't there.  Why wasn't she there?

Oken had noticed something was wrong.  The boy had stopped this time, searching desperately for something across the street, Oken joined him in the search, just what was he looking for?  Then all at once, Zane saw a flash of purple.  He ran to the edge of the road and saw the same car hurtling down the road as he had seen in the picture, stationary, crushed.

Was it Kiele?  He couldn't tell from here.  The flash of purple was visible again and she emerged.  Like a body coming out of the water for air, her body exhumed itself from the crowds.  Standing there at the edge, she looked one way, and forsaking the other, started to cross the street.

Zane leapt forwards, shaking off the grip which Oken had suddenly initiated.  The car was getting closer, but he could make it.  He could save her.  Again.  He would protect her.  He was halfway across the road now but the driver of the car still hadn't spotted him.  Kiele wouldn't have stood a chance.  Zane's senses honed.  He heard nothing else but the thundering of his own footsteps as he made his triumphant journey across the asphalt.  

Several passers by looked across at the running boy but nobody said a word.  No one shouted look out, be careful, watch yourself.  No one cared.  He was an absent blur to them.  A free spirit, doing whatever he wanted.  If he wanted to get himself killed, let him, they thought.  

Kiele still hadn't noticed Zane as her second foot left the relative safety of the pavement.  She was still looking in the wrong direction.  Zane put his last ounces of energy into throwing his body forward, pushing her out of the way.  He watched as she spun backwards, completely amazed at how she was now airborne.  She hit the ground and the car hit him.



\thoughtbreak



Kaitlin had been as hospitable as ever.  She had let Kiele sleep for a while and had fed her up good with an assortment of cakes and biscuits.  Kiele had enquired about Jay, but had gotten no reply.  She hadn't asked about Oken, figuring the woman had probably gotten bored of her questions.  

The two of them had sat there in relative silence for a while, occasionally asking the other a simple and unobtrusive question.  The room was different to how she remembered it.  There were no clocks or watches and though Kiele desperately wanted to ask, the only remnant of the future remaining in the past was the Rumchum Exo 4.  Just what was it with this particular piece?

Kiele felt it rude to ask, but couldn't help herself.  ``That's a nice watch,'' she said.  

Kaitlin laughed, ``No dear,'' she said, ``that is an expensive watch.  Bought for a young man as a peace offering.''  Kiele was intrigued.  Kaitlin hadn't been so open about it before.  

The young girl didn't want to pry, but the questions kept on coming in her mind.  ``Who was it for?'' she asked.

``My son.''

``Rob?''  It was the next logical question, but it had been stupid of her.  How could she have known the inscription on the back of the watch from all the way over there.  She recovered quickly, ``I'm sorry,'' she said, ``I took a look at the watch earlier when you went to find us something to eat.''

Kaitlin smiled at her.  ``It's OK dear,'' she said.  ``I'm not mad.''

Kiele smiled back embarrassed at her indiscretion.  She wanted to ask more, but something stopped her.

``Rob wasn't his real name,'' the older lady said suddenly.  ``It was a cruel joke we used to use.  Truth is if I hadn't gotten that inscribed, things could have turned out quite differently.''

``What was his real name?'' Kiele asked, sipping her tea.

``Oken,'' she replied, ``Oken Brown.''  

The young girl could hardly contain her surprise.  Unwittingly, unknowingly and completely unexpectedly she had stumbled upon a veritable diamond in the rough.  This world had seemed so cruel, so brutal.  Yet here was Kaitlin, loving, kind, caring, with exactly all the information she needed to meet her parents.

``He lives a few streets down,'' she said, ``but we haven't spoken in years.''  She took a gulp of tea.  ``If we see each other in the street, he nods to me, but nothing more.''

Kiele was genuinely saddened by her story.  How could Oken be so cold? she thought.  It just wasn't fair.  Of course Kiele didn't know the full story.  They never do.



\thoughtbreak



The car rammed his body hard.  Bones breaking, muscles being stretched far beyond their limits.  Blood was expelled in huge bursts as it showered the car and a few of the passers by.  He hadn't stood a chance.  His body had been well cared for, but it hadn't been able to fight against the forces of a gigantic bullet.  

The dead corpse flew through the air, scattering particles of dust and smoke, gracefully exiting the world in an arc of mortality.  It hit the ground and rolled once, twice, three times, before coming to a halt in a crumpled mess.  

It was unsightly.  Blood poured from every crack in the body.  The uneven street and slight incline, made the thick liquid embark on a parade down the street, shocking everyone who saw it.  Mothers and fathers turned the children's heads away, youngsters craned theirs to get a better view, some even laughing at the misfortune of the young man.

Kiele picked herself up and looked at her protector.  It was a shock to her.  She clasped her hand to her mouth.  She had known the victim for so long, and now he was lying there dead with no hope of a reprise.  In a weird way she was kind of happy.

Zane picked himself up and looked across at the crumpled heap of the younger version of the antagonist they had crossed paths with earlier that day.  The victim was Jessie.

As Zane had leapt across the road, an unsuspecting Jessie had crossed it in much the same way Kiele had.  Zane had managed to push Kiele out of the way, and land over the other side of the road, before the driver had really even noticed they were there.

Jessie hadn't been so lucky.  He didn't have a protector looking out for him, a guardian angel, willing to give their life for him.  He had crossed the road as just plain Jessie.  He had been on his way to pick up something to eat before the show.  Now he was going nowhere.  

Suddenly Zane felt something deep inside.  Something was wrong.  Of course, without Jessie, the future couldn't happen.  He instinctively felt for the shield generator that he should have placed into his pocket before he left, that he had rehearsed placing into his pocket so many times.  

It wasn't there.  It wasn't there because he hadn't put it there.  There had been no spare power cells.  There had been no point.  It wouldn't have been able to save him.  He looked across at Oken.  If there was one man who had a shield generator it would be him.  Little did Zane know, Oken was already wearing one.  

Oken watched the boy in slow motion as he clambered to his feet and began to shout out across the street.  Everyone seemed to be already ignoring them.  Kiele grabbed at his shirt and tugged.  Something was hurting inside.  Something was hurting deep inside.  She hadn't yet realised what all this meant.  Was she feeling remorse for being pleased at Jessies demise.

``Oken,'' shouted the boy, ``Oken!''  His words were inaudible to everyone except that one man.  History had begun to adjust itself, ripping the boy and his girl from the time frame.  Zane, back to his life, but Kiele?  She had no future, she didn't exist.  Without Jessie, there was no Kiele.  

She looked up at her protector, ``Zane,'' she cried heavily, ``it hurts Zane, what's wrong.''  He realised his mistake.  His mistake had been saving her.  He'd been damned either way.  Her destiny had been to die there.  Either by the car, or by being saved.  

He looked down at her, ``Just a minute,'' he said, ``I'll make it all better, I promise, just give me a minute.''

Oken looked back across the road at the two figures, who were seemingly unaffected by reality.  The wind blew, but their hair stayed still.  People walked round them, but not consciously.  There was another force at work there.  Something stronger.  Old father time?

``Oken, for crying out loud,'' he shouted, ``Why won't you save us?  Give me a shield generator.''  The ripping was more painful now and he dropped to his knees.  His heart, his very soul felt like it was tearing in two.  Losing Kiele had been painful, but this was excruciating.  It was like he was forgetting everything he had ever known.  He had had parents, but he couldn't remember them.  What was going on.

Kiele was experiencing something similar.  Though she knew the man in front of her was her father, she was beginning to feel less and less attached to the broken body on the floor.  People had begun to crowd round him now, the blood still parading across the street as a marching band.

Oken watched them.  His heart was tearing too.  The girl was his daughter.  He so desperately wanted to save her, to save them both, but something stopped him.  Zane's words.  He had never felt like he had done anything for anybody before in his life.  He had always assumed himself selfish, brash.  He had forgotten about his kindness towards Ruben, his adopted brother in name only.  He had forgotten about all the advice he had given to his other Zone members.

All Oken could think about was how he couldn't bring himself to save these two in front of him.  Zane was calling out, weaker and weaker now.  Screaming for the man to do something.  Then Oken realised he was doing something.  His daughter had been born into a family of hatred, that much he had guessed from Zane's descriptions.  What better gift than to take that pain away?  And Zane?  If he made it back, the G-TEP would have hunted him down like a dog, and killed him.  What life was that for a talented young man?

Zane was losing everything now, only two things remained in his heart, in the very core of his soul, Kiele, and love.  She turned to him, her face in disjointed pain.  They were both on their knees now and she kissed him one last time.  The boy held on, he couldn't think of what more to do.  This was the end.  She was his love, and he was hers.

They sat there in an everlasting embrace, frozen in time and space as suddenly they became ghosts and blew away in the wind, their remnants scattered across the streets.  

The smell of death filled the air.  It was obvious that Jessie had died on impact.  His fragile bones hadn't been able to cope with the stresses that the car had imparted upon him.  His legs were a tangled mess of bone and muscle.  Blood oozed from the crack in his head still and Oken was sure he'd heard one passer by exclaim that parts of his brain were visible.  In the distance he could hear the wail of the emergency services siren.  All too often now, they took too long to reach the accident scenes that victims that had a chance or surviving usually died because they didn't receive treatment in time.  

Oken started thinking about the young man's future and realised how much pain and suffering he had imparted on so many people.  Maybe it would have been different if he had been given a second chance?  Oken didn't think so.

But he himself had been given a second chance.  He had seen the fruits of his labour.  Pain.  Suffering.  Though something had held him back before the death of Jessie had freed him.  He had been scared of he unknown.  Scared of making a mistake that would somehow trigger  off events that were even worse.  Zane's words had stuck with him.  

Oken lifted the black holdall in his hand.  The shield generator in his pocket still hummed.  He reached in and switched it off.  The future had already been changed.  It was a clean slate for him now.  There was no way things could turn out anywhere near what Zane had described.  He could have all the things he had sworn he never wanted.  A wife, a family, a real life.  

He took a step forward and another.  Then he turned round.  He walked back to his apartment and closed the door.  It had been a surprisingly short trip.  He opened the holdall and took out his equipment.  He removed the power cells from each of the devices and placed them on his counter.  Then he took the bag and walked out of the door.  

He crossed the hallway and opened the incinerator shaft.  The heat sprung forth, crossing his face and making him reel back slightly.  The opening was around half a metre square and Oken gingerly placed the bag in the gap.  He looked back at his apartment, still visible and saw his desk, the desk he had spent so many days and nights working on the contents of the bag.  He saw an image of Kiele in his mind, sweet little Kiele, he hadn't even gotten to say hello.  He released his grip and the bag fell into the depths of the fire below.

Bethany screamed.

