\chapter{33}
\section{Ulterior Motive}


Saturday came and Kiele was awoken to the sound of Mark rattling her door.  She opened her eyes and blearily looked towards the door.  It was the first time he had knocked on her door in a long time, usually he just barged in.  He was so rude in fact that Kiele had taken to using the lock on the door whenever she wanted some time to herself.  She knew of course that it wouldn't stop him if he really wanted to force his way into the room, but at least then she would have an early warning of some description.

Kiele had forgotten to lock the door the previous evening and now staring at it through hardly functioning eyes, she called out, ``It's open.''  Mark entered the room.  It wasn't often he surprised her, but today was an exception.  He was wearing a shirt and jeans, and in all honesty he looked like any normal father.  Come to think of it, she thought, he looked like a real gentleman.  Like the ones she had read about so often in books or seen on TV.  His usual scruffy demeanour had seemingly been abolished for the day.   

He looked around the room as if it had been a long time since his last visit and turned to face the sleepy princess lying in her bed, covers pulled up to her neck.  It hadn't been particularly cold that night, but she found it impossible to sleep unless she had something covering her.  

``Come on, get up,'' he said almost excitedly.  ``You want to go visit Zane right?''  She suddenly felt very nervous.  Mark was never excited about anything to do with her life.  Though she knew Mark had a vested interest in Zane for some reason, she couldn't fathom why he would be encouraging her to go and visit.  Sure she was supposed to be keeping Zane interested, but Mark wouldn't know she was actually in love with him.  She'd managed to hide it well.  He was definitely up to something.  

Kiele decided to challenge her father.  ``Why are you being so nice to me?'' she asked.  She was now sitting up in bed rubbing her eyes as the light from the window tried so desperately to blind her.

``No reason,'' came the reply.  ``I knew you were going in to see Zane and I thought I'd tag along too.''

``You do realise how bizarrely you are acting don't you?''

``Well don't you want to hear the good news?'' he said brimming over with apparent happiness.

``What?'' she said almost sarcastically.  She knew she couldn't trust a word he said.  She got out of bed, walked over towards the window and opened it.  The smell of the morning air came wafting in and she breathed in deeply.  No matter what Mark had to say, he could never take away the smell of a good morning from her.

``I'm going to ask Zane to stay with us for a while, ya know, until he's feeling better.''

If there had been one thing that Kiele had never thought Mark would say, this would have been in the top ten, right up there with 'I love you' and 'You make me so proud Kiele.'  A part of her wanted to run over and hug the oddly joyous figure standing in the doorway.  Another part knew there was a catch.  There just had to be.  Mark had never done anything nice for her in the past, what possible reason would he have to do so now?

Mark had been unable to sleep that night.  He had been plagued with fears of Zane becoming disinterested in Kiele and not wanting to assist in the plan.  He knew the book had been a success, Kiele had mentioned it to her father.  She had asked him why he had given an abolished text to Zane.  He had simply smiled and said he hadn't realised what it was until it was too late, and that you couldn't take back a gift, but Kiele remained unconvinced.  It must be part of his plan, whatever that was.  She couldn't ask.  Her mind had separated both parts of her life.  She was the crossover.  

It was as if Kiele were bridging two worlds, almost as if she were schizophrenic.  When Mark was around, Zane was just an objective, when she was alone with Zane, everything changed.  She new Mark had some kind of scheme involving Zane and that he wanted her to keep him sweet.  The truth be told, after the accident her thoughts of the scheme had taken a back seat.  

Kiele was also only too aware of her feelings for the boy and how she was falling deeper and deeper for him everyday.  Mark either hadn't noticed, or hadn't cared.  Now she was heading towards trouble.  If Mark tried to unite her real world, including him and his awful scheme, and her fantasy world, which comprised of Zane, she wasn't sure she would be able to cope.

He hadn't realised she had been silent for so long.  Of course Mark knew what was going through her mind.  She didn't trust him and he was well aware of it.  It didn't bother him though.  His design was flawless.  Once Zane saw what he possessed he would be entirely infatuated with it.  He knew Zane had a love for physics.  His test results and recent offer of a scholarship at the largest physics lab in Alendria were a testament to that.  

Once Zane realised that Mark was in possession of Oken's blade, the desire would grip him.  Just as it had Mark.  He didn't need to bet on it, it was a certainty.  Zane would have everything he needed there, a loving home, Kiele and the blade.

``Why ever would you do a thing like that?  Why would he want to stay here?'' she asked her father.

``I need to keep an eye on him, answers your first question, and secondly?  Of course he would want to stay here.  You're here.''  He smiled and just like that it was over.  She was a pawn in his sick game again, his plan to do…...something.  She knew that if she refused to cooperate she would be hurt, badly.  He may even turn against Zane now.  So she had no choice but to go along with him, for now at least.  She would talk when he told her to, walk when he told her to, but in her mind there was a line, and if he tried to make her cross it, she would fight back.  She would fight back like never before.

The young girl scared herself a little with the last thought.  She hadn't ever fought back against Mark in her life.  Come to think of it, this was the only time she had ever really challenged anything he had said.  He was being nice because he needed her onside.  If she made out that staying with them was a bad idea, Zane may refuse, and Mark wouldn't like that. So she decided there and then to obey.  She made the choice to obey, until she decided otherwise.

``I'll have to let Jolie know I don't need a lift,'' she said, beginning to play along with his little game.  Mark smiled, finally the little runt was catching on.  He had the power, not her.  He was going to win this battle and she didn't stand a chance.



\thoughtbreak



The ride to the hospital had been exceedingly uncomfortable.  Mark had been practising being nice.  It wasn't something that came naturally to him and with Zane's impending visit, he had to learn how to behave like a decent human being fast.  Kiele had mistaken it for a genuine showing of emotion to begin with.  It was why she had questioned his methods.  Had she realised what he was really doing, she would have just kept her mouth shut.

Something kept eating away at her, every time her head was filled with a void she began to think more and more about the plan.  Never once before had she questioned what Mark was scheming.  She hadn't ever felt the need.  Before the accident she had possessed no real feelings for Zane.  

She knew Mark wasn't that intelligent, but she did know that he could be incredibly devious.  What was it that Zane had that Mark would want?  She couldn't fathom it.  What scared her more was that by cooperating she was drawing her infatuation closer and closer into the jaws of the crocodile.  It was an apt analogy, Mark's temper had the snapping reaction of an angry reptile about to chew into its juicy prey.

Was she making a mistake?  What choice did she have?  The ride to the hospital had been filled with these questions and many more like it.  She was in far too deep now.  She should have called it off at the start.  Would Mark have still hurt his daughter then?  She'd shaken her head at that point and giggled to her self.  He didn't even class her as his daughter.  She had never seen one shred of evidence that would allude to it anyway.

No, maybe it was better this way.  She could keep an eye on Zane too, for the side of the light.  She would protect him.  Just as he had done her.  She would make sure that he never came to any harm.  Kiele really did love him.  It was beginning to strike her even more now.  It wasn't just a crazy college crush, like Janus had described.  She knew him deeply, his soul, his very being.

Kiele longed to kiss him.  Those sweet lips she had watched for hours as they talked.  Once or twice, when he had become sleepy during her afternoon visits she had wondered about stealing a kiss., but every time she had denied herself.  She wanted it to be when Zane was fully coherent.  When he wanted to kiss her too.  The moment would happen.  It would be a sealing of fates, a promise that she would forever hold in her heart.  Once they kissed, she just knew she would fall into his heart forever.  

It was partly a by product of Zane's good looks and unmistakable charm, but also of her father's consistent resentment of anything remotely resembling emotion towards her.  She hadn't ever given any part of her heart to anyone and she knew that once the blood began to flow, she wouldn't be able to stop it.  Not for anyone.  Still, she had to time it right.  Keep Zane hanging on, just for a little longer, till Mark had gotten what he required, then she would run away with him.  Then they could be together, to use the tired cliché, forever.  She was sure Mark wouldn't chase her then, once his plan was executed, he wouldn't care.

Mark had often remarked that he had had her for a reason, and had always suffixed it with phrase like, 'but it wasn't so you could be insolent' or 'but it wasn't to buy you expensive gifts.'  She finally felt that she was being used for that purpose.  To be honest, she had never felt more used in all her life.  Kiele was being fed, watered, clothed, for one reason, to keep Zane interested.  It all came back to the plan again.  At that moment the car coming to a stop in the parking area broke her train of thought.



\thoughtbreak



They walked into the foyer as Kiele had done many times before.  'Today would be different', she thought, 'today would be the last time'.  Mark had enquired about how Zane had been doing a few days ago.  She had informed him that the doctors had said he was able to go home, if someone was available to look after him for a while.  When Zane had told them he lived alone, they had rescinded their offer and told him he would have to stay in hospital for another two weeks minimum, Zane had been surprised, but his government insurance had covered it.  Now Mark had offered to take care of Zane, Kiele was pretty sure that the doctors would allow him to leave once more.

Kiele pressed the button to call the lift and watched as it slowly pulsated with light.  Mark, still in his new and improved outfit, stood beside her, letting her lead the way, making her feel as if she was in charge.  It frustrated her insanely.  She knew exactly what he was doing.  He was treating her like she was a five year old child.  Again.  He had never been so patronising to her, but then they'd rarely been out anywhere together for any appreciable length of time.

Eventually the lift arrived and was signified by the sounding of a small tone from the small speaker.  The two of them waited for the doors to open and then stepped inside without saying a word to each other.  Kiele pressed the button for the third floor and the lift made its weary way up the shaft to arrive at its destination.  She had never liked travelling in lifts, the noise of the cables and pulleys always scared her.  

She couldn't remember it, but when she was about two years old, Mark had found great pleasure in putting Kiele in empty lifts, pressing the button and then running out before the doors closed.  He would then race the lift up the stairs to meet her at the required floor.  When the doors opened she was always sat there on the floor screaming at being left on her own.  When she finally cottoned on to the fact that Mark was coming back each time, she had stopped crying and unsurprisingly as soon as there was no more reaction, Mark ceased in his sick little game.

The lift doors opened and the two of them walked out, Kiele stepping slightly ahead of her father.  The pair continued down the hall and reached the door to the ward.  As they entered, Kiele could see that Zane was reading again.  He had told her that he'd finished that damned book on Friday.  She guessed he must be reading it through again.  It made her feel slightly sad.  Didn't he think about her when she was gone?  

Zane was still deep in his book when the two of them arrived at the foot of his bed.  He looked up, not expecting to see Kiele, but certainly not expecting to see Mark.  He jumped slightly and hid the book under the covers.  

``It's a little late for that,'' said Mark sternly.  Zane looked down sheepishly.  He felt ashamed, but he hadn't expected to see Mark again.  He'd thought the gift had been a one off.  Maybe Kiele had mentioned his aptitude for physics, or maybe he just imagined that it was something boys his age would be interested in.  He was of course wrong, there was only one boy Zane could think of, who would have enjoyed reading that book, and that was himself.  It had merged his and Oken's world, giving him the idea that there really wasn't that much separating him and the master.

``Sorry Sir,'' came the reply.  

Kiele couldn't quite believe Zane had called her father sir.  She couldn't even bare to call him Dad, let alone give him the respect to call him sir.  She guessed it must be different for Zane.  He was unaware of the way Mark usually acted, the way he treated her.  Had he known he probably wouldn't be calling him 'Sir' right now.

Zane adjusted his pillows and sat bolt upright in the bed.  He began wiggling his toes, trying to overcome the pins and needles which had gripped his lower legs.  On the unit next to him, a glass of water sat and he tried, in vain, to reach it.  Kiele saw his attempt and leaned over to get it for him.  He drank, the cool liquid quenching his thirst so good.  

When he was finished, she took the glass from him and placed it back onto the top of the unit.  The underside of the glass was slightly wet, probably a result of an overenthusiastic nurse, and a small ring was visible from where Kiele had picked up the glass.  She leant over and hugged the boy, quietly asking if he was OK.  This was the first time she'd openly shown her affection for him in front of her father.  Zane nodded, but surprisingly Mark said nothing.  It hadn't been what Kiele had expected.  She had expected him to call her to one side and throw her into a wall again.  Maybe Mark was a little more complicated than she had first thought?   

``So I hear you're allowed to come home now?'' The sentence was more of a statement than a question, but Mark managed to turn it in to one anyway.  He was trying to be likeable, something which a) he wasn't particularly good at and b) wasn't required for his day job.

Zane shook his head.  ``I wish, but because I live alone at home, they've decided to keep me in for another two weeks.  Just to be on the safe side.  I feel like I could run a marathon right now.''  He was getting carried away with himself, ``Well almost.''

He looked genuinely depressed.  His mouth turned down at the edges.  Kiele smiled.  He looked so cute, like a downtrodden puppy dog.  She suddenly realised how happy he was going to be when Mark announced he could stay with them.  Suddenly she was mad at Mark.  How come he got to be the good guy?  She hadn't realised it before, but Mark was set to become a shining star through his actions.  Zane would be so happy to get away from the hospital.  She wished it could have been her decision that would make him smile.  Alas, it was yet another thing that Mark had stolen from her.

Mark spoke as if he'd been practising the sentence all week.  ``Well I was thinking about your situation,'' he began, elongating his next word, ``a-n-d, how about about you come and stay with us for a while.  Just till you get back on your feet?''  Zane's face lit up.  His eyes were beaming now and he looked over at Kiele and smiled.  

``You really mean it?'' he asked.

``You betcha!'' came a forced reply. 

Zane was grinning from ear to ear.  He turned to Kiele and whispered loudly and in plain sight, ``Did you have something to do with this?''  Kiele truthfully shook her head but her father jumped in.

``What do you think Zane?  That I came up with the idea on my own?''  Zane grinned inanely.  Kiele was seeing red.  Why had he lied?  She didn't want to be part of his sick games any more.  Sure she had wanted Zane to stay.  Sure she had wanted it to be her idea, but it hadn't been.  Kiele wouldn't never have suggested it because she knew at every level that Mark would have refused.  She didn't want to lie to Zane, but now she had no choice.  If she contested Mark's words it would only make things worse.

Zane grabbed her hand and pulled her forward.  Suddenly her heart fluttered, it was like she had been swept off her feet.  He took her hand in his and ever so gently raised it to his lips and tenderly kissed the back of her hand.  Her heart melted, and once again she yearned to kiss him properly.  She saw Mark out of the corner of her eye and the moment was broken.  

Mark hadn't been impressed with what he saw, but then as long as Zane performed the tasks he had set for him in advance, whilst he lived under his roof, everything would be fine.  If the little girl started to become a problem he would just have to take care of it.  

Kiele blushed and carefully withdrew her hand, not so fast as to make Zane think she hadn't appreciated his gentlemanly display, but not to slow as to almost request an encore.  Zane looked across at Mark.

``I'd give you one too, but I don't think you'd appreciate it as much.''  He giggled and Mark even managed a small forced titter.  He extended his hand towards Zane.

``We men prefer to shake hands,'' he said smiling.  Zane reached forwards and took hold of Mark's hand, the same hand that, as Jessie, had pulled the trigger on Kaitlin's life only two days previous.  The two of them shook hands for a few seconds before breaking apart.  It was a union which worried Kiele.  These two seemed to be getting along too well.  On the one side of her was the man of her dreams, her literal hero.  On the other, a gremlin in her nightmares, the very epitome of hell on earth for her.

``I really appreciate it Mr Matthews,'' said Zane.

``Please,'' he replied, ``call me Mark.''

They both smiled and Kiele decided it best to join in, lest she be questioned for lacking joviality.  

``Can we stop by my place and pick up some of my stuff?'' asked Zane.

``Of course.  Let me go find a doctor and we'll get you discharged and ready to go.''  

Zane could hardly believe his luck.  He had been expecting to stay in this dingy hole for another two weeks, now he got to go and stay with Kiele and her loving father.  Mark left the two love birds and went to find a doctor.  

``Thank you so much,'' said Zane to Kiele, ``You have no idea how depressed I was getting in here.''  She said nothing but nodded to the young man who would soon be living with them.  ``Living on your own is OK, but living on your own in here, is just sheer hell.''

Kiele couldn't help but wonder if Zane would still call it sheer hell if he knew what Mark was really like.  He didn't seem to be catching on, but then the devil had seemingly been improving his acting skills by the minute.  'A real family man aren't you daddy?  Let's just hope you get what you want from him before he sees your true colours.'  But of course, she didn't mean that, she didn't mean that at all.

