\chapter{25}
\section{}
Cryptic Message  

Ric and Jessie had hit it off from the start.  After the raid on the Zone, Jessie had been taken to Ric to be interrogated.  They seemed to have shared some common roots as the discussion had turned from interrogation to banter.  Ric had then drafted Jessie into the G-TEP, citing his knowledge of the underground scene vital to future investigations.  His name had been changed to Mark and though he still lived in the same town, his facial features had been 'altered' to 'protect' his identity.

Ric and Jessie had spent a large amount of time together.  Jessie had shared stories of Oken's mastery to a fascinated Ric.  His detesting of temporal offenders was much more of an outward display than he cared to admit.  Deep down he had admired Oken for doing on his own, what it had taken groups of people years to do.

Then had came the fateful day, Jessie and Ric had been at lunch at an out of town café when Jessie had mentioned of his thirst for the same power that Oken had wielded.  Both of them knew Ruben had full knowledge of the blade's whereabouts, but they had no proof.  They had beaten him till he was half dead, and yet he still hadn't talked.  He would have made one incredible operative Ric had joked.

The thought of holding that much power in his hand intrigued Ric and over the course of the next few lunches, Ric had probed Jessie for loyalty.  How far was this weasel prepared to go, to get the power he so desperately sought?  As it turned out Jessie passed his little test, and surpassed all expectations.  Ric's job, now becoming mind numbingly boring since the massacre, needed a new lease of life.  Obtaining a time machine was just the ticket, especially whilst doing it under the noses of the G-TEP crew.

A few weeks later Ric invited Jessie over to 'talk.'  He fleshed out his plans to avoid detection whilst developing a temporal weapon, but left it at that.  He made no attempt to suggest methods for obtaining the base device they would need to complete the task.  Nor did he mention how they would get hold of someone with enough brains to turn a temporal weapon into a time machine.  

It was Jessie who had had the brainwave after one too many beers one night.  The brainwave of his life, something that just couldn't fail.  When he had told Ric, he had been beside himself with excitement.  Ric had supplied the DNA samples from the G-TEP archives and had helped Jessie obtain the necessary documentation and permits for the birth.  No one could say these two men were not dedicated.  Now they just had to wait for Ruben to slip up.

It had taken seventeen years, but to be honest, once complete, they would have all the time in the world.  The culmination of events had been foretold.  Ric had informed Jessie that some temporal activity had been spotted in the time-line and that it had matched the signature of Oken's weapon.  Through the surveillance on Jolie, Zane had been found by chance, as a suitable candidate for completing the work.  Zane was, after all, the top academic, not only in his class, but within a two hundred mile radius.  

 Jessie had set his 'daughter' to work on Zane.  Her task was to incite interest in her and keep him on a short leash.  She had done her task well as far as Jessie was concerned.  He had no idea that she had fallen for the boy.

His plan had turned into an obsession.  His life was the plan, he lived and breathed for the moment that he would wield complete and unrivalled power over the earth.  Ric as his co-pilot, they would control anything and everything.  It was a dream, a dream that had taken him through nappy changing, temper tantrums, screamings of 'I hate you'.  Once she had gotten a little older he had fully asserted his authority and the backlash had all but stopped.  Ric had steered well clear, leaving Jessie to do all the hard work.

The final task was to obtain the weapon itself.  Once again, Kiele was to be used here.  It was true, Jessie would never have used his own daughter as a chip in his bargaining.  He knew he would have to prove his seriousness to Ruben.  He would probably have to kill her eventually anyway, else she may spill the beans on their plan to the G-TEP.

It was an extreme plan but so far everything had started to fall into place.  Jessie had needed something special to convince Ruben to give over the most powerful weapon on the planet.  Kiele was that something special.  It had been a sacrifice losing all those years to caring for a child that wasn't even his, but if everything worked out, it would be worth it.  They would finally be able to achieve what they both wanted.  What the world needed.

Throughout the seventeen years, Ric's ambitions had grown steadily.  He no longer wanted just to possess a time machine.  Now he wanted something more.  Something grandiose. 



\thoughtbreak



Ruben couldn't process it all.  Oken had a daughter.  A daughter he had never met.  A daughter he would never know he had.  Jay too.  It was getting too much to bear.  He put his hand to his face.  His mind was becoming confused.  It wasn't working properly.  Ever since his dealings with the G-TEP, Ruben had suffered from strong panic attacks.  They came at various times, when he was stressed, worried, or sometimes even happy.

Would he really give up Oken's most treasured possession to save Kiele?  'It was a beautiful name,' thought Ruben.  If Jessie had picked it, it was quite possibly the only good thing he had ever done for her.  It still upset Ruben that he could no longer use the name his mother had given him.  Ruben, meaning 'see, a son' had been chosen by his mother as a reminder that his father had expected him to be a girl.  When Ruben had been born she had even exclaimed the phrase.  The name had stuck.  Ruben had loved his name.  Michael Stapes just wasn't befitting for him.

Ruben mused further.  He could take whatever Jessie could throw at him.  He could take the torture, the abuse, the hatred, but Kiele?  He couldn't subject her to it, he just couldn't.  Oken's daughter, he had to protect her.

``My daughter was in an accident today,'' Jessie said, breaking the silence.  He thought quickly, his earlier phone call gave him an idea.  It just might work.  

``I caused the accident, or rather I will cause the accident.''  He smiled grimly.  ``Once you have given me what I have asked for I will travel back and show you just how serious I am.  It should be adequate proof that sooner or later you will give it up.'' 

Thinking hard for a way out, Ruben found a flaw in Jessie's outlandish plan. ``How do I know it was you that caused the accident.  That's no proof.''  He was pleased with his reasoning.  His brain had won through again.  

``I've seen evidence at G-TEP, the accident was caused by a traveller from the future and I'd like to put bets on that being me.''  Jessie had been expecting that question too.

``How do I know you didn't just create the accident in the present?'' asked the learned man.

``I'll leave you a message,'' he said, ``on the train.  Give me a time and a place in your history and I'll go back and listen to what was said.''  Embracing his theatrical side he added, ``Then I'll spray paint it on the front of the train for all to see.''

Ruben had to give it to the weasel, it would definitely prove it.  He only had to think of a time and place that no one else in the world would possibly know about.  It would have to be before the Zone, before this cretin had started monitoring his entire life.  Yazmine?  No, he could get to her, make her talk.  It had to be something else.  

Then he remembered; His first date with Yazmine.  She had never shown up.  They had supposed to be meeting under a tree in old man Jones' field.  He remembered his words at the time.  'Guess I can go watch football instead.'  He had been so dismayed that he had actually spoken the words out loud.  He knew the exact time of day the event occurred because he remembered looking at his watch, waiting for Yazmine to show.  ``October forth,'' he said, ``twenty thirty, at around lunchtime.  Old man Jones' field.''

``You got it,'' said Jessie.  ``Guess you'd better go and find out what was on that train.''  The little man arose and went to walk out of the door.  ``When you find out what was written there, when you believe that I'm serious, call me.''

With that, Ruben was left in his room alone.  His heart was pounding still and his legs collapsed from under him.  Lying there on the floor a panic attack ensued.  He began trembling, slowly at first, and then more violently.  The paresthesias had spread to his feet and hands and it felt like his whole body was tingling, whilst almost convulsing at the same time.  

Tears appeared in his eyes before streaming out of the sides like tiny waterfalls down the sides of his face.  Damn that Jessie, damn him.  Damn it.  He sobbed in pain.  Pain for his lost friends, Oken, Jay, Leon, he'd lost everyone.  Now he was about to lose the only thing he'd managed to hold onto all his life.  Oken's Bethany.  

As the attack got worse his brain stepped into save him and he passed out.  The stress on his mind and body had been too much.  A visit from Jessie he could have handled, a visit from Jessie with his normal jibes about how much Oken had deserved to die.  Ruben could have even handled the time Jessie told him how he had pushed Leon over the edge.  However the combination of what he had been told today had been far too much.  His body, now still, rested.  When it awoke it would have to find that train.  



