\chapter{42}
\section{A Constant Reminder}


Kiele was instantly aware of the terror that had suddenly gripped her.  She stood in the hallway, facing her father, shaking like a leaf.  She tried to pull herself together, to get a grip on the situation but her body and mind resisted.  It was almost as if they had been expecting this moment all along and now it had arrived they had succumbed to it's mastery.  

Mark looked so calm, so collected, so terrifying.  Had this encounter taken place before Zane had been living with them, it would have been an entirely different story.  Shouting would have ensued, her room, usually a place of serenity, would have been violated by the words of her father.  Yet here he was today in a state of complete control.  Totally ready to do what was necessary.

``You lied to me,'' he said to her briskly.

Her soul sprang to the forefront and pushed her.  ``I never lied, I just didn't tell you everything.''  Was she really standing up to him?  Was she really going to argue with him?

``I saw your little passionate liaison,'' he said.  ``You're in love with him aren't you?''

Kiele said nothing, petrified by the maniac standing before her.  He had warned her several times.  Each time she had sweetly but distinctly told him that she knew her place, her part in the order of things.  She had of course been lying, but she had never meant for Mark to find out.  Seeing him standing there at the gig had been one of the biggest shocks of her life.

``I think you should answer me,'' he said, ``and please don't try to insult my intelligence by claiming it was just an act.''  He was getting a little more agitated now, the pot that was Mark, had most definitely been stirred.

``I didn't mean for it to happen,'' she said sullenly, ``but I won't lie to you.  I love him.''  Her words were said with such clarity that it surprised both Kiele and Mark.  She couldn't really believe the words that were springing forth from her mouth.  She was acting a little sassy, Mark wouldn't like that, but she wasn't about to just roll over and die. 

``I didn't ask for what you meant,'' he said.  ``Your intentions don't matter to me at all.''  He paused, ``What I do care about is whether you obey me or not, and clearly in this case you have not.  You had a job to do and you failed.''  He looked at the girl in front of him, she was nothing to him, a shadow of a weak little soul, just like her mother.  He had hated her too.

``You can't change the way I feel,'' she said through gritted teeth.  ``Besides, he loves me too.''

``Now,'' he said, ``that does surprise me.  You're not exactly pretty to look at.  I can't understand for the life of me what he sees in you.''

Mark's head was flung to the side by some kind of force.  This was the first thing she noticed.  The second was that her arm was extended.  The third was that it was her hand that was in contact with his face.  She had slapped him.  She had slapped Mark across the side of the face.  Her heart was racing ten to the dozen.  Why had she done that?  Stupid girl! Stupid, stupid, stupid girl!  The years of pent up anger and aggression towards him had just finally gotten to much for her.

Mark stood there, his head now turned to look directly at her again.  She was surprised at how calm he appeared to be.  Then as if by magic he lurched forward and grabbed hold of her hair and began moving away from her in great strides.  It took her a while to associate the two.  She sudden felt the tension on her scalp as thousands of tiny little strands of hair tried to make their escape at once.

Kiele's head was flung backwards, knocking her off balance and to the floor, but this didn't stop Mark, he just kept walking.  Despite his weasel like appearance Mark was actually strong.  He dragged her body, kicking and screaming across the hall floor, the carpet burning any unclothed part of her body that came into contact with it.  It felt as if she were on hot coals and it was all she could do to try and keep hopping from one appendage to the other, in order to prevent the skin leaping from her body as the friction of the carpet claimed its souvenir.

Mark reached the doorway to the basement and stopped.  Whilst they had been moving, the pain on her scalp had been bearable, but now as the blood came rushing back and her heart kicked in with an all new rhythm, wave after wave of agony trounced her senses.  

``Are you going down voluntarily?'' he asked, motioning to the basement.  She tried to blink a few times to shake the tears of the sting from her eyes, but everything was still blurry.  She made out the doorway to the basement.  The last thing she wanted was to go down into a small enclosed space with Mark, but it seemed it was either her way, or a painful way.

She nodded in agreement and Mark stood there waiting as slowly she got to her feet and began walking down the stairs.  The wood of the bannister felt solid in her hands, offsetting the wobbling of her legs.  She could feel Mark right behind her, mirroring each step she took.  As she continued to descend into hell, she suddenly felt a sharp pain in her legs, followed by them giving out completely.

The young girl fell forward gracefully through the air, towards a shelving unit full of goodness knows what.  She managed to put her arms out in front of her in mid air and as she fell against the unit, her arms caressed each shelf, toppling over a good fifty percent of what was on each one.

Kiele's body landed in a confused heap on the hard stone floor.  There were no cuts, no bruises, no visible signs that anything had taken place, apart from the mess on the floor.  How did he always manage that? she thought.  It was almost as if his physical abuse somehow manifested itself as a mental projection, not one ever saw the physical scars she received at the hands of her so called father.

Mark was already on top of her, dragging her by the hair again over to the end of the room.  Her attacker looked up at the clock, Zane would be another twenty minutes minimum and that was if there were no queues, and if he had decided on his choice of food before he arrived at the alley.  Kiele was traversing the floor on all fours on her back, like a gigantic four legged spider.  Her mind was even fuzzier now and she had only just realised that she was actually in the basement.

``Subtle persuasion is an art form you know,'' said the dark figure as he crossed in front of the light, transforming himself into a silhouette.  ``I've been practising it for years, and I thought I was getting pretty good at it.''  The shadow he had been casting on her suddenly left and her eyes were immediately battered with photons from the light, forcing them to close in her less than sober state.

Now Mark was crouched down next to her, his mouth inches from her ear.  ``Then I find out what you've really been up to,'' he said.  ``Then I find out that you have been playing me for weeks.''  She sat there in complete silence, hoping that once his speech was out of the way, he would just let her go.  She had been punished enough, her scalp burning from ill treatment.  Whoever had said that women could hang from their hair had either been crazy, or lying.

``What to do Kiele?'' he asked.  She remained silent, somehow still maintaining the energy for a level of defiance which annoyed Mark.  ``Do you realise what you've done?'' he asked.  ``I had a deadline, and now I've missed that deadline.  People are not going to be happy and it's all thanks to you.''  The word 'you' was shouted and her face screwed up as the pain of his bellowing smashed against her eardrum.

It was the first time that Mark had made any kind of indication that the plan was not entirely his own.  In her dilapidated state, this worried Kiele.  Had the plan been exclusively his idea, it couldn't have extended beyond moderate impact.  Now there were others involved, Mark could be anywhere on the scale, from hired monkey to co-conspirator.  She still had no idea what it was he intended to do.

``What I want from you is simple,'' he said, getting up and walking back into the light again.  Her heart relaxed slightly and her brain began to function again.  She was in pain all over, like after running a marathon and she felt completely exhausted.  

Mark continued, ``I want you to break it off with him.''  She looked up, confused.  ``By breaking his heart, he'll have nothing left to turn to, and will focus all his efforts on completing his work.''  She shook her head.

``No,'' she said defiantly.  ``You can't just turn off my feelings like that.  You can't tell me what to do.  I'm sick of it.''  Her mouth was saying all kinds of things now, and she just couldn't stop it.  It was as if her brain had rewired itself and now it was letting Mark know what it really thought, completely bypassing the usual filters she would have had in place.  

``What are you going to do anyway,'' she said foolishly, ``cut me?  Make me bleed?''  Why had she put ideas in his head?  All at once her mouth seemed to decide that actually a little bit of control may be beneficial, and handed the reigns back to her brain.

``Make you bleed?'' he said.  ``Make you bleed?'' he repeated, picking up a circular saw from one of the benches of the room.  She looked down at his shoes, unable to comprehend the possible nature of the chain of events that were about to unfold.  

``The trouble isn't making you bleed Kiele,'' he said, emphasising the word bleed.  As he did so, he spun up the saw and cut a large slit in a sand bag which had been sitting on a lower shelf below the device, keeping some cables from moving.  As the fabric parted, the sand inside gushed out and small particles of it were whipped across the room by the spinning blade of the saw.  It wound down.

``The trouble is making it stop.''  He walked over to her, saw still in hand and she watched as the sand continued to pour out of the bag, collecting on the floor in a pool of glistening yellow blood.  The blade twinkled in the stark light, almost bragging to Kiele at its previous accomplishment.

Mark knelt down next to her and placed the stationary blade on her shoulder.  He moved the saw downwards, making the blade walk over her body, her breast, her stomach, he rotated it slightly, changing course before continuing down her leg and finally jumping off at her kneecap.  She was breathing hard now, her adrenaline supply had been pumped to all major organs in her body and she could almost feel spasms of energy gripping her.  She dare not fight back physically, Mark would overpower her in seconds.

``I remember seeing a girl once, just like you, brain splattered across the pavement.''  His words were menacing but oh so soft.  ``It'll be interesting to see how this compares.''

He spun up the blade.  The motor kicked in and rotated the ruthless teeth at fantastic speeds.  The noise was incredible, Kiele's heart was at breaking point now, and the spasms had begun to manifest themselves physically.  She had to gain control over her body, convulsing at the wrong point in time could literally kill her.

Mark swung the spinning disk in front of her face, left, right, left, right, almost trying to hypnotise her.  She followed the saw with her eyes, thinking it best to focus on it at all times.  She was now sat up against one of the shelving units that supported a work bench, her back pressed up against the hard wood.

The disk was still spinning, the noise was still unbearable and slowly, but ever so purposefully, Mark began moving it closer and closer to her face.  She refused to scream, but the teeth were chattering so close to her cheek.  She loved Zane, but she wasn't about to leave him all alone with this monster.  She turned her head to the side, exposing her beautifully soft cheek to the whim of the blade.  It came closer still, the air it expelled as it whipped through space, thrashed against her.  The high pitched scream of the expectant saw cut through her even before the gnashing teeth touched her delicate skin.

``Stop!'' she screamed, ``Stop!''  The words felt like complete defeat.  The blade halted its onslaught, but as it pulled away she felt a sharp pain deep on the outer side of her thigh.  She hadn't noticed Mark's hand gently slip the scalpel into her flesh until it had been too late.  The saw began winding down and Mark removed the scalpel quickly.  She arched her back in pain, opening her mouth to scream, but her mind refused.  

It had all been misdirection.  Mark was never going to slice off her face with a circular saw.  How would he explain that to Zane?  She had caved to his demands, but he had still managed to inflict her with a real physical scar.  Nothing too obvious, but a mark that would forever remind her of that day and the price she would pay for disobeying.

The blood began to ooze from the laceration, and as if by magic Mark was already there, bandage in hand.  He tipped some alcohol onto a rag and before she could protest, he slammed the pain soaked purifier onto the cut.  The spirit seeped into her bloodstream and set off an excruciating chain of agony.  She thrust a hand down towards Mark's and tried desperately to claw it away.  She was screaming but she didn't realise, her face not even looking at the cut or Mark.  Her eyes were screwed up in pain until like, a wave of peace, it subsided.  

Kiele was left with a slight throbbing pain and as Mark rudely but expertly bandaged her leg, her hatred for him grew faster and further than it had ever done so before.

``I'd be careful about keeping that clean,'' he said as he got up.  ``Last thing we want is an infection.''  He walked up the stairs and left the dungeon.

Kiele just sat there, regaining some kind of composure and control of her battered body.  He wasn't a father.  He was some kind of grim torturer.  Who had ever heard of a father plunging a scalpel into their own daughter's leg, or threatening to cut them open with a circular saw.  He was one sick man.  

Yet if she disobeyed, she knew there would be consequences.  He had a habit of always finding her, always knowing where she was.  He worked as a salesman, was all she knew, maybe he had connections?

The cut had been painful, but not wholly debilitating.  She could still stand, and after a little experiment, she found she could walk fine too.  Mark had been very clever, maximising agony, but at the same time minimising long term effect, at least physically anyway.

Kiele leaned on one of the workbenches.  It was only now that the true enormity of what she had agreed to sunk in.  She was going to have to tell Zane that their relationship, the most amazing aspect of her life so far, was over.  The one ray of light, the one glimmer of hope in her life had been ripped away from her, by that pig of a father.  Her long term plan was still unchanged, let Mark finish his 'plan' and they could run away together.  Just her and Zane.  

Suddenly the 'plan' was brought to the forefront of her mind again.  She was now more than a little scared.  It was no longer Mark's plan, it was someone else's and it appeared he was just a small cog in a much larger machine.



\thoughtbreak



It wasn't until now that Zane realised Kiele had changed into trousers.  He stood there cradling the sobbing figure that only a few hours ago had been jumping to sounds of Cobery and his crew.  'Just what had changed so drastically?' he thought.  She was crying on to his shoulder now and Zane was beginning to realise that her outburst, had not been directed completely at him.  

Maybe she didn't love him, but she still cared for his feelings and for Zane, that was enough.  He would respect whatever she decided.  He still loved her with all of his heart and if one day she changed her mind, he would be waiting for her.

``Kiele,'' he said softly, stroking her tantalisingly soft hair, ``It's OK if you don't love me.''  Her grip tightened but she said nothing.  Almost as if it were a response.  A yes?  A no?  He couldn't tell.  He held her close as the wind whisked its way through the park, whistling past the bars and slowly turning a squeaky old roundabout.  All the kids in the neighbourhood loved the old little park, unlike the new age plastic and acrylic monstrosities, this one was like travelling back in time, a piece of days gone by sitting right there in their city.

``I'll wait for you,'' he said, almost unaware he was speaking now, the words just springing forth from his soul.  ``I promise I'll wait for you.''

Kiele couldn't quite believe what she was hearing.  She had just displayed what was probably her most violent temper ever in front of him, and yet he still remained calm.  'He must love me with his whole heart,' she thought.  It pained her.  She loved him.  Oh she loved him so much, but she knew what would happen if Mark saw them together again, or more accurately she didn't know, that was what scared her.  She couldn't risk it, not even in secret.  A part of her was praying he wasn't watching them right now.  

She broke away from Zane and walked off in the direction of home, without saying a single word.  Her heart was screaming for her to go back, tugging at her every string, like a toddler to a mother.  Every time she pushed it away, that damn heart kept coming back, pushing her harder and harder.  She bit onto her lip hard.  The pain seemed to quell the agony in her heart.  She bit down harder, unknowingly drawing blood that seeped into her mouth, filling it with that bitter taste.

She wiped a forefinger against the lip and inspected it as she continued walking.  The blood had been coursing through her veins carrying her love for Zane.  She gripped her bottom lip and squeezed hard between finger and thumb.  It hurt, but the pulsing of the blood as it left her body seemed to take away the pain.  Perhaps she could remove her love for Zane this way?  

The blood left her lip in waves, propelled by the forces of her heart.  It ran down her hand and once she knew she was out of sight, she dropped to her knees and sobbed once more.  Why was she trying to kill the pain so quickly?  Did she really want to forget about him so soon?  Her stomach was in knots and her heart in tatters.  She had gone from having it all to nothing in two hours of terror and pain.

She knelt there for a few more minutes before finally finding the strength to rise again.  Her leg was in pain, but that would subside.  There was nothing left for her to do now, she had officially been cleared of her duties.  For now she was free, still a prisoner, but free.



\thoughtbreak



Zane hadn't seen Kiele kneel for he had been in far too much shock.  He hadn't understood, even though he had told her he had.  It made no sense to him at all.  He loved her, and it had been clear she had loved him back.  All those hours in the hospital, the meals she had cooked for him when Mark had been out working, the tickets to C-bex Lunacy, they were all indications of love.  So why then had she decided to leave him?  There had been no defined start to their relationship, they had really fallen into one, but there had been a most definite end and this had been it.

Tears still fresh in his eyes, he wiped them aside.  He chuckled slightly as he wondered what his father would have made of him right now.  He would have probably told him that real men don't cry, that they keep it bottled up inside or something to that effect.  ``Sorry dad,'' he said out loud, ``Sometimes things are far too important to bottle up.''

He slowly walked his way back to the house.  He would work on the device.  He would finish it, and then he would get the hell out of there.  It wasn't that he didn't want to be near Kiele any more, but being close to him was obviously painful for her.  Just what had he done to change her mind?  He racked his brains, once, twice, three times.  Nothing.  He hadn't even given her the flowers yet, not that that should have been a bad thing.  He had left them on her bed for her to find when she had retired to her room.  'A little reminder,' he had thought.  He had to get his mind off her.  At least for the moment.  It was all starting to get too painful.

As he walked back in roughly the same vein as Kiele had done, he began trying to think about the device instead.  It wouldn't take much more to complete, he just had to overcome the last hurdle.  He was pretty confident that the rest of his theories had been correct.  This really was the last step.

The plodding help his thinking and Zane stepped through each individual part of the process.  His mind was a buzz with technology, theories, electronics, fields.  All of them interacting in his brain.  Anyone else would have had trouble just modelling one of these complicated processes with the power of thought alone.  Zane was different, his brain being equipped with something others just didn't seem to possess.  To call him a human computer would have been starkly insulting.  However, in essence that was exactly what Zane was, an organic super computer.  

His success in the realms of physics had been largely due to his ability to simulate complex models in his brain before having to waste time trying them out on paper.  It had been a legacy he had been passed from his father, who had unknowingly applied it to a different field.  Working as a G-TEP agent required the ability to quickly think through a number of possible situations simultaneously.  It was something that just came naturally to them both.

Suddenly his mind jumped.  It skipped back over a previous step and replayed it again, and again, and again.  Zane had made an incorrect assumption.  Something so small that it had been overlooked by himself and Mark.  He changed the parameters in his mind and reran the simulations again.  Everything checked out.  It would of course require testing, vigorous testing, but in theory at least, the job was complete.

He smiled to himself as he walked the rest of the way home.  His journey was coming to an end.  Soon he would be free, totally free.  



\thoughtbreak



Kiele opened the door to her room and was hit by the sweet smell of flowers.  It confused her at first, knowing she hadn't placed any flowers in her room for a good few weeks at least.  She looked down and saw the beautifully combined bouquet of flowers on her bed.

She could almost see the scent dripping off the petals, coating her room with the odour of Zane's love for her.  It sickened her.  At any other time she would have been overjoyed at receiving flowers, especially unexpectedly and especially from Zane.  After the events that had transpired that evening, she felt a lot less lovingly towards the flora.  It was a constant reminder not of Zane, but of what she had done to him.

Zane's tired and confused expression broke through to the forefront of her mind once again.  She closed her eyes and tried to shake it free, hoping so desperately to release the ties which bound it to her thoughts.  Alas her will appeared too weak and his image stayed there, frozen in time and pain.  The last thing she had wanted to do was to upset him, but there had been no other way.  Mark hadn't said so in so many words, but she knew full well what his exit had meant.  Either she fixed the problem, or he would fix it for her.

Kiele picked up the flowers and the love seeped into her hands.  The anger inside her bubbled to the surface and she almost flew in to a fit of rage, ready to tear each and every head from the bouquet.  Something inside her prevented the massacre and instead she just flumped down onto the bed, bouquet still in hand.

The bouquet really was beautiful.  She looked at the intricate details of each flower, how they were so similar, but also how each had their own subtle differences that made them unique.  Sometimes a petal was in the slightly wrong place, other times there was a certain oddness to the pattern and she was certain that one even had a slightly different smell to the others.

Kiele regretted her actions, but she hadn't had a real choice, had she?  Once again it had been one of Mark's fake choices.  She remembered them from her youth.  Though he never called them that, she quickly cottoned on to the fact that when Mark told her it was her decision whether she obeyed him or not, that it was his way of threatening her in an entirely passive manner.

The cold tap was dripping on the sink in her room.  She listened to the rhythmic thump as each droplet fell into the basin and then from the plughole down into the waiting water below.  She put the flowers to one side and stood to her feet, crossing the room and turning off the little drum.  As she did so, she caught sight of Zane coming back home through her window.  He would often look up at her window as he walked past, but today he made no such gesture.  Today he was on a mission.





