\chapter{44}
\section{}
Confession  

Zane arrived at the school shortly before his morning lessons were due to begin.  Kiele hadn't appeared, but then he didn't care.  He had been hanging on to the hope that there was still something there between them, but there wasn't any point now.  It had all been a trick, a cruel little game played by father and daughter, a union of evil.

The morning had passed slowly with people asking him left right and centre where Kiele was.  They had seemed surprised when he had replied that he just didn't know.  In the end he lied.  He said he had just gotten a message from her, that she wasn't feeling well and was in bed.  He hoped she wouldn't turn up at school now else he would look a complete fool.

Maths bored him sometimes.  His grasp of the subject was far beyond that which was needed to complete his courses and it sometimes made for extremely mind numbing sessions in which he would have preferred to just stay at home, working on his own projects.  The only enjoyment he received was pointing out mistakes in the teachers workings out on the board, or pointing out to them that if their workings were correct then they had made some generic assumptions.  Most teachers feared teaching a maths lesson that included the illustrious Zane.  In all other disciplines he was relatively silent.

The sun was glowing outside and its ambience flowed into the room, creating strong shadows from his high vantage point.  One side of the room was lined with windows and these were themselves lined with a workbench.  It housed various mathematical and geometric models, text books and papers.  The lesson hadn't even begun yet and he was already bored.

He took out his personal computer panel from his bag and began to thumb through his files idly, whilst waiting for his lesson to start.  The decryption algorithm that he had programmed to try to read Mark's calendar item was still there.  His finger hovered over the delete key and then stopped.  Just what had been in that file?  He had to know.  Was it details of their date?  Had Mark told her how to act around him?

The algorithm still wasn't complete.  He made some tweaks to it and ran it again.  The output displayed on the screen.



PPFOWI WOJUU JJFJAO EOJQO WDDDD QWHFI....



It didn't make sense.  He needed something else, he was missing something.  Perhaps a key of some kind, or a password.  His cryptography wasn't great, but generally algorithms like this would include a key that would be required to decode it again.  He tried incorporating 'Kiele' into the algorithm, but it failed again.



KKDOS EOOOW QWHHJ JJSOK HHDHS JOOJE.....



He started trying random words, 'love', 'plan', 'betrayal', all meeting with the same failure.  

The teacher walked into the room.  Mr Failburt.  It was a name that instantly ran true with the students who referred to him simply as 'Fail'.  In some ways, the poor old guy liked the name.  He had always wanted a nickname as a child and now he had one.  True, he didn't think it reflected his nature, but it was a nickname nonetheless.

Fail announced his greeting to the class.  It never appeared too heartfelt.  He was short and rather round, with a pair of neat glasses on his nose, wide rims and shiny metal frames.  His cardigan was years out of fashion and he wore sandals for shoes at every time of the year, even in the most torrential rain.

The teacher began explaining the days lesson.  Zane was uninterested, continually tapping away at the keys.  As Fail talked, he could hear the taping of keys and looked across at Zane several times, trying to gain his attention.  Barnaby, who was sitting next to Zane tapped him on the shoulder and Zane looked up at him.

``Fail's getting ticked at you man,'' he said, ``for crying out loud just stop typing for a sec.''

Zane, almost in a trance, hearing no important or relevant information from Barnaby, turned back to his computer and continued to type.  His fingers flashed across the keys, devouring the words he was typing.  He was interchanging keywords whilst altering his program at the same time.  To anyone else, it would have been a waste of time, but Zane's mind was geared for this.  He would break this code.  He started typing in more random, strange words.  

'Kissaki'.  He typed the word in and pressed enter.  He had heard Jessie use the word during their many chats about the blade and it had always intrigued him.  It was Japanese, but also interesting nonetheless.  Suddenly something became clear on the screen, like it had suddenly jumped off the page of a book, like he was finally able to read for the first time in his life.  The foreign language now became part of him, he read slowly, purposefully and with utter dread.

``Mr Krecker, if you are going to continue disrupting my lesson,'' started the failing teacher, ``you had better do it outside.''

Zane said nothing, but simply picked up his bag and laptop, still staring at the screen and walked past his classmates and towards the door.  Fail hadn't expected him to leave without a fight.  He had expected some kind of attack on the mathematical proof he had written up on the board before the class had entered.

The young man continued walking until he was met by Failburt.  The older, much older, man stood in his way.  He breathed onto Zane who was sure he could smell tobacco mixed with an alcoholic substance.  In truth, Fail had taken a swig before starting his lesson with Zane, and was a prolific smoker, though never in front of the students.

``It's a little hard for me to leave the room with your fat ass standing there,'' said Zane.  It was completely out of character.  Zane had never once insulted a teacher.  Sure he had made their lives difficult on a number of occasions, but had never taken to blatant name calling.  It just wasn't in his nature.  Fail was completely taken aback by the boy who stood before him, staring in disbelief at the screen.  It was as if Zane was in some kind of trance.  

``I beg your pardon?'' questioned the teacher.

``I apologise'' said Zane.

``For what exactly?'' the teacher suddenly became interested.  It appeared Zane was going to apologise to him after all.  Then he would sit back down and the lesson would continue.

Zane looked down at the balding man, eye to eye, face to face.  He spoke purposefully and slowly.

``I...am....sorry....you....are..deaf...Now.....get..out...of...my....way.''

Fail moved to one side, utterly astounded at the rudeness displayed by the young prodigy.  The rest of the class were sat there in just as much amazement as Fail.  Just what was up with Zane?  The young man walked out of the door and he heard it slam behind him.  Fail began barking instructions to the class about how they were going to learn about linear expansion theorems.  How ironic that Zane had used an advanced form of those in the algorithm he had just written.

Zane walked down the corridor similar to the one he had cradled Kiele in.  That one had been on the East side, this one on the South side.  His pace quickened and he closed the lid of his computer.  He had to find Jolie.  She would be able to help him he was sure.  He was unaware of the small figure of Kiele watching him as he walked down the corridor.  She had decided to face the music.  She had decided to fight.  

Kiele started after him.  Zane pushed his way through two double doors and raised a hand as light bouncing off of the schools many sports trophies temporarily blinded him.  He blinked a few times, stopping to do so before regaining his vision and continuing on towards his destination.  

His stalker watched him go through the double doors.  She was around fifteen metres behind him.  Just where was he off to.  She had seen him exit Fail's lesson with a bang, his retro clothing distinguishing his, but she had no idea why.  He had been carrying his laptop, but then that was nothing new.  Her mind was jolted by a sudden banging echoing round the walls.

As she squinted to see through the double doors, Zane's figure hammering on Jolie's classroom door was immediately visible.  Just what was he doing?  It was time to find out.  She pushed the double doors as she had finally reached them and they swung open obediently, garnishing the hammering with a squeak of their own.

Jolie opened the door and exited the room.

``Zane,'' she said, ``whatever's the matter?  You can't just go rattling people's doors like that.''  She wasn't cross, but she wasn't particularly happy either.

``Jolie,'' he began, ``you need to see this.  I really need your help.''

She looked confused.  Just what was he asking?  He was in the middle of a lesson, a particularly difficult one at that.

``I can't just leave my class,'' she began.

``Yes you can,'' he replied.  ``This is a matter of life and death.''



\thoughtbreak



It wasn't long now until he was due to make his jump and he was getting nervous.  Suffering from a bout of the flu, Jessie had been told to stay at home by the G-TEP officials.  He was of course fine, but he had required a suitable excuse to stay home.  If he had left the during work hours and they had traced his car they would have noticed him visiting home, something strictly frowned upon during office hours.  Official trips only.

Jessie's stomach was tying in knots.  It wasn't that he was scared of causing a train crash that would almost kill two people.  He was scared of the time jump.  He had no idea what it would feel like.  Would it hurt?  Would it instead be pure heaven?  It was difficult to say.  He had heard it described in both ways.  

He poured himself another stiff drink and took a swig, the cool alcohol calming his nerves and stealing away his anxiety.  He took another swig.  'Not too much now', he thought, 'I need to remain in complete control'.  

He flicked on the TV and began watching some mindlessly boring daytime show.  It wasn't as if there was nothing on any of the other channels to watch, it was more that Jessie wasn't interested.  His stomach turned again.  When would it stop?  He decided to go over the mission specifications one last time.  

Jessie stood up and walked out of the lounge and through the kitchen towards the basement.  He descended slowly, a little tipsy from his earlier drink.  Perhaps he should have stayed sitting a little longer.  Perhaps he shouldn't have had the drink at all.  His mind still a little blurry he sat down at the computer terminal and loaded the file.  The system prompted him for a password and he carefully typed 'Kissaki'.

The system beeped in acceptance and showed the plans to a slightly incoherent Jessie.  His mind still wouldn't focus.  He needed to lay down for a while, the drink definitely hadn't been a good idea.  He climbed the stairs, retired to his room and slept.



\thoughtbreak



``So, let me get this straight,'' Jolie mused, ``You built a time machine from Oken's blade?  Believing  you were working for the G-TEP?''

Zane nodded.  The full reality of his actions still hadn't set in.  He was scared.  He had read the file, he knew what was about to happen.  In a little under two hours, Jessie would be on his way to the past, to attempt to kill Kiele.  He was pretty sure he would fail.  Knowing the events that had taken place, but then something inside him still wanted to stop the event from occurring.

``Zane how could you have been so stupid?'' she said.  ``Why would the G-TEP want to build a time machine?''  He hung his head in shame.  He didn't know.  The excuse Mark had given him had been lame and he didn't want to repeat it.

``I'm sorry,'' he said glumly.

``Sorry?'' she replied, ``Sorry?!'' It was a shout now.  ``You read the bottom line I assume?''  It was a question, though one which didn't need answering.  Of course he had read it.  The chilling sign-off from Ric Jackson, 'Let the Emblem divide my friend, let the Emblem divide.'

``They are going to tear apart the very fabric on which this society is based.''  She was almost screaming now.  ``They are going to destroy everything and all you can say is you're sorry?''  The tears began to collect in his eyes.  He had been so preoccupied with completing his task, so enthralled at finally being able to do something worthy of his parents praise, that he hadn't really stopped to think of the whys.

Why did Mark want it?  What was he going to do with it?  How could he be sure it was legal?  Why couldn't they tell Kiele too?  He broke down, the tears that had been collecting now spewing forth and covering his lap.  

Kiele had been watching the exchange of conversation from behind the glass door, but had been unable to hear the words being spoken.  She now stood with her hand clasped to her mouth as she saw the raw emotion Zane displayed.  Was it for her?  Was he really worried about her?  She burst into the room, flinging the door open and rushing to his side.

``Kiele,'' shouted Jolie, ``this really isn't the time, please go and wait outside.''  The girl was confused.  Was Zane in trouble?  She looked up at Jolie and manifested the confusion on her face, contorting it to match her emotions.  Jolie answered as if able to read minds, ``Yes Kiele, Zane is in a whole lot of trouble.''

``Then I'm staying,'' said the girl defiantly.  Zane put a hand on her leg as she sat next to him on the plush stools.  They were around knee height and covered in a blue material which seemed to shed tiny hairs for free.  The room itself was small, roughly ten feet square, used primarily for counselling sessions.  Usually the glass would have been opaque by now, preventing Kiele or anyone else from seeing into the room, however the mechanism was awaiting repair.

The blinds on the windows weren't sufficient to stop all of the light from entering the room, and though the spotlights in the ceiling did a good job of lighting the room, the sun overpowered them with ease.  There were several units adorning the room, housing books, careers advice, relationship documentation and doctrine of various other natures.

``Kiele, I really think it's best that you leave now,'' said Jolie sternly.

``Let her stay,'' said Zane, adding, ``After all, this concerns her more than either of us.''

``That's just not true Zane,'' said Jolie raising her voice again.  ``It's not just a little problem that affects a few people any more, it never was.  It's the start of a global catastrophe.  We have to warn the governments.''

``It's no use,'' said the boy, ``Ric would intercept anything G-TEP related before it got to anyone useful.''  It was true too.  Ric got to see all reports about G-TEP related matters before they were passed on to higher powers.  There was seemingly no one left to turn to.

``What are you talking about?'' cried a confused Kiele.  ``Who is Ric?''  She was really scared now.  The conversation had taken a tone of urgency she hadn't heard before.  Her eyes were wide and she looked ready to burst with frustration, he eyes flitting from Zane to Jolie and back.  What were they talking about?  What didn't she know?  She felt she should know it, whatever it was.  She shook Zane's arm viciously.

``What is it Zane?'' she shouted.

``Calm down Kiele,'' said Jolie.  ``You're just exacerbating things.''

``Then tell me what's going on,'' she said almost crying, ``I can help.  I know I can.''

Zane looked at Jolie, who in turn looked back at Zane.  He sighed heavily.  He was really going to tell her, about her father, about the time machine, about everything.

``Kiele,'' he began, breathing in and out again as if losing the words he wanted to say.  ``Your father, he's not the man I thought he was.''  She began to open her mouth to agree with him vehemently, but he lifted a finger for her to remain silent.  ``But he's also not the man you think he is either.''

She cocked her head to one side and a confused look appeared.  There was no sign of an interruption, so Zane continued.

``Your father works for the G-TEP.''

``What?'' she cried out.  It couldn't be true.  She stood up, but Zane pulled her back down again.

``He hatched a plan to go back in time and destroy the Emblem, but he couldn't do it on his own.''  He looked down sheepishly at his own existence, ``He needed me.''  

Suddenly everything became clear.  Kiele realised her part in the plan; obtain the trust of Zane and bring him into the family.  He was instrumental to the plan, but she'd never seen it before.  She had had no idea of the scale of her father's scheme.  

Her mind began to fill with solutions.  It still hadn't sunk in.  A time machine?  Destroy the Emblem?  Each of them in themselves were monumental tasks.  Had Zane really done it?  Had he helped bring about the destruction of their society.  A voice in her head spoke, 'You were part of the plan too don't forget.'  Her heart sank.  It was true.  

``Why can't we go to the authorities?''  It was already too late, had she thought the question through, she would have been able to come up with the answer herself.

``Kiele, they are the authority here and finding the names of someone in another construct would be too time consuming.  There's only one thing left to do,'' he looked up at Jolie, ``I have to stop him myself.''  He had been sat with his elbows on his knees looking down at his feet.  Now, looking up at Jolie, the teacher was astounded at how grown up he sounded.  He was no longer Zane the student, he was a responsible adult, ready to take on the consequences of his actions.

Standing there now, all three of them were having difficulty comprehending the task ahead, or the events that had led up to them.  It was only now that Jolie herself was realising her part in the atrocity that was being planned.  She had caused Ruben to slip up, she had led Mark to the device.  She screamed inside, how could she have been so stupid?  She had berated Zane for his part, but she couldn't bring herself to confess to her own.  All three of them had been led by a desire and now their selfishness was coming back to haunt them.

Zane picked up the laptop and passed it to Kiele.  ``You should really read this,'' he said.  ``It's an encrypted calendar reminder that I found on Mark's computer.''  She looked at the screen and her mouth dropped agape.  



Jessie, 



When you arrive you'll find a train marked as 2243 on the right hand side of the platform.  This is the target.  There will be an open door somewhere along the passage.  Remember to close all doors behind you and when you reach the drivers carriage lock all doors with the override control.  You will meet resistance along the way in the form of a train driver, however you will over power him and kill him.  I'll leave those details up to you, but from my perspective it looked quick and fun.  You should punch in code 4453:4499:2283 into the control panel and then get the hell out of there.  The automated system will do the rest.  

Once complete remember to call me.  Don't worry about a thing, neither Kiele nor Zane will never suspect you, and after tonight it won't matter anyway.  I will come over, and together we will end this hypocritical excuse for a government.  

Let the Emblem divide.  



Ric



It wasn't enough, she thought.  Two young women and one young man.  It wasn't enough to stand up to Jessie and whoever this Ric guy was.  He would likely have a weapon, and if it was a firearm, they stood no chance.  What could they do?  There was no one else she trusted enough to reveal the details to.  Or was there?

She pulled out her phone and looked through the numbers.  There was one man who could help her now, one man who himself had a vested interest in the events that would transpire.  Ruben.  She found the number stored as she expected and pressed the dial button.  Zane looked at her inquisitively, but she held up a finger for him to be quiet.  The phone rang and rang, but no one picked up.  Frustrated by the lack of an answer, she tried again.  

Kiele was still looking blankly at the laptop.  She couldn't believe what she was reading.  Her own father.  He was going to try to kill her.  Each time she thought about it it sent a chill down her spine.  Her own flesh and blood was going to try to kill her.  It made her feel sick to the stomach.  She needed to get some air, but there was far too much going on.  She had to stay, she had to keep abreast of what was happening.  

Suddenly he heard Jolie speak, ``No, no, Ruben, please don't hang up.''  She sounded so desperate, like she was ringing up a lover after an argument.  ``Please,'' she shouted, ``we really need your help.''

Though it was only Jolie who could hear his replies, both Zane and Kiele could sense the way the conversation was going.  Not well.

``You can help us,'' she said, ``I know you feel bad about what you've done, but you have a chance to rectify it now.  To save everyone.  I know what's going on.''

Jolie was silent as she listened intently to the other end of the phone line.  Suddenly her face went as white as a sheet, as if she'd seen a ghost, or a corpse she wasn't expecting.  Kiele tapped her on the leg, and tried to grab her attention.

Jolie's voice changed from the frantic panic of five minutes ago to a completely soft and heartbroken tone.  ``She's dead?''  Ruben had just informed her of Kaitlin's demise.  It had been a shock to the young woman who had know her for many years and spent a great deal of time talking to her and gaining her trust, her knowledge and her friendship.  Though initially she had sought her purely for information, Kaitlin had become like a mother to her, always looking out for her and listening to her.  Sometimes they didn't speak for weeks, months on the odd occasion, but when they did, it was as if they had never been apart.

Jolie's eyes filled with tears and and her emotions finally crumbled.  Her diaphragm let off a spasm as she came to terms with the news and an impatient Ruben on the other end yelled loud enough so that both Zane and Kiele could hear.

``See I couldn't even save an old lady, so what chance do I have saving you all?''  The phone connection went dead, terminated by a broken man, looking for isolation.

