\chapter{05}
\section{}
Meeting  

The next morning when Oken awoke, he was reminded of the surprising length of time that it had taken for him to get to sleep.  He reminisced about the evening's events and of course Jay.  Oken didn't want to think about it.  Every time he did, a strange feeling began to wash over him.  He looked over at the half open window and saw the many trees which blocked his complete view of the sun.  He could hear the birds twittering in the branches which hung outside and he smiled.

It took him double the normal time to get up.  His mind was on other things.  Had he been asked though, he would not have revealed that a good ninety percent of those other things included Jay.  He had tried to remove her from his mind as he sat down to watch cartoons over breakfast.  It was always good therapy for a troubled mind Oken assured himself.  He poured out a bowl of cereal and covered it with milk.  He stuck the spoon in and began to swirl it round.  All at once his thoughts were no longer on the cereal and were once again fixed on Jay.  Oken was unaware that he was swirling faster and faster.  Nor was he aware of the closeness of the milk to the edge of the bowl.

The milk left the bowl and Oken jumped, sending the rest of the milk and cereal jumping too.  Most of it landed in his lap, but some made it to the floor.  He began to mop it up and realised that he'd now have to change again before work. Of course he blamed Jay for his little mishap, but deep down he knew that it was his own fault.  He just couldn't stop thinking about her.  It was truly maddening.

He didn't want to admit it though and instead thought it best to avoid the subject for as long as humanly possible.  He finished his breakfast in between fits of hilarity at the comedic insanity which performed before him, spewing forth from the rectangular shaped panel on the wall.  He switched the television off and put his bowl in the sink.  He looked down at his watch and realised that he was already five minutes late for work.  

He put on his shoes at the door, which were now an off-black grey, largely due to the amounts of dust in both his apartment and the library.  The laces were also looking grubby, distorted by the numerous times they had been left undone and had been trodden on all day.  Flakes of mud flew off as he tied the laces and he decided that he ought soon to invest in a new pair.  

Oken was, by nature, a relatively clean man, but today he had just run clean out of time.  He couldn't believe how long it had taken him to do his normal routine and the child inside him immediately shifted the blame to someone else.  Jay.  Had it not been for her, it would have been the makers of the cartoons, or the manufacturers of the toothpaste dispensers which he had wrestled with for at least three minutes during his ritualistic morning routine.

Oken didn't have a car, not yet anyway.  In some ways he was glad he didn't, less expense and less harm to the environment, but in other ways he wished he did have.  Today was one of those days and as he half-walked, half-ran to work, he couldn't help thinking that maybe on his way home he'd buy a car, in case of emergencies such as this, he certainly had the finances.

He passed the shops and places that he usually saw everyday, but somehow they all seemed a little more insignificant than usual.  Jay had been the cause of this too.  Man, why did she keep popping into his head?  Sure she was nice enough, but she wasn't his type, was she?  Did he even have a type?



\thoughtbreak



He reached the library quicker than he had expected.  He pushed open the larger than life door and made his way to the sign-in desk.  His shoes made an all too familiar thumping on the carpeted floor and Oken realised that this was not the first time he'd been late.  He arrived at the desk with a smile for the waiting receptionist.  She was real, unlike in the police station and her tone of voice cut through him like Bethany had cut through Yaz.

``You're a bit late today Oken, aren't you?'' she said in that unmistakably smug tone to which he had become accustomed.  Oken apologised and for a moment was about to explain that it was all Jay's fault, but then he realised that Jay had nothing to do with it and that it was all in his mind.  He apologised again and made his way to his section.

The library itself was huge and stored all the books one could ever need, some in electronic format, which was more common in the science section and some in the more traditional paper format.  The tall stacks towered over him and Oken felt the same dwarfed feeling he normally felt when walking past them.  The books were all arranged neatly in alphabetical order and the stacks looked much tidier than they would have in a library years ago.  This was largely due to the standardisation of book sizes in 2033.  Books were now only published in three sizes, small, big and extra big.  Oken had always despised the term 'extra-big' but it had been a government decision and he was at no liberty to argue.  Since most of the Emblem had been converted to a common language, the word 'big' stood out as easy to read, write and say.  

It was at this moment that an elderly gentleman approached him holding a copy of Kreshtik Skeltars - Of The Spirit Of Time and asked him if he had a copy in 'extra-big.'  Oken shuddered and moved off to the stacks, motioning for the old man to follow.  The pair looked in vain for over ten minutes but the library clearly didn't have what he was after.  They never did.

He apologised to the old man who looked at him thoughtfully for a second.  ``Did I say Extra-Big,'' he said, ``I meant Big.''  Oken took the opportunity to remove the old man from his presence by closing his eyes.  Who had come up with these new standardised names.

``I'm sorry,'' he said, ``but we don't have this particular book in.......Big, either.''  The old man muttered under his breath, probably something about the younger generation Oken thought.  He replaced a rogue book on the shelf and made his way to his desk.  As he looked down at the mounding paperwork and the lamp which had gathered copious amounts of dust, he thought about how nice it would be to have a picture of someone special on his desk like the other workers seemed to.  A voice in his head asked him if he would like the picture to be of Jay.  He gave no reply.

He looked down and noticed the scrap of paper he had been idly doodling on.  In fact he had been writing a poem.  As he looked down at it, he re-read the words and his stomach knotted.  It was one of the lamest things he had ever read and as he sat there, he scribbled it out feverishly.  He had been trying to capture his feelings, in a creative manner of course.  By the look of the piece of paper, it had backfired spectacularly.  

Oken was feeling very very strange.  He had never felt like this before.  A part of him wondered if it was love, but he was too proud to admit it.  He did admit though, that he was looking forward to seeing her again at the next Zone match, if she was there.  He sat down in his chair and looked at the piles of work he had to do.  Some of them were dated six months ago.  Many of them were requests for books which Oken was sure were no longer needed now.  Even so he had to get on with it.  He picked up the first request, ``Comparisons of modern and pre-temporal science'' by ``Erwin Padrio.''  He walked over to the appropriate section and looked through the books.

His gaze was startled when he saw the first book he had ever read on the subject of Temporal Mechanics, ``The temporal nature of time'' by ``Jamilio Hadrenkes.''  He pulled the book out of the stack and caught a glimpse of someone standing on the other side.  Oken noticed something strange about her.  For one thing, she was female.  This troubled him.  He didn't see many females in the temporal mechanics section, nor in the science section come to that.  As he looked closer he could see her bright red hair almost burning in the mid-morning sun.  

She turned and Oken was shocked to see that the female with the bright red hair was Jay.  She had obviously dyed it that night.  He couldn't help notice how different she looked.  She spotted him quickly and shone a dazzling smile which made Oken once again feel this funny feeling.  She reached the end of her stack and entered the one which Oken was currently attending.  She walked up to him and smiled once more.

``Thought I'd come and say hello,'' she said and continued, ``as I was in the area.''  She could see that Oken looked a little awkward, even put out, by her presence.  She wondered if he would have preferred it if she hadn't come at all.  All Oken was really wondering was just how long had she been standing there?  Had she been watching him?  He was sure he would have noticed.

He spoke.  ``How did you find me?'' he asked.  From the moment the words left his mouth he realised the full extent of the stupidity of the question.  The library was the only one for 200 kilometres, and he had already told her that he worked in the science section.  She almost laughed but then decided against it and instead opted to change the subject.

``So,'' she began, ``have you written any books here?''  Her voice was so soothing thought Oken.  He knew he hadn't and thought better of it than to lie to her.  Instead, he decided to tell her about the book he was holding.

``No.  I haven't written any books.  I'm not bright enough for that,'' he said.  ``I wouldn't know where to begin.  But this book here is the first book I ever read on Temporal Mechanics.''  She took the book from him and opened the cover.  With her head down, Oken found it difficult to see her expression through the shiny red hair.  Her face was a picture of pure amazement.  She understood absolutely nothing and as she turned the pages, she realised that this man had a lot more to him than she had first thought.

She remembered how he had been at the Zone, incredibly strong, both in character and in physique.  Then, even though he had been at his own apartment, he had been somewhat shy and reserved towards her.  She had contemplated that perhaps it was just because he didn't like her, but something inside her had hoped it wasn't.

She too had found it very difficult to sleep that night and had decided to give university a miss for the day; primarily so that she could go and visit Oken, although there was no way that she was going to tell him that.  She had kept thinking of the kind man that she knew lay behind the rough exterior.  A part of her wanted to stay there all day, but she knew that she had a thousand and one things to get on with.

She looked up and saw Oken looking at her.  She thought it would scare her, but in fact it made her feel slightly special.

``Wow.'' She said, handing the book back to him.  He nodded and smiled.

``It takes a little while to get into.'' he replied, ``but the ending's a killer.''  As he thought about it, he realised the truth of his statement.  She chuckled and all at once Oken forgot his seriousness and realised how good it felt to make her laugh.  He wished she could stay all day, even if she just sat in the corner and read a book.  Things got so lonely sometimes and to have someone there would have made all the difference.

``I'm sorry,'' she said, ``I have to get back.  I have a tonne of work to do.''  Oken motioned to the stack of papers that lay on his desk and she smiled.  ``I'll see you at the Zone.''

She walked away and Oken sighed.  Deep down he had known that she wouldn't stay, but he had secretly hoped she would change her mind.  She looked back to give him one last smile, and maybe a wink, but he was gone.  She saw him sitting at his desk, head resting in one hand, and pen in the other.

Oken picked up the first book request again, 'Comparisons of modern and pre-temporal science' by 'Erwin Padrio.'  He had carried it with him back to the desk for reasons unknown.  Now he returned to the stack.  He could still smell Jay's perfume hanging there in the air.  It was a beautiful glistening scent, full of sweetness and cheer.  It was definitely not at all like the current trend of fragrances which some bright spark had made mood dependant.  

He picked out the requested book and carried it back to his desk.  It was in electronic format so all it consisted of was a thin sheet of e-ink paper, designed to show any of the books pages at the touch of the screen.  The little tab which protruded from the edge of the book was made from an ageing plastic and Oken could see that this one was in desperate need of repair.  He decided to leave it and bill the borrower who had requested the book when it was returned.

When the time came for Oken to return to his humble abode, he piled the remaining paperwork on his desk.  He had only gotten through the first twelve book requests.  It was true he had been doing other things, besides just book requests, but his productivity had dipped to below twenty percent of his normal efficient speed.

After a quick shower, Oken lay down to go to sleep.  He knew that it was going to take him a long time to drop off, but he lay there anyway.  He turned on the television and flicked through the four hundred or so meaningless channels.  Finding nothing interesting in the first fifty, he decided that it was time to try sleeping.  He turned over and began to think about all that had happened in the past few days.  Within a couple of minutes he was sound asleep.



