\chapter{12}
\section{}
A Prayer  

As the applause of debris and bullets died away, the chaos began to ensue.  People started running wildly, some in the direction of the exits, some just in any direction that didn't look paved with blood.  The atmosphere stank of anxiety and fear, a stark contrast to fifteen minutes ago.  Ruben had been watching intently at the funfair unveiling before his very eyes.  He walked slowly through the swarm of human liquid, which crashed against him like the ocean against the shore.

Ruben couldn't hear anything, and all he could see was the man he had such fond memories of, lying there, dead on the ground before him.  Surprisingly, he looked almost at peace.  Jay was lying awkwardly on top of his torso and from Ruben's angle he could just about see her face.  She was smiling.  He couldn't quite believe it.

The gunfire had stopped long ago, but Ruben didn't care.  His friend, his very good friend was gone.  All his memories, his thoughts, his knowledge, his companionship.  He had been more than a friend to Ruben, he'd been his brother.  A while back, Ruben had gotten himself into trouble with a loan shark.  He had foolishly bet on a fight that he had heard some insider information on.  

Poor Ruben had had no idea that the information was false and he would never have suspected that it had been crafted specifically to entice him to place a bet.  Though well educated, people often used the word gullible to describe Ruben.  Oken had known different.  He had known Ruben as a very genuine soul, who always took what people said at face value.  Maybe he was just too trusting.

Ruben wasn't the kind of guy to shy away from a fight, but when dealing with mob gangs it was either pay up, or end up in a grave.  Ruben had heard of their reputation, going after families and friends.  He didn't want that on his conscience.  Despite his rather robust appearance, Ruben was actually a very loving man.  So he did  what any man would have done in that situation, he told his best friend.

Oken had withdrawn the money for him the following day.  It took him longer than expected because he had lost his bank identification card.  The gang got their money, and Ruben got to keep his life.  The event had brought the two closer together.  They were brothers now.  At least that's how Ruben saw it.  It hadn't been the first time Oken had assisted him in a time of need.

Now, his brother was lying there, dead on the floor.  Though he was dead, the blood oozing from his lacerations made Ruben question the status of his friend's mortality.  The crowds were still running around in fear.  Had the attackers been of a darker persuasion, it would have been like shooting fish in a barrel.

Through the commotion Ruben still found it hard to believe what was happening.  He knelt down next to the two corpses and carefully pulled bodies so their heads rested in his lap.  A single tear freed itself from Ruben's eye.  It skilfully navigated through the raging perturbations in the air, caused by the noise all around it.  As one girl screamed, the sound waves excited the tear into a mambo, before it hit Jay's cheek and collapsed onto her skin, covering a small patch with Ruben's love.

Ruben pulled them further towards him, protecting them and resting their heads in the crooks of his arms.  He reached down to their hands.  The difference was unimaginable.  There was Oken with his strong, large, rough hands, compared to Jay's tiny, soft, delicate pads.  It was at this point that Ruben's self control started to dwindle.  His breathing became erratic and his heart was pounding.

'These were good people,' Ruben thought.  Why did they have to go?  His chest heaved uncontrollably.  Why did they have to leave him?  The tears were fighting to get out now, pushing and shoving at the corners of the dark man's eyes.  He looked up to the heavens.  His chest heaved once more and the grip Ruben had of their hands tightened.  He lifted them up and tried to speak.  Nothing came out.

The well of tears that had been held back for what seemed like an eternity suddenly sprang forth.  Like a family of wildebeest running from a predator, the salt water galloped down his face.  When they hit his lips, they spread sideways, enhancing Ruben's already erratic breathing with a hissing noise.

``P-p-p-please Lord,'' the words came bursting from his lips like cooking popcorn, ``they were good people, and they were my friends.''  The tears continued to stream down his face leaving wet patches on his friends scalps.  He continued through the sobbing reinvigorated and a lot louder, ``Dear Father in heaven, these were my best friends in the world.''  He sniffed and heaved once again, ``An' the only reason that they did what they did, was …......... because they could see no other other …. way...than this.''  At this point he began shouting, ``Please Lord, listen to me, I know I've done bad stuff too, but I know they are sorry.....THEY ARE SORRY......but they can't tell you now.  Let them into your Kingdom.  I beg you.''

Ruben had been unaware that throughout his prayers two things were happening; one, people were fleeing the Zone in their hundreds but two, they were being replaced very rapidly by G-TEP soldiers, who were keen to cleanse the area of temporal disturbances.  Constructs had been placed into quarantine for much less than this.  An entire continent in quarantine?  It had been sheer hell.  

Martial law had been declared throughout, families split up as soldiers set up same sex camps.  Truth be told it was more about providing a quick and efficient workforce than it was about anything to do with temporal disturbances.  Such was the stigma behind it though, that it was used as an excuse for an abundance of crimes against humanity.

The G-TEP forces had pretty much occupied the entire floor by now and one soldier in particular was making his way over to the only civilian, or 'criminal' as he saw it, left alive on the platform.  His stance was firm and he stared down at the blubbering heap of a maggot that was splayed on the ground before him.  The soldier, a one Richard Palmer, extended the arm that was down by his side till it was straight.  The gun he was holding in his hand glistened in the stark lighting of the platform.  Cold and calculating the weapon responded to its masters movements.  In a swift moment Ric tipped the gun to its side, and pulled back the reload mechanism.  The mechanical click echoed round the entire platform, but was unheard by Ruben, still concentrating on his petition to the Lord.

``I Ric Palmer of the G-TEP force, order you to stand to your feet.''  He hadn't realised that his voice sounded so authoritative.  The man before him ignored him entirely.  It was as if Ric had never been there at all.  

Ruben continued his prayers. ``I never ….. ...e...ver..got....to thank..you...my friend.....Lord, please....tell this good man.....''  His voice was almost unintelligible now.  To an outsider, an outsider such as Ric, it seemed like Ruben was sitting there hissing gibberish through his teeth.  Ric had had enough.  He moved his arm and fired his weapon into the ceiling for a good 10 seconds.  Ruben didn't even flinch.  

Ric, looking up to the ceiling shouted out ``Stand to your feet punk.''  It wasn't as if Ruben wasn't listening, the words just had no meaning to him.  His attention was focussed entirely on the two slumped figures in front of him.  Ric shouted again, this time slightly more aggressively, but Ruben still made no point of moving.  

The temper of the G-TEP soldier suddenly snapped and he brought the muzzle of the gun, still super heated from the recent discharge, and planted it directly under Ruben's chin.  The burly man screamed out in pain, gripping his friends hands as he did so.  The flesh burned well and as parts of it seared, others cleaving to the shiny black muzzle, intent on torturing Ruben with its heat.  

Ric ripped the gun away, tearing yet more flesh from Ruben's already misshapen jawline.  Blood dripped on to Jay and Oken's hands and it was at this point that Ruben took his turn to snap.  Ric had intruded into his world of pain by introducing yet more agony.  Wasn't it enough that he and his friends had already taken what family he had.  He didn't want to listen to Ric, but he was sure as hell going to tell him something.  ``I'm praying for the souls of my......my friends,'' he screamed.  ``Can't you leave us in peace, Oh Holy Father take him away...take him away.....'' 

Ric just stood there all the more resolute.  His hair, hidden by his helmet, was starting to get itchy.  He hated these damn uniforms but more importantly he hated being ignored and he definitely hated being told what to do.  Ric had been through countless missions and had always hated being bested by anyone.  He was a driven man, driven to be the best.  This sniffling wreck in front of him had no right to talk to him that way.  Not only was he involved with criminals but he was a cry baby.  It never even entered Ric's head that his state of mind could have been remarkably similar if anything had ever happened to his family or friends.  For now, Ric was king.  He leaned over to speak into Ruben's ear, purposefully and slowly and as he did so his dog tags slipped out from his shirt and jostled gently against the shoulder of the burly man.

``Don't you realise cretin, that I have the power to grant you life or death?''  Said Ric through clenched teeth.  He turned to Leon, who had joined him on the platform and gave an evil little smile.  To his colleagues he always seemed to be driven by hatred and desire, never by love or justice.  His decisions were always made so quickly and with such precision, but consistently lacking in emotion and feeling.  He was, to all intents and purposes, a robot.  Following orders was the name of his game, and he didn't mind one bit.  ``Well, cretin?  Do you realise the power I hold over you?''

Ruben's face contorted.  His teeth clenched and his mouth was dry.  He was more angry than he'd ever been in his life.  Angrier than when his brother stole his little red fire truck.  Angrier than when his wife had left him for a ``better'' man.  It could have been said that right now Ruben was the epitome of anger.  His veins pulsed and he turned to face Ric's ear before whispering.  ``Thoust would have no power over me, if thoust hadn't been given it from the Lord above.''  The words flowed so freely that Ric had to turn his head to see if it was still the same man that sat there before him.  

The two remained motionless for a moment, eyes making complete contact, both absolutely still, calm and calculating.  Ric smiled, turned his head back to the centre and said, ``You call him your Lord?''  He made a small noise of acknowledgement that sounded like a muffled hmm, before continuing, ``Your Lord could never love you.  You can't even follow my orders, so how could you possibly follow his?''

As Ric withdrew his head and shoulders, the anger rose in Ruben once again and noticing the dog tags as they gently caressed his collarbone, he grabbed hold of them with his right hand and thrust his fist downwards.  Ric could never have dreamt of the speed with which Ruben's arm could move, nor the speed at which his head could move, exceedingly fast towards Ruben's shoulder.  The head met the shoulder with a crack.  His nose completely crushed, Ric felt blood start rushing to the affected area, before billowing out all over Ruben's shoulder.  It looked like a miniature red waterfall as it made it's way from Ric to Ruben and then on to the floor.

The other soldiers in the room all readied their weapons and began to take aim at Ruben as Ric stumbled backwards.  Coincidently, Leon wasn't the only one with a headache that day.  Ric's head was throbbing and his ego had been more than crushed.  Ruben grinned before saying calmly, ``It's not about following orders cretin, it's about trying your best always.''  Upon regaining his balance and with absolutely zero remorse, Ric swung his gun up over his head and brought it crashing down on Ruben's poor skull.  The oversized man cocked his head to one side and fell backwards.  'Unconscious fool,' thought Ric.  

Leon joined Ric and the pair of them grabbed Ruben's arms and tried in vain to drag the hulk to their holding vehicle, Leon all the while, trying to hold back the vomit lingering all too closely in his throat, and Ric trying to stem the bleeding from his crushed nostrils.  Ric stopped and motioned for Leon to do the same.  It was no use, the man was far too heavy for them to move on their own.  Sighing, Ric motioned to one of the lower ranking soldiers to bring a gurney on which to wheel the behemoth back to their lair.  As they waited, the veteran surveyed the platform of the Zone.  ``Sure kept this secret'' he mentioned.  

``You're telling me,'' replied Leon in a shaky tone.  ``It's a wonder no one found out about this place before.''  He walked over to one of the walls and ran his fingers along it's rough surface, as if reading it's history.  

``Intel said it's been here for over 5 years,''  added Ric.  He had to admit, he was rather impressed that such an illegal arena had been kept secret for so long.  The supplies, the bodies, just how had they managed it?  In some ways it mattered precious little now.  The Zone was at its end.

``Leon,'' started Ric, his voice changed in tone from banter to authoritative, ``we.......we need to talk.''  The pause indicated that Ric was less than impressed with the young recruit's performance.  Though in Leon's mind he had proved his worth a thousand times over.  G-TEP forces were known throughout the world for their absolute zero tolerance of anything they disliked.  Many civilians and criminals alike had tried to bring G-TEP agents to trial with little success.  They lived by their own law and made up their own rules, but Leon was different.  He didn't see the world the same way as these other gun-ho, trigger happy, zealots.  

Leon walked over to Ric, and the two of them trailed after the gurney, which was now fully laden with an unconscious Ruben.  ``I'm not going to deny you did a great job today,'' said the officer, ``but I get the feeling that it wasn't completely as planned.  You have to be willing to be cold, to kill without emotion.''  

He waved his gun around as he tried to explain his reasoning.  ``These people are scum,'' he began before tasting yet more blood on his lips.  ``They deserve to die.''  He wiped the blood on the sleeve of his uniform.  Leon had slowed slightly and suddenly stopped, head down shoulders slumped.  Ric turned round, still pressing his finger to his philtrum, testing to see if he had managed to stem the flow of blood.  His nose wasn't broken, but it sure hurt like hell and he wasn't about to let the new recruit see that he was actually feeling his injury.

Leon looked at the ground.  Just what had been accomplished today?  Really?  Jay and Oken were not the only ones to have been injured.  Had it all been worth it?  Leon just couldn't decide.  He backtracked in his mind, they hadn't just been injured, they'd been killed, and by his hand too.  The courage welled inside him and he spoke.  ``I wonder if I've made a mistake Ric,'' he said quietly, keeping his head exactly where is was.

``What on earth are you talking about?'' said his superior abruptly.  ``You're a natural killer, you just gotta stop thinking about it.''  Ric had taken out a small handkerchief and was dabbing his nose with it.  There was no denying that Leon was a first class sharpshooter, but his dedication wasn't to killing.  He'd taken the shot, but not consciously.  A subconscious reaction to a predefined stimulus.  Oken moved, Leon fired.  That had been all.  'Ric knew this, and yet he was saying very little,' thought Leon.  

Ric continued talking, ``You popped that guy good.''  He was smiling, but Leon couldn't see that.  ``The scumbag had it coming to him one way or another,'' Ric sneered.

Finally Leon had the courage to speak out.  It was the biggest confession of his life.  His heart was pounding and as he looked at the ground, he could see his reflection in the wet asphalt.  It had been raining since the evening at the Zone had begun and now the ground was covered in a silky lining, offering any onlooker a mirror version of the world to peruse.  

``I really didn't mean to kill him,'' said the young recruit.  His resolution of earlier to 'get his man' was gone.  He was choked up, almost crying and could never have anticipated what would happen next.

Ric ran towards him, arm outstretched, right hand making a gigantic C shape, purposefully designed for cupping young men's throats and forcing them against immovable objects.  In this particular case, the destination was a wall, about two metres behind his victim.  Leon raised his head in response to a grunting roar which had begun to emit from Ric's general direction.  The veteran's blade of a hand hit Leon squarely in the throat, throwing his head forwards into its previous downward position.  As Leon was pushed backwards he lost his footing, but Ric was strong enough for the both of them as he held up the little reject that hung before him.  

The force with which he hit the wall took them both by surprise.  Leon's head was snapped back up by the sudden change in momentum, only to be flung back down again as a result of coming into contact with the wall.  The wall had responded to being impacted by scratching a large amount of skin from the back of Leon's scalp.  He winced in pain, but just hung there, making no attempt to break free.  He deserved this.  He wasn't cut out for this, and Ric was about to tell him just that.  Wasn't he?  Leon couldn't be sure.  His head was pounding and it seemed like nothing mattered any more.  His family seemed a million miles away and he wished he could have been picking raspberries in the fields with his wife, as he had done so many summers ago.







