\chapter{13}
\section{}
Fruit Picking  

It had been the most wonderful summer for the both of them.  Just recently married they could have almost classed the time on the farm as a honeymoon.  Leon had met Shana there at the farm several years previous, whilst picking raspberries.  Though most of the green areas had been either built on, or demolished, a few still remained and it had become a fairly popular idea to grow fruit on them for the public to pick and buy from the land owners.  

Shana looked across the rows of raspberry plants.  Her new husband was about three rows away from her, feverishly picking away at the lush raspberries that stood before him.  She picked off a raspberry.  It was an exceedingly plump specimen, far too good for her husband she chuckled as she popped it into her mouth and bit down on the soft crimson fruit.  She picked off another raspberry, this time in rather stark contrast to the previous one.  It was small, and slightly shrivelled.  'Perfect for my hubbie' she thought and smiled.

She carefully took aim for an overhead bombing of the love of her life, and tossed the raspberry.  It almost floated through the air before landing on Leon's head with a soft plop.  Except, Leon didn't notice.  He was so intent on grabbing the most delicious specimens for him and his wife that he hadn't even felt it as it caressed his giant melon.  Shana had always joked about Leon having a larger than average sized head, and he had always replied that that was what made him more intelligent that her.

Shana unphased by the lack of interest from her husband, picked off a few more runts and threw them singly at Leon.  Again they met with no reaction.  'Well', she thought, 'if he wants to play it like that.'   She grabbed a whole bunch of berries feverishly picking yet more little runts from the bush.  She pulled her arm back and threw them, this time in a much more direct manner.  The up and over approach clearly didn't have enough force, so this time she threw them as hard as she could.  

At least five hit their mark and one, a little squishier than the rest, actually managed to explode on Leon's face.  He looked up at his wife with an unimpressed little grin and then laughed.  ``Don't you have anything better to do than throw our hard earned provisions at me?'' he asked.  As he did so he picked up a small twig and threw it back at her.

``I wasn't throwing the good ones at you,'' she said ducking out of the way, ``You're not worth that.''  They both smiled at each other.  Their relationship was of the kind that they could say anything to each other in jest and it would never be taken to heart.  They loved each other so dearly that Shana couldn't actually remember them ever having a fight.  Not a real one anyway, not like you see on TV.  

``What were you so deep in thought about anyway?'' she asked.  The reply wasn't what she had hoped for.  This was supposed to be their time away from worries and troubles, but somehow Leon found it difficult to switch off.  

``I was just thinking about the G-TEP offer,''  he said.  They had both been finding it difficult to earn money lately.  Shana had a degree in Ancient History, which was all very interesting, but difficult to bring in the money.  Leon on the other hand had been a police officer for several years.  He had been called in as backup on a hostage situation and it was his expert shot that had saved three civilians.  Following this, he had been scouted by G-TEP central command who had offered him a very generous salary.

He still hadn't decided though.  He had three days left until the offer expired.  Did he really want to go into that line of work?  It seemed like it was too good to be true; new house, new location, more money, generous benefits.  G-TEP seem to be the cream of the crop.  Yet something inside him didn't feel right.  Shana climbed her way through the holes in the bushes and joined her husband.  She put her arms round his neck and kissed him sweetly.  

``You're not supposed to be thinking about work,'' she said.  ``We agreed on no work thoughts for the entire weekend.''  It was true, Leon knew it, yet such a big decision in his life, in their lives, deserved a great deal of attention.

``I know sweetie,'' he said lovingly.  He truly was sorry that it had encroached on their weekend, but it seemed like now it was here, it was a good time to talk about it.  He continued, ``I just really needed to think about it, and....'' Shana had turned and was watching a butterfly skitter around the sky with the ease of a leaf being blown in the breeze.  He gently turned her head back towards him.  Placing his finger and thumb on her delicate chin.  ``I needed to discuss it with you.''

``I'm scared Leon, that's all.''  Her voice seemed particularly sad, and he wondered if that was a result of him spoiling the day by bringing up work, or if she was genuinely disappointed in him for considering the offer.  ``You're a good man Leon, you protect people and you are so just, it's scary sometimes.''  She afforded her self a little smile.  Her head had slipped down so she was looking at his neck and she started playing with the daisy chain that she had crafted for him earlier.  Initially he had rejected the gift, but a short sharp look from Shana always had an uncanny way of changing his mind.

She twisted one of the stems of the chain carefully to and fro between her finger and thumb, trying her hardest not to listen to, or become engaged in the conversation at all.  Leon lifted her chin up with his fingers again.  In the setting sunlight he could scarcely believe how genuinely beautiful Shana was.  'Many girls are pretty,' he thought, though he'd never tell Shana that, but he knew of no other that was just so radiant with natural beauty.  She'd had no surgery, and rarely wore make up, entirely in contrast to the way society viewed beauty.

``If I take this job Shana, I'll be protecting even more people.  In an even greater way.  Protecting memories and loved ones.''  Her eyes met his, but still she didn't seem convinced.  She wondered what it was that really drove him.  Was it the money?  The power?  No.  Leon wasn't like that.  Deep down she knew all Leon wanted was to protect people in a just and peaceful manner.  Her mood changed.  She knew her husband.  

She smiled at him before remarking, ``You just want to wear a new fancy uniform, cos you think it impresses me.''  Leon returned the smile and removed her arms from his neck before turning and walking away.  As he did so he joked back, ``Well, what can I say, I know how you feel about men in uniform.  After all why did you throw that bottle at my head the day we met.''  Shana's faced changed  to show a an unimpressed glance.  Leon looked back over his shoulder and poked, ``I had no choice but to arrest you, you know.''  

He laughed and she ran towards him as he tried to dart away from her.  She jumped through the air and tackled him to the ground.  The two of them lay there on the ground looking into each others eyes.  ``I really love you Leon,'' she said.  ``No matter what you do, your heart will always guide you to what's right.''

``Thanks Shana,'' said Leon, ``You know I'm kinda fond of you too.''  She widened her eyes in surprise and disbelief at how cheeky her husband had just been.  She grabbed a handful of raspberries from Leon's basket and smooshed them onto his cheek. ``Oh Shana'', he shouted, smiling and laughing.  It was truly the happiest moment of his life.



\thoughtbreak



``You're a coward Leon,'' shouted Ric, ``a freakin' coward.''  His grip was still strong and Leon was snapped out of his thoughts once more.  ``How the hell you managed to get into this squadron I'll never know.  Sure, you're a sharpshooter, probably one of the best, but there's no way your sorry ass will last if you carry on showing your emotions like that.''  He was shouting so loudly at Leon that it masked the noise of the gurney being inserted into the ambulance.

As he hung there it hit him.  He wasn't saving civilians any more.  Sure he was getting the bad guy, but so many of the G-TEP missions ended in death and destruction.  It was their mark, their way.  It wasn't him.  This wasn't the way Leon Jackson worked, it wasn't in him.  He began to feel the anger once again and desperate to regain some of his honour and some control over the situation shouted back, ``I'm not like you Ric, I...'' 

Before he could finish Ric snapped back all the louder, ``You're damn right you're not like me.  You're nothing like me'' He drew back his spare hand and with the force of what seemed like ten men he punched Leon in the side of the head.  As he did so he relinquished his grip of the young man, tossing him to one side as if he was a worthless pile of garbage.  

The new recruit lay there, unable to find either the will or the strength to get back up.  Suddenly his stomach could last no longer and he promptly vomited out yet more of his lunch, along with the last remaining portions of his pride.  Ric laughed at the weak little being lying there on the ground.  He turned and motioned to the other soldiers.  

``Come on 'men', let's get out of here.''  He emphasized the word 'men'.  He walked to the G-TEP assault vehicle and climbed inside.  Before shutting the over-head door he looked back at Leon and said, ``by the way, this will all be in my report.''  He smiled smugly and pulled the door shut.  The vehicle sped off at great speed, narrowly missing an elderly pedestrian as it did so.

Leon squeezed his forehead with his hands.  Just how had he gotten into this in the first place?  It was never supposed to be like this.  The academy had been a walk in the park, training had been easy.  Yet the real deal, actually taking aim and calculating to shoot someone.  That wasn't Leon.  Shana had been right all along.  She had always voiced her concerns that he wasn't up to this, that it wasn't in his nature.  He'd tried to palm her off with excuses about justice and honour, about protecting the innocent.  In reality, the G-TEP was nothing like that.  

The ambulance containing Ruben's unconscious body still hadn't left yet and Leon felt the urge to accompany him to the hospital.  After all someone should probably guard him until he was questioned.  The driver of the ambulance climbed up into the front cabin.  Leon shouted out for him to wait and the driver obliged, stepping back down again.  Leon walked slowly over to the ambulance driver.  

``I saw the whole thing man,'' said the driver, ``why d'ya take that from the likes of him?''  Leon said nothing.  The driver continued, ``I'll be a witness if you want to press charges against him.''  Leon shook his head.  It wouldn't help.  It never did.  

``Can I ride with him?'' Leon eventually asked.  The driver nodded and opened up the rear door for him.  Leon climbed in the back and sat there motionless, surveying the innards of the vehicle.

There lay Ruben, still as the night's sky, his skin almost shimmering from sweat.  It looked like he'd been painted with diamonds to appear in a stage show.  Leon had always liked stage shows.  They were rare nowadays, people much preferring to see the latest films in 3D, though even the cinemas were fading now.  

He looked up at the drip hanging from the rail above.  Probably not a necessity Leon thought, just keeping him comfortable.  The thin tube made its way down to Rubens arm, before terminating in a sonic needle.  The high pitched hum of the micro-compressor was totally inaudible against the roar of the Ambulance's engines.  There were no sirens, none were needed, Ruben wasn't critical.

As the ambulance made off down the road Leon looked out of the window at the passing traffic.  The people outside had no idea what he'd done, what he was responsible for.  They probably didn't even care.  Leon wasn't looking forward to going home.  He couldn't bear to tell Shana that she had been right all along.  It wasn't as if he was a proud man.  He felt guilty more than anything.  He had promised Shana that everything would be OK.  He had made a solemn promise.  How could he ever look her in the eyes again.  She would forgive him of course.  She always did.  She was that type of person.  To Leon, she was an amazing testament to the goodness that was still prevailing in an otherwise seemingly evil world.   





