\chapter{27}
\section{A Small Victory}


When she arrived home it was already approaching eight and she felt the need to sneak in to avoid detection.  Mark had told her to be back by ten, and here she was coming home two hours early.  Jolie had hired another taxi to take them both home and Kiele was now exhausted.  She had fallen asleep in the taxi a few times on the short ride home and now all she wanted to do was get to bed.

``You're late,'' came a voice from inside the lounge.  

It was Mark.  He sounded angry, but why?  He had given her a strict deadline and she was home way before the curfew.  What did he have to be angry about?

``You said ten pm,'' she said foolishly.

``Come in here,'' he barked, ``You know how much I hate talking to you through a brick wall.''

She walked into the room with the Mt Taleberg bag hanging from her delicate hands in front of her.  

``And what the heck is that?'' he snapped.  ``I'm not made of money Kiele.''  It had been a mistake to bring the bag into the lounge.  Mark wasn't stupid.  He knew who Mount Taleberg was, and he also knew they were the most expensive fashion outlet in the history of time.  

``It was a present from someone,'' she replied.  It was the whole truth and there was nothing he could do about it.  It wasn't as if she had coaxed Jolie into it either.  She had offered, unreservedly.  She had no idea how 'dad' was going to react next.  In her mind she often called him dad, but it was used in much more of a derogatory sense.  When she said it out loud, people assumed it as a term of endearment.  In her own head, she could twist it to be whatever she wanted.  Right now it read this; 'Dad' - a foolish man who has just discovered he has been placed in checkmate by his test tube of a daughter.

As he stood there all he could feel was his anger.  He tried to push it aside so as to think somewhat rationally.  He had to remember his plan, at all times, nothing could jeopardise that.  If he destroyed the clothing, whatever it was, it would arouse suspicion from that teacher.  If he left it alone, Kiele would think she could walk all over him.  His plan didn't have far to go now.  The wheels were already in motion and soon neither of those events would matter anyway.  He decided to let her win.  Just this once.

``Well then I guess you're a lucky girl''

It wasn't the response she had expected, but secretly it had been the one she had hoped would come true.  It was almost like a dream.  She had outsmarted her father.  Well, Jolie had in any case.  Knowingly or unknowingly, it didn't matter, Kiele was proud of this moment.  She turned to walk out of the lounge.  Mark said nothing as she left.



\thoughtbreak



She hadn't slept that well during the night, tossing and turning for most of it.  Yet when the morning had come, she had felt largely refreshed.  It was a typical Sunday morning, the birds were singing high in the trees and she could hear the choir in the nearby church faintly in waves as the wind carried the sound.  She had never been to a church in her life.  It had never really seemed like the right thing for her.  She believed in a higher being, a god if you will, but not in the sorts of things the usual churchy people did.  

Her father had apparently been a church goer in his youth.  He had told her this one drunken evening in front of the TV.  As a result he hated church, church goers, church songs, church ministers, in short, anything that had ever been inside, seen or listened to anything to do with a church.

Kiele climbed out of bed, her muscles aching from the day before.  The refreshment she had felt had seemingly been confined to her mind.  As she stood up straight her body screamed at her to sit back down.  It wasn't ready to get up yet.  Kiele on the other hand was.  She was going to see Zane again.  As she made for the door, her eyes caught the sight of the Mt. Taleberg bag sitting on her chest of drawers.  She smiled sweetly.

The young girl walked out of her room and entered the next door along, the bathroom.  Mark clearly wasn't up yet as the room hadn't taken on its odour of cologne and man.  She locked the door, turned on the shower and slipped off her nightgown.  As she looked at her body in the full length mirror, she was amazed at how little damage she had sustained.  A few bruises here and there, the odd cut and graze.  She was so lucky to have avoided the types of injuries Zane had had inflicted upon him.  She rethought the statement, she hadn't been lucky, Zane had saved her.

When the water's temperature felt right, she stepped into the shower unit.  The liquid began to run down over her body.  She winced as it hit the grazes on he legs and arms.  She had been so tired the night before that she hadn't bothered to have a shower and had collapsed in bed, confused, but pleased that she had finally gotten one over on Mark, the evil dictator.  She began to sud herself with soap and had to hold her breath and bite down to ease the pain.  The soap had been even worse than the water on its own.  Deciding to make it a fairly fleeting visit, she turned off the water and took a spare towel from the pile.  

Expertly covered by the towel, she exited the bathroom and re-entered her room.  It smelt sweet in the early mornings.  She had set the fragrance generator to a combination of candy floss, spring meadow, and had thrown a little bit of toast for good measure.  She found it helped her get up in the mornings.  She looked at the clock, 8:45.  She had half an hour until Jolie was due to arrive.  

Kiele hadn't told Mark that Jolie was coming to collect her.  Sundays were Mark's days.  He did what ever he wanted on a Sunday and she did the same.  The truth was Mark did whatever he wanted every single day of his life, it was just that he made her consciously aware of it on Sunday.  No work, no cooking, no cleaning, no talking.  Just beer, TV and food.

The young girl opened the Mt. Taleberg box and put on the dress.  Looking in the mirror, she was still pleased at how good it looked on her.  She twisted left, then right, then left again.  'Come on Kiele' said a voice in her head, 'we have to get ready to go.'  She picked out some appropriate shoes and walked into the kitchen.  It was long and thin, with what appeared to be a drinks bar on one side.  It would have been a breakfast bar, except it faced a wall.  It was great for preparing food on, but kind of pointless for trying to have a conversation with a family.  It suited this family well, they hardly spoke much unless Mark wanted to shout at her for something and they usually ate in separate rooms anyhow.  

The fruit in the bowl looked like its contents were getting old fast and she wasn't about to make herself feel ill.  She picked out a cereal box, not that Mark had left her much to go on and filled up a bowl.  There was a small amount of milk in the fridge, but she dare not use it.  Mark would have hunted her down and thrown her against the wall again if she didn't leave him any milk for his morning tea.  Looking for an alternative, she tipped the cereal back into its box and prepared to make herself some toast.

The bread was loaded gingerly into the toaster and the dial set.  She always found it amazing that out of all the enhancements to technology, the toaster still reigned supreme in the kitchen for cooking bread.  As she watched the heat panels begin to glow, she was sure she could see something reflecting in the shiny chrome surface of the toaster, over the other side of the room.  She turned around and sure enough there was a small package sitting on the bar.  

It had been wrapped up expertly, so precise.  'Should she open it now?' she thought.  Who was it from?  As she approached the package she saw that it had been addressed to Zane.  Had Mark really gotten him a gift.  She picked it up.  Clearly a book, she thought.  Mark had bought Zane a book.  How peculiar.  As she stared at it a little longer, the toast popped out.  Kiele ignored it.  Her eyes were transfixed on the book.  ``T....em......nat.....me''  The title was practically unreadable through the thick wrapping paper, yet she couldn't help but wonder what was inside.

Kiele turned around, still holding the package and picked up the toast.  She hadn't even realised it had been sitting there for a full two minutes.  Buttering the toast, she gave the book's cover another going over.  It was no use, she couldn't decide what was depicted on the cover.  It looked like a monkey.  Why would Mark buy Zane a book about a monkey?

She supposed she could open the package and then re-wrap it again.  It had after all been Kiele that had taught Mark how to wrap presents.  After he had seen how good she was at it, she was even allowed to wrap up her own Christmas and birthday presents.  It didn't matter to her too much, they were never anything particularly exciting.  Mark just didn't care about her enough to buy her anything she would have wanted, let alone loved.

It was the fact that he had never bought her anything really nice in her life that made this book seem all the more insulting.  Deep down it was like a small spear had just been pushed through her already dysfunctional heart.  He had bought something for Zane, wrapped it up, and left it on the side for her to give it to him.  She knew Zane was wanted by her father for something, but she had no idea what.  Until now she hadn't cared.  The facts hadn't really sunk in, primarily because she had been falling for him.  All she had been told to do was become good enough friends with him that he could be asked over for dinner one evening.  That had been weird enough, but now the book.  Just what was her father planning?

She had never been allowed a boyfriend before, not ever.  She wasn't even allowed one now.  Mark had specifically told her not to fall for him.  He didn't have to know.  She just wouldn't tell him.  Kiele had become a fairly good actress during her lifetime with daddy.  When he had gone off at the neighbours, she had told them that he was dealing with a lot of stress right now, acting the part of a strong confident young woman oh so well.  It was for her benefit more than his, though she hated living with him, it was better than the alternative.

The plan.  She'd heard Mark talk about it on the phone several times.  He had been on about it for a long time.  She knew nothing about it.  She supposed he had been thinking about moving away.  Maybe when she was eighteen he would kick her out.  Maybe that had been the plan.  Now, it seemed a little different, like he was trying to get Zane on side.  The clock chimed its cheery little song.  It was 9:00.  She crammed as much of toast as she could fit into her delicate little mouth and ran into her bedroom.  

Quickly applying some make-up she tried in vain to make herself prettier and to hide the fading evidence of yesterday's encounters.  She adjusted the dress quickly and fixed her hair as best she could.  'Fifteen minutes to get to the rendezvous,' she thought.  That wasn't a lot of time.  She had told Jolie not to pick her up at the house, as it may wake the giant.  Instead she planned to walk halfway down the road.  Jolie had booked a taxi for them both.  

Kiele picked up her small hand bag and almost sprinted for the door.  She was stopped by a figure standing in the doorway.  It was Mark.  He grabbed her by the jaw and pulled her close.  She couldn't help but notice how violent he had become lately.  

``Where is it?'' he questioned.  

``What are you talking about?'' she answered truthfully.  Then she realised.  The book.  ``I put it in my bag to give to him,'' she said obediently.  Mark twisted his head slightly and squinted out of one eye, as if testing her for truth.  

``You make damn sure it gets to him in the condition it was when you picked it up.''

She nodded.  ``Sure,'' she said.  ``What is it anyway?''

``That's none of your concern,'' he said, ``but I guess you'll find out soon enough.''

She thought he was going to tell her what it was, but instead he dropped her jaw and went lumbering back to his room.  She flexed her jaw muscles.  It hurt, but no way near as much as yesterday.  She recomposed herself and left the house to meet Jolie.



\thoughtbreak



When they arrived at the hospital it appeared as if nothing had changed.  They walked past the room where Kiele had been savaged and she shuddered ever so slightly.  The curtains were still drawn over the windows and she instinctively tightened her senses.  

Jolie had picked her up on time.   It would have been OK, had Kiele gotten there on time also.  She had only been three minutes late, but it had caused Jolie to worry and she had almost called the house.  Luckily as the phone had reached her hands, Kiele had knocked on the window of the taxi and startled the young teacher.  The ride to the hospital had been uneventful, punctuated only by the traffic lights and police cars which seemed to be present en masse today.  

As they reached the room Kiele's heart sank a little, Zane still wasn't awake.  Part of her was pleased, she had so desperately wanted to be there when he awoke.  The other part of her was sad.  She had hoped he would be better today.  She wanted to see that cheeky smile again.  

As Jolie walked through the door, Kiele's bag knocked against her.  The weight of Mark's gift felt apparent now, almost heavy.  Kiele still had no idea what was inside, but he would know if she disobeyed him.  He had an uncanny knack for that.

There was no one else in the room.  The nurse had already done her morning rounds and had tended to the patients.  Jolie took a brief look at the chart and Kiele walked over to his side.  The sun was streaming in the window now and creating light patterns on the wall where it hit the shiny chrome of the bed.  

She picked up his hand in hers and whispered sweetly, ``Why won't you wake up?''  As if in response, he stirred.  The monitor bleeped in its alerting fashion and Jolie was roused from the chart.  

``It says here he's been doing that all night,'' said the teacher.  Kiele pulled up a chair and sat down next to the silent boy.  In the early morning sun he looked much more pale than yesterday.  His eyes were closed and his breathing was steady.  Kiele wanted to give the watch back, but he wouldn't have been able to do anything with it even if she did.

There was a fresh vase of flowers on one of the side units and their smell seemed to break the normal clinical odour of hospitals.  Jolie replaced the chart and sat on a chair on the opposite side.  She took up the remaining hand and placed it in hers.  She had no duty to be there, just something inside her had told her that she wanted to.  It had been an odd feeling, breaking into her subconscious at the end of yesterday.  She had so many questions running round in her head.  

Who had crashed the train?  Why wasn't Zane waking up?  What had Ruben meant when he had spoken about the writings on the train?  Why was Kiele's father such an ass?  She hadn't been able to sleep, most of the night filled with musing and meditation.  Now she was back there again with compassion and wishful thinking, praying that Zane would come round.

There was a rattle as the door opened and the doctor walked in.  He picked up the chart that Jolie had been studying and spent the next two minutes flipping over pieces of e-ink paper, before finally letting out a small 'hmm.'  He replaced the chart and asked, ``Are either of you family of the boy?''

Jolie was the one to respond, she was the grown up after all, thought Kiele.  ``No,'' she said, ``Zane doesn't have any immediate family in the vicinity.''

``I see,'' said the man in the white coat, he was the same doctor they had seen the day before and though he had been lenient then, his stance was a little more solid now.  ``Well may I ask who you two are then?'' he enquired.  The two girls seemed frightened to tell the truth, like they had been caught doing something mischievous by their parents.  In Jolie's case, frightened she would get a telling off, as his teacher she probably wasn't supposed to be there.  In Kiele's current situation, wondering if she would wake up with a knife embedded in her eye.

Again it was Jolie who answered the doctor's question, ``I'm his primary teacher at the school he attends, and this is his girlfriend.''  Kiele's eyes widened in shock when she heard Jolie's words and she had to run them through her own mind once or twice.  When they reached three times round she blushed heavily.  Jolie knew she had to make it convincing, the doctor wouldn't let her stay if she was 'just a friend', but a girlfriend, well that put a whole different spin on things.  As it so happened, Jolie was right.

``Ahh, young love,'' the doctor mused.  ``I had a girlfriend once.''  He turned towards the door before adding, ``I've been married to her for twenty nine years now.''  Jolie smiled, but it didn't last long.  She was anxious to find out Zane's condition.  When was he likely to wake up?

``Do you know what's wrong with him?'' she asked in a worried tone.  The doctor silently apologised for the joke with his eyes.  He hadn't meant to be insensitive.  He hadn't quite realised how important this boy was to them.  All patients were cared for by loved ones, some more than others, he thought.

``He should be waking up any time now,'' he said.  ``He just needed a lot of rest after his surgery.  It can take a lot out of a body, especially if it's already been damaged.''  

Jolie and Kiele both nodded.  Kiele had seen how bad Zane had looked when he had been in the ambulance.  She had been by his side while he went to hell and back.  Now all she wanted was for him to wake up.  

The doctor walked towards the door and opened it.  ``I'll be back a little later,'' he mentioned offhandedly.  ``Please don't hesitate to call someone if his condition improves.''  He walked through the opening and closed the door gently behind him.  The sullen sounds of the hustle and bustle of outside faded once more and they were once again alone with the boy.

As Kiele looked at his bandages she couldn't help but feel a little guilty.  It should have been her that was lying there.  Not him.  He needed his rest.  He needed to get up and about.  He was going to be part of her fathers plan.  How had that last one gotten in there?  She sighed; The book.  It was still hanging off of her shoulder and was a constant reminder that 'he' was in the room with her.  In her thoughts, in her actions, Mark was there.  Cretin.  

Kiele couldn't wait till he awoke, she could give him the book, and he would toss it to one side and chat with her the entire night away.  It could of course, never happen like that.  Visiting hours had to end sometime.  Maybe she could slip under the covers and hide there with him.  No one would know.  Then they could spend the night talking, getting to know one another.  It was so romantic.  A voice in her head, who only appeared when she was getting carried away spoke, 'Kiele, you're being silly now'.  Derailed.

As they sat there, watching, waiting, the hand that was in Kiele's began to move.  Slowly at first and then more purposefully, flexing and bending his fingers as if testing the water with his toes before jumping in.  

``Jolie look!'' exclaimed Kiele.  Jolie turned to where Kiele was pointing.  Her eyes widening and her mouth smiling.  It seemed like the prince was awakening.  He squeezed her hand once, twice, three times.  ``Zane,'' she whispered, ``Zane, are you awake?''  A groan garnished the room as the young man started slowly but surely rolling his head.

``I'll go and get a nurse,'' said Jolie, rising to her feet and hurriedly leaving the room.  In an instant Kiele was alone with him.  Alone with Zane.  She slyly bent forward and kissed him on the hand.  As she retreated, she smiled sweetly.  It was no use.  Despite her fathers instructions, the fickle beast called love had ensnared her.  She couldn't tell him straight away, but as soon as her father was done talking to him about his stupid plan, they could be together.  

Zane began gasping a little, before coughing and finally coming to.  He blinked a few times, still unable to focus on anything in the room.  Jolie had returned now with the nurse and the two of them took up a defensive position on the left hand side of the bed.  The nurse went over to the monitor briefly to check his vitals before turning and facing the patient.  

``Zane,'' she called slowly, ``Zane can you hear me?''  He made no audible reply and she pulled out a small device and shone a light into his eyes.  She tugged at one side and a small e-ink screen dropped down.  ``He's waking up for real now,'' said the nurse.  

``Where am I?'' came a very groggy, squelchy voice.

``Zane you're in the hospital, do you remember?'' said the nurse.

``Yah,'' he replied a little clearer now, ``I remember.''  He was still turning his head left and right as he spoke, trying to focus on anyone or anything.  It was proving difficult but not impossible.  He saw what looked like a Jolie shaped figure, followed by a Kiele shaped young woman, and finally a blob he hadn't seen before.  The blob was the nurse.  

``Is there anything I can get you?'' she asked the young man.

``Can you wash my hand,'' he said seriously, but still with a definite croak.  ``My left hand, someone appears to have dribbled on it.''  Though he had been semi-conscious, Zane had felt Kiele's tiny indiscretion.  Her face went redder than a poppy, and Jolie couldn't help but laugh.  

``There's nothing wrong with your senses hey Zane?'' laughed the nurse.  ``He'll wake up properly over the next few hours,'' she said, ``although by the sounds of it, he's already getting cheeky.''  She turned to Kiele, ``You wanna nip that in the bud,'' she said, ``else he'll be walkin' over you for the rest of your life.''  Kiele, still bloodshot red let out a smile.  If she really did want to have a relationship with Zane someday, she was going to have to get used to that.  

It wasn't her fault she kept her feelings behind such a high and solid wall.  Her father had made her that way.  If she had shown weakness, she had been ridiculed.  Once she'd made the mistake of telling Mark she fancied a boy in her class when she was around ten years old.  He had responded by pointing to him when he dropped her off the next day and saying, 'Is that the one you told me you wanted to kiss?'  It had been cruel and she had never lived it down.  So she'd hidden away.  She'd hidden everything away.  Now, finally, she was breaking free of his hold.

Zane turned his head back towards Kiele.  His eyes were beginning to focus a little more and he saw her, now standing, in the Mt. Taleberg dress.  She looked absolutely beautiful, as if she had been called away from a trip to the theatre or a fancy restaurant.  He couldn't quite believe his eyes.  Kiele saw him looking her up and down, blinking several times as he did so.  When his eyes finally met hers she tipped her head to one side and curtsied.  The dress billowed slightly at the hem.

``Do you like it?'' she asked.

``Wow,'' he replied.  

He blinked again to make sure he wasn't dreaming.  Had she really dressed up to come and visit him?  Jolie looked on at the two young hearts.  She remembered what it had been like to feel so in love, but that had been years ago now.  She remembered the happiness she had felt at meeting that someone special for the first time. She smiled.  

``Kiele, you look amazing,'' he blurted.  'It had all been worth it,' thought Jolie.  He was literally gob-smacked.  The dress accentuated her figure and they way she had arranged her hair fit perfectly.  She performed a little twirl to solidify the image.  He closed his eyes tight, trying to take a mental photograph.  If this was the last thing he saw, he wouldn't mind at all.  If he died, right there, he would die a happy man.  

