\chapter{01}
\section{Initiation}


He held the dark weapon tightly in his hand. The leather grip felt warm and enticing, almost as if the weapon were an extension of his own body, as if the barrier between grip and skin were somehow non-existant. He knew however, that beneath the warm grip lay a cold metal, ready and waiting to shock somebody's skin with its temperature. In some ways, he had come to think of the weapon as being an entity in itself. It seemed to have moods, sometimes as black as the night, but other times as warm as a hot summer's day. This he found particularly ironic. This weapon was meant to kill. The thought had been circling around his head all day, slowly building. The anticipation, the years of literal blood, sweat and tears compounded together in his mind and as he stood there holding his masterpiece he could feel his body temperature rising, the adrenaline surging and suddenly, he felt sure he was going to pass out.

It was not as if Oken hadn't killed before. He was an elite member of an underground culture, an ambassador of death. He was one of the best and though renouned for his fearless attitude, even he shuddered at this new weapon cradled in his hand. This dark weapon. A weapon so powerful that it threatened the very existence of every other human being on the planet. To be truthful, Oken wasn't particularly interested in 'every other human being' on the planet; he was only interested in one, namely this evenings opponent. His desire was solely focused on his upcoming performance, to please the crowds who would soon gather to watch him fight. It wasn't even the popularity that fuelled him, in short that did nothing for him at all, but the noise, the atmosphere, the aggression. That was what fuelled him.

Since Oken's birth the world had become increasingly unstable and dangerous. With various governments attempting to exact rule over territories to which they had no claim, acting like wolves from a pack, scrapping at every last piece, it had certainly made the world an 'interesting' place. Interesting, but terrifying. Oken had been a soldier in the armed forces of a since collapsed government. Like a student without a master, he had wandered far and wide in search of a calling, bold and bloodied and forever changed. Searching but never finding.

Oken had discovered his calling in the form of an illegal underground community, in which he had fast become a star, a prodigy, some might say a ruler. However, he had little time for his own status among the people. His only driving force was to be the best. To win through at all costs. Though his rugged persistence would often betray peoples opinions of him, he was a highly intelligent man. An accomplished physicist and chemist, Oken had been recognised as a child, as one of the brightest youths of the century. Scholorships were lined up, his life practically mapped out for him, his parents proud and his future certain. Oken would be a star.

That was until the Temporal War in 2028, a horrific struggle from start to finish. The war had changed the world in ways unimaginable. One or two of the more affluent governments had developed temporal weapons; that is, weapons with the ability to affect time and history. These said weapons were able to obliterate souls from existence, but their enpungement was not limited to that point on, but permeated through the whole of history, leaving no trace that they had ever existed. The worlds timelines had been altered and history had changed forever. Though many scientists had tried, no one could predict the outcome of manipulating time.

The assassination of Emperor Wong-Chee by a terrorist group, who had stolen a temporal weapon in 2027, had discharged him from the world forever. His obliteration erased his triumphant victory over Al-Capor in 2024 from history. This in turn changed the course of events forever, allowing the terrorist country of Chee-Nai to once again claim the right to rule themselves. Of course without any kind of temporal shielding, the general population would have had no knowledge that anything had ever transpired at Al Capor and would never have known about Emporer Wong-Chee and his swift dampening of the agression of his terrorist neighbour.

The world had finally regained some stability when the Emblem had been established, a governing body consisting of six constructs, Alendria, Prestone, Phenley, Cantaris, Ranshaw and Liast. The previous world governments had all but crumbled under increasing pressure from society and had had no choice but to band together like some ragtag group of mercinaries. At the first general assembly of the Emblem Council it was concluded that the collective experience of all previous governments had the best chance of bringing peace and stability to the world and so the Emblem was born.

Each Emblem construct largely governed itself with its own laws and military forces. Though this caused certain difficulties it seemed to offer a unilateral stability. In essence, though one huge empire, each Emblem effectively operated as a separate state or country, a by product of the differing cultures native to planet Earth. One law was constant however, a law above all others: The law detailing the use and development of temporal weapons.

Temporal weapons had, to all intents and purposes, been outlawed from the very beginning, but controlling and policing this had proven to be difficult at best. To combat this, the Emblem established a separate military force to try to detect and police temporal violations. The goal of the G-TEP, or Global Temporal Enforcement Programme, was to monitor and discover the development of any temporal weapons and to crush their creators before they had a chance to use them, or develop them further. Of course with the presence of such force with seemingly carte blanche power, the citizens of the Emblem had protested against the use of such violence. It was however eventually deemed a necessity by the majority to protect the Emblem's way of life.

Oken had developed a temporal weapon. He had built temporal shielding around his apartment to avoid detection and had tried never to leave the building with anything that the G-TEP could ever detect. It could be said that Oken's crowning achievement had been the reduction in size and power consumption of his temporal shielding. Without it, he would most likely be dead already. Today though, would be the day. Today he would unleash his weapon on his opponent, kiss that suckers soul goodbye and perform the greatest show ever seen. A temporal dissolving up close. He bit his lip as he stood there thinking about it and drew in air sharply making a smacking noise. He sure as heck didn't want to miss this.

The physicist had constructed a custom scabbard inside which he had included yet more temporal shielding. It was into this that he now slipped his deadly sword, slowly and carefully, the rear of the blade emitting a sullen screech as it met with the scabbards rim. It suddenly dawned on Oken how crude the word sword was. A sword was something swashbucklers and prirates used, people had sword fights, some even engaged in swordplay! No, she was far more elegant than that, he tried to replace the word in his mind, searching for a more suitable candidate. Weapon perhaps? Or maybe even blade.

He packed his bag hurriedly and left the apartment building. The old door creaked as it slowed under the automatic closing mechanism and finally came to rest with a soft bump. He headed down the steps at the front of the building and turned left. He felt an urge to run. Something inside of him scolded him, perhaps his conscience. He was carrying not only an offensive weapon, but one of the upmost abhorance to any and all. He glanced down at the bag and smiled, a thin, weathered smile. The thinness came from his lips, but the weatheredness was from his past and as he allowed his mind to wander to some of those days spent on the battlefield, the smile waned, his muscles seemingly tiring from the facade. Was this really all he had to offer? asked a voice. Yes.

It was not uncommon for people to carry blades and other offensive weapons through some of the towns of the Emblem. In fact in Alendria, Oken's home construct, it seemed to be more prevalent than anywhere else. He had often wondered how the increase of military force had brought about so much peace. The answer was quick, the answer was clear. Fear. The world was a peaceful place because it was scared. If anyone stepped out of line, there could easily be a dozen trigger happy idiots on them in seconds. The knife-edge tension thrilled him. His attention shifted as he walked along the roads and he glanced at the people he passed. He mused on their respective lifestyles, on their pasts. If he cut one of them down right now, if he obliterated them from history; Would anyone realise they had gone? Would history really change? Did one person here have so much impact on the worlds events?

He noticed a youth terrorising another young man. Instinctively his right hand twitched, ready to go for the sword, but he stopped and realised that this wasn't the time, and that here, in the wide open streets, was definitely not the place. Despite this, his hand still held the invisible grip of the sword, glued and unable to move, perhaps hoping beyond all hope, that the thug would turn his attention away from the young man and towards Oken himself. Then he would show him. Then he could use his 'blade' and rid the world of this repugnant soul. Violence has its place he told himself.

Oken was not violent at heart. However the years and years of fighting, both in the war and subsequently in the Zone, had left him with an all too strong desire to fight to survive. He had never married, and had never fathered children. He was fast approaching his thirties and was beginning to show some definite signs of ageing. His hair had turned grey at the age of 24 and in all honesty he could quite easily be mistaken for an age of 40. The small lines on his face, his darkly tanned skin, the numerous small scars adorning his body all pushed at his age, encouraging it onwards. These days there were, of course, treatments available to change his hair colour back to the jet black that it had once been, but appearances mattered little to man like him.

As he walked along to his showcase event, a pang of sadness hit him and a small part of him longed for somebody to share his achievement with. Today could be his last day on Earth, and in a moment he realised how sad and insignificant his own life was. After a brief recanting of his life tough he continued on, entirely comfortable with the fact that he had no idea whether he would make it out alive. This was his last chance, his only chance to show people what he was made of. His only drive was to show off his achievement, to be the first fighter to sport a temporal weapon. Yet in his heart he knew that if the G-TEP forces came, and it was a distinct probability, it could be the last fight he ever took part in. In fact he could scratch the 'could be', It was damn sure to be.

His heart began pounding again. He watched the cars zooming along the road, sleek and streamlined, though from a design point of view, largely unchanged in the last 60 years. There had been an effort to produce hover cars, first proposed as a means of cutting down on road maintenance, however public trials had always resulted in crashes; occasionally on tragic scales.

One particular crash, or 'accident' as it had been dubbed, had occurred when the reactor of one such hover car exploded, something which the manufacturers had claimed could never happen. The resulting explosion had wiped out half a village in the southern construct of Prestone. At the time, there was talk of sabotage by terrorist groups. Some even said that the government had been involved. Allegedly, ministers were trying to stop the minature reactors from becoming mass producable and ruining a very lucrative subsidy that had been in place for fossil fuels. At the time, the government of Prestone had been creating large revenues by exploiting fuel workers in eastern Cantaris. If the reactors became mass producable a large source of Prestone's income would be lost. The allegations were never proved, but the technology silently vanished, working its was into military hands.

As Oken rounded the corner he came face to face with a close acquaintance of his, one who had many faces. Death. A girl lay motionless on the pavement having just been hit by a car. Crowds of people were gathering round, yapping endlessly into their phones, some even taking pictures. Oken wasn't sure if any of them were calling for help, or whether they were just trying to relay traffic information to their co-workers, who were still working hard in the offices of the surrounding areas. An accident this bad would ensure that the main route out of the suburb would be blocked for at least a couple of hours.

The girl, in her late teens, lay in a pool of blood and the smell of death filled the air. It didn't take a genius to see that she had died on impact. Her fragile bones giving in to the stresses that the car had forcibly imparted upon her. Her legs were a tangled mess of bone and muscle. Blood oozed from the crack in her head and Oken was sure he had heard one passer by exclaim that parts of her brain were visible. In the distance he could hear the wail of the emergency services siren. All too often these days they took so long to reach accident scenes that victims with a good chance of survival died because they didn't receive medical treatment in time.

Oken's attention shifted to the young girl's family and suddenly he realised how important her life would have been to so many people. On her clothes, a school crest was visible and she was wearing a purple blazer, an instant indication that she was of the highest intelligence at her particular institution. For an instant, Oken wished he was able to bring her back. He wished he was able to give her a second chance. Maybe one day he would be able to.

Throughout his thoughts, he hadn't stopped walking. He didn't want to be seen as one of the hoards of hungry panthers, pushing and vying to get a good view of the corpse lying in the road. He walked past the accident, seemingly unaffected at the sight of the event, his avoidance a sign of respect for her life. Though it was unlikely that any of the onlookers would have classed him as insensitive for doing so, for they were far too busy taking pictures, he justified his actions to himself. It was his way of dealing with it, and for him, it was far better than being one of the pack.

The driver of the car, a young woman in her mid twenties, was sitting on the pavement sobbing quietly, rocking to and fro. Her hands rushed through her hair as she tried desperately to wipe the memory from her mind. Several passers by were trying to comfort her, telling her that it wasn't her fault. Others took to screaming abuse, asking why she wasn't watching where she was going, if she'd been drinking or was on a high. Oken wondered if that was truly the case or not. There was no way of him knowing, for he had not seen the accident first hand. Though give him a few more months and maybe he would be able to go back in time with or at least see back in time and find out who was really at fault; the woman, or the girl who now lay there forever more encased in an eternal sleep.

As he rounded the corner he smelled the freshly baked bread that the old fashioned bakers still made and thoughts of the accident quelled. He considered going inside to get himself an iced bun or a kleeptin, a beautiful delicacy from Southern Prestone, but decided quickly against it. He didn't want to draw any more attention to himself than he had to.

His journey took him through the park and as ironic as it may be, he marvelled at creation. He saw the trees standing tall, the grass as green as ever and he could hear the birds chirping in the bushes as he walked by. Even the smaller animals marked their own territory in some way he mused. He found it remarkable that each bird's song was so intricately different and how complex their tones were. He saw a rabbit bounce out into the empty field beyond and scamper around in a wild frenzy without a care in the world. The grass swayed back and forth in the calm breeze of the summer.

It had taken him over three years of his life to develop this blade and over those three years people's opinions of him had changed drastically. He had first discovered the underground meeting place, popularly called 'The Zone', by accident on his way home from his regular job at the library. He had taken a back alley, something that bore him no fear and when asked if he was a fighter or a spectator by a large surly man at the door to what looked like a disused warehouse, he had instinctively replied 'fighter'. He would show the mugger a thing or two. It was his nature. The man was not a mugger however, nor was he looking to beat on Oken. The man was a bouncer and Oken was immediately whisked into a small room with several other people dressed from head to toe in armour of various kinds. This had not been too concerning for Oken, what had worried him more was the fact that some of them were armed to the teeth.

Zone fights normally lasted for about fifteen minutes. They were not classed as bouts to the death, but several extremists believed that this was the only honourable way to conclude a battle. There were no real rules to the fights. As long as you stayed in the ring, which was the platform of a disused railway, and fought as hard as you could, you would ultimately be fine or not as the case often was. Victory was declared when your opponent was either dead, or when they left the platform of their own accord. If you didn't save enough energy to make it out of the ring on your own, that was your hard luck.

\thoughtbreak

Oken's first fight had only lasted thirty seconds. He had been pitted against a skinny, stealthy looking fighter. Oken had never fought ``In The Zone'' before and had no idea what was going on or what was expected of him, but from the banter he had overheard he had a pretty good idea. He stood in the small room waiting to be told where to go next, his heart racing and his mind oddly still. Before he could ask any questions, a man entered and told him that it wasn't going to be an easy fight, but that if he won, he would receive four million credits, no questions asked. Oken, who was at the time, desperate for money, accepted. His job at the library barely paid the bills. If he could add a little extra to that, well that would be no bad thing.

Walking out into the ring, he saw his opponent standing across the platform. Oken was drenched in ambivalence, feeling both intense fear and a hungry excitement coincidently. The fear he suppressed, the excitement grew on him. All around the platform, spectators clawed at the reinforced glass, chanting and shouting till their lungs were hoarse.

Water dripped from the ceiling in a steady rhythm and Oken used this to retain a sense of timing. He had no idea what weapons this guy would posses; he assumed that he would be as well armed as the other fighters he had seen earlier. His heart began pounding. He felt sick, but strangely it was not an unpleasant sensation. The wave of nausea was somehow comforting, it amost felt as though he were home again. His mind flashed to the battlefield once more. Yes. Home.

 Oken tested the ground with his feet, it was solid. He looked up at his opponent. Was he supposed to kill this guy, or merely injure him? As he glanced around the room at the platform's spectators, he noticed several banners with the phrase 'Hand 2 Hand Ronnie' scrawled in large friendly letters. 'Maybe this guy only used his bare hands?' Oken thought.

He was in luck. He'd stumbled, unknowingly, into one of the beginner hand to hand combat bouts. His heart raced further still. What was he doing here? Why had he said fighter? His answer was quick. Pride, and it was pride that wouldn't allow him to walk away from this fight either. He heard some music start up in a dim corner of his mind. It was not a track that he recognised. The purely electronic sound waves battered the pair stood in a face off, the simple but overpowering lead line designed to psyche up competitors. Ronnie began moving his arms and legs in what Oken could only describe as something related to Thai Chi.

Oken dusted off his jacket and removed it. He was really going to do this. He was used to fighting, the war had taught him enough of that, but not hand to hand and certainly not illegally. Even though no one had said as much, Oken had gathered that the goings on of the Zone couldn't possibly be legal. The angry tigers clawing at the glass, the shouting, the weapons, certainly not legal.

Ronnie was still performing his ritualistic dance of movement and mime, and Oken was quite sure he'd even seen Ronnie gesture a twig breaking action with his hands. The war veteran raised his eyebrows and for the first time since arriving in the Zone, all of his fear and anxiety left him. He dropped his jacket on the floor, the air trapped inside scooting dust across the floor as the heavy cloth was dragged by gravity, and prepared to fight.

Suddenly he was unaware of anything else but the water dripping from the ceiling. Time seemed to slow down and he followed one drip from the ceiling to the floor with this eyes. He could almost hear it rushing through the air like a speeding bullet. He could see a blurry Ronnie in the distance standing stock still, totally out of focus. He could see the crowds moving, jumping with anticipation, creating an animated mural of colour all around him. He smiled, this may actually be fun. In an instant, the water droplet hit the floor, the host screamed go, the music hit a climax and the crowd roared. Oddly enough, the last thing Oken noticed was that Ronnie started running very very fast towards him.

The next thirty seconds were a blur to Oken, but he still remembered exactly what happened. He also began to run towards Ronnie, each step making a thundering crash on the floor and send waves of impact shooting up his legs. He was totally unaware of his actions, letting a latent subconscious take control, allowing an inner persona to step forth and control him. There was a pillar slightly to the left of him about three steps away. Inner Oken directed him to the pillar and he made every effort to reach it. In one fluid motion he began to run up the side of the stone face. The change of direction from horizontal to vertical arrested him. He took the first step, and then with the second he thrust himself away from the pillar in the direction Ronnie was travelling. Ronnie had no time to see where Oken was and was hit completely unaware when Oken dropped from the skies onto Ronnie's back. Oken felt the crack. Ronnie sure as heck felt the crack. The crowd heard the crack through the thumping rhythm reeled back at the noise.

Ronnie and Oken fell to the floor in a confused union. Oken managed to quickly turn his fall into a roll and ended up standing next to his fallen opponent, who was now left groaning on the platform's asphalt. Ronnie was not dead, nor was he mortally wounded, but Oken had managed to break a vertebrae or two in Ronnie's back which would definitely put him out of action for at least a few months, a diagnosis that was later confirmed by one of the Zones medical staff.

The culture of the Zone was so brutal that doctors certificates were used as trophies by the victors and copies posted up on boards next to fight descriptions, oft written by hopeful young journalists. The feeling Oken had experienced by winning his first bout had been indescribably good. He was a hero. As soon as the fight was over, hundreds of people swarmed onto the platform to congratulate this new fighter on his victory. To the present day, Oken held the record for the shortest fight ever in the history of the Zone.

Not long after that, things had taken a more interesting turn. Fighters started arriving at the Zone with performance enhancing drugs, many of them experimental, and mechanical advantages to help them win their battles. It was not against the rules, but it turned the sport into a much more specialised field. The old hand to hand bouts quickly became a thing of the past as the fighters invested more and more time and effort into gaining an advantage over their opponents.

The winnings Oken had received had been close to Four million credits, which for him was an awful lot of money, almost as much as Oken earned in a month and he realised that he could augment his meagre income quite significantly by occasionally fighting here. Since that first fight, Oken had spent almost all of his spare time developing new fighting tools and weapons; after all he needed to keep up with the game. Super-Humanity was nothing new, all the new kids had it. But SupHum in itself was not enough to win a fight and certainly not enough to perform well, no, to Oken and to most of the spectators, it was the way in which it was used that showed the calibre of the fighter.

So elusive and secret was the Zone and its members that if anyone was ever caught using any weapon or tool intended for battle, outside of the Zone, their membership would be revoked and in all likelyhood they would be killed by Zone extremists. One kid had learnt this the hard way when he used his Super-Humanity device to rig a college basketball game on a Saturday night. Nine-tenths gravity was a neat advantage over the other players. The poor soul never got to see the subsequent Tuesday.

\thoughtbreak

Oken reached the Zone shortly after 6pm. It was a good twenty minute walk from his apartment and he was greeted by loyal fans and ring organisers.

``So you in the Zone tonight Okie?'' said one enthusiastic fan. Oken didn't answer, he didn't like being called 'Okie' or anything else besides his actual name.

``Saw you last weekend man,'' came one comment, ``you were awesome.'' Oken was used to comments like this and he'd begun to take them with a pinch of salt. He was dimly all to aware of the fickle nature of popularity. Winning gave rise to popularity relatively easily, but if you lost, the ride back up to the top was far harder. It took much more than just time to bring a fighter back.

``So, what you got for us tonight then my friend?'' Oken looked up to see a dark skinned man standing in front of him. It was Ruben, a long time bouncer at the Zone and one of Oken's oldest friends. Ruben gave him a pat on the back and slapped him five.

Oken responded to the gesture, ``We'll have to wait and see Ruben. We'll just have to wait and see.'' Ruben had known Oken for a long time, and a comment like this could only mean one thing; he had something special planned for tonight. The big bouncer nodded his mind putting the puzzle pieces together. The nodding became more emphatic and resulted in him quickly running off to ask another bouncer to cover his shift. Oken was swamped by hordes of fans asking all kinds of questions and shoving electronic devices under his nose for him to sign. The fighter pushed his way through, wholly uninterested in their attention. 'It was the buzz that drove him, when would they realise that?'

Through the years, Oken had worked his way through the ranks to become one of the favourite fighters in the Zone and in doing so had unsuprisingly made several enemies. This had often been down to him forcing them to withdraw from fights, given that he rarely killed his opponents. Although these enemies had lost their almost tribal followers, they still posed a significant threat to him because their driving force had changed. What was once driving force to achieve excellence was replaced by revenge.

Oken walked slowly through the crowds of bustling people. He could feel their anticipation, their excitement. It seeped off them in waves, and Oken absorbed it all, feeling more powerful with each and every step. He'd grown to love his walk from the front door to the fighter's lounge, or the 'Chiller' as it was known.

The Chiller was a place for participants to rest before their matches. Inside, they talked about various things including new tools and weapons that they were developing. Oken was one of the most well respected oracles in this ironic little gathering. His knowledge was quite literally overwhelming. If anyone had a problem with their technology, Oken knew how to fix it almost instantly. He gave this information away freely, never concerned for one moment that it may one day lead to his defeat. He enjoyed helping people, he enjoyed upping the ante. Secretly, or perhaps not so, he just loved the challenge.

One of the barmaids walked in with a tray full of drinks. She set it down on the table in the centre of the room. The ornate mahogany legs sat at odds with the rest of the Zone. The glass top, polished and clean sat atop a delicately detailed frame. An antique table was definitely not the sort of thing one would expect to find in an underground fighting arena but then there were a hundred and one things that were ironic about this place.

``So Oken, I got a problem with one of my SupHum devices man,'' said a fairly new fighter known only as Skins. He was tall and rather skinny and appeared to be covered from head to toe in technology and tattoos.

``What's up?'' replied another fighter. Oken who had been looking at the floor turned his head to look at Skins and nodded for him to continue and share the problem with the group. 'It all seemed so civilized' thought Oken as he sat there. These people were about to go and beat the living daylights out of each other over the course of the next few hours and here they were discussing the finer points of physics and chemistry.

``Well,'' continued Skins, ``I'm finding it hard to keep the reactor from topping out at 359 Kelvin. I just can't cool it fast enough.'' He took a swig from his hipster bottle and carried on. ``I'm scared it's gonna blow and take my back out with it.'' He checkled and then realised his mistake. Being vulnerable and showing it were two different things. He looked down at the floor rather sheepishly his cheeks flushing. Several of the other fighters chuckled.

``Mmmm, fried flesh,'' said Oken. ``Sounds like you need to vent the exhaust quicker. Try using a turbo charger on the exhaust system, but inject some Obium Gas too, that should help reduce the heat and at the same time give you an out for the zeta build up.'' He swirled the port in his glass and took a sip, raising his eyebrowsas he did so, awaiting some kind of acknowledgement from Skins. After a short pause the tattooed man nodded. He said nothing, knowing full well that it was a fairly simple solution to a common problem. His shame grew.

The door knob turned and noise filled the room. All but one of the fighters looked up to see who was about to enter the inner most circle of the Zone. It was Jessie, an arrogant, overenthusiastic, and often hyperactive youngster who was despised by most of the fighters for his boyish good looks and charm.

``Aww man,'' he exclaimed. ``Did you see that accident down on Caster Street. Dumb blonde never saw it coming.'' His voice rasped as he spat out his story.

Oken was on his feet. He lunged towards Jessie and took him by the throat. His arm extended outwards from his body, thrusting young Jessie's fragile body into the wall, knocking over a smaller table complete with drinks and glasses. The glasses smashed to the floor and shards lay strewn everywhere. Jessie was finding it hard to breathe. It was obvious that he'd been winded by the blow, which had taken him completely by surprise. All of the other fighters watched on in earnest. They had no quarrel with Oken. In fact, most of them thought that Jessie had had it coming to him for a long time.

``You've made quite a mess there Jessie,'' said Oken in a calm unwavering tone. ``Now clean it up, and watch your mouth. Have a little respect for the dead.'' He emphasised the last 'd' in the word dead. Jessie nodded in between struggles for his breath, his nose twitching in anger. Oken cocked his head to one side and raised a single eyebrow, waiting for an answer from the wimp before him.

``Y-y-y-es,'' Jessie coughed. Oken dropped him to the floor and the boy sat for a while in a crumpled heap regaining his breath, but all the while losing his dignity. The other fighters continued attending to their drinks unaffected by the events that had just occurred. A barmaid came hurriedly through the door and as she flung it open it connected with Jessie's head. The noise was enough to make all of the fighters wince and then the room filled with laughter. Jessie got up quickly, if a little shakily, leaning on the door handle to help regain some of his balance. The barmaid made a quick apology and Jessie was gone, slamming the door behind him.

No one had noticed the big black holdall that Oken had brought with him into the Zone. It now rested beside him on the floor, its contents remaining unknown to all except Oken. He knew what was in it. He wanted to gingerly open the zip and let the monster out, but it wasn't time just yet. Soon though, they would all see what was inside the bag. Soon all his hard work would pay off. Oh how he waited for that moment. He finished his drink and sat back in the chair. 'Not long now,' he told himself.
