\chapter{21}
\section{}
Alone  

Leon was in pain, but could still move.  His wounds just superficial, he was able to sit himself upright.  He began to sob.  The pain around his neck was dreadful.  Catching a glimpse of himself in the mirror in the bedroom, he could see the bright reddy purple mark tracing its way around his throat.  Just a few seconds longer, he thought, just a few seconds longer and I would have been rid of this world.  

The voices in his head were laughing now, Ric amongst them.  Laughing at the fact that he hadn't been able to complete his final mission either.  He could hear Ric joking that that made him zero percent successful.  The pain was excruciating.  Not physical pain, but psychological agony of seemingly failing at everything he did.  In the distance the phone started ringing.  It had been set to auto answer, and there came worrying sound of Shana.

``Leon honey, please pick up,'' she said.  ``Tim phoned me saying he was hearing a lot of noise coming from the house.''  She paused  ``Are you OK?''  Another pause, ``Listen, I'm on my way home.  I'll be there soon.''  Leon hadn't heard her.  He hadn't wanted to.  If he tried hard enough he could still complete his mission.  He remembered the gun in his jacket.  He hadn't wanted to use that.  It reminded him of what he had done to those people.  He had no other choice though.  He saw his jacket hanging on the post of the bannister.  He could even see the gun protruding from the inside pocket.

As he reached inside to get the gun, the tears began again.  He felt the soft fabric of the jacket against his hands and found the pocket.  The tears were coming faster now, his sobbing rhythmically bouncing his head and torso.  This really was the end.  He wished things had turned out differently.  He remembered that time in the picking fields once more.  How happy Shana had been that day and how quickly he had been able to ruin that.  

Leon felt so guilty, for that and for killing those relatively innocent people.  He'd had no personal vendetta against them.  Had they hurt him?  No.  Sure they enjoyed hurting each other, but that was their business.  Resolute and strong Leon pulled himself to his feet.  He was still a little shaky from the fall.  He winced in pain and closed his eyes tight, putting the barrel of the gun to his head like it was an extension of his own body.  

The gun, a Triflex 83, was jet black and cold.  Oh so cold against his skin.  Leon was running a high fever and the gun offered such amazing relief from the pain running around inside him.  The voices reassured him that the gun could make it all better.  He would be free, happy, no longer tied down to this life.  

He dragged the barrel of the gun across his forehead as he stood to attention.  Eyes red and head in pain he stood there at the top of the stairs.  He pushed the barrel into the side of his head as if menacing himself.  'I have the power to do this' he told himself.  'There's nothing you can do to stop me.'

The phone rang again and auto-answered as it had been requested.  It was Shana and this time her voice managed to cut through to him.  ``Are you there Leon?'' she asked hurriedly, ``please answer me, for heavens sake I love you.''  

``I'm here,'' he said, keeping the gun to his head.  Unwavering in his resolution to end himself.  ``I'm going to make things all better.''

This worried Shana, she couldn't see him, she had no idea what he meant.  Better?  That could mean anything; I'm baking a cookie, I'm eating shallots, I'm about to kill myself.  ``Leon hunny, are you OK?''

Of course he was OK, what was she babbling on about.  He was more OK than ever.  In a few minutes he'd be the most OK he had ever been.  

``I'm fine,'' he managed to say.  ``You don't have to worry any more,'' he said, starting to cry once again, ``I'm going to make things OK for us.''  His voice was wavering and Shana feared the worst.  Little did she know that her worst fears were already coming true.  

Shana tried to reason with him for a few minutes, telling him that she loved him, begging him to step outside and go and see Tim.  Hearing that name had only enraged him further and he had stood there hissing and spitting about how much he hated that man.  The gun was pressed further and further into his skull, making a mark that felt kind of good.

As they continued to discuss it, a sharp rap came at the door, Leon's muscles tensed, and in a moment of complete lack of concentration, the trigger was pulled.  The bullet left the barrel and entered the landscape that was Leon's skull, the bone pressured into splitting apart, allowing the bullet to travel further.  It ripped through his brain tissue and exited on the left side of his head, exploding forth with blood and calcium in a fury of madness.  The Triflex 83 was a powerful weapon, the preceding event could have been replayed in slow motion at a sales conference as a testament to its sheer effectiveness as a weapon.

The bullet seemed to speed up on leaving Leon's skull and embedded itself in a nearby wall.  Leon never felt a thing.  His body lost its delicate balance and fell forward down the stairs, assisting Leon on his lonely descent into his own personal hell.  His body bounced and flopped against each stair and when he reached the bottom he just lay there motionless in a crumpled heap, blood shrieking from his head.  The exit would was small, but complete, and blood began to flow quite steadily from the family man gone wrong.

Shana had heard the shot and had started screaming at Leon.  ``Leon, for heavens sake,'' she screamed, ``please answer me.  I'm so worried about you.''  Nothing.  She screamed his name again in frustration, hoping that it was a joke, that he was playing some kind of sick trick on her.  It was infinitely better than the alternative.  The phone hung up as Shana realised that joke or not, he wasn't going to answer.

Tim had heard the shot and started knocking on the walls and the door in alternation.  He had no keys and so couldn't get in, but he was fully aware of what Shana could expect when she arrived home.  How could he tell her.  Only 10 minutes earlier he'd been banging on the wall with Leon in a game of who can annoy their neighbour the most.  Usually a calm and considerate person, Tim had taken to playing Leon at his own game, but the game was far beyond that now.  Leon was dead.  His final mission complete, no one would know that again, it had been an accident.  

He hadn't meant to pull the trigger, not so soon anyway.  He wanted to take the opportunity to pray for Shana and Ruben.  He wasn't sure where he was going after he died, so he had wanted to ensure he got the time to say the things he needed to say whilst he was still in the land of the living.  It was one of the first things that had entered his mind when he had dropped from the ceiling, that he had been given an opportunity to pray.

As the blood trickled down his skull and started to ooze on the carpet, the room started to fill with the stench of death.  It crept into every nook and cranny of the room and then started to seep through into every room in the house.  The ladder, noose and wooden beam lay motionless at the top of the stairs, a permanent reminder to whoever found Leon, that this had been entirely premeditated.  He had wanted to die.  He had wanted to be free.

Tim started hammering on the door again.  There was no way he would be able to gain access to the house until authorities arrived with the override code.  Home security had become a lot more sophisticated in recent years and doors were now reinforced to the point that only the owner of the building or the authorities with the override code would be permitted access.



\thoughtbreak



Shana arrived home to a frantic Tim.  The authorities hadn't arrived yet and he still had no idea what had transpired in the building.  Shana had phoned again in desperation during her journey home but her calls had met with no response.  Anyone inside the building would have known the reason why.  Tim tried to explain the events as they had happened, but his mind was all confused and all he wanted now, was to get inside the building to help Leon.  



\thoughtbreak



Though Leon hadn't been particularly fond of Tim, Tim had in fact quite enjoyed Leon's company.  He would have described his neighbour as a little strange, very calm, but always with something interesting to say.  Once, over a beer they had discussed the worlds economy and the falling of the global market.  Tim had never heard anyone talk about it with as good an insight as Leon, and Tim was an investment banker.  He should have been able to counter Leon's every argument for the reason why the government could have prevented the tragedy.  He hadn't though.  He had just listened to the man speak.  

They had talked way into the night, Leon offering his opinions and Tim occasionally offering his counter argument.  In the end Shana had returned from the bedroom and called Leon up to sleep.  He'd been reluctant to leave, but had obliged.  He didn't want to make Shana angry, he'd never made her angry.  He loved her with all of his heart and only wanted to make her happy.



\thoughtbreak



Shana pressed her thumb to the plate and swiped her DrKey.  The system acknowledged her access and opened the door.  She walked in first, her body shaking in absolute terror.  Tim followed her and was joined by a policeman in his early forties.  The authoritative figure had turned up just as Shana had been authorised to enter the building.  The police officer had called out to her to step back out of the house, but she hadn't heard him, or had ignored him.  The officer continued, apparently it was a crime scene and they wanted to get inside first to collect any evidence.  

``I'm going in first,'' she said.  ``It's not my fault you took your own sweet ass time getting here.''  The officer had grabbed hold of her arm as he had pushed past Tim.  Now she shrugged him off and stepped forwards.  For a woman who was expecting to find her husband dead she showed a surprising amount of self restraint.  

She didn't have to go far before the sight of blood met her eyes and instantly she knew Leon was dead.  Her head lifted by a few degrees and the body of her beloved husband was now clearly visible.  The grief overcame her in waves.  First, causing her to clasp her hand to her mouth, less she explode with fury at some – thing.  Next her legs gave way, less she tried to run away from the sight before her.  Finally her head tipped back and she howled like nothing Tim or the officer had ever heard before. 

Tim bent down next to Shana and held her close.  She turned her head to sob into his neck and Tim immediately felt the soft, wet, sensation of her tears.  He hadn't even looked up at the fallen figure of his friend.  He afforded himself a quick glance but it was too much.  He turned his head away in disgust at Leon's body lying there, so disfigured and lifeless.

The blood had begun to congeal now, leaving dark patches on the carpet of the stairs.  It had obviously rushed out pretty fast to begin with, as the officer could see a trail of the red substance as it wound its way down the cream shag-pile that adorned the stairway.  

He turned to Shana who was still sobbing uncontrollably, ``Ma'am, we need to get you out of here.''  She sat there still, unable to move.  Wanting to with her whole being, but totally frozen to the spot.  ``Come on ma'am,'' he said again in the calmest of voices.  Tim stood up and two men put their arms under hers and lifted her free from the the ground she had been glued to.  The three of them exited the room, leaving Leon alone.  Dead and alone.



