\chapter{20}
\section{}
Family Home  

Leon hadn't been feeling good all day.  Now he'd arrived home he felt even worse.  The clock read 19:05, but he couldn't see it properly.  Leon was blind drunk.  It had started as a pick-me-up idea but had very quickly turned into a whole different saga.  He was nursing a black eye which he had received from some random guy in the bar, after he'd called him an impatient pig.  It wasn't like Leon and it was a damn good thing that Shana was out at her parents.  

Leon sat in the chair.  It was his chair.  The only chair he liked to sit in.  He'd become much more reclusive lately and he and Shana had started to fight on a regular basis.  It wasn't that he wanted to argue with her, it was just that she was always so right.  All the time, like a sickness.  Not in a funny sitcom way, but in everything they did.  Leon always seemed to be the one to make the mistakes and it was really starting to tick him off.

As he sat there musing, he reached across and grabbed another beer from the table.  He'd brought a six pack of light beers home with him to chill out to.  'It wasn't fair' his head thumped, 'it wasn't as if he never did anything to help around the house.'  He threw his shoes off in a fit of rage.  One spun off a little too far to the left and knocked over a glass vase that had been perched quite safely on the table only seconds earlier.  The vase hit the floor and its contents, some flowers and their water, joined their receptacle in a clumsy disarray.  At first, it appeared he had gotten away with it; the vase hadn't shatter like he had expected.  Then a tall candlestick, which Leon hadn't noticed teetering on the edge, fell off too, piercing the vase and exploding it into a thousand pieces.  

In anger at the mess he had created, Leon picked up another can of beer and hurled it at the glass topped coffee table which had been supporting them for many years.  The can hit the surface of the table and in an instant the safety of the surface was no more.  Small trinkets and his half eaten dinner made their way to the floor to join the flowers, vase and water.  That should do it, thought Leon, have to give the little lady something to bitch about.

A part of Leon's mind started itching, scratching away at him.  Why are you doing this? It screamed.  This isn't you.  Where is the real Leon?  The small voices were drowned out by the much larger voice which seemed to be taking pleasure in the destruction of his living room, 'His' living room.  He paid for it after all.  If he wanted to destroy things, then he was perfectly within his right.  

The day hadn't gone well.  It had started off with him thinking about them again.  Though he swore a million times he wouldn't, he had.  He hadn't been able to help himself.  It was like a bad dream that he would never be able to wake up from.  Though two months had passed since that fateful event, he was still no closer to being healed for what he had done.  He had shot and killed three people.  In cold blood.  The small voices were back, claiming it was an accident, that he hadn't been of sound mind or body.  The bigger voices shouted back, he had been prepared to go to whatever lengths were necessary to complete his first mission.  

Leon wished he'd never joined the stupid G-TEP.  It wasn't as if anything good had come out of it.  If just one person had told him not to go ahead with it on the morning of that first mission, he'd never have completed his training, or stayed with G-TEP.  On his arrival back from their trip to the Zone, Ric had taken great pleasure in telling his superiors and the entire base that it was he who had taken the shots.  

Ric had told them all of his glee at watching the bullets enter their targets bodies, and then explode out the other side.  His friends had lapped it up.  They'd been as hell bent on benevolent violence as he was.  Leon had cowered in the corner as Ric had also recounted the tale of how he had punched the new recruit in the face for his back chat.  That had given them all a great laugh.  Leon had left the room at that point, totally uninterested in anything anyone had to say.  

The young recruit was given a desk job, but hated it.  The constant berating, the ever cocky Ric it was all just too much.  Several times he'd tried to transfer to another section, even leave the G-TEP altogether, but they had rejected every single proposal.  It was either their way, or an exceedingly miserable life.  

The television was displaying a football game from the 2000s, a sport Leon had always enjoyed playing as a young lad.  Today though, he was watching, and he was angry.  Definitely not a good combination.  ``Come on you stupid cripples,'' he jeered.  The next door neighbour banged on the wall as the sounds of smashing coffee tables and jeering had finally gotten too much.  Leon arose in another of his rage fits and started hammering on the wall.  If the neighbours could encase the room in yet more noise, then why the hell couldn't he?

The man on the other side of the wall stopped and so did Leon, confident that he had asserted his authority over Tim and Joan next door.  He never had liked them that much anyway.  Shana had been so overjoyed when they had discovered the pair living next door.  Leon had found them both boring as hell.  Tim with his love of ancient civilisations was about as interesting as a brick wall and Joan?  Well you could have stuck her face on a BBQ and she still wouldn't have been an interesting topic of conversation.

The voices tried to make an impact again.  'This is how Ric behaves,' they said.  'This isn't you.  Please listen to us.'  Leon responded by taking another swig from his beer can.  He'd practically finished it and  turned around from the chair he'd mounted to respond to Tim and Joan's intrusive rudeness.  He noticed the beer can lying in the middle of the now defunct coffee table.  How convenient, he thought.

He opened the can quickly, the pressure squirting some of the contents over the lounge.  A fine mist of beer hung in the air for a brief period before dissipating throughout the room, coating everything it touched with a slightly sticky film.  Let her moan about that, was his reasoning.

One of the idiots in the office had really wound him up today.  Everyday for the last month the cretin had told him how meaningless Leon's job seemed to him.  He remembered his words, ``How can you live with yourself, knowing you're doing nothing at all to help anyone?''  It had hurt, but with every passing day, it had begun to shape him.  He started wanting to be stronger, to be more like Ric.  Until today.  The weasel had come in asking him if he it bothered him that Ric had taken the shot on Oken and not him.  

Apart of him had wanted to tear the freak's head off there and then, but Leon had opted for the more subtle approach.  He would wait until there was the least amount of suspicion, and then pounce on the unsuspecting rat and rip him a new air hole.  The anger had been growing inside him for weeks and weeks, and now it had made a home in Leon.  It was here to stay and unfortunately today, he had brought it home.

It was the anger and outbursts that had forced Shana to leave for a while.  She was visiting her parents and had suggested that Leon take some time for himself, to clear his head.  Of course Leon had taken it as a sign that she wanted to get rid of him, and had turned it into a scene.  After refuting the fact multiple times, Shana ended the argument by carrying her already fully packed bags out to the car herself and slamming the front door.  That had been two days ago.  How quickly he had descended into chaos without her there.

Leon's head was really pounding now and he started to look around for a form of relief.  Sleeping wasn't going to cure it, so he went to the drawers in the kitchen to look for some pills.  Whilst in there he saw the crockery that his in-laws had bought for their wedding anniversary.  He hadn't been keen on it from day one.  'Why are you being so light-hearted about this?' asked the big voice.  'You hate those plates.  You've always hated those plates.'  

In point of fact, the plates were actually rather pleasant.  A solid colour with an oriental looking pattern around the edges, gave them a look of both class and expense.  Leon had a vendetta against them now though and so they had to go.  He plunged his hand into the rack on which the crockery lived.  It took him several attempts to grab hold of something firm, before he ripped it away from its current position and sent the crockery flying towards him.  

Using his arm as a shield, the plates and bowls bounced off Leon and impacted various locations around the kitchen.  All but one of the items smashed, sending broken pieces of porcelain skittering across the floor.  Unfortunately Leon spied the surviving plate.  It offended him with its presence.  He lifted it high into the air, as if winning some award, and then in a sharp explosive moment hurled it towards the sink.  It smashed against the taps, covering the entire area with dangerous shards.

No one could tell him what to do now.  He was his own boss.  He staggered around aimlessly.  Again the little voices piped up, 'remember what Ruben said'.  'Pfft.  Who cares,' came the reply.  He found the drawer he was looking for and took out a box of Dixumin.  He couldn't even remember the recommended dosage and there was no way he was going to be able to read the instructions.  He took two, and washed them down with a swig of beer.  

He went back into the lounge and flicked the volume up on the television.  The football match was still going strong and Leon decided to get cosy for the night.  He'd watch the game and then he'd go to bed.  Not when Shana said, when he said.  That's what a man did, that's what Ric would have done.  

It suddenly dawned on him that he had been acting in the most stupid of ways.  He hadn't realised it before, but he had accomplished what the age old phrase had stated; He had become the thing he had hated the most.  His mind turned from rampant anger, to total and utter despair.  What had he done?

He looked around at the 'family home', now decorated with his hatred of Ric.  He needed to clean it all up before Shana came home or she would kill him, quite literally.  Now that wasn't a bad idea.  The big voices in his head became his greatest enemy.  Why did he need to stay around here?  What did he actually do on this earth that was of any use to anyone?  As far as he could tell, absolutely nothing.  He had killed innocent people, wrecked his house.  He was a shell, a completely empty shell.

He had no idea what he was even fighting for any more.  The  cause of justice and peace had gone.  Why?  Then it hit him.  He had become the thing he despised all his life.  All this time he had been fighting and he hadn't ever realised it had been against himself.  That's why he woke up each morning struggling to find something to live for.  Sure there was Shana, but even she'd all but given up on him now.  Truth be told, she was just giving him some space, some time to do exactly what he was doing.  Time to reflect on his life.

Damn that G-TEP.  He wished again he'd never joined.  It was his biggest mistake, but then again it was exactly that.  It was 'his' biggest mistake.  As the television roared on louder and louder he discovered his epiphany.  All the mistakes he'd ever made, were his fault.  He'd made made them, on his own.  In truth any reasonable person would have agreed with him, of course his mistakes had been his, no one else could have made them for him.  It was obvious his mind wasn't all there.  Yet he had decided that all the wrong decisions could have been avoided somehow, if only he had been a better person.

'There's only one way to escape' a single voice in his head told him, 'remove yourself from the equation.  If you're not here, you can't make wrong choices any more.  You can't ruin people's lives.'

Was that really what he'd done?  He thought about it.  Of course.  He'd ruined the families of Oken, of Jay of the other victims.  He'd ruined his own wife's life.  How many more would be subjected to the onslaught of Leon the wrong decision maker.  

The pills were having no effect.  Leon needed a way to make the pain stop for good.  He'd never wanted to hurt all those people.  He'd never wanted to inflict so much pain.  They wouldn't forgive him.  Some of them never could.  They were dead.  Ruben had told him that they would forgive him from heaven when they got there.  'Pffft, what did he know?'

He remembered seeing some suicides in his training missions.  Most had hung themselves.  It seemed like the easiest way to go, or to avoid being caught.  He hated taking pills and couldn't imagine having to swallow large amounts of them.  No, the best way would be to hang himself.  Shooting himself would arouse too much suspicion, Leon wanted to slip away silently.

Leon's mind was set and so he went about the house to gather the items he would need for his endeavour.  Rope.  He made his way to the bedroom.  He remembered a coil of the stuff he used when decorating one part of the house.  It had been a clever idea.  He had taken the rope and made a border up the stairs with it.  It gave a maritime feel as one ascended to the first floor.

The rope wasn't in its usual place,  Shana had blatantly tidied it away in one of her cleaning missions.  Damn it.  Undeterred, Leon thought again.  A belt.  Of course a belt would hold his weight, but then it would be difficult to secure to the ceiling.  Come to think of it, how was he going to attach anything to the ceiling.  Slowly, Leon's plan was falling apart.  He was failing once again.  The voices loved it.  'Can't even work this out, can you?' they jeered.

With renewed vigour, the extension lead that Leon used when doing DIY sprang into view.  It was sitting under the bed, glowing bright orange and was just perfect for the job.  He whipped it out and instinctively checked its strength.  As he left the bedroom he noticed that the loft hatch was open.  Shana must have been tidying yet more things up there.  His rope was probably hidden away in the depths of the attic.  Never mind, the thought, as he went to close the hatch.  Then all at once it hit him, the hatch could be used to stage his performance.

The man on a mission went looking for a beam or a bar which he could place up into the attic across the hole, from this he could tie his noose and get down to business.  He had a mission once more.  Leon, in his state of utter disarray was so focussed on the task in hand, he hadn't noticed the television had switched itself off,  sensing no one was in the room, it had switched off to save power.

Moving downstairs, Leon went past his maritime theme and made his way to the garage.  There just had to be some wood in there.  The doorway to the garage was thick with different coloured paints adorning it's surface.  Leon always used this door for testing colours before putting them on the walls.  When they had moved in, Shana had wanted to redecorate the entire house, and Leon had obliged.  He loved her so much.  This was why he was doing this.  If he was dead, he could never hurt her again.  The voices neglected to mention that by his actions he would be hurting her more than he could have ever imagined.

The door handle clicked downwards, and swung open.  Leon, now inside, found what he was looking for.  It was a little smaller than he'd hoped, but it would do the job it was told.  He also grabbed the small steps, requiring something to raise himself up with.  The ceiling in this particular house was abnormally high, especially on the first floor.  It made the whole house seem that much more spacious, but also made it so much difficult to heat in the winter.

Leon almost ran back to the landing area, leaving the garage door unlocked.  It was lucky that Tim hadn't caught him, he was in no mood for conversation now.  He set up the steps and began to tie knots in the extension cord.  The plugs and sockets danced as Leon faffed around with the cables, trying to get things just so.  His mind was still blurry, so was his vision, but he had managed to sober himself up a little, thinking about the mission to hand.  

Leon wasn't aware of the proper knots one should tie when making a noose.  He remembered seeing the old western movies, where the nooses always looked so finely crafted.  Leon's looked like a six year old had tried to coil the cable, gotten it in a mess and thrown a monumental tantrum shortly after.  He had tied successive knots in the cable, to ensure maximum strength.  To save time, he had also tied the knots in the cable with it already round his neck.

He pulled it upwards. Now that was a fine noose, he heard himself thinking.  As he climbed up onto the ladder, he slipped the wooden bar through the knot farm he had tied in the other end of the cable.  He was really going to to do this.  The little voice shouted as loud as it could.  'Please stop.'  Leon had noticed that his voices had become a lot more audible.  No longer just thoughts in his head, but sounding more like real voices.  People he knew.  The little voice was Shana and she was begging him to stop.  

``It's best for all of us,'' he said out loud.  Ric agreed with him.  Reaching up he tried to put the bar up into the attic hatch, but found he was too short.  Luckily for Leon there were another two steps left.  He climbed further and managed to lift the bar through the hatch.  He twisted it ninety degrees and rested it on the two longer sides of the hatch.  There was little slack on the cable and the time had come to make the final decision.

If anyone had come in now and told him to stop he would.  He had started shaking and the effects of the pills had started to kick in.  Dixumin was a great painkiller, but it also made the patient rather drowsy.  As he stood there fully upright he closed his eyes and imagined standing in line at the police academy, waiting to be greeted by the Global G-TEP commander.  His commander and chief had visited the police base once and Leon had felt very privileged to shake his hand.  

Eyes still closed, the tears began to stream down his face.  Shana started crying too, screaming at him to stop.  Yet everyone else seemed to be telling him to go.  Finally she could be heard no longer.  Unsure if it was a good thing or not, Leon's feelings burst forth once again and he broke down in tears.  

With one final effort he bent his legs as much as they would allow and prepared to launch himself backwards.  His legs would then drop downwards and he would swing forwards, knocking the steps over and completing the mission.  His mission.  His final mission.  He pushed back and swung away from the steps as planed.  As his momentum shifted from backwards to forwards he kicked out with his legs, sending the steps flying forward, collapsing as they went.  

The strain on his neck was unbearable and he found himself unable to breathe.  As he hung there, he felt the most at peace he had ever felt in his life.  It was all over, everything was complete.  As he began to lose conciousness, aided by the drugs now coursing his veins, he could almost sense the pull of death as he tried to breathe.  

But as the weight of the man on the cable persisted, the wooden beam found itself unable to take the strain.  It had been dampened in the garage, and now decided that it was time to give up the fight.  Leon never heard the splitting of the fibres, but he did feel the sudden slack in the cable, followed by a short period of free fall, culminating in a harsh landing on a set of small aluminium step ladders.  





