\chapter{22}
\section{The Plan}


She'd been sat there for a while now, next to the young man who had saved her life.  She'd been watching him sleep and silently stroking his hand with hers.  The room in which Zane slept was comfortable, but definitely without luxury.  Similar to the room in his dream, it was filled with the same whitewashed furniture.  Zane had remembered it from when he had visited the hospital where his mother had died.  His father had died on impact, completely crushed by the force of the other car hitting theirs.  His mother had survived the accident and had been rushed to here, Majilna Hospital, supposedly the best there was, at least for those without insurance that is.  

  Kiele wondered what he was thinking.  Where was his mind?  In truth Zane was doing exactly what his body looked like, resting.  He wasn't plagued by nightmares or dreams, his mind and body just slept, safe in the knowledge that he had managed to save the damsel; that Kiele was safe.  

The monitor beeped, though it was largely unneeded now.  Zane was no longer in a critical condition, he just needed vast amounts of attention, and an even larger amount of rest.  The drip hanging above his head was doing its job nicely thought Kiele.  She didn't think she'd ever seen anyone so at peace.  She'd watched her father sleeping many times in the past, when he had come home late from work and had started yelling at her.  She'd always found it impossible to get to sleep after that, her adrenalin pumping and her heart racing, she'd usually waited until he'd fallen asleep before watching him.  Just for a while.  It was the only time he seemed really human any more.

The door to the small room opened and the doctor walked in.  ``Any change Kiele?'' he asked.  She shook her head.  The hospital had been dealing with another large emergency at the time Zane had been brought in, and they appeared to be severely understaffed.  The doctors had seen how much Kiele had cared for this young lad, and had left her in charge of monitoring him.  It was risky, but there were plenty more patients needing much more urgent medical attention.  

``He'll come around soon I'm sure,'' said the doctor.  He appeared to be in his late fifties, that was Kiele's guess anyway.  He had a sweet face, with a tuft of grey hair billowing from his head.  He looked like the kind of man one would normally associate with being a granddad.  The corners of his eyes were home to several crows feet but it still didn't entirely rob him of his youthfulness.  He wore a large long white coat that appeared to be at least two sizes too big for him.  

``Is there anything I can get for you?'' he asked, ``Any one you'd like me to call?''  Once again she shook her head.  A girl of few words thought the doctor.

``My father should be here soon,'' she said.  He smiled.  It was always better when a patient could go home with family he thought.  

``I'm pleased your scan was all right,'' the doctor said with total sincerity.  It was a pleasure to find a well mannered teenager in today's society.  So many of them had been turned evil by the media, inciting desire, hatred and fear in to so many young hearts.  If he hadn't become a hospital resident, he would have gone into psychiatry, in an attempt to heal the hearts broken by the world of tomorrow.

Kiele said nothing more and the doctor knew he had out-stayed his welcome.  She liked him, but at the moment she just wanted to be alone with Zane.  It wasn't meant to be though, as a pretty young woman knocked on the door and entered the room.  It was Jolie and Kiele was overjoyed to see someone she knew.  She jumped up from the chair she had been perched on the corner of and ran to Jolie, throwing her arms around her as she went.  Jolie was taken a little by surprise.  It hadn't been quite the reception she had expected.

The two of them stood there for a while as the doctor made his escape.  No doubt he would see them again soon, but he wanted to leave the two alone for a while.  They parted and Jolie could see Kiele had tears in her eyes.  

``It was horrible,'' she began, flustered and almost excited at the same time.  ``He threw himself in front of the train and saved me, and I saw him get hit by all this rubble, and I didn't know what was going to happen, and the ambulance took an age to get here.''  Kiele trailed off, she had been limited by the oxygen in her lungs and she found her self breathing heavily to regain her composure.  

``I'm so sorry,'' said Jolie, ``Kiele I'm so sorry.''  The teacher stroked the side of the young girl's face.  She had felt so guilty after hearing the news about her students, that she had almost been sick in the taxi.  Upon arriving at the hospital she had spoken to reception who had informed her that both Zane and Kiele were alive, and that Zane was just having some minor surgery to remove some debris.  She had slumped to the floor when she had heard the news and the nurse on duty had run around from her little enclosure to ensure that the poor young woman hadn't banged her head as she had fainted.  

As it transpired Jolie hadn't fainted at all, but the news of Zane and Kiele had been too much to take in all at once.  They weren't her children, but she'd always paid more attention to these two.  They were the only pair in the class who didn't have stable parental figures in their lives.  She had met Kiele's father once and had not been impressed with what she had seen and felt.  He had seemed nice, but something underneath worried her.  He appeared to care more about her grades than her happiness, which was usual in some parents, but it had seemed creepy, almost as if there had been an alternative motive.  

Standing there together one could have sworn they were indeed mother and daughter.  They held the same chiselled features and bright eyes.  Kiele brought up a chair for Jolie to sit on and the two of them rested their legs by Zane's side, both facing his bed.  Jolie had seen a doctor who had told her Zane's condition, but she wanted to hear from Kiele how he really was.

``How has he been?'' she asked the young girl.  

``He hasn't woken up from the operation yet,'' she said, ``but the doctors think he'll make a full recovery.''  It was the best news both of them had heard all day.  Kiele looked at Zane and placed her hand on his again.  

``Jolie?'' she said.  Jolie acknowledged her with a hmm.  ``He almost died in the ambulance,'' she said.  ``I was so scared that I'd lost him,'' she corrected her self, ``that we'd lost him.''  Jolie turned to the side and smiled.  Kiele had taken quite a shine to Zane since he had saved her.  They had seemed like casual acquaintances before, bickering like the young adults they were, but now there seemed to be a whole different depth to their relationship.

``He's strong,'' said Jolie.  ``You know that.''  It was true.  Zane had been through so much, and to survive it all as he had, was a show of his strength of character.

``I know,'' said Kiele.  She placed her fingers on top of his and rubbed his palm with her thumb.  It was soothing.  Not for Zane, but for Kiele.  Jolie waited a while and the two of them sat there in silence, looking at the strong lad.  

Finally she asked, ``Is your father coming to pick you up?''  It was a question she didn't want to answer.  She'd told the doctor what he wanted to hear, that her father had been called, but she had no idea when he would actually arrive.  She felt so embarrassed to be telling her teacher that she had no idea when her father would come to pick her up from hospital.  Once he had heard she was OK, he hadn't cared much.  He knew that if he didn't go to pick her up, she would find her way home eventually.  Heaven help her if she didn't.

At that moment he appeared.  First behind glass, and then through the door.  The girls had no idea how long he had been standing behind them.  He was about six foot and had short black hair.  His face looked weathered but he wasn't what you would consider ugly.  

He hadn't seen them hugging, that much was known, Jolie, who had been facing the doorway, would have seen him.  As the door opened, Kiele quickly released her soft grip of Zane's hand and shrank back into here chair.  

``Hi there,'' he said in an almost cheery tone.  Jolie was perplexed.  Did the man have no feelings whatsoever?  It was obvious that Kiele was in pain, both physically and emotionally and his candid attitude was definitely not helping.  ``Heard you knocked your head pretty bad?''  The question was directed at Kiele but she didn't really want to answer.  Jolie stepped in for her.

``Kiele is fine,'' she said, ``but she's very upset, and needs a lot of TLC right now.''  

``Oh.....sure....sure,'' he said, making wink wink gestures at Jolie.  She wasn't biting.  Her earlier suspicions had been unfortunately confirmed today and she found herself wishing she could just take Kiele home with her.  He looked at Kiele and touched her gently on the arm, ``Can we have a little word before you say goodbye to your friends?''  She nodded obediently and the two of them walked out of Zone's room.

Jolie was left to sit and stare at the young student of hers.  He was so bright, so brilliantly bright, a really gifted child.  He rarely showed it in her classes, but she'd heard rumours from the other teachers that problems they put up on the board to be solved over summer, were solved by Zane in fifteen minutes.  He hadn't liked to brag about it though and had waited until after class before showing the teacher his answer.  He'd even managed to point out a fundamental flaw in one of the math teachers problems.  He'd pointed out that the problem wasn't solvable unless you made a terribly generic assumption.  Zane solved the problem completely, the rest of the class however made the terribly generic assumption.  Maths was the only lesson he dared speak out in.



\thoughtbreak



Outside the room Kiele's father took on a completely different form.  He grabbed her by the forearm, crushing her delicate wrists and she found herself completely unable to flex her fingers.  He dragged her into a spare room and closed the door.  The room was dark, there were no lights on and it seemed to spook Kiele more than usual.  Though she was in a public place, she was scared of her father, more than anyone else on the planet.  To be perfectly honest, she had been almost more scared of her father coming to get her, than she had been of Zane dying.  

``Let go Mark,'' she said furiously, ``it's hurting.''

His voiced raised and hit the ceiling, ``Don't you call me that, don't you ever call me that.  My name is 'dad' understand.''  She nodded.  Why in the hell had she said that?  She was just angry she supposed, angry at his blatant disregard for her friend and her life.  She shouldn't have spoken to him like that.  It wasn't going to grease the wheels.

``What the hell did you do?'' he shouted at her.  ``Are you trying to ruin everything?''  She looked up at the man she so desperately wanted to call dad.  He was far taller than her and she spoke softly and purposefully.

``I don't know what happened,'' she said truthfully.  ``One minute we were there talking, the next, a train had flown through the wall and....''

He cut her off, ``Do you realise what I could have lost today?''  He was mad, really really mad.  She didn't think she'd ever seen him quite this angry.  Usually he lost his head, shouted, threw a few things, broke some of her things, but today, he was so calm, so collected.  She didn't answer, but instead looked out in the direction of Zane.  How she wished she could have been in there with him and Jolie right now.  Maybe he had woken up, he could be talking right now.  

Her train of thought was rudely interrupted as he slammed his hands down on a nearby work surface and said, ``and don't you dare fall in love with that boy.  I have enough to deal with without that.''

She looked longingly for Zane, hoping to be able to see him through the door, the chance was slim as there was an opaque blind in the way.  

``You can't control my feelings,'' she said under her breath, almost a silent whisper.

He became even more angry. ``What did you say?'' he barked.    When she didn't respond he lunged for her and grabbed her round the neck with both hands and flung her tiny body effortlessly against the nearest wall, knocking into a whitewashed unit as he did so.  The items on the unit scattered all over the place, making an incredible racket.  He held her up so her feet were off of the floor and she gasped for breath.  Her hands grappled with his, grabbing and scratching, trying desperately to get him to release her.  Yet his grip was too strong.

When he was done toying with her, he lowered her just enough so she could touch the floor on tip toes.  A medical student had carelessly left a brand new scalpel out on the side of the opposite unit.  He grabbed it, releasing one hand from around her neck, but ensuring all his weight was maintaining her position against the wall.  

Kiele's heart was pounding now.  He'd never been quite this violent towards her before and she was genuinely frightened at what he was going to do next.  He waved the scalpel in front of her eyes to gain her attention.  She followed it to and fro, to and fro before he stopped in the centre and watched her eyes cross.  There was no denying she was a beautiful young girl.

Dad moved the scalpel towards one of her eyes.  As she turned her head to try to keep as far away from it as possible he released his grip on her neck and quickly flung the side of his forearm against the side of her head.  It hit her hard and reminded her of the pain she had felt earlier in the day.  Stupidly she had pulled her head slightly away from the wall when he had released his grip, only to have it slammed into the wall yet again.  

Kiele's head was held in a sideways position.  She breathed heavily.  Her neck felt so sore and she was finding it more and more difficult to breathe.  He moved the scalpel close to her eye again.  This time she just stood there, feet barely touching the ground, lungs almost ready to give out with fear.  With the delicate finesse of a master calligrapher he stroked her eye lid with the back of the blade.  

``Just you remember who the boss really is,'' he said.  She couldn't nod, but then, she couldn't speak either.  She was in a vice.  ``Just you remember your place in things.''  She managed to let out a small squeak which he took to mean yes.  'He was talking about the plan again,' she thought, 'but just what was it that he was planning?'  

He released his grip suddenly and Kiele found herself falling through the air.  Unable to fire the neurons to her leg muscles quick enough, she collapsed in a heap, smashing her head into a metal bar on the bed.

He chuckled, ``Careful.  We wouldn't want you hurting yourself now would we?''  She couldn't tell if he was joking or not.  She also couldn't tell if she was bleeding or not.  She prayed she wasn't, it would mean she would have to go home straight away without seeing Jolie or Zane.  If Jolie noticed her bleeding it would raise too many questions and Mark wouldn't want that.  She had managed to at least right herself, and put up her hand to see if her head was bleeding.

``Relax,'' he said, ``you didn't hit it that hard.''  She hated him right now.  She wasn't fond of him at the best of times, but today, she really hated him.  Why had he and his mother decided to have a child if he didn't like having her around.  Was it her?  Was it something she'd inadvertently done?  Perhaps when she was little she'd done something to upset him?  She would never know.  She so desperately wanted a father, someone to love.  She'd have given up Mark any day of the week.  It was true he paid for her meals and she never went without, but it wasn't done out of love.  It was done so that she could live in servitude to him, her almighty master.

``We'd better get back in there before they get suspicious,'' he said to her and as he turned,  ``Now, you say anything to that bitch of a teacher,'' he started, ``you mention just one word and I swear I'll cut you girl.''  He was deadly serious.  He'd never made a threat on her life before, and although he could have meant he'd just make a small incision on her skin, she knew he meant something much more.  He meant to cut her open, to gut her like a fish.  



\thoughtbreak



She'd tried so many times to run away, but he'd always found her.  Sometimes she'd disappear from school for weeks at a time.  When she returned Mark would always say they'd had a family emergency, or they'd gone on a last minute holiday to somewhere exotic.  It was always a lie.  He couldn't tell the truth; that she'd run away.  He couldn't tell them that she hated him that much that she wanted to be rid of him forever.  A few times the devil had tempted her to kill him.  When he was sleeping, she'd occasionally heard the voice of temptation pushing her onward.  It wasn't her thoughts, she could never do it.  To kill Mark would mean she was stooping to his level, worse in fact.

She hadn't called him dad since she was about ten years old and he had come in to her room in a blind rage and broken her favourite dolls house.  He hadn't just absent mindedly broken the door, he had come in and smashed the thing to smithereens.  It had lain there in a million pieces.  She'd cried herself to sleep that night and vowed that if he didn't feel like her daddy, then he didn't deserve to be called daddy.  It was a brave thing to do for such a small child, she'd lost her daddy long ago.  He was just a guardian to her now, and not a good one at that judging from his actions in the hospital.

One time she'd fled to her alleged grandmothers house, only to find it empty and deserted.  He had scrawled the address down in a book by the phone, he rarely used electronic devices, and she had looked it up when he had been late home from work one day.  She'd packed up her things and left the house.  When she arrived at the cottage, she found it in a dilapidated state.  The paint was falling off the walls literally.  Small children were playing in the old place as if no one had ever lived there.  She'd sat outside crying for half an hour before her father turned up.  

Mark had laughed and called her a silly girl.  When she asked him where her grandmother was, he'd simply said, 'well she was never there, that's for sure.'  She'd asked him why he'd written down a false address, and he'd replied that he had to know where she was likely to go hiding out.  It had sickened her that she had fallen for his trap.  She was thirteen, and just starting to blossom into a young woman, but he didn't care.  He had trodden all over her dreams, squishing them as if they were the dark skinned people he hated so much.

She had never understood that either.  Mark was awfully racist.  Though the acceptance of dark skinned people had increased over the last fifty years, it had made the people who couldn't accept them even more extreme.  Mark was one of them.  It embarrassed her so much.  

Once when they were out, she was only nine at the time they had taken the train into town.  The train had been packed and they had taken to standing until Mark noticed a 'darkie' sitting in a seat behind him.  He spat into the newspaper that the man had been reading.  'Go on' he had told his young daughter, 'spit onto this man's shoe.  He isn't worthy of sitting down.'  She had shaken her head and refused, so he had swiped at her with the newspaper he had been keeping rolled up under his arm.  No one challenged him, as he forced his young daughter to spit on a stranger's shoe.  Unsurprisingly the man relinquished his seat and moved to another carriage, where ironically, a youngster gave up his seat willingly for the old man.



\thoughtbreak



``You remember your part right?'' said Mark as he reached out for the door handle.  ``You keep him interested, but nothing more and remember what I said, don't you dare fall for him Kiele.''  She nodded.  A part of her wondered if she already had, but she wasn't about to let Mark know that.  He opened the door sharply and rustled the blind which hadn't been fixed properly at their lower edge.

They crossed the hospital hallway and entered the room where Zane still lay asleep.  Jolie looked up as they walked in and the victim adjusted her collar to hide the fading evidence of Mark's aggression.  Jolie didn't even notice her temporary scars as the two of them walked in.  Kiele hadn't quite believed Mark when he had said she wasn't bleeding, but now she guessed he must have been right.

Zane stirred, his breathing becoming slightly erratic.  Jolie and Kiele quickly rushed to his side and the teacher pressed the button to call the nurse.  Mark looked across the room at Zane.  It was hard to believe that this boy was going to change his life forever, hard to believe that he was the key to it all, but enough of that now, he was lucky that the boy hadn't been more seriously injured.  The kid needed to rest if he was going to be of any use to him.  

The call to the nurse had been a false alarm as Zane settled back into his rhythmic coma.  Mark took the opportunity to try to drag Kiele away. ``Come on,'' he said, ``it's time to go.''  Kiele sighed despondently.  She'd desperately wanted to see him wake up, just to hear him speak again.  Mark had other ideas.  ``Get your stuff and let's go,'' he repeated, ``unless you know of another way home that I don't.'' 

Jolie had almost been waiting for this moment.  Slyly and ever so carefully she spoke up, ``I can take Kiele home at the end of visiting hours, if you have somewhere you need to be.''  Mark couldn't argue.  He hadn't seen the nurse come in, but now he was in a bind, three against one and the argument was very reasonable.  He let his daughter win this round.

``OK,'' he agreed, ``But you need to be back home by 10pm.''  The fact that it was only four in the afternoon hadn't deterred Mark from asserting his authority.  On the one hand she'd gotten what she wanted, but Kiele couldn't help but wonder if she would pay for it later.  Mark walked over to her and kissed her on the forehead tenderly.  ``I'll see you at home sweetie.''

``See you,'' she said quietly.  

Mark walked out of the door and closed it behind him.  The nurse was still tending to the young man and she spoke as she checked the monitor, ``Did he say anything when he stirred?'' she asked.

``No,'' said Jolie before adding, ``We're sorry for wasting your time.''  

``Not at all,'' smiled the nurse.  

Jolie genuinely felt bad for calling the nurse out on a false alarm.  They must have a million and one things to deal with, she thought, how careless of her not to have waited a few more minutes.

The nurse was about twenty years old and had shoulder length brown hair.  She pressed a few buttons on the monitor to recall the moments of the blip, checking his brain activity, breathing, pulse, amongst other things.  The snap shots showed a small peak each time, but nothing significant.  She switched to one of the neurological graphs.  ``Your friend isn't even dreaming,'' she mentioned as she showed them the graph.  

Both Kiele and Jolie moved closer, eager to see what the graph had to say.  The nurse traced the line with her finger tip which glowed from the luminosity of the screen.  ``You see this section here?'' she asked.  They nodded as she pointed to the small peak.  ``That's when he stirred.  The brain fired off the signals to move his muscles that's all,'' she said.  She hadn't meant to sound so condescending or patronising, but it had seemed to come out that way.  Jolie and Kiele hadn't noticed, they were transfixed on Zane and the monitor.

The nurse finished up her tasks cheerily and walked to the door, her pretty short skirt bouncing as she did so.  How ironic that her cheery nature hadn't invoked the same disgust as that which the girls had felt for Mark when he had first visited.  

``Visiting hours will be over shortly,'' said the nurse as she exited the room.  The door closed behind her and the two just stood there.

``Thanks for saying you'd take me home,'' said Kiele.  ``You really didn't have to.''  Jolie looked at her and smiled.  She had known how badly Kiele had wanted to stay, and having it denied by Mark had brought her into action, like a soldier in the reserves.  

``It's fine Kiele,'' she said.  ``I know how badly you wanted to stay with Zane.''  Kiele sat down again and took up his hand again, now that the coast was clear and Mark had left.  He was breathing so peacefully again now and she so desperately wanted to take hold of him and wake him up.  Though she wouldn't admit it, Jolie would have liked to do the very same thing.  

The two of them sat there in silence for the next few minutes before an announcement came over the tannoy to signal the end of visiting hours.  It had hardly seemed worth fighting Mark now, but it had been a small victory for both women.  Neither of them wanted to leave, but they'd much rather have followed the hospitals rules that the rules of Mark, the evil dictator.  

As Jolie moved to the door Zane stirred again, and they both rushed back to his side but alas, it had been another false alarm.  It was getting frustrating now.  Jolie returned to the door and put an arm out to guide the young Kiele as she desperately tried to outstay her welcome.  The two of them exited the room and closed the door.



