\chapter{07}
\section{}
In Anticipation  

The rest of the week passed fairly slowly and Oken did not see Jay again.  She was very busy with her university work and although she dearly wanted to see Oken, she knew that Friday night was only a few days away.  It was what had kept her going.  Oken had also been wishing for Friday to come and now he had finished the week and it was finally here.  It was the chance for him to show, once again, his mastery.

The anticipation of the fight was still there, pumping through his veins.  He knew all too well that he had to concentrate and not let the thoughts of that sweet young woman get the better of him.  He suspected that her presence may actually make it easier to concentrate.  

It was already five pm and Oken had arranged to meet Jay outside the Zone at six thirty.  He sat on the cream coloured sofa and gazed out across the cityscape which stood in all its majesty before him.  He could see the cars whizzing their way through the mazes of tarmac, beeping their horns as they went.  It was an amazing sight and Oken had been extremely lucky to have been able to afford such a luxurious apartment.  Below him were thousands of people who were all leading their own lives, unaware of the towering figure watching their every move.  

Oken picked off a single car and watched it as it zoomed its way through the streets below.  The car didn't seem to follow a significant pattern, in fact the path it followed seemed rather random.  Oken saw it reach it's destination and from his vantage point found at least three routes which would have enabled the car to complete it's journey in at least half the time.

Most of buildings below Oken's were a good deal shorter, and it was easy for him to see the roadways which had been laid out before him.  He wondered how close Jay lived.  He picked out a little house on one of the roads and had already begun to plan his route there.  Take a left onto Janson Street, right at the traffic lights.  It would have been an almost perfect route to walk as it passed through the park.  The likelihood of Jay living in his town were slim, the likelihood of her living in that particular house were second to none.

Oken looked down at the table which sat purposefully in front of him.  He saw the caustic pattern of light made by the water filled glass which was standing there from yesterday.  Oken rarely drank anything apart from water.  Not only was it good for the system but he liked the taste.  He knew that the water companies added in various minerals and vitamins to the water supply as part of their never ending plan to help the growing youth, but this didn't deter him from drinking it, as it did the growing youth.

As the water rippled in the early evening breeze, the pattern danced and gyrated on the table's surface.  The synthetic beech wood top had a slight orange glow to it which shone in the lights pattern.  Oken watched the distortion of the image that he could see through the water filled glass.  He began to imagine the surface of the water as time.  He watched how it distorted and twisted and it suddenly hit him that Bethany allowed him to do that for real.

Oken picked up the glass and drank from it.  It wasn't that he was particularly thirsty, but he needed something to do to pass the time.  His black holdall had been packed since 4:30 and he was desperately searching for things to do.  

Last week had been easier.  There had been tonnes of final checks to be made and charging of devices to be completed.  Oken looked out of the window again and saw a motor cyclist weaving his way through the traffic.  The constant swerving and turning of the bike made Oken feel almost seasick.  The glass was still in his hand and he placed it back on the table.  He looked at his watch 5:10.  This was pathetic.  He decided to go for a short walk.

As he left the apartment building, he felt the warm sun beat down on his neck.  It had always bothered him when the sun was this hot and he pulled his collar up to cover as much of his neck as he could.   He put his hands into the pockets of his trousers and walked down the steps that he and Jay had sat on only a week ago.  He could almost see her sitting there listening intently to his every word.  He closed his eyes.

He started his walk to the Zone.  It seemed to take longer than usual.  Perhaps it was the anticipation of the fight, or perhaps it was the anticipation of seeing Jay again.  He didn't know.  He crossed the road where the young girl had been knocked down exactly a week ago and could still see the blood stains on the tarmac.  Flowers had been laid by the roadside as a sign of respect for the young girl who had meant so much, to so many people.  Oken was saddened by the fact that he had forgotten about her himself.  He hadn't ever met her, but seeing her in that fragile state, Oken had felt a sense of connection that he wanted to preserve.  He hung his head in a silent thought for her and continued to walk.

As he was early, he decided to take the scenic route to get to the Zone.  The park was in full bloom and Oken felt a subtle sense of irony at the way in which he adored nature.  Oken loved the trees, the birds and the flowers.  Of course he would never admit that to anyone else, not even Jay.  As he thought about it more and more, he decided that perhaps it wouldn't be so bad if Jay found out about his love for the good things in life.  He just couldn't put his finger on the feelings that he had for her and as he walked through the park, he wondered whether he was seeking just friendship from her, or whether he desired something more.

He decided that he would probably know the answer to that question upon seeing her that evening and promptly decided to forget all about it.  The lake in the park was already a buzz of life before Oken reached it, but as he passed, he disturbed the wildlife even further and a flurry of water and feathers filled the air.  He smiled as he continued his journey.

The light was getting a little dimmer now, and Oken could see the sun, now low in the sky, bathed in a ring of flame.  The heavens looked as if they were a burning inferno which would gradually be extinguished over the next hour or so.  By the next morning it would be a cool blue once more.  Oken looked down at his watch and smiled.  Not long to go now he thought.

As he walked through the wooded section of the park his footsteps made crunching noises as they snapped the twigs which lay beneath his feet.  In a childish way, it made him feel superior.  He was the master of the wood.  He brushed past the trees and pulled a leaf off as he passed.  He threw it to the side and watched it float to the ground.  

The Zone was only another few minutes away and Oken already knew that he was going to be early, very early.  He had estimated that he would get there at around 6:00.  His elongated walk had doubled his usual journey time but it was still not enough.  Oken contemplated going into the bakers once again, to get a snack before reaching the Zone, but again decided against it.  As he rounded the last corner he saw the warehouse up ahead.  The big steel door already being guarded by Ruben had begun to rust in places and for a moment Oken wondered about its rigidity.  

The door had three locks on it, spaced evenly along the opening edge.  Rust was forming below each of these too, where the water dripped off after the rain.  Oken also noticed a large dent which distorted the otherwise perfect shape.  He presumed it must have been the result of a brawl or fight or something similar.

Ruben spotted him and shot him a beaming, knowing smile.  Oken felt as though he were an animal caught in the glare of headlights.  He stopped still and saw Ruben turn and speak to someone out of his line of sight.  Ruben's golden jewellery sparkled in the light of the setting sun.  

He found it almost ironic that Ruben was always dressed so smartly.  Oken had, once or twice, asked Ruben why he had never taken up fighting in the Zone himself.  Ruben had always been quiet about this subject, until one evening after a particularly heavy drinking session, Ruben revealed that he wouldn't fight because of his mother.  

She had been a God fearing woman and had tried in vain to impart her religion on Ruben.  He had been there when she had died and her final words were a prayer that he would grow into a nice boy, would look after people, protect them and do what was right.  Ruben had seen his job as a bouncer as just that.  Protection.

The unknown figure that Ruben had spoken to stepped round the wall that was blocking Oken's view and he was surprised to see that Jay was already here waiting.  He looked down at his watch which read a little after 6:00.  He saw her standing there with her bright red hair once again, glowing in the sunlight.  She was smiling and as Oken walked closer, Ruben shouted out to him.

``She's been here since quarter past five.'' he said, giving Oken another beaming smile and Oken could see Jay beginning to go very red.  ``Said she was doing some research or something but I haven't seen any notepad if you know what I'm saying.''  Oken did know what he was saying and smiled back.  Jay had lowered her head in embarrassment and Oken decided to come to her rescue.

``But you know Ruben, that's why I'm here early too.''  Jay looked up at him and gave him a look signifying that she needed no defence, but Oken continued anyway.  ``I'm doing some research too.''  He had now reached Ruben and Jay and he smiled at her apologetically.  

Ruben intervened, ``You can go in now if you want.''  His voice was one of a long time friend.  He was always doing favours for Oken.  Be it getting him into the Zone early or obtaining parts for his weapons development, Oken knew he could always count on Ruben.  

Oken nodded and replied, ``That would be great Ruben.''  The big man gently unlocked the bolts that were preventing the door from opening.  Oken was surprised at how easily the locks turned.  Judging by the amounts of rust on the door, he would have expected them to take a far greater force to overcome hysteresis.  Ruben pulled the door open and gestured for Jay to enter.  She did so and Oken followed, nodding in thanks to Ruben who closed it behind them.

The Zone was the quietest Jay had ever seen it.  There was no music, no jumping crowds, just a couple of production crew members walking round checking that everything was in order ready for the show.  The Zone had lost its special something without the crowds and the music.  It now looked bare and uninviting.  A part of her wondered why she was even here at all.  She looked round at Oken who was still standing slightly behind her.  He smiled at her and walked towards the Chiller.  Jay followed with a renewed sense of intrigue.  

The door to the Chiller made an echoing shriek in the silence of the Zone.  The noise boomed around the chamber and the platform below and Oken saw several of the crew members turn their heads to see who the culprit was.  They both walked into the room where they had been present a week ago when Oken had made his surprise speech.  Jay sat down on one of the chairs at the far end of the room.  Oken sat in a seat which was directly opposite from her.  It was almost as if they were scared of each other, and on some levels they were.

``I think I'm beginning to understand you a little better now Oken,'' Jay said.  ``At first I thought you were just an efficient fighter.  Now though, I see you have a shy side too.''  Oken didn't like being called shy but he could definitely see where she was coming from.  She had sat down first and if he had wanted to, he could have sat right next to her, but he didn't.  He sat opposite her, with the table in the middle guarding the no man's land.  

``Things aren't always as clear cut as we think they are,'' said Oken.  He could see her watching him and decided to change the tact slightly.  ``Did you manage to finish your report?'' he enquired without giving her time to reply to his previous statement.  She nodded and took a sheet of paper out of her bag, which Oken hadn't noticed that she had brought with her.  He gestured a look at the report but was denied as she snatched it out of his vision.  

``You're not allowed to see it until it goes up on the board.''  Jay said in a motherly tone.  Oken smiled and he realised that the decision had been made.  He really did like Jay.  He could see them being happy together but, being the cautious man that he was, there was no way that he was going to reveal that.  He would wait for her to make the first move, if indeed there was to be any moving at all.

They talked for the best part of the next forty five minutes until the rabble started to enter the Zone.  At first the music started out quietly but pretty soon Oken could feel it thumping on the steel door which lay between them and the party outside.  It felt like an angry mob was on the other side banging on the door, trying to get inside and entice the occupants into dancing.  Oken didn't feel like dancing and neither did Jay.  They were happy just enjoying each others company.  

Oken switched the giant television screen on which hung on the Chillers wall and they saw the platform alive with energy and alcohol.  It was not a sight that pleased Oken, but then it was the only place that he could fight like this.  The atmosphere was one thing, but sometimes the people could be real idiots.  Over the past few years, Oken had begun to live for the fighting, but now he felt ready for a change of pace.  He looked over at Jay and wondered if she would be a part of this new pace.

The normal crowd started to gather at the Chiller door and pretty soon the room was abuzz with life yet again.  Oken saw Ruben enter the room and he walked over to his friend, half smiling, in a sort of wicked excitement.  He tapped Oken on the shoulder and began to speak.  

``Hey Oken, you're up against the El Morra tonight,'' he said rather quickly.  Oken raised his eyebrows in surprise and Ruben continued, ``Yeh, he requested it himself.''  Oken nodded slowly and his bottom lip protruded a little.  El Morra was well known in the Zone.  He was more of a legend than a regular.  He only showed up a couple of times a year, but when he did it was normally to vanquish the top dog of the day.  Oken had seen him battle several times before.  He was quick and strong and normally sported a large array of impressive weapons.  

The quiet chatter of the crowd gradually grew to a flutter of excitement.  Several people had overheard what Ruben had said and now the news had spread not only to the Chiller but also to the outside.  People were already cheering even though the main match wouldn't start for another few hours or so.  Even the people down on the platform below had begun to hear the news.  

Zeus and the production crew were already in their little box, testing the cameras out and making sure that each was set-up with the correct slow motion parameters in order to capture Oken's majestic style.  Even Darren, who would normally be donning his bandanna at about this time to avoid breathing the smoke that was regularly purposefully projected in his direction, was feverishly testing cables and radio links to make sure that not a second was missed.  This was to be a spectacular fight.  Oken against El Morra, the two champions.  Neither of them having ever lost a fight.  El Morra had been attending Zone meetings from the very start six years ago, though Oken had the upper hand in that he had, statistically at least, won more fights.

Almost everyone there was sure Oken would win.  There were rumours that El Morra was in serious financial debt and wanted a way to end his life with glory and honour, rather than being captured by the GFC, the Global Finance Committee.  The GFC had a habit of going after people like El Morra, people who didn't generally owe that much, but who were picked on either because of their ethnic origins, their geographical location, or a sad combination of both.

Oken took a swig from his drink, which had been courteously poured for him by one of the barmaids, and relaxed a little.  Jay was now leaning on the arm of his chair smiling.  Almost everyone in the room sensed that there was something going on between them, but nobody wanted to say anything.  He sat back into the chair and let out a big sigh.  He didn't want to tell them but today would be his last fight, whether he won or lost.

It was a shock to Oken too, but he had decided in a short period of time that enough was enough.  Sure, it was exciting to be a member of a highly secretive elite underground fighting culture, but Oken wanted more from his life now.  Now that he had met Jay that is.  For the first time he had met someone that he could see himself being with.  For the first time he had met someone who seemed to return the interest.  Oken had been thinking about it for the whole week and the fight with El Morra had clinched it.  Today would be the day when he would retire.



\thoughtbreak



Earlier that day three workmen had approached Zeus with news that they were afraid of a pressure build up in the train tunnels that would cause the collapse and maybe explosion of the walls which terminated the tracks.  Zeus was informed that there was a simple procedure to rectify the situation that would involve cutting some small rectangular holes in the walls and reinforcing them with steel plates.  The owner was not informed however that these men were actually G-TEP enforcers, sent out by the same team that Jessie had spoken with.  His name was Viktor, General Viktor to be exact, but few people outside the G-TEP knew this.

The enforcers had cut the holes that afternoon and had fitted the metal plates which were there to 'reinforce' the wall.  The holes were fairly small and only measured a foot wide by two inches high.  Zeus had also not been informed that these holes were actually to act as gunning points for the troops to aim through, in order to try and pick off Oken and his weapon.

The men had finished around 3:00pm, way before anyone from the Zone's gathering had turned up.  Zeus tried his best to keep at least two hours between normal business meetings and Zone meetings.  After being assured from the so called workmen that everything was in order and that there was no need to panic, they left.

Now, on the other sides of the wall, in both sections of the tunnel, were two sharpshooters poised and ready to take the shot that would end Oken's reign of temporal terror.  On the left hand side was Lieutenant Ric Palmer, a veteran sniper from the G-TEP's special training camp in Phenley.  On the right was Lieutenant Leon Jackson, a fairly new recruit who was fresh from the same camp.

Leon hadn't been feeling well all day and now he had a splitting headache, made worse by the hundreds of screaming fans and the intolerable music.  He was sure that he was also running a fever and he felt more than a little shaky.  He dropped back from his position at the gunning hole, and sat down on the train tracks.  He took a small bottle of water from his jacket, and sipped it slowly.  He had been briefed on the mission that morning.  It was common practice not to reveal any details about a mission before the day it was to be carried out.  

As Leon sat there, he became much more aware of the tunnel in which he was situated.  It wound its way down for about fifty metres before branching into two directions.  The walls were filthy and the smell was horrendous.  It smelt like someone had died down there and had never been found.  Leon looked up at the ageing lighting which hung from the ceiling.  Water dripped from the bulb and Leon was glad that the railway had been closed down; for he was sure it was a safety hazard.

He checked his weapon over once more and took one last sip from the water bottle.  He placed it back into its pouch and turned around again to once more face the music.  Leon had been top of the training camp.  The building was now littered with pictures of him achieving various marksman awards.  As well as being an A-grade sharpshooter, Leon was also fairly well versed in the intricacies of temporal mechanics.  It was something that came with the territory.

Through the gunning hole, he could see the plethora of people jumping around and dancing.  A part of him wished he could join the crowds but he had a job to do.  He found it difficult to believe that these everyday people could just sit by and watch murders without even batting an eyelid.  This place had been going for six years, that was the intel, and Leon thought that it was about time it was shut down for good.

As he was standing to his feet there was a crackle from his radio and a voice spoke, ``OK, intel says the target should be arriving in around forty minutes.  Stand fast until then.  I repeat, take no action until target has been confirmed.''  

Leon picked up the radio and pressed in the button to reply.  ``Rodger GRT.''  

His voice sounded rather dry and he could hear his croaky tone.  He was definitely not well.  The sweat began to pour off of his head and he closed his eyes.  Only another couple of hours, he thought.  He held his weapon tightly and began using the public in front of him for target practice.  They continued gyrating in front of him, blissfully unaware that he was even there.  The orders had been only to fire if Oken used a temporal weapon, or on the command of a higher officer.  The orders had also specified that if people inadvertently got in the way, then they were authorised to remove them from the equation.



\thoughtbreak



The first fight was about to start.  The Chinese fighter from last week was back and this time he was up against a much more experienced opponent.  Oken was sure that the veteran would win but even so, he considered it a good match.  The door to the chiller opened and the two men exited, knowing full well that one of them probably wouldn't make it back again.

Oken noticed the blade that hung from the veterans belt.  It was fairly short and was still in its scabbard.  The handle was decorated with incredible detail.  There were two dragon heads with their necks intertwining around the circumference.  Oken liked the design, probably of oriental origin.  He guessed that the sword itself may have been an antique, buffed up for the fight.  

The fighters were now out the door and the chattering began as to whose money was on who.  

Jay leaned over to Oken and asked excitedly, ``So who's your money on?''  Oken chuckled and shook his head.  Jay had come to love the frenzy created by the fights, in essence the vivid brutality that Oken had once sported had somehow seeped into her.  She seemed to crave the atmosphere as much as he had.

``I try not to make bets.'' Said Oken.  It was true that he rarely placed a wager on anything, but it was more out of respect for the other fighters in the context of the Zone.  He didn't want to profit from someone else's death.  That was just the way he was.  Jay seemed not to have realised that.  She had thought she had Oken all figured out.  She thought she had mapped him out completely, but she was reminded once again that there was still work to do.

Their attention was drawn away from each other and onto the television screen in the Chiller.  The two tigers were about to be released out of captivity and into the wild, their thirst to survive as prominent as ever.  The music had once again slowed down ready for the fight to begin.  It was the thumping bass line that rattled the crowds, thought Oken.  The music personified the fighting perfectly; the calm before the storm.  The crowds knew what to expect next, an explosion of action and a symphony to the ears.  

The bouncers started clearing the platform away and no one seemed to resist.  It was time for the fight.  They had been dancing for well over an hour now and they were tired and ready to sit back and watch the action.  Ironically enough, there was never anyone sitting in the spectator stands.  

Oken felt the hot air from the dance area outside the door flood into the room.  He felt as though he had been caked with human sweat from head to toe.  It was not a feeling he welcomed.  The smell of hot bodies and mixed cologne was definitely not inviting, at least, not to him anyway.  The room felt a little smaller now, and Oken found it difficult to breathe properly, for fear of infecting himself with the insanity from outside.  He motioned for one of the other fighters to shut the door, so that he could once again breathe fresh air.  The door was closed and Oken relaxed a little.



\thoughtbreak



Leon watched as the crowds made their way back up the stairwells to the spectator stands.  He still found it difficult to believe that people were still engaging in pointless raw brawling as entertainment.  He once again readied his weapon and began practice aiming.  It was  difficult to aim through the gunning hole.  Had it been made a little larger Leon would have found it a lot easier.  He was still sweating and a large part of him wondered if he was going to last the evening.

The two fighters met on the platform below and had anyone looked carefully enough, they would have seen Leon's rifle barrel aimed and ready to answer the call, just behind the reinforced hole.  Leon tightened his grip and prepared to fire.  His radio crackled and the voice spoke.

``These two are not the target.  I repeat, they are not the target.  Stand fast.''  The speech ended with another radio crackle.  It seemed funny to Leon that despite all of the technological advances in the modern world, there was still a crackle on a communications radio such as this.  Unbeknownst to him it was now a feature, as opposed to a flaw, designed to alert troops of both the incoming and termination of messages.

Leon picked up the radio and replied, ``Rodger GRT.''  His voice still sounded rather raw and Ric, overhearing his reply, wondered whether he was capable of the task ahead.  Leon surveyed the battle arena that lay before him through the small slit in the wall.  The pillars could make it difficult to get a shot, however, the holes had been strategically placed to ensure that if one sniper was unable to obtain a clear shot then the other stood a much better chance.  Leon followed one of the competitors as he made his way onto the starting position, marked out by a simple taped line.

The music became even thinner and for an instant Leon wasn't sure it was still playing.  Then the loudspeakers screamed that all important word.  GO.



\thoughtbreak



Oken and Jay were now in the spectator stands, at Jay's request.  Oken had never really watched a fight from up here and he was bewildered at how small everything seemed.  He watched the two fighters run towards each other as the music blared once more.  Oken wasn't an old man, but he was sure his eardrums were about to pop.  He looked across at Jay, she seemed so calm in such a sea of chaos.  The crowds were jumping up and down, cheering for their favourite fighter.  Some of them looked so ferocious that Oken was sure they would have felt more at home in the ring, rather than in the stands alongside his delicate Jay.

He looked back down at the fight below.  The competitors were exchanging numerous blows and blocks, never once letting up and all the time checking their surroundings for anything that they could use to their advantage.

It was about five minutes into the match before one of the fighters found his advantage.  He was being chased by the veteran and he was running towards a pillar.  He launched himself from the pillar into the air, performing a hundred and eighty degree spin.  His legs were coiled up to his body and with one fluid motion he exploded one leg towards the side of the veterans head.  His foot met with his opponents skull with a resounding crack.  The veteran was dead on impact.  Once again the Chinese fighter had proven that he really was as good as the rest.

The veteran fell to the floor, lifeless and Oken couldn't help but feel a little disappointed.  The fight had only lasted five minutes and it hadn't been all that impressive.  It hadn't seemed to bother the crowds at all.  Through the numerous cheers and chants Oken could sense the overall support for this new comer.

Oken and Jay returned to the Chiller as the bouncers began removing the body of the late veteran.  The burly removal men had no respect for the sad, limp body of the fallen hero whatsoever and from the television screen in the Chiller, Oken saw them dragging him up the stairs, his head hitting every step, hard.  Would he have been treated in the same way?  

Oken had become friends with many of the bouncers and hoped he would be shown just a tad more respect than that, though deep in his mind he really wasn't sure.  They were there to do a job after all.  Showing respect to the loser of a fight?  It just wasn't the done thing here.  This was a house of violence and brutality.  

Oken picked up his drink and began sipping it once more.  He felt the cool liquid quench his undying thirst.  The beverage wound its way down his throat and all the while it soothed and calmed his horse innards, caused not from shouting but from the anticipation of the upcoming fight.  Oken could see the Chinese fellow entering the Chiller.  He got up and walked towards the victorious man and offered a hand shake.  The out of breath man accepted and Oken pulled him forward to whisper in his ear.

``You're not invincible.  Just remember that.  Don't let it go to your head.''  Oken's voice was chilling and for a moment, even he was a little scared by it.  The Chinese fighter nodded and walked past him.  Oken had always offered his support and advice wherever possible.  He could see that the power and glory was already beginning to go to this guys head.  He just wanted him to see that fighting was the not the be all and end all.  

A part of him yearned to shout hypocrite, as fighting was all that Oken had lived for, for a very long time.  It was only since Jay had appeared on the scene that he had begun to think otherwise.  He felt ready now though.  After fighting for so long in the war, the spirit had begun to leave him.  He felt ready to start his life again with something new, someone new.



\thoughtbreak



Leon had never seen anything like it in his life.  His expression was one of amazement and disgust.  For the one part, the sheer speed and agility of the fighters made him envious, on the other hand though the brutality of it all was very difficult for him to take in.  Leon had heard the crack of the man's neck as the Chinese fellow had kicked him.  It had been a cold murder, one which would have had him locked up for a good many years, if the police had been involved.  Leon had been a police officer before becoming a G-TEP enforcer.  How he wished he could go back to those days now.  

The police weren't there however.  The G-TEP was above the law.  The government had deemed it necessary to give the organisation complete control over situations of a temporal nature.  These enforcers were given special dispensation to kill anyone who they deemed necessary, to preserve the accurate flow of time.  

There had been many protests over the power that the G-TEP enforcers held over the general population.  One particular demonstration in Liast had seen over three thousand protesters marching to the government building in the capitol, screaming at the tops of their voices for the government to repeal their decision and to prevent such atrocities from occurring.  It had started off peacefully, but very quickly had turned into a bloodbath.  Two hundred people lost their lives amid the stampedes and police crowd control.  Dead bodies had lain everywhere and the news of this event sent shock-waves through the far reaches of the Emblem.

Leon had remembered that day well.  The news had come while he had been studying for his final G-TEP entry exam and had made him second guess his decision to join this ruthless force.  He didn't want to be hated by the world, but at the same time, he felt like he had a job to do, that he had something special to offer.

Suddenly Leon's stomach got the better of him and he promptly vomited down the side of the train tunnel.  He cleaned himself up and looked away from the mess he had just made.  He couldn't smell the revolting pile of sick that was festering on the floor.  The odour seemed to be so at home in the tunnel that Leon noticed no difference.  His hands started shaking and his self confidence wavered uncontrollably.  Was he up to the task?  He reminded himself of the sights he had just seen and recomposed himself.  This was one of the most important missions he would ever go on wearing his G-TEP uniform.  It was his first.

