\chapter{46}
\section{}
Prophecy Fulfilled  

The knock on the door had taken them all by surprise and the figure behind the knock shocked Jolie even more.  Ruben stood there now at the door to the basement, watching Zane who was frantically pacing the floor.  Just what had changed his mind?  What had made him suddenly come rushing over to their aid.  Jolie didn't know, but she was about to find out.

``What changed your mind?'' she asked.  

``I guess I listened to what you said a little too well,'' he replied.  Her words had stuck with him.  Though she hadn't said the phrase 'second chance', it was something he felt he could gain from this.  A chance to do things right, to set the record straight with his god.  He wasn't a bad person, sure he made mistakes, but then didn't everyone?  It wasn't about making mistakes, it was about what you did to rectify those mistakes.  

He didn't want to divulge exactly how he had escaped from his quarantined state.  After the incident at Kaitlin's, Jessie had taken Ruben back home and posted some guards outside.  He knew Ruben was a broken man, he wouldn't fight back, Jessie had taken everything from him.  Everything but the glimmer of hope he had seen and felt talking to Jolie.   Ruben had easily overpowered the two guards, knocking them unconscious and strapping them to the banister of his stairwell.  

Seeing as Jessie was the only one who had him under surveillance, no one would know he had gone, at least, not in the immediate future.  Ruben had picked up some supplies and left the house, hailing a taxi and setting off towards the Matthews residence.  

Ruben was still a little out of breath from running to the door.  It had been left wide open and he had just fallen inside.  He had seen the others sitting in the hallway and had called out to them.  Now he stood there, resolute as ever to prevent Jessie from winning.  He was going to protect Kiele, Jolie and the boy, whom he had yet to meet.

``We have to catch him as soon as he comes back,'' said Zane, ``I've got no idea when he's going to make his next jump, he could have even programmed it into his returner.''  Had Jessie really planned that far ahead?  ``Once we catch him, everything will be fine.''

``Not entirely,'' said Ruben.  ``I don't believe we've met yet'' he said extending his hand out towards the young boy who was still down in the basement.  Zane continued pacing, this was no time for pleasantries.  

``My name is Ruben, I was the one that was charged with guarding the device up until now.  Up until I was blackmailed into giving it up.  You are?''  His change of tone seemed almost bipolar.  

Zane remained silent.  He still didn't trust this figure.  What possible reason could he have had for giving up the device.  If he had kept it safe, none of this would have ever happened.  

``That's Zane,'' chirped Kiele.  ``He worked on the device, believing it to be a sanctioned action for G-TEP.''  Ruben nodded.  Zane continued to pace.  

``Zane,'' Ruben began, ``You have to make a jump too.''  The boy stopped pacing and looked up at the tall dark figure.  ``You are the one that saves Kiele.''  Zane didn't believe him.  He kicked a box in the basement as he continued to pace.  If Jessie showed up now, he was going to throttle him.  He gripped his fists tightly, believing his fingers to be tightly wrapped around Jessie's throat.

``I refuse to jump,'' he said.  ``I can't risk changing the past.  I can't risk making things any worse than they already are.''

Ruben interrupted him, ``But you do jump Zane.''  He continued, ``After I spoke to Jolie, I gathered as much intel on the crash as I could without raising suspicion.''  He pulled out a few sheets of paper from his pocket.  ``There were two people moving on that train, Jessie was one and I know for a fact you were the other.''

``How can you be so sure?''  He shouted back.  His pacing had stopped now and he was standing, hands on the railings of the stairs looking up at Ruben.  

``I analysed the data that came back from an explosion that occurs on the train,'' he said.

``So!''

``So the only thing that could have made that kind of explosion was a Greenberg XRS-49 fragmentation grenade.  I also happen to know there are only fourteen in existence, a bit of a collectable really.''

``What makes you think that it was me?'' Zane said loudly, ``What about the other thirteen people?''  He suddenly thought of something, ``Besides I don't have one?''

``I know,'' said Ruben.  He reached into his back pocket and pulled out a small spherical device, about the size of a tangerine.  ``But I do.''

He held it up in the light.  It looked like any standard issue grenade, a large yellow stripe round the equator with the letters XRS-49, embossed in the side and accentuated with a grey paint, complementing the green of the shell.  The pin and trigger were shining, almost made of chrome and Kiele saw the reflection of Rubens eyes as he held it up for Zane to see.

``So you see Zane,'' started the man, ``it's highly unlikely to be anyone else, seeing as you are standing here,'' he threw the XRS-49 down into the basement, ``you have the grenade, you have access to a time machine, and you have a reason to want to go back.''

Zane had caught the grenade.  He had been a little surprised that Ruben had thrown it to him, he had always considered these kind of things to be exceedingly dangerous but then he guessed Ruben knew better.  He looked at it.  In his hand was a weapon of incredible power.  Part of him wanted to cram it down Jessie's throat, part of him wanted to blow the device sky high, but he still had to use it.  Damn. 

``Zane,'' the voice had increased in urgency, ``You have to go now.  If you wait any longer, Ric will see two blips on his radar instead of just one.  If you go now, your temporal echoes will merge in Jessies'.''

Was he really going to do this?  He looked up at Kiele and Jolie who were both looking at him, blissfully unaware of the fear that was gripping his heart.  He had expected Jessie to know, at some level at least, details of his work on the device.  As it had turned out the whole thing had rested on him, his theories, his work.  What if he had gotten things wrong?  He guessed as the accident had occurred, he must have created a successful device.  Damn time.

``You can do it Zane!''  It was Kiele.  She had remained relatively silent throughout their exchanges, only making a noise to agree or disagree with something he or Ruben had said.  Now she took full control of the conversation.

``I know you're scared,'' she said, ``but I also know that you will always protect me.  I have known it from the moment you saved me in the Zone.''  She moved forward and walked down the stairs to Zane, throwing her arms around him.  She could feel his beating heart, so strong, so vibrant as it bashed against her breast.  She kissed him hungrily, their lips cleaving to each other and his fear left him.  Kiele was right.  He had vowed to protect her always, he would jump.  He must jump.  Kiele needed him.

``I guess this is it then,'' he said.  

None of them had any idea whether he would make it back alive.  It had appeared that there was no body in the wreckage, but then who could tell.  There had been one partial skeleton found , but it had been so badly damaged that it was unidentifiable.  Ruben neglected to inform Zane of this.  Of course the skeleton was that of Markus the train driver, but Ruben didn't know this.

Zane broke away from Kiele's embrace and walked over to the control panel before making some adjustments to the computer, trying to account for movement of the train and various other environmental factors.  Jolie joined them down in the basement and Kiele walked over to her, hugging her tightly, requiring an acknowledgement of some kind.

The light from the monitor filled the room with a glow and Zane now took hold of the second returner and plugged in one of the four remaining power cells.  The other he placed into the second portable shield generator and stuck it into his pocket.  He breathed deeply and looked over his shoulder at his companions.

``Perhaps you'd better get out of the basement,'' he said, ``Remember what it was like last time?''

``We're not going anywhere Zane,'' said Jolie, ``it didn't kill us before and it won't kill us now.  We're here for you.''

He smiled.  He missed his parents.  This was the kind of love and support he had been used to.  Not the half hearted attempt of care that the government had offered.  His heart raced once more.  This really was it.  He checked everything again.  

``If all goes well,'' he said, ``I'll see you soon.''  

Kiele attempted to walk towards him once more, she wanted to hold him one last time, but Jolie held her back.  Zane was ready.  Jolie couldn't imagine the amount of courage he must have mustered to reach this point.  Kiele would break his concentration and she knew by the look on Ruben's face that time was not something they had an abundance of.  The dark figure nodded in agreement to Jolie.  If she hadn't stopped Kiele, he would have probably stepped in in her place.  'Better that it was done by a friend,' he thought.  

Ruben still couldn't believe how closely she resembled both Jay and Oken.  She obviously had no idea who her parents were, and he wasn't about to tell her.  It was better this way.  Her soft face was waiting expectantly, her eye almost twitching as she waited for Zane to press the button and ignite the chain of events.

``Kiele,'' he said finally, ``I love you.''

Before she could reply he pressed the button and his body was thrown up into the air.  The shell of light grew, quickly at first from the centre of the device in his hand.  The muscles in Zane's hand were tightening now.  The shell slowed as it enveloped his body, moving to every extremity of his relatively fragile skeleton.  His left hand managed to keep hold of the device whilst his other spasmed into claw like poses.  The tone began, low at first, then rising.  Zane's body began to convulse, hovering three feet in the air it jerked and rocked as wave after wave of temporal energy hit his flesh.

Zane was in pain.  His face contorted and his vocal chords were unable to make a coherent sound.  He screamed out and his agony finally found a voice.  It was echoed throughout the shell which had now began to encompass the other occupants in the room.  Kiele tried to scream out too, but no sound was heard.  The noise was unbearable and brought her to her knees followed swiftly by Jolie and Ruben.  She tried to make her way over to Ruben to ask him to stop the process, but something held her in place.

Zane's body was racked with vibration now, shaking faster and faster.  He was sure his muscles were about to burst, his bones about to crack.  The sphere had reached its maximum and began to shrink rapidly.  As it closed around his body it appeared to cut him.  Inside the sphere, his body was present, outside it didn't exist.  As the three other people in the room looked at the poor boy's body, they could see the shell seemingly cut him into a small and smaller pieces, taking his arms, legs, head as it reduced around the returner device.

Kiele threw her hands over her eyes as the three of them were thrown once again to the floor.  She couldn't bear to look any more.  The shell receded completely and the noise vanished.  Zane was gone.  They looked at each other in a weird sense of confusion.  Now all they had to do was wait.

It was agonising.  The machines whirred away to themselves, tethering the two explorers to the time-frame, awaiting their return.  Kiele had peeked at Zane just as he had vanished and had seen the pain screaming across his face.  It had been one of the hardest things to watch in her life and now her emotions managed to get the better of her once again.

``It hurt, didn't it?'' she asked, picking herself up off the ground.  She dusted her skirt and blazer off.

Ruben tried to alleviate her fears.  ``Not necessarily,'' he said.  They all knew he was lying.  It had looked like the single most painful experience anyone could ever go through.  Kiele still couldn't shake the image of his rattling body, floating, bathed in the light of the shell.

Would he ever return?  

As they sat there the room all of a sudden began to shudder slightly.  At first it could have been mistaken for optical fatigue, an artefact, something a little odd.  It happened again, and in an instant there was a glowing sphere in the room.  Someone was coming back.





