\chapter{10}
\section{}
The Lesson  

The history lesson had started very slowly, and Zane had wondered at various point throughout its duration, how much longer it was going to take.  He had never had a particular interest in the past, thinking it to be a useless recollection of mankind's mistakes.   He looked around the room he was sitting in and breathed a sigh.

There were about fifty chairs and tables in the room, each one occupied by a young human being of around seventeen years old.  The more enthusiastic of these had books and stationary adorning their desks.  The less enthusiastic, like Zane, preferred a more relaxed approach.  He had his legs stretched out and he was sitting in a kind of slump in the polycarbonate chair.

Around the walls were posters and pictures of various historic events.  Zane didn't think he'd actually ever looked at one closely.  The lecturer scanned the class room and her beady eyes met with Zane's.  She gave a disapproving stare at the way in which the young man was sitting, and after a while he shifted his position in order to stop the eyes which had begun to burn through his skin.

The floor was made from a granite composite and looked all shiny and new.  It was the only part of the room which Zane found remotely interesting.  Perhaps that was why he spent most of his time staring at it.  It had been coated with a special protective layer, to stop the chairs from scraping it when the rebellious mob left their tedious lectures.

The window caught his eye next.  Outside, there was an array of students playing various games on the fields which surrounded the college building.  He saw how happy they all appeared and a part of him wished he could join them but then he remembered how much he hated sports.  He just wanted to be out of this damn lecture.  He was studying Physics as his major, and why he had to take a damn history lesson he would never know.  Supposedly it broadened their horizons.  'Kept history teachers in work more like,' he thought.

After about fifteen minutes or so Zane's attention was suddenly drawn to the screen upon which pictures of a grey haired man were being shown.  Zane sat up and listened.  It wasn't often that they got to see pictures in the lecture, despite all the advances in technology.  Normally research of this kind was set for homework.  

The lecturer began commenting.  ``Oken Brown,'' she paused, ``He looks harmless enough but he was one of the most ruthless criminals ever to have graced God's earth.''  Suddenly Zane became interested.  ``He developed the first hand held temporal weapon, and used it in an underground fighting arena only twenty years ago.''  The lecturer had begun pacing and she could see that other people in the class had begun to show some interest too.  She was a small woman, in her late twenties with her shortish brown hair swept back and tied in a small pony-tail.

``He was born in 2009 and was sent, as a young man to fight in the temporal war.''  The students were never taught much about the war, it was mostly an unapproachable subject deemed too horrific to talk about.  ``After this, he returned home a changed man.  Before going to war he had dreamed of becoming a respectable physicist, hoping to work at the university, developing temporal computation devices.  But the war changed him into a ruthless killer.''  She emphasised the words 'ruthless killer' in a way which made it sound like a child's story.   One of the students laughed and was promptly thrown out of the class amidst the chuckles and giggles of his fellow classmates.

``Now if I may continue,'' said the teacher, ``Oken Brown found a job working at a local library in the science section.  He stacked books all day everyday, but at night, once a week; he would go and compete in one of the most brutal sports known to man, at the Zone.''  Zane was getting more excited.  They never normally put the projector on for one picture.  There had to be more.  There just had to be.  He sat there in his hungry anticipation and waited for the pictures to roll by.  Maybe they would show Oken's temporal weapon.  Had Oken been there at that moment he would probably have smiled at the attention his picture had created.

``Oken killed over thirty people during his three years attending the Zone's meetings.''  The pictures on the projector screen changed to show the doctors certificates that the Zone attendees had used as their trophies.  ``These certificates were put on display as trophies to show off the fighters skills.''  Through the flicking of the pictures, Zane noticed two words cropping up almost constantly, Oken Brown.  Several of the pictures had bullet holes visible somewhere in the image.

The teacher continued, ``On a bright summer day in 2038, Oken Brown brought a temporal weapon to the Zone.  The following video footage may disturb some of you.''  The projector changed its constant hum to a high pitched whistle as it began to play video footage of Oken's first battle against Yaz.

It was at that moment that Zane first saw Bethany.  He saw Oken begin to twist and turn the metallic beauty.  It cut the air, leaving a trail of amazement behind the sharp blade.  Zane had never seen a sword like it.  It was a cross between science fiction and fantasy.  The crystal hanging majestically in the centre of the blade gave it a sci-fi look, while the oriental handle gave it a more fantasy feel.  Zane was truly astounded.

The lecturer continued, ``What you are about to see is actual footage, shot at actual speed.  There is no camera trickery involved.''  The video showed the moment when Oken had first squeezed the handle of Bethany tightly.  For an instant, Oken seemed to slip into some sort of hyperactive dance.  It looked as if the camera had been replayed at a higher speed, but Oken still retained his majesty and skill.

Some of the students started shouting out in disgust.  Jeering at the teacher and yelling about trying to corrupt them with fake videos.  Zane knew different.  It wasn't only his faith in temporal mechanics, but he had seen something the others had not.  They were continuing to badger the fragile teacher as she shrank back at her desk.  She had tried to get a word in edgeways, but had failed.  Zane stood up.

``Hey guys, shut up.''  His voice was stern and the class reeled at the volume at which the words had left his mouth.  Some started jeering at him but he continued unabated.  ``Jolie,'' he said, addressing the lecturer, ``play the video again.''  She nodded and the video began again.  Several people threw their arms up in disgust at the idea of having to sit through the façade again.  Zane took the lecture over.  ``Notice how the rest of the building is reacting to his movements, albeit at at slower speed,'' said Zane.  ``Notice also the reflections of the lights in the blade.''  

The students were astounded.  It was at that point that they too saw the unimaginable power which Oken had possessed.  Several of them raised their eyebrows at what they now saw to be genuine, but one of them still couldn't make the leap of faith and protested to Zane.

``It's CG man.  It's been done on a computer.''  He shouted.  Zane looked over at him with a tired glance.  This particular protester was always a pain when it came to discussions.  Zane felt it best to end it there, rather than protest any further.

``You believe what you like, I know my truth.''  The class roared in admiration for Zane.  He was well liked among the students and held a certain rapport for being a peacemaker.  It was true, Zane was a peacemaker, and a good speaker too.  He had been brought up well by his parents who had died in an accident shortly before his sixteenth birthday.  Unlike some people who tended to de-rail in these circumstances and rightly so, he had found strength in the memories of his parents and had been able to live a practically normal life.

Zane was beginning to enjoy this lecture even though he had vowed that he never would.  There was something about this Oken character that intrigued him.  It wasn't the fact that he had been a cold blooded killer, or at least, that's what Zane had immediately classified him as, but his dedication to science.  The fact that one man had single handedly created a temporal weapon with little more knowledge than what he had read in books.  This guy must have been a genius.

Jolie regained control and continued, ``A week or so after the shooting of this video, this man, Oken Brown was killed, along with his lover, and several other people in a G-TEP raid at the fighting arena.''  Zane's eyes widened with surprise.  He had expected this great man to have escaped the authorities.  He had expected better from him.  In the short few minutes that Zane had been acquainted with Oken, he had developed a certain affinity for him.  Now he was  angry with him.  Zane had wanted to see more.  More of this skill.  More of this sheer mastery.  ``It is not known exactly how the fire-fight started, but it is believed that Oken had decided to use the weapon against innocent bystanders and that the G-TEP forces opened fire, purely to save lives.''

``It was shortly after this, that not only were all people who had had exposure to temporal weapons massacred by the government, but all literature related to temporal mechanics was sought out and destroyed to try to prevent any more events like it.''

The class idiot who had earlier been removed from the lesson made a good eighty percent of the class jump by slamming his face against the window and making groaning zombie noises as he smeared his ugly mug up and down the window pane.  Zane didn't jump.  Neither did Kiele who had been staring at the window, waiting for the inevitable to take place.  Jolie shot the boy a glance, waiting for his idiocy to subside.  When, after around 45 seconds it hadn't she walked towards the door and exited.

Throughout the entire episode of the disciplinary hearing taking place in the corridor, complete with jeering and general noise making from the rest of the class, Zane sat in complete silence.  The current situation owed him no attention whatsoever.  To him, the current situation was a nuisance and an annoyance, hindering him from hearing about a subject that he had only recently started paying attention to.  Zane starred at the slowly pulsating image on the wall.  A slight distortion ran down the image at regular intervals, and prompted a quick concern about the quality of the equipment from Zane.  The face of Oken seemed weathered and old, though he could only have been around thirty years of age, he thought.  

Little did anyone in the class realise, but Zane had a secret passion for the temporal things in life.  Temporal mechanics was a closely guarded secret these days.  Many in fact, didn't know it was a separate physics subject.  Zane had been told about it by his father who had been a retired G-TEP enforcer prior to his death.  Zane's father had told him many stories about working in the G-TEP, but none about any actual, real missions, involving real temporal terrorists.  It had always annoyed him somewhat, but he had respected his father's profession and his decision to hide certain truths from him.

Zane remembered one such story about a woman who had filed a claim that her boyfriend was a G-TEP violator.  The lead up to the operation had taken several months, with the woman providing information on a weekly basis.  Time and motion studies, reading habits and even bedroom encounters.  The G-TEP mounted a huge force and one morning stormed the building, only to find the man in bed with the woman's best friend.  The claim had been false.  The woman had wanted only to get back at her husband by gracing him with a visit from the G-TEP forces.  What she had failed to foresee, was the shooting of both her best friend and her lover, whom she had already forgiven in her heart.

Zane's father hadn't been present on the mission, but had told Zane the story many times, as an encouragement not to cry wolf, and to always tell the truth and strive for justice.  He had also told his son that true forgiveness harboured no ill feelings, or revenge, that he believed that the woman couldn't have ever really forgiven her boyfriend.  The woman was ordered to be executed for her part in the atrocity.  

As it was, these storied fascinated Zane, and had made him yearn to understand temporal mechanics one day, despite its outlawed status.  The video of Oken had only served to drive him further forward into his fantasy of one day controlling a temporal device.  His love of physics was clear and he had been awarded several prizes already for his work and experiments, even at such a young age.  

The disciplinary in the hall way had escalated to the point of a student throwing a chair through a window.  Zane sighed.  This was supposed to be a good school.  One of the best in the region.   He watched as the glass fell to the floor and scattered itself in disarray.  In the distance, Zane gathered that the principal had been called to the scene and the student was now being dragged away by security officers beating him as they went.



\thoughtbreak



Though times had become much more peaceful in recent years, it had been seen by many to be only as a result of a society living in fear.  It was true, most people went around their daily lives doing exactly what they were asked, exactly what they were supposed to do, but it wasn't so much that they were good people, rather that they were scared of the consequences of doing something, doing anything wrong.

Almost every building now had a security officer assigned to it to assist in keeping the peace.  The overhead of this new civic service was extreme.  Taxes were high and people were generally poor.  If you lived in a particular part of town, you would all generally have the same cooker, the same washing unit, (which had come to unite the dishwasher and washing machine), the same media unit, even the same curtains and often, front door.  Clothing was practically the only thing to distinguish the throng of people in their daily daze.

The world had become bland and boring, but certainly not uneventful.  Though the frequency of terrorist attacks and criminal activity had decreased, the scale on which these events now happened had increased dramatically to compensate.  A father disheartened with his lifestyle and the fact that his wife was having an affair didn't just kill his family any more, he killed the whole damn street.  Anyone who spoke to his wife on a daily, weekly and sometimes even monthly basis was a target.  Society lived in perpetual fear.

Zane had, like most, grown up in this society knowing nothing of the previous world.  The youngsters of the day were starting to bring back some of the good old mischief that Zane's father had occasionally told him about.  The fear was slowly regressing.  Tearaways like the mischievous student were becoming more common place.  Life was returning to normal.



\thoughtbreak



Jolie returned to the class looking flustered and tired.  In the preceding battle she had lost her usually prim and proper hairstyle and looked, to all intents and purposes, as if she had literally been dragged through a hedge backwards.  She scanned the class, presumably looking for other potential trouble makers.  The large beating stick of the security officer standing to her right was a quiet symbol of the undying peace she was expecting from the rest of the lesson.  

Zane felt sorry for Jolie.  She had been teaching at the college for several years now but he had never really gotten to know her.  She taught history and he loved physics.  Having said that, the previous history teacher had been bland and inoffensive, but Jolie had tried on several occasions to spice up the lessons and the curriculum with trips out to locations of famous battles or events, usually ending with either boredom for all involved, tears from one of the girls in the class at losing some item of jewellery or make-up, or a little bit of both.

She just didn't seem to know how to engage her students,  until today of course when her choice of subject had hit jackpot for Zane.  For some reason he would never be able to understand that just because he was interested in the subject it didn't mean everyone else was.  He wasn't a particularly selfish person, he didn't believe the world revolved around him, but he had a strange perception that most other people agreed with his tastes.  He put up his hand as Jolie was sitting in her chair at the front of the class.  ``Jolie, do you have any more footage to show us?'' Zane asked.  The class groaned.  It sounded like a fog horn that ships used to use in the 1900s.  

``I don't have any more footage to show you Zane, but I do have some more information,'' Jolie replied, as she sank back into her chair.  She placed a data disk into the console in front of her.  The spinning disk built up speed almost instantly and data began streaming to each of the pupils consoles sat neatly on their desks.  Her chair cast a stark shadow against the wall at the back of the class as the low mid afternoon sunlight streamed in through the window.  If Zane moved his arm slightly to the left he could make it look like the chair only had three legs.  A passing thought, as the reality of Jolie's comment sunk in, and the noise of the console brought him to life.

The screen turned blue, and a report about Oken was displayed, it detailed his war efforts, who his parents had been, and had a link to a report about Jay.  It was obvious that someone had either misinformed the researcher, or they hadn't dug as deep as they could have done for they listed Jay as having lived with Oken for three years before his final battle, and that they were about to have a child together.

Zane studied the information carefully.  So Oken had worked at a library, Zane read.  Was this where he gotten all his knowledge from?  Zane sighed.  He'd never be able to do the same.  The books were long gone.  There really was nothing left.  It saddened him that the government seemed to follow the same recipe every time.  If there was something they didn't understand, or couldn't make money out of, they destroyed it.  

Zane had read about a disease that was ripe in the early 21st century called cancer.  It had been cured by a man called Jacob Toulouse, but had caused such a significant drop in pharmaceutical sales and medical development that the government had papers drawn up, showing that his research was flawed, and when people spoke out against their 'findings' they mysteriously disappeared.  Once public knowledge of this had spread, people began to distrust the governments of the world, and the rest as thy say is history.

Oken had been a well educated man, why had his life taken the route it had?  Zane mused over Oken's military career and the obvious effect it had imparted on him.  There was nothing really detailed in the report, just a few pieces of information here and there.  Why was Jolie telling them about this?  What did it have to do with the course?  Jolie's next words would explain all.

``I'm teaching you about this event because we are living mere miles from the origin of this event, and the epicentre of the repercussions that would eventually spread throughout the world.''  She stood up and bent over to face her students, leaning on the desk in front of her.  The desk was old in style, but new in manufacture, made of poly-wood, the all purpose plastic wood alternative, so the singing termites chimed on the advert.

``This man single handedly changed history.  Our history.  It wasn't long ago that this man used to walk the same streets we walk today.  It wasn't long ago that his dark and benevolent nature was rife in this very town.''  Jolie could feel herself getting carried away with her own words.  Why would they care that she had written her university D-chat, on Oken and his effect on society? 

She slowly thought back to the months she had spent researching and painstakingly piecing together evidence about the last few years of Oken's life.  It had been an obsession that she had never wanted to end and truth be told it hadn't.  She was still on the lookout for information, spending her weekends delving into papers and researching leads on the web.  She knew she had gotten some details wrong, but overall, she had been pretty pleased with the result.  

Jolie had good reason to be impressed with herself, she had passed the course that year with a grade at least two steps higher than anyone else in her class.  Zane would never have let up questioning the young teacher if he had known, it was lucky for Jolie that he hadn't read the name of a certain historical paper that used to grace his fathers desk from time to time.  

``Tomorrow, I'm taking you all to the site of the Zone itself.'' She said.  ``Many lives were lost there, and to some it can be a disturbing place, but it should help you complete your assignment for this week.''  She turned and began to write on the blackboard.  Zane could hardly contain his excitement.  

Kiele was bored.  It was strange to find a blackboard in such a modern school, but recently it had become a hip new trend to bring back some of the old teachings tools to create a contemporary rustic feel to a school.

The words began to form as the white cylinder deposited its life force on the board.  The thousands of words it would write somehow contained, almost constrained within its body, itching for someone to use it and release its wisdom.  In the hands of some, it would bear great fruit, in the hands of others, only bad advice and ill thought words would come forth.

The wand finished its journey across the black landscape.  The handwriting of this young enthusiastic teacher was riddled with loops and fancy curls that most would find difficult to read.  Zane was used to this kind of scripture.  His father had made him sit down many times and write pages and pages of cursive writing.  It was his insurance that if all electronic devices failed Zane would be a king among men, able to still write properly and elegantly.  Most schools and colleges now taught writing in block letters, using a varied form of the Arial font, prevalent in the early 21st century.  Zane's father had despised the decision and had vowed to teach his son how to write properly.

``How do you think Oken would have felt knowing the impact of his actions during his last fight?  Discuss.''  It wasn't real history for a change.  Zane was actually a little excited at this assignment.  It was creative writing, something Zane had always wanted to have a flair for, even believed that he did have a flair for at one stage, until that blasted Cacey Rustle had started reading his poem out in class, much to the amusement of everyone present.

A siren sounded, indicating the end of the lesson, and in fact, the end of the day for Zane and his class.  His classmate who had been thrown out earlier was now outside in a cage, awaiting transportation home.  It was a common sight to see a troublesome student, even at university level, being confined to a cage.  Many had protested against the practice, but it seemed to serve a purpose.  The students were made to feel like a monkey for a day, or even just an hour, and the next day they were model citizens again.

As the class filtered out of the room and into the hallway, Zane and Kiele were the only two students left.  Jolie walked over to them, pausing briefly to let a rabble of marauding monkeys go past.  ``He's a pretty interesting character all right.''  She motioned to the board, where Oken's face was still being emblazoned into the wall.  ``I often wonder what he would have done, if he had known what was coming.''

``Perhaps he already knew.''  The voice was new, new to today's cacophony of sounds anyway, a mile away from the primates that had left the room only seconds before.  Softer than the siren, and more serene than Jolie.  It was Kiele.  She started again, ``I mean, perhaps he had already seen the future and knew it was the right thing to do.  It's possible.  Right?''

``There is no evidence to suggest that Oken could see the future Kiele.  I'm sorry to tell you, that all he seemed to be able to do was affect the flow of time.''  Jolie seemed already tired with this line of questioning.  It was as if she'd asked the same question many times herself, and no matter how hard she'd tried, she hadn't been able to come up with a shred of evidence that there was any decency inside the dark figure that was Oken Brown.

``All he seemed to be able to do.''  Zane repeated the words coldly.  ``All he seemed to be able to do?''  Both Kiele and Jolie were a little taken a back by the words that just fell out of the mouth of the young boy sitting staring at the picture on the wall.  ``The guy was a freakin' genius.  He read books at the library and made something that affected the flow of time.''  Zane still seemed to be in a daze, mesmerised by the image, still flickering not five meters in front of him.

``But people had done it before Zane.  Oken was not the first.''  Jolie seemed to be in an argumentative mood today.  It ticked off Zane.  She sat on the corner of one of the desks and knocked off a dictation device.  She bent down to pick it up and Zane noticed for the first time a small tattoo in the small of Jolie's back.  

``Nice tatt Jolie.''  He said softly, his anger fleeting for a second.  The teacher turned a pale shade of pink and even Kiele felt for her.  Zane seeing the tattoo had been a mistake.  Though she had nothing to hide, that small indiscretion was something she was not proud of.  It was almost as if Zane had violated her trust, almost as if he had seen her naked.  

She continued, ignoring his remark, ``Besides, Zane, Oken probably had help from friends making the device.  I doubt he could have achieved something so complex on his own.''  This last sentence seemed to have marked the end of the conversation in Zane's mind.  Already he was exploring new possibilities.  Not even caring about the response just aired.

``I bet he even had a name for his sword''  Zane ventured.  Kiele giggled.  

``Yes Zane, I'm sure he named a piece of metal.''  She tittered away to herself, and though he would defend his statement, he managed to release a slight grin.

``People used to name their cars back in days gone by.  It was a way of associating with an object which they would often spend a great deal of time with.''  Zane's smile vanished.  ``Perhaps it was a way to justify spending so much time with an inanimate object.  Personifying it.''

The luminosity of the  classroom had grown dim and just then the automatic lighting switched on, bathing the room in a warm yellow glow, not dissimilar to the current hue of the dying sun.  The beams of light from the twelve overhead tubes covered their faces in photons, changing their appearances ever so slightly and making their features softer and less angular.  The diffuse filters in front of the lights removed the stark sharp shadows engraved by the sun and replaced them with fuzzy edged areas of grey.  There was no black and white any more.  Grey filled the room.

``Maybe he wanted to give his life meaning,'' Zane began on another line of thought rather aggressively.  ``Maybe he wanted to be remembered for something''

Kiele scoffed.  ``For killing loads of people?'' she asked before answering her own question very quickly with  a sarcastic.  ``Great.''  Zane wasn't biting.  Sarcasm didn't tend to affect his demeanour; another lesson from his father.  He got up and walked to the window before leaning out of it.  

``Perhaps it was all he had.''  Said Zane solemnly.  ``Perhaps it was the only thing in his life which actually held any meaning for him.''  His voice had lost all aggression and was now actually quite soothing.  

Kiele looked at her watch before exclaiming out loud, ``Oh shute, I'm late.''  She hurriedly packed her bag with her gear, dropping a few things which Zane dragged himself away from the window to help her with.  ``Thanks.''  She said.

She started for the door, before turning back to give a last comment for analysis.  ``Perhaps he never intended to kill anyone at all.''

Jolie who had been silently listening to the lively exchange of ideas nodded before adding, ``Perhaps Kiele.  Perhaps.''  

Kiele walked out of the room, her short skirt bouncing with her quick sharp steps.  Zane watched her exit the building and walk out of the school yard.  He had never really paid much attention to her before and it was only now that he realised that she was in fact quite pretty.  Her hair was tied back in a simple pony tail and was a beautiful blonde shade.  Zane had heard the rumour that blondes were often quite scatty, but had never once witnessed this from Kiele.  She wore a fairly tight fitting top, but nothing so as to cause alarm from teachers, or elevated heart rates from the males in the class.  The design on her top was simple and political in nature, reading, ``The scientists were wrong, global warming was a big tease.''  The blue denim skirt was faded and was starting to show signs of wear.  It was after all Kiele's favourite.

Jolie also watched Kiele as she exited the school.  She saw a strong confident female member of the class, brimming with potential and intelligence.  'The clothing is a front', she thought, 'this girl could be so successful.'

As the caretaker bots began to scrub the floors clean from all the slung 'poo' of the day, Zane pulled himself away from the window and began to pack his bag.  ``You two have quite a lot in common you know,'' she said.  ``I look forward to reading both of your assignments.''  She stood up and walked to her desk and began arranging things for the next day.  She didn't really have much to organise, but it was getting late now and the desk had begun to dig into her thighs.

``I must admit,'' said Zane, ``I'm quite looking forward to writing it.''  He threw the bag over his shoulder and started for the door.  ``Thanks Jolie.''

``Whatever for?'' Said the young teacher, genuinely astounded at the boys remark.

``Thanks for a cool assignment.''  He looked back and smiled at her, and then so that she didn't get totally the wrong idea he added, ``for a change.''  They both laughed and Zane left the room, whilst Jolie watched him trace almost exactly the same path that Kiele had taken.  They were both keen on route optimisation she observed.  They had both worked out, either subconsciously or consciously, the quickest route from the door leading out of the college to the gates.  It intrigued her and she hoped dearly that their assignments would spark off an interest in the subject she enjoyed so much.  She wondered if any of the class would come up with any new ideas or theories about the man that was Oken Brown, the man she had studied for so long.

It was as if he had been a part of her life now for so long that she couldn't break away.  His face was still glowing on the wall.  She stood up, walked to the wall and ran her finger down the side of his outline, casting her own shadow on the wall as she did.  Projection technology hadn't changed much, and still remained very prevalent in schools, especially those with reduced funding.

The caretaker walking into the room got the wrong idea completely.  ``I wish my wife gave me as much attention as that'' he said.  

She laughed and remained facing the board before saying under her breath, ``What were you like, Mr Brown.  What were you really like?''





