\chapter{08}
\section{Missing}


The tension was rising inside the Zone and the second match between two mediocre opponents was about to begin.  Oken watched them leaving the spectator stands, one at each end, and slowly make their way down the stairs to the platform below.  One of them was holding a staff, much like Yaz had used, the other had two medium length swords.

The blades typically used in the Zone were far more sophisticated than those of thirty years ago.  They had razor sharp edges, and were reinforced with unnaturally strong alloys.  They had been machined down to incredible accuracy and were usually protected by layers of Neo-Tough, a strong engineering alloy designed to keep blades edges sharp.  They were incredibly powerful and could cut almost anything.  Oken had given Bethany a Neo-Tough coating.  It had taken him an age, but it had been worth it.

As Oken looked down at the floor of the Chiller, he decided to sit this one out.  He wanted to conserve his energy for his fight against El Morra.  Oken could see the many bloodstains which had been worn away by years of hustle and bustle of the Chiller.  There were shoe scuffs, chewing gum, and scratches presumably made by people accidentally dropping their weapons on the floor.  He had even seen one or two people leaning on their blades, ruining the tips of their weapons on the cold surface of the floor.  It had sickened him that they showed so little respect for the facilitators that kept them alive in battle.  

Oken looked across at Jay.  She motioned for him to join her out in the spectator stands, but he shook his head and gave a tired expression.  Jay immediately understood and sat back down in her chair.  Oken had instantly thought her reaction incredibly sweet.  He was glad that she hadn't wanted to leave him.  He smiled at her and mouthed the words thank-you.  With the Chiller door open she wouldn't have known if he had actually spoken the words anyway.  She smiled back and winked.  Ruben who was now sitting next to Oken saw this and nudged his elbow to get his attention.  Oken turned to Ruben who gave him a double wink and made his famous kissing face once more.

Oken smiled and shook his head.  Ruben had a habit for blowing things out of proportion.  The two of them hadn't even been out together on a date yet, plus there was the age difference to consider and the fact that she had a lot of work to do whilst still at university.  Oken stopped abruptly.  It sounded like he was considering asking her out.  His brain halted for a while.  Full stop.

Amid the confusion of his mind, images of the fight began to enter.  The bout was lasting a lot longer than had been expected due to a combination of some expert blocking and attacking.  No sooner had one opponent finished defending, than he was back on the attack again.  Oken could see the concentration on the fighters faces.  They were very strong, and fast too.

The twirling rhythm of the fight was totally hypnotic.  Oken had never realised before exactly how beautiful a fight could be.  It was fantastic.  Here were these two dancers, performing what he could only describe as art in front of his very eyes.  The blows, although powerful and devastating, were also graceful, building up into a crescendo of fury.  Music began forming in Oken's head, not the incessant rhythmic thumping that the crowd were dancing to, but a symphony of instruments, carefully coordinated and choreographed to match the fighters moves.  He suddenly became aware of the intricate pattern of the match.

It was at this point that Oken could tell the pair were evenly matched.  The music was so steady, so harmonious, that Oken couldn't see an ending to it.  The ending would be abrupt and unexpected when it happened, and it was.

The staff fighter managed to butt his opponent in the chest, forcing him to spit the air that was contained in his lungs, clean from his body.  He then twirled the staff around to whack the wounded creature in the face, sending his head snapping sideways.  The move was incredible.  The staff fighter managed to grab one of the swords from his opponent, jump in the air and rotate the weapon three hundred and sixty degrees, slicing the now defenceless character across the chest.

There had been no noise audible above the roar of the crowds and the insanity of the music.  There was however an awful lot of blood.  It started as a trickle coming from the wound, and then, as the two halves of the man's body fell apart it gushed forth, covering the floor.  The crowd went wild.  It wasn't often that a fighter was defeated in such a way.  The blood started trickling its way across the floor like tiny little rivers.  It meandered round the various bumps that lay in its path, and built little ponds where the dips occurred.

Oken couldn't help but feel a little sick by the sight that lay before him.  He knew that his upcoming fight would be postponed for a little while now.  It would take the clean up crew some time to remove the mess of the body that lay on the platform below.  The bouncers quickly arrived on the scene and began mopping up the blood and carting the carcass away.  They used large buckets and plastic bags for most of the remaining rubbish.  Meanwhile, a hungry photographer, presumably working for one of the junior journalists, was snapping away, lighting up the Zones platform in flashes of  intricate detail.

There was another person however, who was not impressed by the display of blood and guts.



\thoughtbreak



Leon felt very sick once more.  He had been shocked by the first fight, but this latest slaughter rocked the very centre of his existence.  It was against everything he believed in.  He believed in peace, love and justice.  That was why he had joined the G-TEP in the first place, to uphold that way of life.  Justice had become almost like a religion to him.  

The sight of the clean up operation was too much for him to bear.  He thought he was going to be sick again, but luckily he managed to contain the churning feeling that was erupting deep in his belly.  Leon had already decided that he would take a long holiday after the mission was over, but in the back of his mind he couldn't help from wondering exactly when that would be.  When would this mission be over? When could he go home and relax?  

The questions continued but no matter what the question was, Leon realised he knew none of the answers.  As he stood there, prone, ready to take out the man who had broken G-TEP law, he thought about the family of the fighter who was now being mopped up with a sponge only ten metres from his face.

Leon could smell the blood.  It started off faintly, but soon grew into a stench that he was sure was amplified by the atmosphere.  It sickened him.  Leon checked his weapon over once again, in order to be ready for the task which lay before him.  He couldn't mess it up, that much was certain.  For the past six months he had been waiting for a mission in which to prove to himself that he was all that he could be.

The training missions were normally concerned with ambushing a temporal weapon transport ring, or destroying a cache of munitions.  Nothing they had trained for could possibly prepare them for this.  The landscape was odd and the perpetrators insane.  There hadn't been a G-TEP violation since Leon could remember.  Now Oken had managed to cause a serious stir in the upper ranks of the Emblem.  Their instructions had been simple.  Take him out.  

Already the bouncers were beginning their final sweep of the floor.  The blood was fading already, the vigorous scrubbing performed by the hired muscle leaving only a faint sign that anything significant had ever taken place. 

Leon knew that this mission was important.  Not only would Oken be eliminated, but the Zone would be permanently shut down.  It was a house of brutality and crime and had to be stopped.  Leon allowed himself a slight smile.  Today was a good day for justice.



\thoughtbreak 



As Oken sat in the cool Chiller he couldn't help but feel a sensation that something was wrong.  He couldn't quite put his finger on it, but there was something not quite right.  He wasn't allowed to continue his train of thought though, as El Morra burst into the room.  The Chiller fell totally silent.  Several of the younger fighters got up out of their seats in order for the legend to sit down.  He obliged, sitting in a seat offered to him by a particularly ruthless looking young fighter.  Oken flashed a smile towards El Morra who promptly smiled back.  They knew each other fairly well.  They had met before, but never fought.  

El Morra was wearing a black suit and carried with him two black holdalls which went largely unnoticed.  His hair was pulled right back over his head and gelled down.  It was an ancient hairstyle, but El Morra liked the classics.  His shoes were also black and so shiny that you really could see your face in them.

The Legend was around forty years of age.  He was the oldest fighter in the Zone and knew that his time was coming to retire.  He admired Oken and had seen the tapes of his previous fight.  El Morra was fully aware of the splendour that brewed in his opponent.  It may be his last fight but that didn't concern him in the slightest.  He had the same philosophy as Oken, he enjoyed the atmosphere, the fury.

El Morra's hair was a jet black that reflected the light perfectly in the presence of the gel.  His eyes looked tired and wrinkles had begun to form at the edges.  El Morra was tired of fighting too.  He wanted it to be over but he also wanted to end it as a champion.  He wasn't going to give in to Oken.  He would do his best to kill the master.  El Morra realised that Oken's weapon would give him a definite advantage, but he too had a few tricks up his sleeve.

On the wall above Oken's head, pictures of the previous fight were already beginning to appear.  The final blow was seen in its horrific detail and the contrast of the image had been altered to make the blood look even more real.

Jay was still sitting next to Oken.  She tapped him on the shoulder and gave him a smile.  She knew Oken could beat the ageing El Morra.  After all, Oken had beaten Yaz without acquiring a single injury.  Jay moved closer to Oken's ear and spoke in a soft tone.  ``You'll beat him without a doubt Oken.''  

The confidence that the young woman had in him was very flattering.  He couldn't help thinking about his decision and wondered whether to tell Jay that he would be retiring after this battle.  He decided to save it for later.  It would be a surprise.  He knew now that his feelings for her had far surpassed a simple liking.  He now wondered if it was actually love.  He looked across at her and at once smiled.  He thanked her and saw her expression change.

She was the most beautiful woman that Oken had ever seen.  He still didn't think it was right that she came here.  It just didn't fit her personality.  She was the kindest, sweetest person he had ever met.  He wasn't about to give her up.  He wanted to be with her.

Ruben entered the room and stood among the excitement.  He motioned for everyone to quieten down and then spoke. 

``Today's fight is between the legendary sombrero El Morra and the Time-Bending Oken Brown.''  Ruben had thought the names up by himself.  They had sounded somewhat cooler when he had been repeating them to himself earlier, but now they seemed to sound rather childish and silly.  The eyes of all the Chillers occupants fell on Ruben with a renewed silence.  Ruben smiled.  

He gestured for Oken, his long time buddy, to get up and say something which would rescue him, but Oken shook his head and said, ``You made the names up Ruben, now you live with the consequences.''  Everyone laughed and even Ruben through the clenched angry teeth, chuckled a little.  It was true, they were truly terrible names.

The chiller returned to its normal hustle and bustle and Oken decided it was time for him to start setting up.  He reached down for his black holdall which was always at his feet, ready to answer his call, and froze.  It wasn't there.



\thoughtbreak



Leon had just been informed that the target would be entering the arena shortly.  Revised instructions had been made but the core was the same, he was only to commence firing if Oken used a temporal weapon.  The tension was mounting in Leon's mind.  The instructions cut through him like Bethany would have.  In a little while, he may have to kill someone in order to preserve the Emblem's way if life.  It was a simple statement, but one which had dire consequences if Leon messed it up.  

He had checked his weapon no less than twenty-six times since he had arrived on the scene, and now for the twenty-seventh, he checked it again, knowing that it had to be working perfectly.  The rifle shone in the dim light of the tunnel.  Leon had been sitting here for well over two hours and his ill feelings had not gotten any better.  He decided that as soon as he got home, he would rest and not get up the following morning.

The water which had started to leak into his shoes was incredibly cold and squelched when Leon pressed down.  He let out a small groan and decided that tomorrow he would also buy a new pair of shoes.  The smell was still there, and Leon knew it was getting closer and closer to the time.  The tunnel wrecked of death and blood, death, blood and vomit.  On the other side of the tunnel, Ric smelt the scent of death too, the difference being that Ric had smelt it before and knew exactly how to deal with it.  

Leon took the safety catch off of his rifle and prepared to fire.  He felt like a coiled cobra, waiting to spring out and shoot his deadly venom into his victim's bloodstream.  Leon suddenly felt a strong sense of power.  It made him feel good.  He aimed once again through the gunning hole and made sure that both he and his gun were steady, the odour of hot sweating bodies darting in and out of Leon's lungs as he breathed heavily.



\thoughtbreak



Oken was instantly gripped with unmistakable fear.  His beloved Bethany was missing.  All too quickly the thoughts came flooding back to him.  He had packed it early that afternoon, even remembering to pack the film which Jay had wanted to borrow.  He had stowed it away in his hidden safe zone.  All of a sudden the fear turned to a shot of realisation.  He hadn't picked it up on the way out.  The temporal shields were in place, arranged earlier by Oken himself, but the main requirement, the star of the show, was waiting patiently at home.

His thoughts had been of Jay and not of how he would win the fight against his opponent.  He had completely forgotten the tool which he would require in order to win.  His heart sank.  It wasn't until he realised the full effect of what he had done that he started to feel very sick.  He would lose for sure.  El Morra was a fantastic fighter and he would have needed the advantage that Bethany provided to even stay even, let alone win.

He looked over at Jay who was smiling sweetly at him.  It was too late, he thought.  There was no way he could back out of a fight, it just wasn't allowed.  He thought about getting Ruben to drive back to the apartment and pick the bag up for him, Ruben knew where the hideout was, but he knew that there just wasn't enough time.  

What should he do?  He couldn't fight without a weapon.  He got up.  The fear had gripped him so tightly that he stumbled when rising.  Ruben quickly supported him and shot him a grin.  In the midst of his fear he hadn't noticed El Morra getting to his feet and preparing to head down to the platform below.  Oken took hold of Ruben's arm and pulled him to one side.  Jay got up and attempted to walk over as well but Oken held up his hand and she knew that it was an important private conversation.  She respected his gesture and stayed back.

``Ruben, I've been real stupid.  I've forgotten the blade,'' said Oken.  His voice was as dry as ice and Oken knew that Ruben wasn't going to believe him the first time round.  He looked up at his long time friend who had a serious look on his face.  The serious look turned into a big grin.

``You can't fool me with that one man,'' came Ruben's reply.  ``I've known you for too long.''  It was true that Oken had known Ruben a long time but through their times together Ruben had never known Oken to look so serious and so sad.  His expression of happiness turned to that of concern for his amigo.  When he next spoke it was in a much more concerned tone.

``Oken, you're not kidding are you?'' he asked of the grey haired figure that stood before him.  Oken shook his head and Ruben felt the same fear that had gripped Oken only moments before.  It felt like it was crushing his larynx and made it almost impossible to talk.  Despite this, Ruben was still able to add a glimmer of hope to Oken's now almost futile battle.  ``Oken man, you just tell me anything you need, and I'll get it for you.''

Oken knew the words that Ruben spoke were the honest truth.  Ruben would have done anything to help out his old friend, but Oken didn't know what he could ask for that would actually have any real effect.  He knew he had to have a weapon if he were to stand any chance of holding his own in the fight.  

Ruben already had an idea of what his request may be and without waiting for Oken to say a word, he ran to one of the metal cupboards in the Zone where confiscated weapons were stored.  He punched in the code to undo the electronic lock.  The tears were welling up inside him, not yet present in his eyes, still somewhere deep down in his throat.  This would certainly be the end for Oken.  His brother.

Oken hadn't been a good friend to Ruben, he had been the best.  They had been like brothers.  Ruben picked out a sword which bore some resemblance to Bethany and removed it.  He saw how the shine of the scabbard reflected the hungry crowd as they waited, thirsting for more blood.  Ruben's heart sank.  It seemed that they were about to get their wish.

He walked back over to Oken and handed him the weapon.  Oken gave him an appreciative smile.  They were men of few words but both knew the other well enough to read their expressions precisely.  Ruben gave a half smile back at the man who stood before him.  He was looking older now and Ruben had not realised just how old until now.  The worry of his impending doom weighed heavy on his moderate frame.  

El Morra walked past them and Oken heard him shout something about getting the show on the road.  He knew it was time.  El Morra was making his way down the stairs to the platform.  Jay came running out of the Chiller door and threw her arms around Oken, who was ultimately shocked.  He had never experienced this kind of physical attention before.  It felt so good.  He'd been admired for years now, but it was a totally different feeling to this.  This felt like love.  He could feel his stomach begin to knot and for a second he forgot all about the fight which he was about to enter.  This moment was all about him and Jay.

He hugged her back.  He loved her, it was true.  He had been hit by love at first sight.  Never believing it was possible, or indeed probable, it had taken him completely by surprise, but he loved her.  If, by some sheer quirk of fate, he made it out alive, he would tell her so.  He could feel her warmth seeping into his cold body.  He didn't want to let her go.  

He could feel her breathing heavily and knew that she was crying.  He wanted her to stop.  Dear God, please let her stop.  She had no idea about his chances of getting out alive, she was just worried for the man she had grown to care so much for in such a short period of time.  He didn't want to fight any more but knew that if he refused he probably wouldn't make it out of the Zone alive anyway.

He stroked her hair and whispered words of confidence into her ear.  ``It'll be all right Jay, it'll all be OK.''  He didn't believe the words himself, so why was he pretending now?  He loved her and though it ripped his heart to shreds, he just couldn't let her know the truth.  He had to try to comfort her.  Through her whimpering and the heavy dance music her words hit him like a blow to the head.

``I love you,'' she said.  He wanted to return the words but wondered whether it was fair.  If he told her he loved her and then he died in the ring would she end up hating him, never truly believing him?  Knowing Jay  it wouldn't be the case.  On the other hand maybe it was what she needed to hear.  Oken spoke slowly and purposefully. 

``I'll be back soon,'' he said.  The words left his mouth and upon receipt at Jay's ear, she lifted her head to show Oken her beautiful face.  Her eyes were red and her make-up had run slightly, but Oken could still see the inner beauty in Jay shining through.  Their eyes met and Oken noticed the sad soul which had so wished for those loving words to be bestowed upon her.

She hugged him even tighter and Oken smiled and hugged her tighter too.  Through the crowds of jumping insanity, there stood two people deeply in love, but afraid to show it.  Oken released his grip on the petite woman.  She relinquished her hold over him too and they stood there for a minute just gazing into each others eyes.  Ruben entered their scene and tugged on his friend's sleeve.

``Time to go my man,'' he said, his eyes already tearing at the sight.  His oldest friend had found love at last, something he could retire with, but in all probability he wouldn't even be breathing past the next five minutes.



\thoughtbreak



Leon had not seen what had transpired up in the spectator stands.  In truth, even if he had seen it, it would have been doubtful if it would have moved him.  Leon was now hell bent on getting the man.  He wanted Oken to die, so that the Emblem's way of life would continue, honouring the traditions of peace and tranquillity.  Once his mind was set, Leon's determination always won through.

He watched as Oken made his way down the stairs and onto the platform below.  The dark figure moved with a delicate finesse which Leon found incredibly ironic.  It took him little time to aim up on the figure as he stood opposite him about twenty metres in distance.  The aim of his assault rifle hungrily ravaging the sight of Oken the temporal violator.  

Leon began to feel hot once more, his hands started shaking and the radio crackle startled him so much that he nearly fired.  ``Alpha 2 : That is your target, repeat that is your target.''  He slowly picked up the radio, not once looking away from the perpetrator that stood before him.

``Rodger GRT,'' he replied stealthily as the two men began performing the ritualistic swordplay.  Leon could only see Oken, but had he been able to see El Morra too, it would have been obvious who was the better trained.  El Morra.

Oken's blade whisked through the air and flew past his side at unimaginable speed.  A part of Leon actually now wanted to watch the show.  He enjoyed action movies, with explosions and cocky clichés.  He watched as the masterful Oken swung the old battered sword in front of his eyes.  The assault rifle felt almost alive in his hands and he wanted to let his anger out now and kill this poor excuse for a civilised human.  Leon had no idea of Oken's desire to retire that evening and return to the society that he believed had deserted him when he had gone off to war.  In truth, it was his parents that had betrayed him.



