\chapter{32}
\section{}
Sleeping Beauty  

They rounded a corner, arriving in a secluded car park.  Jessie hadn't been heading there for any particular reason, he just wanted somewhere quiet to interrogate Ruben.  The poor boy on the back seat was trembling with fear.  He'd managed to delay the inevitable for a good hour or so.

``So Ruben,'' started his captor, ``we're not going to have any more problems now are we?''  Ruben shook his pounding head.  He couldn't do any more.  He had been broken before, but today was more than he could bear.  Jessie had taken everything from him.  He wasn't going to risk Kiele's life again.

Jessie switched the engine off and turned round in his seat.  He pulled off the gag which had been preventing Ruben from breathing properly, let alone talking.  Now the two enemies sat there.  Of course Jessie had his handgun ready and waiting as he leaned against the two front seats to face the dark skinned giant in the back, the fingers of his free hand gripping the leather and making small indentations.  He was breathing more calmly now, a by product of the Ditraxicaemol.  It was time to find out just what this cretin knew.

``So where is it?'' asked Jessie.  There was no beating around the bush, no small talk, no insults to which Ruben had become accustomed to, just a simple question.  In all honesty, Jessie was tired.  He wanted to get this over with and get on with the next phase of his plan.

``I'll take you there,'' croaked Ruben, ``It's not far, 1422 Chesterly Drive.''

Jessie nodded.  Somehow he just knew that Ruben was telling the truth this time.  He hadn't been lying about the distance, Chesterly Drive was only about five to ten minutes away.  He climbed back into the drivers seat and began to drive off out of the car park.

The car's tyres screeched on the tarmac surface, something that no advance in technology seemed to have been able to quell.  Several people had been at the other end of the large asphalt area and had looked over on hearing the noise.  It didn't matter now though.  Jessie was on the way to completing the most important phase of his mission.  Once he had the device he could relax.  It would be easy after that, Zane would take care of the rest.  

He flicked on the indicator and the orange lights flashed.  He exited the car park crossing a few lanes of on coming traffic and carefully made his way down the street towards his target.  The street lamps were beginning to come on now and though darkness was a fair few hours away, it seemed as if the lights had all decided to come on slightly earlier to prepare for the impending doom of night time. 

Ruben lay there silently.  The gag hadn't been replaced, but he was finding it difficult to breathe anyway.  The street lights had become almost a blur now as the little car zipped along the road that would eventually lead to Bethany.  Each light illuminated the innards of the car with its passing touch, almost as if it was trying to grab hold of what lay inside.

Jessie's mind was calm again.  He could concentrate once more.  Phase one was almost complete.  Ric would be pleased, and Jessie?  He would be able to achieve what they had dreamt of for so long.  Neither one of them was particularly impressed with the way the governments of the Emblem went about their business.  One event specifically stuck out in Ric's mind as a turning point for the integrity of the system.  It was this turning point that had driven him to collaborate with Jessie.

The creation of the Emblem hadn't gone smoothly, but it was one particular set of talks that had been hit by more problems than any other.  Set to be the greatest collaboration of governing minds since records began, every major country in the world had sent representatives to the event.  Unfortunately, the terrorists had decided that the event should take place without several key players, and they had planned numerous assassinations and disrupted the talks.

Against their entire ethos, the organisers of the events took it upon themselves to use time travel to rectify the 'problems'.  The assassinations had been prevented and the talks had gone ahead relatively peacefully.  The Emblem had been created and life was good, relatively speaking.

On finding out about the event, Ric had never quite forgiven the Emblem for this pure act of hypocrisy, using a system which they themselves outlawed to assure their own existence seemed undeniably wrong to him.  Of course only a few people in the world knew what actually transpired there.  Ric had been told about it when he had visited the global G-TEP commander for an awards ceremony, over eight years ago.  Since that point, he had vowed to bring down the Emblem, to cause Emblem Divide.

It hadn't been hard to get Jessie on board, Ric had known all along that the little weasel would be fairly easy to manipulate.  A few suggestions here, a few criticisms there and even Jessie himself had come up with the idea of preventing the Emblem from ever being created.  Of course doing so could undoubtedly alter the time line so that Bethany and Oken's technology would never be created.  This suited Jessie and Ric also.  They were fully prepared to lose the memories.  They had to protect the integrity of the world.  In their eyes, they would be martyrs in an otherwise unholy land.  Purging the government of corruption.

Emblem Divide.  The two words seemed to fit together so nicely in his mind.  It was a name Ric had invented for their overriding mission and he too had been proud at how powerful it had seemed.  An Emblem, a symbolic reference.  Divide, to split apart.  Their plan was going to change the world forever.

Jessie and Ric hadn't seen the time-line that had resulted from the failed talks.  It was known only to a few people in the world and not even the global commander was privy to that type of information.  Knowing how ones choices affect ones future is a dangerous thing indeed.  In truth, after the assassinations, various countries had decided to declare war on each other once more, blaming them for the murders which had taken place.  One fateful afternoon, one hundred and fourteen million people had been wiped out by several simultaneous nuclear attacks from warring states.  Biological weapons were also deployed en masse, killing countless millions over the coming weeks and months, or so records told.

They arrived at 1422 Chesterly Drive.  It was a dilapidated, run down neighbourhood on the outskirts of the commercial district.  The destruction often happened to areas close to the commercial hubs.  People were too drawn to the city, too tempted to spend money, and so their quality of life suffered as a result.  The house they were looking for actually looked fairly well kept.  It hadn't been lived in for years, but its exterior at least, gave a sense of care and attention.

There were curtains in the windows, a well kept garden at the front and a little wooden fence, not entirely unlike the one surrounding Kaitlin's place.  Each window had three panes of glass, splitting in vertical lines from top to bottom, a common configuration for a house of this age.  Some of the neighbouring houses had replaced them with single panes, but this one remained entirely untouched.

Bethany had been moved from her previous secret location to here by an unnamed party.  Ruben had never known who the unnamed party was, but he had always had his suspicions.  Leon.  He had visited here only once before to confirm that he knew where to find the legacy of his fallen comrade.  After receiving a cryptic tip-off.  

Leon had managed to hide the device, stealing it from under the G-TEPs noses.  There had been talk of the organisation acquiring time travelling devices and he was dead against it.  After accompanying Ruben to the hospital, the young officer had made the extremely gutsy decision to find Bethany.  Shortly before his suicide, he had contacted Ruben anonymously and gave him details of how to find the device and a time and date it would be safe to check its location.  Details which no one else had understood, surveillance or not.  Ruben was the only other living soul that Leon trusted to care for such a device.

Jessie pulled up alongside the road.  For an active district, there were surprisingly few cars lining the roads.  He switched off the engine and looked back at Jessie in the mirror.  

``Can I go in and get it myself?'' he asked.  To an outsider it may have appeared odd for Jessie to be asking Ruben's permission to go and retrieve the blade, but Jessie was really asking about security measures, codes and traps.  He didn't want to be caught out again.

``I've never been inside,'' said a truthful Ruben.  ``I guess I should come too.''

Jessie opened the car door and stood outside for a while, surveying the area.  Just how was he going to play this?  He didn't want to risk another visit from the police, but there were a fair number of people around.  If they saw him, in plain clothes, leading a bound and beaten man into a house, someone may snap and call the authorities.  He couldn't have that.  He would have to completely untie Ruben, and trust him.

He had been leaning on the car door and the slightly degrading rubber seal had left a black mark on his arm.  He slammed the door shut and rubbed off what he could from his thick insensitive skin.  He opened the door to the rear of the vehicle and watched in glee as Ruben shrank back in fear.  He was genuinely frightened thought Jessie,  how pathetic.

``I'm going to untie you now,'' he said to Ruben, ``but I swear if you try another trick, you and everyone you've ever known will be dead.''  His voice was cold, purposeful and menacing.  Ruben had never heard his captor sound quite so calm and collected. 

``I won't try anything,'' said Ruben, ``You have my word.''  Jessie appreciated his honesty.  Unlike him, Ruben had meant what he said.  His 'word' was actually worth something.  Jessie would have lied without a second thought, but Ruben wasn't that type of person.  Throughout his entire interrogation he had never lied, he just hadn't fully told the truth.

Jessie removed the bindings from Ruben's legs and hands and the man once again felt remarkably free.  The gun had been pointed in his general direction, just as an indication that it was still there, but was now resting peacefully in Jessie's holster.  Ruben climbed out of the car and stood there for a second or two, as Jessie had done.

They walked up to the door and Ruben pressed his thumb to the plate.  Though dilapidated, each house had something about it which was oddly out of place.  Some had expensive curtains showing through, others had expensive lawn decorations, others expensive cars.  This house however, 1422 Chesterly Drive, had an electronic thumb plate.

They heard the click of the lock as the portal to the inside became grimly available.  Jessie, eager to reassert his dominance, stepped in first, opening the door carefully, so as to make minimal noise.  It was unnecessary, there was really no one there.  As they entered, Jessie expected the weapon to be on show somewhere, primed in all its glory and splendour, but it was no where to be seen.

Ruben walked ten numbered paces and bent down.  The hallway was covered with a laminate flooring, which some how made the place feel even colder.  It was obvious someone had been keeping this house alive regularly.  Plants were tended to, the floor was relatively clean.  Just who had invested so much time into the upkeep of an empty house?

The hallway led off to the kitchen in front of them and to a lounge to Ruben's right hand side.  Beneath Ruben lay the root of all his problems.  Bethany.  He didn't resent her existence, or Oken for creating her.  Having seen Oken fight in tandem with that vicious she devil had been a true marvel, and Ruben would have given anything to see it again.  As he hung there in a stooped position, he said a silent prayer that Jessie would somehow change his mind, that everything would be OK.  

Jessie became impatient.  ``So where is it Ruben?'' he snapped, ``I don't exactly see it anywhere.''

Ruben sighed.  ``It's under the floor.''

With that Ruben pressed his hand to the floor and part of it lit up.  Unbeknownst to Jessie, the floor they were standing on was covering a small underground cave.  The place where Ruben had placed his super-sized mitts, had been a scanner, and now his hand-print was being read into the miniature computer which was sat underneath solely for the purpose of guarding Oken's treasure.

A little light blinked green and a portion of the floor began to move.  Jessie had been standing on part of it and now he stepped back in amazement.  This looked like it was truly going to be it.  Ric would be pleased, they were one step closer to Emblem Divide.  

As the floor panel withdrew, the dark eerie shape of Oken's black holdall became sullenly apparent.  It wasn't hidden in any wrappings, or protected by any chains, it just sat there, begging for someone to take it away and tinker with it.  Its dark colour unchanged in all the years it had lain there in its coffin.

Jessie pulled out a small device and scanned the area in front of him.  He had to be sure that removing the device wasn't going to leave any traces that could be picked up by the G-TEP forces on one of their routine scouts around the city.  It seemed clean, a lower tone indicating that the presence of temporal residue was below normal parameters.  The tomb had been outfitted with temporal shielding to prevent the residue from seeping out into the rest of the house, but over the years it had naturally dissipated anyway, as most things do.

Jessie bent down and picked up the black holdall, placing it on the floor next to him.  He asked Ruben to shut the door, which he himself had left open in his eagerness to grab his crown jewels.  Ruben obliged, half wishing he could just run out, half wishing he could kill Jessie.  He prayed for forgiveness.

The weasel, looking left and right, like someone considering performing a very secretive act, gently caressed the zip of the holdall until he found the zip tag.  Carefully and with the greatest intentions, he pulled the tag towards him, parting the material and opening the gateway to a new world, a new world without the Emblem.



\thoughtbreak



Bethany lay there sleeping peacefully.  It was almost ironic that a weapon capable of so much destruction and despair could be so beautiful.  She was still so sleek, diffusing the light as it bounced off her brushed surface.  The grip lay untouched, and though it had been used by Oken before, anyone viewing this blade would have believed she had never been touched by anyone.  Jessie moved his head to adjust his angle of viewing slightly, the edge of the blade seemed to almost cut through the air as it sat there majestically, the final point of the blade imperceivable to the naked eye.

He had wondered why she wasn't in her scabbard, but after seeing how beautiful, how delightful she looked, it was clear to him.  Whoever had laid her naked body here had done so as a sign of respect.  They obviously hadn't ever expected to see her again.  Just as a body at a funeral is found in a pristine and hypothetical state, the burier of Bethany had taken great care to leave this beauty looking at her best, and that was most definitely not in the scabbard.  It lay underneath her, crushed by her presence, as if being purposefully hidden.

Jessie looked up at Ruben.  ``She's beautiful, isn't she.''  

He couldn't lie, and though he never wanted to be seen to agree with Jessie, he knew what he felt in his heart.  It was the most beautiful blade ever created.  Jessie bent down, and with both hands slid underneath her delicate body, lifted the sleeping beauty from her slumber.  She stirred gently as if believing she was being awoken by a prince.  

Suddenly the blue crystal burst into life, showering the blade with light.  Oken had never expected to die, he hadn't built in any kind of special mechanisms to prevent others from using her.  It had been a mistake, but ultimately one which he would never know.  Bethany had responded to someone touching her.  Over the years, her power cells had remained one hundred percent intact, ready to answer the call of her next master.  Jessie was that master, he had complete control of her.  She would grant him unimaginable power, the power to change history.

Jessie stroked the blade's groove along it's non-cutting edge.  ``This is called the Hi or the blood groove'' he said.  It was obvious that Jessie had a liking for Japanese swords.  He pointed to the guard, now holding the blade in one hand.  ``Here is the tsuba.''  He turned the sword over, moving the tip in a long arch, watching it as it went.  ``But my favourite part of all, is the Kissaki.''  He was referring to the tip of the blade usually reserved for stabbing opponents.  

They were protected by the shield generators, Jessie could sense that and he decided to test the blade out.  Just for a second.  Ruben was standing opposite him now, the hole in the floor between them.  Jessie squeezed the grip of the blade, instinctively knowing how Oken had designed it to function.  Time slowed down and for the first time, Jessie heard the unmistakable whooshing noise that Oken had heard all those years ago.  

Jessie admitted to himself that he was a little afraid.  There was something of unimaginable power in his hands, something that could literally rewrite the pages of history.  He released the grip and time spun back up to normal.  He breathed out heavily, as if he had been holding his breath for minutes.  Ruben blinked.  Jessie was calmer than he had ever seen him before.  A part of him wondered if all Jessie had ever wanted was to hold Bethany, to caress her sweet naked body in the palms of his hands, to know that the power to change one and all lay at his finger tips.  

Jessie replaced the blade into the black holdall and zipped it back up.  It had been a life changing experience for him.  Never before had he felt so invulnerable, so special in his entire life.  In fact, he had all but forgiven Oken for the events that had started him on this journey all those years ago.  He thanked Oken for creating such a beautifully menacing creature as Bethany.  The show must go on however, there would be fireworks and sacrifice, blood and wine, heaven and hell, but the show would go on. 

Jessie instructed Ruben to remove the shield generators from under the floor, he would probably need them later.  Ruben obliged, trembling in fear at the mistake he had just been forced to make.  Jessie was one powerful man now.  He could potentially change the world however he saw fit.  Ruben was, of course, forgetting the difficulty in predicting the results of ones actions.  Removing someone from time, didn't always go according to plan.  If Jessie and Ric executed their plan as expected, they wouldn't be protected by wearing temporal shields, for a temporal shield cannot save itself.  If they changed the world in such a way that Oken never created his weapon, the shield generators would never have been created.

The two men walked out together and Ruben carried the four small black devices as Jessie opened the boot.  They were smaller than the others, packed tightly into the black holdall, intended to cover only a small spherical area.  Each one had a power light which had been extinguished when Ruben had pulled the power.

The gear was placed in the boot and Ruben was re-bound and re-gagged.  Jessie had decided to take Ruben back home and place him under 24 hour supervision with a G-TEP force.  The bungle of creating a mission ID earlier had actually served a purpose in the end, as it meant he could quite easily call HQ and obtain a unit to monitor the poor baby.

Jessie relaxed into the driving seat as he pulled away.  His task was complete, Ric could rest easy.  He had done his part and now he was awaiting the reward, the fruits of his labour.  Jessie was awaiting Emblem Divide.



