\chapter{38}
\section{When's The Wedding?}


The class was a veritable chatter of excitement as the two figures of Kiele and Zane were seen walking past the school gates together, holding hands.  Jolie had obviously been informed and the class were now offering up their suggestions of quips the young teacher could say as they entered the class room ten minutes late.

``Say, 'Did you two find a room OK?' Jolie,'' asked Janus.  

``No no, say 'I didn't know it was possible to kiss for that long,''' chirped Mikael, though they hadn't kissed.

Jolie interrupted before the next member of the class could offer their crude and indecent proposal.  ``How about we just give them some space, all right?''

As the couple continued across the field, on a completely unoptimised path, noticed Jolie, they suddenly broke away from each other and Zane dropped behind as Kiele went on ahead.  It was clear they didn't want the rest of the class knowing about the level of their relationship just yet.

``See,'' said Jolie, ``They're shy about it.  Please give them some space, they'll tell you when they're ready.''  She sat down at her desk and took out a pile of datadisks from her bag.  ``Now,'' she said, ``I have written down some notes and copied them onto disk for each of you, regarding your assignments.  I know how some of you moan about the speed of the net lately, so I thought I'd remove at least one obstacle from your path.''  She began walking up and down the rows of chairs and desks, continuing, ``Remember you have another few weeks before it's due in, so I'm expecting something really special.  Oh and class, don't forget the schools memorial festival in a few weeks time.''

The festival was going to be a time of great celebration for the school.  It had been standing its ground for over fifty years and though the war had torn apart many villages, towns and cities, somehow the school had stayed standing.  The members of the school board had thought it important to commemorate the fifty year anniversary with something special, so they had paid out to decorate both students and school in décor from twenty five years ago.  Most of the students were excited.  Some hated the idea.

Kiele had disappeared from view and was now making her way towards the classroom door, totally unaware of the knowledge that the class possessed.  Zane, still in view was trudging along, slowing again to give Kiele enough of a head start that people wouldn't suspect they had arrived as a pair in any respect.

There came a knock on the door and Kiele entered.  The class remained totally silent.  When Jolie's back had been turned, the class had shuffled round slightly so that the only two seats left were at the front of the class, right next to each other.  Kiele apologised to Jolie silently and took up her place in one of the spare seats.  She found it odd that the only two spare seats had been right next to each other, but decided to put it down to coincidence.

Jolie continued discussing the importance of the assignment as another knock came on the door.  It was of course Zane.  He entered the class room and also found it rather strange that the only spare desk was next to Kiele.  He sat down and unfortunately decided to pass comment to the young woman sat next to him.  His Kiele.

``Fancy seeing you here,'' he whispered.  

The words had hardly left his lips when the entire class erupted in a roar of 'ooooooooOOO', immediately chorused by banging on desks and wolf whistling.  The two late comers hung their heads in sheer embarrassment.  They had planned it down to the very last detail.  What they hadn't expected was for Mikael to have spotted them holding hands as they walked in the front gates to the college.  It was a mistake, but neither of them had been to blame.

Jolie started yelling for the class to be quiet.  She wasn't particularly good at it.  She was tired and her voice had never lent itself to screaming at people anyway.  She was far too gentle a person for that.  Eventually Mikael took it upon himself to stand up and holler at the rest of the class to be quiet.  Once the noise had reduced to an acceptable level, the questions began.  

``Have you kissed him yet?'' shouted a new voice to the crowds, Leanne.  Kiele began to glow red.  She was trying so hard to ignore everyone, but they just kept on.

``When's the wedding?'' shouted another.  Ordinarily she would probably have been able to cope with such class participation, but today she was feeling particularly fragile.  Zane shouted back for the 'idiot to shut up,' but the jeering persisted and once again grew into a crescendo of a rabble which Jolie couldn't contain.  One young lad at the front got up and started pretending to kiss an invisible girl with his back to the class.  This was met with a shower of paper balls and yet more jeering.  

Zane looked across at Kiele.  He was sure he could see a tear rolling its way down her cheek.  He stood up, throwing the chair he was sitting on behind him and held out his hand to Kiele.  She looked up at him and all too quickly Zane could see that the little make up she had applied that day had begun to run.  There wasn't just one tear, there were several.  

Jolie, still unable to contain the class was trying to now quieten down individual trouble makers, but she was meeting high resistance and very little success.  Kiele grabbed hold of Zane's hand and he pulled her arm towards him.  She had to stand to keep from toppling over and Zane instantly regretted yanking her arm so hard.  She sprung to her feet and he opened the door, dragging her outside.  

The class went wild once more and though the door was now firmly shut, the banging and screaming could still be heard from far down the corridor.  The window seemed to be pulsating with the vibrations of the air from inside the cage.  Zane had regretted leaving Jolie in there to deal with the mess, but he had bigger, more important things to worry about; Kiele.  

She flung her arms around his neck.  Being slightly shorter than he was, she had to stand on tip toes to reach properly.  Her arms met at just below the elbow and she slumped forward so her body was pressed up against his.  She rested her head on his chest and the tears began to flow.  She hadn't wanted any of this.  She hadn't wanted the stupid class to know.  She hated them all.  She hated them all.

All except Zane.  It had been the nicest thing anyone had ever done for her.  Though she had had friends in the class, how many of them would stick their neck out for her against every one else.  Only one name sprang to her mind and she currently had her arms wrapped so tightly around the bearer of that name, Zane Krecker.  She just couldn't believe that one person would be willing to risk his entire reputation on her.  She was a nobody, just what did he see in her anyway?

Zane couldn't believe what he had just done either.  He had vowed he wouldn't bow to the pressures of the classroom.  He had even told Kiele as much, stating that when they were at school, they should appear as if they were two separate entities, at least for now.  

After their meeting in Haito's and that glorious meal that they had shared, they had both decided that they wanted to keep their liaison between themselves.  On the one hand it made it more exciting.  Knowing and sharing something so special that no one else knew about.  On the other hand it was entirely practical.  Kiele still had no idea what Mark's reaction would be to them dating.  He hadn't spoken to her much of late, at least not since the basement incident, but she still saw that glint in his eye every now and then and she didn't like it.  It was evil, it was horrific.  She wouldn't let him know about them.  She would protect her Zane.

Now the illusion was over.  It was unlikely that Mark would find out through any of her school friends, but if they had seen through the disguise, what chance did she have against her father?  She hadn't realised yet that it hadn't been a flaw of their design, but of their implementation.  

Zane put his arms around the young girl, helplessly inebriated by the scent of her hair.  He couldn't help but hold her close.  The tears were still flowing fast and he could feel her breathing hard against his chest.  He hated what the class had done to her.  Her body rocked gently as her irregular breathing continued and Zane brought one of his hands up to cradle her head.

The door opened and Jolie walked out of the classroom.  She looked left down the corridor and then right, spotting the couple locked in their embrace.

``Kiele, I'm so sorry,'' she started.  ``Please, come back inside.''  She ignored Jolie.  It wasn't anything personal, but she couldn't bring herself to talk right now.  Her eyes were still flooded and her breathing hadn't returned to normal yet.  Zane held Kiele close, gently stroking her hair.  

``We'll come back in shortly,'' Zane dictated to Jolie.  The teacher was impressed at how he protected the young girl, not even worrying about standing up to authoritative figures.  He wasn't asking for Jolie's permission to stay outside a little longer, he was telling her.  Security had been called to the classroom and several burly men were now running down the corridor.  The teacher flagged them down and explained the situation.  Their shiny badges sparkled in the light as it bounced off the metal.  

The corridor was well lit, and so it should have been.  One side of it contained doors to around ten classrooms, the other side was comprised of huge window panels.  At each end, the corridor turned a corner and ended with a wall of glass and a set of double doors.  Previously, there were gates which closed across during the night, but during the day the corridor had been completely open to both students and the elements.  

It had been an incredibly poor design and several of the staff had threatened to leave if then ends of the corridors weren't bricked up and doors placed instead.  Finally the management had relented and the glass walls had been placed at either end of the corridor.  It served well during the winter, but the summer made the whole area act like a giant greenhouse.  The doors were usually left open, but it was getting to an odd time of year where the temperature fluctuated often and today they were closed.

Jolie returned from talking to the security guards and rejoined Kiele and Zane.  She watched as the young girl lay against her protector and as he in turn lay against the wall.

``Take as long as you need Zane,'' said Jolie.  She wasn't being overly soft on Kiele.  She guessed that her father was a difficult man to live with and having Zane living with them now must have put extra strain on her father's temperament.  Jolie went to walk past Zane but he put his hand out and caught her arm.

``I'm sorry Jolie,'' he said.  ``I meant no disrespect by telling you we would be staying outside for a while.''

The teacher smiled, she really liked Zane.  He was a perfect match for Kiele.  Since the accident, Jolie had often pictured the two of them together, but she had never imagined that they would actually make a go of it.  Both of them were as shy as each other.  Yet here they were, totally inseparable.  Jolie couldn't imagine what Kiele's father thought about it.  Perhaps he didn't know.

``It's fine Zane,'' Jolie replied.  ``You look after Kiele.''

Kiele lifted her head from Zane's chest, turned to face Jolie and placed it back down again, snuggling up to the young man again.  His hands were now further down by his sides, with her hands resting one each side of her head.

``Thanks Jolie,'' she said.

The teacher smiled and nodded before going back into the classroom.  



\thoughtbreak



``So is the device ready?''  The voice was unmistakable as Jessie picked up the phone.  He hated Ric checking up on him, but somehow he knew it was all part of the process.  There was a deadline, Jessie hadn't yet rung to give him a status report that week and so logically, Ric would want to check up on his progress.

``No, it's not ready yet,'' came Jessie's solemn reply.  He knew his partner would be angry, but at this point in time, he had nothing more to give him.  He paced around the kitchen in circles, waiting for the next question.

``What's the hold up?'' 

``He's having some power stabilisation issues and we don't have a whole lot of resources to play with,'' explained Jessie.  It was all true.  Zane was fairly sure he had most of his theory correct, it was literally now a matter of working out how to stabilise the output from Oken's power cells.  It was a problem for Zane, his work had mostly been in the theoretical side, not the physical side.  Though he was no stranger to experimentation, he rarely had to deal with many implementation issues.

``Will you be ready in time?'' asked Ric coldly, as if not believing the little weasel could even tie his own shoe laces.

``We'll be ready,'' came his reply.  ``I still have plenty of time.''

Now Ric's mood turned.  He was getting annoyed with the little boy on the other end of the phone.  He didn't seem to realise that if they weren't the ones to make the time shift on the deadline, someone else was.  Someone who could be hoping to affect their future plans.  

``Damn it Jessie,'' he shouted, ``we do not have all the time in the world.''  His voice hardened once more.  ``You have one more week to complete this, that includes time seek testing and a full blown live subject test.  Do not mess this up.''

The other side of the phone line went dead and Jessie kicked out at the door in anger.  His foot, although not equipped with enough force to penetrate the thin wood, still managed to make a dent that would be hard to miss when the kids got home.  He had to get Zane to concentrate harder.  Kiele seemed to be a limiting issue.  Perhaps he would have to get a little more aggressive.



\thoughtbreak



The two of them sat on the bench in the cool breeze.  The weather had taken another turn.  Snuggled up against one another, they could hardly feel the cool air as it whipped around the fields.  Zane had placed his jacket around them both and was sitting with his arm around her waist.  She had tucked both hands between her thighs and was hunched over.  They had been sat there for the best part of ten minutes when Kiele spoke.

``Thanks for protecting me Zane,'' she said.  He lifted the arm that was round her waist and ruffled her hair gently.  She shook away from him.  She liked the way he treated her, with respect, but also so lovingly.  She felt safe around him, as if he could prevent any harm from coming to her.  The only thing she had to worry about now was her father.  

``You know we really should go face the music,'' said Zane reluctantly.  She snuggled up to him closer.  She really didn't want to go.  It was so warm and safe out there against the elements, Zane and her.

``Can't we stay here a few minutes longer?'' she asked him.

He nodded, ``I guess.''

They sat there for a few more minutes in silence before the thought of her father and his plan once again entered Kiele's mind.  Zane protected her, she thought.  She had vowed to protect him also.  What good was she just sitting here ignoring what seemed to be the biggest threat to Zane, her father?

``Zane,'' she began.  ``I know this may sound a little odd.''  She was talking down to his shoes and he gently lifted her chin up so he could hear her better.  She smiled and continued, ``I'm a little scared about you and my father.''

His faced turned to utter confusion.  He had no idea what she meant, as far as he was concerned there was nothing wrong with his work.  ``Whatever do you mean?'' he asked.

Her head had slipped back down now, and Zane didn't try to lift it again.  She was thinking hard about how to phrase it.  How she could make it sound less extreme.  She couldn't possibly tell Zane about her fathers actions at the hospital for example, or in the basement.  He would likely go home and try to discuss it with Mark and that wouldn't end well for either of them.  She was well aware of that.  

``What are you guys up to?'' she asked quietly.

He replied quickly.  A little too quickly and immediately on the defensive.  ``Nothing to worry about.''

It wasn't a lie.  Not in Zane's mind.  As far as he was concerned, he had full justification and permission to do what he was doing.  Mark had asked him not to tell Kiele about his job, and he respected him for that.  He didn't want to worry his daughter with all the possibilities that working as a G-TEP agent may entail.

``Don't you trust me?'' said Kiele painfully.

``Kiele, I trust you more than anyone I've met in my life,'' he said, ``but it's really nothing to worry about, just a little lesson in physics.  Your father's actually quite a keen physicist.''

She ceased questioning.  Zane obviously wasn't going to tell her.  Maybe he thought she wouldn't understand what it was that they were working on.  She was sure he'd never lie to her.  In truth she was right on both counts.  Zane was protecting her once again.  He couldn't let her know what it was they were working on, it certainly wouldn't put her mind at ease.  Zane was fully aware of how dangerous his task was, and how desirable the final product would be to a great many people.  He had to respect Mark's wishes and keep it firmly between them.

She looked up at Zane.  It had been a few minutes since she had finished questioning her partner and now she sat there, wishing more than anything to reconcile with a kiss.  They still hadn't kissed.  It was driving her crazy.  She wanted to give her heart away completely.  In point of fact, she already had, but the kiss was the signing of the contract, crossing the 't's and dotting the 'i's.

He looked down at her, his head was a good twenty to thirty centimetres above hers, and their eyes locked.  It was one of those now or never moments.  She began to move closer to him, and he began lowering his head towards her.  This time it would happen she thought.  In the distance, the end of morning siren was heard, but was completely ignored by both parties who now sat poised to show their love for each other.

They moved closer still and Kiele closed her eyes, it was a moment she had dreamt about on several occasions.  Each time Zane's hand had been resting on the back of her head, tenderly cradling her whilst he kissed her lips.  She felt his hand moving through her hair, just as she had imagined.  It felt amazing.  The breeze whipped through the courtyard and tossed sections of her hair into Zane's face.  He smiled, eyes still wide open, he didn't want to miss this.  

Kiele's heart was racing now.  Her father couldn't find out about this, that was for sure.  He would instantly know she had fallen for him.  It had been difficult enough to contain her affection for Zane around the house, but this would be too much.  She scrubbed her father from her thoughts, this was about her, her and Zane.

The doors to the college entrance burst open and a throng of students poured out.  Zane and Kiele broke apart in the nick of time.  None of the students had spotted them, Jolie had, but none of the students had been paying attention, being far too interested in getting out of class on time for their change of lesson.  Damn it, thought Jolie, they were so close.  She had been rooting for them ever since she had seen them sitting together outside, watching them out of the corner of her eye.

They both arose and Zane parted with his coat.  Kiele wrapped it around herself and silently thanked her guardian.  They were met by various members of their class, most wanting to apologise for their earlier indiscretion, but some still hell bent on trying to upset the new couple.  Mikael who seemed to have had a change of heart was going around challenging the opposers in a threatening tone, whilst the others gathered around the pair, gently patting them on the back in a congratulatory manner.

  ``I'm really sorry,'' said Janus genuinely.  ``I really didn't mean to upset you.''

``It's fine.  Don't worry about it at all,'' said her forgiving friend.

Zane, Kiele and a few of their closer friends walked off towards the next lecture of the day.  None of them particularly wanting to go.  Jolie watched as the group of youngsters made their way in front of the window.  Zane was walking with his arm round Kiele and she was smiling and laughing with the rest of them.  Jolie was pleased.  It seemed like something good had come out of the accident after all.





