\chapter{30}
\section{Avoidance}


``So you believe me now?'' said Jessie in the coldest tone possible.

``I guess I have no choice,'' came the reply.  It was Ruben.  He couldn't believe that it was all coming to pass.  There was no way it could have been overheard by anyone.  Maybe it had been extracted from his mind under hypnotism, but then if that was the case, why hadn't they tried to obtain the details of Oken's secret location earlier.  

Ruben was out of ideas, he had to give it to Jessie, it was a damn fine plan and he hated him for it.  He hated him for everything.  Ruben had no idea what Jessie was planning, he had no idea that he was collaborating with Ric.  Just why did he want the technology so badly?

The worried man scuffed the floor like a disgruntled teenager whilst he listened for the man at the other end to state his demands.  It was crucifying him.  Throughout the entire time the phone had been pressed to his ear, Ruben was asking forgiveness from Oken.  He was betraying his brother, his best friend, so as to save Oken's daughter.   It was an impossible situation and for a second he felt he was about to have another attack.  

He closed his eyes and concentrated his minds eye on a single point in space.  Everything was relative to that point.  Everything would be OK.  He just had to relax.  He grabbed hold of the breakfast bar in front of him with his left hand and rested on its cold surface.  His brain was going into overdrive now, the single point had been replaced by thousands.  There had to be another way.  There had to be something he could do to stop this mad man.

``I'll come by to pick you up'' said Jessie.  ``Just be ready, we won't be hanging around.''  He was deadly serious.  He didn't want to give the G-TEP any ideas about what was going on, it was strictly an in and out job.  He had visited Ruben only a few days earlier, visiting him again would be suspicious but he had no one else left to entrust picking the retard up with.  He had toyed with asking Ric to do it, but something he had said earlier had made him think otherwise.  It was up to him.  He would do it.  He would receive the wonderful gift, the power that would redeem the world.  His thoughts ran away from him and he dragged himself back down to earth.

Ruben swallowed hard, ``I'll be ready,'' he said, ``but you'd better keep one eye open at all times.''  He slammed the phone down, hoping dearly to kill Jessie with the force.  It hadn't gone the way he had wanted.  Jolie had phoned him earlier in the day and told him the phrase he so desperately hadn't wanted to hear.  He hadn't quite believed it and though Jolie persisted, Ruben said nothing of the consequences of the message she had just delivered.  It was better that way.  She was a nice lady and he didn't want to risk getting her involved in his problems.  Especially as they had now escalated severely.



\thoughtbreak



Jessie arrived and walked up to the door.  It was already half open and sported an unimpressive attempt to fix the damage he had caused only a few days previous.  Jagged bits of wood stuck out at all angles and Jessie smiled as he remembered the look on Rubens face when he had entered.  It had been one of horror and terror combined.  Oh! had it been glorious.  

The agent kicked the door the rest of the way open and it flung against a unit inside the house.  Ruben didn't have many items in his house, but those he did have he treasured, even though he found it harder and harder to drive himself into taking care of them.  Dusting and polishing had been a thing of the past a long time ago, and Ruben had let his once rustic living area fall into a deep depression.

As the door hit the sideboard, it made fifteen of Ruben's mothers antique plates jump as they were propelled by their usually solid footing.  Jessie shouted, ``Come on idiot, time to go.''  When Ruben didn't reply he kicked the door squarely in the centre and sent it swinging towards the sideboard for a second time.  It carried with it the full force of Jessie's foot and his slightly too large G-TEP issue boots.  The reinforced frame of the door made contact with the sideboard again, sending the plates toppling forward, leaving contact with the shelves they had been sat on for so many years.

Had Ruben been around he would have winced as each one fell through the air to its eventual doom.  Some hit the sideboard on the way down, others, had been given enough energy in order to be thrown clear of the furniture entirely.  It mattered not their route, each one ended with the same fate, smashing into hundreds of pieces.  The legacy of Ruben's mother's collection lay in complete tatters.  One lonely plate remained on the sideboard, defiant at the sight of its friends demise.  Jessie took out his side arm and jabbed the butt of it into the centre of the plate, showering himself with shards of broken porcelain.

He shouted out again, ``Come on retard.  I warned you.''  Still there was no reply.  Ruben was no where to be seen.  Jessie had a problem.  All of a sudden his rage brewed to the surface and he picked up a nearby chair and hurled it towards Ruben's coffee table.  It hit the table and once again the room was filled with a crescendo of breaking glass and anger.  

Jessie reached in his pocket for his phone and dialled a number quickly.  As he stood there waiting for the recipient to answer he began kicking at various items of Ruben furniture.  First a chair, then a glass door of a cabinet, before finally Jessie's foot became one with a piano.  The lower boards of the upright piano couldn't hold out against the force of Jessie's boot and they caved under the pressure, unable to prevent the intrusion of this evil force.  The piano screamed in pain.  

On the other end of the phone, someone picked up.  ``What the heck are you calling me for?  You know what we agreed.''  It was Ric, he wasn't happy at being disturbed at work, on duty, by the weasel that was supposed to have had the job done two weeks ago.  He hadn't been impressed when he had learned about Jessie's little train crash, but nonetheless had allowed him to carry out his plan.  Jessie was a child, and occasionally Ric had to pander to him to get what he wanted.  This had been one of those occasions.

``He's gone,'' shouted Jessie, ``he's freakin' gone.''

``Well where the heck could he have gone to?'' screamed Ric down the phone.  This was not how it was supposed to be.  He knew Jessie had to get the device somehow.  He knew that 'someone' had travelled back in time in the near future, but he couldn't tell who it was.  He had erased the records as soon as they had appeared so as not to raise any suspicion from any of the other G-TEP agents.  One such agent had indeed questioned the evidence that had been so quickly deleted from the system.  Ric had explained about the difference between residue signatures and echo signatures.  The agent, only a junior, had no idea what he was talking about and had left the room before his ego had been bruised further.

Jessie was thinking hard now, he had no idea where the cretin would have run off to.  Didn't he care about Kiele at all?  His plan was falling apart.  Had Ruben actually grown a spine?  Maybe he was tying to find Kiele right now?  Jessie didn't think so.  Ruben wasn't about to dash into the fray to save her.  He was the kind of man to take the path of least resistance.  That's how Jessie viewed him at any rate.  

``Jessie.  Concentrate.''  Shouted Ric.  Ric used Jessie's real name regularly.  Mark was reserved only for outside communications.  He had been used to calling people by dual names, he had been in the G-TEP for years after all.  ``If you don't find him, it'll be your life in danger, not......''

``Don't threaten me,'' Jessie snapped back interrupting Ric and startling his superior slightly.  ``I'll find him.  I know how important this is.''  He hung up on Ric.  This was not going well.  He shouldn't have called.  Ric was furious and that was a situation that could well have been avoided.  Jessie was well aware of Ric's connections both in the G-TEP and in the underground circles.  If Ric wanted Jessie dead, it would be so.

He hated how his partner had become his superior.  It had been Jessie's idea in the first place anyway, had it not?  He couldn't remember now but his current situation was certainly not good.

Jessie racked his brains.  Where would Ruben go?  Then it hit him, the only person who had attempted to visit him whilst he had been on trial.  The old lady.  What was her name?  Kaitlin.  He picked up his phone and began using the built-in directory to search for her address.  He knew she wasn't far from the Zone, but far enough that to search every house would have taken him all afternoon and would have raised some suspicions at the same time.

Damn Ruben.  Damn his tiny little brain.  Ruben couldn't hope to outrun him or out smart him.  The address popped up on the small screen and Jessie loaded it into his navicom.  It began giving him verbal directions, but he silenced it, ``I know where it is ya freakin piece of tat.''  He kicked his foot into yet another item of furniture and stormed out of the room.  



\thoughtbreak



As he ran down the road, Ruben rediscovered how out of shape he really was.  He had decided to give Jessie the slip on the spur of the moment.  Even his own mind hadn't fully understood what was going on.  He had to make a stand somehow, he had to stand up against the regime.  For some reason Jessie wanted that device, and he had to keep it out of his hands.  

His feet were moving faster now as he settled into the rhythm.  He hadn't taken a taxi, that would have allowed him to be tracked too easily, biometrics and all.  He had decided the best way to proceed was to quite literally make a run for it.  He could almost imagine the rage that was brewing inside Jessie as he discovered the house empty and his prized possession slipping from his fingers.

Ruben was scared, not just a little nervous.  Ruben was terrified and he was heading towards one of the only people who could make it all better.  She had been like a mother to him on countless occasions and now he was going to ask his 'mother' for one last piece of advice.  Deep down Ruben didn't expect to make it away from Jessie forever.  This was his last ditch effort.  She may have a secret card up her sleeve, she may be able to help him out just this one last time.

He rounded the corner of another road and was almost knocked over by a red car.  The driver shouted at him, but Ruben was in a world of his own.  He felt almost invincible as he pressed on down the street.  He was fairly certain that Jessie was acting alone, or in cahoots with only a small group of people.  This worked to his advantage, it meant Jessie couldn't call on the small army which was the G-TEP to come and flush him out.  It was Ruben against Jessie, Jessie against Ruben.  Who would win?  He really couldn't say.

As he continued down the long road, he noticed the almost hypnotic pattern the old wooden fences made as he ran, it was almost stroboscopic.  His head was at ninety degrees as he ran forward , until a dog barking in front of him brought him back to his sense.  The dog, on a lead, continued barking at him as he gave it a wide birth.  The owner scowled at Ruben as he ran past.  When would people look where they were going, thought the pedestrian.

Ruben's lungs were beginning to fail on him.  He was breathing hard and sweating all over.  He was a wreck.  He hadn't been out of the house properly in over eight years.  Jessie had seen to it that his life could be a misery no matter where he went.  So he had secluded himself in the house.  Once a week he had ordered a new set of books and once a week they had turned up on his doorstep.  He hadn't cared for the newer fiction at all, no, Ruben had fallen in love with the sound of the late twentieth century.  It sounded like such a simpler time.  Only a few years before he and Oken had been born.

Bang!  A car door slammed next to him and in his confusion Ruben believed wholeheartedly that he was being shot at.  He dived for the floor, scraping off both elbows as he did so.  He continued crawling along the floor whilst the owner of the car, a young woman in her thirties shouted after him.  She was asking if he was OK, but Ruben could only hear anger in her voice.  She was obviously out to get him too.

Finally he reached the door he had been looking for.  It was wooden, painted green with an old fashioned knocker in the centre.  With a definite purpose, he pulled back on the knocker and attacked the door.  

``Please be in, please be in, please be in.''  He repeated the words almost as if he were casting a spell.  He started looking round him left, then right, then left again.  The woman who had shot at him earlier was gone and the neighbourhood was once again quiet.  Ruben could hear someone walked around inside and without thinking he slammed his hands on the door.  ``Kaitlin!'' he shouted.  ``Kaitlin, it's me Ruben.  You have to let me in.''

The door opened and the worried face of Kaitlin appeared, just what kind of trouble had Ruben gotten himself into now.  She looked tired and worn, Ruben had no idea he had awoken her from a well deserved afternoon nap.

``Ruben,'' she started, ``What in heaven's name is the matter?''

Ruben was jerking around on the door step like a young boy in desperate need of visiting the toilet and it was obvious he wanted to go inside.  Sighing, Kaitlin let him in and closed the door behind him.

``Bolt it,'' he said.  When she didn't obey his command he lunged for the door and bolted it top and bottom.

``Ruben stop!'' she shouted, ``Just stop.''

The man stood there.  Now in his late forties Ruben looked wildly out of place cowering behind the locked door.  Kaitlin took him by the hand and pulled him into the lounge.  

``He's after me,'' he huffed, ``Jessie.  He's after me.''  

Kaitlin shook her head as she looked at the mess before her.  He was crumbling before her very eyes and she knew that if she wanted to get any information out of him, she needed to calm him down, else he would shortly be having a panic attack.  

``Ruben, he's dead.  Remember?  There was an accident, and he died.''  She rubbed his back slowly in large circles as the old man gasped for breath.  Now it was Ruben's turn. He shook his head.

``No.''  He coughed, ``He's still very much alive.  They changed his name Kaitlin.  They changed is damn name!''  

Her eyes widened in fear.  Had they really done such a thing?  Jessie had been disliked by a large proportion of the community and the G-TEP in an attempt to cover up a) the events at the Zone and b) the annoying brat who had been so highly recommended by Ric, they had changed his name to Mark Matthews.

``Ruben,'' she started, ``are you sure?''

``Yes,'' he wheezed, ``He's been visiting me since the Zone.''

``Oh my.  Why didn't you ever tell me?'' she asked.  Before he replied, she already knew the answer.  They would have killed him if he had.  He didn't reply, seeing the realisation on her face.  She looked at the sad lonely man in her lounge.  He was a shadow of the man she once knew, a skilled watchmaker and loving husband.  She had always loved Ruben like her own son, and she had known that Yasmine wasn't right for him, but could never bring herself to confess it to his face.

``Why are they after you Ruben?''  She thought it prudent to ask.  Though he was a kind and loving man, sometimes he had a habit of doing the wrong thing.  She wondered if this was one of those times.  

``I hid something from them,'' he said, starting to cry.  ``I hid something from them and now they want it.''  He had almost reverted into a childlike persona.  Tears began welling up in his eyes.  ``I never wanted them to find it Kaitlin,'' he wailed.  ``It was never supposed to be found.  They heard me talking to a woman.''

Suddenly she pounced on him like a hawk.  ``Which woman Ruben?  Which woman did you talk to?''  

``The one from the school,'' he said.  ``She was nice to me and we just talked.''  

Kaitlin put her hand to her mouth.  It had been her fault.  She had told Jolie where Ruben was.  In a roundabouts way.  She hadn't given her the exact address, but she hadn't exactly kept her mouth shut.  She'd known Jolie for years and trusted her implicitly.  Was she really a bad egg?  Had she really given Ruben up to the G-TEP forces for keeping something from them.  She couldn't believe it.

``Did she do this to you?'' Kaitlin asked.  ``Is she responsible?''

``No,'' he said sorrowfully, ``It was Jessie, she knew nothing about it.''

The two of them stood there as Ruben tried to regain what was left of his breath.  

``Go and wash yourself up Ruben.''

He plodded off and Kaitlin sank down into one of the chairs.  With her head in her hands, she prayed for a miracle.



\thoughtbreak



He wasn't going to let that sniffling excuse for a human being get the better of him.  Ruben hadn't left long before he had arrived, he couldn't have gotten far, and the most likely place for him to run to was Kaitlin's.  He couldn't believe that the broken little man had gone behind his back and managed to out smart him.  Why hadn't he seen it coming?  He slammed a hand down on the dashboard of the car.  There was a muffled click as part of the dashboard broke away inside but Jessie didn't care, it wasn't his car anyway.

He ripped through the streets of Alendria in the chase of his life.  If he didn't find Ruben soon, he would be found instead.  Ric could quite easily invent a story about Jessie going rogue, after all, to all intents and purposes, he had.  Ric had managed to keep himself distanced just enough that he could deny all knowledge of the plan.  The G-TEP would never use a brain scan on such a high ranking officer.  It would have sent shock waves through the entire organisation and that was the last thing the global commander wanted.

The car responded to his every movement.  Like a magician waving a magic wand, he commanded his vessel through the flow of traffic.  Though he was a G-TEP employee, his rank didn't require him to have a car with traffic dispersal mechanisms.  He had to rely on his skill at driving in order to make it there.  For a second he eased off the gas, why was he rushing at such great speed?  What was Ruben going to do, realistically?  Kiele was currently under supervision, a little gift from her father, Zane was incapacitated, and Kaitlin?  Well she was an interfering old biddy that should have died a long time ago.  Unless Ruben knew how to get the device working?

He stepped on the accelerator once more, pushing hard.  Ruben had no idea how to turn a temporal weapon into a time machine.  The guy had read a lot of books, but from what Jessie had seen, these particular books were more of the fictional variety.  Ruben didn't have any where near the skill and brain power to make the device work.

The engine roared as the internal computer changed gear.  The car was getting on in years, and though most people had now switched to solar power over the good old internal combustion engine, the G-TEP required a car to have a certain maximum speed.  The solar powered cars of the present day were becoming more and more efficient with every generation.  Continuously variable transmission had been perfected and was now installed in every model.  There were no gears any more, just a smooth transition from low to high speed.

Jessie hated the solar cars.  There was no grunt, no sudden thrust from the gear change.  Modern day cars were sissies.  He loved his internal combustion engine.  Many times over the years, the G-TEP had tried to get Jessie to switch to one of the new solar models, but each time he had refused and apparently it seemed as if G-TEP agents got whatever the hell they wanted, kings in a land of peasants.

He pushed on faster.  The navicom was showing that he was approaching his destination.  Just a little further now, he thought.  Jessie was going to get his man, he spoke slowly and purposefully, ``I'm gonna cut you so deep.''



\thoughtbreak



The water splashed against his face and soothed his sweating pores.  Ruben hadn't been a particularly good runner when he was younger.  Now he was nearing fifty, his body felt all but dead.  He looked up into the mirror and saw his ageing face.  He couldn't give up now.  He needed a way round this, and fast.  He looked at the droplets of water running down his disfigured face.  Had he always been this ugly?  No wonder Yazmine had left him.  His head dropped.  Yazmine.

Suddenly there came a furious knocking on the door.  Instantly Ruben knew who it was.  It had to be Jessie.  He looked around.  There was no escape.  The window of the bathroom only opened a small way and was then trapped by the wall of the house behind.  He started breathing heavily as the door was attacked once again.  What should he do?  There was only one doorway out of the place as far as he knew and running for it would cause problems.  Jessie would see him for sure and then game over.

Ruben could hear Kaitlin beginning to walk towards the door, asking subversively who it was.  He slipped into the shower cubicle and pulled the door shut.  Luckily, the door sported an opaque pane of glass, frosted and without anyway for an outsider to see what or who was inside.  

Kaitlin opened the door, or at least tried to.  As soon as he realised that the bolts had been loosened and that the catch had been unlocked he planted his foot in the middle of the door and forced it open.  It hit Kaitlin in the chest and sent her flying backwards, hitting the wall behind her.  She slumped to the floor in a daze.

The large boots of Jessie entered the building and he slammed the door shut behind him.  He knew the little cretin had to be here.  As Kaitlin nursed herself into a sitting position, Jessie began searching the house room by room.  The kitchen was at the far end of the house and he began there.  

``Come out you freakin coward,'' shouted Jessie as he tipped over the kitchen table, sending cutlery and dishes crashing as he did so.  He was rather enjoying this sudden rush of power, this surge of energy.  No one would stand in his way.  

``Stop it!'' shouted Kaitlin, still lying in the hallway.  ``There's no one here.''  She had been careful not to say 'he's not here.'  It would have given the game away that 'he' really had been there.  It wasn't much, but it could mean the difference between Ruben leaving alive or dead.

``Shut-up Kaitlin,'' shouted Jessie.  ``I know he's here.''  He moved on to the next room, kicking the door to the bathroom wide open.  Ruben froze in fear.  He had heard everything up to this point.  He knew Jessie would find him eventually, yet he stayed quiet.  He didn't want Kaitlin to get hurt, but then he couldn't bring himself to give up either.  It wasn't for his own safety, but for Kiele's.  She had seemed like such a happy young girl.  He couldn't condemn her to death just like that.  Ruben knew that once Jessie had what he wanted, Kiele and whoever else he was holding hostage in his sick game of power, would be killed, or mutilated as he had been.

Jessie looked into the room.  Not seeing anyone immediately he moved down the hallway once more.  Ruben's heart was pounding really fast now.  Had he seen Jessie, it would have been pounding a whole lot faster.  He was brandishing an assault rifle in his right hand.    The boy had escaped this time.  Would Jessie leave now and go home?  

It was such a childish thought that Ruben almost gave himself up there and then.  Who was he to stand up to Jessie?  He forgot what carton of milk he'd used the previous day.  He ate olive green bananas because he thought the yellow ones were poisonous.  He wasn't all there.  Yet here was Ruben at his most resolute.  Staying silent and making the decision to stand tall against this crook of an enforcer, this bully.  He had to be stopped.

Jessie continued on down the hallway.  He went in the bedroom on the opposite side of the passageway and looked under the bed.

``Guess you couldn't fit under there could you,'' he screamed.  As he stood back up he saw his reflection in a full length mirror attached to a large cupboard.  Blind with rage, he swung the rifle at his own face, smashing the reflector and sending shards twirling all over the room.  One or two made it from the cupboard to his shoes and the evil figure kicked them off smashing one into a further three pieces as it hit the wall.

Jessie exited the bedroom and started for the cowering Kaitlin.  As he walked past her, he pointed the barrel of the gun at her old wrinkled face and pushed it forward, making contact with her ageing forehead and forced it against the wall.

``I'm coming back for you Kaitlin,'' he screamed.  He removed the gun from her head and she felt it flop forwards.  How could she have been so careless.  In her attempts to help one young woman overcome an obsession that was driving her crazy, she had inadvertently informed the G-TEP that the case hadn't been completely closed.  She began to cry, slowly at first, then tears began streaming down her face.

Jessie was now in the lounge.  It was just as it had been when Zane and Kiele had visited not a week ago.  Jessie couldn't see Ruben anywhere, yet he hadn't done any looking with his rifle yet.  He swung it around and took out several of the display cases as he did so.  Ruben clearly wasn't here either.  Jessie had obviously been out smarted.  No.  It wasn't true, there was still one source of information entirely untapped.

Remembering the old woman lying precariously in the hallway Jessie turned round.  He stomped towards and heard her gasp as she realised she was next.  She started to try to scrabble away, but Jessie was too fast for her.  He grabbed her by the leg and pulled her limp old body into the lounge.

With the rifle still in one hand he lifted her up into a sitting position with the other.  He pointed the barrel at her head.  She was terrified, blubbering like a baby but still managing to hold out against the forces of evil.  Ruben, still cowering in the shower had heard her cries as she had been dragged into the lounge.  Jessie flicked the safety catch off of the rifle.  Kaitlin began screaming.

``No, no, no, please, no, please no,'' she said.  ``You've taken enough from me already.''  Jessie's face turned slightly pensive.  

``Don't like that approach eh?'' he said with a grin.  ``How about we make it a little more personal then?''  He threw the rifle to one side and reached for his hand gun.  It felt cold against his skin and he gripped it harder to assist the draining of the heat from his hand.  He pushed the tip of the barrel to the side of her face, and smooshed her cheek into her jaw.  

``Where the heck is he?'' he shouted, cocking his head to one side expecting an answer.  She was blubbering still and he had to get her to recompose herself.  He knew she would let up eventually.  He took the gun away from her face and moved it to her mouth, forcing the cold metal between her teeth.  She started screaming through gritted teeth, biting down on the barrel.

``Tell me where he is and I'll make it stop.'' He was actually serious.  He had no intention of killing her just for the sake of it.  She continued screaming, her lips occasionally finding the cold metal and reeling back in fear.

He shouted at her again their faces less than six inches apart, ``Tell me where he is, you stupid witch of a woman.''  He took her support away and she fell backwards to the floor.  Her mouth, now missing the gun, remained open at the shock of the relatively short free fall.  Within seconds he was standing over her, the rifle back in his hands.  ``Well then I guess I have no further use for you.''  

He had built this moment up to a climax, so she would feel there was nothing more.  He had toyed with her feelings both physically and emotionally and now he drew back the sword for the final thrust through her heart.  

Poor Ruben could take it no longer.  He stood to his feet and exploded forth from the shower.  He hadn't meant to break the glass, but it had been so thin it had just happened.  The door to the bathroom was still open and as Jessie began to look up to locate the source of the noise, he was immediately aware of the lumbering giant coming towards him.







