\chapter{03}
\section{}
	Go  

The manager's voice echoed through the platform as the music hit its climatic section.  Yaz had decided, in an extremely short amount of time, he was still going to do his best, despite the high probability that this would be the last fight he ever saw.  He was a respected fighter in his early twenties with no real job and nothing to lose.  He wasn't a weapons developer, he was just a user.  He bought old tools off of previous fighters and then hired some tech-heads to enhance and integrate them.

It was at that instant that Oken knew his dream had come true.  He was about to unleash his weapon for the very first time.  He ran towards Yaz and engaged in some showmanship blocking and advancing.  Yaz knew the game all too well and cottoned on to Oken's idea fast.  Oken wanted Yaz to meet his end with his honour and respect intact.  They were both well aware that Oken could end the fight any time he wanted.  Whilst itching to unleash the deadly power that lay at his finger tips, it gave him great pleasure knowing that he had already won.  The chances of Yaz managing to overpower him, were very slim indeed.

The two of them flipped around, dodging each others attacks, defending masterfully.  The music was still raging and the crowd was still jumping.  The loser of the first battle stood stock still and gazed on in amazement at the way in which these fighters were duelling.  There was absolutely no way that he would ever be able to match their level, they were in a class all of their own.  

The two fighters below became locked in a struggle,  Oken pushing his sword against Yaz's staff, and Yaz forcing back against Oken's sword.  In an explosive instant they flew apart from each another with expert precision, each knowing the others rhythm and timing down to the very last microsecond.  

They both somersaulted and landed about five metres apart, trying to regain their breath as the music thinned once again to a stonking bass line.  They both made advances towards each other, little steps trying to entice the other into a frenzied attack.  It was almost as if they were dancing.  

For a moment Yaz forgot all about Oken's super powers.  Then it was time for Oken, once again, to show his superiority.  The music blared once more and Oken tightened his grip on the handle.  The leather felt warm and inviting.  So effective was his weapon at slowing down time, that he could actually pause to consciously analyse the feelings in his hand.  He also had time to think about his rumbling stomach and time to notice the pretty blonde girl standing in the third row from the back, second one in.

She was in her early twenties Oken decided and for a moment he allowed himself to imagine what it would have been like to be married, what it would have been like to have children.  He looked over at Yaz, who had begun a desperate lunge towards him.  It was time to finish this.

Yaz was closing in on him now and Oken took the initiative to side step the incoming staff butt and spin round to once again face his foe.  Yaz began to turn his head to locate Oken.  The immortal began thinking how cruel it was to play games like this with a warrior as serious as Yaz.  At this point in time though, Oken didn't really care about honour or fairness, his time had come to show what he had created, to show what he was really capable of.

He released his grip on the now sweat ridden handle of Bethany and Yaz wheeled round in awe at the older fighter's speed and finesse.  He made another lunge at Oken who decided once again to make full use of his advantage.  He squeezed the handle and slid down underneath Yaz. In one fluid motion he bent his legs and placed his feet on Yaz's chest.  The muscles in Oken's legs bulged, and he released the coiled springs and the grip simultaneously.  Yaz was airborne and had no idea how it had happened.  He was flying through the air and he had never even seen it coming.  For a moment it even felt good.

The voice in Yaz's mind reminded him that Oken probably had something to do with it and a quick spin of his head saw the figure of Oken standing to his feet.  With a quick twist, which Yaz was sure had ruptured a ligament or two, he managed to propel himself in such a way as to land on his feet.  Oken was just delaying the inevitable and Yaz was quite sure he was enjoying it.

By coincidence, the pretty blonde in the third row from the back, second one in, was also having the same thought.  She had been a follower of Oken's career from the very start and had always admired his sportsmanship, precision and tenacity.  This time though it was different, she was disappointed in Oken, who seemed to be just toying with his prey.  The girl, Jay, was one of the young journalists who had been assigned the Oken - Yaz fight.  Her report would undoubtedly detail Oken's skill and mastery in full, but she was already thinking that a criticism of his over confidence would also be justified.  The word bully sprung to mind, cocky even.

With a final burst of energy Yaz ran towards Oken using the speed as only he knew how.  Oken looked at Yaz, then down at Bethany and squeezed the grip.  As he did so he saw a droplet of sweat fall from the handle and make its way gracefully to the ground, spinning and pulsating.  He sidestepped the incoming Yaz and held out Bethany making sure to cut Yaz in such a way that he would feel as little pain as possible.  The blade was aimed across his chest and though Yaz was aware of the blade's position, he never had time to change direction.  His opponent ploughed into the blade, so sharp, that it made no sound in cutting through the flesh, muscle and bone of Yaz's body.  

As Oken watched the final blow in its grim slow motion, he noticed that no blood spilled from the wounds.  It was as if it was being sucked into a void which began at the bare flesh made by that spiteful Bethany.  As quickly as the cut was made, Yaz was gone.  It started from the lacerations in his chest and then very quickly moved in opposite directions towards his head and his feet.  Oken wasn't quite sure what it was devouring his opponent, but before the two parts of Yaz's body could hit the floor, he was gone.  Erased from existence by Oken's magic marker.

Oken released the grip and watched as a hot ethereal air column rose from where Yaz had once stood.  The show had been spectacular.  It was true that he felt some level of remorse for what he had done, but nothing could overcome his feeling of pride and superiority right now.  The crowd went wild with amazement.  The producer was screaming instructions to replay the shot again, and Ruben?  Ruben just stood there.  He had known it was going to be a fantastic show, but this had just dumbfounded him.  

Oken looked up, turned to face the crowds of screaming, blood thirsty wolves and raised Bethany up to sky.  He held her with both hands above his head and revelled in the mania which he had just created.  Behind him the screens replayed the final blow over and over with pixel perfect quality.  The look on Yaz's face was that of pure fear as he faded into non-existence.  His death had been quick, and from the expression on his face it didn't look as if he had suffered much pain, if any.

Oken gripped Bethany tightly again and familiarised himself with the whoosh once more.  He wanted to savour the moment, and savour it he did.  With time slowed down he could fully appreciate the crowds expressions and sentiments.  He stayed as still as possible.  The time for showing off was over, now he just wanted to revel in the atmosphere he had created.  Three years of his life.  His most arduous task to date, yet he had completed it, and added some style while he was at it.

The crowds began to pour down into the platform below them.  The music increased in volume and Oken flung his head back and roared.  He released the grip and his world was once again loud and proud.  This had been the night he had been waiting for; The night when people had seen what he was truly capable of.  His parents had sent him off to war when he was nineteen even though he had begged them not to.  Oken was an academic and he would have much rather stayed at home and continued with his studies.  Despite the attention the schools, prospective universities and colleges gave him, Oken's parents classed him as a dud and a freak.  They had decided his future for him and that was that.

As the hundreds of excited, drugged up nuisances rushed the field.  Oken felt a sudden sense of panic.  He quickly and expertly replaced Bethany in the scabbard and made his way to one of the stairwells, kicking Yaz's staff as he did so.  He reached the stairs and began to push past the almost fluid like stream of human flesh which was making its way in the opposite direction.  Oken imagined how much easier it would be to reach the top if he used Bethany to cut down and obliterate the hungry mob that barred his path, but was just an inner joke, he never wanted to harm them.

He reached the top and Ruben granted him an unbelieving shake of the head.  It continued as Oken walked slowly towards him, the light reflecting off Ruben's shiny shaven head once more.  This time he could afford the joke.  He held up his hand as if being blinded by the light from his friend's bonce and they both laughed.  Excited fans were running past, slapping Oken on the back and shouting numerous compliments in his face.  

``Well done my friend,'' said Ruben, ``well done.''  Oken could feel the admiration almost seeping off of Ruben's body.  It joined the admiration of a hundred more and filled the atmosphere that fuelled the frenzy.  Ruben put his arm around the older fighter and took him off in the direction of the Chiller.  They didn't reach their destination however.  The Zone's owner was running towards Oken.  For a second, Oken could not tell with any certainty whether the old man wanted to congratulate him, or to rip his head off.  He was panting from running so fast and extended his hand for Oken to shake.  He accepted the offer and smiled.

``Oken…..You……Fantastic,'' panted the executive.  The words had trouble leaving his mouth which was dry and in desperate need of a drink.  He too put his arm around Oken and the three of them walked slowly to the Chiller in order to celebrate this latest achievement.  The crowd was still jumping around, both in the spectator stands, and on the platform below.  He was being bombarded from all directions with hands, pads and the most insane questions he had ever heard.

``Oken, are you a god?'' shouted a drunken man swaying wildly and looking very very ill.  It wasn't long before the man promptly threw up all over the floor and he was removed from the arena by a couple of Ruben's burly associates.  The man began kicking and screaming and once again emptied the contents of his stomach all over himself.  The bouncers shook their heads.  It was amazing how much of a mess some of these so called fans could make.

Oken was ushered to the door of the Chiller and both Ruben and the manager, Zeus, took a step back, as if to let the fighter have the full glory of walking into this throne room.  Inside, everyone was waiting for him to enter.  Many of them had guessed that the weapon had been of a temporal origin, but none of them realised the implications, or thought it possible that it could be turned into a Zone weapon.

The master walked into the room and was met with an almighty cheer.  Ruben and Zeus pushed him forward and all the fighters took their turn at ruffling the grey mop which sat atop Oken's head.  Jessie was standing in the corner and even he was smiling.  Oken presumed that he had been forgiven for his earlier actions.  He looked around at the faces of the fighters in the room.  They were all smiling, some laughing and Oken knew that they all shared his sense of achievement.   It bothered him a little that no one seemed to be scared of him.  Here he was, sword in hand, and everyone was treating him like an old friend.  Perhaps that was why.

Ruben motioned for the other members of the Zone's inner most circle to quieten down.  Everyone began to hush except for one man sitting in a chair next to Ruben.  He was laughing his head off and Oken could see that he had had extensive dentistry.  Ruben gave him a swift slap to the back of the head and the man spun around clutching his head in pain.  

``Pipe down Marty,'' said Ruben, ``Oken's got a couple of words to say,''  Oken didn't remember telling Ruben that he wanted to make a speech, but everyone was looking at him and even Jay had been allowed in to the Chiller to make comments on Oken's post match speech.  It proved how monumental this fight really was, journalists such as Jay had never previously been allowed into the Chiller and the notion of a young female in amongst these savage beasts had an irony that Oken found quite disturbing.  Jay was not in the least bit worried about the huge monsters that surrounded her on all fronts.  She was there to do her job and to get paid.  It was all an experience to her, a way to gain an insight into writing for a business client.

Oken walked into the middle of the room where the table had once stood.  If it had been alive, it would probably have been jealous that its once prominent position in the room had now been given away to someone else.  If the table had been alive though, it probably wouldn't have argued with Oken directly, not with a sword like that at any rate.   Oken put down the drink which some random fighter had forced into his hand and cleared his throat.  Jay leaned forward, hanging on his every breath.  Oken opened his mouth and was aware for the first time of the silence that had fallen.  He didn't like it.  He lived for the paroxysm and now it was gone.

``Come on man, talk!'' said one impatient listener.  He thumped his fist on his leg and then realised that it had been a bad thing to do.  It hurt like hell.  Oken spoke.

``I don't know how it happened,'' he said, with such sincerity that Ruben thought he was about to cry. ``It became an obsession and I just couldn't stop.  In some ways I wish I could go back.''  He turned and walked away.  The crowd was left dumbstruck.  It was not the triumphant speech which they had been expecting.   He opened the door of the Chiller slowly and the noise from out side leapt back in, filling the room with pressure fluctuations that drowned out the surprised gasps and chatter of the inmates.

In a way, Oken had been glad of the music and the crowds.  It made it all the easier for him to slip away unnoticed.  He made his way through the jumping crowds and back down the stairwell to collect his shield generators.  He took the remote out of his pocket and switched them all off simultaneously.  Making his way to each corner of the room, he packed the generators into his bag which had been pushed to one side, out of harms way.  

Jay watched from above.  It wasn't that she was attracted to Oken, she just found his character so interesting.  She had been waiting for an eternity to be assigned an Oken fight, knowing that she could explain the fighter in intricate detail.  Now, after his surprise exit, she was lost.  Maybe he wasn't the man she thought he was.

Her predetermined descriptions of fire and rage that were to leave the fighters mouth were gone.  She had nothing.  She took a deep breath and decided that it was time to talk to Oken about it, face to face.  She walked down the stairwell and found him unplugging his precious generators.  As she got close, the crowds encircled her in their endless dancing.  When the path cleared again, he was gone. 



\thoughtbreak



Oken walked down the street in the twilight with a slow majesty that had become more or less a trademark of his.  He looked back at the place where he had just performed the impossible and smiled a simple little smile.  The event had been over quicker than he had imagined.  He hadn't wanted to leave the platform.  He had wanted to stay isolated down there, watching the crowds shout and cheer from afar.  He had never liked being in tight spaces.  Indeed, a few times after he had fought, the platform had seemed to be the place he felt most at home in.  It was so large and spacious.

Jay opened the back door and saw Oken up ahead.  She ran to catch up with him and he made no attempt to outrun her.  She finally reached him and Oken was surprised that it had taken her so little time.  He could hear her high heels tapping on the concrete surface, making a rhythm that sounded somewhat unnatural.  He slowed.  Out of the corner of his eye he noticed the pale coloured clothes that she was wearing and noticed too that she had some kind of recording device in her hand.

``I'll speak to you,'' he said, ``but not with that thing running.  I want you to work for your report.''  Jay smiled.  She was already beginning to see that his quick exit had been a deviation from his normally humorous and sarcastic nature.  She started to say something and paused, her mouth half open.  She closed it and started again.

``That was quite a show you put on there,'' she said.  A compliment never went unheard she had remembered her journalist lecturer saying.

``So what was wrong with your first question?''  He asked.  Damn it.  She didn't think he'd heard the almost silent whisper that had escaped her lips.  She guessed she shouldn't have made such rash assumptions about a man as knowledgeable as Oken.  She was sure it had been drowned out by a passing car, but quickly noted that it would be in her best interest not to assume things from this point forwards.  

``You still not thought of an answer?'' said Oken.  She hadn't realised it had been that long, but from the tone of Oken's voice she guessed it must have been at least ten seconds.   She went to answer but realised that to her horror, she had forgotten the question she had been asked.  She decided it was time to change tact and for her to begin a new line of questioning.

``How did you come up with the idea of making a temporal weapon?'' she asked, almost grinning to herself at the cheekiness of the question.  All at once he was in front of her and this time, it was not due to the use of temporal weapons either.  It was due to Oken's unmistakable speed and the fact that Jay had been looking down at the road while they walked.   Oken hadn't meant to make physical contact with the delicate young woman, but he found himself holding her arms by her sides, against a wall.

``Don't you ever say that out loud in public again,'' snapped Oken.  Though she had meant the question to be of a fairly intrusive nature, she had not realised just how dangerous it was to say the 't' word in public.  She decided quickly that she would have to be exceedingly careful about what she said from now on and offered up a humble apology.

``I'm sorry,'' she said.  Oken nodded in acceptance and the two of them continued on together in silence until they reached the end of the road.  

Oken loved the summer and in particular the summer evenings.  This particular evening was quiet, all except for the children running around in the park just ahead and the parents yelling after them from the comfort of the dozen or so benches which lined the edges.  A car came up behind them and slowed beside them.  It was Ruben, the fast blend of techno and electronic trance blaring out of the unmistakable Lotus sports car.

``Need a lift my man?'' asked Ruben, shooting a wink at Jay.  He crawled slowly alongside the pair and started making kissing noises.

``I'll walk. Thank-you Ruben,'' said Oken without looking at him.  Ruben couldn't see his face but Oken was smiling.  He found Ruben's sense of humour hilarious.  

``Now I know why you were in a hurry to get out so fast,'' Ruben exclaimed in an all knowing voice.  The bouncer was still hanging out of the window and Oken turned to him with a grin and said,

``You'd better watch the road Ruben.  Don't want to be knocking over any old ladies now do we.''  It was only then that Oken was reminded of the young girl he had seen earlier, and secretly scolded himself for the remark.  Ruben chuckled to himself and took the hint.  He pressed the button to wind the window up and drove off in a cloud of dust that gently rose and seemed to hang in the dim evening air.  Jay had secretly been pleased that Oken had declined the lift, even though she would never have revealed it.  She still wasn't sure about Oken, he seemed harmless enough but she could not let herself forget that finishing blow.  It had been so calmly executed that for a moment she wondered if Oken had been a hit man in a previous life.    

They rounded the next corner in silence and Jay saw some steps leading up to a tall apartment building.  Oken sat down on the steps and gestured for Jay to do the same.  She felt a little uncomfortable at doing so but she needed the information for her report.  Oken turned to her and spoke.  ``I'll let you come up to my apartment providing you keep that recorder switched firmly off.''  Jay had not been expecting such an invitation but understood that Oken was just trying to help her out.  She nodded silently.



\thoughtbreak



Oken's apartment had a strange smell to it which Jay found rather intoxicating.  Unbeknownst to her it was the smell of the many temporal and electromagnetic shield generators which were happily humming to themselves, protecting his life from the G-TEP pigs.  The sound they made summed up to a quiet whisper and Jay stood in the middle of the room examining the apartment in minute detail.

The first thing she noticed was the wooden floor.  It was so shiny that she could see a partial reflection in it.  The wooden theme continued onto the tables and chairs too.  Jay had always liked beech and suddenly felt rather jealous of Oken's abode.  He offered her a drink but she declined.  He motioned for her to sit down on the plush cream coloured sofa which stood on its own feet on the wooden floor.  She did so.

Oken decided after five minutes of silence that it would probably be better if he started the conversation, since she had made no attempt to do so.  In all fairness, neither had he, but that wasn't the point.

``It started out as a daydream,'' he said.  ``One day I was sitting here all alone watching some classic films. It was about two weeks after joining the Zone, and the idea just came to me.  I started looking it up in books at the library and it grew from there.''  He saw her nod and start to hurriedly write down notes on her electronic notepad.  Oken drew in his bottom lip and bit down gently.  He saw the way her arm darted in quick flashes of movement and the way her hair hung in a curtain that covered her face.  He could not see her expression; it was one of sheer panic.

After a short while, Jay settled into the interview, never leaving the corner of her seat.   She even allowed herself a few laughs at Oken's many psychological jabs at his former self.  It was a gentle evening and even Oken was having fun.  He told her about the time he had messed up a temporal reactor and the blast had removed his eyebrows leaving him with a very difficult explanation to find before 9:00am the following morning, when he started work at the library.  He told her many more stories too, all to be kept strictly off the record.    These were his exact instructions.  

For some reason he felt he could trust her, her face so sincere and friendly.  He wondered how on earth she had wound up in a place such as the Zone and ventured the question.  She told him that once when her brother had gone out to one of his 'secret meetings', she had followed and had immediately fallen in love with the atmosphere.  Later when she had taken up journalism, she had decided to use the Zone as a practise run before getting a real job.   Oken had laughed at the words 'real job' and reminded her that he was twenty-nine and still worked in the library as a book stacker, but he could not shake the feeling that she had been a little hurt by his chuckle.  

By the time Oken looked at his watch it was a little after eleven thirty and he pondered on how quickly the time had passed by.  He remembered the old phrase of 'Time goes quickly when you're having fun,' and allowed himself the possibility that maybe he had had more fun than he had originally thought.  Jay was looking tired.  She had stopped writing about forty minutes ago when the conversation had taken a more informal turn.

After an exchange of goodbyes, Oken closed the door and Jay walked away, stopping once and looking back to see if he was looking back at her.  He wasn't, at least not with the door open.  He was actually on the other side, peering through the peep-hole of the antiquated building.  He turned and leaned his back against the door  and smiled.



