\chapter{43}
\section{Ready To Go}


It was the day of the schools anniversary festival and Kiele and Zane had avoided each other for most of the weekend, but each for entirely different reasons.  Kiele had been unable to see Zane without the events of the Friday evening coming flooding back to her.  Now she ate alone, entirely isolated in her room.  She flicked the Monday morning breakfast around her bowl.  How would the class react?  Only last week they had been the most hotly talked about couple on the school campus.  Now they were history and Kiele was sure it would come complete with a package of ridicule and jest.  This time she wouldn't have her Zane to protect her.

Zane was thinking similar thoughts as he sat in the dining area with Mark, slurping up 'Captain Mc Eat-em-alls' most fantastic breakfast cereal.  In truth it was just another wheat based cereal, but Zane had fallen in love with the stupidity of the cereal's mascot years ago and refused to let go.  How was he going to cope today?  He so dearly wanted to continue looking after Kiele, but she had made it deathly clear that they were not to be seen together again.

Zane clicked his neck left and then right, drawing a nod of acceptance from Mark.  The two of them hadn't spoken much during breakfast.  The boy could sense there was something Mark wanted to tell him, or something he was expecting to hear from Zane but he couldn't put his finger on what.

The pair had worked relentlessly on the device over the weekend, much of it spent redesigning the ORT power GOs.  Now the machine lay ready for inputting the final parameters and running a full scale test.  Mark had insisted they wait until today for this, but had thanked Zane for his sterling efforts in fixing the spike problem.  It really had been a sticking point in their research and with Ric phoning Mark every day to complain that the task hadn't been completed yet, it felt so good that he was going to be able to ring him this morning and offer him the good news.

Kiele appeared in the doorway to the kitchen and grabbed some food from the fridge without saying a word to either of them.

``Kiele,'' said Mark, ``just because you're in a grump doesn't mean you have to take it out on the rest of us.''  She saw red and turned sharply to fire off a retort.  This time she would tell the truth.  She had never felt so angry in all her life.  There was Mark sitting in his little chair eating his cereal like nothing had ever happened.  He was the reason she was in this 'grump'.  He was the reason she had been confined to her room for the entire weekend.  

She hadn't noticed that as she had turned, her bag had caught a glass which had been sitting on one of the ledges.  It flew from its stationary position, performing an impressive series of flips and twists as it shot across the room.  The rim of the glass was the first thing to hit the cupboard over the other side of the kitchen, but the strength of the circular shape wasn't enough to keep the structure from buckling.  Waves of stress galloped around the transparent cylinder before suddenly exploding it.

Usually Kiele would have cleaned it up.  Today she just didn't care.  Usually she would have been almost on her knees apologising to her father.  Today she just turned and walked out of the room.  The glass had said all she wanted to say, the explosion of anger still rippling around the kitchen.  Mark didn't shout after her, or scream at her.  He just sat there, munching on his cereal as Zane tried to figure out exactly what was going on.

The young boy rose from his seat, having finished his breakfast, and picked up a dustpan and brush which had been sitting nearby.  He started to sweep up Kiele's anger into the pan, but Mark called over to him.

``Leave it Zane,'' he said, ``I'll clean it up in a while.''  Zane looked back at the man who was sat there still half eating, half talking.  He wasn't looking at Zane at all, he was studying his toast.  ``Go on,'' the father figure said, ``get going or you'll be late.''

Zane nodded and put what he had already scooped up into the bin, carefully resting the pan and brush against the side of a cupboard.  

``Nice blazer by the way,'' called Mark as Zane left the room.

It was clear that Kiele had already left the house and now Zane had the difficult job of trying to catch up with her.  She was small, but she was also pretty damn fast.  He wanted so desperately to try and set the record straight before they got to school, otherwise it was going to be hell for them both.  Despite what she had decided, Zane still felt an overwhelming desire to protect her.



\thoughtbreak



He felt hot in his new celebratory attire, the black trousers and black blazer absorbing all available heat around him.  He felt like he was literally cooking inside.  Up ahead he saw the figure of Kiele, walking as fast as ever.  He quickened his pace, turning it into a slow run.  As he caught up to her she looked behind and saw the man she still loved.

``Zane, just go away,'' she yelled, still coursing down the pavement at her top speed.  She really didn't want to talk to him now.  It wasn't as if anything could be salvaged or fixed by talking.  She had been given her orders, failed once and been severely reprimanded.  As she continued in her efforts to outpace Zane, the cut in her leg began to stress.  It was sore and having to walk at this speed wasn't helping.  

Zane continued to trail just a little bit behind her, unaware of her injury or its cause.  They took a few more steps before Kiele felt the urge to again tell him to desist in his chase.

``You have no idea how much you're hurting me right now,'' she said truthfully.  She was of course, referring to the pain in her leg and not her heart, the latter of which she had managed to suppress for now.  He continued to follow her in complete silence.  

``Zane! For crying out loud, leave me alone.''  Her voice was almost screaming now and several passers by on the other side of the road stopped to look at the arguing pair as they sped down the road.  She could take it no more and decided she would have to face him if there was to be any chance of walking to the school by herself.  She spun around and was instantly gripped by both a pain in her leg as her cut ripped open, and the arms of Zane as her delicate legs gave way from the pain.  

She looked up at him.  He was smiling sweetly at her.  If she hadn't known any better, she would have sworn he had planned the whole thing.  However, it wasn't planned.  Zane hadn't known about the cut, but he had known he needed to be near her.  It was a calling, a destiny.  



\thoughtbreak



``And you're sure it's ready to go?'' he asked Jessie once more, almost as if he had expected the answer to change in the last five minutes.  

``Quit asking me,'' said Jessie.  ``If I say it's ready to go, then it's ready to go.''

``You know I have to be sure,'' said Ric.  His voice had changed a little in tone since the last time Jessie had spoken to him.  He seemed to almost respect the little weasel for actually completing the job like he had asked.  It had taken long enough, but Jessie seemed to have finally pulled through.

``So, we go this evening?'' asked Jessie after a short pause.  He sounded a little nervous and Ric could sense it in his voice.  Was he scared?  He sure as hell should be.  What they were about to do was to change history, to change everything that had happened since the forming of the Emblem.  Ric had no idea if they would even still be alive after tonight.

He took a moment to muse on his train of thought.  After tonight?   The phrase made no sense.  The event wouldn't occur after tonight.  Did this mean it would never take place?  Would that create a loop?  He had no idea.  His brain unable to cope with the problems and intricacies caused by temporal paradoxes.  To be honest he didn't really care.  He had risen through the ranks by being ruthless and efficient, not by being book smart.

Ric sat there in his office on the fourteenth floor of G-TEP HQ.  Being a high ranking officer, his office was never under surveillance.  He had been trusted.  He was trusted.  Whatever he did in that office was deemed necessary for the continued existence of both the G-TEP and the Emblem.  

His desk was made of marble, the top anyway.  It shone in the bright lights, dark, with a hint of grey.  The spotlights adorning the room created an almost clinical feel.  Ric had enjoyed his time in the field, but up here, he was like a general with an army.  If Ric said crush, then crush it was.  If Ric spared the life of some innocent, if was because he himself wanted to.  In essence he saw himself as a god.

The sunlight tried to stream in through the window, blocked by the anti-light coating on the toughened glass.  The rays bounced off the outside, making the building shine in the mid morning sun.  It was an architectural masterpiece and could be seen for miles around, even amidst the other buildings set in the governmental area.  It served as a pillar for the focus of justice and peace, towering over the small building of the police department which lingered in its shadow.

Though there were rarely temporal incidents any more, the G-TEP had still managed to keep hold of practically all of its government funding.  This year in fact, had seen an eight percent rise in the money sent its way.  Both the G-TEP and the government seemed unable to shake the feeling that something may happen, at some place, at some time.  Temporal analysts worked all day everyday continually plotting out probabilities, researching events, historians of the modern age, of the future.  

The phone in Ric's hand felt warmer somehow now.  Ever since Jessie had informed him of his success Ric had been unable to stop smiling.  He was going to rewrite the history books.  Undo everything that the sorry excuse for a government had done.  He was going to be praised by the universe for his astuteness.  

If his plan went correctly he would destroy every single temporal device in existence.  He would destroy everything he had been fighting against, every scrap of resistance.  Losing his life in the process was merely a by product.  His ultimate aim, his dream was coming true.  Let the Emblem divide.

``Yes, we go this evening, the time-line foretold it'' said the general.  ``You however, must leave this afternoon to set up the train accident.  If you don't, you risk causing a paradox.''  Jessie mumbled something about agreeing with him.  ``It's fine Jessie,'' said Ric in an almost fatherly tone.  ``You will do us proud.  Just go to the coordinates marked in the instructions and carry everything out as described.''

``You're sure it will work?'' said Jessie nervously again.

``I'm positive,'' said his partner.  ``There is some talk of an explosion causing the train to derail.  I've had my analysts look into it and we firmly believe this to be caused by an exploding transformer box.  In the primary cabin.''

Jessie nodded, saying nothing.  Ric certainly had a way of planning things down to the last detail.  

``You did get the instructions?'' he asked Jessie.

``Yes, I encrypted them myself,'' he replied.  

``Good.''

The conversation was running thin.  There appeared to be nothing more to say.  Jessie began pacing the room, head down apparently looking for something on the floor.

``Jessie, I want you to contact me once more to tell me everything is OK after you return from the train.  Then I will visit you and together we will end this.''

``OK,'' said Jessie solemnly.

Ric would have dearly loved to go along for the initial ride, to keep an eye on Jessie, but he knew he had things to prepare.  He had to make sure their attempts would go undetected.  He had to be there to intercept questions.  Jessie would never have been trusted to dismiss any kind of temporal activity.  Ric on the other hand?  He just had to wave his magic hands and it would all go away.

``There's nothing more to say now,'' said his master.  He paused before adding, ``Let the Emblem divide.''

``Let the Emblem divide,'' said Jessie nodding.

The little boy hung up his phone.  Was he really ready for this?  Was he really ready to go back in time?  His heart started beating faster.  He guessed he already had been ready.  Assuming it was really him who set up the train accident, he would most certainly go back in time later that day and attempt to kill his daughter.  Some quirk of fate prevented her from dying.  Had it been Zane?  His pushing her out of the way?  Jessie didn't know, but he knew one thing, everything was lining up perfectly.  The Emblem would indeed divide.



\thoughtbreak



``Thanks,'' she said.  The words slipping out without her attaching any real meaning or sincerity.  It was a reflex reaction as opposed to a heartfelt appreciation.  She held her leg and pressed the wound.  She winced in pain.  It still hurt a lot.  A small amount of blood was now seeping through the bandage and onto her skirt.  Zane noticed it.

``When did you do that?''  She closed her eyes and sighed.  Instantly she knew what he was talking about.  She couldn't tell him.  If Mark found out she really would be history.  

``It's nothing,'' she said.  ``I just cut myself shaving is all.''  

``Doesn't look like a shaving cut to me,'' said Zane blatantly.

Kiele was getting tired now and she just wanted to give in.  She wanted so desperately to tell him everything.  She could feel the urge pushing her forward, almost as if it were no longer a desire, but a basic need.  The young girl suppressed it.  Now was not the time.  Yet it kept coming back.  Maybe if she told him, he'd understand.  Maybe he would be able to protect her still.

``Zane,'' she tested the water, ``You trust me right?''

The boy wasn't sure exactly what was coming next.  Sure he trusted her, but what was she about to ask of him?  She had already broken his heart.  Inside the words meant nothing.  He still hadn't accepted her gross misconduct the other day.  He had forgiven her, but not accepted it.  Though he made no outward signs that would suggest otherwise, he was still very much in love with Kiele and believed wholeheartedly that she still loved him too.

``Of course I trust you.''

``Zane this is going to be really difficult to hear and,'' she looked around before lowering her voice and abruptly finishing her previous sentence.  ``Not here.''

Kiele took hold of Zane's arm and began to run clumsily forward in the general direction of the college.  Zane couldn't quite believe what was happening.  It had been such a turn around.  Her personality had changed entirely.  He knew she loved him.  She would tell him as much now he was sure.  

They ran through the narrow busy streets and out into the park area.  Kiele's leg was hurting ferociously now.  She refused to let the little cut stop her from breaking free of her father once and for all.  She was really going to do this.  She was going to tell Zane everything.  The plan, his vicious attacks, everything.  If he believed her, she would be able to be with him forever, they could run away together.  She wouldn't ever have to see Mark again.  

If he didn't believe her?  She would in all probability be killed.  She didn't care.  Her mind was set.  Living wasn't living if she was forced to do his bidding for the rest of her life. Living wasn't living if she couldn't hold the man she loved.  Living wasn't living if....  Her mind trailed off.  She noticed a wooded section off to her right and zigged into a new direction almost knocking Zane off his feet.

He managed to follow her, still holding her hand, that warm inviting feeling flooding his body once more.  Where was she taking him?  Though they were under the cover of bushes and trees, Kiele still felt it necessary to run.  It was as if she were trying to outrun her father, trying to leave him for safety.  She was going to put all her eggs in one basket now.  She was going to stand up to him for the last time.  It was life or death.  Zane would decide.

They continued running.  As she pushed a branch out of the way, it sprang back and hit Zane squarely in the face.  He stopped dead, almost pulling Kiele over when their arms went as taught as rope.  

``Enough,'' he said.  She looked back, at him almost wounded.  Why wouldn't he follow her further?  She noticed the red mark now appearing across his face and immediately realised her mistake.  She had been so intent on getting as deep into the woods as possible that she hadn't thought once about Zane.  Yet again her father had taken precedence.  

``What ever you have to tell me, here is fine.''  His words seemed so final.  Devoid of love, yet caring all the same.  He wanted some answers.  He looked at the girl as she sat down on the dirty floor.  She was nervous, he could tell that instantly.  She looked shifty, like someone who has just robbed a bank, or been caught red handed.

``Zane,'' she began.  A twig snapped under his feet and her head shot up towards the location of the sound.  'Just what was making her so jumpy?' he thought.  

``Zane, I don't even know how to tell you what I have to say.  You're probably not going to believe me, but in all seriousness if you don't I'm dead.''

``What are you talking about Kiele?'' he said, almost ridiculing her statement.  ``Do you realise how ridiculous that......''

``Just shut up and let me speak, this is hard enough as it is.''  Her voice cut through him as it had done the other night and suddenly Zane began to take her seriously.  He sat down opposite her and looked directly at her.  She was having trouble coordinating her thoughts with her speech, unable to begin.

They sat there in silence for several minutes before she mustered up the strength and coherence to speak.  A light breeze dusted the leaves with it's presence and prickled the back of her neck.  She looked up and their eyes met once more.

``Zane, I've lived my life in fear.''  He looked confused.  ``For a long time I've lived fearing the one person from whom I should have been able to ask for protection.''  She broke away from his gaze.  ``My father.''

``Why are you so scared of him?'' he asked, a little too hurriedly.  It caught her off guard, and she started to shut herself away again.  Her mind unable to cope with the pressure of disobeying Mark once more.  Zane had started to be come a little like her father and sitting here now, talking to him, reminded her of talking to her father.  He was being too rough with her emotions, she just couldn't take it much more.

``He's not the man you think he is,'' she shouted at him.  

He yelled back, ``And he's not the man you think he is either.''

It was a mistake.  He could see tears beginning to form in her eyes.  She was getting distraught.  He hadn't meant to yell, just something inside of him had wanted to stand up for Mark.  They had gotten to know each other well and Zane respected the man for his work, his career, his drive.  

Kiele decided to try one more time.  ``Zane, my father has a plan.  Something he thinks is monumental and he asked me to.........''

The young man looked confused once more, his brow furrowed and his eyes narrowed.  ``Kiele, what do you mean?'' he said interrupting, ``I know what his plan is.''

``You do?'' she asked.  It was the ultimate insult.  She, his own daughter, hadn't been thought worthy enough to know the plan, yet here was Zane, a relative outsider, who apparently knew everything.  It sickened her.  She almost tried to make a run for it there and then, but feeling the stabbing pains returning to her leg rethought her idea.

``You want to know what it is don't you?'' he said.  

She looked at him and nodded.  Eyes filling once more, her body yearning to hold the man in front of her.  She wanted to know so desperately what it was that had caused her so much physical and emotional pain through the years.

``I'm sorry,'' he said, ``I can't tell you.''

The tone was soft and loving, yet it was as if by speaking the words he had reached into her very chest, taken hold of her heart with fingers and thumbs in a delicate grip and, like a piece of tissue paper, torn it apart.  'He cared more about Mark than he did about her,' she thought.  She was racked with despair.  The only man she had ever loved was beginning to turn out just like her father.  Anger rose inside of her and with her last effort she struck out.

``Did you know that our relationship was part of his plan?''

The tone was full of malice, sadness and resentment, yet Zane heard none of those, only the actual words themselves mattered to him.  She could have said them in the cheeriest of ways, and it would still have thrown him backwards.

Zane hadn't been expecting it.  Suddenly it made complete sense.  Had she never really loved him at all?  Had it all been an elaborate rouse?  It was true he probably wouldn't have helped Mark had he not been involved with Kiele.  Was she telling the truth?

He sat in stunned silence.

``What he didn't count on was that I would fall in love with you,'' she continued, but the words seemed to fall on deaf ears.  Zane was still beginning to process the first piece of information.  In some ways so was Kiele.  She had really disobeyed this time.  It hadn't been an accident, but a conscious decision to let Zane know exactly what had been going on.

``And you just went along with it?'' he said, beginning to lose control.  ``And you just played the part like a good little girl?''  His eyes had become like fire.  He was angry.  He'd risked his life for a faking little witch.  She'd never really loved him at all, he could see it now.

``No Zane,'' she said.

``You followed his orders,'' he shouted, pointing at her.  ``That makes you just like him.''

He got up and began to walk away.  Kiele was distraught.  She called out to him, but he ignored her.  She screamed his name, and in frustration beat the very ground she was sat on.  Yet it didn't bring him back.  She cried, big round tears that fell to the ground like buckets of water, coating the dry soil with nutrition.

She lay down and wept.  It was all over.  Soon she would be dead.  There was no point fighting any more.  He would find her, and he would kill her.

