\chapter{28}
\section{}
Really Good Book  

Zane's condition improved over the next hour or so and by midday he was chatting happily with his visitors, making jokes and embarrassing Kiele.  He was on his way to making a full recovery and much quicker than expected it seemed.  Already he'd been talking about getting up and walking, but the nurse had warned him she would have to bring out the straitjacket if he tried to do anything other than rest.

Kiele was happy, it seemed Zane really was going to be OK.  After the incident in the ambulance and the surgery, she had been fearful that her hero would never awaken.  She had to be careful now.  Zane was clearly falling for her, she was a woman, she could tell.  The words of her father still ringing fresh in her mind.  His threat had been real, if she disobeyed she would have an 'accident' a serious 'accident.'  Was she clever enough to satisfy both criteria successfully, loving Zane and keeping her father's wishes?  How difficult was it to hide smite anyway?

The two girls had been for lunch and were now returning to Zane's room.  As they paced down the long corridor, Kiele noticed nurses running towards his room carrying all manner of apparel.  Something was wrong.  Seriously wrong.  Doctors were now arriving too.  The young girl slid down to her knees and grappled for Jolie's hand to steady her.  She couldn't take this any more, the too-ing and fro-ing was getting too much.  Jolie walked forward and broke away from Kiele, she ran towards the room and looking up, Kiele could hear her shouting 'What's happened?  What happened to him?' but she heard no reply.  

Had her father found out what she really thought of the boy?  What was wrong with him?  He'd seemed so much better when they had left.  It was hard for Kiele to think of anything other than the worst.  It seemed as if fate was playing a cruel trick on her.  She already had to deal with the threats from her father, and the accident.  Now it seemed as if Zane wouldn't make it through the day.

The nurse who had attended to Zane prior to lunch ran towards Jolie.  They exchanged words and Jolie clasped her hand to her mouth and walked slowly back to Kiele.  As she reached her she knelt down.  ``It's not him,'' she said to the worried young girl, ``it's not Zane.''  

Kiele looked confused.  ``Are you sure?'' she asked in disbelief.  Her mind had raced through so many possibilities for the cause of Zane's demise, several involved her father.

``I'm sure,'' she said.  ``He was doing so well that they moved him to a different ward.''  Kiele looked up to the heavens in obvious relief.  She closed her eyes, let out a huge sigh, and swallowed hard.  Jolie hugged her tightly and the two sat there for a second, reeling from the shock of the gut-wrenching moment.

The nurse walked up the corridor and helped the two young ladies up, ``I really do apologise,'' she said.  ``Someone was supposed to come and inform you that he had moved.''  She was genuinely sorry.  The nurse hated the way people seemed to just forget things they were told round here.  The member of staff decided she would escort them down to see Zane, it was only fair after what the hospital had put them through.  



\thoughtbreak



Zane was now in a ward with other people, and not in his own room.  It made him feel a little self conscious and nervous, something he wasn't accustomed to feeling for such long periods of time.  As he turned his head, he noticed Jolie and Kiele coming through the doorway.  Previously he had been looking out of the windows at the city below.  The hospital was up on a high ridge and Zane had managed to sweet talk a nurse into giving him a position next to the window.  His cheekiness was returning all right.

He found it odd that a hospital would be built in such a vulnerable location.  They didn't experience many earthquakes in Alendria, but he still found it odd to position a building of such importance on what he considered unstable ground.  Planning permission had been sought in a rush, bribes exchanged hands and the hospital had been built, but of course, Zane had no knowledge of these events.

The boy beamed as he saw his two favourite people in the world coming to visit him again.  He had felt so lonely when they had gone to lunch.  They had promised to come back but Zane hadn't held out much hope, he thought it was a tactic to allow them to escape, but they seemed quite content with spending their entire Sunday by his side.  It warmed his heart no end.

An old man in the bed opposite saw the two young women walk up to Zane, Jolie gave him a hug and Kiele leaned over and very gently kissed him on the cheek.  ``I wish I had your visitors'' he shouted across the room.  The woman sitting next to him, obviously his wife, hit him with her handbag before exclaiming, ``Well you're married to me so be thankful for what you've got.''  Zane laughed, or tried to.  His body was still sore from surgery and every part of him just generally hurt.  It wouldn't have been so bad if he could reach the damn itch on his foot.  They both sat down.

``How are you feeling?'' asked Kiele.

``I'm OK,'' he replied, ``I'm always OK.''  It was a lie, but Kiele knew the sentiment.  No one ever really wanted to know how people were feeling.  

``Come on,'' she said, ``how are you really feeling?''

``You've opened up a flood gate,'' he joked before reeling off a huge list.  ``My back is killing me, the skin on my chest is burning off, my foot itches, my eyes are sore, my shoulders feel like someone has been standing on them and I managed to throw up on that pretty young nurse over there at lunch time.''  At each item in the list he had tried to indicate it with his hands, as if talking to someone who was entirely unfamiliar with the human body.  

Kiele had resented his description of the nurse as pretty.  Surely she was the only pretty one there?  Her thoughts were put on hold as she turned to look at the woman Zane had been referring to.  She was a large woman, in her early fifties Kiele supposed, not that there was anything wrong with that, but she could tell immediately that she was not the young, pretty nurse Zane had been describing.  She smiled.

``Had you going on that last one didn't I?'' he said gleefully.

``You didn't throw up?'' she asked.

``I meant more about the young and the pretty,'' he replied, ``I threw up good.''  He smiled a knowing smile and as he did so, his good friend the nurse looked round.  He shot her a wink and she scowled at him before storming out of the ward.  ``I think I've made a friend there,'' he said softly, before wincing in pain at turning over.

They sat there in silence for a few minutes.  The afternoon visiting period had just begun and many of the other patients on the ward were receiving visitors too.  Some hugged their loved ones, some sat down and held their hands, one or two had to be quiet as their friend or family member was sleeping.  A soft breeze was blowing in through the open windows at Zane's end of the ward.  The old man opposite was still transfixed on the beautiful women who were sat out of reach before him.  

``We were really worried about you Zane.''  It was Jolie who had broken the short silence. 

He smiled at her, ``it'll take more than a speeding train to stop me.''  Though he was joking, Kiele could see how seriously the incident had affected him.  He had never considered his own mortality before, he had never considered that he may die so young.  He had always felt invincible and it had always seemed to him that you had to hit a certain age before death became possible.  To Zane, death was a function purely of age.  The older you got, the more likely you were to die.

As she sat there, Kiele once again felt the book weighing her down, coincidently Jolie was also feeling pressure.  She had to ask Zane about the writing on the train.  If not for her own sake, for Ruben's.  Kiele reached into her bag and pulled out the small package.  

``This is for you,'' she said.  She refused to tell him it was from Mark, but then she also didn't want to lie to him.  Her statement gave no extraneous information away, whilst maintaining the criteria of not lying.  It was true the package was for him, but she hadn't bought it, she didn't even know what was inside.

``Thanks,'' said Zane.  

``Aren't you going to tell him it's from me?'' came a voice from behind them.  

The girls had been so intent on Zane, that they hadn't noticed Mark walking up behind them.  Zane too had been engrossed in either conversation or trying to pull off his hospital tag with one hand.  Mark was standing there in jeans and a rotten tee-shirt.  Holes were appearing in multiple locations, but he didn't care.  The girls sat there dumbstruck, Kiele especially.  She hadn't expected to see her father at the hospital again.  

``Thought you may enjoy it,'' he said smiling, ``open it later.  OK?''  Zane nodded and put the package to one side.  Kiele was angry now.  She had been waiting for hours for him to open the package and see what her father had bought him.  Having said that, this was Mark they were talking about, he would have probably found the most disgusting looking old book he could and wrapped it up for a joke.

Mark looked over at Kiele and touched her gently on the shoulder.  She flinched slightly but not so that anyone other than Mark noticed.  ``Can I have a moment of your time young lady?'' he asked.  She was looking at him now and his eyes had started to make holes in the back of her head.  She nodded slowly and the two of them got up and walked away.  Slowly at first and then their pace quickening.

Jolie sat there looking at the recovering student.  Though she didn't mind visiting him, it would have been so nice if he had had some family to look after him.  As she pondered their being alone, the question Ruben asked once again started pushing in her mind.  If she was going to question Zane on it, now was the only opportunity she would have for a while.

``Zane,'' she started.  He ceased trying to break the hospital tag again and looked up at her.  ``I have something to ask you.''  She began to lay out her emotional landscape, ``But if you don't want to talk about it that's fine, and it's going to sound a little odd, I'm sorry.''  She looked down and recomposed herself.

``Zane,'' she started again, ``did you happen to see any writing on the train?''  He frowned.  What in heaven's name was she talking about?  Writing on the train?  She fleshed her question out, ``I don't know, anything painted or sprayed.''  He began to slowly shake his head, still frowning and totally in silence.

All of a sudden his body jerked and his eyes widened.  It was as if he was suddenly in intense pain.  In truth, he was just having a profound moment of realisation.  

``I remember something, it was red.  All in red.'' he said.

``Go on,'' said Jolie.

``Guess I can......'' he trailed off.  ``Something about football.  Does that sound weird?''  

She shook her head.  ``Not at all.  Anything else?''

He tried to recall the memory once more, ``Guess I can go watch football instead,'' he said completely.  ``That's it, that's what was written.  How did you know Jolie?''

He looked confused.  Jolie had expected this.  After all, if someone was hit by a car and friend asked if there had been a message on the front it, what would the victim think?  It all seemed rather suspicious.  Zane asked again.

``Jolie?''

``It was a question the police asked'' she lied.

He nodded and turned to look out of the window again.  They were up on the third or forth floor now and several birds flew past the texiglass windows in infinite grace, their wings hardly even flapping, just gliding down to the city below.

Though he was feeling more comfortable now, he just wanted to go home.  His body was tired all over and he longed for his own bed in which to relax.  The government medical insurance wouldn't last long anyway.  He would be out in a week maximum.  Unless he was on his death bed, they would try their best to get rid of him.  Now that he thought about it more though, he wondered if Kiele would give him the same amount of attention if he were at home.  



\thoughtbreak



Outside the ward Mark and Kiele stood knee deep in repugnance.  Mark had visited the hospital to make sure of two things.  He needed to see that Zane had received his gift, the starting point of their friendship.  He also needed to ensure that Zane knew it was from him.  His task was complete, but he took the opportunity to remind Kiele of her place once more.

``How is he?'' asked Mark.  

``What do you care?'' she snapped back fiercely.  It had been a mistake.  Mark hadn't started off aggressively, maybe now he should change tact as the young lady was obviously looking for a fight.

``Cut it out Kiele,'' he said.  He was serious and though they were just standing in a corridor, she still felt vulnerable.  These people couldn't save her.  Neither could Zane.  She decided to cooperate.

``He's doing well,'' she said.  ``He's woken up fully now.''

``Any brain damage?''

``Not that they can see.''

It was good news.  It had been troubling Mark since the accident.  He needed the boy, the accomplished physicist.  If anyone could make the damn thing work it was him.  Mark nodded.  There was a short silence.

``Don't distract him from his reading, understand.''  She sighed and nodded at the same time.  She was sick and tired of his plan.  He turned and walked away.  Not even asking once how she was, or whether she would be home for dinner.  He didn't care.  It was the honest truth.  She turned and walked back into the room.  At least she hadn't been thrown against a wall this time.

