\chapter{23}
\section{Mt. Taleberg}


As they sat there in the taxi on the way home the world seemed to whizz by in a blur.  It had been a long day for both of them.  Jolie had visited the legend that was Ruben and had been called away because two of her students had been involved in a horrific accident.  Kiele had been in that horrific accident and survived with little more than a few scratches and a bruised neck.  They were both tired and as they sat there Kiele could almost feel herself nodding off.  

The taxi had been painted green by the owner of the fleet.  Looking to make a statement, each taxi in the fleet had been painted its own unique colour and had the name of the colour inserted into the phrase 'The **** Taxi', which was visible in large letters on the side.  They were riding in the 'The Green Taxi' right now and though the ride was smooth, the driver was going a little too fast for Jolie's liking.  It wasn't like he was about to crash, Jolie just much preferred taking things at a nice easy pace.  

The interior of the taxi was nice, decked in a plush cream ripstop leather with wooden accents.  It felt like they were riding in a limousine.  She guessed that's what the owner of the fleet had been trying to capture and in her eyes, he'd done a fantastic job.  The cars were classy, yet purposeful.

``Is everything OK?'' Jolie asked.  She'd hardly had time to think before the words came tumbling out.  Kiele looked at Jolie, what did she mean?  Had she seen the way Mark had treated her?  Impossible.  Maybe she just had a good sense for these kind of things?  It was impossible to say for sure.

``Yeh,'' Kiele answered.  Had she believed it, she would have said it with a little more conviction, but as it was, she had replied in a rather weak tone.  Jolie picked up on this instantly and decided to try to press just that little bit further.

``If you need to talk I'm here,'' the teacher said.  ``I know sometimes it can seem like there's no one around to share things with, especially when people don't always act in the proper manner,'' she was of course referring to Mark.  She continued, ``but I want you to know, you always have a friend in me.''  She meant it too.  Though Kiele was not her daughter, the presence of a strong female role model in her life was something Jolie felt of great importance.  Kiele was silent.  She wanted to say thank you, but the Mark inside refused to let her.

``You don't get on well with your dad do you?'' asked the teacher, wondering instantly if she had gone too far.  She hadn't wanted to spook the girl, just help her.

``Who does?'' came Kiele's reply.  ``Everything's fine at home.  He just rubs me up the wrong way sometimes.''  Inside, Kiele's head screamed.  'You mean when he throws you up against walls?' it asked.  'Or when it tries to cut your eyeball open with a scalpel?'  She quenched the anger and sat there in apparent harmony with herself.  It wasn't as if she didn't want to talk, but the stern warning her father had given her about the educator was still very fresh in her mind.  It would take a lot to dissolve the memory of having you head rammed against a wall, and a scalpel almost slice into your eye.

Though Jolie knew she was hiding something, she let it go, not wanting to upset her or put the young girl through any more stress.  Jolie had known her for a few years now and though she progressed steadily, Jolie couldn't help but imagine how much further she could have gotten with the encouragement that she so desperately sought.

The taxi rounded a corner and Kiele's neck, still sore from the trauma, flopped over to one side.  It happened to be the side that Jolie was sitting and Kiele managed to catch it before it hit her.  Still, her head was at an odd angle now and she left it there.  After a few seconds she let it drift the rest of the way onto Jolie's shoulder.  



\thoughtbreak



Manufacturers, driven by the constant threat of financial meltdown, had tried to shave everything off the cost of production.  If this meant a less luxurious product, then so be it.  The consumers would understand they had assured themselves.  The manufacturer of the Taxi, a one Shubara Motors Inc, had made the assumption and had impressively managed to shave forty six percent off of the cost of production across all models.  This particular model had been a hit, with taxi firms.  Unfortunately the consumers didn't seem to understand so well.  Instead one manufacturer actually increased the cost of production of one model by thirty percent.  Against all the odds, it outsold all others by a factor of seven percent.  Incidentally, Shubara Motors Inc had gone into administration the next year.



\thoughtbreak



Jolie sat there with the young girl resting on her shoulder.  She wanted to ask her more, but couldn't bring herself to break Kiele's apparently peaceful mood.  Jolie hadn't ever seen her angry, but as the old saying went, 'if it ain't broke, don't fix it.'  Finally it was Kiele who broke the silence.  

``Do you think Zane could hear us?'' she asked the learned woman.  Though she already knew Jolie wouldn't know the answer, she hoped that her reply would insight some reassurance that Zane was going to be OK.  The doctors had said he would be fine, but he still hadn't woken up yet.

``I'm not sure,'' said Jolie with little reassurance.  ``But I like to think he did.''  She smiled and Kiele did the same.

The poor thing, thought Jolie, all she can think about was Zane.  She needed a break, something to distract her, just for a few hours.  It seemed as if she wasn't going to get much sympathy from home.  Without thinking she tapped on the divider between them and the driver.  The glass became transparent and suddenly they could hear the music blaring away in the front of the car.

``Do you think you could drop us off at the commercial district instead?'' asked Jolie loudly.  The driver nodded, whilst singing the second chorus of Metallica's 'Unforgiven II'.  For a brief second Jolie was unsure whether he was head banging, or whether he was nodding.  He complemented his actions with a thumbs up for confirmation and once again the divider became opaque.  

``What are you doing?'' said Kiele angrily.  Jolie hadn't expected such a fearful reaction.  ``My dad said I had to come home at ten!''  

Kiele clearly wasn't thinking properly and Jolie calmly replied, ``It's only just gone five.  We have plenty of time.''  Kiele calmed down and looked at the watch; Zane's watch.  She had put it on her wrist for safe keeping, fully expecting to give it back to Zane that very afternoon.  Jolie noticed it and commented, ``that's a very bulky watch isn't it?'' 

``It's Zane's,'' she said, ``Kaitlin gave it to him earlier.  He was so excited.''  She hung her head a little.  ``He's gonna be mad if he wakes up and finds it gone.''  And just like that they were back to Zane.



\thoughtbreak



The young man in bed fifty eight stirred again.  His monitor beeped erratically for a few seconds before settling down to normal.  The nurse had been in not five minutes before, plumping pillows and arranging flowers.  The room looked really relaxing and the nurse couldn't help but wonder if anyone would mind her taking a kip in here.  Of course she'd never do it, but the room just seemed to expel sleepiness.  She yawned.  She'd only been on her shift fifteen minutes.  It was going to be a long night.  



\thoughtbreak



When they reached the commercial district they had exited the taxi and had paid the fare.  Most taxi companies now took payment up front, but this one liked the touch of the good old days.  Jolie had been expecting to pay more for her trip, but seeing as they had stopped sooner than expected, the price had been proportionally decreased.

They had walked past several outside shops and Jolie had tugged Kiele into the main shopping precinct.  It was beautiful in there and for a moment Kiele forgot about her day completely.  They walked past an electronics store, which had been eager to show them the latest in home entertainment and media management.  They pressed on through, for Jolie was on a mission.

Jolie had suggested that they first hit Mount Taleberg, a well known and highly sought after fashion outlet.  Kiele had protested that they were far too expensive and that there was just no point in even looking.  Her teacher had insisted that they try, after all there might be a sale on, she had dreamed.  

Jolie and Kiele both lived in a fairly affluent neighbourhood, considering the world around them and they could afford to treat themselves once in a while.   'Today was different though,' thought Jolie.  It wasn't about her at all.  Today was all about Kiele.  Her plan was to find a dress that Kiele found absolutely irresistible and buy it for her as a thank you gift for looking after Zane.

They stood in front of the store.  It really was quite magnificent.  There were stone pillars, quite clearly not made of real stone, adorning the entrance on either side.  Above the top of the entrance, a slogan was carved into a horizontal slab of stone.  ``If it ain't Taleberg, it ain't unique.''



\thoughtbreak



It was an odd slogan.  It implied that every other store copied their style and designs, when the truth was almost the reverse.  Taleberg had been sued many times over their twenty year history for  creating what was known in the trade as fusion pieces.  They would take two designs from two highly successful stores and merge them together to create a unique item of clothing.  It was true, the clothing was unique, but Taleberg designers never had to do any real design work.  

The fashion industry had been up in arms.  Designers had filed law suits left, right and centre, but none of them could stop the awesome force of Mount Taleberg.  The red carpet events were littered with outpourings of their designs.  Partly because they were so highly fashionable, but also because Taleberg bribed celebrities into wearing their outfits in return for ridiculous sums of money.



\thoughtbreak



Kiele was the first to break.  She almost ran inside.  It couldn't be classified as running as she had kept both feet on the floor at all times.  It was more of a power walk.  She started to pick out a few items of clothing and hold them up against herself.  She yelled over to Jolie who smiled and walked inside.  Her plan appeared to be working.

As Jolie entered, she noticed the tall security guard eyeing Kiele as a potential shoplifter.  He kept his vision fixed on her whilst he moved his hand to press the button on his comms device.  He opened his mouth to speak, but Jolie got there first.

``She's with me,'' she said.  The guard looked at the young woman before him.  She was pretty, very pretty.  He looked back across at Kiele and then back to Jolie.  

``She's my daughter'' Jolie offered.  This seemed to grease the right wheels with the guard and he nodded knowingly.  His mouth closed and his hand dropped back to his side.  He rolled back on his heels and began to survey the shop once more, piercing each customer with his razor sharp vision.

Jolie left the man's side and walked over to Kiele.  She was beside herself with excitement.  ``Look Jolie,'' she said excitedly, ``this one's actually half price.''  Jolie looked at the price tag.  If this was half price, her brain didn't want to do the mathematics required to calculate the full price.  

``Wow,'' said Joile genuinely enthusiastically as she felt the material, ``that is a really nice top.''

The two of them continued to walk around the shop, one occasionally calling the other other to look at a particular item that had caught their fancy.  Kiele had never been on a trip like it in her life.  Having never had a mother, and living with her 'demented' father, the only items of clothing she had been allowed to buy were of the cheapest brand possible.  

She hadn't cared, not being one of the fashionistas, but it had pained her occasionally to see all of her friends in beautiful dresses, and yet there she was in the latest tat.  Mark had never understood.  He had never wanted to.

As they rounded yet another long rail of beautiful clothes, they hit upon something different.  Taleberg was known for their slightly kooky looking fashion, but what stood before them was a truly beautifully dress.  It was made from a silky material and had a floral pattern on it.  The print was made up of mauve and white flowers but from afar it looked like a pale shade of pink.  The skirt was slightly gathered and it flared as it reached just below the knee.  The back was left with a large piece cut away, starting wide at the top, before tapering to a point about five inches from the base of the spine.  

Kiele walked towards it in pure awe.  It was beautiful.  Nothing too special, but so feminine and pretty.  The material was a soft cotton now she had taken a closer look, lacquered with some kind of spray.  She reached out to grab the price tag, but her companion stopped her.  

``How about you just try it on first,'' Jolie said.  Kiele, who had wondered why she had been denied access to the tag smiled.  She took the dress and as she walked away heard Jolie say, ``Don't look, just try it on.''

In the dressing room she mused over the day as she carefully undressed.  Her body was red in places with scratches and grazes from the events proceeding, her emotions had also taken quite a beating.  She had been able to cope with Zane, just about, but the addition of her father had been too much.  She adjusted her bra straps, making herself feel a little more comfortable.  She picked up the dress and slipped it over her head and onto her slim figure.  It fit perfectly.  She stood and looked at herself in the mirror for a good five minutes.  It was the most beautiful she had ever looked, or felt.

The young girl put both of her hands up to her hair and pulled it into a bunch at the back.  Two shorter strands of hair fell out at either side of her face.  'Not bad Kiele' she said to herself, 'not bad.'  She heard a titter of laugher coming from a nearby cubicle.  She really hadn't noticed that she'd said it out loud.  She released her hair, ruffling it and blowing a kiss into the mirror.  She had never felt so good in all her life.  How ironic that it was her teacher that had been the parent she had always wanted?  She guessed it often happened like that.  

Kiele replaced the beautiful dress with the denim skirt and brown top she had been wearing earlier.  Her father, the pig, hadn't even brought a change of clothes when he'd come to try to drag her home.  What an ass.  Her top was covered in dust and dirt.  No wonder that security guard had given her a funny look upon her entry into his domain.

Though Jolie had told her not to, it was too hard to resist looking at the label.  After all Jolie had told her to 'try it on first' and she had.  'She technically wasn't breaking any....' her brain stopped as she noticed the price.  39,000,000emb.  It was about the same price as as two weeks work.  Even for the upper class it was an expensive purchase.  Something you 'invested' in rather than bought.  

She felt a little dirty.  There was no way she was worthy of trying on a dress like this.  It was far too good for her.  As she pulled back the curtain of the changing rooms she noticed the how heavy the dividing fabric was.  She had been in far too much of a rush when she entered, and had thrown the curtain closed, not really caring if it was properly concealing her or not.  Now she had the opportunity to feel how out of place she really was.  This wasn't her world.  She didn't deserve it.  



\thoughtbreak



Jolie hadn't expected to see him so soon, she certainly hadn't expected to see him right now.  As she had been waiting for Kiele to emerge from the changing room she had spotted a rather odd looking figure standing about twenty metres away.  It wasn't a particularly cold day, yet here was someone wearing a huge overcoat, topping it off with a large hat.  The colour of the two items of clothing were a dark brown and they stuck out like a sore thumb against the bright blue of new denim jeans.

Ruben, now seeing Jolie was alone, quickly walked over towards her.  She had recognised his figure the moment she had seen him, even though she hadn't seen his face.  His walk was hurried yet slow at the same time, the size of him presumably being the culprit for making him looks so awkward whilst doing the most ordinary of things.

``Are you following me?'' she asked the huge man.  She was a little concerned.  They had only met the once and here was this guy, legendary or not, creeping up on her in public places.  It just seemed wrong.

``No,'' he said, ``but I need something from you fast.''  His voice was wavering and now Jolie could see his face she could also see he was in a little bit of a panic.  It didn't surprise her, the clothes gave away the fact that Ruben hadn't been outside properly in a long time.  What could he possibly want from her?  She hoped Kiele wouldn't come out whilst Ruben was there.  That was an explanation she didn't want to have to produce.

``I don't understand,'' she said, ``how did you know I was here?''  It was a very good point.  If Ruben hadn't been following her since earlier in the day, how the heck did he know where she was.  In truth she wanted to know the answer, in truth she also didn't.

``It's not important now,'' he snapped quickly before seemingly getting to the point.  ``Your students, the ones in the accident?'' he asked.  

``Yes?'' enquired Jolie.  It was highly probable that the news story had broken by now, they never stayed quiet for long.  Journalists were like vultures these days and she was almost surprised no one had swooped to try to interview her already.  

Ruben continued, breaking her trail of thought, ``Did they say anything about any writing on the train?''  Jolie's face turned to one of utter confusion.  Writing?  What the heck did he mean?





