\chapter{34}
\section{}
The Experiment  

``And this will be your room'' said Mark as he opened the door to a box shaped, but entirely roomy area.  Zane was actually quite excited.  He hadn't had his own 'room' since living with his parents.  Even though now he had an entire apartment to live in, having just one room that was his own seemed to feel more special.  

The curtains were blue and fairly light, allowing some sun into the room, whilst blocking the majority at the same time.  There was a bed at one end of the room, with a blue duvet cover over it and a string of cupboards along the wall containing the window.  The carpet was once again blue, but this time a much deeper shade, a very regal, royal blue.  It was also very thick and made Zane feel like a VIP as his feet were cushioned by its rotund fibres.  The boy couldn't wait to take off his shoes, so he could feel the carpet licking his toes as we walked across it.  A private little fantasy.

The rest of the house had been shown to him in moderate detail.  There were no surprises, it was an average house.  Zane did however notice that unlike most abodes, this one actually had a loop around all the major rooms on the bottom floor.  The hallway, containing the downstairs bathroom and his and Kiele's room, joined up with the kitchen which ran along the other side of the hallway.  The kitchen then ran along until it met a small dining room, before hitting the lounge.  The lounge had another exit also, and this led back into the hallway again, creating a circular feel to the property.  Zane liked it and was positive that some Feng Shui practitioner had designed it with flow in mind.

The house had been decorated to modern standards.  Very little wallpaper was present, except perhaps to accentuate various features.  Most of the walls had been painted and some even had the new LumiChoice coating, which allowed the owner to change the colour of the walls as they saw fit.  Most rooms were fairly bland in nature, his actually being one of the more colourful specimens.  

Zane had been surprised on his travels that he hadn't seen more images or evidence of Kiele's mother.  He knew she had died before Kiele had been born, but somehow the house felt devoid of her presence.  He had expected some older photos of Mark and her to be dotted around.  Maybe the pain was too great, he had concluded.  Maybe it was just Mark's way of dealing with it.

It was almost like a dream walking around the house.  It felt like Zane was home again.  He hadn't been in a family home for almost two years, though inside it seemed a heck of a lot longer.  It was going to be fun to live here for a while.  He had to keep reminding himself of that.  It would only be for a while.  His mind had gotten carried away at several points around the tour and he had imagined having birthdays and Christmases there.  It had saddened him when the realisation had set in that by all accounts that wouldn't be happening.

Christmas especially, was a lonely time for Zane.  He had spent his last Christmas in bed most of the day, rising only to relieve himself and cook a Sunday roast for one.  Though he had been alone, he had actually quite enjoyed it.  He had sat there reminiscing about Christmases past, his mother's dinners, his father's speeches.  No Christmas was the same without them, but Zane had entered a new part of his life now, a part where he had grown up.  

Most of his spare time was spent studying and he found little time for socialising or recreation.  To be honest, he didn't feel the need.  He enjoyed learning; it was what he was good at.  He had his workbench in his apartment where he could try out moderate physics experiments, ideas and theories that he hoped one day would come to fruition.  Occasionally he would allow himself an old action movie to watch, or a graphic novel.  It wasn't much, but it was all he needed.  It satisfied his mind.

Now he had Kiele, things were different.  He wanted to get to know her, to really get to know her.  They had talked a lot at the hospital, but the setting never really lent itself to deep conversation.  Mostly they had just been idling chatting.  It was scary in a way how much he felt he had changed since meeting her.  If someone had told him prior to the accident that he would throw himself in front of a train to protect a young girl, he wouldn't have believed it.  He would have been ashamed to admit it, but he most certainly wouldn't have believed it.  Things were different now.  He had met Kiele and she had turned his life upside down.  Quite literally.  

``So what do you think Zane?'' asked Mark

``You have a fantastic house,'' he replied.  ``And once again, I'm really grateful to you for letting me stay a while.''

``No problem,'' said Mark, ``it really is our pleasure.''

Zane felt a slight twinge and his back suddenly flinched in pain.  He grabbed at the pain aimlessly, knowing full well that it stemmed from deep inside and couldn't be quashed by scratching at his skin, or poking it.  Kiele rushed to his side and put an arm round him.  

``You've probably been up for too long,'' she said, ``Come on, sit down for a while.''

Zane obliged, sitting on the end of his new sleeping apparatus.  Mark helped him to lie back and Zane thanked them both.  

``We'll let you get some sleep now, just shout if you need anything.'' said Mark.

``I'm just in the next room,'' said Kiele, ``so I'll be straight in if you need anything.''

Mark left the room and Kiele was left standing over her hero.  

``Kiele?'' said the boy, ``would you mind staying a while?''

She smiled and said, ``you're supposed to be getting some rest.''  He looked sad, ``Let me go grab a book and I'll sit in the corner and read.  Is that OK?''  He nodded.  As she left the room she thought about how fun it was going to be having Zane staying in the next room.  Then she remembered Mark.  She just hoped she could keep the two parts of her life separate enough that she didn't go mad.



\thoughtbreak



It was the first time that Kiele and Mark had eaten dinner in the same room for years.  Even when she was younger he had dished up her meal, walked into the lounge and then slammed the door behind him, always making sure he slammed the door to the hallway too.  Sometimes it had upset her and she hadn't eaten anything, instead she would retire to her room and cry until the pain subsided.  As she had gotten older, she had begun to take her meals to her own room out of habit.  

Today was totally different.  Embarrassingly she had been caught out, trying to take her meal back to her room.  It was such a common reaction to dinner time that she had completely forgotten that Zane was with them.  Mark had called after her, saying something like, 'And where do you think you're going young miss.  We eat our meals together remember?'

She hadn't answered back, but it had been hard not to.  She had to get used to Mark's new little game.  There had been many over the years, but this one was something new.  It felt entirely unnatural.  Mark was being nice.

Kiele looked down at her plate, consisting of meatballs and spaghetti.  Honestly, Mark wasn't a bad cook at all.  He had really made an effort and had even opened a bottle of wine, which only Zane was denied.  His medication prohibited him drinking alcohol completely, not that it worried him, he rarely ever drank.  Kiele was sipping her wine slowly and watching Zane, who was already half way through his meal.

``So Zane, I hear you're quite the physicist?'' Mark asked.

``I dabble mainly,'' came the reply through incessant chomping, ``Though I have had some success proving Vikrali's theorem of Quasi-linear field growth for meta states of sub series particles.''  He had been concentrating so hard on filling his face he hadn't noticed the two other participants at the table stop and look at him in genuine surprise.

Mark looked at Kiele and raised an eyebrow, impressed at the young boys aptitude for the language of science.  Not that he had known what it meant.  For the first time, Kiele actually found something that Mark did funny.  She giggled at his expression.  Maybe it was because she was tired, but it had been pretty funny, 

'Quasi-field growing meta theorems.'  Suddenly she realised the wine was beginning to affect her.  Her usual stiff stance against her father had been broken.  Had it been part of his plan, perhaps, but it would more that likely be a coincidence.  She hadn't drunk alcohol often, and never in front of Mark.  No it was far more likely, that her merriness was entirely her fault.

Zane looked up at his house mates and laughed.  

``I'm so sorry,'' he said, ``living on my own, nobody really cares if I go on about physics or not.''  

``I hope you're a deep sleeper Kiele, or you're going to be hearing lectures on Quantum Mechanics through the walls in the middle of the night.''  They all smiled again and Zane grinned as he filled his mouth with his last forkful.

``More Zane?'' asked Mark.

``No no,'' he replied, ``I couldn't eat another bite, but thank you anyway.''

Mark tipped his head in acknowledgement and retrieved the bowl which he had offered to Zane.

Kiele had decided to say very little.  She couldn't risk getting into a fight with her father, or saying something stupid in front of Zane.  Her head was spinning a little now.  She wasn't drunk, just very merry.  It had only taken one glass of wine and suddenly she felt rather ashamed.  She had always believed she could hold her alcohol, not that she had ever put it to the test.  Now she knew otherwise.

Zane placed his knife and fork down and sat back.  He rubbed his belly clockwise with his left hand as the food began to settle in his stomach.  It had been a good meal.  He had forgotten how much he missed eating with others in such a relaxed environment.  Sure he did it everyday at school, but it wasn't the same.  It wasn't an intimate setting.  He picked up his glass of fruit juice and sipped it slowly.  It was sweet with a hint of bitterness, comprised of various summer berries according to the label.

He let his head roll back slightly, expressing some of the tension in his neck, but also relaxing, in the company of friends.  His mind drifted to Kiele sitting next to him.  She was unbelievably cute, even more so when she wasn't dressing up to go outside.  Her hair was a little dishevelled and her eyes shone in the dim light of the dining room.  It was almost a romantic setting, and Mark had called it a celebratory dinner at Zane's recovery and his staying with them.

Zane stretched his feet out into the area under the spare chair.  There were four chairs encircling the table, and only three of them were engaged.  Mark and Kiele were still eating, Kiele being the slowest.  It was quiet, perhaps a little too quiet, yet in their own way, each of them were enjoying the time together, even Mark.

``Listen Zane,'' said Mark, attempting to appear as if he was getting down to business, ``I have a little physics experiment you may be interested in.''

Immediately, Zane was on the alert.  Kiele would have been, but her current state of mind meant she was more interested in the folds of her napkin, than the current conversation.  She wasn't drunk, but the word physics had been mentioned again, and she was in no mood to engage in a conversation that she really didn't understand.

``What kind of experiment is it?'' asked Zane.

``It's a little complicated to explain,'' said Mark, ``how about I show you first thing tomorrow.''

Zane nodded.  ``Sounds great,'' he said.

Mark finished up, and the two men sat there waiting for Kiele.  Eventually she caved and pushed her plate away from her.  She had gotten through most of the meal and to be honest she found it rather enjoyable.  She hadn't actually eaten a meal from her father in a while, mainly because he usually only cooked for himself now.  Kiele wasn't a bad chef either, she had learnt to make herself pretty much most dishes.

They sat there for a few minutes before Mark got up and began to clear the dishes.  Zane stood to his feet and attempted to take over the task, but Mark stopped him.

``You've barely been home for a day kid, rest up, they'll be plenty of time for helping out around the place.''

Kiele tugged at his sleeve and the injured party sat back down.  He didn't like being told he couldn't do something.  It made him feel inferior.  Perhaps it was teachings from his father, perhaps just a perception on his part.



\thoughtbreak



Mark usually commanded the lounge, but today he had remained in the kitchen clearing up and had instructed Kiele to take Zane into the lounge and watch TV.  Kiele had done as her father had asked, with a constantly suspicious mind.  Was he going kick the door down in five minutes time, yelling and screaming about something entirely not her fault?  What was he planning?

They had both sat down on opposite ends of the sofa, each hoping the other would move closer, but neither wanting to make the first move.  In the end it was Kiele who had shifted closer to Zane in order to help him figure out how to use the media control device.  That had been the premise anyway.

Now she was there, sat only inches from him.  It wasn't as if she hadn't been this close to him before, but the setting, the environment was different.  In the hospital, there had been other people around, at school there were hundreds of kids, even at the Zone there had been the looming sound of the high street outside, just a few steps away.  In her own home it was different, almost intimate.

Kiele wanted to kiss him again, but knew she couldn't.  She was watching him, watching the TV.  Out of the corner of his eye, he could see her.  She had her head cocked to one side and she was playing with one strand of her hair repeatedly.  Both hands had joined in the ritual of stroking this one tiny section of hair as she watched him unrelentingly.  His lips moved slightly as the characters of the film talked about something entirely uninteresting to her.  It was getting too much to bare.  She threw her body towards the sofa and started watching TV too.

The screen was around fifty inches in diagonal, recessed into the wall and clearer than a photograph.  The TV, a Sonia X501, was one of the best on the market.  A re-run of a classic sitcom was currently being displayed and the two of them sat there, now closer than ever, watching, waiting.  

Eventually Kiele could take it no longer, and she rested her head on his shoulder, taking hold of his elbow with her hand.  Zane knew he had worn a tee-shirt for a reason.  Her touch was so gentle, so feminine.  Once again he could feel her heat passing through into his body.  Her hair fell across her face and with her spare hand, she carved it aside so as to be able to see the screen a little more clearly.  Her heart was pounding now.  This was the closest they had ever been.  

Mark was hovering in the doorway, seemingly undetected by the two teenagers sitting on the sofa.  He watched as Kiele, his 'daughter', appeared getting closer to the boy.  As long as he was able to keep his concentration on the device, things would be fine.  Mark turned and walked away.  He would play Mr Nice Guy for as long as it took, but if Kiele over stepped the boundary, his boundary, then he would bring her down hard.

Zane knew Mark had been standing there, his senses were as sharp as Bethany.  He put his arm round Kiele and gently tickled her side with his nails.  She flinched a little and giggled.  With her other hand she flattened his hand against her side an held it there.  This was what she wanted.  She felt so warm, so safe, and in her own house too.  She'd never thought she could ever feel this safe in her own home.  Whatever happened, Zane would look after her.  Zane would protect her.







