\chapter{19}
\section{}
Under Contract  

She wasn't sure if the address was correct, but the description of the house appeared the be accurate.  The bent bicycle wheel and the old cushions suggested that this was definitely the place she was looking for.  It was a fairly rough neighbourhood.  Had she been going there at any other time in the day she would have been particularly frightened.  As it was, the sun was high in the sky, and the usual hustle and bustle of the commercial district spilled into this otherwise quiet town.  

A car behind her suddenly sprang into life, taking her by surprise.  The vehicle sped off, leaving a trail of dust in the air and a bad taste in her mouth.  'Idiot', she thought.  She'd walked over five miles to get here and she certainly wasn't about to give up now.  This could be it, the place she'd been in search of for many years.  A place of refuge, but also of vast amounts of information.  Could it be?

The door bell was fingerprint activated, installed by the needlessly paranoid, it gave the occupant of the house a way to verify who was calling.  She pressed her thumb to the plate, and a soft buzz was heard.  Removing her thumb, she saw her fingerprint fade from sight.  A bell rang inside somewhere, but she couldn't locate it.  It sounded faintly like an old fashioned alarm clock.  She put her hand back by her side and waited.

After a while, a voice spoke over the intercom.  ``Yes?''  She had expected more but there was nothing.  The question was repeated again, but slightly more aggressive.  

A little nervous, she replied to the voice, ``I'm looking for Michael Stapes.''  The intercom seemed to cut out.  The light which had indicated someone was listening vanished.  Was that it?  Had the occupant decided against engaging in conversation?  A buzzer sounded somewhere close by and it sounded as if the door had clicked open.  She gingerly pushed it forwards and walked through the hole it created in the wall.

Inside the house was an absolute tip.  There was mess everywhere, echoing the look of the outside in a much more real way.  A man walked towards her.  The lighting was so low that she could hardly make out his figure.  All of the curtains had been drawn for maximum removal of light.  The occupant was either photosensitive, or rarely entertained guests.  No shoes on his feet, the figure walked closer to her before stopping about a metre away.  She could just about make out the shape of a man.

``Are you Michael Stapes,'' she asked conservatively.  The reply was nothing like what she was expecting.

``I guess so''

She decided to push a little further, he seemed harmless enough, if a little weird.  ``Well are you or not?''

He became aggressive and she could see for the first time a bottle of what appeared to be alcohol in his hand.  ``This is his house isn't it?  Do you see anyone else here?  If I'm not Michael Stapes then who the hell is?''  He was shouting now and had taken several steps forwards.  She step backwards in fear, not noticing the pile of old magazines at her feet.  She tripped backwards and fell.

She was surprised when she didn't hit the ground and all of a sudden noticed an arm cradling her.  The figure had prevented her hitting the ground rather effectively.  Had light been a little more prevalent, it could easily have been the final scene in a superhero movie as the figure triumphantly held his girl.  A gust of cold air navigated its way down the hallway and ruffled her skirt, sending a spine tingling sensation down her back.  

``I apologise'' he said, helping her up.  ``That wasn't meant for you.  The truth is I haven't had many visitors lately.''  He flicked on a light switch and the room was dimly lit at last.  It was suddenly apparent why he preferred to live in a dimmer world.  His face had been disfigured in places.  He gestured to her to follow him and the two of them made their way to the kitchen.  On the way they past piles of boxes of various description.  It appeared that Michael had moved in, but never unpacked.

The kitchen was much cleaner than the rest of the place and it certainly came as a breath of fresh air.  The window was open too, which blew in smells and ideas from the commercial district, still buzzing.  He began to make a coffee for himself.  He needed something to sober up.  He offered the coffee granules to her and she nodded, saying, 'yes please.'  She never usually drank coffee,  but in this case, she was willing to make an exception.  She sat down on one of the bar stools which had been placed next to a breakfast bar on which Michael was now brewing their beverages.

The kitchen was small but most definitely comfortable.  About three to four metres in length and width, it seemed luxurious, but without the added headache of being a nightmare to clean.  It was quite obviously taken good care of, perhaps it was the only room that Michael lived in.  She took the time to study the items in the room.  A huge fridge stood in the corner, one of the ones with the built in media centres, so you could bake to the sound of your favourite song, or watch a TV show during breakfast.  There was a dish washing machine in another corner, almost as big as the fridge.  It looked untouched, and it wouldn't surprise her if it had never been used.  If he really was the only one living here, she couldn't imagine he got through much cutlery or crockery.  

``I pretty much live in this room'' came a voice.  He seemed sad and confused.  He had no idea why she was here, yet he was treating her like an old friend.  Perhaps, she mused, he just needed someone to talk to.  By the looks of the house, he had been living here alone for quite some time.  He pushed the now completed coffee towards her and she took a sip, noting the abnormally high temperature of the liquid and the abnormally high coffee flavour.  He clearly didn't make coffee too often either.

She had to start talking, but was afraid to.  She knew she must say something soon, else it would have appeared that a stranger had just walked in off the street and sat down for a coffee with this odd man.  She had been looking for him for a long time.  Now she was fairly sure she'd found him.  The pieces fit, but she had no idea how he was going to react.  Michael Stapes may not take kindly to what she was about to say.  

She offered up some idle banter to pass the time, whilst her courage brewed.  ``Have you lived here long?'' she asked.  

``Long enough that I've forgotten anywhere else that I've lived'' came the reply.  It was definitely meant to be solemn, even a little depressive.  Until now the man had been standing a few steps away from her on the other side of the breakfast bar.  The bar had incorporated an overhanging section of shelves, containing fruits and spices.  Except in this house the phrase was, once containing fruits and spices.  A lonely apple and a small jar of pickles were the only things adorning these shelves.  The section had made it difficult for her to see Michael, and she had spent most of the last few minutes with her neck bent, trying to watch him as he spoke.  Upon realising this he moved forward and sat down.  

They now faced each other, eyes making contact.  She was a little scared, but she couldn't have imagined how scared he was.  Eventually he snapped, the tension had been brewing in him for a while and when she had offered no explanation to her visit he had assumed one instead.  Living on his own for so long seemed to have zapped his patience.  It appeared, however, oddly normal.  

``There's no need for you people to keep checking up on me,'' he said, lowering his head and looking into his coffee.  He dipped one finger in the beverage and she winced.  How could he withstand that heat?  He withdrew the finger and made a small droplet of coffee rest on the surface of the breakfast bar, his finger red and most certainly burnt.

``I'm not checking up on you,'' she said.  ``I came here to talk to you about something.''  He appeared to be listening but she couldn't be sure.  She added, ``Something that you may not want to talk about right away.''  Still his head stayed down.  The coffee his main focus of attention.  Part of her wanted to swipe the mug from the bar, but doing so would probably have invoked a rage from this well built man, and she certainly didn't want to do that.

``Go on,'' was his reply.  He continued dipping his fingers into his drink and making droplets on the counter.  After a few more, she could see he was making a geometric pattern of some description.

``My name is Jolie,'' she said.  ``For a large portion of my life I have been studying something.''  No reaction from the beast.  ``Something which happened many years ago,'' still nothing, ``which I believe you may have been involved in.''  She sat back to take a breath.  That had been harder work than she had imagined and she still hadn't really told him the real reason for her visit.  ``I'm here to talk to you about Oken Brown.''  

She had expected some kind of reaction.  She had even planned for it, a can of mace in her bag, but what happened was completely unexpected.

``How did you find me?'' he enquired.  He was past the point of caring now.  It had been so many years since the events of old.  He wondered if it even mattered any more.  Officially he was still bound to secrecy over the events that had taken place.  Officially, if the G-TEP found him talking about them, he would be obliterated.  They always liked to scare people.  There was never any talk of people being killed.  In their terms and agreements people would always be subjected to summary obliteration.

Jolie was so taken aback by his candid response that it was a good few minutes before she could find the courage to talk further, so much so, that Michael looked up to see if she was still there.  It had suddenly occurred to him that this woman was actually quite beautiful.  She reminded him of someone he once knew.  

``A friend gave me your name,'' she said.  That was the truth.     Michael didn't need to ask anything further, he already knew who that friend would have been.  How she had become acquainted with them would probably be a whole different story but that he didn't care about right now.  

``I guess you'd better ask your questions then,'' he said sullenly, ``since you clearly have no interest in me.''  It wasn't that he really cared either way, but he rarely had visitors and if they weren't trying to sell him bibles or broaches for his 'significant other', they were checking up on him.  Making sure he was obeying the rules.  Why they hadn't just installed CCTV throughout his house he'd never understood.  It would have made things a lot simpler.  He'd even suggested it at one point.  They had reeled off some passage from their code about privacy policies or something equally stupid.

The world of the day was odd when it came to rights, especially for the G-TEP.  Peoples privacy was paramount, so sacred, that nothing could break it, but to that very same organisation, peoples lives clearly meant very little.  The G-TEP was permitted to kill anyone it deemed necessary, but they couldn't install CCTV for surveillance.  The whole system reeked of convenience and he hated it for what it had become.  No one respected life any more, but privacy was paramount.  His doorbell was a testament to that fact.

She drew in a deep breath and plunged in her first question.  ``What was he like?'' she asked.  It had seemed an odd one to start with, but she needed to just dive in there, no more time for thinking and analysing the best method of attack.

``Quite simply, he was the greatest friend a man could ever have.''  His focus now on some distant object hovering in the sky, she supposed he was recalling memories of a lost comrade in arms.  ``He took care of them, like they were his family.  He never got on well with his real family, not after they sent him off to war.  He never really recovered from that you know?''  

It was believable, the war had been described by many historians as the most brutal clash between human factions that the world had ever seen.  One side broke the rules, the other side did even worse and it escalated from there.  People had been gassed, maimed, tortured, beaten, you name it.  All in the name of protection and a love for one's own country.  It seemed more like it had been in the name of aggression and a hate for another's country to her.

He continued, ``He met a girl, just before he died,'' his eyes glazing whilst recalling, ``she was sweet, oh she was the sweetest thing you'd ever seen.''

She interrupted him ``This was Jay?'' she asked, ``the woman he had been living with for a few years?''

``No,'' he corrected her, ``the two of them never shared a house.  They had only known each other a short period.  I could tell they was meant for each other though.''  He smiled as his eyes began to well slightly.  Jolie smiled too, this was incredible.  Very quickly she remember that it would probably have been best she took some notes.

``Would you mind if I wrote some of this down?'' she asked.  He shook his head, most of what he said would could have easily been conjecture and speculation anyway.  

``No names,'' he said, ``that's all I ask.''  She nodded.  They were reasonable and acceptable terms.  The midday sun streamed in through the window and onto the breakfast bar.  Both occupants of the kitchen had their hands and lower arms on the bar.  The suns rays heated her hands to the point where she withdrew from the sunlight.  It seemed strange that he had chosen this room as his refuge from the rest of the building.  It was the only room that was lit adequately, every other room drenched in a thick darkness.  When the door to the kitchen had been opened, it had been like walking into heaven.  It was warm, inviting and felt safe.

Jolie pulled the pen and notepad from her bag.  A small book, with a leather binding, crammed full of her knowledge about Oken.  She had once been asked why in this day in age she still kept a physical notebook.  Most people would have used voice dictation device and stored it on a memstick.  She preferred actually writing things down, then she knew that she had actually seen the information first hand.  All the virtual technologies seemed rather unreal to her at times.  Plus in the late evenings, she could flick through her notes and muse about the man and his methods, often spending hours at a time thinking and feeling.

``Did he have many friends?'' she asked.  

``A few,'' he replied.  ``He was well respected in the community, both in the Zone and near his house.''  He corrected his bad sentence.  He had never been good with words but he felt like this lady needed him to be.  So each of his answers he thought out thoroughly before uttering.  ``What I mean was, in his in his local area.''  It still didn't sound right, but he had tried.  Jolie jotted something down that Michael couldn't see.

``How come you're still alive?'' was the next one.  It shocked Michael to the core.  She was jumping all over the place and it had thrown him for six.  He hadn't expected a blunt question so soon.  Jolie, noticing his expression apologised.  

He shook his head, informing her that a sorry wasn't necessary, ``It's OK,'' he added.  ``The G-TEP took great pleasure  in torturing me for information.''  He pointed to his scars.  ``In the end I made a deal with them and I gave them information in exchange for my life.''  He seemed sad.  It was as if he had been broken again right before her eyes.  

How terrible it must have been, to hold out for so long, to have been inflicted with so much pain, and then to have relented at the end, making all the suffering null and void.  It sickened her that the G-TEP were able to get away with such atrocities, but the world was what it was now.  

``I never told them what they really wanted to know though,'' he said.  ``I never gave them everything.''  He appeared to take great pride in this and his face lightened when he told her.  ``They pushed me for days, weeks, months even'' he said, ``whipping me, punching me, cutting me, I gave them something, but not what they were really after.''  For some reason he trusted her, she seemed so genuine that the words gushed out.  Maybe he had just decided it was time to let go, time to stop caring.  Plenty of times he'd thought about ending it all.  She sat there listening intently, her forehead held up by her two fingers and thumb.  She looked at him in disbelief.  He'd been through a lot.  He'd truly been to hell and back.  

``Did you know him well?'' she asked tentatively.  He sat back and chuckled to himself, obviously remembering something, an inside joke maybe, or something other than the bad times.

``Lady, he was my best friend,'' said Michael.  ``There was nothing I wouldn't have done for that man.''  He was smiling broadly now.

``You still think about him often don't you?''

``I think about him a lot,'' he said, ``I pray for him a lot too.''  His faced became more sincere and saddened a little.  ``That man needed a lot of prayer for what he'd done,'' and just like that he became more upbeat again, ``I sure do hope he's in heaven now, then one day I can see him again.''  He looked at her directly in the eyes, as if telling a secret.  ``If I get there that is.''

He was a simplistic man, she thought.  Not mentally challenged, just simple.  His needs were few, that much was obvious, but the G-TEP had taken everything he had, that was painfully obvious too.  She waited a while before changing the topic again.  ``Have you always lived alone?''

Michael thought long and hard about this.  He felt weak and wasn't sure he was able to recall any more of his history.  ``Yes,'' he answered.  It was a lie and he felt terrible for lying to such a pretty young woman, but he had no choice.  He just wouldn't have been able to take it.  The memories  were painful, sometimes too painful.  

Jolie had finished off her coffee and was trying to write down more of her notes.  She was noting not only the answers which he gave, but also her perceptions of his impressions, his life.  As she sat there a small tabby cat pushed it's way through the door.  It was barely a year old, still kitten like and oh so cute.

``Yours?'' she asked.  At first, he didn't know what she was talking about.  The fridge?  The breakfast bar?  The house?  Finally it clicked, she was talking about the cat.  He nodded, and bent down to stroke the feline.  

``Benzo'' he said abruptly.  

``Benzo?'' she replied.  This time she was the one who was confused.

``Her name is Benzo.''  The realisation set in and Jolie's mind was once again in a state of cohesion.  Benzo circled the stool which Michael was sitting on a few times before he managed to scoop her up and place her on the bar.  She wandered over to Jolie and sniffed her inquisitively.  Jolie giggled.  She hadn't seen a kitten like this in a long time.  Michael pointed over to a saucer that was sitting on the counter behind her.  ``Would you mind?'' he asked.  Jolie realised he was asking if she could pour some milk for the little kitten.

``Sure,'' she answered.  She walked over to the fridge and cowered in its presence.  It was truly stupendous, far too large for a single man's needs.  She opened it and was markedly unsurprised at the lack of anything inside.  On the right were several cartons of milk.  Most of which seemed to be edging towards the out of date checkpoint.  As she looked closer, she could see they were lined up in date order.  It really was like a race to the finish.  Who would reach their use by date, before being drunk.  

Michael noticed her looked at the milk.  ``Yes,'' he said, ``they are all open.''  She hadn't been looking at that, or for an explanation, but since he had brought the subject up she took the opportunity to ask.

``Any particular reason why?''

``My brain doesn't work so good in the mornings.''  He chuckled a little, ``it's kinda of a leftover from what they did to me.''  Michael was of course referring to the savage beatings and torturing he had received at the hands of the G-TEP, his fellow countrymen.  Glancing over her shoulder, Jolie could see him rubbing his forehead in apparent pain.  He continued, ``but then, I guess I can't put the blame squarely on them.  After all, I was there and I knew full well what he was doing.  I just couldn't tear myself away.''

Had she detected a hint of regret coming from the large man in the kitchen?  She picked out the newest carton of milk she could find and carried it over to where the saucer was.  

``Bring it over here,'' he said.  She picked up the saucer and placed it on the bar in front of them.  Then she retook her position on the stool and poured some milk for Benzo.  The little kitten was beside herself with joy.  She licked a few times and then scampered around to the other side of the saucer in apparent joviality.  

The two of them watched the kitten for a while, licking, scampering, looking back at them, cleaning herself, waiting for more milk.  The hairs on the pretty little creature were so well formed, she truly was a beautiful cat.

``Why did he do it Michael?'' she asked softly.  For a second the man seemed to have completely ignored her.  He was in his own little world, watching Benzo beg him with her eyes for more of the white stuff.  After a full minute he came to and realised that Jolie was waiting for an answer from him.

``I'm sorry,'' he said, ``I thought you were talking to someone else for a second.  The name still confuses me.''  

She frowned.  What did he mean?  The name?  His name was Michael Stapes, wasn't it?  He hung his head a little lower, trying to avert eye contact.  If he wasn't Michael Stapes, then who the hell was he.  For a second her mind race with improbable scenarios.  Maybe he was a hitman, sent there to kill her for her constant digging up of Oken's past.  Maybe this man had killed Michael and was squatting in his house, taking on his persona.  After all, she'd never seen a picture of him.  She had no idea what he was meant to look like.  His face was disfigured, maybe there was no beatings, maybe he was from prison, maybe he did it to himself.  Her mind took a breath before continuing it's onslaught.  Her train of thought was caught short by an interruption from what's-his-name.  

``Michael Stapes isn't my original name,'' he said.  She was confused.  The burly man had sensed her confusion after his blunder.  Of course no one was meant to know it was him.  He had been Michael Stapes for so long, but every once in a while he tripped up.  Maybe it was the simplistic mind.  

Jolie decided to mount her high horse.  ``So what is your real name then?'' she almost shouted, speaking a lot louder than his soft confession.  She stood up from the stool, frightening Benzo as the feet scraped on the hard stone floor.  The little kitten leapt down from the bar and ran out of the cat flap.  She watched him go, regretting scaring the little thing.  

Michael stood up and pleaded with her to sit down.  ``I'm sorry,'' he said.  ``I'm not allowed to talk about my past really.  I thought it would be OK if you didn't know my name, and I hadn't had anyone visit in such a long time.''  He seemed really sad now, ``I was just enjoying the company.''  Jolie stood their, her arms now folded, still awaiting an answer from the ogre who had lied to her.

``My name is Ruben,'' he said.  

``Come again?'' she asked.

``Ruben,'' he repeated once more, ``my real name is Ruben.''  

He hadn't needed to add a surname and she hadn't needed to ask for one.  Ruben was a legend of the Zone story.  A defiant figure who stood up to the G-TEP forces and against their oppressive regime.  He now stood before her in all of his glory, but in Ruben's mind he was standing there naked, unmasked and guilty.  She continued to stand there in shock.  Complete shock.  So many times she had tried to contact him, or find out where he was.  Never once anything close to a reply.  She had hypothesised that he had been killed in the massacre, because he certainly didn't seem to have existed on earth any more.    



\thoughtbreak



The truth, was that the G-TEP had done a damn good job of hiding him.  Leon had played a part in the scheme and had played up to Ruben's good behaviour and information, which had led to the recovery of some of Oken's equipment.  Leon and Ruben had become friends during their encounter in the ambulance and true to his word, Leon had guarded and protected Ruben all he could.  

His name had been changed to Michael Stapes and he had been given a small house as a thank you in compensation for the savage beatings and torture he had received.  It was true that the G-TEP global commander had been attempting, for a while, to turn the force into a more caring, more considerate organisation.  Leon had shown great aptitude in this and the commander listened to his recommendations intently.  However, one of the most effective and ruthless of all soldiers also deserved his attention.  Ric had been instrumental in the capture of many temporal mad scientists, hell bent on destroying or reviving something or other.

Ruben had been living at the house ever since.  He had been authorised to move if he desired, but why would he want to?  His past would follow him there too.  Ruben wasn't under house arrest, but he had known they watched him.  Plenty of times he'd wanted once, just once, to visit the Zone again, to pay his respects to his fallen comrade in arms.  Or to visit the graves of his friends.  He had never plucked up the courage.  

The G-TEP kept close tabs on him and visited him every three months like clockwork, ensuring he wasn't divulging information, making weapons, or tinkering with anything remotely linked to temporal mechanics.  At one point he had even joked with a G-TEP officer that he should maybe turn over his watch.  For his insolence, he had received a almighty punch in the stomach.  He had wanted to retaliate so badly, but Jesus and his fear of the consequences stopped him.

Since leaving the Zone and living in this place, his priorities had changed.  Hell, his whole outlook on life had changed.  He regretted his misspent time at the Zone.  He regretted the death of his friends.  He had no one now.  

A few years after the events of the Zone he had tried to search for Yazmine, hoping, praying that she would drop her life for him, that she would see how pathetic he was and feel the urge to care for him, to love him.  A private investigator was hired, and began reporting back information.  She was living in some distant region that Ruben couldn't even pronounce.  Apparently she had a new husband and three beautiful children.  The PI's description of the children had been so accurate that Ruben could have sworn he had seen them in real life.

The G-TEP had stepped in and asked him to cease his activities.  Apparently he was breaking his conditions.  The very next day Ruben, unable to believe them had looked up the conditions of his release.  He saw nothing in there about any private investigators.  True, Ruben wasn't a lawyer, but he understood plain English.  When he reached the end of the document he saw the clause to which they must have been referring;



``G-TEP reserves the right to modify create, and delete any other clauses as they see fit, backdating if necessary, with or without the consent or the knowledge of the persons to which this agreement pertains.''



In short, the G-TEP could to anything they liked.  They could have stopped him keeping Benzo, had they desired to do so.  He had signed his life away and at that point he wished he was dead.  It wasn't Leon's fault at all.  Ruben had been grateful to him for all he had managed to do for his sorry excuse for a soul.  It was Ric's way of having the last word.  As if the scars weren't enough.  



\thoughtbreak



Jolie still stood there dumbstruck.  She couldn't even think of what to say.  Finally after what seemed like an eternity to both her and Ruben she spoke.  ``I am so sorry,'' she said.  ``I never meant to........''  She started again, ``If I'd have known........''  He walked over to her and drew her close.  His once insanely muscular arms gripping her tightly.  She'd had no idea who he really was.  She thought she'd struck gold when it had transpired that he was a good friend of Oken's, but she could never have hoped to meet Ruben.

He continued to embrace her and the tears started to flow.  She'd been so cold, thinking of him as just a pump she could work for information.  It sickened her somewhat.  No, it sickened her to the core.  She'd become almost as heartless as the G-TEP.  She felt his warm arms holding her tight.  It was nice.  She could tell he'd forgiven her for everything.  

``It's OK,'' he said.  ``It's really OK.''  As they stood there locked as one, something started to sing in Jolie's bag.  It was her phone.  She broke free of his embrace and quickly rummaged for it.  In the few seconds it had taken her to find it, the volume of the ringing had increased to an ear splitting level.  It was playing a theme from Beethoven's Moonlight sonata, the third movement to be exact.  She slapped the phone open a put it to her ear and Ruben was left standing there, arms still partially outstretched.  He hadn't hugged anyone in such a long time.  He'd scarcely had time to even realise that it was a hug he had been in the middle of.

He could hear a rather hurried voice on the other end.  Through the ear piece the sound was muffled, he definitely heard something about an emergency.  Jolie listened intently, ``Oh my.......'' she trailed off.  After a few seconds she slung the phone down onto the bar.  ``I have to leave now,'' she rushed.  ``I'm so sorry.''  He nodded and she picked up her bag.  After slinging the phone into it, she rammed the container on to her shoulder and headed out of the kitchen door.

She found her own way to the front door leaving Ruben alone once more.  It had been a short meeting, but an enjoyable one.  Ruben wished she hadn't had to go.  It had been nice to talk to someone who had appreciated him and what he had been through.  He missed talking to Leon.

Now outside, Jolie had all but forgotten about the meeting she had just left.  The phone call had been to inform her that two of her students had been involved in an accident whilst visiting the Zone.  She was beside herself with worry and though she could have walked to the hospital on any other day, today she just couldn't imagine being able to do it.  She really was in too much of a state.  She walked over to the taxi stop and leaned into the window of a vacant vehicle.  The driver asked her destination and she got in.

As the taxi pulled away, she found herself thinking the worst.  Maybe they were dead, why oh why had she let them go there alone?  When she had asked Kaitlin, there seemed to be no doubt in her mind that it was the right thing to do.  It wasn't an official trip, so she hadn't had to jump through the usual bureaucratic hoops that schools employed these days, bringing with them a crowd of job titles that just had to be filled. 

She couldn't even bring herself to look out of the window, preferring to look down at her shoes, deep in shame.  The taxi driver tried to lighten the mood, ``you look like somebody died love'' he said carelessly.  She ignored him.  Until she arrived at the hospital she had no way of knowing.  

